### 2019-01-09 Data Preparation.Rmd
Initializing scrip for data preparation

---
title: "Data Preparation"
author: "DARS"
date: "1/9/2019"
output: pdf_document
---

# Import Data

# Variable Engineering

# Save Data

### 2019-01-09 Data Preparation.Rmd
Including libraries and importing manuals

@@
 ---
+#Libraries:
+```{r setup, include=FALSE}
+
+library(tidyverse)
+library(tidytext)
+
+library(tm          ) # text mining
+library(topicmodels)  #topic modeling
+
+library(pdftools)
+library(ggplot2)
+
+```
 
 # Import Data
+To expand our topic modeling of course content, we would like to analyse the material in the course manuals.
+The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
+```{r}
+corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
+                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
+```
 

### 2019-01-09 Data Preparation.Rmd
Updating Libraries

@@
 ---
-#Libraries:
+# Libraries:
 ```{r setup, include=FALSE}
-
 library(tidyverse)
@@
 
-library(tm          ) # text mining
-library(topicmodels)  #topic modeling
-
-library(pdftools)
-library(ggplot2)
-
+library(gsheet) # import spreadsheets from google drive
+library(tm)
+library(hunspell) # Stemmer
 ```

### 2019-01-09 Data Preparation.Rmd
Create dataframe from Corpus for Course Manuals
Updating date in YALM

@@
 author: "DARS"
-date: "1/9/2019"
+date: "`r Sys.Date()`"
 output: pdf_document

### 2019-01-09 Data Preparation.Rmd
Importing course catalogues

@@
 # Import Data
+
+## Textual Data
+
+## Course Catalogues
+In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
+The corpus `corpus` contains the pdfs of the `5` most recent course catalogues.
+```{r corpus, cache = TRUE}
+corpus <- Corpus(x             = DirSource("Catalogues"),
+                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
+```
+
+### Course Manuals
 To expand our topic modeling of course content, we would like to analyse the material in the course manuals.

### 2019-01-09 Data Preparation.Rmd
test

--- 2019-01-09 Data Preparation.Rmd
@@
 ---
-# Libraries:
+#Libraries:
 ```{r setup, include=FALSE}
+
 library(tidyverse)
@@
 
-library(gsheet) # import spreadsheets from google drive
-library(tm)
-library(hunspell) # Stemmer
+library(tm          ) # text mining
+library(topicmodels)  #topic modeling
+
+library(pdftools)
+library(ggplot2)
+
 ```
@@
 # Variable Engineering
+We create a dataframe from the Corpus:
+```{r}
+
+manuals_td <- tidy(corpus_manuals)
+
+```
+#TEST
+```{r}
+test <- "test" 
+```
 

### 2019-01-09 Data Preparation.Rmd
test
test2
test5
test end
Added titles ("Course Manual" and "Student Data")

--- 2019-01-09 Data Preparation.Rmd
@@
 
-### Course Manuals
+## Course Manuals
 To expand our topic modeling of course content, we would like to analyse the material in the course manuals.
@@
 ```
+## Student Data
 
 # Variable Engineering
+We create a dataframe from the Corpus:
+```{r}
+
+manuals_td <- tidy(corpus_manuals)
+
+```
 

### 2019-01-09 Data Preparation.Rmd
Adding titles ("Transcripts" and "Course Manuals")
Creating lists of AoD and assessments

--- 2019-01-09 Data Preparation.Rmd
@@
 # Import Data
+The datasets we use are saved as spreadsheet on our google drive *DARS*.
+We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
+We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
+
+## Setup
+Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis.
+The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`.
+In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
+```{r list}
+lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
+
+lists <- list(
+  Assessment      = lists_brut$Assessment,
+  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
+  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
+  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
+  )
+```
 
@@
 
-## Course Catalogues
+### Course Catalogues
 In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
@@
 # Variable Engineering
+We create a dataframe from the Corpus:
+```{r}
+
+manuals_td <- tidy(corpus_manuals)
+
+```
 

### 2019-01-09 Data Preparation.Rmd
Importing dataset for courses

@@
 ---
-# Libraries:
-```{r setup, include=FALSE}
+
+```{r setup, message = FALSE}
 library(tidyverse)
@@
   )
+```
+
+## Course Data
+We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
+The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong and in which period(s) they are offered, the tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
+
+```{r import data from drive}
+d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
+  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
+print(d_course)
+
+d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
+  select(- `Comment on Assessment`) %>%
+  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
+  mutate(assessment_covered = as.logical(assessment_covered)) %>%
+  filter(assessment_covered) %>%
+  select(- assessment_covered) %>%
+  arrange(Code)
+print(d_assessment)
+
+d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
+  select(- c(Comments, Comments_for_Jeroen)) %>%
+  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
+  mutate(AoD_covered = as.logical(AoD_covered)) %>%
+  rename(ILO = Objectives) %>%
+  filter(AoD_covered) %>%
+  select(- AoD_covered) %>%
+  arrange(Code)
+print(d_ILO)
 ```

### 2019-01-09 Data Preparation.Rmd

@@
 ```
+## Student Data
+
+### Transcripts
 
 # Variable Engineering
+
+##Course Manual 
 We create a dataframe from the Corpus:

### 2019-01-09 Data Preparation.Rmd
Importing student transcripts

--- 2019-01-09 Data Preparation.Rmd
@@
 ```
+## Student Data
+The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
+`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
+```{r transcripts}
+transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
+print(transcripts)
+```
 
 # Variable Engineering
+
+##Course Manual 
 We create a dataframe from the Corpus:

### 2019-01-09 Data Preparation.Rmd
Determining AoD met with ILOs

@@
 
+## AoD
+In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
+For instance, if one of the ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
+
+### AoD from ILOs
+In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
+```{r}
+d_AoD_ILO <- d_ILO %>%
+  select(Code, AoD) %>%
+  unique
+
+print(d_AoD_ILO)
+```
+
 ##Course Manual 

### 2019-01-09 Data Preparation.Rmd
Determining AoD met with assessments

@@
 
-##Course Manual 
+### AoD from Assessment Type
+In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
+We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
+`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
+```{r}
+map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
+                                  mutate_all(as.logical))
+rownames(map_assessment_AoD) <- lists$Assessment
+print(map_assessment_AoD[1:5, 8:12])
+```
+
+Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers.
+In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`.
+Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
+```{r}
+d_AoD_assessment <- tibble(Code        = character(0),
+                           Assessment  = character(0),
+                           AoD         = character(0))
+
+for(i in 1 : nrow(d_assessment)){
+
+  observation <- d_assessment[i, ]
+
+  assessment  <- observation$Assessment
+  AoD_covered <- map_assessment_AoD[assessment, ]
+  AoD         <- lists$AoD[AoD_covered]
+
+  if(length(AoD) >= 1){ # if no AoD are covered by assessment (e.g. written exam), then do not rbind rows to d_AoD_assessment
+      AoD_assessment_tidy <- cbind(observation, AoD) %>%
+    as_tibble
+      d_AoD_assessment <- rbind(d_AoD_assessment, AoD_assessment_tidy)
+  }
+
+}
+
+print(d_AoD_assessment)
+```
+
+Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
+```{r}
+d_AoD_assessment <- d_AoD_assessment %>%
+  select(Code, AoD) %>%
+  unique
+print(d_AoD_assessment)
+```
+
+## Course Manual 
 We create a dataframe from the Corpus:

### 2019-01-09 Data Preparation.Rmd
Combining AoD met from ILOs, and from assessment

@@
 
+### Combining AoD from ILOs and from assessments
+Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
+```{r}
+d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
+  unique %>%
+  arrange(Code)
+print(d_AoD)
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Generating variables at the course level

@@
 
+## Course Data
+Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
+The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers.
+We use a `full_join` to add these variables to the tibble `d_course`.
+```{r}
+d_ILO_detail <- d_ILO %>% 
+  select(Code, ILO) %>%
+  unique %>%
+  count(Code) %>%
+  rename(n_ILO = n)
+print(d_ILO_detail)
+
+d_assessment_detail <- d_assessment %>%
+  group_by(Code) %>%
+  summarise(n_assessment = n(),
+            `Assessments Covered` = paste(Assessment, collapse = ", "))
+print(d_assessment_detail)
+
+d_AoD_detail <- d_AoD %>%
+  group_by(Code) %>%
+  summarise(n_AoD = n(),
+            `AoD Covered` = paste(AoD, collapse = ", "))
+print(d_AoD_detail)
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Including newly created variables to the course dataset

@@
 
+```{r}
+d_course <- d_course %>%
+  full_join(d_ILO_detail       , by = "Code") %>%
+  full_join(d_assessment_detail, by = "Code") %>%
+  full_join(d_AoD_detail       , by = "Code") %>%
+  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
+print(d_course)
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
creates tidy dataframe from course manuals.

--- 2019-01-09 Data Preparation.Rmd
@@
 ---
-
-```{r setup, message = FALSE}
+# Libraries:
+```{r setup, include=FALSE}
 library(tidyverse)
@@
 # Import Data
-The datasets we use are saved as spreadsheet on our google drive *DARS*.
-We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
-We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
-
-## Setup
-Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis.
-The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`.
-In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
-```{r list}
-lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
-
-lists <- list(
-  Assessment      = lists_brut$Assessment,
-  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
-  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
-  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
-  )
-```
-
-## Course Data
-We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
-The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong and in which period(s) they are offered, the tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
-
-```{r import data from drive}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
-  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
-print(d_course)
-
-d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-  select(- `Comment on Assessment`) %>%
-  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
-  mutate(assessment_covered = as.logical(assessment_covered)) %>%
-  filter(assessment_covered) %>%
-  select(- assessment_covered) %>%
-  arrange(Code)
-print(d_assessment)
-
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
-  select(- c(Comments, Comments_for_Jeroen)) %>%
-  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
-  mutate(AoD_covered = as.logical(AoD_covered)) %>%
-  rename(ILO = Objectives) %>%
-  filter(AoD_covered) %>%
-  select(- AoD_covered) %>%
-  arrange(Code)
-print(d_ILO)
-```
 
@@
 
-### Course Catalogues
+## Course Catalogues
 In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
@@
 ## Student Data
-The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
-`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
-```{r transcripts}
-transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
-print(transcripts)
-```
+
+### Transcripts
 
@@
 
-## AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
-For instance, if one of the ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
-
-### AoD from ILOs
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r}
-d_AoD_ILO <- d_ILO %>%
-  select(Code, AoD) %>%
-  unique
-
-print(d_AoD_ILO)
-```
-
-### AoD from Assessment Type
-In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
-We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
-`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-```{r}
-map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
-                                  mutate_all(as.logical))
-rownames(map_assessment_AoD) <- lists$Assessment
-print(map_assessment_AoD[1:5, 8:12])
-```
-
-Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers.
-In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`.
-Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r}
-d_AoD_assessment <- tibble(Code        = character(0),
-                           Assessment  = character(0),
-                           AoD         = character(0))
-
-for(i in 1 : nrow(d_assessment)){
-
-  observation <- d_assessment[i, ]
-
-  assessment  <- observation$Assessment
-  AoD_covered <- map_assessment_AoD[assessment, ]
-  AoD         <- lists$AoD[AoD_covered]
-
-  if(length(AoD) >= 1){ # if no AoD are covered by assessment (e.g. written exam), then do not rbind rows to d_AoD_assessment
-      AoD_assessment_tidy <- cbind(observation, AoD) %>%
-    as_tibble
-      d_AoD_assessment <- rbind(d_AoD_assessment, AoD_assessment_tidy)
-  }
-
-}
-
-print(d_AoD_assessment)
-```
-
-Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
-```{r}
-d_AoD_assessment <- d_AoD_assessment %>%
-  select(Code, AoD) %>%
-  unique
-print(d_AoD_assessment)
-```
-
-### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
-```{r}
-d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
-  unique %>%
-  arrange(Code)
-print(d_AoD)
-```
-
-## Course Manual 
+##Course Manual 
 We create a dataframe from the Corpus:
@@
 
+From `manuals_td` we are only interested in the text, and the Code of the course.
+However, we don't have the code but we have a document id that includes it.
+Therefore we select only the `text` and `id` columns of the `manuals_td`.
+Then, we extract the code from the `id` and save it in under `Code`, We aso extract the concentration from the `id` and save it under `Concentration`.
+Finally, we unnest the dataframe to have only one word per row, and call this ``manuals_tokens.
+
+```{r}
+manuals_tokens <- manuals_td %>%
+  select(id,text) %>%
+  mutate(Concentration= substring(id, 1, 3), Code= substring(id,1,7))%>%
+  unnest_tokens(word, text)
+```
+
 # Save Data

### 2019-01-09 Data Preparation.Rmd

@@
 # Import Data
+The datasets we use are saved as spreadsheet on our google drive *DARS*.
+We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
+We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
+
+## Setup
+Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis.
+The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`.
+In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
+```{r list}
+lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
+
+lists <- list(
+  Assessment      = lists_brut$Assessment,
+  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
+  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
+  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
+  )
+```
+
+## Course Data
+We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
+The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong and in which period(s) they are offered, the tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
+
+```{r import data from drive}
+d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
+  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
+print(d_course)
+
+d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
+  select(- `Comment on Assessment`) %>%
+  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
+  mutate(assessment_covered = as.logical(assessment_covered)) %>%
+  filter(assessment_covered) %>%
+  select(- assessment_covered) %>%
+  arrange(Code)
+print(d_assessment)
+
+d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
+  select(- c(Comments, Comments_for_Jeroen)) %>%
+  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
+  mutate(AoD_covered = as.logical(AoD_covered)) %>%
+  rename(ILO = Objectives) %>%
+  filter(AoD_covered) %>%
+  select(- AoD_covered) %>%
+  arrange(Code)
+print(d_ILO)
+```
 
@@
 
-## Course Manuals
+### Course Manuals
 To expand our topic modeling of course content, we would like to analyse the material in the course manuals.
@@
 ## Student Data
-
-### Transcripts
+The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
+`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
+```{r transcripts}
+transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
+print(transcripts)
+```
 

### 2019-01-09 Data Preparation.Rmd
Add observations for the UGR2000's (missing from original dataset)

--- 2019-01-09 Data Preparation.Rmd
@@
 
+The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level).
+Yet, these course are also offered at the `2000` level (intermediate level).
+We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
+```{r}
+d_course <- d_course %>%
+  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
+          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
+                                  Code == "UGR3002" ~ "UGR2002",
+                                  Code == "UGR3003" ~ "UGR2003",
+                                  Code == "UGR3005" ~ "UGR2005")))
+
+print(filter(d_course, Code %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
+                                   "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Adding additional variables at the course level

@@
 
+Finally, we add a series of informative variable at the course level.
+```{r}
+d_course <- d_course %>%
+  mutate(
+    `Missing from ILO File` = as.logical(`Missing from ILO File`),
+    Letters = substring(Code, 1, 3),
+    Number  = as.numeric(substring(Code, 4, 7)),
+    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
+                        between(Number, 2000, 2999) ~ "Intermediate",
+                        between(Number, 3000, 3999) ~ "Advanced"    ))
+print(select(d_course, Code, Letters, Number, Level))
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
updated explanation Variable Engineering for course manuals

--- 2019-01-09 Data Preparation.Rmd
@@
 
-## AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
-For instance, if one of the ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
-
-### AoD from ILOs
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r}
-d_AoD_ILO <- d_ILO %>%
-  select(Code, AoD) %>%
-  unique
-
-print(d_AoD_ILO)
-```
-
-### AoD from Assessment Type
-In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
-We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
-`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-```{r}
-map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
-                                  mutate_all(as.logical))
-rownames(map_assessment_AoD) <- lists$Assessment
-print(map_assessment_AoD[1:5, 8:12])
-```
-
-Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers.
-In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`.
-Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r}
-d_AoD_assessment <- tibble(Code        = character(0),
-                           Assessment  = character(0),
-                           AoD         = character(0))
-
-for(i in 1 : nrow(d_assessment)){
-
-  observation <- d_assessment[i, ]
-
-  assessment  <- observation$Assessment
-  AoD_covered <- map_assessment_AoD[assessment, ]
-  AoD         <- lists$AoD[AoD_covered]
-
-  if(length(AoD) >= 1){ # if no AoD are covered by assessment (e.g. written exam), then do not rbind rows to d_AoD_assessment
-      AoD_assessment_tidy <- cbind(observation, AoD) %>%
-    as_tibble
-      d_AoD_assessment <- rbind(d_AoD_assessment, AoD_assessment_tidy)
-  }
-
-}
-
-print(d_AoD_assessment)
-```
-
-Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
-```{r}
-d_AoD_assessment <- d_AoD_assessment %>%
-  select(Code, AoD) %>%
-  unique
-print(d_AoD_assessment)
-```
-
-### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
-```{r}
-d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
-  unique %>%
-  arrange(Code)
-print(d_AoD)
-```
-
-## Course Data
-Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers.
-We use a `full_join` to add these variables to the tibble `d_course`.
-```{r}
-d_ILO_detail <- d_ILO %>% 
-  select(Code, ILO) %>%
-  unique %>%
-  count(Code) %>%
-  rename(n_ILO = n)
-print(d_ILO_detail)
-
-d_assessment_detail <- d_assessment %>%
-  group_by(Code) %>%
-  summarise(n_assessment = n(),
-            `Assessments Covered` = paste(Assessment, collapse = ", "))
-print(d_assessment_detail)
-
-d_AoD_detail <- d_AoD %>%
-  group_by(Code) %>%
-  summarise(n_AoD = n(),
-            `AoD Covered` = paste(AoD, collapse = ", "))
-print(d_AoD_detail)
-```
-
-```{r}
-d_course <- d_course %>%
-  full_join(d_ILO_detail       , by = "Code") %>%
-  full_join(d_assessment_detail, by = "Code") %>%
-  full_join(d_AoD_detail       , by = "Code") %>%
-  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
-print(d_course)
-```
-
-The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level).
-Yet, these course are also offered at the `2000` level (intermediate level).
-We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r}
-d_course <- d_course %>%
-  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
-                                  Code == "UGR3002" ~ "UGR2002",
-                                  Code == "UGR3003" ~ "UGR2003",
-                                  Code == "UGR3005" ~ "UGR2005")))
-
-print(filter(d_course, Code %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
-                                   "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
-```
-
-## Course Manual 
+##Course Manual 
 We create a dataframe from the Corpus:
@@
 Then, we extract the code from the `id` and save it in under `Code`, We aso extract the concentration from the `id` and save it under `Concentration`.
-Finally, we unnest the dataframe to have only one word per row, and call this ``manuals_tokens.
+Finally, we unnest the dataframe to have only one word per row, and call this `manuals_tokens`, this creates a variable `word` and adds all of the text from the course manuals under this column.
 

### 2019-01-09 Data Preparation.Rmd
Extracting course overviews from course catalogues

--- 2019-01-09 Data Preparation.Rmd
@@
 
+## Course Catalogue
+In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
+
+### Extracting Overviews
+We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
+To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`).
+These pages are typically headers.
+Excluding them before the analysis allows use to keep the code relatively simple.
+We also make use the fact that the overviews always start with the code of the course, i.e.
+it starts with one of the elements of `course_code` and use `grep` to identify the first page of each overview.
+We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.
+
+In the loop, we first determine the content of the current and following page.
+If the current page is the first page of an overview, then we identify the overview (one or two pages) and save it to the tibble `d_description`.
+To identify the overview of a course, we check if the following page is either the first page of an overview or a page to exclude.
+If it is either of these, then the overview correspond to the content of the current page; but if the following page is neiter of these, then the overview correspond to the content of the current page and that of the following page.
+
+```{r overview}
+# Setup
+n_catalogue <- length(corpus)
+calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
+d_description <- tibble(Code            = character(0),
+                        `Calendar Year` = character(0),
+                        Overview        = character(0))
+
+course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP")
+course_code <- paste(course_code, collapse = "|")
+
+content_to_exclude <- c("^Core Courses \\(COR\\)",
+                        "^Humanities \\(HUM\\)",
+                        "^Sciences \\(SCI\\)",
+                        "^Social Sciences \\(SSC\\)",
+                        "^Skills Trainings \\(SKI\\)",
+                        "^Projects \\(PRO\\)",
+                        "^Undergraduate Research \\(UGR\\)",
+                        "Appendix")
+content_to_exclude <- paste(content_to_exclude, collapse = "|")
+
+# Loop
+for(n in 1 : n_catalogue){
+
+  cat <- content(corpus[[n]])
+
+  pages_to_exclude     <- grep(pattern = content_to_exclude, x = cat)
+  first_three_letters  <- substr(cat, start = 1, stop = 3)
+  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)
+
+  page_start_loop <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
+  page_end_loop   <- length(cat)
+
+  for(page in page_start_loop : page_end_loop){
+
+    current_page           <- page
+    following_page         <- page + 1
+    current_page_content   <- cat[page          ]
+    following_page_content <- cat[following_page]
+
+    if(current_page %in% first_pages_overview){
+
+      if(following_page %in% c(first_pages_overview, pages_to_exclude)) course_overview <- current_page_content
+      else course_overview <- paste(current_page_content, following_page_content)
+
+      # Save Overview
+      Code <- substring(course_overview, first = 1, last = 7)      
+      year <- calendar_years[n]
+      d_description <- add_row(d_description,
+                               Code            = Code,
+                               `Calendar Year` = year,
+                               Overview        = course_overview)
+    } # close if-statement
+  } # close for-loop (page)
+} # close for-loop (n)
+
+print(d_description)
+```
+
 ## Course Manual 
@@
 ```{r}
-
 manuals_td <- tidy(corpus_manuals)
-
 ```

### 2019-01-09 Data Preparation.Rmd
Extracting course descriptions from course overviews

@@
 
+### Extracting Descriptions
+Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews.
+The description section contains a brief description (200-500 words) of the content of the course.
+To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
+The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
+The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
+Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost overviews.
+A handful overviews do not contain a *Literature* section.
+For these, the section *Instructional Format* marks the end of the description section.
+```{r description}
+# Setup
+symbol_to_line <- c("\r\n", "\n")
+symbol_to_line <- paste(symbol_to_line, collapse = "|")
+
+start_descrip <- c("^Description", "^Course Description")
+start_descrip <- paste(start_descrip, collapse = "|")
+
+end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
+                   "^Required Litera", "^ Literature$", "Literature \\(all")
+end_descrip   <- paste(end_descrip, collapse = "|")
+
+d_description <- d_description %>%
+  mutate(Description = NA)
+
+# Loop
+for(course in 1 : nrow(d_description)){
+
+  overview <- d_description$Overview[course]
+
+  overview_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
+  line_start    <- grep(pattern = start_descrip, x = overview_line) + 1
+  line_end      <- grep(pattern = end_descrip  , x = overview_line) - 1
+
+  # for overviews w/o Literature section, find section Instructional Format.
+  if(is_empty(line_end)){
+    line_end <- grep(pattern = "^Instructional format$", x = overview_line) - 1
+    print(paste("line_end irregular for", d_description$Code[course],
+                "in catalogue", d_description$`Calendar Year`[course]))
+    } # close if-statement
+
+  description <- paste(overview_line[line_start : line_end], collapse = " ")
+
+  d_description$Description[course] <- description
+
+}
+
+print(d_description)
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Tidying course overwies and descriptions

@@
 
+### Tidy Text Format
+We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
+```{r tidy text data}
+d_overview_tidy <- d_description %>%
+  select(Code, `Calendar Year`, Overview) %>%
+  unnest_tokens(output = word, input = Overview)
+print(d_overview_tidy)
+
+d_description_tidy <- d_description %>%
+  select(Code, `Calendar Year`, Description) %>%
+  unnest_tokens(output = word, input = Description)
+print(d_description_tidy)
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Stemming course overviews and course descriptions

@@
 
+### Stemming
+We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
+We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`).
+We then apply `stem_hunspell` on the words of `d_overview_tidy`.
+Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find the a list containing *once* each term present in the course overviews and apply the function `stem_hunspell` on this list.
+We save the terms and their stems in the tibble `stems`.
+Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
+```{r function stem_hunspell, cache = TRUE}
+stem_hunspell <- function(term) {
+  # look up the term in the dictionary
+  stems <- hunspell_stem(term)[[1]]
+
+  if (length(stems) == 0) { # if there are no stems, use the original term
+    stem <- term
+  } else { # if there are multiple stems, use the last one
+    stem <- stems[[length(stems)]]
+  }
+
+  return(stem)
+}
+
+stems <- d_overview_tidy %>% 
+  select(word) %>%
+  distinct %>%
+  arrange(word) %>%
+  mutate(word_stem = purrr::map_chr(.x = word,
+                                    .f = stem_hunspell))
+
+# terms for which the stem differs from the original word
+stems %>%
+  filter(word != word_stem)
+```
+
+```{r stemming}
+d_overview_stem <- d_overview_tidy %>%
+  left_join(stems, by = "word") %>%
+  rename(word_original = word,
+         word = word_stem) %>%
+  filter(!word %in% stop_words$word)
+print(d_overview_stem) # See humanities - humanity
+
+d_description_stem <- d_description_tidy %>%
+  left_join(stems, by = "word") %>%
+  rename(word_original = word,
+         word = word_stem) %>%
+  filter(!word %in% stop_words$word)
+print(d_description_stem) # See starting - start
+```
+
 ## Course Manual 

### 2019-01-09 Data Preparation.Rmd
Saving data for other scripts
Footnotes

@@
 # Save Data
+
+```{r}
+save(lists, d_course, d_AoD, d_assessment, d_transcript,
+     file = "data_pillar_1.RDATA")
+save(lists, d_course, d_AoD, d_assessment, d_transcript,
+     d_overview_stem, d_description_stem,
+     file = "data_pillar_2.RDATA")
+```
+
+[^1]: We do not include all assessments and all AoDs on the plots in order to keep them readable.
+
+[^2]: We are currently cleaning the dataset containing the transcripts of all the students of the college (alumni and current students) in order to integrate it to the analysis.

### 2019-01-09 Data Preparation.Rmd
Updating YALM

@@
 date: "`r Sys.Date()`"
-output: pdf_document
+output: pdf_document:
+    number_sections: TRUE
 ---

### 2019-01-09 Data Preparation.Rmd
optional preprocessing (removes stopwords and numbers) from course manuals

--- 2019-01-09 Data Preparation.Rmd
@@
 ```
+COMMENT SOFIA: save a_clean_transcript as d_transcript
 
@@
 
-## Course Catalogue
-In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
-
-### Extracting Overviews
-We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
-To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`).
-These pages are typically headers.
-Excluding them before the analysis allows use to keep the code relatively simple.
-We also make use the fact that the overviews always start with the code of the course, i.e.
-it starts with one of the elements of `course_code` and use `grep` to identify the first page of each overview.
-We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.
-
-In the loop, we first determine the content of the current and following page.
-If the current page is the first page of an overview, then we identify the overview (one or two pages) and save it to the tibble `d_description`.
-To identify the overview of a course, we check if the following page is either the first page of an overview or a page to exclude.
-If it is either of these, then the overview correspond to the content of the current page; but if the following page is neiter of these, then the overview correspond to the content of the current page and that of the following page.
-
-```{r overview}
-# Setup
-n_catalogue <- length(corpus)
-calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
-d_description <- tibble(Code            = character(0),
-                        `Calendar Year` = character(0),
-                        Overview        = character(0))
-
-course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP")
-course_code <- paste(course_code, collapse = "|")
-
-content_to_exclude <- c("^Core Courses \\(COR\\)",
-                        "^Humanities \\(HUM\\)",
-                        "^Sciences \\(SCI\\)",
-                        "^Social Sciences \\(SSC\\)",
-                        "^Skills Trainings \\(SKI\\)",
-                        "^Projects \\(PRO\\)",
-                        "^Undergraduate Research \\(UGR\\)",
-                        "Appendix")
-content_to_exclude <- paste(content_to_exclude, collapse = "|")
-
-# Loop
-for(n in 1 : n_catalogue){
-
-  cat <- content(corpus[[n]])
-
-  pages_to_exclude     <- grep(pattern = content_to_exclude, x = cat)
-  first_three_letters  <- substr(cat, start = 1, stop = 3)
-  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)
-
-  page_start_loop <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
-  page_end_loop   <- length(cat)
-
-  for(page in page_start_loop : page_end_loop){
-
-    current_page           <- page
-    following_page         <- page + 1
-    current_page_content   <- cat[page          ]
-    following_page_content <- cat[following_page]
-
-    if(current_page %in% first_pages_overview){
-
-      if(following_page %in% c(first_pages_overview, pages_to_exclude)) course_overview <- current_page_content
-      else course_overview <- paste(current_page_content, following_page_content)
-
-      # Save Overview
-      Code <- substring(course_overview, first = 1, last = 7)      
-      year <- calendar_years[n]
-      d_description <- add_row(d_description,
-                               Code            = Code,
-                               `Calendar Year` = year,
-                               Overview        = course_overview)
-    } # close if-statement
-  } # close for-loop (page)
-} # close for-loop (n)
-
-print(d_description)
-```
-
-### Extracting Descriptions
-Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews.
-The description section contains a brief description (200-500 words) of the content of the course.
-To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
-The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
-The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
-Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost overviews.
-A handful overviews do not contain a *Literature* section.
-For these, the section *Instructional Format* marks the end of the description section.
-```{r description}
-# Setup
-symbol_to_line <- c("\r\n", "\n")
-symbol_to_line <- paste(symbol_to_line, collapse = "|")
-
-start_descrip <- c("^Description", "^Course Description")
-start_descrip <- paste(start_descrip, collapse = "|")
-
-end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
-                   "^Required Litera", "^ Literature$", "Literature \\(all")
-end_descrip   <- paste(end_descrip, collapse = "|")
-
-d_description <- d_description %>%
-  mutate(Description = NA)
-
-# Loop
-for(course in 1 : nrow(d_description)){
-
-  overview <- d_description$Overview[course]
-
-  overview_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
-  line_start    <- grep(pattern = start_descrip, x = overview_line) + 1
-  line_end      <- grep(pattern = end_descrip  , x = overview_line) - 1
-
-  # for overviews w/o Literature section, find section Instructional Format.
-  if(is_empty(line_end)){
-    line_end <- grep(pattern = "^Instructional format$", x = overview_line) - 1
-    print(paste("line_end irregular for", d_description$Code[course],
-                "in catalogue", d_description$`Calendar Year`[course]))
-    } # close if-statement
-
-  description <- paste(overview_line[line_start : line_end], collapse = " ")
-
-  d_description$Description[course] <- description
-
-}
-
-print(d_description)
-```
-
-### Tidy Text Format
-We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
-```{r tidy text data}
-d_overview_tidy <- d_description %>%
-  select(Code, `Calendar Year`, Overview) %>%
-  unnest_tokens(output = word, input = Overview)
-print(d_overview_tidy)
-
-d_description_tidy <- d_description %>%
-  select(Code, `Calendar Year`, Description) %>%
-  unnest_tokens(output = word, input = Description)
-print(d_description_tidy)
-```
-
-### Stemming
-We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
-We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`).
-We then apply `stem_hunspell` on the words of `d_overview_tidy`.
-Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find the a list containing *once* each term present in the course overviews and apply the function `stem_hunspell` on this list.
-We save the terms and their stems in the tibble `stems`.
-Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
-```{r function stem_hunspell, cache = TRUE}
-stem_hunspell <- function(term) {
-  # look up the term in the dictionary
-  stems <- hunspell_stem(term)[[1]]
-
-  if (length(stems) == 0) { # if there are no stems, use the original term
-    stem <- term
-  } else { # if there are multiple stems, use the last one
-    stem <- stems[[length(stems)]]
-  }
-
-  return(stem)
-}
-
-stems <- d_overview_tidy %>% 
-  select(word) %>%
-  distinct %>%
-  arrange(word) %>%
-  mutate(word_stem = purrr::map_chr(.x = word,
-                                    .f = stem_hunspell))
-
-# terms for which the stem differs from the original word
-stems %>%
-  filter(word != word_stem)
-```
-
-```{r stemming}
-d_overview_stem <- d_overview_tidy %>%
-  left_join(stems, by = "word") %>%
-  rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
-print(d_overview_stem) # See humanities - humanity
-
-d_description_stem <- d_description_tidy %>%
-  left_join(stems, by = "word") %>%
-  rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
-print(d_description_stem) # See starting - start
-```
-
 ## Course Manual 
@@
 ```{r}
+
 manuals_td <- tidy(corpus_manuals)
+
 ```
@@
 ```
+###(Optional) Pre-processing Course Manuals- Removing stopwords
+Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
+For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers.
+We save these words in different dataframes and then exclude with an antijoin.
+```{r}
 
+data("stop_words")  #imports common stopwords
+
+my_stop_words <- data.frame (word = c(1:11, "students", "______________________________________________________________________________")) #no stemming ("students")
+number_stopwords <- number_stopwords <- manuals_tokens %>% #can be cleaner by using unique (?)
+  mutate(is_number=grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",word))%>% #finds stand alone numbers (incl. -, and .)
+  filter(is_number==T)
+
+manuals_tokens_preprocessed <- manuals_tokens %>%
+  anti_join(stop_words)     %>%
+  anti_join(my_stop_words) %>%
+  anti_join(number_stopwords, by = c("word"="word"))
+
+```
 # Save Data

### 2019-01-09 Data Preparation.Rmd
adding libraries used in transcripts.
imports grade data

@@
 library(hunspell) # Stemmer
+
+library(rlist)
+#library(tidyr) #(maybe incuded in tidyverse)
+#library(tibble)
 ```
@@
 COMMENT SOFIA: save a_clean_transcript as d_transcript
+
+ALL OTHER STUDENTS:
+The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.
+
+```{r Data Import}
+t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
+t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
+d_dirt <-rbind(t1, t2)
+d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
+```
 
@@
 ```
+
 # Save Data

### 2019-01-09 Data Preparation.Rmd

--- 2019-01-09 Data Preparation.Rmd
@@
 print(transcripts)
+```
+COMMENT SOFIA: save a_clean_transcript as d_transcript
+
+ALL OTHER STUDENTS:
+The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.
+
+```{r Data Import}
+t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
+t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
+d_dirt <-rbind(t1, t2)
+d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
 ```
@@
 ```
+###(Optional) Pre-processing Course Manuals- Removing stopwords
+Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
+For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers.
+We save these words in different dataframes and then exclude with an antijoin.
+```{r}
+
+data("stop_words")  #imports common stopwords
+
+my_stop_words <- data.frame (word = c(1:11, "students", "______________________________________________________________________________")) #no stemming ("students")
+number_stopwords <- number_stopwords <- manuals_tokens %>% #can be cleaner by using unique (?)
+  mutate(is_number=grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",word))%>% #finds stand alone numbers (incl. -, and .)
+  filter(is_number==T)
+
+manuals_tokens_preprocessed <- manuals_tokens %>%
+  anti_join(stop_words)     %>%
+  anti_join(my_stop_words) %>%
+  anti_join(number_stopwords, by = c("word"="word"))
+
+```
 

### 2019-01-09 Data Preparation.Rmd
renames transcript variables

@@
 ```
+##Student Data
+###Renaming Variables
+First we rename the variable names to make them more comprehensible:
+```{r}
+d_rename <-d_dirt %>%
+  rename(
+    ID                     =  "X...Student.Number", 
+    Code                   =  "Module..Abbrev..", 
+    `Course Title`         =  "Module..Desc..",
+    `Program Abbreviation` =  "Program..Abbreviation.", 
+    `Program Description`  =  "Program..Description.",               
+    Year                   =  "Academic.Year",                      
+    Session                =  "Academic.Session",
+    `Appraisal Code`       =  "Appraisal.Type",                     
+    `Appraisal Title`      =  "Appraisal..Description.",             
+    Attempt                =  "Number.rep..attemp",                 
+    Grade                  =  "Grade.symbol",                        
+    `Appraisal Status`     =  "Appraisal.Status",                   
+    `Appraisal Status Description` =  "Appraisal.Status..Desc..",    #is only NA: unique(d4$Appraisal.Status..Desc..)       
+    `Booking Reason`       =  "Module.Booking.Reason..Description.",
+    `Appraisal Date`       =  "Appraisal.date",                      
+    `Attempted Credits`    =  "Attempted.credits",                  
+    `Earned Credit`        =  "Earned.Credits",                      
+    `Credit Type`          =  "Credit.Type",                        
+    `Personnel Number`     =  "Personnel.Number",                  
+    `Name (Employee/Applicant)`=  "Name.of.employee.or.applicant",      
+    `Individual Work`      =  "Individual.Work",                     
+    `Academic Work ID`     =  "Academic.Work.ID",                   
+    `Booking Status`       =  "Booking.Status",                      #empty
+    `Booking Status Description` =  "Booking.Status..Desc..",             
+    `Event Object Id`      =  "Event.Object.Id",                     #empty forwards and including      
+    `Business Event Abbreviation` =  "Business.event.abbr.",               
+    `Event Description`    =  "Event.Description",                   
+    `Start time`           =  "Start.time",                         
+    `End time`             =  "End.time",                            
+    `Date`                 =  "Date",                               
+    `Studyplan`            =  "Studyplan",                           
+    `Conditional booking`  =  "Conditiona.booking",                 
+    `Wachtlist`            =  "Wachtlist",                           
+    `Object ID`            =  "Object.ID",                          
+    `Object Name`          =  "Object.name",                         
+    `Start Date`           =  "Start.date",                         
+    `End Date`             =  "End.Date",                            
+    `Number of Weeks`      =  "Number.of.weeks",                      #until this one next has values              
+    `Appraiser ID`         =  "Appraiser.ID",                        
+    `Appraiser Name`       =  "Appraiser.Name"
+
+  ) 
+```
+
+###Identifying usless variables
+Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
 

### 2019-01-09 Data Preparation.Rmd
transcripts: identifies useless variables and saves them as a vector.

@@
 Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
+```{r}
+not_keep <- c("Booking Status",
+              "Appraisal Status Description",
+              "Credit Type",
+              "Personnel Number",
+              "Event Object Id",     
+              "Business Event Abbreviation",               
+              "Event Description",                   
+              "Start time",                         
+              "End time",                            
+              "Date",                               
+              "Studyplan",                           
+              "Conditional booking",                 
+              "Wachtlist",                           
+              "Object ID", #? has values e.g. 50236380                        
+              "Object Name",  #?  has values, e.g. "BE-Universitair Ziekenhuis Brussel"
+              "Start Date",   #? has values, e.g.  "12/16/13"                     
+              "End Date",     #? has values, e.g. "5/14/10"                      
+              "Number of Weeks", 
+              "Name (Employee/Applicant)",
+              "Appraiser ID",      #HAS VALUES BUT NOT IMPORTANT, e.g. 70011933
+              "Appraiser Name",    #HAS VALUES BUT NOT IMPORTANT, e.g.  J.J. Briede  
+              "Academic Work ID",  #has values, eg.53EA405080711826E10000008978030A
+              "Attempted Credits", #HAS VALUES BUT NOT IMPORTANT
+              "Earned Credit",
+              "Individual Work",
+              "Appraisal Status",
+              "Booking Reason",
+              "Appraisal Date" #day when grades were put in
+              ) 
+```
 

### 2019-01-09 Pillar 2 - Topic Modeling.Rmd
Creating RMD for topic modeling

---
title: "Pillar 2 - Topic Modeling"
output: github_document:
  number_section: TRUE
---

### 2019-01-09 Data Preparation.Rmd

@@
 
+Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
+```{r}
+d_rename <-d_rename %>%
+  mutate(Period= case_when(
+    (Session==100)~"1",
+    (Session==101)~"1",
+    (Session==102)~"1",
+    #(Session==190)~"1", #is not there
+    (Session==191)~"1",
+    (Session==200)~"2",
+    (Session==201)~"2",
+    (Session==202)~"2",
+    (Session==291)~"2",
+    (Session==300)~"3",
+    (Session==330)~"3",
+    (Session==350)~"3",
+    (Session==400)~"4",
+    (Session==410)~"4",
+    (Session==420)~"4",
+    (Session==430)~"4",
+    (Session==450)~"4",
+    (Session==460)~"4",
+    (Session==481)~"4",
+    (Session==482)~"4",
+    (Session==500)~"5",
+    (Session==520)~"5",
+    (Session==530)~"5",
+    (Session==550)~"5",
+    (Session==551)~"5",
+    (Session==560)~"5",
+    (Session==552)~"5",
+    (Session==580)~"5",
+    (Session==600)~"6",
+    (Session==610)~"6",
+    (Session==620)~"6",
+    (Session==630)~"6",
+    (Session==650)~"6",
+    (Session==660)~"6",
+    (Session==680)~"5",#WHHHHHHHHHHHHHHHHHAAAAAAAAAAATTTTTTTTTTT?????? Why is this period 5
+    (Session==1)~"1,2,3,4,5,6",
+    (Session==2)~"1,2,3",
+    (Session==3)~"4,5,6",
+    #(Session==203)~c("2","3"),#is not there
+    (Session==350)~"3,4,5",
+    (Session==403)~"4,5",
+    (Session==900)~"1,2,3,4,5,6",
+    (Session==910)~"1", #ASK ABOUT THE 900'S
+    (Session==911)~"1",
+    (Session==912)~"1",
+    (Session==913)~"1",
+    (Session==914)~"1",
+    (Session==915)~"1",
+    (Session==916)~"1",
+    (Session==920)~"1",
+    (Session==923)~"1",
+    (Session==930)~"1",
+    (Session==940)~"1",
+    (Session==950)~"1",
+    (Session==960)~"1"
+     )
+           )
+```
+
 # Save Data

### 2019-01-09 Data Preparation.Rmd
drops useless variables

@@
 ```
+###Dropping useless variables:
+Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:
+
+```{r}
+d_reduce <- d_rename %>%
+  select(-not_keep,-Session,-`Program Abbreviation`)
+
+d_reduce <- d_reduce[!duplicated(d_reduce),]
+```
+###Extracting grades
 

### 2019-01-09 Pillar 2 - Topic Modeling.Rmd
Adding libraries
Writing function that orders bars in barplots within facets

@@
 ---
+
+```{r library, message = F}
+library(tidyverse)
+library(tidytext)
+
+library(ggwordcloud) # Word Clouds
+library(topicmodels)
+library(lemon)
+library(ggthemes)
+```
+
+```{r function reorder_within & co., echo = FALSE}
+
+# Function for ordering within facet:
+# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
+
+reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
+  new_x <- paste(x, within, sep = sep)
+  stats::reorder(new_x, by, FUN = fun)
+}
+
+scale_x_reordered <- function(..., sep = "___") {
+  reg <- paste0(sep, ".+$")
+  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
+}
+
+scale_y_reordered <- function(..., sep = "___") {
+  reg <- paste0(sep, ".+$")
+  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
+}
+```

### 2019-01-09 Data Preparation.Rmd
extracts final grades

@@
 ###Extracting grades
+We notice that there are several values under `Grade` for the same course.
+We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor".
+So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:
+
+```{r}
+d_grade <- d_reduce %>%
+  filter(`Appraisal Title` == "Grade supervisor") %>%
+  mutate(`Course concentration` = substr(Code, start = 1, stop = 3))
+
+d_grade <- d_grade[!duplicated(d_grade),]
+```
 

### 2019-01-09 Data Preparation.Rmd
estimating concentrations of students based on courses

@@
 
+##Estimating concentrations:
+For our analysis we would also like to know what the concentration of each student is.
+However, this is not given, so we will have to estimate.
+We know that the maximimum amount of courses a student can take outside of their concentration is 2.
+Therefore, if any student has more than two courses in one concetration, this should count towards the concentration.
+We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration.
+However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided".
+Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"
+
+NOTE TO RAPHAEL: we might want o have your course concentrations because they take double concentrations into account!
+
+```{r}
+d_student_concentration <- d_grade %>%
+  group_by(ID, `Course concentration`) %>%
+  summarise(count = n()) %>%
+  arrange(ID,desc(count)) %>% #LONG
+  spread(`Course concentration`,count, fill=0) %>% #WIDE
+  transmute(student_Concentration = case_when(
+    (HUM  >  2    &   SSC >  2   &  SCI <= 2) ~ "HUM/SSC",
+    (HUM  >  2    &   SSC <= 2   &  SCI >  2) ~ "HUM/SCI",
+    (HUM  >  2    &   SSC <= 2   &  SCI <= 2) ~ "HUM",
+    (HUM  <= 2    &   SSC >  2   &  SCI >  2)  ~ "SSC/SCI",
+    (HUM  <= 2    &   SSC >  2   &  SCI <= 2) ~ "SSC",
+    (HUM  <= 2    &   SSC <= 2   &  SCI >  2)  ~ "SCI",
+    (HUM  <  2    &   SSC <  2   &  SCI <  2) ~ "UNDECIDED",
+    (HUM  >  2    &   SSC >  2   &  SCI >  2) ~ "CONFUSED", #normal cases ^
+    (HUM > SCI    &   HUM > SSC)              ~ "HUM",
+    (SSC > SCI    &   SSC > HUM)              ~ "SSC",
+    (SCI > HUM    &   SCI > SSC)              ~ "HUM",
+    TRUE ~ "oops"
+  ))
+```
+
+Since we will need to check each student with an "oops" concentration to see what happened, lets separate this data for later:
+```{r}
+checkup <- filter(d_student_concentration, student_Concentration == "oops") 
+```
+
 # Save Data

### 2019-01-09 Pillar 2 - Topic Modeling.Rmd
Loading datasets created in the file Data Preparation
Writing function that generates a word cloud

@@
 ```
+
+# Setup
+```{r}
+load("data_pillar_2.RDATA")
+```
+
+# TF-IDF
+# TF-IDF
+```{r function make_barplot and make_WC, out.height=8, out.width=16}
+make_barplot <- function(data, facet, n_col = 5){
+
+  facet <- enquo(facet)
+
+  g <- data %>%
+    rename(facet = !!facet) %>%
+    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
+    geom_col(show.legend = F) +
+    labs(x = NULL, y = "tf-idf") +
+    scale_x_reordered() +
+    facet_wrap(~ facet, scales = "free", ncol = n_col) +
+    coord_flip()
+
+  ggsave(paste(facet[2], "_BP.jpeg", sep = ""), path = "Plots")
+  return(g)
+
+}
+
+make_WC <- function(data, facet, n_col = 5){
+
+  facet <- enquo(facet)
+
+  g <- data %>%
+    rename(facet = !!facet) %>%
+    group_by(facet) %>%
+    mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
+    ungroup() %>%
+    mutate(angle = 10 * sample(-2:2, n(), replace = T, prob = c(1,1,4,1,1))) %>%
+
+    ggplot(aes(size = freq^0.7, label = word, 
+               angle = angle, color = freq^0.7)) +
+    geom_text_wordcloud_area(area_corr_power = 1,
+                             eccentricity    = 1,
+                             rm_outside      = T) +
+    scale_radius(range = c(2, 10), limits = c(0, NA)) +
+    scale_color_gradient(low = "red", high = "blue") +
+    facet_wrap(~ facet, ncol = n_col) + 
+      theme(
+        strip.text.x     = element_text(),
+        panel.background = element_rect(fill = "white"),
+        plot.title       = element_text(hjust=0.5)
+      )
+
+  ggsave(paste(facet[2], "_WC.jpeg", sep = ""), path = "Plots")
+  return(g)
+}
+```

### 2019-01-09 Data Preparation.Rmd
finds what year is a students first, second, third, etc

@@
 
+###Getting UCM_YEAR
+In order to compare the trajectories of students, we would like to know if the courses were taken in their first, second, third, or whatever year.
+However, we only have the calendar years.
+Lets find out to what year of study each calendar year corresponds per student.
+
+First, lets find out, which year was a student's first year and which year was a student's last year (we will also create a variable `Subs_year` that we will substract later to transform from Calendar Year to UCM Year, and a second variable `LengthUCM` that shows us how many years each student stayed at the college):
+```{r}
+
+d_year <- d_grade %>%
+  select(ID, Code, Year, Period, Grade,`Booking Status Description`, `Course concentration`) %>%
+  group_by(ID) %>%
+  summarise(FirstYear=min(Year), LastYear=max(Year)) %>%
+  mutate(LengthUCM = LastYear-FirstYear, Subs_year=FirstYear-1)
+```
+
+Now, lets make a dataframe of students against years, where the year appears in the corresponding cell if a student was in the college at that time:
+
+```{r}
+
+d_year1 <- d_grade %>%
+  select(ID, Code, Year, Period, Grade, `Booking Status Description`, `Course concentration`) %>%  
+  group_by( ID, Year) %>%
+  summarise(Count = n())%>%
+  mutate(Present = case_when(Count > 0 ~ Year))%>%
+  select(-Count) %>%
+  spread(Year,Present, fill = 0)
+
+```
+
+Now we have collected all the years a student has been at the college in a single row (one row per student), and we also know what is the first and last year of each student.
+Let's join these dataframes:
+
+```{r}
+
+d_time <- left_join(d_year1, d_year)
+
+```
+
+Ideally, we would like to have a dataframe of students against calendar years filled with the corresponding UCM year (e.g.
+if the year 2017 was the first year of student 45, we would like to see the cell corresponding to student 45 and year 2017 marked with a "1").
+
+```{r}
+var_years <- as.character(2007:2017)
+
+d_time <- d_time %>% 
+  mutate_at(
+    vars(var_years),
+    funs(. - Subs_year)) %>%
+  mutate_at(
+    vars(var_years),
+    funs(case_when(. < 0 ~ 9999999999, #HORRIBLE FIX
+                   T     ~ .)))
+
+d_time[d_time == 9999999999] <- NA
+
+```
+
 # Save Data

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
minor changes

@@
 title: "Pillar 2 - Topic Modeling"
-output: github_document:
-  number_section: TRUE
+output: github_document
 ---
@@
 # TF-IDF
-# TF-IDF
+## Functions for Generating Barplots and Word Clouds
 ```{r function make_barplot and make_WC, out.height=8, out.width=16}
@@
 ```
+
+## Course Level
+```{r tf-idf per course}
+tdm_top <- d_overview_stem %>%
+  filter(`Calendar Year` == "2018-2019") %>%
+  count(Code, `Calendar Year`, word, sort = T) %>%
+  bind_tf_idf(term = word, document = Code, n = n) %>%
+  filter(n >= 2) %>%
+  group_by(Code) %>%
+  top_n(10, tf_idf) %>%
+  ungroup %>%
+  filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) # select 25 courses at random
+
+make_barplot(data = tdm_top, facet = Code)
+make_WC(data = tdm_top, facet = Code)
+```
+
+## Cluster Level
+```{r tf-idf per cluster}
+tdm_top <- d_overview_stem %>%
+  left_join(select(d_course, Code, Cluster), by = "Code") %>%
+  filter(`Calendar Year` == "2018-2019",
+         !is.na(Cluster)) %>%
+  count(Cluster, `Calendar Year`, word, sort = T) %>%
+  bind_tf_idf(term = word, document = Cluster, n = n) %>%
+  filter(n >= 5) %>%
+  group_by(Cluster) %>%
+  top_n(10, tf_idf) %>%
+  ungroup
+
+# Plots
+make_barplot(data = tdm_top, facet = Cluster, n_col = 4)
+make_WC(data = tdm_top, facet = Cluster, n_col = 4)
+```
+
+## Concentration Level
+```{r tf-idf per concentration}
+tdm_top <- d_overview_stem %>%
+  left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
+  gather(key = "key", value = Concentration,
+         c("Concentration", "Concentration (additional)"),
+         na.rm = T) %>%
+  filter(`Calendar Year` == "2018-2019") %>%
+  count(Concentration, `Calendar Year`, word, sort = T) %>%
+  bind_tf_idf(term = word, document = Concentration, n = n) %>%
+  filter(n >= 5) %>%
+  group_by(Concentration) %>%
+  top_n(10, tf_idf) %>%
+  ungroup
+
+# Plots
+make_barplot(data = tdm_top, facet = Concentration)
+make_WC(data = tdm_top, facet = Concentration)
+```
+
+# LDA
+
+## Fitting Model

### 2019-01-10 Data Preparation.Rmd
transition to github_document
creates student data dataframe with most variables, but cleaning is still necessary

@@
 
+Now, lets get the data as we want it for our analysis.
+For our analysis we would like to know what course a student took, when, whether they passed or failed, what grade they got, what the concentration of the student is, and what the concentration of the course is (we will convert grades to numeric here).
+Then, we would like to know on what year of their studies the student took the course.For this we will create a years dictionary and join it with our student data:
+
+```{r}
+d_students <- d_grade %>%
+  select(ID, Code, Year, Period, Grade, Attempt,`Booking Status Description`, `Course concentration`) %>%
+  arrange(ID, Year, Period)%>%
+  left_join(d_student_concentration, by="ID") %>%
+  mutate(Grade = as.numeric( sub(",",".", Grade))) %>%
+  replace_na(list(Grade=-1))
+
+# Years dictionary:
+year_dic <- d_time %>%
+  select(-FirstYear,-LastYear,-LengthUCM,-Subs_year)%>%
+  gather(Cal_Year,UCM_Year,var_years)%>%
+  drop_na(.) %>%
+  mutate(Year=as.integer(Cal_Year))%>%
+  select(-Cal_Year)
+
+#adding the ucm year to transcripts:
+d_students <- d_students %>%
+  left_join(year_dic, by=c("ID","Year"))
+
+#removing repeated values:
+d_students <- d_students[!duplicated(d_students),]
+
+```
+
 # Save Data

### 2019-01-10 Data Preparation.Rmd
cleans grade data for capstone (needed to find capstone year)

@@
 
+###Removing master Program data and Cleaning Capstone Data 
+We noticed that we had the data for people who stayed at this university for their masters. To filter these courses out we find out in which year people took their capstone courses.
+
+For this we keep only the capstones. We expect some people to have repeated capstones:
+```{r}
+capstone_count <- d_students %>%
+  filter(Code=="CAP3000") %>%
+  group_by(ID)%>%
+  summarise(Count=n())
+
+capstone_count
+```
+However, what is surptising is that some people have two different passed capstones:
+
+```{r}
+passed_capstone_count <- d_students %>%
+  filter(Code=="CAP3000", `Booking Status Description`=="Completed with Success") %>%
+  group_by(ID) %>%
+  summarise(Count=n(), Max = max(Grade), Min = min(Grade), Attempts= max(Attempt))
+
+```
+
+We can check the grades for people who had repeated passed capstones (lets just bring them to the top of the list):
+```{r}
+passed_capstone_count %>%
+  arrange(desc(Count), desc(Min), Attempts)
+```
+There are 1712 people who did capstone.
+We see that most students who have two passed Capstones, have in reality only 1, since the other capstone had a failing grade and the passing grade was on the second attempt (count starts at 0) was indeed failed.
+However there are two students who indeed have two different passed Capstones: one is student 282995 who has two different passing grades(because of a change in grading system at the collegue during the year 2008-2009), the other is student 544450 who has the same grade passed at two different moment in time.
+
+We can check if there are any students with passing capstone who do not have a grade of at least 5.5. We do this by looking at the lowest Max values:
+```{r}
+passed_capstone_count %>%
+  arrange(Max)
+```
+We see the lowest grade for a passing capstone is 5.6, so this is fine.
+
+Now lets just keep the highest value for each student and correct for student 282995:
+```{r}
+passed_capstone_grades <- passed_capstone_count %>%
+  mutate(`Booking Status Description`= "Completed with Success", Code="CAP3000", Grade= case_when(ID== 282995~7.7,
+                                                                                  T~Max)) %>%
+  select( ID, Code, Grade,`Booking Status Description`)
+passed_capstone_grades
+```
+
+Now we can figure out the Capstone Year,
+
 # Save Data

### 2019-01-10 Pillar 1 - Sequential Pattern Mining.Rmd

---
title: "Pillar 1 - Sequential Pattern Mining"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

```{r library, message = F}
library(tidyverse)
```

# Setup
```{r}
load("data_pillar_1.RDATA")
```

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
Fine-tuning YALM
Fitting LDA model

@@
 title: "Pillar 2 - Topic Modeling"
-output: github_document
+author: "DARS"
+date: "`r Sys.Date()`"
+output: 
+  github_document:
+    toc: TRUE
 ---
@@
 ## Fitting Model
+```{r}
+d_overview_cast <- d_overview_stem %>%
+  count(Code, word, sort = T) %>%
+  cast_dtm(Code,word, n)
+```
+
+```{r}
+LDA_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
+LDA_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
+LDA_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
+```
+
+## Results

### 2019-01-10 Data Preparation.Rmd
detects capstone year

@@
 date: "`r Sys.Date()`"
-output: pdf_document:
-    number_sections: TRUE
+output: 
+  github_document:
+    toc: TRUE
 ---
@@
 
-Now we can figure out the Capstone Year,
+####Capstone Year
+Now we can figure out the Capstone Year.
+
+First we get the years for which there is a corresponding passing capstone grade, and check for repetition:
+```{r}
+
+capstone_finish_year <- inner_join(passed_capstone_grades, d_students)
+
+head(capstone_finish_year)
+
+count_before <- passed_capstone_grades %>%
+  group_by(ID) %>%
+  summarise(counts_of_id= n())
+
+count_after <- capstone_finish_year %>%
+  group_by(ID) %>%
+  summarise(counts_of_id= n())%>%
+  filter(counts_of_id > 1)  #these students have repeated capstones.
+
+count_after
+
+```
+From count_after we see that student 544450 has two passed capstones at different moments in time, we already knew this and we must ask Richard why this is the case.
+However, since both capstones where passed in 2010, this creates no problem for our current purposes.
+However, let's remove the later version.
+We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
+```{r}
+to_remove <- capstone_finish_year%>%
+  filter(ID==544450)
+to_remove <- to_remove[duplicated(to_remove$ID),]
+
+capstone_finish_year <- capstone_finish_year%>%
+  anti_join(to_remove) %>%
+  rename(`Capstone Year`= Year)%>%
+  select(ID,`Capstone Year`)
+
+capstone_finish_year
+```
+
+Lets create a dataframe where we include the capstone year.
+Then, if a course is given later than the capstone year, we want to remove it.
+Therefore, lets substitute na values with the year 9999 (or will ucm be open in the year 9999?).
+```{r}
+d_transcripts <- d_students %>%
+  group_by(ID) %>%
+  left_join(capstone_finish_year) %>%
+  ungroup() %>%
+  replace_na(list(`Capstone Year`=9999)) %>%
+  mutate(`After Graduation`=`Capstone Year`-`Year`)
+
+d_transcripts
+```
+Now we will remove all courses with negative `After Graduation`:
+```{r}
+master_courses <- d_transcripts%>%
+  filter(`After Graduation`<0)
+
+d_transcripts <- d_transcripts %>%
+  anti_join(master_courses)
+
+head(d_transcripts)
+
+```
+
+One last thing.
+The variable `Booking Status Description` shows whether a student passed or failed the course.
+However, some mistakes in the way the data was handled meant that the course status of some students was never confirmed.
+We need to ASK RICHARD, but for the moment, we will just look at the grades to change into pass and fail.
 

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
Function to visualize LDA

@@
 ## Results
+
+```{r function visualize_LDA, eval = F}
+visualize_LDA <- function(results, id_plot = "test", facet = F, topic_names = NULL){
+
+  # Setup
+  topic_letter <- tibble(topic_number = 1:26,
+                         topic_letter = c(topic_names,
+                                          paste("Topic", LETTERS[(length(topic_names)+1) : 26])))
+
+  # Beta Distribution: term-topic
+  term_topic <- tidy(results, matrix = "beta") %>%
+    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
+    mutate(topic = topic_letter) %>%
+    select(-topic_letter)
+
+  term_topic %>%
+    group_by(topic) %>%
+    top_n(10, beta) %>%
+    ungroup %>%
+    ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
+    geom_col(show.legend = F) +
+    facet_wrap(~ topic, scales = "free") +
+    scale_x_reordered() +
+    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
+    coord_flip() +
+    theme_light() +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggsave(paste(id_plot, "beta.jpeg"),
+         width = 15, height = 10, path = "Plots")
+
+  # Gamma Distribution: document-topic
+  doc_topic <- tidy(results, matrix = "gamma") %>%
+    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
+    mutate(topic = topic_letter,
+           facet = document) %>%
+    select(-c(topic_letter, document))
+
+  if(facet) doc_topic <- separate(doc_topic, facet, c("document", "facet"), sep = "_") %>%
+    add_count(facet) %>%
+    group_by(facet, topic) %>%
+    summarise(gamma = sum(gamma)) %>%
+    ungroup
+
+  # Plot 1
+  doc_topic %>%
+    filter(gamma > 0.05) %>%
+    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
+    geom_col(show.legend = F) +
+    facet_rep_wrap(~ topic, scales = "free",
+                   repeat.tick.labels = "bottom") +
+    scale_x_reordered() +
+    coord_flip() +
+    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
+    theme_light() +
+    theme(axis.text.x = element_text(angle = 90, hjust = 0),
+          plot.title = element_text(hjust = 0.5))
+
+  ggsave(paste(id_plot, "gamma1.jpeg"),
+         width = 15, height = 10, path = "Plots")
+
+  # Plot 2
+  doc_topic %>%
+    filter(gamma > 0.05) %>%
+    ggplot(aes(reorder_within(topic, by = gamma, within = facet), y = gamma, fill = topic)) +
+    geom_col(show.legend = F) +
+    facet_rep_wrap(~ facet, scales = "free",
+                   repeat.tick.labels = "bottom") +
+    scale_x_reordered() +
+    coord_flip() +
+    labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
+    theme_light() +
+    theme(axis.text.x = element_text(angle = 90, hjust = 0),
+          plot.title = element_text(hjust = 0.5))
+
+  ggsave(paste(id_plot, "gamma2.jpeg"),
+         width = 15, height = 10, path = "Plots")
+
+}
+```

### 2019-01-10 Data Preparation.Rmd

@@
 
+```{r}
+booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
+  mutate(`Booking Status Description`= case_when(Grade<5.5~"Completed Unsuccessfully",
+                                                 Grade>5.5~"Completed with Success"))
+
+clean_transcripts <- d_transcripts %>% 
+  left_join(booked, by= c("ID", "Code", "Year", "Period", "Grade", "Attempt", "Course concentration", "student_Concentration", "Capstone Year", "After Graduation"), suffix=c("-old", "-new"))%>%
+  select(-`After Graduation`)%>%
+  mutate(Pass= case_when(
+    (`Booking Status Description-new`=="Completed with Success")~"Pass",
+    (`Booking Status Description-new`=="Completed Unsuccessfully")~"Fail",
+    (`Booking Status Description-old`=="Completed with Success")~"Pass",
+    (`Booking Status Description-old`=="Completed Unsuccessfully")~"Fail",
+    T~"error in clean_transcripts"
+  )) %>%
+  select(-`Booking Status Description-new`,-`Booking Status Description-old`,-"UCM_Year-new")
+```
+
 # Save Data

### 2019-01-10 Data Preparation.Rmd
updating libraries
adds time data to student data. transcripts are ready to save.

--- 2019-01-10 Data Preparation.Rmd
@@
 ```
-COMMENT SOFIA: save a_clean_transcript as d_transcript
 
@@
 However, some mistakes in the way the data was handled meant that the course status of some students was never confirmed.
-We need to ASK RICHARD, but for the moment, we will just look at the grades to change into pass and fail.
+We need to ASK RICHARD, but for the moment, we will just look at the grades of those courses which were not confirmed to change into pass and fail.
+
+```{r}
+booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
+  mutate(`Booking Status Description`= case_when(Grade<5.5~"Completed Unsuccessfully",
+                                                 Grade>5.5~"Completed with Success"))
+
+clean_transcripts <- d_transcripts %>% 
+  left_join(booked, by= c("ID", "Code", "Year", "Period", "Grade", "Attempt", "Course concentration", "student_Concentration", "Capstone Year", "After Graduation"), suffix=c("-old", "-new"))%>%
+  select(-`After Graduation`)%>%
+  mutate(Pass= case_when(
+    (`Booking Status Description-new`=="Completed with Success")~"Pass",
+    (`Booking Status Description-new`=="Completed Unsuccessfully")~"Fail",
+    (`Booking Status Description-old`=="Completed with Success")~"Pass",
+    (`Booking Status Description-old`=="Completed Unsuccessfully")~"Fail",
+    T~"error in clean_transcripts"
+  )) %>%
+  select(-`Booking Status Description-new`,-`Booking Status Description-old`,-"UCM_Year-new")
+```
+####Ordering in Time
+We would like to have a column `Time` that codes for both year and period (e.g.
+Year_1 Period_2 should be 1.2), as well as a column `Periods` with the year and period as numbers (e.g.
+Year_2 Period_1 should be period 7).
+
+CHECK: we still have students who's first record is of their last year. This appears as UCM_Year=1.
+
+```{r}
+
+a_clean_transcripts <- clean_transcripts%>%
+  separate(Period, 
+           c("T1","T2","T3","T4","T5","T6"), 
+           sep="," 
+           ) %>%
+  gather( key = "Time", value = "Period", T1,T2,T3,T4,T5,T6) %>%
+  drop_na(Period) %>%
+  select(-Time) %>%
+  mutate(Periods = (`UCM_Year-old` - 1) * 6 + 
+           as.numeric(Period)
+         )
+
+a_clean_transcripts$Time= paste(a_clean_transcripts$`UCM_Year-old`,
+                                a_clean_transcripts$Period, 
+                                sep="."
+                                )
+#FINAL DATA:
+d_transcript <-a_clean_transcripts%>%
+  select(-`UCM_Year-old`,-Period)
+```
+NOTES: The data is now arranged so as to respect the order in time for each individual student.
+However, the comparison is still tricky as people who finished in 2008 will have CAP recorded as taken on their first year since this is all the data we have.
+COMMENT SOFIA: save a_clean_transcript as d_transcript
 

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd

@@
 ```
+
+```{r visualization LDA, eval = F}
+visualize_LDA(LDA_SCI_2 , id_plot = "SCI, k = 2" )
+visualize_LDA(LDA_SCI_5 , id_plot = "SCI, k = 5" )
+visualize_LDA(LDA_SCI_10, id_plot = "SCI, k = 10")
+
+visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10", facet = T)
+visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17", facet = T)
+visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25", facet = T)
+
+visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
+              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
+                              "Sociology", "Law", "Research", "International Politics",
+                              "Philosophy", "Humanities"))
+
+visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
+              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
+                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
+                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
+                              "Math", "Management and ?"))
+visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
+              topic_names = c(
+                "Information", "Psycho", "Bio", "Chem", "Sociology",
+                "History", "skills", "Europe", "Philosophy", "IR",
+                "Conference", "Law", "Media", "Philosophy", "Economics",
+                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
+                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
+```

### 2019-01-10 Data Preparation.Rmd
debug import section

--- 2019-01-10 Data Preparation.Rmd
@@
 
-```{r setup, message = FALSE}
+```{r libraries, message = FALSE}
 library(tidyverse)
@@
 library(hunspell) # Stemmer
-
-library(rlist)
-#library(tidyr) #(maybe incuded in tidyverse)
-#library(tibble)
+#library(rlist)
 ```
@@
   )
+
+rm(lists_brut)
 ```
@@
 In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
-The corpus `corpus` contains the pdfs of the `5` most recent course catalogues.
-```{r corpus, cache = TRUE}
-corpus <- Corpus(x             = DirSource("Catalogues"),
+The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
+```{r corpus_catalogues, cache = TRUE}
+corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
                             readerControl = list(reader = readPDF(control = list(text = "-layout"))))
@@
 The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
-```{r}
+```{r corpus_manuals, cache = TRUE}
 corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
@@
 ```
+
 ## Student Data
@@
 `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
-```{r transcripts}
-transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
-print(transcripts)
-```
+
 COMMENT SOFIA: save a_clean_transcript as d_transcript
@@
 ```{r Data Import}
-t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
-t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
-d_dirt <-rbind(t1, t2)
-d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
+d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", na.strings=c("","NA")),
+                      read_csv("Raw Grades/grades2.csv",na.strings=c("","NA"))) 
+d_transcript <- d_transcript[!duplicated(d_transcript),] #could use distinct() from dplyr
 ```
@@
 # Setup
-n_catalogue <- length(corpus)
+n_catalogue <- length(corpus_catalogues)
 calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
@@
 
-  cat <- content(corpus[[n]])
+  cat <- content(corpus_catalogues[[n]])
 

### 2019-01-10 Data Preparation.Rmd

@@
 `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
-
-COMMENT SOFIA: save a_clean_transcript as d_transcript
 
@@
 However, some mistakes in the way the data was handled meant that the course status of some students was never confirmed.
-We need to ASK RICHARD, but for the moment, we will just look at the grades to change into pass and fail.
+We need to ASK RICHARD, but for the moment, we will just look at the grades of those courses which were not confirmed to change into pass and fail.
 
@@
 ```
+####Ordering in Time
+We would like to have a column `Time` that codes for both year and period (e.g.
+Year_1 Period_2 should be 1.2), as well as a column `Periods` with the year and period as numbers (e.g.
+Year_2 Period_1 should be period 7).
+
+CHECK: we still have students who's first record is of their last year. This appears as UCM_Year=1.
+
+```{r}
+
+a_clean_transcripts <- clean_transcripts%>%
+  separate(Period, 
+           c("T1","T2","T3","T4","T5","T6"), 
+           sep="," 
+           ) %>%
+  gather( key = "Time", value = "Period", T1,T2,T3,T4,T5,T6) %>%
+  drop_na(Period) %>%
+  select(-Time) %>%
+  mutate(Periods = (`UCM_Year-old` - 1) * 6 + 
+           as.numeric(Period)
+         )
+
+a_clean_transcripts$Time= paste(a_clean_transcripts$`UCM_Year-old`,
+                                a_clean_transcripts$Period, 
+                                sep="."
+                                )
+#FINAL DATA:
+d_transcript <-a_clean_transcripts%>%
+  select(-`UCM_Year-old`,-Period)
+```
+NOTES: The data is now arranged so as to respect the order in time for each individual student.
+However, the comparison is still tricky as people who finished in 2008 will have CAP recorded as taken on their first year since this is all the data we have.
+COMMENT SOFIA: save a_clean_transcript as d_transcript
 

### 2019-01-10 Data Preparation.Rmd
going back to  previous version

--- 2019-01-10 Data Preparation.Rmd
@@
 library(hunspell) # Stemmer
-
 library(rlist)
-#library(tidyr) #(maybe incuded in tidyverse)
-#library(tibble)
 ```
@@
 # Import Data
-The datasets we use are saved as spreadsheet on our google drive *DARS*.
+The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons).
 We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
@@
 The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
-`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
+`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.
 ```{r transcripts}
@@
 
-ALL OTHER STUDENTS:
 The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

### 2019-01-10 Data Preparation.Rmd
updating libraries

@@
 library(hunspell) # Stemmer
-library(rlist)
+#library(rlist)
 ```

### 2019-01-10 Data Preparation.Rmd
debugging import section

--- 2019-01-10 Data Preparation.Rmd
@@
 The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
-```{r corpus_manuals, cache = TRUE}
+```{r}
 corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
@@
 ```
-
 ## Student Data
 The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
-`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
+`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.
 
-ALL OTHER STUDENTS:
 The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.
@@
 ```{r Data Import}
-d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", na.strings=c("","NA")),
-                      read_csv("Raw Grades/grades2.csv",na.strings=c("","NA"))) 
-d_transcript <- d_transcript[!duplicated(d_transcript),] #could use distinct() from dplyr
+
+x <- read_csv("Raw Grades/grades1.csv", col_types = cols())
+t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
+t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
+d_dirt <-rbind(t1, t2)
+d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
 ```

### 2019-01-10 Data Preparation.Rmd
Punctuation in Course Data

@@
 We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
-The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong and in which period(s) they are offered, the tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
+The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
+The tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment; and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
 

### 2019-01-10 Data Preparation.Rmd
debugging import d_transcript

--- 2019-01-10 Data Preparation.Rmd
@@
 
-```{r Data Import}
-
-x <- read_csv("Raw Grades/grades1.csv", col_types = cols())
-t1 <- read.csv("Raw Grades/grades1.csv",na.strings=c("","NA"))
-t2 <- read.csv("Raw Grades/grades2.csv",na.strings=c("","NA"))
-d_dirt <-rbind(t1, t2)
-d_dirt <- d_dirt[!duplicated(d_dirt),] #could use distinct() from dplyr
+```{r import d_transcript}
+d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
+                     read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
+  distinct()
 ```

### 2019-01-10 Data Preparation.Rmd

@@
 The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
-```{r corpus_catalogues, cache = TRUE}
+```{r import corpus_catalogues, cache = TRUE}
 corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
@@
 The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
-```{r}
+```{r import corpus_manuals, cache = TRUE}
 corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
@@
 
-```{r import d_transcript}
+```{r import d_transcript, cache = TRUE}
 d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),

### 2019-01-10 Data Preparation.Rmd
Student data, cut explanation
debugging import data - done

@@
 In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
-```{r list}
+```{r import list}
 lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
@@
 
-```{r import data from drive}
+```{r import d_course d_assessment and d_ILO, cache = TRUE}
 d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
@@
 ```{r import d_transcript, cache = TRUE}
-d_transcript <-rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
+d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                       read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%

### 2019-01-10 Data Preparation.Rmd
##Student data in Data Import description

--- 2019-01-10 Data Preparation.Rmd
@@
 ### Course Manuals
-To expand our topic modeling of course content, we would like to analyse the material in the course manuals.
+To expand our topic modeling of course content, we analyse the material in the course manuals.
 The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
+
 ```{r import corpus_manuals, cache = TRUE}
@@
 ## Student Data
-The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2].
-`transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.
-
-The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.
+The tibble `d_transcripts` contains the transcripts information of students as was provided.
+It has 40 columns, and rows correspond to a type of grade (e.g.
+final grade, attendance) per student per course per time they took it.
 

### 2019-01-10 Data Preparation.Rmd
debugging AoD section

--- 2019-01-10 Data Preparation.Rmd
@@
                       read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
-  distinct()
+  distinct
 ```
@@
 In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r}
+```{r d_AoD_ILO}
 d_AoD_ILO <- d_ILO %>%
@@
 
-### AoD from Assessment Type
+### AoD from Assessments
 In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
@@
 `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-```{r}
+```{r map_assessment_AoD}
 map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
@@
 Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r}
+```{r d_AoD_assessment}
 d_AoD_assessment <- tibble(Code        = character(0),
@@
 
-  assessment  <- observation$Assessment
-  AoD_covered <- map_assessment_AoD[assessment, ]
+  assessments <- observation$Assessment
+  AoD_covered <- map_assessment_AoD[assessments, ]
   AoD         <- lists$AoD[AoD_covered]
 
-  if(length(AoD) >= 1){ # if no AoD are covered by assessment (e.g. written exam), then do not rbind rows to d_AoD_assessment
-      AoD_assessment_tidy <- cbind(observation, AoD) %>%
-    as_tibble
-      d_AoD_assessment <- rbind(d_AoD_assessment, AoD_assessment_tidy)
-  }
+  if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
+                                                 as.tibble(cbind(observation,
+                                                                 AoD)))
 
@@
 
-print(d_AoD_assessment)
+rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
 ```
@@
 Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
-```{r}
+```{r d_AoD_assessment distinct}
 d_AoD_assessment <- d_AoD_assessment %>%
   select(Code, AoD) %>%
-  unique
+  distinct
 print(d_AoD_assessment)
@@
 Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
-```{r}
-d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
-  unique %>%
+```{r rbind d_AoD_ILO and d_AoD_assessment}
+d_AoD <- rbind(d_AoD_ILO,
+               d_AoD_assessment) %>%
+  distinct %>%
   arrange(Code)
+
+rm(d_AoD_ILO, d_AoD_assessment)
 print(d_AoD)

### 2019-01-10 Data Preparation.Rmd
Formatting titles

--- 2019-01-10 Data Preparation.Rmd
@@
 # Variable Engineering
-
-## AoD
+##Course Data
+### AoD
 In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
@@
 
-### AoD from ILOs
+#### AoD from ILOs
 In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
@@
 
-### AoD from Assessment Type
+#### AoD from Assessment Type
 In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
@@
 
-### Combining AoD from ILOs and from assessments
+#### Combining AoD from ILOs and from assessments
 Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
@@
 
-## Course Data
+### Courses
 Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
@@
 
-## Course Catalogue
+##Textual Data
+### Course Catalogue
 In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
 
-### Extracting Overviews
+#### Extracting Overviews
 We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
@@
 
-### Extracting Descriptions
+#### Extracting Descriptions
 Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews.
@@
 
-### Tidy Text Format
+#### Tidy Text Format
 We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
@@
 
-### Stemming
+#### Stemming
 We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
@@
 
-## Course Manual 
+### Course Manual 
 We create a dataframe from the Corpus:
@@
 ```
-###(Optional) Pre-processing Course Manuals- Removing stopwords
+####(Optional) Pre-processing Course Manuals- Removing stopwords
 Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
@@
 ```
+
 ##Student Data

### 2019-01-10 Data Preparation.Rmd

@@
 
-#### AoD from Assessment Type
+#### AoD from Assessment
+
 In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.

### 2019-01-10 Data Preparation.Rmd
text AoD

@@
 ### AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
-For instance, if one of the ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
+In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it.
+For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
 

### 2019-01-10 Data Preparation.Rmd
text AoD from ILOs

@@
 #### AoD from ILOs
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
+In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
 ```{r d_AoD_ILO}

### 2019-01-10 Data Preparation.Rmd
debugging course data

--- 2019-01-10 Data Preparation.Rmd
@@
 # Variable Engineering
-##Course Data
-### AoD
+
+## AoD
 In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it or if one of its assessments cover it.
@@
 
-#### AoD from ILOs
+### AoD from ILOs
 In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs and then we take the unique combination of course and AoD in case a course had several ILOs covering the same AoD.
@@
 
-#### AoD from Assessment
-
+### AoD from Assessments
 In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
@@
 
-#### Combining AoD from ILOs and from assessments
+### Combining AoD from ILOs and from assessments
 Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
@@
 
-### Courses
+## Course Data
 Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
@@
 We use a `full_join` to add these variables to the tibble `d_course`.
-```{r}
+```{r d_course detail}
 d_ILO_detail <- d_ILO %>% 
   select(Code, ILO) %>%
-  unique %>%
+  distinct() %>%
   count(Code) %>%
   rename(n_ILO = n)
-print(d_ILO_detail)
 
@@
             `Assessments Covered` = paste(Assessment, collapse = ", "))
-print(d_assessment_detail)
 
@@
             `AoD Covered` = paste(AoD, collapse = ", "))
-print(d_AoD_detail)
+
+d_course_detail <- d_ILO_detail %>%
+  full_join(d_assessment_detail, by = "Code") %>%
+  full_join(d_AoD_detail       , by = "Code")
+
+rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
+print(d_course_detail)
 ```
 
-```{r}
-d_course <- d_course %>%
-  full_join(d_ILO_detail       , by = "Code") %>%
-  full_join(d_assessment_detail, by = "Code") %>%
-  full_join(d_AoD_detail       , by = "Code") %>%
+```{r join d_course_detail}
+d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
   select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
+
+rm(d_course_detail)
 print(d_course)
@@
 We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r}
+```{r create UGR2000}
 d_course <- d_course %>%
@@
 Finally, we add a series of informative variable at the course level.
-```{r}
+```{r d_course additional info}
 d_course <- d_course %>%
@@
 
-##Textual Data
-### Course Catalogue
+## Course Catalogue
 In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
 
-#### Extracting Overviews
+### Extracting Overviews
 We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
@@
 
-#### Extracting Descriptions
+### Extracting Descriptions
 Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews.
@@
 
-#### Tidy Text Format
+### Tidy Text Format
 We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
@@
 
-#### Stemming
+### Stemming
 We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
@@
 
-### Course Manual 
+## Course Manual 
 We create a dataframe from the Corpus:
@@
 ```
-####(Optional) Pre-processing Course Manuals- Removing stopwords
+###(Optional) Pre-processing Course Manuals- Removing stopwords
 Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
@@
 ```
-
 ##Student Data

### 2019-01-10 Data Preparation.Rmd

@@
 
-```{r overview}
+```{r extracting overview}
 # Setup
@@
 
-course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP")
-course_code <- paste(course_code, collapse = "|")
+course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
+  paste(collapse = "|")
 
@@
                         "^Undergraduate Research \\(UGR\\)",
-                        "Appendix")
-content_to_exclude <- paste(content_to_exclude, collapse = "|")
+                        "Appendix") %>%
+  paste(collapse = "|")
 
@@
 
+rm(n_catalogue, calendar_years, course_code, content_to_exclude,
+   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
+   page, current_page, following_page, current_page_content, following_page_content,
+   course_overview, Code, year)
 print(d_description)
@@
 For these, the section *Instructional Format* marks the end of the description section.
-```{r description}
+```{r extracting description}
 # Setup
-symbol_to_line <- c("\r\n", "\n")
-symbol_to_line <- paste(symbol_to_line, collapse = "|")
+symbol_to_line <- c("\r\n", "\n") %>%
+  paste(collapse = "|")
 
-start_descrip <- c("^Description", "^Course Description")
-start_descrip <- paste(start_descrip, collapse = "|")
+start_descrip <- c("^Description", "^Course Description") %>%
+  paste(collapse = "|")
 
 end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
-                   "^Required Litera", "^ Literature$", "Literature \\(all")
-end_descrip   <- paste(end_descrip, collapse = "|")
+                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
+  paste(collapse = "|")
 
@@
 
-  overview_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
-  line_start    <- grep(pattern = start_descrip, x = overview_line) + 1
-  line_end      <- grep(pattern = end_descrip  , x = overview_line) - 1
+  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
+  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
+  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
 
@@
   if(is_empty(line_end)){
-    line_end <- grep(pattern = "^Instructional format$", x = overview_line) - 1
+    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
     print(paste("line_end irregular for", d_description$Code[course],
@@
 
-  description <- paste(overview_line[line_start : line_end], collapse = " ")
+  description <- paste(overview_by_line[line_start : line_end], collapse = " ")
 
@@
 
+rm(symbol_to_line, start_descrip, end_descrip,
+   course, overview, overview_by_line, line_start, line_end, description)
 print(d_description)

### 2019-01-10 Data Preparation.Rmd

@@
 We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
-```{r tidy text data}
+```{r tidy d_description}
 d_overview_tidy <- d_description %>%
@@
 Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
-```{r function stem_hunspell, cache = TRUE}
+```{r stemming dictionary, cache = TRUE}
 stem_hunspell <- function(term) {
-  # look up the term in the dictionary
-  stems <- hunspell_stem(term)[[1]]
-
-  if (length(stems) == 0) { # if there are no stems, use the original term
-    stem <- term
-  } else { # if there are multiple stems, use the last one
-    stem <- stems[[length(stems)]]
+  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
+  n_stems <- length(stems)            # number of stems
+  if (n_stems == 0) term              # if no stems, return original term
+  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
 }
 
-  return(stem)
-}
-
-stems <- d_overview_tidy %>% 
+dictionary <- d_overview_tidy %>% 
   select(word) %>%
@@
 # terms for which the stem differs from the original word
-stems %>%
-  filter(word != word_stem)
+filter(dictionary, word != word_stem)
 ```
 
-```{r stemming}
+```{r stemming d_description}
 d_overview_stem <- d_overview_tidy %>%
-  left_join(stems, by = "word") %>%
+  left_join(dictionary, by = "word") %>%
   rename(word_original = word,
@@
 d_description_stem <- d_description_tidy %>%
-  left_join(stems, by = "word") %>%
+  left_join(dictionary, by = "word") %>%
   rename(word_original = word,

### 2019-01-10 Data Preparation.Rmd
text AoD

--- 2019-01-10 Data Preparation.Rmd
@@
 #### AoD from ILOs
+(For this section we use: `d_ILO`-indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD)
+
 In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
@@
 #### AoD from Assessment
+(For this section we use: `d_assessment`-indicates which type(s) of assessment each course contains with one row per course-assessment)
 
@@
 `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
+
 ```{r map_assessment_AoD}
@@
 
-Now that we have the matrix `map_assessment_AoD`, we create the tibble `d_assessment_clean` which only contains the assessments that are covered by each course and we loop through its rows to determine which AoD, each assessment covers.
-In the loop, we first extract the row of `d_assessment_clean` and save it as `observation` and determine the corresponding assessment which we save as `assessment`.
-Then we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
+Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments.
+To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
+In the loop, we first extract the row of `d_assessment` and save it as `observation`.
+Then, we determine the corresponding assessment which we save as `assessment`.
+Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
 ```{r d_AoD_assessment}
@@
 We use a `full_join` to add these variables to the tibble `d_course`.
-```{r d_course detail}
+```{r}
 d_ILO_detail <- d_ILO %>% 
   select(Code, ILO) %>%
-  distinct() %>%
+  unique %>%
   count(Code) %>%
   rename(n_ILO = n)
+print(d_ILO_detail)
 
@@
             `Assessments Covered` = paste(Assessment, collapse = ", "))
+print(d_assessment_detail)
 
@@
             `AoD Covered` = paste(AoD, collapse = ", "))
-
-d_course_detail <- d_ILO_detail %>%
-  full_join(d_assessment_detail, by = "Code") %>%
-  full_join(d_AoD_detail       , by = "Code")
-
-rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
-print(d_course_detail)
+print(d_AoD_detail)
 ```
 
-```{r join d_course_detail}
-d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
+```{r}
+d_course <- d_course %>%
+  full_join(d_ILO_detail       , by = "Code") %>%
+  full_join(d_assessment_detail, by = "Code") %>%
+  full_join(d_AoD_detail       , by = "Code") %>%
   select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
-
-rm(d_course_detail)
 print(d_course)
@@
 We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r create UGR2000}
+```{r}
 d_course <- d_course %>%
@@
 Finally, we add a series of informative variable at the course level.
-```{r d_course additional info}
+```{r}
 d_course <- d_course %>%

### 2019-01-10 Data Preparation.Rmd
Explanation AoD Assessment
Text in #Courses Variable Engineering

@@
 To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
-In the loop, we first extract the row of `d_assessment` and save it as `observation`.
+In the loop, we first extract a row of `d_assessment` and save it as `observation`.
 Then, we determine the corresponding assessment which we save as `assessment`.
@@
 ### Courses
+(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)
+
 Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers.
-We use a `full_join` to add these variables to the tibble `d_course`.
+For this we create the following three tibbles:
+1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
+2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
+3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
+Then we use a `full_join` to add these variables to the tibble `d_course`.
 ```{r d_course detail}

### 2019-01-10 Data Preparation.Rmd
Text in Textual Data

@@
 ### Course Catalogue
+(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
+
 In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
@@
 #### Extracting Overviews
+
 We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
@@
 We also make use the fact that the overviews always start with the code of the course, i.e.
-it starts with one of the elements of `course_code` and use `grep` to identify the first page of each overview.
+it starts with one of the elements of `course_code`; and we use `grep` to identify the first page of each overview.
 We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.

### 2019-01-10 Data Preparation.Rmd
text on Extracting descriptions, and Stemming

@@
 ##Textual Data
+
 ### Course Catalogue
@@
 #### Extracting Descriptions
-Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews.
+
+Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
 The description section contains a brief description (200-500 words) of the content of the course.
@@
 The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
-Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost overviews.
+Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
 A handful overviews do not contain a *Literature* section.
 For these, the section *Instructional Format* marks the end of the description section.
+
 ```{r extracting description}
@@
 #### Tidy Text Format
+
 We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
@@
 We then apply `stem_hunspell` on the words of `d_overview_tidy`.
-Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find the a list containing *once* each term present in the course overviews and apply the function `stem_hunspell` on this list.
+Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews.
+Then, we apply the function `stem_hunspell` on this list.
 We save the terms and their stems in the tibble `stems`.

### 2019-01-10 Data Preparation.Rmd
debugging corpus of manuals

--- 2019-01-10 Data Preparation.Rmd
@@
 ### Courses
-(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)
-
 Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-For this we create the following three tibbles:
-1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
-2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
-3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
-Then we use a `full_join` to add these variables to the tibble `d_course`.
+The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers.
+We use a `full_join` to add these variables to the tibble `d_course`.
 ```{r d_course detail}
@@
 
-rm(n_catalogue, calendar_years, course_code, content_to_exclude,
+rm(corpus_catalogues,
+   n_catalogue, calendar_years, course_code, content_to_exclude,
    n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
@@
 ```{r tidy d_description}
-d_overview_tidy <- d_description %>%
+d_overview <- d_description %>%
   select(Code, `Calendar Year`, Overview) %>%
@@
 
-d_description_tidy <- d_description %>%
+d_description <- d_description %>%
   select(Code, `Calendar Year`, Description) %>%
@@
 
-dictionary <- d_overview_tidy %>% 
+dictionary <- d_overview %>% 
   select(word) %>%
@@
 ```{r stemming d_description}
-d_overview_stem <- d_overview_tidy %>%
+d_overview <- d_overview %>%
   left_join(dictionary, by = "word") %>%
@@
   filter(!word %in% stop_words$word)
-print(d_overview_stem) # See humanities - humanity
 
-d_description_stem <- d_description_tidy %>%
+d_description <- d_description %>%
   left_join(dictionary, by = "word") %>%
@@
   filter(!word %in% stop_words$word)
-print(d_description_stem) # See starting - start
+
+rm(stems, stem_hunspell)
+print(d_overview_stem) # See humanities - humanity
 ```
@@
 We create a dataframe from the Corpus:
-```{r}
-manuals_td <- tidy(corpus_manuals)
+```{r d_manual}
+d_manual <- tidy(corpus_manuals) %>%
+  select(id, text) %>%
+  mutate(Code = substring(id, 1, 7)) %>%
+  select(-id) %>%
+  rename(Manual = text)
+
+rm(corpus_manuals)
+print(d_manual)
+```
+
+```{r join manuals to d_course}
+d_course <- full_join(d_course, d_manual, by = "Code")
 ```
@@
 
-```{r}
-manuals_tokens <- manuals_td %>%
-  select(id,text) %>%
-  mutate(Concentration= substring(id, 1, 3), Code= substring(id,1,7))%>%
-  unnest_tokens(word, text)
+```{r d_manual tidy}
+d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
 ```
+
 ####(Optional) Pre-processing Course Manuals- Removing stopwords
@@
 
+my_sw <- c("______________________________________________________________________________")
+
 data("stop_words")  #imports common stopwords
 
-my_stop_words <- data.frame (word = c(1:11, "students", "______________________________________________________________________________")) #no stemming ("students")
-number_stopwords <- number_stopwords <- manuals_tokens %>% #can be cleaner by using unique (?)
-  mutate(is_number=grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",word))%>% #finds stand alone numbers (incl. -, and .)
-  filter(is_number==T)
+my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
 

### 2019-01-10 Data Preparation.Rmd

@@
 ##Textual Data
+
 ### Course Catalogue
+(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
+
 In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.

### 2019-01-10 Data Preparation.Rmd
Spacing

--- 2019-01-10 Data Preparation.Rmd
@@
 ## Student Data
-The tibble `d_transcripts` contains the transcripts information of students as was provided.
+The tibble `d_transcripts` contains the transcript information of students as was provided.
 It has 40 columns, and rows correspond to a type of grade (e.g.
@@
 
-#### Tidy Text Format
+### Course Manuals
+
+### Tidy Text Format
 
@@
 ##Student Data
+
 ###Renaming Variables

### 2019-01-10 Data Preparation.Rmd
move section up

@@
 
-### Course Catalogue
+### Extracting Text
 (For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
@@
 
-### Course Manuals
+### Extracting Course Manual Text
+We create a dataframe from the Corpus:
+```{r d_manual}
+d_manual <- tidy(corpus_manuals) %>%
+  select(id, text) %>%
+  mutate(Code = substring(id, 1, 7)) %>%
+  select(-id) %>%
+  rename(Manual = text)
+
+rm(corpus_manuals)
+print(d_manual)
+```
+
+```{r join manuals to d_course}
+d_course <- full_join(d_course, d_manual, by = "Code")
+```
 
@@
 ### Course Manual
-We create a dataframe from the Corpus:
-```{r d_manual}
-d_manual <- tidy(corpus_manuals) %>%
-  select(id, text) %>%
-  mutate(Code = substring(id, 1, 7)) %>%
-  select(-id) %>%
-  rename(Manual = text)
-
-rm(corpus_manuals)
-print(d_manual)
-```
-
-```{r join manuals to d_course}
-d_course <- full_join(d_course, d_manual, by = "Code")
-```
 

### 2019-01-10 Data Preparation.Rmd
new text for sections that were moves

@@
 ### Extracting Text
+In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.
+
+####Course Catalogues
 (For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
 
-In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues.
-
-#### Extracting Overviews
+##### Extracting Overviews
 
@@
 
-#### Extracting Descriptions
+##### Extracting Descriptions
 
@@
 
-### Extracting Course Manual Text
-We create a dataframe from the Corpus:
+### Course Manuals
+####Extracting Full Text
+(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))
+
+Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
 ```{r d_manual}
@@
 
+Separately, we want to add the manual textual information to`d_course`which contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
 ```{r join manuals to d_course}

### 2019-01-10 Data Preparation.Rmd
removing stopwords section
including d_manual to stemming section

--- 2019-01-10 Data Preparation.Rmd
@@
   unnest_tokens(output = word, input = Description)
-print(d_description_tidy)
+
+d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
 ```
@@
 
-dictionary <- d_overview %>% 
+dictionary <- select(d_overview, Code, word) %>%
+  rbind(d_manual) %>% 
   select(word) %>%
   distinct %>%
-  arrange(word) %>%
   mutate(word_stem = purrr::map_chr(.x = word,
@@
 filter(dictionary, word != word_stem)
+
+my_sw <- c("______________________________________________________________________________")
+
+data("stop_words")  #imports common stopwords
+
+my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
+
+manuals_tokens_preprocessed <- manuals_tokens %>%
+  anti_join(stop_words)     %>%
+  anti_join(my_stop_words) %>%
+  anti_join(number_stopwords, by = c("word"="word"))
+
 ```
@@
 ```{r d_manual tidy}
-d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
+
 ```
@@
 ```{r}
-
-my_sw <- c("______________________________________________________________________________")
-
-data("stop_words")  #imports common stopwords
-
-my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
-
-manuals_tokens_preprocessed <- manuals_tokens %>%
-  anti_join(stop_words)     %>%
-  anti_join(my_stop_words) %>%
-  anti_join(number_stopwords, by = c("word"="word"))
 

### 2019-01-10 Data Preparation.Rmd

--- 2019-01-10 Data Preparation.Rmd
@@
 ```
+### Removing Stopwords
 

### 2019-01-10 Data Preparation.Rmd
text: tidy text format

@@
 
-We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
+To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
 ```{r tidy d_description}

### 2019-01-10 Data Preparation.Rmd
remove irrelevant sections

@@
 
-### Course Manual
-
-From `manuals_td` we are only interested in the text, and the Code of the course.
-However, we don't have the code but we have a document id that includes it.
-Therefore we select only the `text` and `id` columns of the `manuals_td`.
-Then, we extract the code from the `id` and save it in under `Code`, We aso extract the concentration from the `id` and save it under `Concentration`.
-Finally, we unnest the dataframe to have only one word per row, and call this `manuals_tokens`, this creates a variable `word` and adds all of the text from the course manuals under this column.
-
-```{r d_manual tidy}
-
-```
-
-####(Optional) Pre-processing Course Manuals- Removing stopwords
-Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
-For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers.
-We save these words in different dataframes and then exclude with an antijoin.
-```{r}
-
-```
-
 ##Student Data

### 2019-01-10 Data Preparation.Rmd
explanation of student data

@@
 ## Student Data
-The tibble `d_transcripts` contains the transcript information of students as was provided.
+The tibble `d_transcript` contains the transcript information of students as was provided.
 It has 40 columns, and rows correspond to a type of grade (e.g.
@@
 ##Student Data
-
+(In this section we use: `d_transcript`- contains the transcript information of students as was provided.
+It has 40 columns, and rows correspond roughly to a type of grade (e.g.
+final grade, attendance) per student per course per time they took it).
 ###Renaming Variables

### 2019-01-10 Data Preparation.Rmd
empty space
code for removing stop words

--- 2019-01-10 Data Preparation.Rmd
@@
 
-To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
+We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
 ```{r tidy d_description}
@@
 Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
-```{r stemming dictionary, cache = TRUE}
+```{r creating dictionary, cache = TRUE}
 stem_hunspell <- function(term) {
@@
 
-dictionary <- select(d_overview, Code, word) %>%
-  rbind(d_manual) %>% 
-  select(word) %>%
+my_dictionary <- rbind(select(d_overview, word),
+                       select(d_manual  , word)) %>%
   distinct %>%
@@
 # terms for which the stem differs from the original word
-filter(dictionary, word != word_stem)
-
-my_sw <- c("______________________________________________________________________________")
-
-data("stop_words")  #imports common stopwords
-
-my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
-
-manuals_tokens_preprocessed <- manuals_tokens %>%
-  anti_join(stop_words)     %>%
-  anti_join(my_stop_words) %>%
-  anti_join(number_stopwords, by = c("word"="word"))
-
+filter(my_dictionary, word != word_stem)
 ```
 
-```{r stemming d_description}
-d_overview <- d_overview %>%
-  left_join(dictionary, by = "word") %>%
+```{r stemming}
+stem_with_dictionary <- function(data)  data %>%
+  left_join(my_dictionary, by = "word") %>%
   rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
+         word = word_stem)
 
-d_description <- d_description %>%
-  left_join(dictionary, by = "word") %>%
-  rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
+d_overview    <- stem_with_dictionary(d_overview)
+d_description <- stem_with_dictionary(d_description)
+d_manual      <- stem_with_dictionary(d_manual)
 
-rm(stems, stem_hunspell)
-print(d_overview_stem) # See humanities - humanity
+rm(stem_hunspell, my_dictionary, stem_with_dictionary)
+print(d_overview) # See humanities - humanity
 ```
+
 ### Removing Stopwords
+
+```{r}
+# own stopwords
+sw_own <- c("______________________________________________________________________________")
+
+remove_sw <- function(data) data %>%
+  filter(! word %in% c(stop_words$word,
+                       sw_own))
+
+d_overview    <- remove_sw(d_overview)
+d_description <- remove_sw(d_description)
+d_manual      <- remove_sw(d_manual)
+
+rm(stem_hunspell, my_dictionary, remove_sw, sw_own)
+```
 

### 2019-01-10 Data Preparation.Rmd

@@
 
-### Course Manual
-
-From `manuals_td` we are only interested in the text, and the Code of the course.
-However, we don't have the code but we have a document id that includes it.
-Therefore we select only the `text` and `id` columns of the `manuals_td`.
-Then, we extract the code from the `id` and save it in under `Code`, We aso extract the concentration from the `id` and save it under `Concentration`.
-Finally, we unnest the dataframe to have only one word per row, and call this `manuals_tokens`, this creates a variable `word` and adds all of the text from the course manuals under this column.
-
-```{r d_manual tidy}
-
-```
-
-####(Optional) Pre-processing Course Manuals- Removing stopwords
-Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers.
-For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers.
-We save these words in different dataframes and then exclude with an antijoin.
-```{r}
-
-```
-
 ##Student Data
+(In this section we use: `d_transcript`- contains the transcript information of students as was provided.
+It has 40 columns, and rows correspond roughly to a type of grade (e.g.
+final grade, attendance) per student per course per time they took it).
 

### 2019-01-10 Data Preparation.Rmd
Explanation transcripts

--- 2019-01-10 Data Preparation.Rmd
@@
 final grade, attendance) per student per course per time they took it).
+
 ###Renaming Variables
@@
 ###Identifying usless variables
-Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
+Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage.
+
+NOTE TO RAPHAEL: This was in case we later wanted to use any of the non-empty variables, but I don't think we need this anymore, so you can safely just cut this section and select fewer variables later.
 ```{r}

### 2019-01-10 Data Preparation.Rmd
structure

--- 2019-01-10 Data Preparation.Rmd
@@
 
-### Course Manuals
-####Extracting Full Text
+#### Course Manuals
+#####Extracting Full Text
 (For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))

### 2019-01-10 Data Preparation.Rmd
more suitable names to var. of d_transcript

--- 2019-01-10 Data Preparation.Rmd
@@
 ```{r}
-d_rename <-d_dirt %>%
-  rename(
-    ID                     =  "X...Student.Number", 
-    Code                   =  "Module..Abbrev..", 
-    `Course Title`         =  "Module..Desc..",
-    `Program Abbreviation` =  "Program..Abbreviation.", 
-    `Program Description`  =  "Program..Description.",               
-    Year                   =  "Academic.Year",                      
-    Session                =  "Academic.Session",
-    `Appraisal Code`       =  "Appraisal.Type",                     
-    `Appraisal Title`      =  "Appraisal..Description.",             
-    Attempt                =  "Number.rep..attemp",                 
-    Grade                  =  "Grade.symbol",                        
-    `Appraisal Status`     =  "Appraisal.Status",                   
-    `Appraisal Status Description` =  "Appraisal.Status..Desc..",    #is only NA: unique(d4$Appraisal.Status..Desc..)       
-    `Booking Reason`       =  "Module.Booking.Reason..Description.",
-    `Appraisal Date`       =  "Appraisal.date",                      
-    `Attempted Credits`    =  "Attempted.credits",                  
-    `Earned Credit`        =  "Earned.Credits",                      
-    `Credit Type`          =  "Credit.Type",                        
-    `Personnel Number`     =  "Personnel.Number",                  
-    `Name (Employee/Applicant)`=  "Name.of.employee.or.applicant",      
-    `Individual Work`      =  "Individual.Work",                     
-    `Academic Work ID`     =  "Academic.Work.ID",                   
-    `Booking Status`       =  "Booking.Status",                      #empty
-    `Booking Status Description` =  "Booking.Status..Desc..",             
-    `Event Object Id`      =  "Event.Object.Id",                     #empty forwards and including      
-    `Business Event Abbreviation` =  "Business.event.abbr.",               
-    `Event Description`    =  "Event.Description",                   
-    `Start time`           =  "Start.time",                         
-    `End time`             =  "End.time",                            
-    `Date`                 =  "Date",                               
-    `Studyplan`            =  "Studyplan",                           
-    `Conditional booking`  =  "Conditiona.booking",                 
-    `Wachtlist`            =  "Wachtlist",                           
-    `Object ID`            =  "Object.ID",                          
-    `Object Name`          =  "Object.name",                         
-    `Start Date`           =  "Start.date",                         
-    `End Date`             =  "End.Date",                            
-    `Number of Weeks`      =  "Number.of.weeks",                      #until this one next has values              
-    `Appraiser ID`         =  "Appraiser.ID",                        
-    `Appraiser Name`       =  "Appraiser.Name"
 
-  ) 
 ```
@@
 ###Identifying usless variables
-Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage.
-
-NOTE TO RAPHAEL: This was in case we later wanted to use any of the non-empty variables, but I don't think we need this anymore, so you can safely just cut this section and select fewer variables later.
+Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage
 ```{r}
-not_keep <- c("Booking Status",
-              "Appraisal Status Description",
-              "Credit Type",
-              "Personnel Number",
-              "Event Object Id",     
-              "Business Event Abbreviation",               
-              "Event Description",                   
-              "Start time",                         
-              "End time",                            
-              "Date",                               
-              "Studyplan",                           
-              "Conditional booking",                 
-              "Wachtlist",                           
-              "Object ID", #? has values e.g. 50236380                        
-              "Object Name",  #?  has values, e.g. "BE-Universitair Ziekenhuis Brussel"
-              "Start Date",   #? has values, e.g.  "12/16/13"                     
-              "End Date",     #? has values, e.g. "5/14/10"                      
-              "Number of Weeks", 
-              "Name (Employee/Applicant)",
-              "Appraiser ID",      #HAS VALUES BUT NOT IMPORTANT, e.g. 70011933
-              "Appraiser Name",    #HAS VALUES BUT NOT IMPORTANT, e.g.  J.J. Briede  
-              "Academic Work ID",  #has values, eg.53EA405080711826E10000008978030A
-              "Attempted Credits", #HAS VALUES BUT NOT IMPORTANT
-              "Earned Credit",
-              "Individual Work",
-              "Appraisal Status",
-              "Booking Reason",
-              "Appraisal Date" #day when grades were put in
-              ) 
+d_transcript <- d_transcript %>%
+  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
+         `Program (Description)`, `Academic Year`, `Academic Session`,
+         `Appraisal (Description)`,
+         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
+  rename(`Student ID Number` = `Student Number`,
+         `Course Code` = `Module (Abbrev.)`,
+         `Course Title` = `Module (Desc.)`,
+         `Study Program` = `Program (Description)`,
+         `Civil Year` = `Academic Year`, # double check
+         `Period` = `Academic Session`,
+         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
+         `Number Repeated Attempt` = `Number rep. attemp`,
+         `Grade` = `Grade symbol`,
+         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
 ```
@@
 ```{r}
-d_rename <-d_rename %>%
+d_rename <- d_rename %>%
   mutate(Period= case_when(

### 2019-01-10 Data Preparation.Rmd

@@
 Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
-```{r creating dictionary, cache = TRUE}
+```{r stemming dictionary, cache = TRUE}
 stem_hunspell <- function(term) {
@@
 
-my_dictionary <- rbind(select(d_overview, word),
-                       select(d_manual  , word)) %>%
+dictionary <- select(d_overview, Code, word) %>%
+  rbind(d_manual) %>% 
+  select(word) %>%
   distinct %>%
@@
 # terms for which the stem differs from the original word
-filter(my_dictionary, word != word_stem)
+filter(dictionary, word != word_stem)
+
+my_sw <- c("______________________________________________________________________________")
+
+data("stop_words")  #imports common stopwords
+
+my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
+
+manuals_tokens_preprocessed <- manuals_tokens %>%
+  anti_join(stop_words)     %>%
+  anti_join(my_stop_words) %>%
+  anti_join(number_stopwords, by = c("word"="word"))
+
 ```
 
-```{r stemming}
-stem_with_dictionary <- function(data)  data %>%
-  left_join(my_dictionary, by = "word") %>%
+```{r stemming d_description}
+d_overview <- d_overview %>%
+  left_join(dictionary, by = "word") %>%
   rename(word_original = word,
-         word = word_stem)
+         word = word_stem) %>%
+  filter(!word %in% stop_words$word)
 
-d_overview    <- stem_with_dictionary(d_overview)
-d_description <- stem_with_dictionary(d_description)
-d_manual      <- stem_with_dictionary(d_manual)
+d_description <- d_description %>%
+  left_join(dictionary, by = "word") %>%
+  rename(word_original = word,
+         word = word_stem) %>%
+  filter(!word %in% stop_words$word)
 
-rm(stem_hunspell, my_dictionary, stem_with_dictionary)
-print(d_overview) # See humanities - humanity
+rm(stems, stem_hunspell)
+print(d_overview_stem) # See humanities - humanity
 ```
-
 ### Removing Stopwords
-
-```{r}
-# own stopwords
-sw_own <- c("______________________________________________________________________________")
-
-remove_sw <- function(data) data %>%
-  filter(! word %in% c(stop_words$word,
-                       sw_own))
-
-d_overview    <- remove_sw(d_overview)
-d_description <- remove_sw(d_description)
-d_manual      <- remove_sw(d_manual)
-
-rm(stem_hunspell, my_dictionary, remove_sw, sw_own)
-```
 

### 2019-01-10 Data Preparation.Rmd
Deletes renaming variables section and adds text to Selecting Variables section

@@
 
-###Renaming Variables
-First we rename the variable names to make them more comprehensible:
-```{r}
+###Selecting Variables
 
-```
+Our dataframe contains many variables that are either empty or meaningless for our analysis, thus we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
 
-###Identifying usless variables
-Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage.
-
-NOTE TO RAPHAEL: This was in case we later wanted to use any of the non-empty variables, but I don't think we need this anymore, so you can safely just cut this section and select fewer variables later.
 ```{r}

### 2019-01-10 Data Preparation.Rmd
clean period var.

--- 2019-01-10 Data Preparation.Rmd
@@
 ```{r}
-d_rename <- d_rename %>%
-  mutate(Period= case_when(
-    (Session==100)~"1",
-    (Session==101)~"1",
-    (Session==102)~"1",
-    #(Session==190)~"1", #is not there
-    (Session==191)~"1",
-    (Session==200)~"2",
-    (Session==201)~"2",
-    (Session==202)~"2",
-    (Session==291)~"2",
-    (Session==300)~"3",
-    (Session==330)~"3",
-    (Session==350)~"3",
-    (Session==400)~"4",
-    (Session==410)~"4",
-    (Session==420)~"4",
-    (Session==430)~"4",
-    (Session==450)~"4",
-    (Session==460)~"4",
-    (Session==481)~"4",
-    (Session==482)~"4",
-    (Session==500)~"5",
-    (Session==520)~"5",
-    (Session==530)~"5",
-    (Session==550)~"5",
-    (Session==551)~"5",
-    (Session==560)~"5",
-    (Session==552)~"5",
-    (Session==580)~"5",
-    (Session==600)~"6",
-    (Session==610)~"6",
-    (Session==620)~"6",
-    (Session==630)~"6",
-    (Session==650)~"6",
-    (Session==660)~"6",
-    (Session==680)~"5",#WHHHHHHHHHHHHHHHHHAAAAAAAAAAATTTTTTTTTTT?????? Why is this period 5
-    (Session==1)~"1,2,3,4,5,6",
-    (Session==2)~"1,2,3",
-    (Session==3)~"4,5,6",
-    #(Session==203)~c("2","3"),#is not there
-    (Session==350)~"3,4,5",
-    (Session==403)~"4,5",
-    (Session==900)~"1,2,3,4,5,6",
-    (Session==910)~"1", #ASK ABOUT THE 900'S
-    (Session==911)~"1",
-    (Session==912)~"1",
-    (Session==913)~"1",
-    (Session==914)~"1",
-    (Session==915)~"1",
-    (Session==916)~"1",
-    (Session==920)~"1",
-    (Session==923)~"1",
-    (Session==930)~"1",
-    (Session==940)~"1",
-    (Session==950)~"1",
-    (Session==960)~"1"
-     )
-           )
+d_transcript <- d_transcript %>%
+  mutate(Period = case_when(Period == 1 ~ "1 to 6"  ,
+                            Period == 2 ~ "1 to 3"  ,
+                            Period == 3 ~ "4 to 6"  ,
+                            Period == 680 ~ "5"     , # exception
+                            Period == 350 ~ "3 to 5", # exception
+                            Period == 403 ~ "4 to 5", # exception
+                            Period == 900 ~ "1 to 6", # exception
+                            between(Period, 100, 199) ~ "1",
+                            between(Period, 200, 299) ~ "2",
+                            between(Period, 300, 399) ~ "3",
+                            between(Period, 400, 499) ~ "4",
+                            between(Period, 500, 599) ~ "5",
+                            between(Period, 600, 660) ~ "6",
+                            between(Period, 901, 999) ~ "1"))
+
 ```

### 2019-01-10 Data Preparation.Rmd
simplify code for d_transcript

@@
 d_transcript <- d_transcript %>%
+  filter(`Appraisal (Description)` == "Grade supervisor")
   select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
          `Program (Description)`, `Academic Year`, `Academic Session`,
-         `Appraisal (Description)`,
          `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
+  distinct %>%
   rename(`Student ID Number` = `Student Number`,
@@
          `Period` = `Academic Session`,
-         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
          `Number Repeated Attempt` = `Number rep. attemp`,
@@
 ```{r}
-d_reduce <- d_rename %>%
-  select(-not_keep,-Session,-`Program Abbreviation`)
 
-d_reduce <- d_reduce[!duplicated(d_reduce),]
 ```
@@
 ```{r}
-d_grade <- d_reduce %>%
-  filter(`Appraisal Title` == "Grade supervisor") %>%
-  mutate(`Course concentration` = substr(Code, start = 1, stop = 3))
 
-d_grade <- d_grade[!duplicated(d_grade),]
 ```

### 2019-01-11 Data Preparation.Rmd
deletes empty section and updates text

@@
 
-Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
+Each faculty had a different code for their calendars, we want to standardise them so we can compare.
+We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R.
+Vos) and save it under a variable `Period`:
 ```{r}
@@
 ```
-###Dropping useless variables:
-Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:
 
-```{r}
-
-```
 ###Extracting grades

### 2019-01-11 Data Preparation.Rmd
deletes space

@@
 # Save Data
-
 ```{r}

### 2019-01-11 Data Preparation.Rmd
text #Selecting Variables

@@
 
-Our dataframe contains many variables that are either empty or meaningless for our analysis, thus we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
-
+Our dataframe contains many variables and rows that are either empty or meaningless for our analysis.
+First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor").
+Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
 ```{r}

### 2019-01-11 Data Preparation.Rmd
Deletes #Extracting grades section

@@
 
-###Extracting grades
-We notice that there are several values under `Grade` for the same course.
-We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor".
-So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:
-
-```{r}
-
-```
-
 ##Estimating concentrations:

### 2019-01-11 Data Preparation.Rmd
debug student data

--- 2019-01-11 Data Preparation.Rmd
@@
 d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
-                      read_csv("Raw Grades/grades2.csv", col_types = cols())) %>%
-  distinct
+                      read_csv("Raw Grades/grades2.csv", col_types = cols()))
 ```
@@
 
-```{r extracting overview}
+```{r extracting overview, cache = TRUE}
 # Setup
@@
 
-```{r extracting description}
+```{r extracting description, cache = TRUE}
 # Setup
@@
   unnest_tokens(output = word, input = Overview)
-print(d_overview_tidy)
 
@@
 filter(dictionary, word != word_stem)
-
-my_sw <- c("______________________________________________________________________________")
-
-data("stop_words")  #imports common stopwords
-
-my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")
-
-manuals_tokens_preprocessed <- manuals_tokens %>%
-  anti_join(stop_words)     %>%
-  anti_join(my_stop_words) %>%
-  anti_join(number_stopwords, by = c("word"="word"))
-
 ```
@@
 ```{r stemming d_description}
-d_overview <- d_overview %>%
+stem_with_dictionary <- function(data) data %>%
                                          left_join(dictionary, by = "word") %>%
                                          rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
+                                                word = word_stem)
 
-d_description <- d_description %>%
-  left_join(dictionary, by = "word") %>%
-  rename(word_original = word,
-         word = word_stem) %>%
-  filter(!word %in% stop_words$word)
+d_description <- stem_with_dictionary(d_description)
+d_overview <- stem_with_dictionary(d_overview)
+d_manual <- stem_with_dictionary(d_manual)
 
@@
 ### Removing Stopwords
+```{r}
+
+# Own stop words
+sw_own <- c("______________________________________________________________________________")
+
+remove_sw <- function(data) data %>%
+  filter(! word %in% c(stop_words$word, sw_own))
+
+d_description <- remove_sw(d_description)
+d_overview <- remove_sw(d_overview)
+d_manual <- remove_sw(d_manual)
+```
 
@@
 d_transcript <- d_transcript %>%
-  filter(`Appraisal (Description)` == "Grade supervisor")
+  filter(`Appraisal (Description)` == "Grade supervisor") %>%
   select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
@@
          `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
-  distinct %>%
   rename(`Student ID Number` = `Student Number`,
@@
          `Number Repeated Attempt` = `Number rep. attemp`,
-         `Grade` = `Grade symbol`,
-         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
+         Grade = `Grade symbol`,
+         `Status` = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
+  distinct
 ```
 
-Each faculty had a different code for their calendars, we want to standardise them so we can compare.
-We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R.
-Vos) and save it under a variable `Period`:
+Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes and save it under a variable `Period`:
 ```{r}
@@
 ```
+###Dropping useless variables:
+Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:
 
+```{r}
+
+```
 ###Extracting grades
@@
 
-```{r}
-d_student_concentration <- d_grade %>%
-  group_by(ID, `Course concentration`) %>%
-  summarise(count = n()) %>%
-  arrange(ID,desc(count)) %>% #LONG
-  spread(`Course concentration`,count, fill=0) %>% #WIDE
+```{r, eval = FALSE}
+d_concentration <- d_course %>%
+  select(Code, Concentration, `Concentration (additional)`) %>%
+  gather(key = X, value = Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  select(Concentration, `Student ID Number`) %>%
+  count(Concentration, `Student ID Number`) %>%
+  spread(key = Concentration, value = n, fill = 0) %>%
+  mutate(n_course = HUM + SCI + SSC,
+         `Student Concentration` = case_when(
+           n_course < 20 ~ "not enough courses",
+           HUM > 5 & SSC > 5 & SCI > 5 ~ "confused",
+           HUM > 5 & SSC > 5           ~ "HUM/SCI",
+           HUM > 5                     ~ "HUM",
+                     SSC > 5 & SCI > 5 ~ "SSC/SCI",
+                     SSC > 5           ~ "SSC",
+                               SCI > 5 ~ "SCI"
+  ))
+
   transmute(student_Concentration = case_when(
@@
 Since we will need to check each student with an "oops" concentration to see what happened, lets separate this data for later:
-```{r}
+```{r, eval = FALSE}
 checkup <- filter(d_student_concentration, student_Concentration == "oops") 
@@
 First, lets find out, which year was a student's first year and which year was a student's last year (we will also create a variable `Subs_year` that we will substract later to transform from Calendar Year to UCM Year, and a second variable `LengthUCM` that shows us how many years each student stayed at the college):
-```{r}
+```{r, eval = FALSE}
 
@@
 
-```{r}
+```{r, eval = FALSE}
 
@@
 
-```{r}
+```{r, eval = FALSE}
 var_years <- as.character(2007:2017)
@@
 
-```{r}
+```{r, eval = FALSE}
 d_students <- d_grade %>%
@@
 For this we keep only the capstones. We expect some people to have repeated capstones:
-```{r}
+```{r, eval = FALSE}
 capstone_count <- d_students %>%
@@
 
-```{r}
+```{r, eval = FALSE}
 passed_capstone_count <- d_students %>%
@@
 We can check the grades for people who had repeated passed capstones (lets just bring them to the top of the list):
-```{r}
+```{r, eval = FALSE}
 passed_capstone_count %>%
@@
 We can check if there are any students with passing capstone who do not have a grade of at least 5.5. We do this by looking at the lowest Max values:
-```{r}
+```{r, eval = FALSE}
 passed_capstone_count %>%
@@
 Now lets just keep the highest value for each student and correct for student 282995:
-```{r}
+```{r, eval = FALSE}
 passed_capstone_grades <- passed_capstone_count %>%
@@
 First we get the years for which there is a corresponding passing capstone grade, and check for repetition:
-```{r}
+```{r, eval = FALSE}
 
@@
 Therefore, lets substitute na values with the year 9999 (or will ucm be open in the year 9999?).
-```{r}
+```{r, eval = FALSE}
 d_transcripts <- d_students %>%
@@
 Now we will remove all courses with negative `After Graduation`:
-```{r}
+```{r, eval = FALSE}
 master_courses <- d_transcripts%>%
@@
 
-```{r}
+```{r, eval = FALSE}
 booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
@@
 # Save Data
+
 ```{r}
@@
 save(lists, d_course, d_AoD, d_assessment, d_transcript,
-     d_overview_stem, d_description_stem,
+     d_overview, d_description, d_manual,
      file = "data_pillar_2.RDATA")

### 2019-01-11 Data Preparation.Rmd
minor change

@@
 
-```{r stemming d_description}
+```{r stemming data sets}
 stem_with_dictionary <- function(data) data %>%

### 2019-01-11 Data Preparation.Rmd

@@
                             between(Period, 901, 999) ~ "1"))
-
-```
-###Dropping useless variables:
-Now that our `Period` variable is clean, we can exclude the variables that we will not use, and we will delete newly generated duplicate rows:
-
-```{r}
-
-```
-###Extracting grades
-We notice that there are several values under `Grade` for the same course.
-We are interested in keeping only the final grades, corresponding to the rows where `Appraisal Title` is marked as "Grade supervisor".
-So lets extract the grades and add the course concentration by keeping the first three letters of the `Code`:
-
-```{r}
 

### 2019-01-11 Data Preparation.Rmd
data preparation debugged

@@
 
-rm(stems, stem_hunspell)
-print(d_overview_stem) # See humanities - humanity
+rm(stems, stem_hunspell, stem_with_dictionary)
+print(d_overview) # See humanities - humanity
 ```
@@
 d_manual <- remove_sw(d_manual)
+
+rm(sw_own, remove_sw)
 ```
@@
 We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
-```{r}
+```{r, eval = FALSE}
 to_remove <- capstone_finish_year%>%

### 2019-01-11 Data Preparation.Rmd
Copy Paste

--- 2019-01-11 Data Preparation.Rmd
@@
 library(tidytext) 
-
 library(gsheet) # import spreadsheets from google drive
@@
 lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
-
 lists <- list(
@@
   )
-
 rm(lists_brut)
@@
 print(d_course)
-
 d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
@@
 print(d_assessment)
-
 d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
@@
   unique
-
 print(d_AoD_ILO)
@@
                            AoD         = character(0))
-
 for(i in 1 : nrow(d_assessment)){
@@
                                                                  AoD)))
-
 }
-
 rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
@@
   arrange(Code)
-
 rm(d_AoD_ILO, d_AoD_assessment)
@@
   rename(n_ILO = n)
-
 d_assessment_detail <- d_assessment %>%
@@
             `Assessments Covered` = paste(Assessment, collapse = ", "))
-
 d_AoD_detail <- d_AoD %>%
@@
             `AoD Covered` = paste(AoD, collapse = ", "))
-
 d_course_detail <- d_ILO_detail %>%
@@
   full_join(d_AoD_detail       , by = "Code")
-
 rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
@@
   select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
-
 rm(d_course_detail)
@@
                                   Code == "UGR3005" ~ "UGR2005")))
-
 print(filter(d_course, Code %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
@@
                         Overview        = character(0))
-
 course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
   paste(collapse = "|")
-
 content_to_exclude <- c("^Core Courses \\(COR\\)",
@@
   paste(collapse = "|")
-
 # Loop
@@
       else course_overview <- paste(current_page_content, following_page_content)
-
       # Save Overview
@@
 } # close for-loop (n)
-
 rm(corpus_catalogues,
@@
   paste(collapse = "|")
-
 start_descrip <- c("^Description", "^Course Description") %>%
   paste(collapse = "|")
-
 end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
@@
   paste(collapse = "|")
-
 d_description <- d_description %>%
   mutate(Description = NA)
-
 # Loop
@@
   line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
-
   # for overviews w/o Literature section, find section Instructional Format.
@@
 }
-
 rm(symbol_to_line, start_descrip, end_descrip,
@@
   rename(Manual = text)
-
 rm(corpus_manuals)
@@
   unnest_tokens(output = word, input = Overview)
-
 d_description <- d_description %>%
@@
   unnest_tokens(output = word, input = Description)
-
 d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
@@
 }
-
 dictionary <- select(d_overview, Code, word) %>%
@@
                                     .f = stem_hunspell))
-
 # terms for which the stem differs from the original word
@@
 d_manual <- stem_with_dictionary(d_manual)
-
-rm(stems, stem_hunspell)
-print(d_overview_stem) # See humanities - humanity
+rm(stems, stem_hunspell, stem_with_dictionary)
+print(d_overview) # See humanities - humanity
 ```
@@
 ```{r}
-
 # Own stop words
 sw_own <- c("______________________________________________________________________________")
-
 remove_sw <- function(data) data %>%
   filter(! word %in% c(stop_words$word, sw_own))
-
 d_description <- remove_sw(d_description)
@@
 d_manual <- remove_sw(d_manual)
+rm(sw_own, remove_sw)
 ```
@@
                             between(Period, 901, 999) ~ "1"))
-
 ```
@@
 ```{r, eval = FALSE}
-
 d_year <- d_grade %>%
@@
 ```{r, eval = FALSE}
-
 d_year1 <- d_grade %>%
@@
   spread(Year,Present, fill = 0)
-
 ```
@@
 
-```{r}
-
+```{r, eval = FALSE}
 d_time <- left_join(d_year1, d_year)
-
 ```
@@
 var_years <- as.character(2007:2017)
-
 d_time <- d_time %>% 
@@
                    T     ~ .)))
-
 d_time[d_time == 9999999999] <- NA
-
 ```
@@
   replace_na(list(Grade=-1))
-
 # Years dictionary:
@@
   select(-Cal_Year)
-
 #adding the ucm year to transcripts:
@@
   left_join(year_dic, by=c("ID","Year"))
-
 #removing repeated values:
 d_students <- d_students[!duplicated(d_students),]
-
 ```
@@
   summarise(Count=n())
-
 capstone_count
@@
   summarise(Count=n(), Max = max(Grade), Min = min(Grade), Attempts= max(Attempt))
-
 ```
@@
 ```{r, eval = FALSE}
-
 capstone_finish_year <- inner_join(passed_capstone_grades, d_students) 
-
 head(capstone_finish_year)
-
 count_before <- passed_capstone_grades %>%
@@
   summarise(counts_of_id= n())
-
 count_after <- capstone_finish_year %>%
@@
   filter(counts_of_id > 1)  #these students have repeated capstones.
-
 count_after
@@
 to_remove <- to_remove[duplicated(to_remove$ID),]
-
 capstone_finish_year <- capstone_finish_year%>%
@@
   mutate(`After Graduation`=`Capstone Year`-`Year`)
-
 d_transcripts
@@
   filter(`After Graduation`<0)
-
 d_transcripts <- d_transcripts %>%
   anti_join(master_courses)
-
 head(d_transcripts)
-
 ```
@@
                                                  Grade>5.5~"Completed with Success"))
-
 clean_transcripts <- d_transcripts %>% 
@@
 ```{r, eval = FALSE}
-
 a_clean_transcripts <- clean_transcripts%>%

### 2019-01-11 Data Preparation.Rmd
Course Data text

@@
 ## Setup
-Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis.
-The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`.
-In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
+First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
+` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
+Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively).
+We also any imported emtpy cells.
 ```{r import list}
@@
 ##Course Data
+The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
+
 ### AoD
@@
   select(Code, AoD) %>%
-  unique
+  distinct
 print(d_AoD_ILO)
@@
 `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
+Thus, the first step is to import this matrix:
 
@@
 
-Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
+Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
 ```{r d_AoD_assessment distinct}
@@
 #### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
+Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
 ```{r rbind d_AoD_ILO and d_AoD_assessment}
@@
 ### Removing Stopwords
+
 ```{r}

### 2019-01-11 Data Preparation.Rmd
change title

@@
 # Variable Engineering
-##Course Data
+##Program Data
 The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.

### 2019-01-11 Data Preparation.Rmd
comments on stemming

@@
 We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
+
 We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`).
-We then apply `stem_hunspell` on the words of `d_overview_tidy`.
-Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews.
-Then, we apply the function `stem_hunspell` on this list.
-We save the terms and their stems in the tibble `stems`.
-Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
+We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`.
+However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals.
+Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
 ```{r stemming dictionary, cache = TRUE}
@@
 ```
-
+Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.
+Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
 ```{r stemming data sets}

### 2019-01-11 Data Preparation.Rmd
removing stopwords comments

@@
 ```
+
 ### Removing Stopwords
-
+Finally, we want to filter out some uninformative words from our textual data.
+For this, we first store all the unwanted words in a vector `sw_owm`.
+We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`.
+Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
 ```{r}

### 2019-01-11 Data Preparation.Rmd
computing and plotting tf-idf

--- 2019-01-11 Data Preparation.Rmd
@@
 library(hunspell) # Stemmer
-#library(rlist)
 ```
@@
 ## Setup
-First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
-` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
-Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively).
-We also any imported emtpy cells.
+Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis.
+The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`.
+In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
 ```{r import list}
@@
 # Variable Engineering
-##Program Data
-The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
-
+##Course Data
 ### AoD
@@
   select(Code, AoD) %>%
-  distinct
+  unique
 print(d_AoD_ILO)
@@
 `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-Thus, the first step is to import this matrix:
 
@@
 
-Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
+Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
 ```{r d_AoD_assessment distinct}
@@
 #### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
+Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
 ```{r rbind d_AoD_ILO and d_AoD_assessment}
@@
 ### Removing Stopwords
-
 ```{r}

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
computing and plotting tf-idf

@@
 library(ggthemes)
+library(rlang)
 ```
@@
 ```{r function make_barplot and make_WC, out.height=8, out.width=16}
-make_barplot <- function(data, facet, n_col = 5){
+plot_tf_idf <- function(data, facet, top = 10, n_col = 5){
 
-  facet <- enquo(facet)
+  facet_enquo <- enquo(facet)
+  facet_quo <- quo(!!facet_enquo)
+
+  facet_ensym <- ensym(facet)
+
+  return(facet_ensym == sym("Cluster"))
+
+}
+
+plot_tf_idf(d_course, facet = Cluster)
+
+  data <- data %>% 
+    filter(n >= 2) %>%
+    group_by(Code) %>%
+    top_n(10, tf_idf) %>%
+    ungroup
+
+  data <- if(facet = quo(Course)) filter(data, Code %in% sample(unique(.$Code), size = n_col^2, replace = F))
+          else if(facet = quo(Cluster)) left_join(data, select(d_course, Code, Cluster), by = "Code")
 
@@
   ggsave(paste(facet[2], "_BP.jpeg", sep = ""), path = "Plots")
-  return(g)
+  print(g)
 
@@
   bind_tf_idf(term = word, document = Code, n = n) %>%
-  filter(n >= 2) %>%
-  group_by(Code) %>%
-  top_n(10, tf_idf) %>%
-  ungroup %>%
-  filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) # select 25 courses at random
 

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
Plot tf-idf

--- 2019-01-10 Pillar 2 - Topic Modeling.Rmd
@@
     toc: TRUE
+    fig_heigt: 8
+    fig_width: 16
 ---
@@
 ## Functions for Generating Barplots and Word Clouds
+
+```{r}
+compute_tf_idf <- function(data) data %>%
+                                   count(Code, word) %>%
+                                   bind_tf_idf(term = word, document = Code, n = n)
+
+tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
+tf_idf_overview <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
+tf_idf_manual <- compute_tf_idf(d_manual)
+```
+
 ```{r function make_barplot and make_WC, out.height=8, out.width=16}
-make_barplot <- function(data, facet, n_col = 5){
+plot_tf_idf <- function(data, facet = Course, top = 10, n_col = 5, plot_id = NULL){
 
-  facet <- enquo(facet)
+  # Setup
+  facet_enquo <- enquo(facet)
+  facet_ensym <- ensym(facet)
 
+  # Data
+
+  data <- 
+    if(facet_ensym == sym("Course")) data %>%
+      filter(Code %in% sample(unique(.$Code), size = n_col^2, replace = F)) %>% # random selection of courses
+      rename(facet = Code) %>%
+      group_by(facet) %>%
+      filter(n >= 2) %>%
+      top_n(top, tf_idf) %>%
+      ungroup
+
+    else if(facet_ensym == sym("Cluster")) data %>%
+      left_join(data, select(d_course, Code, Cluster), by = "Code") %>%
+      rename(facet = !!facet_enquo) %>%
+      group_by(facet) %>%
+      summarise(tf_idf = sum(tf_idf))
+      filter(n >= 10) %>%
+      top_n(top, tf_idf) %>%
+      ungroup
+
+      return(data)
+
+  # Barplot
   g <- data %>%
-    rename(facet = !!facet) %>%
     ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
@@
 
-  ggsave(paste(facet[2], "_BP.jpeg", sep = ""), path = "Plots")
-  return(g)
+    ggsave(paste(plot_id, facet_ensym, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+    print(g)
 
-}
-
-make_WC <- function(data, facet, n_col = 5){
-
-  facet <- enquo(facet)
-
+  # Word Cloud
   g <- data %>%
-    rename(facet = !!facet) %>%
     group_by(facet) %>%
     mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
-    ungroup() %>%
-    mutate(angle = 10 * sample(-2:2, n(), replace = T, prob = c(1,1,4,1,1))) %>%
-
-    ggplot(aes(size = freq^0.7, label = word, 
-               angle = angle, color = freq^0.7)) +
+    ggplot(aes(size = freq^0.7, label = word, color = freq^0.7)) +
     geom_text_wordcloud_area(area_corr_power = 1,
@@
 
-  ggsave(paste(facet[2], "_WC.jpeg", sep = ""), path = "Plots")
-  return(g)
+  ggsave(paste(plot_id, facet_ensym, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  print(g)
+
 }
@@
 ## Course Level
-```{r tf-idf per course}
-tdm_top <- d_overview_stem %>%
-  filter(`Calendar Year` == "2018-2019") %>%
-  count(Code, `Calendar Year`, word, sort = T) %>%
-  bind_tf_idf(term = word, document = Code, n = n) %>%
-  filter(n >= 2) %>%
-  group_by(Code) %>%
-  top_n(10, tf_idf) %>%
-  ungroup %>%
-  filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) # select 25 courses at random
-
-make_barplot(data = tdm_top, facet = Code)
-make_WC(data = tdm_top, facet = Code)
+```{r tf-idf per course, out.height=8, out.width=16}
+set.seed(123)
+plot_tf_idf(tf_idf_description, plot_id = "description_")
+set.seed(123)
+plot_tf_idf(tf_idf_overview, plot_id = "overview_")
+set.seed(123)
+plot_tf_idf(tf_idf_manual, plot_id = "manual_")
 ```
@@
 ```{r tf-idf per cluster}
+
 tdm_top <- d_overview_stem %>%

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
functions prepare_tf_idf_

@@
 ```{r function make_barplot and make_WC, out.height=8, out.width=16}
-plot_tf_idf <- function(data, facet = Course, top = 10, n_col = 5, plot_id = NULL){
-
-  # Setup
-  facet_enquo <- enquo(facet)
-  facet_ensym <- ensym(facet)
-
-  # Data
-
-  data <- 
-    if(facet_ensym == sym("Course")) data %>%
-      filter(Code %in% sample(unique(.$Code), size = n_col^2, replace = F)) %>% # random selection of courses
-      rename(facet = Code) %>%
-      group_by(facet) %>%
-      filter(n >= 2) %>%
-      top_n(top, tf_idf) %>%
-      ungroup
-
-    else if(facet_ensym == sym("Cluster")) data %>%
-      left_join(data, select(d_course, Code, Cluster), by = "Code") %>%
-      rename(facet = !!facet_enquo) %>%
-      group_by(facet) %>%
-      summarise(tf_idf = sum(tf_idf))
-      filter(n >= 10) %>%
-      top_n(top, tf_idf) %>%
-      ungroup
-
-      return(data)
+plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){
 
@@
 
-    ggsave(paste(plot_id, facet_ensym, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(plot_id, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
   print(g)
@@
 
-  ggsave(paste(plot_id, facet_ensym, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(plot_id, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
   print(g)
@@
 ```{r tf-idf per course, out.height=8, out.width=16}
+prepare_tf_idf_course <- function(data) data %>%
+                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
+                                          rename(facet = Code) %>%
+                                          group_by(facet) %>%
+                                          filter(n >= 2) %>%
+                                          top_n(10, tf_idf) %>%
+                                          ungroup
+
 set.seed(123)
-plot_tf_idf(tf_idf_description, plot_id = "description_")
+tf_idf_description %>%
+  prepare_tf_idf_course %>%
+  plot_tf_idf(plot_id = "Course_description")
+
 set.seed(123)
-plot_tf_idf(tf_idf_overview, plot_id = "overview_")
+tf_idf_overview %>%
+  prepare_tf_idf_course %>%
+  plot_tf_idf(plot_id = "Course_overview")
+
 set.seed(123)
-plot_tf_idf(tf_idf_manual, plot_id = "manual_")
+tf_idf_manual %>%
+  prepare_tf_idf_course %>%
+  plot_tf_idf(plot_id = "Course_manual")
 ```
@@
 ```{r tf-idf per cluster}
-
-tdm_top <- d_overview_stem %>%
+prepare_tf_idf_cluster <- function(data) data %>%
                                            left_join(select(d_course, Code, Cluster), by = "Code") %>%
-  filter(`Calendar Year` == "2018-2019",
-         !is.na(Cluster)) %>%
-  count(Cluster, `Calendar Year`, word, sort = T) %>%
-  bind_tf_idf(term = word, document = Cluster, n = n) %>%
-  filter(n >= 5) %>%
-  group_by(Cluster) %>%
+                                           filter(!is.na(Cluster)) %>%
+                                           rename(facet = Cluster) %>%
+                                           group_by(facet, word) %>%
+                                             summarise(tf_idf = sum(tf_idf),
+                                                       n = sum(n)) %>%
+                                             filter(n >= 10) %>%
                                              top_n(10, tf_idf) %>%
@@
 
-# Plots
-make_barplot(data = tdm_top, facet = Cluster, n_col = 4)
-make_WC(data = tdm_top, facet = Cluster, n_col = 4)
+tf_idf_description %>%
+  prepare_tf_idf_cluster %>%
+  plot_tf_idf(plot_id = "Cluster_description")
+
+tf_idf_overview %>%
+  prepare_tf_idf_cluster %>%
+  plot_tf_idf(plot_id = "Cluster_overview")
+
+tf_idf_manual %>%
+  prepare_tf_idf_cluster %>%
+  plot_tf_idf(plot_id = "Cluster_manual")
 ```

### 2019-01-11 Data Preparation.Rmd
specifies types of columns

--- 2019-01-11 Data Preparation.Rmd
@@
 ```{r import d_transcript, cache = TRUE}
-d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
-                      read_csv("Raw Grades/grades2.csv", col_types = cols()))
+d_transcript <- rbind(
+  read_csv("Raw Grades/grades1.csv", 
+           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(),`End Date` = col_character()
+                              )
+           ),
+  read_csv("Raw Grades/grades2.csv", 
+           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(), `End Date` = col_character()
+           )
+           )
+  )
 ```

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
minor changes

@@
 # Setup
-```{r}
+```{r load data}
 load("data_pillar_2.RDATA")
@@
 
-```{r}
+```{r compute_tf_idf}
 compute_tf_idf <- function(data) data %>%
@@
 
-```{r function make_barplot and make_WC, out.height=8, out.width=16}
+```{r plot_tf_idf}
 plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){
@@
 ## Course Level
-```{r tf-idf per course, out.height=8, out.width=16}
+```{r tf-idf course, out.height=8, out.width=16}
 prepare_tf_idf_course <- function(data) data %>%
@@
 ## Concentration Level
-```{r tf-idf per concentration}
-tdm_top <- d_overview_stem %>%
-  left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
-  gather(key = "key", value = Concentration,
-         c("Concentration", "Concentration (additional)"),
-         na.rm = T) %>%
-  filter(`Calendar Year` == "2018-2019") %>%
-  count(Concentration, `Calendar Year`, word, sort = T) %>%
-  bind_tf_idf(term = word, document = Concentration, n = n) %>%
-  filter(n >= 5) %>%
-  group_by(Concentration) %>%
-  top_n(10, tf_idf) %>%
-  ungroup
-
-# Plots
-make_barplot(data = tdm_top, facet = Concentration)
-make_WC(data = tdm_top, facet = Concentration)
-```
 
 # LDA
-
+hist
 ## Fitting Model
 ```{r}
-d_overview_cast <- d_overview_stem %>%
+d_overview_cast <- d_overview %>%
   count(Code, word, sort = T) %>%
@@
 ```{r}
-LDA_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
-LDA_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
-LDA_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
+LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
+LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
+LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
 ```

### 2019-01-14 Data Preparation.Rmd
clean code

@@
 ```{r import d_course d_assessment and d_ILO, cache = TRUE}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
-  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
+d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848')
 print(d_course)
+
 d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
@@
 print(d_assessment)
+
 d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
@@
 d_transcript <- rbind(
-  read_csv("Raw Grades/grades1.csv", 
-           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(),`End Date` = col_character()
+  read_csv(
+    "Raw Grades/grades1.csv",
+    col_types = cols(
+      `Program (Abbreviation)` = col_character(),
+      `Appraisal Status` = col_character(),
+      `Module Booking Reason (Description)` = col_character(),
+      `Object name` = col_character(),
+      `Start date` = col_character(),
+      `End Date` = col_character()
       )
     ),
-  read_csv("Raw Grades/grades2.csv", 
-           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(), `End Date` = col_character()
+  read_csv(
+    "Raw Grades/grades2.csv",
+    col_types = cols(
+      `Program (Abbreviation)` = col_character(),
+      `Appraisal Status` = col_character(), 
+      `Module Booking Reason (Description)` = col_character(), 
+      `Object name` = col_character(), 
+      `Start date` = col_character(), 
+      `End Date` = col_character()
       )
@@
 d_AoD_ILO <- d_ILO %>%
-  select(Code, AoD) %>%
-  distinct
+  distinct(Code, AoD)
 print(d_AoD_ILO)
@@
 d_AoD_assessment <- d_AoD_assessment %>%
-  select(Code, AoD) %>%
-  distinct
+  distinct(Code, AoD)
 print(d_AoD_assessment)
@@
 d_ILO_detail <- d_ILO %>% 
-  select(Code, ILO) %>%
-  distinct() %>%
+  distinct(Code, ILO) %>%
   count(Code) %>%
   rename(n_ILO = n)
+
 d_assessment_detail <- d_assessment %>%
@@
             `Assessments Covered` = paste(Assessment, collapse = ", "))
+
 d_AoD_detail <- d_AoD %>%
@@
             `AoD Covered` = paste(AoD, collapse = ", "))
+
 d_course_detail <- d_ILO_detail %>%
@@
   full_join(d_AoD_detail       , by = "Code")
+
 rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
@@
 ```{r join d_course_detail}
-d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
-  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
+d_course <- d_course %>%
+  full_join(d_course_detail, by = "Code") %>%
+  select(Code, `Course Title`, Cluster,
+         n_ILO,
+         n_assessment, `Assessments Covered`,
+         n_AoD, `AoD Covered`, 
+         everything())
+
 rm(d_course_detail)
@@
   mutate(
-    `Missing from ILO File` = as.logical(`Missing from ILO File`),
     Letters = substring(Code, 1, 3),
@@
                         between(Number, 3000, 3999) ~ "Advanced"    ))
+
 print(select(d_course, Code, Letters, Number, Level))
@@
 
-##Textual Data
+## Textual Data
 
@@
 
-####Course Catalogues
+#### Extractin Text: Course Catalogues
 (For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
@@
 
-#### Course Manuals
-#####Extracting Full Text
+#### Extracting Text: Course Manuals
 (For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))

### 2019-01-14 Pillar 1 - Sequential Pattern Mining.Rmd
adds arules code

@@
 library(tidyverse)
+library(arules)
 ```
@@
 ```
+
+#Getting dates
+For a first exploration of arules, we conceptualise our framework like this:
+
+transaction = student
+item = course
+
+```{r}
+t_transactions <- d_transcript %>%
+  select(`Student ID Number`, `Course Code`) %>%
+  transmute(transaction = paste(`Student ID Number`, `Course Code`)) %>%
+  summarise(transactions = paste(transaction, collapse = "\n"))
+
+write(t_transactions$transactions, file = "demo_single")
+tr <- read.transactions("demo_single", format = "single", cols = c(1,2))
+#inspect(tr)
+
+results <- apriori(
+  data = tr, 
+  parameter = list(
+    supp = 0.21,
+    smax = 0.5, # max support
+    conf = 0.51,
+    minlen = 2,
+    maxlen = 2
+    ),
+  appearance = NULL,
+  control = NULL
+  ) %>%
+  inspect
+
+colnames(results)[2] <- "association"
+
+results %>%
+  arrange(confidence)
+
+summary(rules)
+inspect(head(rules, n = length(rules[1])))

### 2019-01-14 Data Preparation.Rmd
simplify code for extracting overviews

@@
                         Overview        = character(0))
+
 course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
   paste(collapse = "|")
-content_to_exclude <- c("^Core Courses \\(COR\\)",
+
+content_to_exclude <- c(
+  "^Core Courses \\(COR\\)",
   "^Humanities \\(HUM\\)",
@@
   "^Social Sciences \\(SSC\\)",
-                        "^Skills Trainings \\(SKI\\)",
-                        "^Projects \\(PRO\\)",
+  "^Skills Trainings \\(SKI\\)", "^Skills Training \\(SKI\\)",
+  "^Project \\(PRO\\)", "^Projects \\(PRO\\)",
   "^Undergraduate Research \\(UGR\\)",
-                        "Appendix") %>%
+  " UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research"
+  ) %>%
   paste(collapse = "|")
-# Loop
+
+# Loop 1
 for(n in 1 : n_catalogue){
@@
 
-  pages_to_exclude     <- grep(pattern = content_to_exclude, x = cat)
-  first_three_letters  <- substr(cat, start = 1, stop = 3)
+  # Overview section in catalogue
+  page_overview_start <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
+  page_overview_end   <- grep(pattern = "Appendix", x = cat) - 1
+    if(length(page_overview_end) == 0) page_overview_end <- length(cat)
+  cat_overview <- cat[page_overview_start : page_overview_end]
+
+  # Course description only
+  pages_to_exclude <- grep(pattern = content_to_exclude, x = cat_overview)
+  cat_overview <- cat_overview[! 1 : length(cat_overview) %in% pages_to_exclude]
+
+  # First pages of course overviews
+  first_three_letters <- substr(cat_overview, start = 1, stop = 3)
   first_pages_overview <- grep(pattern = course_code, x = first_three_letters)
 
-  page_start_loop <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
-  page_end_loop   <- length(cat)
+  # Loop 2
+  for(page in first_pages_overview){
 
-  for(page in page_start_loop : page_end_loop){
+    # Extract description
+    overview <- if(page + 1 %in% first_pages_overview) cat_overview[page]
+                else paste(cat_overview[page : (page + 1)], collapese = " ")
 
-    current_page           <- page
-    following_page         <- page + 1
-    current_page_content   <- cat[page          ]
-    following_page_content <- cat[following_page]
-
-    if(current_page %in% first_pages_overview){
-
-      if(following_page %in% c(first_pages_overview, pages_to_exclude)) course_overview <- current_page_content
-      else course_overview <- paste(current_page_content, following_page_content)
-      # Save Overview
-      Code <- substring(course_overview, first = 1, last = 7)      
+    # Save overview
+    Code <- substr(overview, start = 1, stop = 7)
     year <- calendar_years[n]
-      d_description <- add_row(d_description,
+    d_description <- d_description %>%
+      add_row(
         Code = Code,
         `Calendar Year` = year,
-                               Overview        = course_overview)
-    } # close if-statement
+        Overview = overview
+      )
+
   } # close for-loop (page)
+
 } # close for-loop (n)
+
 rm(corpus_catalogues,
    n_catalogue, calendar_years, course_code, content_to_exclude,
-   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
-   page, current_page, following_page, current_page_content, following_page_content,
-   course_overview, Code, year)
+   n, cat,
+   page_overview_start, page_overview_end,
+   pages_to_exclude, cat_overview,
+   first_three_letters, first_pages_overview,
+   page, overview, Code, year)
 print(d_description)

### 2019-01-14 Data Preparation.Rmd
bug when extracting overview fixed

@@
 # Variable Engineering
-##Program Data
+## Program Data
 The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
@@
                         `Calendar Year` = character(0),
-                        Overview        = character(0))
+                        Overview        = character(0),
+                        Description     = NA)
 
@@
     # Extract description
-    overview <- if(page + 1 %in% first_pages_overview) cat_overview[page]
-                else paste(cat_overview[page : (page + 1)], collapese = " ")
+    overview <- if((page + 1) %in% first_pages_overview) cat_overview[page]
+                else paste(cat_overview[page : (page + 1)], collapse = " ")
 
@@
         `Calendar Year` = year,
-        Overview = overview
+        Overview = overview,
+        Description = NA
       )
@@
 ```{r extracting description, cache = TRUE}
+
 # Setup
@@
   paste(collapse = "|")
-d_description <- d_description %>%
-  mutate(Description = NA)
+
 # Loop
@@
 
-Separately, we want to add the manual textual information to`d_course`which contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
-```{r join manuals to d_course}
-d_course <- full_join(d_course, d_manual, by = "Code")
-```
-
 ### Tidy Text Format
@@
   unnest_tokens(output = word, input = Overview)
+
 d_description <- d_description %>%
@@
   unnest_tokens(output = word, input = Description)
+
 d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
@@
 ### Stemming
-We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
+We then use the function `hunspell_stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
 
-We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`).
+We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`).
 We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`.
@@
 }
+
 dictionary <- select(d_overview, Code, word) %>%
@@
 Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.
+
 Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
@@
 d_manual <- stem_with_dictionary(d_manual)
-rm(stems, stem_hunspell, stem_with_dictionary)
+rm(stem_hunspell, stem_with_dictionary)
 print(d_overview) # See humanities - humanity

### 2019-01-14 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-01-10 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
+
+#Getting dates
+For a first exploration of arules, we conceptualise our framework like this:
+transaction = student
+item = course
+
+##Data preparation
+First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
+
+```{r}
+d_transactions <- d_course %>%
+  select(Type, Code, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(Code) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  select(`Student ID Number`, Code) %>%
+  group_by(`Student ID Number`) %>%
+  summarize(list_course = list(Code)) %>%
+  group_by()
+
+transactions <- as(d_transactions$list_course, "transactions")
+```
+
+We apply Apriori algorithm:
+```{r}
+results <- apriori(
+  data = transactions, 
+  parameter = list(
+    supp = 0.02,
+    smax = 1, # max support
+    conf = 0.4,
+    minlen = 2,
+    maxlen = 2
+    ),
+  appearance = NULL,
+  control = NULL
+  ) %>%
+  inspect
+
+colnames(results)[2] <- "association"
+
+results %>%
+  arrange(desc(confidence))
+```
+
+```{r}
+d_transcript %>% filter(`Course Code`=="SSC3016")
+```
+
+Now we include data for pass and fail
+
+```{r}
+d_transactions <- d_course %>%
+  select(Type, Code, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(Code) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  select(`Student ID Number`, Code) %>%
+  group_by(`Student ID Number`) %>%
+  summarize(list_course = list(Code)) %>%
+  group_by()
+
+transactions <- as(d_transactions$list_course, "transactions")
+```

### 2019-01-14 Pillar 1 - Sequential Pattern Mining.Rmd
adding pass fail to apriori

@@
 ```{r}
-d_transactions <- d_course %>%
+d_transaction_passed <- d_course %>%
   select(Type, Code, Letters) %>%
@@
   left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  select(`Student ID Number`, Code) %>%
+  mutate(Outcome = case_when(Grade > 5.5 ~"Pass",
+                             T~"Fail")) %>%
+  mutate(Item= paste(Code, Outcome, sep = "_")) %>%
+  select(`Student ID Number`, Item) %>%
   group_by(`Student ID Number`) %>%
-  summarize(list_course = list(Code)) %>%
+  summarize(list_course = list(Item)) %>%
   group_by()
 
-transactions <- as(d_transactions$list_course, "transactions")
+transactions_passed <- as(d_transaction_passed$list_course, "transactions")
+
 ```
+We apply Apriori algorithm:
+```{r}
+results_passed <- apriori(
+  data = transactions_passed, 
+  parameter = list(
+    supp = 0,
+    smax = 1, # max support
+    conf = 0.4,
+    minlen = 2,
+    maxlen = 2
+    ),
+  appearance = NULL,
+  control = NULL
+  ) %>%
+  inspect
+
+colnames(results_passed)[2] <- "association"
+
+results_passed %>%
+  separate(lhs, into = c("LHS", "LHS_pass"), sep= "_", remove = F) %>%
+  separate(rhs, into = c("RHS", "RHS_pass"), sep= "_", remove = F) %>%
+  filter(RHS_pass == "Fail}") %>%
+  arrange(desc(count))
+```

### 2019-01-14 Data Preparation.Rmd

@@
 rm(stem_hunspell, stem_with_dictionary)
-print(d_overview) # See humanities - humanity
+print(d_description) # See starting - start
 ```
@@
 d_manual <- remove_sw(d_manual)
+
 rm(sw_own, remove_sw)
+print(d_description) # stop words (on, the, of, etc, are excluded)
 ```

### 2019-01-15 Pillar 1 - Sequential Pattern Mining.Rmd
adds arulesSequence code, data is already as transactions but cspade doesnt run because of some (strict order) requirement

@@
 library(arules)
+library(arulesSequences)
 ```
@@
 ```
+#Mining-sequences
+Let I = {I1, I2,..., Ip} be the set of all items.
+An itemset is a nonempty set of items.
+A sequence is an ordered list of events.
+A sequence s is denoted <e1e2e3 ···el>, where event e1 occurs before e2, which occurs before e3, and so on.
+Event ej is also called an element of s.
+In the case of customer purchase data, an event refers to a shopping trip in which a customer bought items at a certain store.
+The event is thus an itemset, that is, an unordered list of items that the customer purchased during the trip.
+The itemset (or event) is denoted (x1x2 ···xq), where xk is an item.
+For brevity, the brackets are omitted if an element has only one item, that is, element (x) is written as x.
+
+SequenceID = `Student ID Number`
+Event ID   =  UCM_YEAR_Period OR Year_period. 
+Items      =  Course
+```{r}
+d_sequence_transactions <- d_course %>%
+  select(Type, Code, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(Code) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+  mutate(Time= paste(`Civil Year`,Period, sep="")) %>%
+  select(Code,`Student ID Number`, Time) %>%
+  group_by(`Student ID Number`, Time) %>%
+  arrange(Time,`Student ID Number`) #%>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+  #summarize(list_course = list(Code)) %>%
+  #group_by()   #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
+
+sequence_transcript_data <- data.frame(item=d_sequence_transactions$Code)
+
+transcripts.tran <- as(sequence_transcript_data, "transactions")
+
+ transactionInfo(transcripts.tran)$sequenceID <- d_sequence_transactions$`Student ID Number`
+
+ transactionInfo(transcripts.tran)$eventID <- d_sequence_transactions$Time
+
+inspect(head(transcripts.tran))
+
+```
+now we find frequent sequential patterns
+```{r}
+frequent_trajectories <- cspade(transcripts.tran, parameter = list(support = 0.50))
+```
+
+#Visualisation
+It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful.
+We might need to sample.
+See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/

### 2019-01-15 Data Preparation.Rmd
debug data prep

@@
 We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
-
 ## Setup
@@
 ## Textual Data
-
 ### Course Catalogues
@@
 ## Textual Data
-
 ### Extracting Text
@@
   rbind(d_manual) %>% 
-  select(word) %>%
-  distinct %>%
+  distinct(word) %>%
   mutate(word_stem = purrr::map_chr(.x = word,
                                     .f = stem_hunspell))
+
 # terms for which the stem differs from the original word
@@
 d_manual <- stem_with_dictionary(d_manual)
+
 rm(stem_hunspell, stem_with_dictionary)
@@
 sw_own <- c("______________________________________________________________________________")
+
 remove_sw <- function(data) data %>%
   filter(! word %in% c(stop_words$word, sw_own))
+
 d_description <- remove_sw(d_description)
@@
 
-##Student Data
+## Student Data
 (In this section we use: `d_transcript`- contains the transcript information of students as was provided.
@@
 
-###Selecting Variables
+### Selecting Variables
 

### 2019-01-15 Pillar 2 - Topic Modeling.Rmd
include rm()

@@
 
-```{r compute_tf_idf}
+```{r compute_tf_idf, cache = TRUE}
 compute_tf_idf <- function(data) data %>%
@@
 tf_idf_manual      <- compute_tf_idf(d_manual)
+
+rm(compute_tf_idf())
 ```
@@
   plot_tf_idf(plot_id = "Course_manual")
+
+rm(prepare_tf_idf_course)
 ```
@@
 ## Cluster Level
-```{r tf-idf per cluster}
+```{r tf-idf per cluster, cache = TRUE}
 prepare_tf_idf_cluster <- function(data) data %>%
@@
   plot_tf_idf(plot_id = "Cluster_manual")
+
+rm(prepare_tf_idf_cluster)
 ```
@@
 ## Concentration Level
+```{r, cache = TRUE}
+prepare_tf_idf_concentration <- function(data) data %>%
+                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
+                                                 filter(!is.na(Concentration)) %>%
+                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+                                                 rename(facet = Concentration) %>%
+                                                 group_by(facet, word) %>%
+                                                   summarise(tf_idf = sum(tf_idf),
+                                                             n = sum(n)) %>%
+                                                   filter(n >= 10) %>%
+                                                   top_n(10, tf_idf) %>%
+                                                 ungroup
+
+tf_idf_description %>%
+  prepare_tf_idf_concentration %>%
+  plot_tf_idf(plot_id = "Concentration_description")
+
+tf_idf_overview %>%
+  prepare_tf_idf_concentration %>%
+  plot_tf_idf(plot_id = "Concentration_overview")
+
+tf_idf_manual %>%
+  prepare_tf_idf_concentration %>%
+  plot_tf_idf(plot_id = "Concentration_manual")
+
+rm(prepare_tf_idf_concentration, plot_tf_idf,
+   tf_idf_description, tf_idf_overview, tf_idf_manual)
+```
 
 # LDA
-hist
 ## Fitting Model
-```{r}
+```{r, eval = FALSE}
 d_overview_cast <- d_overview %>%
@@
 
-```{r}
+```{r, eval = FALSE}
 LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))

### 2019-01-16 Data Preparation.Rmd
adds additional filter and calenar year variable to transcripts

--- 2019-01-14 Data Preparation.Rmd
@@
 d_transcript <- d_transcript %>%
-  filter(`Appraisal (Description)` == "Grade supervisor") %>%
+  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
   select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
@@
          `Study Program` = `Program (Description)`,
-         `Civil Year` = `Academic Year`, # double check
+         `Year_numerical` = `Academic Year`, # double check
          `Period` = `Academic Session`,
@@
 We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R.
-Vos) and save it under a variable `Period`:
+Vos) and save it under a variable `Period`.
+We also create another variable:
 ```{r}
@@
                             between(Period, 600, 660) ~ "6",
-                            between(Period, 901, 999) ~ "1"))
+                            between(Period, 901, 999) ~ "1")) %>%
+  mutate(`Calendar Year`= paste(Year_numerical,Year_numerical+1, sep = "-"))
 ```

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
LDA on description, overview and manual

@@
     toc: TRUE
-    fig_heigt: 8
-    fig_width: 16
 ---
@@
 
-rm(compute_tf_idf())
+rm(compute_tf_idf)
 ```
@@
 ## Cluster Level
-```{r tf-idf per cluster, cache = TRUE}
+```{r tf-idf cluster, cache = TRUE}
 prepare_tf_idf_cluster <- function(data) data %>%
@@
 ## Concentration Level
-```{r, cache = TRUE}
+```{r tf-idf concentration, cache = TRUE}
 prepare_tf_idf_concentration <- function(data) data %>%
@@
 ## Fitting Model
-```{r, eval = FALSE}
-d_overview_cast <- d_overview %>%
-  count(Code, word, sort = T) %>%
-  cast_dtm(Code,word, n)
+```{r}
+my_cast_tdm <- function(data, level) data %>%
+  count(Code, word) %>%
+  cast_dtm(Code, word, n)
+
+d_description_cast <- my_cast_tdm(d_description)
+d_overview_cast <- my_cast_tdm(d_overview)
+d_manual_cast <- my_cast_tdm(d_manual)
 ```
@@
 ```{r, eval = FALSE}
-LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
-LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
-LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
+LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
+LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
+LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))
+
+LDA_overview_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
+LDA_overview_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
+LDA_overview_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
+
+LDA_manual_10 <- LDA(d_manual_cast, k = 10, control = list(seed = 123))
+LDA_manual_17 <- LDA(d_manual_cast, k = 17, control = list(seed = 123))
+LDA_manual_25 <- LDA(d_manual_cast, k = 25, control = list(seed = 123))
 ```

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
function to view LDA

@@
 ```{r plot_tf_idf}
-plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){
+plot_tf_idf <- function(data, n_col = 5, plot_id = NULL){
 
@@
 ## Fitting Model
-```{r}
+```{r my_cast_tdm}
 my_cast_tdm <- function(data, level) data %>%
@@
 d_manual_cast <- my_cast_tdm(d_manual)
+
+rm(my_cast_tdm)
 ```
@@
 
-  # Setup
-  topic_letter <- tibble(topic_number = 1:26,
-                         topic_letter = c(topic_names,
-                                          paste("Topic", LETTERS[(length(topic_names)+1) : 26])))
-
-  # Beta Distribution: term-topic
-  term_topic <- tidy(results, matrix = "beta") %>%
-    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
-    mutate(topic = topic_letter) %>%
-    select(-topic_letter)
-
-  term_topic %>%
+  # Beta distribution
+  tidy(LDA_description_10, matrix = "beta") %>%
+    mutate(topic = paste("Topic", topic)) %>%
     group_by(topic) %>%
@@
     ungroup %>%
+
   ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
@@
 
-  # Gamma Distribution: document-topic
-  doc_topic <- tidy(results, matrix = "gamma") %>%
-    left_join(topic_letter, by = c("topic" = "topic_number")) %>%
-    mutate(topic = topic_letter,
-           facet = document) %>%
-    select(-c(topic_letter, document))
+  # Gamma Distribution
+  data_gamma <- tidy(LDA_description_10, matrix = "gamma") %>%
+    mutate(topic = paste("Topic", topic)) %>%
+    rename(Code = document) %>%
+    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")
 
-  if(facet) doc_topic <- separate(doc_topic, facet, c("document", "facet"), sep = "_") %>%
-    add_count(facet) %>%
+  if(ensym(facet) == sym("Course")) data_gamma <- data_gamma %>%
+                                      rename(facet = Code)
+
+  if(ensym(facet) == sym("Cluster")) data_gamma <- data_gamma %>%
+                                       filter(is.na(Cluster)) %>%
+                                       rename(facet = Cluster)
+
+  if(ensym(facet) == sym("Concentration")) data_gamma <- data_gamma %>% 
+                                             filter(!is.na(Concentration)) %>%
+                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+                                             rename(facet = Concentration)
+
+  # Gamma Distribution: plot 1 docu-topic
+  data_gamma %>%
     group_by(facet, topic) %>%
-    summarise(gamma = sum(gamma)) %>%
-    ungroup
-
-  # Plot 1
-  doc_topic %>%
+      summarise(gamma = sum(gamma))
     filter(gamma > 0.05) %>%

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
functions to prepare and visualize output of LDA

@@
 ## Results
-
-```{r function visualize_LDA, eval = F}
-visualize_LDA <- function(results, id_plot = "test", facet = F, topic_names = NULL){
-
-  # Beta distribution
-  tidy(LDA_description_10, matrix = "beta") %>%
+```{r}
+prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
                                         mutate(topic = paste("Topic", topic)) %>%
@@
                                             top_n(10, beta) %>%
-    ungroup %>%
+                                          ungroup
 
-  ggplot(aes(x = reorder_within(term, by = beta, within = topic), y = beta, fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, scales = "free") +
-    scale_x_reordered() +
-    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
-    coord_flip() +
-    theme_light() +
-    theme(plot.title = element_text(hjust = 0.5))
+prepare_data_LDA_gamma <- function(results, facet = Course){
 
-  ggsave(paste(id_plot, "beta.jpeg"),
-         width = 15, height = 10, path = "Plots")
-
-  # Gamma Distribution
-  data_gamma <- tidy(LDA_description_10, matrix = "gamma") %>%
+  data_gamma <- tidy(results, matrix = "gamma") %>%
     mutate(topic = paste("Topic", topic)) %>%
@@
 
-  # Gamma Distribution: plot 1 docu-topic
-  data_gamma %>%
+  data_gamma <- data_gamma %>%
     group_by(facet, topic) %>%
-      summarise(gamma = sum(gamma))
-    filter(gamma > 0.05) %>%
-    ggplot(aes(reorder_within(facet, by = gamma, within = topic), y = gamma, fill = facet)) +
+      summarise(gamma = mean(gamma)) %>%
+    filter(gamma > 0.05)
+    ungroup
+
+}
+```
+
+```{r function visualize_LDA, eval = F}
+visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
+
+  data_prepared %>%
+  ggplot(aes(x = reorder_within(term,
+                                by = beta,
+                                within = topic),
+             y = beta,
+             fill = topic)) +
     geom_col(show.legend = F) +
-    facet_rep_wrap(~ topic, scales = "free",
-                   repeat.tick.labels = "bottom") +
+    facet_wrap(~ topic, scales = "free") +
+    scale_x_reordered() +
+    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
+    coord_flip() +
+    theme_light() +
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggsave(paste(id_plot, "beta.jpeg"),
+         width = 15, height = 10, path = "Plots")
+
+}
+
+visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){
+
+  data_prepared %>%
+    ggplot(aes(reorder_within(facet, 
+                              by = gamma, 
+                              within = topic), 
+               y = gamma, 
+               fill = facet)) +
+    geom_col(show.legend = F) +
+    facet_wrap(~ topic, 
+               scales = "free") +
     scale_x_reordered() +
     coord_flip() +
-    labs(x = "(Group of) Courses", y = "Gamma", title = "Main Courses/Clusters of each Topic") +
+   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
     theme_light() +
@@
 
-  # Plot 2
-  doc_topic %>%
-    filter(gamma > 0.05) %>%
-    ggplot(aes(reorder_within(topic, by = gamma, within = facet), y = gamma, fill = topic)) +
+}
+
+visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){???
+
+  data_prepared %>%
+    ggplot(aes(reorder_within(topic, 
+                              by = gamma,
+                              within = facet), 
+               y = gamma, 
+               fill = topic)) +
     geom_col(show.legend = F) +
-    facet_rep_wrap(~ facet, scales = "free",
-                   repeat.tick.labels = "bottom") +
+    facet_wrap(~ facet, 
+               scales = "free") +
     scale_x_reordered() +
     coord_flip() +
-    labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
+  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
     theme_light() +
@@
 }
+
 ```

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
funciton to prepare LDA reuslts for visualization

@@
 ## Results
-```{r}
+```{r LDA prepare}
 prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
@@
                                             top_n(10, beta) %>%
-                                          ungroup
+                                          ungroup %>%
+                                          arrange(topic, desc(beta))
 
-prepare_data_LDA_gamma <- function(results, facet = Course){
+prepare_data_LDA_gamma <- function(results, level = Course){
 
@@
     mutate(topic = paste("Topic", topic)) %>%
-    rename(Code = document) %>%
-    left_join(select(d_course, Code, Cluster, Concentration, `Concentration (additional)`), by = "Code")
+    rename(Code = document)
 
-  if(ensym(facet) == sym("Course")) data_gamma <- data_gamma %>%
+  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                       rename(facet = Code)
 
-  if(ensym(facet) == sym("Cluster")) data_gamma <- data_gamma %>%
-                                       filter(is.na(Cluster)) %>%
+  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
+                                       left_join(select(d_course, Code, Cluster), by = "Code") %>%
+                                       filter(!is.na(Cluster)) %>%
                                        rename(facet = Cluster)
 
-  if(ensym(facet) == sym("Concentration")) data_gamma <- data_gamma %>% 
-                                             filter(!is.na(Concentration)) %>%
+  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
+                                             left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                              gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
@@
       summarise(gamma = mean(gamma)) %>%
-    filter(gamma > 0.05)
-    ungroup
+    filter(gamma > 0.05) %>%
+    ungroup %>%
+    arrange(facet, desc(gamma))
+
+  return(data_gamma)
 
 }
+
+# Bet Distribution
+LDA_description_10 %>% prepare_data_LDA_beta
+
+# Gamma Distribution
+LDA_description_10 %>% prepare_data_LDA_gamma(level = Cluster)
 ```
 
-```{r function visualize_LDA, eval = F}
+```{r LDA visualize}
 visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
@@
 
-visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){???
+visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){
 
@@
 }
-
 ```

### 2019-01-16 Pillar 1 - Sequential Pattern Mining.Rmd
puts transcript data into transaction format

@@
 ```{r library, message = F}
+#detach(package:tm, unload=TRUE) #there is overlap with tm package in inspect()
+
 library(tidyverse)
@@
   filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-  mutate(Time= paste(`Civil Year`,Period, sep="")) %>%
-  select(Code,`Student ID Number`, Time) %>%
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+  select(`Student ID Number`, Code, Time) %>%
+  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
   group_by(`Student ID Number`, Time) %>%
-  arrange(Time,`Student ID Number`) #%>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  #summarize(list_course = list(Code)) %>%
-  #group_by()   #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
+  summarize(list_course = list(Code)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
+  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
 
-sequence_transcript_data <- data.frame(item=d_sequence_transactions$Code)
+list_course <- d_sequence_transactions$list_course
+names(list_course) <- d_sequence_transactions$TransactionID
 
-transcripts.tran <- as(sequence_transcript_data, "transactions")
-
- transactionInfo(transcripts.tran)$sequenceID <- d_sequence_transactions$`Student ID Number`
-
- transactionInfo(transcripts.tran)$eventID <- d_sequence_transactions$Time
-
-inspect(head(transcripts.tran))
+my_transactions <- as(list_course, "transactions")
+transactionInfo(my_transactions)$sequenceID <- d_sequence_transactions$`Student ID Number`
+transactionInfo(my_transactions)$eventID <- d_sequence_transactions$Time
+transactionInfo(my_transactions)$transactionID <- NULL
 
 ```
-now we find frequent sequential patterns
+
+now we find frequent sequential patterns. 
+The parameter values are: 
+support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
+
+maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
+maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
+mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
+maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
+maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
 ```{r}
-frequent_trajectories <- cspade(transcripts.tran, parameter = list(support = 0.50))
+frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
+summary(frequent_trajectories)
+as(frequent_trajectories, "data.frame")
+
+inspect(head(frequent_trajectories))
+
 ```

### 2019-01-16 Pillar 2 - Topic Modeling.Rmd
functions to visualize LDA output

@@
 ```{r plot_tf_idf}
-plot_tf_idf <- function(data, n_col = 5, plot_id = NULL){
+plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){
 
@@
 
-  ggsave(paste(plot_id, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
   print(g)
@@
 
-  ggsave(paste(plot_id, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
   print(g)
@@
   prepare_tf_idf_course %>%
-  plot_tf_idf(plot_id = "Course_description")
+  plot_tf_idf(id_plot = "Course_description")
 
@@
   prepare_tf_idf_course %>%
-  plot_tf_idf(plot_id = "Course_overview")
+  plot_tf_idf(id_plot = "Course_overview")
 
@@
   prepare_tf_idf_course %>%
-  plot_tf_idf(plot_id = "Course_manual")
+  plot_tf_idf(id_plot = "Course_manual")
 
@@
   prepare_tf_idf_cluster %>%
-  plot_tf_idf(plot_id = "Cluster_description")
+  plot_tf_idf(id_plot = "Cluster_description")
 
@@
   prepare_tf_idf_cluster %>%
-  plot_tf_idf(plot_id = "Cluster_overview")
+  plot_tf_idf(id_plot = "Cluster_overview")
 
@@
   prepare_tf_idf_cluster %>%
-  plot_tf_idf(plot_id = "Cluster_manual")
+  plot_tf_idf(id_plot = "Cluster_manual")
 
@@
   prepare_tf_idf_concentration %>%
-  plot_tf_idf(plot_id = "Concentration_description")
+  plot_tf_idf(id_plot = "Concentration_description")
 
@@
   prepare_tf_idf_concentration %>%
-  plot_tf_idf(plot_id = "Concentration_overview")
+  plot_tf_idf(id_plot = "Concentration_overview")
 
@@
   prepare_tf_idf_concentration %>%
-  plot_tf_idf(plot_id = "Concentration_manual")
+  plot_tf_idf(id_plot = "Concentration_manual")
 
@@
 
-```{r, eval = FALSE}
+```{r, cache = TRUE}
 LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
@@
 
+```{r}
+# Bet Distribution
+LDA_description_10 %>%
+  prepare_data_LDA_beta %>%
+  visualize_LDA_beta
+
+# Gamma Distribution 1
+LDA_description_10 %>%
+  prepare_data_LDA_gamma(level = Cluster) %>%
+  visualize_LDA_gamma1
+
+# Gamma Distribution 2
+LDA_description_10 %>%
+  prepare_data_LDA_gamma(level = Cluster) %>%
+  visualize_LDA_gamma2
+```
+
+```{r}
+visualize_LDA <- function(data, level = Course, id_plot = "test"){
+
+  # Beta distribution
+  data %>% 
+    prepare_data_LDA_beta %>%
+    visualize_LDA_beta(id_plot = id_plot)
+
+  # Gamma 1 distribution
+  data %>% 
+    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
+    visualize_LDA_gamma1(id_plot = id_plot)
+
+  # Gamma 2 distribution
+  data %>% 
+    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
+    visualize_LDA_gamma2(id_plot = id_plot)
+
+}
+```
+
 ```{r visualization LDA, eval = F}
-visualize_LDA(LDA_SCI_2 , id_plot = "SCI, k = 2" )
-visualize_LDA(LDA_SCI_5 , id_plot = "SCI, k = 5" )
-visualize_LDA(LDA_SCI_10, id_plot = "SCI, k = 10")
-
-visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10", facet = T)
-visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17", facet = T)
-visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25", facet = T)
 

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd
rule induction for courses

@@
 ```{r}
+summary(my_transactions)
+
 frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
+#Looking into this: 
 summary(frequent_trajectories)
@@
 
+```{r}
+rules <- ruleInduction(frequent_trajectories, confidence = 0.2, #we need to play with the parameters.
+                    control    = list(verbose = TRUE))
+as(rules, "data.frame") %>%
+  arrange(desc(lift))
+```
+
 #Visualisation

### 2019-01-17 Pillar 2 - Topic Modeling.Rmd

@@
 ## Course Level
-```{r tf-idf course, out.height=8, out.width=16}
+```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
 prepare_tf_idf_course <- function(data) data %>%
@@
     group_by(facet, topic) %>%
-      summarise(gamma = mean(gamma)) %>%
+      summarise(gamma = sum(gamma)) %>%
     filter(gamma > 0.05) %>%
@@
 
-```{r}
+```{r, cache = TRUE}
 # Bet Distribution
@@
 
+```{r}
+visualize_LDA_all_level <- function(data, id_plot = "test"){
+
+  data %>% 
+    visualize_LDA(level = Course,
+                  id_plot = paste(id_plot, "_course"))
+
+  data %>% 
+    visualize_LDA(level = Cluster,
+                  id_plot = paste(id_plot, "_cluster"))
+
+  data %>% 
+    visualize_LDA(level = Concentration,
+                  id_plot = paste(id_plot, "_concentration"))
+
+}
+```
+
+```{r, cache = TRUE}
+LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
+LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
+LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")
+
+LDA_overview_10 %>% visualize_LDA_all_level(id_plot = "overview_k10")
+LDA_overview_17 %>% visualize_LDA_all_level(id_plot = "overview_k17")
+LDA_overview_25 %>% visualize_LDA_all_level(id_plot = "overview_k25")
+
+LDA_manual_10 %>% visualize_LDA_all_level(id_plot = "manual_k10")
+LDA_manual_17 %>% visualize_LDA_all_level(id_plot = "manual_k17")
+LDA_manual_25 %>% visualize_LDA_all_level(id_plot = "manual_k25")
+```
+
 ```{r visualization LDA, eval = F}

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 Now we include data for pass and fail
-
 ```{r}
@@
   left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  mutate(Outcome = case_when(Grade > 5.5 ~"Pass",
+  mutate(Outcome = case_when(Grade=="NG"~"Fail",
+                             Grade > 5.5 ~"Pass",
                              T~"Fail")) %>%
@@
 ```
+#Sequence mining with pass fail.
+First we add pass fai information to our data set and transform it to transactions class:
+```{r}
+#sequences
+d_pass_sequence_transactions <- d_course %>%
+  select(Type, Code, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(Code) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  mutate(Outcome = 
+           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade > 5.5 ~"Pass",
+                              T~"Fail")
+         ) %>%
+  mutate(Item = paste(Code, Outcome, sep = "_") ) %>%
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+  select(`Student ID Number`, Item, Time) %>%
+  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+  group_by(`Student ID Number`, Time) %>%
+  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
+  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
+
+pass_list_course <- d_pass_sequence_transactions$list_course
+names(pass_list_course) <- d_pass_sequence_transactions$TransactionID
+
+pass_transactions <- as(pass_list_course, "transactions")
+transactionInfo(pass_transactions)$sequenceID <- d_pass_sequence_transactions$`Student ID Number`
+transactionInfo(pass_transactions)$eventID <- d_pass_sequence_transactions$Time
+transactionInfo(pass_transactions)$transactionID <- NULL
+```
+Checking the results:
+```{r}
+as(pass_transactions, "data.frame")
+frequent_pass_trajectories <- cspade(pass_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
+summary(frequent_pass_trajectories)
+
+pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.2, #we need to play with the parameters.
+                    control    = list(verbose = TRUE))
+pass_rules_df <- as(pass_rules, "data.frame") %>%
+  arrange(desc(lift))
+```
+Checking who failed
+```{r}
+pass_rules_df %>%
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = F) %>%
+  filter(str_detect(RHS, "_Fail"))
+```
 

### 2019-01-17 Data Preparation.Rmd

@@
 We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
+
 ## Setup
@@
   select(- `Comment on Assessment`) %>%
-  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
-  mutate(assessment_covered = as.logical(assessment_covered)) %>%
-  filter(assessment_covered) %>%
+  gather(Assessment, assessment_covered, - `Course ID`, factor_key = T) %>%
+  filter(assessment_covered == 1) %>%
   select(- assessment_covered) %>%
-  arrange(Code)
+  arrange(`Course ID`)
 print(d_assessment)
@@
   select(- c(Comments, Comments_for_Jeroen)) %>%
-  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
-  mutate(AoD_covered = as.logical(AoD_covered)) %>%
+  gather(AoD, AoD_covered, -c(`Course ID`, Objectives), factor_key = T) %>%
+  filter(AoD_covered == 1) %>%
+  select(- AoD_covered) %>%
   rename(ILO = Objectives) %>%
-  filter(AoD_covered) %>%
-  select(- AoD_covered) %>%
-  arrange(Code)
+  arrange(`Course ID`)
 print(d_ILO)
@@
 ```{r d_AoD_ILO}
-d_AoD_ILO <- d_ILO %>%
-  distinct(Code, AoD)
+d_AoD_ILO <- distinct(d_ILO, `Course ID`, AoD)
 print(d_AoD_ILO)
@@
 rownames(map_assessment_AoD) <- lists$Assessment
+
+# Print section of matrix
 print(map_assessment_AoD[1:5, 8:12])
@@
 ```{r d_AoD_assessment}
-d_AoD_assessment <- tibble(Code        = character(0),
+d_AoD_assessment <- tibble(`Course ID` = character(0),
                            Assessment  = character(0),
                            AoD         = character(0))
+
 for(i in 1 : nrow(d_assessment)){
@@
 ```{r d_AoD_assessment distinct}
-d_AoD_assessment <- d_AoD_assessment %>%
-  distinct(Code, AoD)
+d_AoD_assessment <- distinct(d_AoD_assessment, `Course ID`, AoD)
 print(d_AoD_assessment)
@@
   distinct %>%
-  arrange(Code)
+  arrange(`Course ID`)
+
 rm(d_AoD_ILO, d_AoD_assessment)
@@
 d_ILO_detail <- d_ILO %>% 
-  distinct(Code, ILO) %>%
-  count(Code) %>%
+  distinct(`Course ID`, ILO) %>%
+  count(`Course ID`) %>%
   rename(n_ILO = n)
@@
 d_assessment_detail <- d_assessment %>%
-  group_by(Code) %>%
+  group_by(`Course ID`) %>%
   summarise(n_assessment = n(),
@@
 d_AoD_detail <- d_AoD %>%
-  group_by(Code) %>%
+  group_by(`Course ID`) %>%
   summarise(n_AoD = n(),
@@
 d_course_detail <- d_ILO_detail %>%
-  full_join(d_assessment_detail, by = "Code") %>%
-  full_join(d_AoD_detail       , by = "Code")
+  full_join(d_assessment_detail, by = "Course ID") %>%
+  full_join(d_AoD_detail       , by = "Course ID")
 
@@
 d_course <- d_course %>%
-  full_join(d_course_detail, by = "Code") %>%
-  select(Code, `Course Title`, Cluster,
+  full_join(d_course_detail, by = "Course ID") %>%
+  select(`Course ID`, `Course Title`, Cluster,
          n_ILO,
@@
 d_course <- d_course %>%
-  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
-                                  Code == "UGR3002" ~ "UGR2002",
-                                  Code == "UGR3003" ~ "UGR2003",
-                                  Code == "UGR3005" ~ "UGR2005")))
-print(filter(d_course, Code %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
+  rbind(filter(., `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
+          mutate(`Course ID` = case_when(`Course ID` == "UGR3001" ~ "UGR2001",
+                                  `Course ID` == "UGR3002" ~ "UGR2002",
+                                  `Course ID` == "UGR3003" ~ "UGR2003",
+                                  `Course ID` == "UGR3005" ~ "UGR2005")))
+
+print(filter(d_course, `Course ID` %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
                                           "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
@@
   mutate(
-    Letters = substring(Code, 1, 3),
-    Number  = as.numeric(substring(Code, 4, 7)),
+    Letters = substring(`Course ID`, 1, 3),
+    Number  = as.numeric(substring(`Course ID`, 4, 7)),
     Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
@@
 
-print(select(d_course, Code, Letters, Number, Level))
+print(select(d_course, `Course ID`, Letters, Number, Level))
 ```
@@
 n_catalogue <- length(corpus_catalogues)
-calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
-d_description <- tibble(Code            = character(0),
-                        `Calendar Year` = character(0),
+academic_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
+d_description <- tibble(`Course ID`     = character(0),
+                        `Academic Year` = character(0),
                         Overview        = character(0),
@@
     # Save overview
-    Code <- substr(overview, start = 1, stop = 7)
-    year <- calendar_years[n]
+    code <- substr(overview, start = 1, stop = 7)
+    year <- academic_years[n]
     d_description <- d_description %>%
       add_row(
-        Code = Code,
-        `Calendar Year` = year,
+        `Course ID` = code,
+        `Academic Year` = year,
         Overview = overview,
@@
 rm(corpus_catalogues,
-   n_catalogue, calendar_years, course_code, content_to_exclude,
+   n_catalogue, academic_years, course_code, content_to_exclude,
    n, cat,
@@
    first_three_letters, first_pages_overview,
-   page, overview, Code, year)
+   page, overview, code, year)
 print(d_description)
@@
     line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
-    print(paste("line_end irregular for", d_description$Code[course],
+    print(paste("line_end irregular for", d_description$`Course ID`[course],
                 "in catalogue", d_description$`Calendar Year`[course]))
@@
   select(id, text) %>%
-  mutate(Code = substring(id, 1, 7)) %>%
+  mutate(`Course ID` = substring(id, 1, 7)) %>%
   select(-id) %>%
   rename(Manual = text)
+
 rm(corpus_manuals)
@@
 d_overview <- d_description %>%
-  select(Code, `Calendar Year`, Overview) %>%
+  select(`Course ID`, `Academic Year`, Overview) %>%
   unnest_tokens(output = word, input = Overview)
@@
 d_description <- d_description %>%
-  select(Code, `Calendar Year`, Description) %>%
+  select(`Course ID`, `Academic Year`, Description) %>%
   unnest_tokens(output = word, input = Description)
@@
 
-dictionary <- select(d_overview, Code, word) %>%
+dictionary <- select(d_overview, `Course ID`, word) %>%
   rbind(d_manual) %>% 
@@
   filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
-  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
-         `Program (Description)`, `Academic Year`, `Academic Session`,
-         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
-  rename(`Student ID Number` = `Student Number`,
-         `Course Code` = `Module (Abbrev.)`,
+  select(`Student Number`,
+         `Module (Abbrev.)`,
+         `Module (Desc.)`,
+         `Program (Description)`,
+         `Academic Year`,
+         `Academic Session`,
+         `Number rep. attemp`,
+         `Grade symbol`,
+         `Booking Status (Desc.)`) %>%
+  rename(`Student ID` = `Student Number`,
+         `Course ID` = `Module (Abbrev.)`,
          `Course Title` = `Module (Desc.)`,
          `Study Program` = `Program (Description)`,
-         `Year_numerical` = `Academic Year`, # double check
-         `Period` = `Academic Session`,
+         Year_numerical = `Academic Year`, # double check
+         Period = `Academic Session`,
          `Number Repeated Attempt` = `Number rep. attemp`,
          Grade = `Grade symbol`,
-         `Status` = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
+         Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
+#  mutate(as.POSIXct('2/5/2010',format='%m/%d/%Y')) %>%
   distinct
@@
                             between(Period, 901, 999) ~ "1")) %>%
-  mutate(`Calendar Year`= paste(Year_numerical,Year_numerical+1, sep = "-"))
+  mutate(`Academic Year`= paste(Year_numerical, Year_numerical + 1, sep = "-"))
 ```
 
-##Estimating concentrations:
+## DO LATER (Estimating concentrations)
 For our analysis we would also like to know what the concentration of each student is.

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 # Setup
+load previous data and create function to find courses
 ```{r}
 load("data_pillar_1.RDATA")
+
+find_course <- function(data = d_transcript, code){
+  c = code
+  x <- data %>%
+    filter(`Course Code`== c)
+
+  return(x$`Course Title`[1])
+}
+
 ```
@@
 ```
-
-```{r}
-d_transcript %>% filter(`Course Code`=="SSC3016")
-```
-
-Now we include data for pass and fail
+Now we include data for pass and fail:
 ```{r}
@@
 #sequences
+fail_threshold <- 6.5
+
 d_pass_sequence_transactions <- d_course %>%
@@
                       Grade > 5.5 ~"Pass",
-                              T~"Fail")
+                              T~"Fail"),
+         Low_grade =
+           case_when(Grade=="NG"~"Sad", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"OK",
+                              T~"Sad")
          ) %>%
-  mutate(Item = paste(Code, Outcome, sep = "_") ) %>%
+  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
   filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
@@
 
-pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.2, #we need to play with the parameters.
+pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.1, #we need to play with the parameters.
                     control    = list(verbose = TRUE))
@@
 pass_rules_df %>%
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = F) %>%
-  filter(str_detect(RHS, "_Fail"))
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove= F to keep columns
+  filter(str_detect(RHS, "_Sad")) %>%
+  arrange(desc(confidence), desc(lift))
 ```

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd
low_grade high_grade threshold + evgueni file

@@
 
+```
+#Data Exploration of Transcripts
+```{r}
+exploration <- d_transcript %>%
+  mutate(Grade = case_when(Grade == "NG"~ "0.0",
+                           T~Grade),
+         Grade=as.double(Grade))
 ```
@@
          Low_grade =
-           case_when(Grade=="NG"~"Sad", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"OK",
-                              T~"Sad")
+           case_when(Grade=="NG"~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                              T~"low score")
          ) %>%
@@
 ```{r}
-pass_rules_df %>%
+view_rules <- pass_rules_df %>%
   separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove= F to keep columns
-  filter(str_detect(RHS, "_Sad")) %>%
+  filter(str_detect(RHS, "low score")) %>% #change so that it changes automatically
   arrange(desc(confidence), desc(lift))
+
+write_csv(view_rules, "Data_Evgueni.csv")
 ```

### 2019-01-17 Pillar 2 - Topic Modeling.Rmd

@@
 compute_tf_idf <- function(data) data %>%
-                                   count(Code, word) %>%
-                                   bind_tf_idf(term = word, document = Code, n = n)
+                                   count(`Course ID`, word) %>%
+                                   bind_tf_idf(term = word, document = `Course ID`, n = n)
 
-tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
-tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
+tf_idf_description <- compute_tf_idf(filter(d_description, `Academic Year` == "2018-2019"))
+tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Academic Year` == "2018-2019"))
 tf_idf_manual      <- compute_tf_idf(d_manual)
@@
   ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
-  print(g)
 
@@
   ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
-  print(g)
 
@@
 prepare_tf_idf_course <- function(data) data %>%
-                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
-                                          rename(facet = Code) %>%
+                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
+                                          rename(facet = `Course ID`) %>%
                                           group_by(facet) %>%
@@
 prepare_tf_idf_cluster <- function(data) data %>%
-                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
+                                           left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                            filter(!is.na(Cluster)) %>%
@@
 prepare_tf_idf_concentration <- function(data) data %>%
-                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
+                                                 left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                                  filter(!is.na(Concentration)) %>%
@@
 my_cast_tdm <- function(data, level) data %>%
-  count(Code, word) %>%
-  cast_dtm(Code, word, n)
+  count(`Course ID`, word) %>%
+  cast_dtm(`Course ID`, word, n)
 
@@
 ```{r LDA prepare}
-prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
+prepare_data_LDA_beta <- function(results){
+
+  tidy(results, matrix = "beta") %>%
     mutate(topic = paste("Topic", topic)) %>%
@@
 
+}
+
 prepare_data_LDA_gamma <- function(results, level = Course){
@@
     mutate(topic = paste("Topic", topic)) %>%
-    rename(Code = document)
+    rename(`Course ID` = document)
 
   if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
-                                      rename(facet = Code)
+                                      rename(facet = `Course ID`)
 
   if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
-                                       left_join(select(d_course, Code, Cluster), by = "Code") %>%
+                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                        filter(!is.na(Cluster)) %>%
@@
   if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
-                                             left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
+                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                              gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%

### 2019-01-18 Data Preparation.Rmd
Keeping UCM courses only

@@
          `Module (Desc.)`,
-         `Program (Description)`,
+         `Program (Abbreviation)`,
          `Academic Year`,
@@
          `Course Title` = `Module (Desc.)`,
-         `Study Program` = `Program (Description)`,
+         `Study Program` = `Program (Abbreviation)`,
          Year_numerical = `Academic Year`, # double check
@@
          Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
-#  mutate(as.POSIXct('2/5/2010',format='%m/%d/%Y')) %>%
   distinct
@@
   mutate(`Academic Year`= paste(Year_numerical, Year_numerical + 1, sep = "-"))
+```
+
+### Keeping UCM program only
+
+```{r}
+d_transcript <- d_transcript %>%
+  filter(`Study Program` == "7501") %>%
+  select(- `Study Program`)
 ```

### 2019-01-18 Data Preparation.Rmd
minor changes to d_transcript

@@
 d_transcript <- d_transcript %>%
+  # only keep one observation (with the final grade) per student-course
   filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
@@
          `Program (Abbreviation)`,
+         `Grade symbol`,
          `Academic Year`,
          `Academic Session`,
-         `Number rep. attemp`,
-         `Grade symbol`,
-         `Booking Status (Desc.)`) %>%
+         `Number rep. attemp`) %>%
   rename(`Student ID` = `Student Number`,
@@
          `Course Title` = `Module (Desc.)`,
+         Grade = `Grade symbol`,
          `Study Program` = `Program (Abbreviation)`,
-         Year_numerical = `Academic Year`, # double check
+         Year_numerical = `Academic Year`,
          Period = `Academic Session`,
-         `Number Repeated Attempt` = `Number rep. attemp`,
-         Grade = `Grade symbol`,
-         Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
+         `Number Repeated Attempt` = `Number rep. attemp`) %>%
   distinct
@@
 
+```{r}
+print(d_transcript)
+```
+
 ## DO LATER (Estimating concentrations)
@@
 Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"
-
-NOTE TO RAPHAEL: we might want o have your course concentrations because they take double concentrations into account!
 

### 2019-01-18 Data Preparation.Rmd
minor changes to d_transcript

@@
 d_transcript <- d_transcript %>%
-  # only keep one observation (with the final grade) per student-course
   filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%

### 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 
-find_course <- function(data = d_transcript, code){
+find_course <- function(code){ #can be modified to accept other data that is not d_transcript
   c = code
-  x <- data %>%
+  x <- d_transcript %>%
     filter(`Course Code`== c)
@@
 ```
+
 #Data Exploration of Transcripts
@@
 exploration <- d_transcript %>%
-  mutate(Grade = case_when(Grade == "NG"~ "0.0",
+  mutate(Grade = case_when(Grade == "NG"~ "-1", #"0,0", #maybe we could just remove these from the analysis and treat them separately?
                            T~Grade),
-         Grade=as.double(Grade))
+         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
+         Grade = as.numeric(Grade))%>%
+  filter(!is.na(Grade)) %>%
+  filter(Grade != -1) #remove NG
+
+summary(exploration)
+
+student_statistics <- exploration %>%
+  group_by(`Student ID Number`) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = mean(Grade), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5))
+
+course_statistics <- exploration %>%
+  group_by(`Course Code`) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = mean(Grade), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5)) %>%
+  inner_join(d_course, by= c("Course Code" = "Code")) #to get only UCM courses for which we have statistics
+
+#We have NA in grades. Something weird is happening. 
+summary(str_detect(d_transcript$Grade, pattern="NA")) #shows NA's = 312 FALSE= 89069 WHY ARE THERE NAs?
+
+has_na <- d_transcript %>%
+  mutate(What = str_detect(Grade, pattern="NA")) %>%
+  filter(is.na(What))
+```
+We have found some NA values for the grades! Students:
+0177849- COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
+0177857
+0222100
+0270148
+0313173
+0317101
+0317349
+
+#Getting graphics
+```{r}
+
 ```
@@
 view_rules <- pass_rules_df %>%
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove= F to keep columns
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
   filter(str_detect(RHS, "low score")) %>% #change so that it changes automatically
@@
 
+#Unifying transaction data
+```{r}
+fail_threshold <- 6.5
+
+category <-"Low_grade" #Outcome or Low_grade
+
+d_pass_sequence_transactions <- d_course %>%
+  select(Type, Code, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(Code) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  mutate(Outcome = 
+           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade > 5.5 ~"Pass",
+                              T~"Fail"),
+         Low_grade =
+           case_when(Grade=="NG"~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                              T~"low score")
+         ) %>%
+  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+  select(`Student ID Number`, Item, Time) %>%
+  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+  group_by(`Student ID Number`, Time) %>%
+  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
+  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
+```
+
 #Visualisation

### 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd
statistics -student, course, concentration, cluster

@@
 library(arulesSequences)
+
+library(rlang)
 ```
@@
 student_statistics <- exploration %>%
-  group_by(`Student ID Number`) %>%
+  group_by(`Student ID`) %>%
   summarise(n = n(),
@@
 course_statistics <- exploration %>%
-  group_by(`Course Code`) %>%
+  group_by(`Course ID`) %>%
   summarise(n = n(),
@@
             Max = max(Grade), 
-            Mean = mean(Grade), 
+            Mean = round(mean(Grade), 2), 
             Median = median(Grade), 
@@
             `Proportion Failed` = mean(Grade < 5.5)) %>%
-  inner_join(d_course, by= c("Course Code" = "Code")) #to get only UCM courses for which we have statistics
+  right_join(d_course, by = "Course ID")
 
+concentration_statistics <- exploration %>%
+  inner_join(select(d_course,-Period, -`Period (additional)`,-`Period (additional bis)`,-`Course Title`), by = "Course ID") %>%
+  #left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
+  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+  group_by(Concentration) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = round(mean(Grade), 2), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5))
+
+cluster_statistics <- exploration %>%
+  inner_join(d_course, by = "Course ID") %>%
+  group_by(Cluster) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = round(mean(Grade), 2), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5))
+```
+We have found some NA values for the grades! Students:
+
+0177849 - COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
+0177857
+0222100
+0270148
+0313173
+0317101
+0317349
+
+```{r}
 #We have NA in grades. Something weird is happening. 
@@
 ```
-We have found some NA values for the grades! Students:
-0177849- COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
-0177857
-0222100
-0270148
-0313173
-0317101
-0317349
 

### 2019-01-18 Data Preparation.Rmd
place section "save data" before the TODO list
include numbers 1 : 10 as stop words

--- 2019-01-18 Data Preparation.Rmd
@@
 # Own stop words
-sw_own <- c("______________________________________________________________________________")
+sw_own <- c("______________________________________________________________________________",
+            as.character(1:10))
 
@@
 
-## DO LATER (Estimating concentrations)
+# Save Data
+```{r}
+save(lists, d_course, d_AoD, d_assessment, d_transcript,
+     file = "data_pillar_1.RDATA")
+save(lists, d_course, d_AoD, d_assessment, d_transcript,
+     d_overview, d_description, d_manual,
+     file = "data_pillar_2.RDATA")
+```
+
+# TODO
+
+## Estimating concentrations
 For our analysis we would also like to know what the concentration of each student is.
@@
 
-# Save Data
-```{r}
-save(lists, d_course, d_AoD, d_assessment, d_transcript,
-     file = "data_pillar_1.RDATA")
-save(lists, d_course, d_AoD, d_assessment, d_transcript,
-     d_overview, d_description, d_manual,
-     file = "data_pillar_2.RDATA")
-```
-
 [^1]: We do not include all assessments and all AoDs on the plots in order to keep them readable.

### 2019-01-18 Pillar 2 - Topic Modeling.Rmd
minor changes

@@
 # Setup
-```{r load data}
+```{r import data}
 load("data_pillar_2.RDATA")
@@
 
-```{r, cache = TRUE}
+```{r LDA fit, cache = TRUE}
 LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
@@
 
-## Results
+```{r LDA save models}
+save(LDA_description_10, LDA_description_17, LDA_description_25,
+     LDA_overview_10, LDA_overview_17, LDA_overview_25,
+     LDA_manual_10, LDA_manual_17, LDA_manual_25,
+     file = "LDA.RDATA")
+```
+
+## Visualization
+### Functions
 ```{r LDA prepare}
@@
                y = gamma, 
-               fill = facet)) +
+               fill = topic)) +
     geom_col(show.legend = F) +
@@
 
-```{r, cache = TRUE}
-# Bet Distribution
-LDA_description_10 %>%
-  prepare_data_LDA_beta %>%
-  visualize_LDA_beta
-
-# Gamma Distribution 1
-LDA_description_10 %>%
-  prepare_data_LDA_gamma(level = Cluster) %>%
-  visualize_LDA_gamma1
-
-# Gamma Distribution 2
-LDA_description_10 %>%
-  prepare_data_LDA_gamma(level = Cluster) %>%
-  visualize_LDA_gamma2
-```
-
-```{r}
-visualize_LDA <- function(data, level = Course, id_plot = "test"){
+```{r LDA visualize all distrib}
+visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){
 
@@
 
-```{r}
+```{r LDA visualize all level}
 visualize_LDA_all_level <- function(data, id_plot = "test"){
@@
   data %>% 
-    visualize_LDA(level = Course,
+    visualize_LDA_all_distrib(level = Course,
                               id_plot = paste(id_plot, "_course"))
@@
   data %>% 
-    visualize_LDA(level = Cluster,
+    visualize_LDA_all_distrib(level = Cluster,
                               id_plot = paste(id_plot, "_cluster"))
@@
   data %>% 
-    visualize_LDA(level = Concentration,
+    visualize_LDA_all_distrib(level = Concentration,
                               id_plot = paste(id_plot, "_concentration"))
@@
 
-```{r, cache = TRUE}
+### Plots
+```{r LDA plot, cache = TRUE}
 LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
@@
 
-```{r visualization LDA, eval = F}
+```{r label, eval = F}
+tidy(LDA_manual_10, "beta") %>%
+  filter(beta > 1e-3) %>%
+  bind_tf_idf(term = term, document = topic, n = beta) %>%
+  group_by(topic) %>%
+  top_n(10, tf_idf) %>%
+  arrange(topic, desc(tf_idf))
 
+  count(term, topic) %>%
+  arrange(desc(n)) %>%
+
+  filter(beta > 1e-3) %>%
+  group_by(term) %>%
+    mutate(n_topic = n(),
+           beta = beta / n_topic) %>%
+  group_by(topic) %>%
+    top_n(10, beta)
+
+  count(topic, term, wt = beta) %>%
+  (term = term, document = topic, n = n) %>%
+  group_by(topic) %>%
+  top_n(10, tf_idf)
+
+  group_by(term) %>%
+  summarise(beta = sum(beta)) %>%
+  arrange(desc(beta))
+
+labels <- list(
+  description_10 = "X"
+)
+```
+
+```{r label bis, eval = FALSE}
 visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,

### 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 course_statistics <- exploration %>%
+  inner_join(d_course, by = "Course ID") %>%
+  filter(between(Year_numerical, 2015,2016)) %>% #filter year
   group_by(`Course ID`) %>%
@@
             `Proportion Failed` = mean(Grade < 5.5)) %>%
-  right_join(d_course, by = "Course ID")
+  inner_join(select(d_course,`Course ID`, `Course Title`), by = "Course ID")
 
@@
             `Proportion Failed` = mean(Grade < 5.5))
+
+year_statistics <- exploration %>%
+  inner_join(d_course, by = "Course ID") %>%
+  group_by(Year_numerical) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = round(mean(Grade), 2), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5))
+
+level_statistics <- exploration %>%
+  inner_join(d_course, by = "Course ID") %>%
+  group_by(Level) %>%
+  summarise(n = n(),
+            Min = min(Grade), 
+            Max = max(Grade), 
+            Mean = round(mean(Grade), 2), 
+            Median = median(Grade), 
+            SD = sd(Grade), 
+            `Proportion Failed` = mean(Grade < 5.5))
+
+percentage_grades_awarded <- d_transcript %>%
+          mutate(Grade = str_replace(string = Grade, pattern = ",",replace = "."),
+                 Grade = as.integer(Grade)) %>%
+  filter(Year_numerical %in% c(2015,2016))%>%
+  mutate(total=n())%>%
+  group_by(Grade) %>%
+  mutate(grade_total=n())%>%
+  select(Grade, grade_total,total)%>%
+  distinct()%>%
+  mutate(Percentage = signif(grade_total/total,digits=2))%>%
+  arrange(Grade)
+
 ```

### 2019-01-21 Pillar 2 - Topic Modeling.Rmd

@@
 
-  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)
 
@@
 
-  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
+  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)
 
@@
 ## Course Level
-```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
+```{r tf-idf course, cache = TRUE}
 prepare_tf_idf_course <- function(data) data %>%
@@
   ggsave(paste(id_plot, "beta.jpeg"),
-         width = 15, height = 10, path = "Plots")
+         width = 16, height = 10, path = "Plots/Topic Model")
 
@@
   ggsave(paste(id_plot, "gamma1.jpeg"),
-         width = 15, height = 10, path = "Plots")
+         width = 16, height = 10, path = "Plots/Topic Model")
 
@@
   ggsave(paste(id_plot, "gamma2.jpeg"),
-         width = 15, height = 10, path = "Plots")
+         width = 16, height = 10, path = "Plots/Topic Model")
 
@@
 
-```{r label, eval = F}
+```{r label, eval = FALSE}
 tidy(LDA_manual_10, "beta") %>%

### 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd
clean sequences code

@@
 ```
-#Mining-sequences
-Let I = {I1, I2,..., Ip} be the set of all items.
-An itemset is a nonempty set of items.
-A sequence is an ordered list of events.
-A sequence s is denoted <e1e2e3 ···el>, where event e1 occurs before e2, which occurs before e3, and so on.
-Event ej is also called an element of s.
-In the case of customer purchase data, an event refers to a shopping trip in which a customer bought items at a certain store.
-The event is thus an itemset, that is, an unordered list of items that the customer purchased during the trip.
-The itemset (or event) is denoted (x1x2 ···xq), where xk is an item.
-For brevity, the brackets are omitted if an element has only one item, that is, element (x) is written as x.
 
-SequenceID = `Student ID Number`
-Event ID   =  UCM_YEAR_Period OR Year_period. 
-Items      =  Course
-```{r}
-d_sequence_transactions <- d_course %>%
-  select(Type, Code, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(Code) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-  select(`Student ID Number`, Code, Time) %>%
-  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID Number`, Time) %>%
-  summarize(list_course = list(Code)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
-  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
-
-list_course <- d_sequence_transactions$list_course
-names(list_course) <- d_sequence_transactions$TransactionID
-
-my_transactions <- as(list_course, "transactions")
-transactionInfo(my_transactions)$sequenceID <- d_sequence_transactions$`Student ID Number`
-transactionInfo(my_transactions)$eventID <- d_sequence_transactions$Time
-transactionInfo(my_transactions)$transactionID <- NULL
-
-```
-
-now we find frequent sequential patterns. 
+#Mining-sequences:
 The parameter values are: 
@@
 maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
+
+#Preparing data frame:
 ```{r}
-summary(my_transactions)
+fail_threshold <- 6.5
 
-frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
-#Looking into this: 
-summary(frequent_trajectories)
-as(frequent_trajectories, "data.frame")
+category <-quo(Discrete_grade) #Outcome or Low_grade or Discrete_grade or #None
 
-inspect(head(frequent_trajectories))
+d_sequence_transactions <- d_course %>%
+
+  select(Type, `Course ID`, Letters) %>%
+
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+
+  select(`Course ID`) %>%
+
+  left_join(d_transcript, by = "Course ID") %>%
+
+    mutate(
+      Grade = case_when(
+        Grade == "NG"~ "-1",
+        T            ~ Grade),
+      Grade = str_replace(string = Grade, pattern = ",",replace = "."),
+      Grade = as.numeric(Grade)) %>%
+
+  # filter(!is.na(Grade)) %>% #remove NaN
+  # filter(Grade != -1) %>% #remove NG
+  mutate(
+    Outcome = 
+           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade  > 5.5 ~"Pass",
+                               T~"Fail"),
+    Low_grade =
+           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                               T~"low score"),
+    Discrete_grade =
+           case_when(Grade <= 5.4             ~ 5.0,
+                     between(Grade, 5.5, 6.4) ~ 6.0,
+                     between(Grade, 6.5, 7.4) ~ 7.0,
+                     between(Grade, 7.5, 8.4) ~ 8.0,
+                     between(Grade, 8.5, 9.4) ~ 9.0,
+                     Grade >= 9.5             ~ 10.0,
+                     T ~ -99999    #this is a control, we should not have any grades here
+                     ),
+    None= "" # this might not be optimal
+         ) %>%
+
+  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
+
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+
+  select(`Student ID`, Item, Time) %>%
+
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+
+  group_by(`Student ID`, Time) %>%
+
+  summarize(list_course = list(Item)) %>%
+
+  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
 
@@
 
+##to transaction
 ```{r}
-rules <- ruleInduction(frequent_trajectories, confidence = 0.2, #we need to play with the parameters.
+transaction_list_course <- d_sequence_transactions$list_course
+names(transaction_list_course) <- d_sequence_transactions$TransactionID
+
+transactions <- as(transaction_list_course, "transactions")
+transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
+transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
+transactionInfo(transactions)$transactionID <- NULL
+
+#checking results
+as(transactions, "data.frame")
+```
+
+##Rule induction
+```{r}
+#FURTURE: create filter by function
+string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
+                           quo_name(category)=="Low_grade"      ~ "low score",
+                           quo_name(category)=="Discrete_grade" ~ "5",
+                           quo_name(category)=="None"           ~ "_" #useless filter
+                           )
+
+frequent_trajectories <- cspade(transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
+
+summary(frequent_trajectories)
+
+rules <- ruleInduction(frequent_trajectories, confidence = 0.1, #we need to play with the parameters.
                     control    = list(verbose = TRUE))
-as(rules, "data.frame") %>%
-  arrange(desc(lift))
-```
-#Sequence mining with pass fail.
-First we add pass fai information to our data set and transform it to transactions class:
-```{r}
-#sequences
-fail_threshold <- 6.5
 
-d_pass_sequence_transactions <- d_course %>%
-  select(Type, Code, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(Code) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  mutate(Outcome = 
-           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade > 5.5 ~"Pass",
-                              T~"Fail"),
-         Low_grade =
-           case_when(Grade=="NG"~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                              T~"low score")
-         ) %>%
-  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-  select(`Student ID Number`, Item, Time) %>%
-  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID Number`, Time) %>%
-  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
-  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
+pass_rules_df <- as(rules, "data.frame") %>%
 
-pass_list_course <- d_pass_sequence_transactions$list_course
-names(pass_list_course) <- d_pass_sequence_transactions$TransactionID
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
 
-pass_transactions <- as(pass_list_course, "transactions")
-transactionInfo(pass_transactions)$sequenceID <- d_pass_sequence_transactions$`Student ID Number`
-transactionInfo(pass_transactions)$eventID <- d_pass_sequence_transactions$Time
-transactionInfo(pass_transactions)$transactionID <- NULL
-```
-Checking the results:
-```{r}
-as(pass_transactions, "data.frame")
-frequent_pass_trajectories <- cspade(pass_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
-summary(frequent_pass_trajectories)
+  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
 
-pass_rules <- ruleInduction(frequent_pass_trajectories, confidence = 0.1, #we need to play with the parameters.
-                    control    = list(verbose = TRUE))
-pass_rules_df <- as(pass_rules, "data.frame") %>%
-  arrange(desc(lift))
-```
-Checking who failed
-```{r}
-view_rules <- pass_rules_df %>%
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
-  filter(str_detect(RHS, "low score")) %>% #change so that it changes automatically
   arrange(desc(confidence), desc(lift))
 
-write_csv(view_rules, "Data_Evgueni.csv")
+pass_rules_df
+
 ```
-
-#Unifying transaction data
-```{r}
-fail_threshold <- 6.5
-
-category <-"Low_grade" #Outcome or Low_grade
-
-d_pass_sequence_transactions <- d_course %>%
-  select(Type, Code, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(Code) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  mutate(Outcome = 
-           case_when( Grade=="NG"~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade > 5.5 ~"Pass",
-                              T~"Fail"),
-         Low_grade =
-           case_when(Grade=="NG"~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                              T~"low score")
-         ) %>%
-  mutate(Item = paste(Code, Low_grade, sep = "_") ) %>% #Change for Outcome/Low_grade
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-  select(`Student ID Number`, Item, Time) %>%
-  arrange(`Student ID Number`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID Number`, Time) %>%
-  summarize(list_course = list(Item)) %>% #if we run the code until here maybe its possible to use sequence_transactions <- as(sequence_transaction$list_course, "transactions")
-  mutate(TransactionID = paste(`Student ID Number`, Time, sep = "_"))
-```
-
 #Visualisation

### 2019-01-21 Pillar 2 - Topic Modeling.Rmd
delete lines with sofia tuning
Ideal number of topics in LDA

@@
 library(rlang)
+library(ldatuning) # ideal number of topics in LDA
 ```
@@
 # LDA
+
+## Ideal Number of Topic
+
+```{r, eval = FALSE}
+result <- FindTopicsNumber(
+
+  d_description_cast,
+  topics = seq(from = 20, to = 150, by = 5),
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  control = list(seed = 123),
+  mc.cores = 1L,
+  verbose = TRUE
+
+)
+
+FindTopicsNumber_plot(result1)
+save(result,
+     file = "LDA_ntopics.RDATA")
+```
+
 ## Fitting Model

### 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+#checking results
+as(my_transactions, "data.frame")
 ```
@@
 #Sequence mining with pass fail.
-First we add pass fai information to our data set and transform it to transactions class:
+First we add pass fail information to our data set and transform it to transactions class:
 ```{r}

### 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd
all course-student combinations

--- 2019-01-21 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
+
 #Visualisation
@@
 See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/
+
+#Puting students into take and not take.
+
+```{r}
+test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
+  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
+  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
+  mutate(
+    take_course = case_when(
+      is.na(Grade)  ~ FALSE,
+      T             ~ TRUE
+      ),
+    PFN = case_when(
+      is.na(Grade)  ~ "not",
+      Grade >= 5.5  ~ "pass",
+      Grade < 5.5   ~ "fail"
+      )
+    )
+
+table(test$PFN)
+
+```

### 2019-01-22 Pillar 2 - Topic Modeling.Rmd
ideal number of topics in LDA
LDA with 120 topics (ideal number)

@@
 
-## Ideal Number of Topic
+## Ideal Number of Topics
 
-```{r, eval = FALSE}
+```{r LDA number topics, eval = FALSE}
 result <- FindTopicsNumber(
@@
 
-FindTopicsNumber_plot(result1)
 save(result,
      file = "LDA_ntopics.RDATA")
+```
+
+```{r LDA number topics plot}
+load("LDA_ntopics.RDATA")
+FindTopicsNumber_plot(result)
 ```
@@
 ```{r LDA fit, cache = TRUE}
-LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
-LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
-LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))
+n_topics <- 120
+levels   <- c("description", "overview", "manual")
+list_nam <- character(0)
 
-LDA_overview_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
-LDA_overview_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
-LDA_overview_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
+for(level in levels){
 
-LDA_manual_10 <- LDA(d_manual_cast, k = 10, control = list(seed = 123))
-LDA_manual_17 <- LDA(d_manual_cast, k = 17, control = list(seed = 123))
-LDA_manual_25 <- LDA(d_manual_cast, k = 25, control = list(seed = 123))
-```
+  dataset   <- get(paste("d", level, "cast", sep = "_"))
+  LDA_model <- LDA(dataset, k = n_topics, control = list(seed = 123))
+  nam <- paste("LDA", level, n_topics, sep = "_")
 
-```{r LDA save models}
-save(LDA_description_10, LDA_description_17, LDA_description_25,
-     LDA_overview_10, LDA_overview_17, LDA_overview_25,
-     LDA_manual_10, LDA_manual_17, LDA_manual_25,
+  assign(
+    x     = nam,
+    value = LDA_model
+  )
+
+  list_nam <- c(list_nam, nam)
+
+}
+
+save(list = list_nam,
      file = "LDA.RDATA")
@@
 # Bet Distribution
-LDA_description_10 %>% prepare_data_LDA_beta
+LDA_description_120 %>% prepare_data_LDA_beta
 
 # Gamma Distribution
-LDA_description_10 %>% prepare_data_LDA_gamma(level = Cluster)
+LDA_description_120 %>% prepare_data_LDA_gamma(level = Cluster)
 ```
@@
 ```{r LDA plot, cache = TRUE}
-LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
-LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
-LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")
+LDA_description_120 %>% visualize_LDA_all_level(id_plot = "description_k120")
 
-LDA_overview_10 %>% visualize_LDA_all_level(id_plot = "overview_k10")
-LDA_overview_17 %>% visualize_LDA_all_level(id_plot = "overview_k17")
-LDA_overview_25 %>% visualize_LDA_all_level(id_plot = "overview_k25")
+LDA_overview_120 %>% visualize_LDA_all_level(id_plot = "overview_k120")
 
-LDA_manual_10 %>% visualize_LDA_all_level(id_plot = "manual_k10")
-LDA_manual_17 %>% visualize_LDA_all_level(id_plot = "manual_k17")
-LDA_manual_25 %>% visualize_LDA_all_level(id_plot = "manual_k25")
+LDA_manual_120 %>% visualize_LDA_all_level(id_plot = "manual_k120")
 ```

### 2019-01-23 Pillar 1 - Sequential Pattern Mining.Rmd
computes statistics (Conf_corr) and beggins to add plots

@@
 library(rlang)
+
+library(ggplot2)
 ```
@@
 
-#Getting graphics
-```{r}
-
-```
-
 #Getting dates
@@
 
-category <-quo(Discrete_grade) #Outcome or Low_grade or Discrete_grade or #None
+category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
 
@@
 
-    mutate(
-      Grade = case_when(
-        Grade == "NG"~ "-1",
-        T            ~ Grade),
-      Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-      Grade = as.numeric(Grade)) %>%
+    # mutate(
+    #   Grade = case_when(
+    #     Grade == "NG"~ "-1",
+    #     T            ~ Grade),
+    #   Grade = str_replace(string = Grade, pattern = ",",replace = "."),
+    #   Grade = as.numeric(Grade)) %>% #this was already done in data preparation
 
@@
 
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
+frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
+                                                               maxsize = 1,
+                                                               maxlen = 2), control   = list(verbose = TRUE))
 
 summary(frequent_trajectories)
+as(frequent_trajectories, "data.frame")
 
-rules <- ruleInduction(frequent_trajectories, confidence = 0.1, #we need to play with the parameters.
+rules <- ruleInduction(frequent_trajectories,
+                       confidence = 0, #we need to play with the parameters.
                        control    = list(verbose = TRUE))
@@
 
-  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
+#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
 
-  arrange(desc(confidence), desc(lift))
+  arrange(
+    LHS, RHS,
+    desc(confidence), desc(lift))
 
-pass_rules_df
+n_students <- length(unique(d_sequence_transactions$`Student ID`))
+
+manual_confidence_rules <- pass_rules_df %>%
+  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
+  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
+  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>%
+  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
+
+  # Compute statistics
+  group_by(LHS,`RHS Course ID`) %>%
+  mutate(Prob_both = sum(support), 
+         Conf_corr = support/Prob_both,
+         n_rule = support * n_students,
+         n_both =Prob_both * n_students,
+         lift_diff= Conf_corr - Prop_low,
+         lift_corr=Conf_corr / Prop_low) %>%
+  ungroup() %>%
+
+  # Filter and edit output
+  filter(str_detect(`RHS Score`, pattern = "low"),
+         str_detect(`LHS Score`, pattern = "low"),
+         n_rule >= 5,
+         Conf_corr > 0.2) %>%
+  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
+  mutate(support = round(support,3),
+         Prob_both =round(Prob_both,3),
+         Prop_low =round(Prop_low,3),
+         Conf_corr= round(Conf_corr,3),
+         lift_diff= round(lift_diff,3),
+         lift_corr= round(lift_corr,3)) %>%
+  arrange(lift_diff)
+
+#FOR PLOTTING
+for_plots <-  manual_confidence_rules %>%
+  group_by(LHS)%>%
+  mutate(LHS_count=n())
+
+```
+#Visualizing rules
+```{r}
+#look at counts
+ggplot(for_plots, aes(LHS))+
+  geom_bar()
+
+#jitter
+ggplot(manual_confidence_rules)+
+  geom_jitter(mapping=aes(x=Conf_corr, y=log(support), color=lift_corr))
+
+ggplot(manual_confidence_rules)+
+  geom_jitter(mapping=aes(x=log(support), y=lift_corr, color = Conf_corr))
+
+#heatmap
+ggplot(select(manual_confidence_rules,LHS,RHS, n_rule), aes(x=RHS,y=LHS, fill=n_rule))+
+  geom_raster() +
+  theme(
+    axis.text.x = element_text(angle=90)
+  )
+
+gglot(table(select(manual_confidence_rules,LHS,RHS)))
+
+hi <- table(select(manual_confidence_rules,LHS,RHS))
+#ggnetwork
 
@@
 ```
+
+We want to change the calculation of confidence and support. The new rules are:
+confidence: number of transactions of RHS/ number of transactions of RHS and compliment= p(A^B)/P(BUBc)
+support:number of transactions of right hand side/number of transactions of RHS and compliment= p(A^B)/p(AUBUBc)
+lift:
+
+#Experimenting with transactions
+```{r}
+fail_threshold <- 6.5
+
+category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
+
+lookup_table <- d_course %>%
+
+  select(Type, `Course ID`, Letters) %>%
+
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+
+  select(`Course ID`) %>%
+
+  left_join(d_transcript, by = "Course ID") %>%
+  mutate(
+    Outcome = 
+           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade  > 5.5 ~"Pass",
+                               T~"Fail"),
+    Low_grade =
+           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                               T~"low score"),
+    Discrete_grade =
+           case_when(Grade <= 5.4             ~ 5.0,
+                     between(Grade, 5.5, 6.4) ~ 6.0,
+                     between(Grade, 6.5, 7.4) ~ 7.0,
+                     between(Grade, 7.5, 8.4) ~ 8.0,
+                     between(Grade, 8.5, 9.4) ~ 9.0,
+                     Grade >= 9.5             ~ 10.0,
+                     T ~ -99999    #this is a control, we should not have any grades here
+                     ),
+    None= "" # this might not be optimal
+         ) %>%
+
+  #mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
+
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+
+  select(`Student ID`, #Item, 
+         `Course ID`, !!category, Time) %>% # Course ID and Time may not be necessary
+
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+
+  group_by(`Course ID`, !!category) %>% ##this makes no sense we should just group id and low_grade
+
+  summarize(Count = n()) %>%
+  #separate(Item, into= c("Course ID", quo_name(category)), sep="_", remove = F) %>%
+  ungroup() %>%
+  group_by(`Course ID`) %>%
+  mutate(Total= sum(Count))%>%
+  filter(Low_grade=="low score")%>%
+  mutate(Prop_low= Count/Total)
+
+lookup_table
+```
+
+```{r}
+pass_rules_df
+test <- pass_rules_df %>%
+  separate(LHS, into=c("c1","c2", "c3", "c4", "c5", "c6","c7", "c8", "c9", "c10"), sep= ",", remove=F) #has values until c6
+
+```
+
+```{r}
+
+length(unique(d_transcript$`Student ID`))
+```

### 2019-01-23 Pillar 2 - Topic Modeling.Rmd

@@
 ```{r LDA fit, cache = TRUE}
-n_topics <- 120
+n_topics <- 5
 levels   <- c("description", "overview", "manual")
@@
   dataset   <- get(paste("d", level, "cast", sep = "_"))
-  LDA_model <- LDA(dataset, k = n_topics, control = list(seed = 123))
+  LDA_model <- LDA(
+    x = dataset,
+    k = n_topics,
+    method = "Gibbs",
+    control = list(
+      nstart = 10,
+      seed = c(1:10),
+      best = TRUE,
+      burnin = 4000,
+      iter = 2000,
+      thin = 500))
   nam <- paste("LDA", level, n_topics, sep = "_")
@@
 ```{r LDA plot, cache = TRUE}
-LDA_description_120 %>% visualize_LDA_all_level(id_plot = "description_k120")
+load("LDA.RDATA")
 
-LDA_overview_120 %>% visualize_LDA_all_level(id_plot = "overview_k120")
+LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")
 
-LDA_manual_120 %>% visualize_LDA_all_level(id_plot = "manual_k120")
+LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")
+
+LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
 ```

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
cleans code- breaks into smaller section and puts code in correct order

@@
 load previous data and create function to find courses
-```{r}
+```{r loading data}
 load("data_pillar_1.RDATA")
@@
 ```
-
-#Data Exploration of Transcripts
+#Simple Rule Mining
+##Data Exploration of Transcripts
 ```{r}
@@
 
-#Getting dates
+##Getting dates
 For a first exploration of arules, we conceptualise our framework like this:
@@
 
-##Data preparation
+###Data preparation
 First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
@@
 support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
-
 maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
@@
 
-#Preparing data frame:
+##Preparing data frame:
 ```{r}
@@
   left_join(d_transcript, by = "Course ID") %>%
-
-    # mutate(
-    #   Grade = case_when(
-    #     Grade == "NG"~ "-1",
-    #     T            ~ Grade),
-    #   Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-    #   Grade = as.numeric(Grade)) %>% #this was already done in data preparation
-
   # filter(!is.na(Grade)) %>% #remove NaN
@@
 ##Rule induction
+##Creating look-up table
 ```{r}
-#FURTURE: create filter by function
-string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
-                           quo_name(category)=="Low_grade"      ~ "low score",
-                           quo_name(category)=="Discrete_grade" ~ "5",
-                           quo_name(category)=="None"           ~ "_" #useless filter
-                           )
-
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
-                                                               maxsize = 1,
-                                                               maxlen = 2), control   = list(verbose = TRUE))
-
-summary(frequent_trajectories)
-as(frequent_trajectories, "data.frame")
-
-rules <- ruleInduction(frequent_trajectories,
-                       confidence = 0, #we need to play with the parameters.
-                       control    = list(verbose = TRUE))
-
-pass_rules_df <- as(rules, "data.frame") %>%
-
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
-
-#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
-
-  arrange(
-    LHS, RHS,
-    desc(confidence), desc(lift))
-
-n_students <- length(unique(d_sequence_transactions$`Student ID`))
-
-manual_confidence_rules <- pass_rules_df %>%
-  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
-  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
-  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>%
-  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
-
-  # Compute statistics
-  group_by(LHS,`RHS Course ID`) %>%
-  mutate(Prob_both = sum(support), 
-         Conf_corr = support/Prob_both,
-         n_rule = support * n_students,
-         n_both =Prob_both * n_students,
-         lift_diff= Conf_corr - Prop_low,
-         lift_corr=Conf_corr / Prop_low) %>%
-  ungroup() %>%
-
-  # Filter and edit output
-  filter(str_detect(`RHS Score`, pattern = "low"),
-         str_detect(`LHS Score`, pattern = "low"),
-         n_rule >= 5,
-         Conf_corr > 0.2) %>%
-  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
-  mutate(support = round(support,3),
-         Prob_both =round(Prob_both,3),
-         Prop_low =round(Prop_low,3),
-         Conf_corr= round(Conf_corr,3),
-         lift_diff= round(lift_diff,3),
-         lift_corr= round(lift_corr,3)) %>%
-  arrange(lift_diff)
-
-#FOR PLOTTING
-for_plots <-  manual_confidence_rules %>%
-  group_by(LHS)%>%
-  mutate(LHS_count=n())
-
-```
-#Visualizing rules
-```{r}
-#look at counts
-ggplot(for_plots, aes(LHS))+
-  geom_bar()
-
-#jitter
-ggplot(manual_confidence_rules)+
-  geom_jitter(mapping=aes(x=Conf_corr, y=log(support), color=lift_corr))
-
-ggplot(manual_confidence_rules)+
-  geom_jitter(mapping=aes(x=log(support), y=lift_corr, color = Conf_corr))
-
-#heatmap
-ggplot(select(manual_confidence_rules,LHS,RHS, n_rule), aes(x=RHS,y=LHS, fill=n_rule))+
-  geom_raster() +
-  theme(
-    axis.text.x = element_text(angle=90)
-  )
-
-gglot(table(select(manual_confidence_rules,LHS,RHS)))
-
-hi <- table(select(manual_confidence_rules,LHS,RHS))
-#ggnetwork
-
-```
-
-#Visualisation
-It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful.
-We might need to sample.
-See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/
-
-#Puting students into take and not take.
-
-```{r}
-test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
-  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
-  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
-  mutate(
-    take_course = case_when(
-      is.na(Grade)  ~ FALSE,
-      T             ~ TRUE
-      ),
-    PFN = case_when(
-      is.na(Grade)  ~ "not",
-      Grade >= 5.5  ~ "pass",
-      Grade < 5.5   ~ "fail"
-      )
-    )
-
-table(test$PFN)
-
-```
-
-We want to change the calculation of confidence and support. The new rules are:
-confidence: number of transactions of RHS/ number of transactions of RHS and compliment= p(A^B)/P(BUBc)
-support:number of transactions of right hand side/number of transactions of RHS and compliment= p(A^B)/p(AUBUBc)
-lift:
-
-#Experimenting with transactions
-```{r}
-fail_threshold <- 6.5
-
-category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
-
 lookup_table <- d_course %>%
@@
   mutate(Prop_low= Count/Total)
+```
 
-lookup_table
+###NOTE for FURTURE: create filter by function
+##Create filter condition.
+```{r}
+string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
+                           quo_name(category)=="Low_grade"      ~ "low score",
+                           quo_name(category)=="Discrete_grade" ~ "5",
+                           quo_name(category)=="None"           ~ "_" #useless filter
+                           )
 ```
+##CSPADE Algorithm:
+```{r}
+frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
+                                                               maxsize = 1,
+                                                               maxlen = 2), control   = list(verbose = TRUE))
+
+#Inspect results CSPADE
+summary(frequent_trajectories)
+as(frequent_trajectories, "data.frame")
+
+```
+##rule induction:
+```{r}
+rules <- ruleInduction(frequent_trajectories,
+                       confidence = 0, #we need to play with the parameters.
+                       control    = list(verbose = TRUE))
+
+pass_rules_df <- as(rules, "data.frame") %>%
+
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
+
+#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
+
+  arrange(
+    LHS, RHS,
+    desc(confidence), desc(lift))
+
+```
+##calculate appropriate measures:
+```{r}
+n_students <- length(unique(d_sequence_transactions$`Student ID`))
+
+manual_confidence_rules <- pass_rules_df %>%
+  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
+  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
+  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>%
+  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
+
+  # Compute statistics
+  group_by(LHS,`RHS Course ID`) %>%
+  mutate(Prob_both = sum(support), 
+         Conf_corr = support/Prob_both,
+         n_rule = support * n_students,
+         n_both =Prob_both * n_students,
+         lift_diff= Conf_corr - Prop_low,
+         lift_corr=Conf_corr / Prop_low) %>%
+  ungroup() %>%
+
+  # Filter and edit output
+  filter(str_detect(`RHS Score`, pattern = "low"),
+         str_detect(`LHS Score`, pattern = "low"),
+         n_rule >= 5,
+         Conf_corr > 0.2) %>%
+  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
+  mutate(support = round(support,3),
+         Prob_both =round(Prob_both,3),
+         Prop_low =round(Prop_low,3),
+         Conf_corr= round(Conf_corr,3),
+         lift_diff= round(lift_diff,3),
+         lift_corr= round(lift_corr,3)) %>%
+  arrange(lift_diff)
+#Inspect results
+manual_confidence_rules
+```
+##Arrange data for plots:
+```{r}
+for_plots <-  manual_confidence_rules %>%
+  group_by(LHS)%>%
+  mutate(LHS_count=n())
+```
+#Visualizing rules
+```{r}
+#look at counts
+ggplot(for_plots, aes(LHS))+
+  geom_bar()
+
+#jitter
+ggplot(manual_confidence_rules)+
+  geom_jitter(mapping=aes(x=Conf_corr, y=log(support), color=lift_corr))
+
+ggplot(manual_confidence_rules)+
+  geom_jitter(mapping=aes(x=log(support), y=lift_corr, color = Conf_corr))
+
+#heatmap
+ggplot(select(manual_confidence_rules,LHS,RHS, n_rule), aes(x=RHS,y=LHS, fill=n_rule))+
+  geom_raster() +
+  theme(
+    axis.text.x = element_text(angle=90)
+  )
+
+gglot(table(select(manual_confidence_rules,LHS,RHS)))
+
+#ggnetwork
+
+#SEE: http://kateto.net/network-visualization 
+g_net <- graph_from_data_frame(d=head(for_plots,50), directed=T) #I BELIEVE THE COLUMNS SHOULD BE REVERSED.
+
+l <- layout_in_circle(g_net)
+plot(g_net, #vertex.shape="none",
+     vertex.size=.9,
+     #vertex.label=NA,
+     vertex.label.cex=0.5,
+     edge.arrow.size=.1, 
+     edge.curved=.1,
+     layout=l)
+
+```
+#Visualisation
+It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful.
+We might need to sample.
+See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/
+
+#Puting students into take and not take.
+
+```{r}
+test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
+  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
+  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
+  mutate(
+    take_course = case_when(
+      is.na(Grade)  ~ FALSE,
+      T             ~ TRUE
+      ),
+    PFN = case_when(
+      is.na(Grade)  ~ "not",
+      Grade >= 5.5  ~ "pass",
+      Grade < 5.5   ~ "fail"
+      )
+    )
+
+table(test$PFN)
+
+```
+
+We want to change the calculation of confidence and support. The new rules are:
+confidence: number of transactions of RHS/ number of transactions of RHS and compliment= p(A^B)/P(BUBc)
+support:number of transactions of right hand side/number of transactions of RHS and compliment= p(A^B)/p(AUBUBc)
+lift:
 
@@
 ```
-
-```{r}
-
-length(unique(d_transcript$`Student ID`))
-```

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
add save file

@@
 
-manual_confidence_rules <- pass_rules_df %>%
+sequence_rules <- pass_rules_df %>%
   separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
@@
   arrange(lift_diff)
-#Inspect results
-manual_confidence_rules
+
 ```
+##Save data
+```{r}
+save(sequence_rules,
+     file = "sequence_rules.RDATA")
+```
+
 ##Arrange data for plots:
@@
 
-#Puting students into take and not take.
+#EXPERIMENTS:
+##Condensing grades
 
 ```{r}
+
+probabilities_manipulated <- d_transcript %>%
+  select(-Course, -Year_numerical,-Period,-`Number Repeated Attempt`,-`Academic Year`)%>% #remove this before expanding grades
+  mutate(Round_grade= round(Grade,0))
+```
+
+##Puting students into take and not take. 
+```{r}
+
+#this df has 731,676 rows:
 test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
@@
 ```
-
-We want to change the calculation of confidence and support. The new rules are:
-confidence: number of transactions of RHS/ number of transactions of RHS and compliment= p(A^B)/P(BUBc)
-support:number of transactions of right hand side/number of transactions of RHS and compliment= p(A^B)/p(AUBUBc)
-lift:
-
-```{r}
-pass_rules_df
-test <- pass_rules_df %>%
-  separate(LHS, into=c("c1","c2", "c3", "c4", "c5", "c6","c7", "c8", "c9", "c10"), sep= ",", remove=F) #has values until c6
-
-```

### 2019-01-24 App Association Rules/server.R
App to explore Sequence Rules

@@ -1,0 +1,23 @@
+
+# Setup
+library(shiny)
+library(dplyr)
+load("sequence_rules.RDATA")
+
+# Server
+function(input, output) {
+  
+  output$rules <- renderDataTable({
+    
+    dataset <- sequence_rules
+      
+    dataset %>%
+      filter(
+        between(support  , input$support[1]   , input$support[2]),
+        between(Conf_corr, input$confidence[1], input$confidence[2]),
+        between(lift_corr, input$lift[1]      , input$lift[2]      )
+      )
+    
+  })
+  
+}

### 2019-01-24 App Association Rules/ui.R

@@ -1,0 +1,63 @@
+
+# Setup
+library(shiny)
+
+fluidPage(
+  
+  # App title
+  titlePanel("Sequence Rules"),
+  
+  # Sidebar layout
+  sidebarLayout(
+    
+    # Sidebar panel for inputs
+    sidebarPanel(
+      
+      # Input: Slider for the support
+      sliderInput(
+        inputId = "support",
+        label = "Support",
+        min   = 0,
+        max   = 1,
+        step  = 0.01,
+        value = c(0, 1)
+        ),
+      
+      # Input: Slider for the Cconfidence
+      sliderInput(
+        inputId = "confidence",
+        label = "Confidence (corrected)",
+        min   = 0,
+        max   = 1,
+        step  = 0.01,
+        value = c(0, 1)
+      ),
+      
+      # Input: Slider for the Cconfidence
+      sliderInput(
+        inputId = "lift",
+        label = "Lift (corrected)",
+        min   = -15,
+        max   = 15,
+        step  = 0.01,
+        value = c(-10, 10)
+      ),
+      
+      # Horizontal line
+      tags$hr(),
+      
+      # Text
+      helpText("TODO: use logarithmic scale for sliders")
+    ),
+    
+    # Main panel for displaying outputs
+    mainPanel(
+      
+      # Output: dataset
+      dataTableOutput(outputId = "rules")
+      
+    )
+    
+  )
+  
+)

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
starting grade addition cbind

@@
 probabilities_manipulated <- d_transcript %>%
-  select(-Course, -Year_numerical,-Period,-`Number Repeated Attempt`,-`Academic Year`)%>% #remove this before expanding grades
-  mutate(Round_grade= round(Grade,0))
+  transmute(tmp_id=paste(`Student ID`,`Course ID`,Year_numerical,Period,`Number Repeated Attempt`,sep="_"),
+            Round_grade= round(Grade,0))
+student_set <- unique(probabilities_manipulated$tmp_id)
+
+for student %in% student_set
+
 ```
@@
 ```{r}
-
-#this df has 731,676 rows:
+#This df has 731,676 rows:
 test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%

### 2019-01-24 Pillar 2 - Topic Modeling.Rmd

@@
   dataset   <- get(paste("d", level, "cast", sep = "_"))
+
   LDA_model <- LDA(
@@
       best    = TRUE,
+
       burnin  = 4000,
-      iter = 2000,
-      thin = 500))
+      iter    = 5000,
+      thin    = 500,
+
+      verbose = 1e3,
+      save    = 1e3,
+      keep    = 1e3)
+    )
+
   nam <- paste("LDA", level, n_topics, sep = "_")

### 2019-01-24 Data Preparation.Rmd
clean grade var.
clean grade
changes names of import

@@
 ```{r import corpus_catalogues, cache = TRUE}
-corpus_catalogues <- Corpus(x             = DirSource("Catalogues"),
+corpus_catalogues <- Corpus(x             = DirSource("./Input/Catalogues"),
                             readerControl = list(reader = readPDF(control = list(text = "-layout"))))
@@
 ```{r import corpus_manuals, cache = TRUE}
-corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
+corpus_manuals <- Corpus(x             = DirSource("./Input/Manuals 2017-18"),
                          readerControl = list(reader = readPDF(control = list(text = "-layout"))))
@@
   read_csv(
-    "Raw Grades/grades1.csv",
+    "./Input/Raw Grades/grades1.csv",
     col_types = cols(
@@
   read_csv(
-    "Raw Grades/grades2.csv",
+    "./Input/Raw Grades/grades2.csv",
     col_types = cols(
@@
 
+### Clean Grade Variable
+
+```{r clean grade variable}
+d_transcript <- d_transcript %>%
+  mutate(Grade = case_when(Grade == "NG"~ "-1",
+                           T~ Grade),
+          Grade = str_replace(string = Grade, pattern = ",",replace = "."),
+         Grade = as.numeric(Grade))
+```
+
 ```{r}

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
relocate files to Output folder

@@
 ```{r library, message = F}
-#detach(package:tm, unload=TRUE) #there is overlap with tm package in inspect()
+library(tidyverse)
 
-library(tidyverse)
 library(arules)
 library(arulesSequences)
-
 library(rlang)
-
-library(ggplot2)
 ```
@@
 load("data_pillar_1.RDATA")
+```
 
-find_course <- function(code){ #can be modified to accept other data that is not d_transcript
-  c = code
-  x <- d_transcript %>%
-    filter(`Course Code`== c)
+Function that returns title of a course given its code.
+```{r}
+find_course <- function(code){
 
-  return(x$`Course Title`[1])
+  dataset <- d_transcript %>%
+    filter(`Course ID`== code)
+
+  title <- dataset$`Course Title`[1]
+
+  return(title)
+
 }
+```
 
-```
 #Simple Rule Mining

### 2019-01-24 LDA trial.R

@@ -1,0 +1,61 @@
+
+#results <- tibble(nstart = numeric(0),
+ #                 burnin = numeric(0),
+  #                iter   = numeric(0),
+   #               thin   = numeric(0),
+    #              k      = numeric(0),
+     #             time   = numeric(0),
+      #            LL     = numeric(0))
+
+#
+# Setup
+nstart <- 10
+burnin <- 1000
+iter   <- 1000
+thin   <- 1
+k      <- 10
+
+# starting time
+t_bef <- proc.time()
+
+#
+# run algorithm
+LDA_model <- LDA(
+  
+  x       = d_description_cast,
+  k       = k,
+  method  = "Gibbs",
+  
+  control = list(
+    nstart  = nstart,
+    seed    = c(1 : nstart),
+    
+    burnin  = burnin,
+    iter    = iter,
+    thin    = thin
+    )
+  
+)
+
+# finish time
+t_aft <- proc.time()
+
+# running time
+t_run <- t_aft - t_bef
+
+# Save
+
+results <- results %>%
+  add_row(
+    nstart = nstart,
+    burnin = burnin,
+    iter   = iter,
+    thin   = thin,
+    k      = k,
+    time   = t_run[3],
+    LL     = LDA_model@loglikelihood
+  )
+
+
+print(results)
+print(t_run[3])

### 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
minor changes

@@
 ```{r loading data}
-load("data_pillar_1.RDATA")
+load("Output/data_pillar_1.RDATA")
 ```
@@
 }
+
+# Example
+find_course("HUM1005")
 ```
@@
 ```{r}
-exploration <- d_transcript %>%
-  mutate(Grade = case_when(Grade == "NG"~ "-1", #"0,0", #maybe we could just remove these from the analysis and treat them separately?
-                           T~Grade),
-         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-         Grade = as.numeric(Grade))%>%
-  filter(!is.na(Grade)) %>%
-  filter(Grade != -1) #remove NG
 
-summary(exploration)
-
-student_statistics <- exploration %>%
-  group_by(`Student ID`) %>%
-  summarise(n = n(),
-            Min = min(Grade), 
-            Max = max(Grade), 
-            Mean = mean(Grade), 
-            Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5))
-
-course_statistics <- exploration %>%
-  inner_join(d_course, by = "Course ID") %>%
-  filter(between(Year_numerical, 2015,2016)) %>% #filter year
-  group_by(`Course ID`) %>%
-  summarise(n = n(),
+# For convenience
+provide_statistics <- function(data){
+  data %>%
+    summarise(
+      n      = n(),
       Min    = min(Grade),
@@
       Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5)) %>%
-  inner_join(select(d_course,`Course ID`, `Course Title`), by = "Course ID")
+      SD        = round(sd(Grade), 2),
+      Fail_rate = round(mean(Fail), 2),
+      Fail_n = sum(Fail)
+      )
+}
 
-concentration_statistics <- exploration %>%
-  inner_join(select(d_course,-Period, -`Period (additional)`,-`Period (additional bis)`,-`Course Title`), by = "Course ID") %>%
-  #left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
+# Student level
+d_transcript %>%
+  group_by(`Student ID`) %>%
+  provide_statistics()
+
+# Course level
+d_transcript %>%
+  inner_join(d_course, by = c("Course ID")) %>%
+  group_by(`Course ID`) %>%
+  provide_statistics()
+
+# Cluster level
+d_transcript %>%
+  inner_join(d_course, by = "Course ID") %>%
+  filter(!is.na(Cluster)) %>%
+  group_by(Cluster) %>%
+  provide_statistics()
+
+# Concentration evel
+d_transcript %>%
+  inner_join(d_course, by = "Course ID") %>%
   gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
   group_by(Concentration) %>%
-  summarise(n = n(),
-            Min = min(Grade), 
-            Max = max(Grade), 
-            Mean = round(mean(Grade), 2), 
-            Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5))
+  provide_statistics()
 
-cluster_statistics <- exploration %>%
-  inner_join(d_course, by = "Course ID") %>%
-  group_by(Cluster) %>%
-  summarise(n = n(),
-            Min = min(Grade), 
-            Max = max(Grade), 
-            Mean = round(mean(Grade), 2), 
-            Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5))
+# Year level
+d_transcript %>%
+  group_by(Year_numerical) %>%
+  provide_statistics()
 
-year_statistics <- exploration %>%
-  inner_join(d_course, by = "Course ID") %>%
-  group_by(Year_numerical) %>%
-  summarise(n = n(),
-            Min = min(Grade), 
-            Max = max(Grade), 
-            Mean = round(mean(Grade), 2), 
-            Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5))
-
-level_statistics <- exploration %>%
-  inner_join(d_course, by = "Course ID") %>%
+# Level level
+d_transcript %>%
+  inner_join(d_course, by = c("Course ID")) %>%
+  filter(!is.na(Level)) %>%
   group_by(Level) %>%
-  summarise(n = n(),
-            Min = min(Grade), 
-            Max = max(Grade), 
-            Mean = round(mean(Grade), 2), 
-            Median = median(Grade), 
-            SD = sd(Grade), 
-            `Proportion Failed` = mean(Grade < 5.5))
-
-percentage_grades_awarded <- d_transcript %>%
-          mutate(Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-                 Grade = as.integer(Grade)) %>%
-  filter(Year_numerical %in% c(2015,2016))%>%
-  mutate(total=n())%>%
-  group_by(Grade) %>%
-  mutate(grade_total=n())%>%
-  select(Grade, grade_total,total)%>%
-  distinct()%>%
-  mutate(Percentage = signif(grade_total/total,digits=2))%>%
-  arrange(Grade)
-
-```
-We have found some NA values for the grades! Students:
-
-0177849 - COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
-0177857
-0222100
-0270148
-0313173
-0317101
-0317349
-
-```{r}
-#We have NA in grades. Something weird is happening. 
-summary(str_detect(d_transcript$Grade, pattern="NA")) #shows NA's = 312 FALSE= 89069 WHY ARE THERE NAs?
-
-has_na <- d_transcript %>%
-  mutate(What = str_detect(Grade, pattern="NA")) %>%
-  filter(is.na(What))
+  provide_statistics()
 ```

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
created cumulative gap transcript (8 -> 8,9,10 grades)

--- 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+```{r, cache = TRUE}
+tmp_distributed_transcript <- d_transcript %>%
+  filter(!is.na(Grade), Grade>=0) %>%
+  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+         Values = T)
+#This is the transcript with cumulative error gap.
+distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
+               )%>%
+  mutate(g1  = g0|g1,
+         g2  = g1|g2,
+         g3  = g2|g3,
+         g4  = g3|g4,
+         g5  = g4|g5,
+         g6  = g5|g6,
+         g7  = g6|g7,
+         g8  = g7|g8,
+         g9  = g8|g9,
+         g10 = g9|g10,
+         ) %>%
+  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
+  select(-Gr_bool )%>%
+  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
+  select(-Trash) %>%
+  mutate(Grade= as.numeric(Grade_new))%>% #can put this into Grade and have just one grade value.
+  select(-Grade_new)%>%
+  arrange(`Course ID`, `Student ID`)
+
+```
+#Condensing grade
+
 ```{r}
-
-probabilities_manipulated <- d_transcript %>%
-  transmute(tmp_id=paste(`Student ID`,`Course ID`,Year_numerical,Period,`Number Repeated Attempt`,sep="_"),
-            Round_grade= round(Grade,0))
-student_set <- unique(probabilities_manipulated$tmp_id)
-
-for student %in% student_set
 

### 2019-01-25 Data Preparation.Rmd

@@
 d_transcript <- d_transcript %>%
-  mutate(Grade = case_when(Grade == "NG"~ "-1",
-                           T~ Grade),
+  mutate(Grade = case_when(Grade == "NG" ~ "NA",
+                           TRUE          ~ Grade),
          Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-         Grade = as.numeric(Grade))
+         Grade = as.numeric(Grade)) %>%
+  filter(!is.na(Grade)) %>%
+  mutate(Fail = Grade < 5.5)
 ```
@@
 save(lists, d_course, d_AoD, d_assessment, d_transcript,
-     file = "data_pillar_1.RDATA")
+     file = "Output/data_pillar_1.RDATA")
 save(lists, d_course, d_AoD, d_assessment, d_transcript,
      d_overview, d_description, d_manual,
-     file = "data_pillar_2.RDATA")
+     file = "Output/data_pillar_2.RDATA")
 ```

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
debug data prep for association rules

--- 2019-01-24 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-library(arules)
 library(arulesSequences)
-library(rlang)
 ```
@@
 
-#Simple Rule Mining
-##Data Exploration of Transcripts
-```{r}
+# Data Exploration
+
+```{r statistic summary}
 
@@
     summarise(
-      n      = n(),
       Min       = min(Grade),
@@
       Fail_rate = round(mean(Fail), 2),
-      Fail_n = sum(Fail)
+      Fail_n    = sum(Fail),
+      n         = n()
       )
@@
 
-##Getting dates
+# Association Rules
 For a first exploration of arules, we conceptualise our framework like this:
@@
 
-###Data preparation
+## Creating Transactions
 First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
 
-```{r}
+```{r AR data prep}
 d_transactions <- d_course %>%
-  select(Type, Code, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(Code) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  select(`Student ID Number`, Code) %>%
-  group_by(`Student ID Number`) %>%
-  summarize(list_course = list(Code)) %>%
-  group_by()
+
+  # Exclude 
+  filter(
+    Type != "Mandatory",              # (i) mandatory courses e.g. COR, CAP, etc
+    ! Letters %in% c("SKI", "PRO",    # (ii) skills & projects (taken by majority of students)
+                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad
+    ) %>%
+
+  # Join with transcripts.
+  left_join(d_transcript, by = "Course ID") %>%
+
+  # Create transactions (student level)
+  group_by(`Student ID`) %>%
+    summarize(list_course = list(`Course ID`)) %>%
+  ungroup
 
@@
 
+## Apriori Algorithm
 We apply Apriori algorithm:

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
experiment with transcipts and enquo

--- 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+#this is new-----
+transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
+#----------------
 d_sequence_transactions <- d_course %>%
@@
 ```
-#Condensing grade
+#puting everything into quasi-function
 
@@
 
+#parameters for analysis
+category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
+transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
+fail_threshold <- 6.5
+
+#Preparing data
+d_sequence_transactions <- d_course %>%
+
+  select(Type, `Course ID`, Letters) %>%
+
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+
+  select(`Course ID`) %>%
+
+  left_join(!!transcript_to_use, by = "Course ID") %>%
+  mutate(
+    Outcome = 
+           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade  > 5.5 ~"Pass",
+                               T~"Fail"),
+    Low_grade =
+           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                               T~"low score"),
+    Discrete_grade =
+           case_when(Grade <= 5.4             ~ 5.0,
+                     between(Grade, 5.5, 6.4) ~ 6.0,
+                     between(Grade, 6.5, 7.4) ~ 7.0,
+                     between(Grade, 7.5, 8.4) ~ 8.0,
+                     between(Grade, 8.5, 9.4) ~ 9.0,
+                     Grade >= 9.5             ~ 10.0,
+                     T ~ -99999    #this is a control, we should not have any grades here
+                     ),
+    None= "" # this might not be optimal
+         ) %>%
+
+  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
+
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+
+  select(`Student ID`, Item, Time) %>%
+
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+
+  group_by(`Student ID`, Time) %>%
+
+  summarize(list_course = list(Item)) %>%
+
+  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
+
+```
+
+##to transaction
+```{r}
+transaction_list_course <- d_sequence_transactions$list_course
+names(transaction_list_course) <- d_sequence_transactions$TransactionID
+
+transactions <- as(transaction_list_course, "transactions")
+transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
+transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
+transactionInfo(transactions)$transactionID <- NULL
+
+#checking results
+as(transactions, "data.frame")
 ```

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+```{r, cache = TRUE}
+tmp_distributed_transcript <- d_transcript %>%
+  filter(!is.na(Grade), Grade>=0) %>%
+  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+         Values = T)
+#This is the transcript with cumulative error gap.
+distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
+               )%>%
+  mutate(g1  = g0|g1,
+         g2  = g1|g2,
+         g3  = g2|g3,
+         g4  = g3|g4,
+         g5  = g4|g5,
+         g6  = g5|g6,
+         g7  = g6|g7,
+         g8  = g7|g8,
+         g9  = g8|g9,
+         g10 = g9|g10,
+         ) %>%
+  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
+  select(-Gr_bool )%>%
+  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
+  select(-Trash) %>%
+  mutate(Grade= as.numeric(Grade_new))%>% #can put this into Grade and have just one grade value.
+  select(-Grade_new)%>%
+  arrange(`Course ID`, `Student ID`)
+
+```
+#puting everything into quasi-function
+
 ```{r}
 
-probabilities_manipulated <- d_transcript %>%
-  transmute(tmp_id=paste(`Student ID`,`Course ID`,Year_numerical,Period,`Number Repeated Attempt`,sep="_"),
-            Round_grade= round(Grade,0))
-student_set <- unique(probabilities_manipulated$tmp_id)
+#parameters for analysis
+category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
+transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
+fail_threshold <- 6.5
 
-for student %in% student_set
+#Preparing data
+d_sequence_transactions <- d_course %>%
 
+  select(Type, `Course ID`, Letters) %>%
+
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+
+  select(`Course ID`) %>%
+
+  left_join(!!transcript_to_use, by = "Course ID") %>%
+  mutate(
+    Outcome = 
+           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade  > 5.5 ~"Pass",
+                               T~"Fail"),
+    Low_grade =
+           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                               T~"low score"),
+    Discrete_grade =
+           case_when(Grade <= 5.4             ~ 5.0,
+                     between(Grade, 5.5, 6.4) ~ 6.0,
+                     between(Grade, 6.5, 7.4) ~ 7.0,
+                     between(Grade, 7.5, 8.4) ~ 8.0,
+                     between(Grade, 8.5, 9.4) ~ 9.0,
+                     Grade >= 9.5             ~ 10.0,
+                     T ~ -99999    #this is a control, we should not have any grades here
+                     ),
+    None= "" # this might not be optimal
+         ) %>%
+
+  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
+
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+
+  select(`Student ID`, Item, Time) %>%
+
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+
+  group_by(`Student ID`, Time) %>%
+
+  summarize(list_course = list(Item)) %>%
+
+  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
+
+```
+
+##to transaction
+```{r}
+transaction_list_course <- d_sequence_transactions$list_course
+names(transaction_list_course) <- d_sequence_transactions$TransactionID
+
+transactions <- as(transaction_list_course, "transactions")
+transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
+transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
+transactionInfo(transactions)$transactionID <- NULL
+
+#checking results
+as(transactions, "data.frame")
 ```

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
debugged association rules section (done)

--- 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-```{r AR data prep}
+```{r}
+
 d_transactions <- d_course %>%
@@
   # Join with transcripts.
-  left_join(d_transcript, by = "Course ID") %>%
+  inner_join(d_transcript, by = "Course ID")
+```
 
+```{r AR data prep}
 # Create transactions (student level)
+transactions <- d_transactions %>%
   group_by(`Student ID`) %>%
@@
 
-transactions <- as(d_transactions$list_course, "transactions")
+transactions <- as(transactions$list_course, "transactions")
+```
+
+```{r AR data prep PF}
+d_transactions_PF <- d_transactions %>%
+
+  # Take outcome of course into account (pass or fail)
+  mutate(PF = case_when(Grade <  5.5 ~ "fail",
+                        Grade >= 5.5 ~ "pass"),
+         `Course ID` = paste(`Course ID`, PF, sep = "_"))
+
+  # Create transactions (student level)
+transactions_PF <- d_transactions_PF %>%
+  group_by(`Student ID`) %>%
+    summarize(list_course = list(`Course ID`)) %>%
+  ungroup
+
+transactions_PF <- as(transactions_PF$list_course, "transactions")
 ```
@@
 We apply Apriori algorithm:
-```{r}
-results <- apriori(
+```{r AR apriori}
+
+# TODO: conmpute support RHS
+
+AR <- apriori(
   data = transactions, 
   parameter = list(
-    supp = 0.02,
+    supp = 0, # min support
     smax = 1,    # max support
-    conf = 0.4,
-    minlen = 2,
-    maxlen = 2
+    conf = 0,    # min confidence
+    minlen = 2,  # min length of rule
+    maxlen = 2,  # max length of rule
+    ext = TRUE,
+    arem = "diff",
+    aval = TRUE,
+    minval = 0
     ),
-  appearance = NULL,
-  control = NULL
+  appearance = list(
+    #lhs = c("HUM1003"),
+    #rhs = c("HUM1007", "HUM1010")
+  ),
+  control = list(
+    verbose = FALSE
+  )
   ) %>%
@@
 
-colnames(results)[2] <- "association"
+colnames(AR)[2] <- "=>"
+```
 
-results %>%
-  arrange(desc(confidence))
-```
 Now we include data for pass and fail:
-```{r}
-d_transaction_passed <- d_course %>%
-  select(Type, Code, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(Code) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  mutate(Outcome = case_when(Grade=="NG"~"Fail",
-                             Grade > 5.5 ~"Pass",
-                             T~"Fail")) %>%
-  mutate(Item= paste(Code, Outcome, sep = "_")) %>%
-  select(`Student ID Number`, Item) %>%
-  group_by(`Student ID Number`) %>%
-  summarize(list_course = list(Item)) %>%
-  group_by()
+```{r apriori PF}
 
-transactions_passed <- as(d_transaction_passed$list_course, "transactions")
+# creating vector of fail course
+course_id_fail <- d_transactions_PF %>%
+  filter(PF == "fail") %>%
+  distinct(`Course ID`)
 
-```
-We apply Apriori algorithm:
-```{r}
-results_passed <- apriori(
-  data = transactions_passed, 
+# Apply apriori
+AR_PF <- apriori(
+  data = transactions_PF, 
   parameter = list(
-    supp = 0,
+    supp = 0, # min support
     smax = 1,    # max support
-    conf = 0.4,
-    minlen = 2,
-    maxlen = 2
+    conf = 0,    # min confidence
+    minlen = 2,  # min length of rule
+    maxlen = 2,  # max length of rule
+    ext = TRUE,
+    arem = "diff",
+    aval = TRUE,
+    minval = 0
     ),
-  appearance = NULL,
-  control = NULL
+  appearance = list(
+    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
+    ),
+  control = list(
+    verbose = FALSE
+    )
   ) %>%
@@
 
-colnames(results_passed)[2] <- "association"
+colnames(AR_PF)[2] <- "=>"
+```
 
-results_passed %>%
-  separate(lhs, into = c("LHS", "LHS_pass"), sep= "_", remove = F) %>%
-  separate(rhs, into = c("RHS", "RHS_pass"), sep= "_", remove = F) %>%
-  filter(RHS_pass == "Fail}") %>%
-  arrange(desc(count))
+```{r AR exploration}
+
+# TODO: MAKE APP
+
+data_rules <- AR
+data_rules <- AR_PF
+
+# Best support
+data_rules %>%
+  arrange(desc(support))
+
+# Best confidence
+data_rules %>%
+  filter(count >= 5) %>%
+  arrange(desc(confidence))
+
+# Best lift
+data_rules %>%
+  filter(count >= 5) %>%
+  arrange(desc(lift))
 ```

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

@@
     ),
-  appearance = list(
-    #lhs = c("HUM1003"),
-    #rhs = c("HUM1007", "HUM1010")
-  ),
+  appearance = NULL,
   control = list(

### 2019-01-25 this can be deleted.Rmd

---
title: "Untitled"
author: "DARS"
date: "1/24/2019"
output: pdf_document
---

```{r pressure, echo=FALSE}
test <- d_transcript %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T) %>%
  filter(!is.na(Round_grade), Grade>=0)

spread(test, key = "Round_grade", value = Values #, fill = F
               )%>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10,
         )%>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  arrange(`Course ID`, `Student ID`)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
debugging AR

@@
 ```{r}
-
 d_transactions <- d_course %>%
@@
     ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
-                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad
+                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
     ) %>%
@@
 
-  # Create transactions (student level)
+  # Create transactions with pass/fail
 transactions_PF <- d_transactions_PF %>%
@@
 ## Apriori Algorithm
+```{r}
+clean_AR <- function(AR){
+
+  AR %>%
+    as("data.frame") %>%
+    filter(
+      count >= 1
+    ) %>%
+    mutate(
+      rules = str_remove(rules, pattern = "_fail"),
+      lhs = substr(rules, 2, 8),
+      rhs = substr(rules, 15, 21),
+      `rhs.support` = confidence / lift
+      ) %>%
+    mutate_at(
+      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+      ) %>%
+    select(
+      lhs, rhs,
+      support, count, lhs.support,
+      confidence, rhs.support,
+      lift
+      ) %>%
+    arrange(
+      desc(count)
+    )
+
+}
+```
+
 We apply Apriori algorithm:
 ```{r AR apriori}
-
-# TODO: conmpute support RHS
-
 AR <- apriori(
@@
   ) %>%
-  inspect
+  clean_AR
 
-colnames(AR)[2] <- "=>"
 ```
@@
   ) %>%
-  inspect
-
-colnames(AR_PF)[2] <- "=>"
+  clean_AR
 ```

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
Runs threshold with added grades --> mkes no sense

--- 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-```{r}
-
+```{r AR data prep}
 d_transactions <- d_course %>%
@@
   # Join with transcripts.
-  inner_join(d_transcript, by = "Course ID")
-```
+  left_join(d_transcript, by = "Course ID") %>%
 
-```{r AR data prep}
   # Create transactions (student level)
-transactions <- d_transactions %>%
   group_by(`Student ID`) %>%
@@
 
-transactions <- as(transactions$list_course, "transactions")
-```
-
-```{r AR data prep PF}
-d_transactions_PF <- d_transactions %>%
-
-  # Take outcome of course into account (pass or fail)
-  mutate(PF = case_when(Grade <  5.5 ~ "fail",
-                        Grade >= 5.5 ~ "pass"),
-         `Course ID` = paste(`Course ID`, PF, sep = "_"))
-
-  # Create transactions (student level)
-transactions_PF <- d_transactions_PF %>%
-  group_by(`Student ID`) %>%
-    summarize(list_course = list(`Course ID`)) %>%
-  ungroup
-
-transactions_PF <- as(transactions_PF$list_course, "transactions")
+transactions <- as(d_transactions$list_course, "transactions")
 ```
@@
 We apply Apriori algorithm:
-```{r AR apriori}
-
-# TODO: conmpute support RHS
-
-AR <- apriori(
+```{r}
+results <- apriori(
   data = transactions, 
   parameter = list(
-    supp = 0, # min support
+    supp = 0.02,
     smax = 1, # max support
-    conf = 0,    # min confidence
-    minlen = 2,  # min length of rule
-    maxlen = 2,  # max length of rule
-    ext = TRUE,
-    arem = "diff",
-    aval = TRUE,
-    minval = 0
+    conf = 0.4,
+    minlen = 2,
+    maxlen = 2
     ),
   appearance = NULL,
-  control = list(
-    verbose = FALSE
-  )
+  control = NULL
   ) %>%
@@
 
-colnames(AR)[2] <- "=>"
+colnames(results)[2] <- "association"
+
+results %>%
+  arrange(desc(confidence))
 ```
+Now we include data for pass and fail:
+```{r}
+d_transaction_passed <- d_course %>%
+  select(Type,`Course ID`, Letters) %>%
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+  select(`Course ID`) %>%
+  left_join(d_transcript, by = "Course ID") %>%
+  mutate(Outcome = case_when(Grade=="NG"~"Fail",
+                             Grade > 5.5 ~"Pass",
+                             T~"Fail")) %>%
+  mutate(Item= paste(`Course ID`, Outcome, sep = "_")) %>%
+  select(`Student ID`, Item) %>%
+  group_by(`Student ID`) %>%
+  summarize(list_course = list(Item)) %>%
+  group_by()
 
-Now we include data for pass and fail:
-```{r apriori PF}
+transactions_passed <- as(d_transaction_passed$list_course, "transactions")
 
-# creating vector of fail course
-course_id_fail <- d_transactions_PF %>%
-  filter(PF == "fail") %>%
-  distinct(`Course ID`)
-
-# Apply apriori
-AR_PF <- apriori(
-  data = transactions_PF, 
+```
+We apply Apriori algorithm:
+```{r}
+results_passed <- apriori(
+  data = transactions_passed, 
   parameter = list(
-    supp = 0, # min support
+    supp = 0,
     smax = 1, # max support
-    conf = 0,    # min confidence
-    minlen = 2,  # min length of rule
-    maxlen = 2,  # max length of rule
-    ext = TRUE,
-    arem = "diff",
-    aval = TRUE,
-    minval = 0
+    conf = 0.4,
+    minlen = 2,
+    maxlen = 2
     ),
-  appearance = list(
-    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
-    ),
-  control = list(
-    verbose = FALSE
-    )
+  appearance = NULL,
+  control = NULL
   ) %>%
@@
 
-colnames(AR_PF)[2] <- "=>"
-```
+colnames(results_passed)[2] <- "association"
 
-```{r AR exploration}
-
-# TODO: MAKE APP
-
-data_rules <- AR
-data_rules <- AR_PF
-
-# Best support
-data_rules %>%
-  arrange(desc(support))
-
-# Best confidence
-data_rules %>%
-  filter(count >= 5) %>%
-  arrange(desc(confidence))
-
-# Best lift
-data_rules %>%
-  filter(count >= 5) %>%
-  arrange(desc(lift))
+results_passed %>%
+  separate(lhs, into = c("LHS", "LHS_pass"), sep= "_", remove = F) %>%
+  separate(rhs, into = c("RHS", "RHS_pass"), sep= "_", remove = F) %>%
+  filter(RHS_pass == "Fail}") %>%
+  arrange(desc(count))
 ```
@@
   select(-Grade_new)%>%
-  arrange(`Course ID`, `Student ID`)
+  mutate(Item=paste(`Course ID`,Grade, sep="_"))%>%
+  select(`Student ID`,`Course ID`)%>%
+  arrange(`Course ID`, `Student ID`) %>%
 
@@
 #puting everything into quasi-function
-
+--------------------------------------------------
 ```{r}
@@
 category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
-transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
+transcript_to_use <- "distributed_transcript" #d_transcript or distributed_transcript 
 fail_threshold <- 6.5
@@
 
-  left_join(!!transcript_to_use, by = "Course ID") %>%
+  left_join(get(transcript_to_use), by = "Course ID") %>%
   mutate(
@@
 #checking results
-as(transactions, "data.frame")
+as(transactions, "data.frame") #WARNING: THIS TAKES A LOT OF TIME, FOR SOME REASON
 ```
+##Create filter condition.
+```{r}
+string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
+                           quo_name(category)=="Low_grade"      ~ "low score",
+                           quo_name(category)=="Discrete_grade" ~ "5",
+                           quo_name(category)=="None"           ~ "_" #useless filter
+                           )
+```
+##CSPADE Algorithm:
+```{r}
+frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
+                                                               maxsize = 1,
+                                                               maxlen = 2 #,
+                                                               #mingap=, #gap between consecutive elements
+                                                               #maxgap=, #hap between consecutive elements
+                                                               #maxwin=  #gap between ANY two elements
+                                                                 ), control   = list(verbose = TRUE))
+
+#Inspect results CSPADE
+summary(frequent_trajectories)
+as(frequent_trajectories, "data.frame")
+
+```
+##rule induction:
+```{r}
+rules <- ruleInduction(frequent_trajectories,
+                       confidence = 0, #we need to play with the parameters.
+                       control    = list(verbose = TRUE))
+
+pass_rules_df <- as(rules, "data.frame") %>%
+
+  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
+
+  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
+
+  arrange(
+    LHS, RHS,
+    desc(confidence), desc(lift))
+
+```
+here I'l playing around with the correct confidence:
+#correcting lookup for this case:
+First we find out raw proportions per course (how many were low grade/high grade, out of a particular course, and the percentage this represents from the total)
+```{r}
+lookup_table <- d_course %>%
+
+  select(Type, `Course ID`, Letters) %>%
+
+  filter(Type == "Elective",
+         ! Letters %in% c("SKI", "PRO"),
+         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
+
+  select(`Course ID`) %>%
+
+  left_join(d_transcript, by = "Course ID") %>%
+  mutate(
+    Outcome = 
+           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
+                      Grade  > 5.5 ~"Pass",
+                               T~"Fail"),
+    Low_grade =
+           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
+                      Grade > fail_threshold ~"high score",
+                               T~"low score"),
+    Discrete_grade =
+           case_when(Grade <= 5.4             ~ 5.0,
+                     between(Grade, 5.5, 6.4) ~ 6.0,
+                     between(Grade, 6.5, 7.4) ~ 7.0,
+                     between(Grade, 7.5, 8.4) ~ 8.0,
+                     between(Grade, 8.5, 9.4) ~ 9.0,
+                     Grade >= 9.5             ~ 10.0,
+                     T ~ -99999    #this is a control, we should not have any grades here
+                     ),
+    None= "" # this might not be optimal
+         ) %>%
+
+  #mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
+
+  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
+
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time)) %>%
+
+  select(`Student ID`, #Item,  #************************************ <- 
+         `Course ID`, !!category, Time) %>% # Course ID and Time may not be necessary
+
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+
+  group_by(`Course ID`, !!category) %>% ##this makes no sense we should just group id and low_grade
+
+  summarize(Count = n()) %>%
+  #separate(Item, into= c("Course ID", quo_name(category)), sep="_", remove = F) %>%
+  ungroup() %>%
+  group_by(`Course ID`) %>%
+  mutate(Total= sum(Count))%>%
+  filter(Low_grade=="low score")%>%
+  mutate(Prop_low= Count/Total)
+```
+
+```{r}
+n_students <- length(unique(d_sequence_transactions$`Student ID`))
+
+sequence_rules <- pass_rules_df %>%
+  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
+  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
+  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>% #add more
+  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
+
+  # Compute statistics
+  group_by(LHS,`RHS Course ID`) %>%
+  arrange(LHS,`RHS Course ID`)
+  mutate(
+    Prob_both = sum(support), 
+    Conf_corr = support/Prob_both,
+    n_rule    = support * n_students,
+    n_both    = Prob_both * n_students,
+    lift_diff = Conf_corr - Prop_low,
+    lift_corr = Conf_corr / Prop_low
+    ) %>%
+  ungroup() %>%
+
+  # Filter and edit output
+  filter(str_detect(`RHS Score`, pattern = "low"),
+         str_detect(`LHS Score`, pattern = "low"),
+         n_rule >= 5,
+         Conf_corr > 0.2) %>%
+  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
+  mutate(support = round(support,3),
+         Prob_both =round(Prob_both,3),
+         Prop_low =round(Prop_low,3),
+         Conf_corr= round(Conf_corr,3),
+         lift_diff= round(lift_diff,3),
+         lift_corr= round(lift_corr,3)) %>%
+  arrange(lift_diff)
+
+```
+
+---------------------------------------------------
 

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
delete conflict

@@
 Function that returns title of a course given its code.
-```{r}
+```{r function find_course}
 find_course <- function(code){
@@
 
-```{r AR data prep}
+```{r AR data prep 1}
 d_transactions <- d_course %>%
@@
   # Join with transcripts.
-  left_join(d_transcript, by = "Course ID") %>%
+  inner_join(d_transcript, by = "Course ID")
+```
 
+```{r AR data prep 2}
 # Create transactions (student level)
+transactions <- d_transactions %>%
   group_by(`Student ID`) %>%
@@
 
-transactions <- as(d_transactions$list_course, "transactions")
+transactions <- as(transactions$list_course, "transactions")
+```
+
+```{r AR data prep 3 (PF)}
+d_transactions_PF <- d_transactions %>%
+
+  # Take outcome of course into account (pass or fail)
+  mutate(PF = case_when(Grade <  5.5 ~ "fail",
+                        Grade >= 5.5 ~ "pass"),
+         `Course ID` = paste(`Course ID`, PF, sep = "_"))
+
+  # Create transactions with pass/fail
+transactions_PF <- d_transactions_PF %>%
+  group_by(`Student ID`) %>%
+    summarize(list_course = list(`Course ID`)) %>%
+  ungroup
+
+transactions_PF <- as(transactions_PF$list_course, "transactions")
 ```
@@
 ## Apriori Algorithm
+```{r}
+clean_AR <- function(AR){
+
+  AR %>%
+    as("data.frame") %>%
+    filter(
+      count >= 1
+    ) %>%
+    mutate(
+      rules = str_remove(rules, pattern = "_fail"),
+      lhs = substr(rules, 2, 8),
+      rhs = substr(rules, 15, 21),
+      `rhs.support` = confidence / lift
+      ) %>%
+    mutate_at(
+      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+      ) %>%
+    select(
+      lhs, rhs,
+      support, count, lhs.support,
+      confidence, rhs.support,
+      lift
+      ) %>%
+    arrange(
+      desc(count)
+    )
+
+}
+```
+
 We apply Apriori algorithm:
-```{r}
-results <- apriori(
+```{r AR apriori}
+AR <- apriori(
   data = transactions, 
   parameter = list(
-    supp = 0.02,
+    supp = 0,    # min support
     smax = 1,    # max support
-    conf = 0.4,
-    minlen = 2,
-    maxlen = 2
+    conf = 0,    # min confidence
+    minlen = 2,  # min length of rule
+    maxlen = 2,  # max length of rule
+    ext = TRUE,
+    arem = "diff",
+    aval = TRUE,
+    minval = 0
     ),
   appearance = NULL,
-  control = NULL
+  control = list(
+    verbose = FALSE
+    )
   ) %>%
-  inspect
-
-colnames(results)[2] <- "association"
-
-results %>%
-  arrange(desc(confidence))
-```
-Now we include data for pass and fail:
-```{r}
-d_transaction_passed <- d_course %>%
-  select(Type,`Course ID`, Letters) %>%
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-  select(`Course ID`) %>%
-  left_join(d_transcript, by = "Course ID") %>%
-  mutate(Outcome = case_when(Grade=="NG"~"Fail",
-                             Grade > 5.5 ~"Pass",
-                             T~"Fail")) %>%
-  mutate(Item= paste(`Course ID`, Outcome, sep = "_")) %>%
-  select(`Student ID`, Item) %>%
-  group_by(`Student ID`) %>%
-  summarize(list_course = list(Item)) %>%
-  group_by()
-
-transactions_passed <- as(d_transaction_passed$list_course, "transactions")
+  clean_AR
 
 ```
-We apply Apriori algorithm:
-```{r}
-results_passed <- apriori(
-  data = transactions_passed, 
+
+Now we include data for pass and fail:
+
+```{r apriori PF}
+
+# creating vector of fail course
+course_id_fail <- d_transactions_PF %>%
+  filter(PF == "fail") %>%
+  distinct(`Course ID`)
+
+# Apply apriori
+AR_PF <- apriori(
+  data = transactions_PF, 
   parameter = list(
-    supp = 0,
+    supp = 0, # min support
     smax = 1,    # max support
-    conf = 0.4,
-    minlen = 2,
-    maxlen = 2
+    conf = 0,    # min confidence
+    minlen = 2,  # min length of rule
+    maxlen = 2,  # max length of rule
+    ext = TRUE,
+    arem = "diff",
+    aval = TRUE,
+    minval = 0
     ),
-  appearance = NULL,
-  control = NULL
+  appearance = list(
+    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
+    ),
+  control = list(
+    verbose = FALSE
+    )
   ) %>%
-  inspect
+  clean_AR
+```
 
-colnames(results_passed)[2] <- "association"
+```{r AR exploration}
 
-results_passed %>%
-  separate(lhs, into = c("LHS", "LHS_pass"), sep= "_", remove = F) %>%
-  separate(rhs, into = c("RHS", "RHS_pass"), sep= "_", remove = F) %>%
-  filter(RHS_pass == "Fail}") %>%
-  arrange(desc(count))
+# TODO: MAKE APP
+
+data_rules <- AR
+data_rules <- AR_PF
+
+# Best support
+data_rules %>%
+  arrange(desc(support))
+
+# Best confidence
+data_rules %>%
+  filter(count >= 5) %>%
+  arrange(desc(confidence))
+
+# Best lift
+data_rules %>%
+  filter(count >= 5) %>%
+  arrange(desc(lift))
 ```

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
solve conflict
creates rules with grades

@@
 
-Now we include data for pass and fail:
-
 ```{r apriori PF}
-
 # creating vector of fail course
@@
 
-```{r, cache = TRUE}
+```{r}
 tmp_distributed_transcript <- d_transcript %>%
@@
   select(-Trash) %>%
-  mutate(Grade= as.numeric(Grade_new))%>% #can put this into Grade and have just one grade value.
+  mutate(Grade= as.numeric(Grade_new))%>%
   select(-Grade_new)%>%
+  filter(!str_detect(Period, " to "))%>% #Crutch FILTER
   mutate(Item=paste(`Course ID`,Grade, sep="_"))%>%
-  select(`Student ID`,`Course ID`)%>%
-  arrange(`Course ID`, `Student ID`) %>%
-
-```
-#puting everything into quasi-function
---------------------------------------------------
-```{r}
-
-#parameters for analysis
-category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
-transcript_to_use <- "distributed_transcript" #d_transcript or distributed_transcript 
-fail_threshold <- 6.5
-
-#Preparing data
-d_sequence_transactions <- d_course %>%
-
-  select(Type, `Course ID`, Letters) %>%
-
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-
-  select(`Course ID`) %>%
-
-  left_join(get(transcript_to_use), by = "Course ID") %>%
-  mutate(
-    Outcome = 
-           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade  > 5.5 ~"Pass",
-                               T~"Fail"),
-    Low_grade =
-           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                               T~"low score"),
-    Discrete_grade =
-           case_when(Grade <= 5.4             ~ 5.0,
-                     between(Grade, 5.5, 6.4) ~ 6.0,
-                     between(Grade, 6.5, 7.4) ~ 7.0,
-                     between(Grade, 7.5, 8.4) ~ 8.0,
-                     between(Grade, 8.5, 9.4) ~ 9.0,
-                     Grade >= 9.5             ~ 10.0,
-                     T ~ -99999    #this is a control, we should not have any grades here
-                     ),
-    None= "" # this might not be optimal
-         ) %>%
-
-  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
-
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-
   mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-
+          Time = as.double(Time))%>%
   select(`Student ID`, Item, Time) %>%
-
   arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-
   group_by(`Student ID`, Time) %>%
-
   summarize(list_course = list(Item)) %>%
-
   mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
@@
 
+```{r}
+
+tmp_distributed_transcript <- d_course %>%
+  select(`Course ID`, Type, Letters) %>%
+  # Exclude 
+  filter(
+    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
+    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
+                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
+    ) %>%
+
+  # Join with transcripts.
+  inner_join(d_transcript, by = "Course ID") %>%
+  filter(!is.na(Grade), Grade>=0) %>%
+  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+         Values = T)
+#This is the transcript with cumulative error gap.
+
+distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
+               )%>%
+  mutate(g1  = g0|g1,
+         g2  = g1|g2,
+         g3  = g2|g3,
+         g4  = g3|g4,
+         g5  = g4|g5,
+         g6  = g5|g6,
+         g7  = g6|g7,
+         g8  = g7|g8,
+         g9  = g8|g9,
+         g10 = g9|g10,
+         ) %>%
+  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
+  select(-Gr_bool )%>%
+  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
+  select(-Trash) %>%
+  mutate(Grade= as.numeric(Grade_new))%>%
+  select(-Grade_new)%>%
+  filter(!str_detect(Period, " to "))%>% #Crutch FILTER
+  mutate(Item=paste(`Course ID`,Grade, sep="_"))%>%
+  mutate( Time = paste(Year_numerical, Period, sep = ""),
+          Time = as.double(Time))%>%
+  select(`Student ID`, Item, Time) %>%
+  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+  group_by(`Student ID`, Time) %>%
+  summarize(list_course = list(Item)) %>%
+  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
+
+```
+
+#puting everything into quasi-function
+--------------------------------------------------
 ##to transaction
 ```{r}
-transaction_list_course <- d_sequence_transactions$list_course
-names(transaction_list_course) <- d_sequence_transactions$TransactionID
+transaction_list_course <- distributed_transcript$list_course
+names(transaction_list_course) <- distributed_transcript$TransactionID
 
 transactions <- as(transaction_list_course, "transactions")
-transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
-transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
+transactionInfo(transactions)$sequenceID <- distributed_transcript$`Student ID`
+transactionInfo(transactions)$eventID <- distributed_transcript$Time
 transactionInfo(transactions)$transactionID <- NULL
@@
 #checking results
-as(transactions, "data.frame") #WARNING: THIS TAKES A LOT OF TIME, FOR SOME REASON
+as(transactions, "data.frame")
 ```
@@
 ```{r}
-string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
-                           quo_name(category)=="Low_grade"      ~ "low score",
-                           quo_name(category)=="Discrete_grade" ~ "5",
-                           quo_name(category)=="None"           ~ "_" #useless filter
-                           )
+# string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
+#                            quo_name(category)=="Low_grade"      ~ "low score",
+#                            quo_name(category)=="Discrete_grade" ~ "5",
+#                            quo_name(category)=="None"           ~ "_" #useless filter
+#                            )
 ```
 ##CSPADE Algorithm:
+
 ```{r}
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
+frequent_trajectories <- cspade(transactions, parameter = list(support = 0.1,
                                                                maxsize = 1,
@@
 
-  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
+  #filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
 
@@
     desc(confidence), desc(lift))
+
+support(frequent_trajectories,transactions, control=list(verbose=T))
 

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
Creating Sequences

--- 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-# Association Rules
+# Association Rules and Sequence Rules
 For a first exploration of arules, we conceptualise our framework like this:
@@
 ```{r AR data prep 1}
+
+#
+# Threshold: low vs high grade
+low_grade <- 6.5
+
+#
+# Transactions
 d_transactions <- d_course %>%
@@
   # Join with transcripts.
-  inner_join(d_transcript, by = "Course ID")
+  select(- Period) %>%
+  inner_join(d_transcript, by = "Course ID") %>%
+
+  # Identifying sequences
+  rename(sequenceID = `Student ID`) %>%
+
+  # Identifying time of event (sequence)
+  mutate(
+    Period  = substr(Period, 1, 1),
+    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
+    ) %>%
+
+  # Identifying item
+  mutate(
+    PF = case_when( Grade <  5.5 ~ "fail",
+                    Grade >= 5.5 ~ "pass"),
+    HL = case_when( Grade <  low_grade ~ "low",
+                    Grade >= low_grade ~ "high"),
+
+    item_PF = paste(`Course ID`, PF, sep = "_"),
+    item_HL = paste(`Course ID`, HL, sep = "_")
+    ) %>%
+  rename(
+    item = `Course ID`
+  )
 ```
 
+### Transactions for Apriori
 ```{r AR data prep 2}
-# Create transactions (student level)
 transactions <- d_transactions %>%
-  group_by(`Student ID`) %>%
-    summarize(list_course = list(`Course ID`)) %>%
+  group_by(
+    sequenceID
+    ) %>%
+  summarize(
+    list_item = list(item)
+    ) %>%
   ungroup
 
-transactions <- as(transactions$list_course, "transactions")
+transactions <- as(transactions$list_item, "transactions")
 ```
@@
 ```{r AR data prep 3 (PF)}
-d_transactions_PF <- d_transactions %>%
-
-  # Take outcome of course into account (pass or fail)
-  mutate(PF = case_when(Grade <  5.5 ~ "fail",
-                        Grade >= 5.5 ~ "pass"),
-         `Course ID` = paste(`Course ID`, PF, sep = "_"))
-
-  # Create transactions with pass/fail
-transactions_PF <- d_transactions_PF %>%
-  group_by(`Student ID`) %>%
-    summarize(list_course = list(`Course ID`)) %>%
+transactions_PF <- d_transactions %>%
+  group_by(
+    sequenceID
+    ) %>%
+  summarize(
+    list_item = list(item_PF)
+    ) %>%
   ungroup
 
-transactions_PF <- as(transactions_PF$list_course, "transactions")
+transactions_PF <- as(transactions_PF$list_item, "transactions")
+```
+
+```{r AR data prep 4 (HL)}
+transactions_HL <- d_transactions %>%
+  group_by(
+    sequenceID
+    ) %>%
+  summarize(
+    list_item = list(item_HL)
+    ) %>%
+  ungroup
+
+transactions_HL <- as(transactions_HL$list_item, "transactions")
+```
+
+### Sequences for CSPADE
+```{r}
+sequences_temp <- d_transactions %>%
+  group_by(
+    sequenceID,
+    eventID
+    ) %>%
+  summarize(
+    list_item = list(item)
+    ) %>%
+  arrange(
+    sequenceID,
+    eventID
+    )
+
+sequences             <- as(sequences_temp$list_item, "transactions")
+sequences@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
+
+#checking results
+#inspect(head(sequences, 10))
+```
+
+```{r}
+sequences_temp <- d_transactions %>%
+  group_by(
+    sequenceID,
+    eventID
+    ) %>%
+  summarize(
+    list_item = list(item_PF)
+    ) %>%
+  arrange(
+    sequenceID,
+    eventID
+    )
+
+sequences_PF             <- as(sequences_temp$list_item, "transactions")
+sequences_PF@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
+
+#checking results
+#inspect(head(sequences_PF, 10))
+```
+
+```{r}
+sequences_temp <- d_transactions %>%
+  group_by(
+    sequenceID,
+    eventID
+    ) %>%
+  summarize(
+    list_item = list(item_HL)
+    ) %>%
+  arrange(
+    sequenceID,
+    eventID
+    )
+
+sequences_HL             <- as(sequences_temp$list_item, "transactions")
+sequences_HL@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
+
+#checking results
+#inspect(head(sequences_HL, 10))
 ```
@@
 
-#Mining-sequences:
+## CSPADE Algorithm
+
 The parameter values are: 
@@
 
-##Preparing data frame:
-```{r}
-fail_threshold <- 6.5
-
-category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
-
-#this is new-----
-transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
-#----------------
-d_sequence_transactions <- d_course %>%
-
-  select(Type, `Course ID`, Letters) %>%
-
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-
-  select(`Course ID`) %>%
-
-  left_join(d_transcript, by = "Course ID") %>%
-  # filter(!is.na(Grade)) %>% #remove NaN
-  # filter(Grade != -1) %>% #remove NG
-  mutate(
-    Outcome = 
-           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade  > 5.5 ~"Pass",
-                               T~"Fail"),
-    Low_grade =
-           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                               T~"low score"),
-    Discrete_grade =
-           case_when(Grade <= 5.4             ~ 5.0,
-                     between(Grade, 5.5, 6.4) ~ 6.0,
-                     between(Grade, 6.5, 7.4) ~ 7.0,
-                     between(Grade, 7.5, 8.4) ~ 8.0,
-                     between(Grade, 8.5, 9.4) ~ 9.0,
-                     Grade >= 9.5             ~ 10.0,
-                     T ~ -99999    #this is a control, we should not have any grades here
-                     ),
-    None= "" # this might not be optimal
-         ) %>%
-
-  mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
-
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-
-  select(`Student ID`, Item, Time) %>%
-
-  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-
-  group_by(`Student ID`, Time) %>%
-
-  summarize(list_course = list(Item)) %>%
-
-  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
-
-```
-
-##to transaction
-```{r}
-transaction_list_course <- d_sequence_transactions$list_course
-names(transaction_list_course) <- d_sequence_transactions$TransactionID
-
-transactions <- as(transaction_list_course, "transactions")
-transactionInfo(transactions)$sequenceID <- d_sequence_transactions$`Student ID`
-transactionInfo(transactions)$eventID <- d_sequence_transactions$Time
-transactionInfo(transactions)$transactionID <- NULL
-
-#checking results
-as(transactions, "data.frame")
-```
-
-##Rule induction
 ##Creating look-up table

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
debug cspade

@@
 
-The parameter values are: 
-support:  a numeric value specifying the minimum support of a sequence (default 0.1, range [0,1]).
-maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
-maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
-mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
-maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
-maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
+```{r}
+subsequences <- sequences %>%
+  cspade(
+    parameter = list(
+      support = 0, # min support of a sequence
+      maxsize = 1, # max number of items of an element of a sequence
+      maxlen  = 2, # max number of element of a sequence
+      mingap  = 1, # min time difference between consecutive element of a sequence
+      maxgap  = 1e4, # max time difference between consecutive element of a sequence
+      maxwin  = 1e4  # max time difference between any two elements of a sequence
+      ),
+    control = list(
+      verbose = FALSE
+      )
+    )
 
-##Creating look-up table
-```{r}
-lookup_table <- d_course %>%
-
-  select(Type, `Course ID`, Letters) %>%
-
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-
-  select(`Course ID`) %>%
-
-  left_join(d_transcript, by = "Course ID") %>%
-  mutate(
-    Outcome = 
-           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade  > 5.5 ~"Pass",
-                               T~"Fail"),
-    Low_grade =
-           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                               T~"low score"),
-    Discrete_grade =
-           case_when(Grade <= 5.4             ~ 5.0,
-                     between(Grade, 5.5, 6.4) ~ 6.0,
-                     between(Grade, 6.5, 7.4) ~ 7.0,
-                     between(Grade, 7.5, 8.4) ~ 8.0,
-                     between(Grade, 8.5, 9.4) ~ 9.0,
-                     Grade >= 9.5             ~ 10.0,
-                     T ~ -99999    #this is a control, we should not have any grades here
-                     ),
-    None= "" # this might not be optimal
-         ) %>%
-
-  #mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
-
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-
-  select(`Student ID`, #Item, 
-         `Course ID`, !!category, Time) %>% # Course ID and Time may not be necessary
-
-  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-
-  group_by(`Course ID`, !!category) %>% ##this makes no sense we should just group id and low_grade
-
-  summarize(Count = n()) %>%
-  #separate(Item, into= c("Course ID", quo_name(category)), sep="_", remove = F) %>%
-  ungroup() %>%
-  group_by(`Course ID`) %>%
-  mutate(Total= sum(Count))%>%
-  filter(Low_grade=="low score")%>%
-  mutate(Prop_low= Count/Total)
+#Inspect results CSPADE
+summary(subsequences)
+as(subsequences, "data.frame")
 ```
 
-###NOTE for FURTURE: create filter by function
-##Create filter condition.
-```{r}
-string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
-                           quo_name(category)=="Low_grade"      ~ "low score",
-                           quo_name(category)=="Discrete_grade" ~ "5",
-                           quo_name(category)=="None"           ~ "_" #useless filter
-                           )
-```
-##CSPADE Algorithm:
-```{r}
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
-                                                               maxsize = 1,
-                                                               maxlen = 2), control   = list(verbose = TRUE))
-
-#Inspect results CSPADE
-summary(frequent_trajectories)
-as(frequent_trajectories, "data.frame")
-
-```
 ##rule induction:
@@
   group_by(LHS,`RHS Course ID`) %>%
-  arrange(LHS,`RHS Course ID`)
+  arrange(LHS,`RHS Course ID`) %>%
   mutate(

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
ungroup()

--- 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r}
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0,
+frequent_trajectories <- cspade(sequences, parameter = list(support = 0,
                                                                maxsize = 1,
@@
 
+Excluding manatory courses.
 ```{r}
@@
 ```{r}
+category
 n_students <- length(unique(d_sequence_transactions$`Student ID`))
@@
   group_by(LHS,`RHS Course ID`) %>%
-  arrange(LHS,`RHS Course ID`)
   mutate(
-    Prob_both = sum(support), 
+    Prob_both = sum(support))%>%
+  ungroup()%>%
+  mutate( 
     Conf_corr = support/Prob_both,
@@
     lift_corr = Conf_corr / Prop_low
-    ) %>%
-  ungroup() %>%
+    )
 

### 2019-01-28 Data Preparation.Rmd

@@
                             between(Period, 600, 660) ~ "6",
-                            between(Period, 901, 999) ~ "1")) %>%
+                            between(Period, 901, 999) ~ "1")
+         ) %>%
   mutate(`Academic Year`= paste(Year_numerical, Year_numerical + 1, sep = "-"))

### 2019-01-29 Jenny/code_for_graphs.R
delete Jenny's folder

@@ -1,68 +1,0 @@
-library(ggalluvial)
-library(tidyverse)
-
-path= "/Users/sofia/Documents/DARS/Jenny/Graphs"
-
-year1 <- "2015-2016"
-year2 <- "2016-2017"
-year3 <- "2017-2018"
-
-
-#--------------------------------------NEW DATA
-#DataFrame:
-d1 <- data %>%
-  group_by(Origin, Destination, Year) %>%
-  summarise(count = n())             # %>%
-  #filter(Year==year3)
-
-#Summary table:
-ttle <-"Complete"
-write.table(d1, paste(ttle," Summary-NEW DATA.csv",sep=""), sep=",", row.names = F)
-
-#Summary bar plot:
-ggplot() +
-  geom_bar(data, mapping = aes(x = Destination)) +
-  facet_grid(Year~Origin)
-
-
-#--------------------------------------OLD DATA
-#DataFrame:
-d2<- old_overview %>%
-  group_by(Origin, Destination, Year) %>%
-  summarise(count=n()) %>%
-  #filter(Destination=="UCM" | Destination=="MSP"| Destination=="UCV") #%>% 
-  #filter(Year==year3)
-  filter(Origin=="UCM")
-
-#Summary table:
-ttle2 <- "Complete"
-write.table(d2, paste(ttle2," Summary-OLD DATA.csv", sep=""), sep=",", row.names = F)
-
-#Summary bar plot:
-ggplot()+
-  geom_bar(d2, mapping= aes(x=Destination))+
-  facet_grid(Year~Origin)+
-  theme_bw()
-
-#--------------------------------------Alluvium Graph
-year <-"2015-2018"
-d <-d2 #can be d1 or d2
-a<-"nan"
-
-if (d==d1){a <- "NEW DATA" }
-if(d==d2){a <- "OLD DATA"}
-if(d!=d1 | d!=d2){a <- "nan"}
-
-ggplot(as.data.frame(d),
-       aes(y = count, axis1 = Origin, axis2 = Destination)) +
-  geom_alluvium(aes(fill = Destination), width = 1/12) +
-  geom_stratum(width = 1/30, fill = "black", color = "grey") +
-  geom_label(stat = "stratum", label.strata = TRUE) +
-  scale_x_discrete(limits = c("Origin", "Destination"), expand = c(.05, .05)) +
-  scale_fill_brewer(type = "qual", palette = "Set1") +
[…]

### 2019-01-29 Jenny/tables_for_plots.R

@@ -1,47 +1,0 @@
-library(dplyr)
-
-nd        <- read.csv("/Users/sofia/Documents/DARS/Jenny/Tables/Complete Summary-NEW DATA.csv")
-
-nd$Origin <- paste(nd$Origin, "to", nd$Destination, sep = " ")
-
-nd <- select(nd,-Destination) %>%
-nd <- group_by(nd,Origin) %>%
-  summarise(count = sum(count)) 
-
-
-ggplot(nd, aes(x=Origin, y= count, fill=Year))+
-  geom_bar(stat = "identity")+
-  theme_bw()+
-  labs(x="Direction of Student Traffic", y="Number of Students", title="Flow of Students within MSLAS",caption="New Data")
-ggsave("Flow of Students within MSLAS-NEW DATA.png", device= "png", width = 25, height= 25, units="cm", path="/Users/sofia/Documents/DARS/Jenny/Simple Graphs")
-
-
-
-#----------------------------------------
-o_mslas <- read.csv("/Users/sofia/Documents/DARS/Jenny/Tables/MSLAS Summary-OLD DATA.csv")
-
-o_mslas$Origin <- paste(o_mslas$Origin, "to", o_mslas$Destination, sep = " ")
-
-o_mslas <- select(o_mslas,-Destination)
-o_mslas<- group_by(o_mslas,Origin) %>%
-  summarise(count = sum(count)) 
-
-ggplot(o_mslas, aes(x=Origin, y= count,fill=Year))+
-  geom_bar(stat = "identity")+
-  theme_bw()+
-  labs(x="Direction of Student Traffic", y="Number of Students", title="Flow of Students within MSLAS",caption="Old Data")
-ggsave("Flow of Students within MSLAS-OLD DATA.png", device= "png", width = 25, height= 25, units="cm", path="/Users/sofia/Documents/DARS/Jenny/Simple Graphs")
-
-#----------------------------
-od      <- read.csv("/Users/sofia/Documents/DARS/Jenny/Tables/Complete Summary-OLD DATA.csv")
-od$Origin <- paste(od$Origin, "to", od$Destination, sep = " ")
-
-od <- select(od,-Destination)
-od<- group_by(od,Origin) %>%
-  summarise(count = sum(count)) 
-
-ggplot(od, aes(x=Origin, y= count, fill=Year))+
-  geom_bar(stat = "identity")+
-  theme_bw()+
[…]

### 2019-01-29 Data Preparation.Rmd
save output of transcript summaries

@@
 ```{r}
-save(lists, d_course, d_AoD, d_assessment, d_transcript,
+save(d_course, d_transcript,
      file = "Output/data_pillar_1.RDATA")

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Student level
-d_transcript %>%
+statistics_student <- d_transcript %>%
   group_by(`Student ID`) %>%
@@
 # Course level
-d_transcript %>%
+statistics_course <- d_transcript %>%
   inner_join(d_course, by = c("Course ID")) %>%
@@
 # Cluster level
-d_transcript %>%
+statistics_cluster <- d_transcript %>%
   inner_join(d_course, by = "Course ID") %>%
@@
 # Concentration evel
-d_transcript %>%
+statistics_concentration <- d_transcript %>%
   inner_join(d_course, by = "Course ID") %>%
@@
 # Year level
-d_transcript %>%
+statistics_year <- d_transcript %>%
   group_by(Year_numerical) %>%
@@
 # Level level
-d_transcript %>%
+statistics_level <- d_transcript %>%
+  # TODO: filter for student who completed their studies
   inner_join(d_course, by = c("Course ID")) %>%
@@
   provide_statistics()
+
+#
+# output
+save(statistics_student, statistics_course, statistics_cluster,
+     statistics_concentration, statistics_year, statistics_level, file = "Output/Transcript Statistics.RDATA")
+rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
+     statistics_concentration, statistics_year, statistics_level)
 ```
@@
 
-## Creating Transactions
+## Data Prep: Creating Transactions and Sequences
 First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
@@
 #
-# Threshold: low vs high grade
-low_grade <- 6.5
+# Threshold: pass grade, high grade
+pass_grade <- 5.5
+high_grade <- 6.5
 
@@
   mutate(
-    PF = case_when( Grade <  5.5 ~ "fail",
-                    Grade >= 5.5 ~ "pass"),
-    HL = case_when( Grade <  low_grade ~ "low",
-                    Grade >= low_grade ~ "high"),
+    PF = case_when( Grade <  pass_grade ~ "fail",
+                    Grade >= pass_grade ~ "pass"),
+    HL = case_when( Grade <  high_grade ~ "low",
+                    Grade >= high_grade ~ "high"),
 
@@
 ### Transactions for Apriori
-```{r AR data prep 2}
-transactions <- d_transactions %>%
+```{r making transactions}
+
+#
+# For convenience
+make_transaction <- function(data = d_transactions, item = item){
+
+  data <- data %>%
     group_by(
@@
     ) %>%
-  summarize(
-    list_item = list(item)
+    summarise(
+      list_item = list(!!enquo(item))
     ) %>%
@@
 
-transactions <- as(transactions$list_item, "transactions")
-```
+  transactions <- as(
+    data$list_item,
+    "transactions"
+    )
 
-```{r AR data prep 3 (PF)}
-transactions_PF <- d_transactions %>%
-  group_by(
-    sequenceID
-    ) %>%
-  summarize(
-    list_item = list(item_PF)
-    ) %>%
-  ungroup
+  return(transactions)
 
-transactions_PF <- as(transactions_PF$list_item, "transactions")
-```
+}
 
-```{r AR data prep 4 (HL)}
-transactions_HL <- d_transactions %>%
-  group_by(
-    sequenceID
-    ) %>%
-  summarize(
-    list_item = list(item_HL)
-    ) %>%
-  ungroup
+#
+# Making transactions
+transactions    <- make_transaction(item = item   )
+transactions_PF <- make_transaction(item = item_PF)
+transactions_HL <- make_transaction(item = item_HL)
 
-transactions_HL <- as(transactions_HL$list_item, "transactions")
+#
+# Checking transactions
+inspect(head(transactions, 10))
+
+rm(make_transaction)
 ```
@@
 ```{r}
-sequences_temp <- d_transactions %>%
+
+#
+# For convenience
+make_sequence <- function(data = d_transactions, item = item){
+
+  data <- data %>%
     group_by(
@@
       eventID
+    ) %>%
+    ungroup
+
+  sequences <- as(
+    data$list_item,
+    "transactions"
     )
 
-sequences             <- as(sequences_temp$list_item, "transactions")
-sequences@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
-
-#checking results
-#inspect(head(sequences, 10))
-```
-
-```{r}
-sequences_temp <- d_transactions %>%
-  group_by(
+  sequences@itemsetInfo <- select(
+    data,
     sequenceID,
@@
     ) %>%
-  summarize(
-    list_item = list(item_PF)
-    ) %>%
-  arrange(
-    sequenceID,
-    eventID
-    )
+    as.data.frame()
 
-sequences_PF             <- as(sequences_temp$list_item, "transactions")
-sequences_PF@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
+  return(sequences)
 
-#checking results
-#inspect(head(sequences_PF, 10))
+}
+
+#
+# Making sequences
+sequences    <- make_sequence(item = item   )
+sequences_PF <- make_sequence(item = item_PF)
+sequences_HL <- make_sequence(item = item_HL)
+
+#
+# Checking sequences
+inspect(head(sequences, 10))
+
+rm(make_transaction)
 ```
 
+## Mining Rules
+
+### Apriori Algorithm
 ```{r}
-sequences_temp <- d_transactions %>%
-  group_by(
-    sequenceID,
-    eventID
-    ) %>%
-  summarize(
-    list_item = list(item_HL)
-    ) %>%
-  arrange(
-    sequenceID,
-    eventID
-    )
 
-sequences_HL             <- as(sequences_temp$list_item, "transactions")
-sequences_HL@itemsetInfo <- as.data.frame(select(sequences_temp, sequenceID, eventID))
-
-#checking results
-#inspect(head(sequences_HL, 10))
-```
-
-## Apriori Algorithm
-```{r}
+# Transform AR from apriori into a readable data frame
 clean_AR <- function(AR){
@@
       rules = str_remove(rules, pattern = "_fail"),
+      rules = str_remove(rules, pattern = "_low"),
       lhs = substr(rules, 2, 8),
@@
 ```{r AR apriori}
-AR <- apriori(
-  data = transactions, 
+
+# Run the apriori algorithm with desired parameters
+my_apriori <- function(data, appearance = NULL){
+
+  data %>%
+    apriori(
       parameter = list(
@@
         conf = 0,    # min confidence
-    minlen = 2,  # min length of rule
+        minlen = 2,  # min length of 
         maxlen = 2,  # max length of rule
@@
         ),
-  appearance = NULL,
+      appearance = appearance,
       control = list(
@@
 
-```
+}
 
-```{r apriori PF}
+#
+# Generating asocciation rules
+AR <- my_apriori(transactions)
+
 # creating vector of fail course
-course_id_fail <- d_transactions_PF %>%
+course_id_fail <- d_transactions %>%
   filter(PF == "fail") %>%
-  distinct(`Course ID`)
+  distinct(`item_PF`)
 
-# Apply apriori
-AR_PF <- apriori(
-  data = transactions_PF, 
-  parameter = list(
-    supp = 0, # min support
-    smax = 1,    # max support
-    conf = 0,    # min confidence
-    minlen = 2,  # min length of rule
-    maxlen = 2,  # max length of rule
-    ext = TRUE,
-    arem = "diff",
-    aval = TRUE,
-    minval = 0
-    ),
-  appearance = list(
-    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
-    ),
-  control = list(
-    verbose = FALSE
-    )
-  ) %>%
-  clean_AR
-```
+AR_PF <- my_apriori(transactions_PF,
+                    appearance = list(both = course_id_fail$`item_PF`))
 
-```{r AR exploration}
+# creating vector of fail course
+course_id_low <- d_transactions %>%
+  filter(HL == "low") %>%
+  distinct(`item_HL`)
+
+AR_HL <- my_apriori(transactions_HL,
+                    appearance = list(both = course_id_low$`item_HL`))
+
+#
+# Save association rules
+save(AR, AR_PF, AR_HL,
+     file = "Output/AS.RDATA")
 
@@
 
-data_rules <- AR
-data_rules <- AR_PF
+rm(clean_AR, my_apriori,
+   transactions, transactions_PF, transactions_HL,
+   course_id_fail, course_id_low
+   AR, AR_PF, AR_HL)
 
-# Best support
-data_rules %>%
-  arrange(desc(support))
-
-# Best confidence
-data_rules %>%
-  filter(count >= 5) %>%
-  arrange(desc(confidence))
-
-# Best lift
-data_rules %>%
-  filter(count >= 5) %>%
-  arrange(desc(lift))
 ```
@@
 ```{r}
+
 subsequences <- sequences %>%
@@
 #EXPERIMENTS:
+
+##TO MOVE UP (These are ready:)
+Rounds grades and add new row from original grade up to 10.
+NOTE: includes mandatory courses.
+```{r}
+distributed_transcript <- d_transcript %>%
+  filter(!is.na(Grade), Grade>=0) %>%
+  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+         Values = T) %>%
+  spread(key = "Round_grade", value = Values) %>%
+  mutate(g1  = g0|g1,
+         g2  = g1|g2,
+         g3  = g2|g3,
+         g4  = g3|g4,
+         g5  = g4|g5,
+         g6  = g5|g6,
+         g7  = g6|g7,
+         g8  = g7|g8,
+         g9  = g8|g9,
+         g10 = g9|g10,
+         ) %>%
+  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
+  select(-Gr_bool )%>%
+  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
+  select(-Trash) %>%
+  mutate(Grade= as.numeric(Grade_new))%>%
+  select(-Grade_new) #%>%
+  #to check that the grades appear from original grade to 10.
+  #arrange(`Student ID`, `Course ID`) 
+```
+
+#TRASH:
 ##Condensing grades
@@
 distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
-               )%>%
+               ) %>%
   mutate(g1  = g0|g1,
@@
 ```
+
 ##Create filter condition.
@@
 here I'l playing around with the correct confidence:
+
 #correcting lookup for this case:
@@
   group_by(LHS,`RHS Course ID`) %>%
-  arrange(LHS,`RHS Course ID`) %>%
   mutate(
-    Prob_both = sum(support), 
+    Prob_both = sum(support))%>%
+  ungroup()%>%
+  mutate( 
     Conf_corr = support/Prob_both,
@@
 
----------------------------------------------------
-
 ##Puting students into take and not take. 
@@
        Grade < 5.5   ~ "fail"
-      )
+       ),
+    Item = paste(`Course ID`, take_course, sep="_")
     )
@@
 ```
+
+```{r}
+test %>%
+ mutate(
+    Period  = substr(Period, 1, 1),
+    eventID = as.numeric(paste(Year_numerical, Period, sep = "")),
+    Item = paste(`Course ID`,Grade, sep="_")
+    ) %>%
+  select(`Student ID`, Item, eventID) %>%
+  arrange(`Student ID`, eventID) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
+  group_by(`Student ID`, Time) %>%
+  summarize(list_course = list(Item)) %>%
+  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
+```

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd
Integrates not taken courses into d_transactions

@@
 ```
+### SOFIA---Take not take courses
+```{r}
+#item and sequenceID
+
+d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
+  left_join(d_transactions, by = c("sequenceID","item")) %>%
+  mutate(
+    Taken= case_when(
+     is.na(Grade)  ~ "not taken",
+      T             ~ "taken"),
+    item_Taken= paste(item,Taken, sep = "_")
+     )
+
+#ARRANGE PROPERLY
+
+d_transactions <- d_transactions_tmp
+
+rm(d_transactions_tmp)
+```
 
@@
 transactions_HL    <- make_transaction(item = item_HL)
+transactions_Taken <- make_transaction(item=item_Taken)
 
@@
 # Checking transactions
-inspect(head(transactions, 10))
+#inspect(head(transactions, 10))
 
@@
 # Checking sequences
-inspect(head(sequences, 10))
+#inspect(head(sequences, 10))
 
-rm(make_transaction)
+rm(make_sequence)
 ```
@@
     mutate(
-      rules = str_remove(rules, pattern = "_fail"),
-      rules = str_remove(rules, pattern = "_low"),
-      lhs = substr(rules, 2, 8),
-      rhs = substr(rules, 15, 21),
+      rules = str_remove(rules, pattern = "[{]"),
+      rules = str_remove(rules, pattern = "[}]"),
+      rules = str_remove(rules, pattern = "[{]"),
+      rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
       `rhs.support` = confidence / lift
     ) %>%
+    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
     mutate_at(
@@
 
-# creating vector of fail course
+# creating vector of low score course
 course_id_low <- d_transactions %>%
@@
 
+AR_Taken <- my_apriori(transactions_Taken)
+
 #
 # Save association rules
-save(AR, AR_PF, AR_HL,
+save(AR, AR_PF, AR_HL, AR_Taken,
      file = "Output/AS.RDATA")
@@
    transactions, transactions_PF, transactions_HL,
-   course_id_fail, course_id_low
-   AR, AR_PF, AR_HL)
+   course_id_fail, course_id_low,
+   AR, AR_PF, AR_HL, AR_Taken)
 
@@
 
-#TRASH:
-##Condensing grades
-
-```{r}
-tmp_distributed_transcript <- d_transcript %>%
-  filter(!is.na(Grade), Grade>=0) %>%
-  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
-         Values = T)
-#This is the transcript with cumulative error gap.
-distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
-               )%>%
-  mutate(g1  = g0|g1,
-         g2  = g1|g2,
-         g3  = g2|g3,
-         g4  = g3|g4,
-         g5  = g4|g5,
-         g6  = g5|g6,
-         g7  = g6|g7,
-         g8  = g7|g8,
-         g9  = g8|g9,
-         g10 = g9|g10,
-         ) %>%
-  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
-  select(-Gr_bool )%>%
-  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
-  select(-Trash) %>%
-  mutate(Grade= as.numeric(Grade_new))%>%
-  select(-Grade_new)%>%
-  filter(!str_detect(Period, " to "))%>% #Crutch FILTER
-  mutate(Item=paste(`Course ID`,Grade, sep="_"))%>%
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time))%>%
-  select(`Student ID`, Item, Time) %>%
-  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID`, Time) %>%
-  summarize(list_course = list(Item)) %>%
-  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
-
-```
-
-Excluding manatory courses.
-```{r}
-
-tmp_distributed_transcript <- d_course %>%
-  select(`Course ID`, Type, Letters)   %>%
-  # Exclude 
-  filter(
-    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
-    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
-                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
-    ) %>%
-
-  # Join with transcripts.
-  inner_join(d_transcript, by = "Course ID") %>%
-  filter(!is.na(Grade), Grade>=0)            %>%
-  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
-         Values = T)
-#This is the transcript with cumulative error gap.
-
-distributed_transcript <- spread(tmp_distributed_transcript, key = "Round_grade", value = Values #, fill = F
-               ) %>%
-  mutate(g1  = g0|g1,
-         g2  = g1|g2,
-         g3  = g2|g3,
-         g4  = g3|g4,
-         g5  = g4|g5,
-         g6  = g5|g6,
-         g7  = g6|g7,
-         g8  = g7|g8,
-         g9  = g8|g9,
-         g10 = g9|g10,
-         ) %>%
-  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
-  select(-Gr_bool )%>%
-  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
-  select(-Trash) %>%
-  mutate(Grade= as.numeric(Grade_new))%>%
-  select(-Grade_new)%>%
-  filter(!str_detect(Period, " to "))%>% #Crutch FILTER
-  mutate(Item=paste(`Course ID`,Grade, sep="_"))%>%
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time))%>%
-  select(`Student ID`, Item, Time) %>%
-  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID`, Time) %>%
-  summarize(list_course = list(Item)) %>%
-  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
-
-```
-
-#puting everything into quasi-function
---------------------------------------------------
-##to transaction
-```{r}
-transaction_list_course <- distributed_transcript$list_course
-names(transaction_list_course) <- distributed_transcript$TransactionID
-
-transactions <- as(transaction_list_course, "transactions")
-transactionInfo(transactions)$sequenceID <- distributed_transcript$`Student ID`
-transactionInfo(transactions)$eventID <- distributed_transcript$Time
-transactionInfo(transactions)$transactionID <- NULL
-
-#checking results
-as(transactions, "data.frame")
-```
-
-##Create filter condition.
-```{r}
-# string_filter <- case_when(quo_name(category)=="Outcome"        ~ "Fail",
-#                            quo_name(category)=="Low_grade"      ~ "low score",
-#                            quo_name(category)=="Discrete_grade" ~ "5",
-#                            quo_name(category)=="None"           ~ "_" #useless filter
-#                            )
-```
-##CSPADE Algorithm:
-
-```{r}
-frequent_trajectories <- cspade(transactions, parameter = list(support = 0.1,
-                                                               maxsize = 1,
-                                                               maxlen = 2 #,
-                                                               #mingap=, #gap between consecutive elements
-                                                               #maxgap=, #hap between consecutive elements
-                                                               #maxwin=  #gap between ANY two elements
-                                                                 ), control   = list(verbose = TRUE))
-
-#Inspect results CSPADE
-summary(frequent_trajectories)
-as(frequent_trajectories, "data.frame")
-
-```
-##rule induction:
-```{r}
-rules <- ruleInduction(frequent_trajectories,
-                       confidence = 0, #we need to play with the parameters.
-                       control    = list(verbose = TRUE))
-
-pass_rules_df <- as(rules, "data.frame") %>%
-
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
-
-  #filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
-
-  arrange(
-    LHS, RHS,
-    desc(confidence), desc(lift))
-
-support(frequent_trajectories,transactions, control=list(verbose=T))
-
-```
-here I'l playing around with the correct confidence:
-
-#correcting lookup for this case:
-First we find out raw proportions per course (how many were low grade/high grade, out of a particular course, and the percentage this represents from the total)
-```{r}
-lookup_table <- d_course %>%
-
-  select(Type, `Course ID`, Letters) %>%
-
-  filter(Type == "Elective",
-         ! Letters %in% c("SKI", "PRO"),
-         ! Letters %in% c("SAS", "SAH", "SAC")) %>%
-
-  select(`Course ID`) %>%
-
-  left_join(d_transcript, by = "Course ID") %>%
-  mutate(
-    Outcome = 
-           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
-                      Grade  > 5.5 ~"Pass",
-                               T~"Fail"),
-    Low_grade =
-           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
-                      Grade > fail_threshold ~"high score",
-                               T~"low score"),
-    Discrete_grade =
-           case_when(Grade <= 5.4             ~ 5.0,
-                     between(Grade, 5.5, 6.4) ~ 6.0,
-                     between(Grade, 6.5, 7.4) ~ 7.0,
-                     between(Grade, 7.5, 8.4) ~ 8.0,
-                     between(Grade, 8.5, 9.4) ~ 9.0,
-                     Grade >= 9.5             ~ 10.0,
-                     T ~ -99999    #this is a control, we should not have any grades here
-                     ),
-    None= "" # this might not be optimal
-         ) %>%
-
-  #mutate(Item = paste(`Course ID`, !!category, sep = "_")) %>% #Change for Outcome/Low_grade/Discrete_grade
-
-  filter(!str_detect(Period, " to ")) %>% #filter courses that spann more than one period
-
-  mutate( Time = paste(Year_numerical, Period, sep = ""),
-          Time = as.double(Time)) %>%
-
-  select(`Student ID`, #Item,  #************************************ <- 
-         `Course ID`, !!category, Time) %>% # Course ID and Time may not be necessary
-
-  arrange(`Student ID`, Time) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-
-  group_by(`Course ID`, !!category) %>% ##this makes no sense we should just group id and low_grade
-
-  summarize(Count = n()) %>%
-  #separate(Item, into= c("Course ID", quo_name(category)), sep="_", remove = F) %>%
-  ungroup() %>%
-  group_by(`Course ID`) %>%
-  mutate(Total= sum(Count))%>%
-  filter(Low_grade=="low score")%>%
-  mutate(Prop_low= Count/Total)
-```
-
-```{r}
-category
-n_students <- length(unique(d_sequence_transactions$`Student ID`))
-
-sequence_rules <- pass_rules_df %>%
-  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
-  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
-  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>% #add more
-  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
-
-  # Compute statistics
-  group_by(LHS,`RHS Course ID`) %>%
-  mutate(
-    Prob_both = sum(support))%>%
-  ungroup()%>%
-  mutate( 
-    Conf_corr = support/Prob_both,
-    n_rule    = support * n_students,
-    n_both    = Prob_both * n_students,
-    lift_diff = Conf_corr - Prop_low,
-    lift_corr = Conf_corr / Prop_low
-    )
-
-  # Filter and edit output
-  filter(str_detect(`RHS Score`, pattern = "low"),
-         str_detect(`LHS Score`, pattern = "low"),
-         n_rule >= 5,
-         Conf_corr > 0.2) %>%
-  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
-  mutate(support = round(support,3),
-         Prob_both =round(Prob_both,3),
-         Prop_low =round(Prop_low,3),
-         Conf_corr= round(Conf_corr,3),
-         lift_diff= round(lift_diff,3),
-         lift_corr= round(lift_corr,3)) %>%
-  arrange(lift_diff)
-
-```
-
+##Not ready to move up:
 ##Puting students into take and not take. 
@@
   left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
+  filter(
+     Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
+    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
+                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
+  )%>%
   select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
@@
     take_course = case_when(
-      is.na(Grade)  ~ FALSE,
-      T             ~ TRUE
+      is.na(Grade)  ~ "not taken",
+      T             ~ "taken"
       ),
@@
 
-table(test$PFN)
+```
+
+```{r}
+trans <- test %>%
+ mutate(
+    Period  = substr(Period, 1, 1),
+    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
+    ) %>%
+   rename(sequenceID = `Student ID`)%>%
+  select(sequenceID, eventID, Item) %>%
+  make_transaction(item=Item)
 
@@
 ```{r}
-test %>%
- mutate(
-    Period  = substr(Period, 1, 1),
-    eventID = as.numeric(paste(Year_numerical, Period, sep = "")),
-    Item = paste(`Course ID`,Grade, sep="_")
-    ) %>%
-  select(`Student ID`, Item, eventID) %>%
-  arrange(`Student ID`, eventID) %>% #Note that integer identifiers must be positive and that transactions must be ordered by sequenceID and eventID.
-  group_by(`Student ID`, Time) %>%
-  summarize(list_course = list(Item)) %>%
-  mutate(TransactionID = paste(`Student ID`, Time, sep = "_"))
+# Run the apriori algorithm with desired parameters
+my_apriori <- function(data, appearance = NULL){
+
+  data %>%
+    apriori(
+      parameter = list(
+        supp = 0,    # min support
+        smax = 1,    # max support
+        conf = 0,    # min confidence
+        minlen = 2,  # min length of 
+        maxlen = 2,  # max length of rule
+        ext = TRUE,
+        arem = "diff",
+        aval = TRUE,
+        minval = 0
+        ),
+      appearance = appearance,
+      control = list(
+        verbose = FALSE
+        )
+      ) #%>%
+    #clean_AR
+
+}
+
+#
+# Generating asocciation rules
+AR <- my_apriori(trans)
+
+AR %>%
+    as("data.frame") %>%
+    filter(
+      count >= 1
+    )
+
+# TODO: MAKE APP
+
 ```
+```

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd
Deleting experiments

@@
 ```
-### SOFIA---Take not take courses
+### Adding not taken courses
 ```{r}
-#item and sequenceID
-
 d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
@@
 ##Not ready to move up:
-##Puting students into take and not take. 
-```{r}
-#This df has 731,676 rows:
-test <- expand.grid(`Student ID`= unique(d_transcript$`Student ID`),`Course ID`= unique(d_course$`Course ID`)) %>%
-  left_join(d_transcript, by=c("Course ID", "Student ID")) %>%
-  filter(
-     Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
-    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
-                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
-  )%>%
-  select(`Course ID`, `Student ID`, Grade, Year_numerical, Period) %>%
-  mutate(
-    take_course = case_when(
-      is.na(Grade)  ~ "not taken",
-      T             ~ "taken"
-      ),
-     PFN = case_when(
-       is.na(Grade)  ~ "not",
-       Grade >= 5.5  ~ "pass",
-       Grade < 5.5   ~ "fail"
-       ),
-    Item = paste(`Course ID`, take_course, sep="_")
-    )
-
-```
-
-```{r}
-trans <- test %>%
- mutate(
-    Period  = substr(Period, 1, 1),
-    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
-    ) %>%
-   rename(sequenceID = `Student ID`)%>%
-  select(sequenceID, eventID, Item) %>%
-  make_transaction(item=Item)
-
-```
-
-```{r}
-# Run the apriori algorithm with desired parameters
-my_apriori <- function(data, appearance = NULL){
-
-  data %>%
-    apriori(
-      parameter = list(
-        supp = 0,    # min support
-        smax = 1,    # max support
-        conf = 0,    # min confidence
-        minlen = 2,  # min length of 
-        maxlen = 2,  # max length of rule
-        ext = TRUE,
-        arem = "diff",
-        aval = TRUE,
-        minval = 0
-        ),
-      appearance = appearance,
-      control = list(
-        verbose = FALSE
-        )
-      ) #%>%
-    #clean_AR
-
-}
-
-#
-# Generating asocciation rules
-AR <- my_apriori(trans)
-
-AR %>%
-    as("data.frame") %>%
-    filter(
-      count >= 1
-    )
-
-# TODO: MAKE APP
-
-```
-```

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 ```{r library, message = F}
+library(arulesSequences)
+
 library(tidyverse)
-
-library(arulesSequences)
 ```
@@
 
-## CSPADE Algorithm
+### CSPADE Algorithm
 
@@
     parameter = list(
-      support = 0, # min support of a sequence
+      support = 0.2, # min support of a sequence
       maxsize = 1, # max number of items of an element of a sequence

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd
Adds filter to subsequences to filter out not taken courses before runnning apriori

@@
   data <- data %>%
+    filter(!is.na(eventID))%>% #this is here casue we have courses that were never taken.
     group_by(
@@
 ## Mining Rules
-
 ### Apriori Algorithm
@@
 ```{r}
-rules <- ruleInduction(frequent_trajectories,
+rules <- ruleInduction(subsequences,
                        confidence = 0, #we need to play with the parameters.
@@
 ```
+
 ##calculate appropriate measures:

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

@@
     parameter = list(
-      support = 0.2, # min support of a sequence
+      support = 0.01, # min support of a sequence
       maxsize = 1, # max number of items of an element of a sequence
@@
 
-  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
+  separate(sequece, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
 
@@
 
+```{r}
+
+# Transform AR from apriori into a readable data frame
+clean_rules <- function(rules){
+  rules %>%
+    as("data.frame") %>%
+    # filter(
+    #   count >= 1
+    # ) %>%
+    mutate(
+      rule = str_remove(rule, pattern = "[<]"),
+      rule = str_remove(rule, pattern = "[{]"),
+      rule = str_remove(rule, pattern = "[}]"),
+      rule = str_remove(rule, pattern = "[>]"),
+      rule = str_remove(rule, pattern = "[<]"),
+      rule = str_remove(rule, pattern = "[{]"),
+      rule = str_remove(rule, pattern = "[}]"),  #this is repeated, because it only removes the first instance
+     # rule = str_remove(rule, pattern = "[>]"), #this is taken out because the rules is marked with a => so it removes that one. 
+      `rhs.support` = confidence / lift
+    ) %>%
+    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
+    mutate(
+      lhs = str_remove(rule, pattern = "[<]"),
+      lhs = str_remove(rule, pattern = "[{]"),
+      lhs = str_remove(rule, pattern = "[}]"),
+      lhs = str_remove(rule, pattern = "[>]"),
+      rhs = str_remove(rule, pattern = "[<]"),
+      rhs = str_remove(rule, pattern = "[{]"),
+      rhs = str_remove(rule, pattern = "[}]"),
+      rhs = str_remove(rule, pattern = "[>]")
+    ) %>%
+    mutate_at(
+      c("support", #"lhs.support",
+        "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+    ) %>%
+    select(
+      lhs, rhs,
+      support, #count, lhs.support,
+      confidence, rhs.support,
+      lift
+    ) #%>%
+    #arrange(
+    #  desc(count)
+    #)
+
+}
+```
 ##calculate appropriate measures:

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
changes repetition of str_remove to str_remove_all

@@
     mutate(
-      rules = str_remove(rules, pattern = "[{]"),
-      rules = str_remove(rules, pattern = "[}]"),
-      rules = str_remove(rules, pattern = "[{]"),
-      rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
+      rules = str_remove_all(rules, pattern = "[{]"),
+      rules = str_remove_all(rules, pattern = "[}]"),
+      # rules = str_remove(rules, pattern = "[{]"),
+      # rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
       `rhs.support` = confidence / lift
@@
     # ) %>%
-    mutate(
-      rule = str_remove(rule, pattern = "[<]"),
-      rule = str_remove(rule, pattern = "[{]"),
-      rule = str_remove(rule, pattern = "[}]"),
-      rule = str_remove(rule, pattern = "[>]"),
-      rule = str_remove(rule, pattern = "[<]"),
-      rule = str_remove(rule, pattern = "[{]"),
-      rule = str_remove(rule, pattern = "[}]"),  #this is repeated, because it only removes the first instance
-     # rule = str_remove(rule, pattern = "[>]"), #this is taken out because the rules is marked with a => so it removes that one. 
-      `rhs.support` = confidence / lift
-    ) %>%
+    mutate(`rhs.support` = confidence / lift) %>%
     separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
     mutate(
-      lhs = str_remove(rule, pattern = "[<]"),
-      lhs = str_remove(rule, pattern = "[{]"),
-      lhs = str_remove(rule, pattern = "[}]"),
-      lhs = str_remove(rule, pattern = "[>]"),
-      rhs = str_remove(rule, pattern = "[<]"),
-      rhs = str_remove(rule, pattern = "[{]"),
-      rhs = str_remove(rule, pattern = "[}]"),
-      rhs = str_remove(rule, pattern = "[>]")
+      lhs = str_remove(lhs, pattern = "[<]"),
+      lhs = str_remove(lhs, pattern = "[{]"),
+      lhs = str_remove(lhs, pattern = "[}]"),
+      lhs = str_remove(lhs, pattern = "[>]"),
+      rhs = str_remove(rhs, pattern = "[<]"),
+      rhs = str_remove(rhs, pattern = "[{]"),
+      rhs = str_remove(rhs, pattern = "[}]"),
+      rhs = str_remove(rhs, pattern = "[>]")
     ) %>%

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
minor changes
removes unnecessary

@@
       rules = str_remove_all(rules, pattern = "[}]"),
-      # rules = str_remove(rules, pattern = "[{]"),
-      # rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
       `rhs.support` = confidence / lift

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Save AR for App

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
+
 ### Adding not taken courses
@@
 # Save association rules
-save(AR, AR_PF, AR_HL, AR_Taken,
-     file = "Output/AS.RDATA")
+AR <- list(
+    AR = AR,
+    AR_PF = AR_PF,
+    AR_HL = AR_HL,
+    AR_Taken = AR_Taken
+    )
 
-# TODO: MAKE APP
+save(AR, file = "App/AR.RDATA")
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Creates fuction for cspade and applies

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Save association rules
-save(AR, AR_PF, AR_HL, AR_Taken,
-     file = "Output/AS.RDATA")
+save(
+  AR = list(
+    AR = AR,
+    AR_PF = AR_PF,
+    AR_HL = AR_HL,
+    AR_Taken = AR_Taken
+    ),
+  file = "Output/AR.RDATA")
 
@@
 ### CSPADE Algorithm
+We apply cspade algorithm
 
 ```{r}
+# Transform rules from ruleInduction into a readable data frame
+clean_IR <- function(rules){
+  rules %>%
+    as("data.frame") %>%
+    # filter(
+    #   count >= 1
+    # ) %>%
+    mutate(
+      rule = str_remove_all(rule, pattern = "[<]"),
+      rule = str_remove_all(rule, pattern = "[{]"),
+      rule = str_remove_all(rule, pattern = "[}]"),
+      rule = str_remove_all(rule, pattern = "[>]"),
+      `rhs.support` = confidence / lift
+      ) %>%
+    separate(rule, into = c("lhs", "rhs"), sep="=") %>%
+    mutate_at(
+      c("support", #"lhs.support",
+        "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+    ) %>%
+    select(
+      lhs, rhs,
+      support, 
+      #count, lhs.support, #figure out how to get these
+      confidence, rhs.support,
+      lift
+    ) #%>%
+    #arrange(
+    #  desc(count)
+    #)
 
-subsequences <- sequences %>%
+}
+```
+We apply cspade followed by rule induction
+```{r}
+# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
+my_IR <- function(data){
+  data %>%
   cspade(
@@
       )
-    )
+    ) %>%
+    ruleInduction(
+      confidence = 0, #we need to play with the parameters.
+      control    = list(verbose = FALSE)
+      ) %>%
+    clean_IR
+}
 
-#Inspect results CSPADE
-summary(subsequences)
-as(subsequences, "data.frame")
-```
+#Generating induced rules
+IR    <- my_IR(data = sequences   )
+IR_PF <- my_IR(data = sequences_PF)
+IR_HL <- my_IR(data = sequences_HL)
 
-##rule induction:
-```{r}
-rules <- ruleInduction(subsequences,
-                       confidence = 0, #we need to play with the parameters.
-                       control    = list(verbose = TRUE))
+#Saving induced rules:
+save(
+  IR = list(
+    IR = IR,
+    IR_PF = IR_PF,
+    IR_HL = IR_HL
+    ),
+  file = "Output/IR.RDATA")
 
-pass_rules_df <- as(rules, "data.frame") %>%
-
-  separate(sequece, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
-
-#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
-
-  arrange(
-    LHS, RHS,
-    desc(confidence), desc(lift))
+rm(clean_IR, my_IR,
+   sequences, sequences_PF, sequences_HL,
+   IR, IR_PF, IR_HL)
 
@@
 
-```{r}
-
-# Transform AR from apriori into a readable data frame
-clean_rules <- function(rules){
-  rules %>%
-    as("data.frame") %>%
-    # filter(
-    #   count >= 1
-    # ) %>%
-    mutate(`rhs.support` = confidence / lift) %>%
-    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
-    mutate(
-      lhs = str_remove(lhs, pattern = "[<]"),
-      lhs = str_remove(lhs, pattern = "[{]"),
-      lhs = str_remove(lhs, pattern = "[}]"),
-      lhs = str_remove(lhs, pattern = "[>]"),
-      rhs = str_remove(rhs, pattern = "[<]"),
-      rhs = str_remove(rhs, pattern = "[{]"),
-      rhs = str_remove(rhs, pattern = "[}]"),
-      rhs = str_remove(rhs, pattern = "[>]")
-    ) %>%
-    mutate_at(
-      c("support", #"lhs.support",
-        "confidence", "rhs.support", "lift"),
-      funs(round(., 5))
-    ) %>%
-    select(
-      lhs, rhs,
-      support, #count, lhs.support,
-      confidence, rhs.support,
-      lift
-    ) #%>%
-    #arrange(
-    #  desc(count)
-    #)
-
-}
-```
 ##calculate appropriate measures:

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 # Save association rules
-save(
-  AR = list(
+AR <- list(
     AR = AR,
@@
     AR_Taken = AR_Taken
-    ),
-  file = "Output/AR.RDATA")
+    )
 
-# TODO: MAKE APP
+save(AR, file = "App/AR.RDATA")
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
disables maxwin in clean_IR

@@
 We apply cspade algorithm
-
 ```{r}
@@
       mingap  = 1, # min time difference between consecutive element of a sequence
-      maxgap  = 1e4, # max time difference between consecutive element of a sequence
-      maxwin  = 1e4  # max time difference between any two elements of a sequence
+      maxgap  = 1e4 # max time difference between consecutive element of a sequence
+      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
       ),

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
include different types of AR in Shiny App

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Generating asocciation rules
-AR <- my_apriori(transactions)
+AR_taken <- my_apriori(transactions)
 
@@
 
-AR_Taken <- my_apriori(transactions_Taken)
+AR_not_taken <- my_apriori(transactions_Taken)
 
@@
 # Save association rules
-AR <- list(
-    AR = AR,
-    AR_PF = AR_PF,
-    AR_HL = AR_HL,
-    AR_Taken = AR_Taken
-    )
-
-save(AR, file = "App/AR.RDATA")
+save(AR_taken, AR_PF, AR_HL, AR_not_taken,
+     file = "App/ARR.RDATA")
 
@@
 ### CSPADE Algorithm
-We apply cspade algorithm
 
 ```{r}
-# Transform rules from ruleInduction into a readable data frame
-clean_IR <- function(rules){
-  rules %>%
-    as("data.frame") %>%
-    # filter(
-    #   count >= 1
-    # ) %>%
-    mutate(
-      rule = str_remove_all(rule, pattern = "[<]"),
-      rule = str_remove_all(rule, pattern = "[{]"),
-      rule = str_remove_all(rule, pattern = "[}]"),
-      rule = str_remove_all(rule, pattern = "[>]"),
-      `rhs.support` = confidence / lift
-      ) %>%
-    separate(rule, into = c("lhs", "rhs"), sep="=") %>%
-    mutate_at(
-      c("support", #"lhs.support",
-        "confidence", "rhs.support", "lift"),
-      funs(round(., 5))
-    ) %>%
-    select(
-      lhs, rhs,
-      support, 
-      #count, lhs.support, #figure out how to get these
-      confidence, rhs.support,
-      lift
-    ) #%>%
-    #arrange(
-    #  desc(count)
-    #)
 
-}
-```
-We apply cspade followed by rule induction
-```{r}
-# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
-my_IR <- function(data){
-  data %>%
+subsequences <- sequences %>%
   cspade(
@@
       )
-    ) %>%
-    ruleInduction(
+    )
+
+#Inspect results CSPADE
+summary(subsequences)
+as(subsequences, "data.frame")
+```
+
+##rule induction:
+```{r}
+rules <- ruleInduction(subsequences,
                        confidence = 0, #we need to play with the parameters.
-      control    = list(verbose = FALSE)
-      ) %>%
-    clean_IR
-}
+                       control    = list(verbose = TRUE))
 
-#Generating induced rules
-IR    <- my_IR(data = sequences   )
-IR_PF <- my_IR(data = sequences_PF)
-IR_HL <- my_IR(data = sequences_HL)
+pass_rules_df <- as(rules, "data.frame") %>%
 
-#Saving induced rules:
-save(
-  IR = list(
-    IR = IR,
-    IR_PF = IR_PF,
-    IR_HL = IR_HL
-    ),
-  file = "Output/IR.RDATA")
+  separate(sequece, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns
 
-rm(clean_IR, my_IR,
-   sequences, sequences_PF, sequences_HL,
-   IR, IR_PF, IR_HL)
+#  filter(str_detect(RHS, string_filter)) %>% #FILTER (YES) --> uncomment, (NO)-->comment
+
+  arrange(
+    LHS, RHS,
+    desc(confidence), desc(lift))
 
@@
 
+```{r}
+
+# Transform AR from apriori into a readable data frame
+clean_rules <- function(rules){
+  rules %>%
+    as("data.frame") %>%
+    # filter(
+    #   count >= 1
+    # ) %>%
+    mutate(`rhs.support` = confidence / lift) %>%
+    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
+    mutate(
+      lhs = str_remove(lhs, pattern = "[<]"),
+      lhs = str_remove(lhs, pattern = "[{]"),
+      lhs = str_remove(lhs, pattern = "[}]"),
+      lhs = str_remove(lhs, pattern = "[>]"),
+      rhs = str_remove(rhs, pattern = "[<]"),
+      rhs = str_remove(rhs, pattern = "[{]"),
+      rhs = str_remove(rhs, pattern = "[}]"),
+      rhs = str_remove(rhs, pattern = "[>]")
+    ) %>%
+    mutate_at(
+      c("support", #"lhs.support",
+        "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+    ) %>%
+    select(
+      lhs, rhs,
+      support, #count, lhs.support,
+      confidence, rhs.support,
+      lift
+    ) #%>%
+    #arrange(
+    #  desc(count)
+    #)
+
+}
+```
 ##calculate appropriate measures:

### 2019-01-30 App/server.R

@@ -3,19 +3,22 @@
 library(shiny)
 library(dplyr)
 load("sequence_rules.RDATA")
+load("AR.RDATA")
 
 # Server
 function(input, output) {
   
   output$rules <- renderDataTable({
     
-    dataset <- sequence_rules
+    rules <- get(
+      paste(input$rules, input$item, sep = "_")
+      )
       
-    dataset %>%
+    rules %>%
       filter(
-        between(support  , input$support[1]   , input$support[2]),
-        between(Conf_corr, input$confidence[1], input$confidence[2]),
-        between(lift_corr, input$lift[1]      , input$lift[2]      )
+        between(count     , input$count[1]     , input$count[2]),
+        between(confidence, input$confidence[1], input$confidence[2]),
+        between(lift      , input$lift[1]      , input$lift[2]      )
       )
     
   })

### 2019-01-30 App/ui.R

@@ -13,14 +13,43 @@ fluidPage(
     # Sidebar panel for inputs
     sidebarPanel(
       
+      
+      # Input: button for the type of rules
+      radioButtons(
+        inputId = "rules",
+        label = "Type of rules",
+        choices = c(
+          "Association rules" = "AR",
+          "Sequence rules"    = "SR"
+        ),
+        selected = "AR"
+      ),
+      
+      # Input: button for the type of rules
+      radioButtons(
+        inputId = "item",
+        label   = "Type of item in rules",
+        choices = c(
+          "Course taken"      = "taken",
+          "Failed grade"      = "PF",
+          "Low grade (< 6.5)" = "HL",
+          "Course taken & not taken" = "not_taken"
+          
+        ),
+        selected = "taken"
+      ),
+      
+      # Horizontal line
+      tags$hr(),
+      
       # Input: Slider for the support
       sliderInput(
-        inputId = "support",
-        label = "Support",
-        min   = 0,
-        max   = 1,
-        step  = 0.01,
-        value = c(0, 1)
+        inputId = "count",
+        label = "Count",
+        min   = 5,
+        max   = 150,
+        step  = 1,
+        value = c(5, 150)
         ),
       
       # Input: Slider for the Cconfidence
@@ -33,7 +62,7 @@ fluidPage(
         value = c(0, 1)
       ),
       
-      # Input: Slider for the Cconfidence
+      # Input: Slider for the Confidence
       sliderInput(
         inputId = "lift",
         label = "Lift (corrected)",

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Include different types of AR in shiny app

@@
 ```{r}
-d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
-  left_join(d_transactions, by = c("sequenceID","item")) %>%
+d_transactions_not_taken <- expand.grid(
+
+  # Expand along students (sequenceID) and courses (itemID)
+  sequenceID = unique(d_transactions$sequenceID),
+  item       = unique(d_transactions$item),
+  stringsAsFactors = FALSE
+  ) %>%
+
+  # Join with d_transactions
+  left_join(
+    d_transactions, 
+    by = c("sequenceID", "item")
+    ) %>%
+
+  # Create 
   mutate(
-    Taken= case_when(
+
+    taken = case_when(
       is.na(Grade) ~ "not taken",
-      T             ~ "taken"),
-    item_Taken= paste(item,Taken, sep = "_")
+      TRUE         ~ "taken"),
+
+    item_taken= paste(item, taken, sep = "_")
+
      )
 
-#ARRANGE PROPERLY
-
-d_transactions <- d_transactions_tmp
-
-rm(d_transactions_tmp)
 ```
@@
 transactions_HL    <- make_transaction(item = item_HL)
-transactions_Taken <- make_transaction(item=item_Taken)
+transactions_Taken <- make_transaction(data = d_transactions_not_taken, item = item_taken)
 
@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken,
-     file = "App/ARR.RDATA")
+     file = "App/AR.RDATA")
 
@@
    course_id_fail, course_id_low,
-   AR, AR_PF, AR_HL, AR_Taken)
+   AR_taken, AR_PF, AR_HL, AR_not_taken)
 

### 2019-01-30 App/server.R

@@ -2,7 +2,6 @@
 # Setup
 library(shiny)
 library(dplyr)
-load("sequence_rules.RDATA")
 load("AR.RDATA")
 
 # Server

### 2019-01-30 App/ui.R

@@ -47,9 +47,9 @@ fluidPage(
         inputId = "count",
         label = "Count",
         min   = 5,
-        max   = 150,
+        max   = 1000,
         step  = 1,
-        value = c(5, 150)
+        value = c(5, 1000)
         ),
       
       # Input: Slider for the Cconfidence
@@ -66,17 +66,12 @@ fluidPage(
       sliderInput(
         inputId = "lift",
         label = "Lift (corrected)",
-        min   = -15,
-        max   = 15,
+        min   = 0,
+        max   = 100,
         step  = 0.01,
-        value = c(-10, 10)
-      ),
+        value = c(0, 100)
+      )
       
-      # Horizontal line
-      tags$hr(),
-      
-      # Text
-      helpText("TODO: use logarithmic scale for sliders")
     ),
     
     # Main panel for displaying outputs

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Last touch sequence rules: saves results, removes unnecessary objects and old code

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Generating asocciation rules
-AR_taken <- my_apriori(transactions)
+AR <- my_apriori(transactions)
 
@@
 
-AR_not_taken <- my_apriori(transactions_Taken)
+AR_Taken <- my_apriori(transactions_Taken)
 
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_not_taken,
-     file = "App/ARR.RDATA")
+AR <- list(
+    AR = AR,
+    AR_PF = AR_PF,
+    AR_HL = AR_HL,
+    AR_Taken = AR_Taken
+    )
+
+save(AR, file = "App/AR.RDATA")
 
@@
 ### CSPADE Algorithm
-We apply cspade algorithm
 ```{r}
 # Transform rules from ruleInduction into a readable data frame
-clean_IR <- function(rules){
+n_students <- length(unique(d_transactions$sequenceID))
+
+clean_SR<- function(rules){
+
   rules %>%
     as("data.frame") %>%
-    # filter(
-    #   count >= 1
-    # ) %>%
     mutate(
@@
       rule = str_remove_all(rule, pattern = "[}]"),
-      rule = str_remove_all(rule, pattern = "[>]"),
-      `rhs.support` = confidence / lift
+      rule = str_remove_all(rule, pattern = "[>]")
       ) %>%
     separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
-    mutate_at(
-      c("support", #"lhs.support",
-        "confidence", "rhs.support", "lift"),
-      funs(round(., 5))
-    ) %>%
     select(
@@
       support,
-      #count, lhs.support, #figure out how to get these
-      confidence, rhs.support,
+      confidence,
       lift
-    ) #%>%
-    #arrange(
-    #  desc(count)
-    #)
+    ) %>%
+    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
+    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
+    # Compute statistic
+    group_by(lhs,`RHS Course ID`) %>%
+    mutate(
+      lhs.rhsCourse.support = sum(support),
+      confidence.corr = support / lhs.rhsCourse.support,
+      count = support * n_students,
+      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students
+
+      # TODO: coñpute rhs.support
+      # lift.corr = confidence.corr / rhs.support
+
+  ) %>%
+  ungroup() %>%
+    mutate_at(
+      c("support",
+        "confidence", "lift"),
+      funs(round(., 5))
+    )
 
 }
+
 ```
@@
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
-my_IR <- function(data){
+my_SR<- function(data){
  data %>%
@@
     parameter = list(
-      support = 0.01, # min support of a sequence
+      support = 0, # min support of a sequence
       maxsize = 1, # max number of items of an element of a sequence
@@
       ) %>%
-    clean_IR
+    clean_SR
 }
 
-#Generating induced rules
-IR    <- my_IR(data = sequences   )
-IR_PF <- my_IR(data = sequences_PF)
-IR_HL <- my_IR(data = sequences_HL)
+#Generating sequence rules
+SR   <- my_SR(data = sequences   )
+SR_PF <- my_SR(data = sequences_PF)
+SR_HL <- my_SR(data = sequences_HL)
 
-#Saving induced rules:
-save(
-  IR = list(
-    IR = IR,
-    IR_PF = IR_PF,
-    IR_HL = IR_HL
-    ),
-  file = "Output/IR.RDATA")
+#Saving sequence rules
+SR <- list(
+    SR = SR,
+    SR_PF = SR_PF,
+    SR_HL = SR_HL
+    )
 
-rm(clean_IR, my_IR,
+save(SR, file = "App/SR.RDATA")
+
+#clean unnecessary objects
+rm(clean_SR, my_SR, 
    sequences, sequences_PF, sequences_HL, 
-   IR, IR_PF, IR_HL)
+   n_students,
+   SR, SR_PF, SR_HL)
 
@@
 
-##calculate appropriate measures:
-```{r}
-n_students <- length(unique(d_sequence_transactions$`Student ID`))
-
-sequence_rules <- pass_rules_df %>%
-  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
-  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
-  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>%
-  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
-
-  # Compute statistics
-  group_by(LHS,`RHS Course ID`) %>%
-  mutate(Prob_both = sum(support), 
-         Conf_corr = support/Prob_both,
-         n_rule = support * n_students,
-         n_both =Prob_both * n_students,
-         lift_diff= Conf_corr - Prop_low,
-         lift_corr=Conf_corr / Prop_low) %>%
-  ungroup() %>%
-
-  # Filter and edit output
-  filter(str_detect(`RHS Score`, pattern = "low"),
-         str_detect(`LHS Score`, pattern = "low"),
-         n_rule >= 5,
-         Conf_corr > 0.2) %>%
-  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
-  mutate(support = round(support,3),
-         Prob_both =round(Prob_both,3),
-         Prop_low =round(Prop_low,3),
-         Conf_corr= round(Conf_corr,3),
-         lift_diff= round(lift_diff,3),
-         lift_corr= round(lift_corr,3)) %>%
-  arrange(lift_diff)
-
-```
-##Save data
-```{r}
-save(sequence_rules,
-     file = "sequence_rules.RDATA")
-```
-
-##Arrange data for plots:
-```{r}
-for_plots <-  manual_confidence_rules %>%
-  group_by(LHS)%>%
-  mutate(LHS_count=n())
-```
 #Visualizing rules
@@
          g9  = g8|g9,
-         g10 = g9|g10,
+         g10 = g9|g10
          ) %>%
@@
 ```
-
-##Not ready to move up:

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 # Save association rules
-AR <- list(
-    AR = AR,
-    AR_PF = AR_PF,
-    AR_HL = AR_HL,
-    AR_Taken = AR_Taken
-    )
-
-save(AR, file = "App/AR.RDATA")
+save(AR_taken, AR_PF, AR_HL, AR_not_taken,
+     file = "App/AR.RDATA")
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
nothing, adds space

@@
 ```
-
+#Experiments
 #Visualizing rules
@@
 ```{r}
+
 distributed_transcript <- d_transcript %>%
@@
   #arrange(`Student ID`, `Course ID`)
+
 ```

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Expanded transcripts

@@
 ```
+###Expanded Transcripts
+```{r}
 
+d_transcript_expanded <- d_transcript %>%
+  filter(!is.na(Grade), Grade>=0) %>%
+  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+         Values = T) %>%
+  spread(key = "Round_grade", value = Values) %>%
+  mutate(g1  = g0|g1,
+         g2  = g1|g2,
+         g3  = g2|g3,
+         g4  = g3|g4,
+         g5  = g4|g5,
+         g6  = g5|g6,
+         g7  = g6|g7,
+         g8  = g7|g8,
+         g9  = g8|g9,
+         g10 = g9|g10
+         ) %>%
+  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
+  select(-Gr_bool )%>%
+  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
+  select(-Trash) %>%
+  mutate(Grade= as.numeric(Grade_new))%>%
+  select(-Grade_new) #%>%
+  #to check that the grades appear from original grade to 10.
+  #arrange(`Student ID`, `Course ID`)
+
+#changing to transactions
+
+d_transactions_expanded <- d_course %>%
+
+  # Exclude 
+  filter(
+    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
+    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
+                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
+    ) %>%
+
+  # Join with transcripts.
+  select(- Period) %>%
+  inner_join(d_transcript_expanded, by = "Course ID") %>%
+
+  # Identifying sequences
+  rename(sequenceID = `Student ID`) %>%
+
+  # Identifying time of event (sequence)
+  mutate(
+    Period  = substr(Period, 1, 1),
+    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
+    ) %>%
+
+  # Identifying item
+  mutate(
+    PF = case_when( Grade <  pass_grade ~ "fail",
+                    Grade >= pass_grade ~ "pass"),
+    HL = case_when( Grade <  high_grade ~ "low",
+                    Grade >= high_grade ~ "high"),
+
+    item_PF = paste(`Course ID`, PF, sep = "_"),
+    item_HL = paste(`Course ID`, HL, sep = "_")
+    ) %>%
+  rename(
+    item = `Course ID`
+  ) 
+#%>%
+  #arrange(sequenceID, item) %>%
+  #select(sequenceID, item, Grade, everything())
+```
 ### Transactions for Apriori
@@
 ```
-#Experiments
-#Visualizing rules
-```{r}
-#look at counts
-ggplot(for_plots, aes(LHS))+
-  geom_bar()
-
-#jitter
-ggplot(manual_confidence_rules)+
-  geom_jitter(mapping=aes(x=Conf_corr, y=log(support), color=lift_corr))
-
-ggplot(manual_confidence_rules)+
-  geom_jitter(mapping=aes(x=log(support), y=lift_corr, color = Conf_corr))
-
-#heatmap
-ggplot(select(manual_confidence_rules,LHS,RHS, n_rule), aes(x=RHS,y=LHS, fill=n_rule))+
-  geom_raster() +
-  theme(
-    axis.text.x = element_text(angle=90)
-  )
-
-gglot(table(select(manual_confidence_rules,LHS,RHS)))
-
-#ggnetwork
-
-#SEE: http://kateto.net/network-visualization 
-g_net <- graph_from_data_frame(d=head(for_plots,50), directed=T) #I BELIEVE THE COLUMNS SHOULD BE REVERSED.
-
-l <- layout_in_circle(g_net)
-plot(g_net, #vertex.shape="none",
-     vertex.size=.9,
-     #vertex.label=NA,
-     vertex.label.cex=0.5,
-     edge.arrow.size=.1, 
-     edge.curved=.1,
-     layout=l)
-
-```
-#Visualisation
-It might be a nice idea to visualise using Sankey diagrams, although I don't know if there will be too many courses for it to be meaningful.
-We might need to sample.
-See https://analyzecore.com/2014/10/31/sequence-carts-analysis-sankey/
 
 #EXPERIMENTS:
-
 ##TO MOVE UP (These are ready:)
@@
 NOTE: includes mandatory courses.
-```{r}
-
-distributed_transcript <- d_transcript %>%
-  filter(!is.na(Grade), Grade>=0) %>%
-  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
-         Values = T) %>%
-  spread(key = "Round_grade", value = Values) %>%
-  mutate(g1  = g0|g1,
-         g2  = g1|g2,
-         g3  = g2|g3,
-         g4  = g3|g4,
-         g5  = g4|g5,
-         g6  = g5|g6,
-         g7  = g6|g7,
-         g8  = g7|g8,
-         g9  = g8|g9,
-         g10 = g9|g10
-         ) %>%
-  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
-  select(-Gr_bool )%>%
-  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
-  select(-Trash) %>%
-  mutate(Grade= as.numeric(Grade_new))%>%
-  select(-Grade_new) #%>%
-  #to check that the grades appear from original grade to 10.
-  #arrange(`Student ID`, `Course ID`)
-
-```

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
removes unecessary text
removes objects at the end of expanded transcript chunk

@@
 # Data Exploration
-
 ```{r statistic summary}
@@
   mutate(Grade= as.numeric(Grade_new))%>%
-  select(-Grade_new) #%>%
-  #to check that the grades appear from original grade to 10.
-  #arrange(`Student ID`, `Course ID`)
+  select(-Grade_new)
 
 #changing to transactions
-
 d_transactions_expanded <- d_course %>%
@@
   )
-#%>%
-  #arrange(sequenceID, item) %>%
-  #select(sequenceID, item, Grade, everything())
+
+rm(d_transcript_expanded)
 ```
@@
 ```
-
-#EXPERIMENTS:
-##TO MOVE UP (These are ready:)
-Rounds grades and add new row from original grade up to 10.
-NOTE: includes mandatory courses.

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Text editing

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Setup
-load previous data and create function to find courses
+We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
 ```{r loading data}
@@
 
-Function that returns title of a course given its code.
+We create a function, which, when given the code of a course, returns its title.
 ```{r function find_course}
@@
 # Data Exploration
-
+We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level).
+We save the results in the environment `Transcript Statistics`.
 ```{r statistic summary}
@@
 provide_statistics <- function(data){
+
   data %>%
@@
       Max       = max(Grade), 
-      Mean      = round(mean(Grade), 2), 
+      Mean      = mean(Grade), 
       Median    = median(Grade), 
-      SD        = round(sd(Grade), 2),
-      Fail_rate = round(mean(Fail), 2),
-      Fail_n    = sum(Fail),
-      n         = n()
+      SD        = sd(Grade),
+      `Failure Rate` = mean(Fail),
+      `Failure Count`    = sum(Fail),
+      Count     = n()
+      ) %>%
+    mutate_at(
+      vars(Mean, SD, `Failure Rate`),
+      round,
+      digits = 2
     )
+
 }
@@
      statistics_concentration, statistics_year, statistics_level, file = "Output/Transcript Statistics.RDATA")
+
 rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
@@
 ### CSPADE Algorithm
+We apply cspade algorithm
 ```{r}
 # Transform rules from ruleInduction into a readable data frame
-n_students <- length(unique(d_transactions$sequenceID))
-
-clean_SR<- function(rules){
-
+clean_IR <- function(rules){
   rules %>%
     as("data.frame") %>%
+    # filter(
+    #   count >= 1
+    # ) %>%
     mutate(
@@
       rule = str_remove_all(rule, pattern = "[}]"),
-      rule = str_remove_all(rule, pattern = "[>]")
+      rule = str_remove_all(rule, pattern = "[>]"),
+      `rhs.support` = confidence / lift
       ) %>%
     separate(rule, into = c("lhs", "rhs"), sep="=") %>%
+    mutate_at(
+      c("support", #"lhs.support",
+        "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+    ) %>%
     select(
@@
       support, 
-      confidence,
+      #count, lhs.support, #figure out how to get these
+      confidence, rhs.support,
       lift
-    ) %>%
-    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
-    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
-    # Compute statistic
-    group_by(lhs,`RHS Course ID`) %>%
-    mutate(
-      lhs.rhsCourse.support = sum(support),
-      confidence.corr = support / lhs.rhsCourse.support,
-      count = support * n_students,
-      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students
-
-      # TODO: coñpute rhs.support
-      # lift.corr = confidence.corr / rhs.support
-
-  ) %>%
-  ungroup() %>%
-    mutate_at(
-      c("support",
-        "confidence", "lift"),
-      funs(round(., 5))
-    )
+    ) #%>%
+    #arrange(
+    #  desc(count)
+    #)
 
 }
-
 ```
@@
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
-my_SR<- function(data){
+my_IR <- function(data){
   data %>%
@@
     parameter = list(
-      support = 0, # min support of a sequence
+      support = 0.01, # min support of a sequence
       maxsize = 1, # max number of items of an element of a sequence
@@
       ) %>%
-    clean_SR
+    clean_IR
 }
 
-#Generating sequence rules
-SR   <- my_SR(data = sequences   )
-SR_PF <- my_SR(data = sequences_PF)
-SR_HL <- my_SR(data = sequences_HL)
+#Generating induced rules
+IR    <- my_IR(data = sequences   )
+IR_PF <- my_IR(data = sequences_PF)
+IR_HL <- my_IR(data = sequences_HL)
 
-#Saving sequence rules
-SR <- list(
-    SR = SR,
-    SR_PF = SR_PF,
-    SR_HL = SR_HL
-    )
+#Saving induced rules:
+save(
+  IR = list(
+    IR = IR,
+    IR_PF = IR_PF,
+    IR_HL = IR_HL
+    ),
+  file = "Output/IR.RDATA")
 
-save(SR, file = "App/SR.RDATA")
-
-#clean unnecessary objects
-rm(clean_SR, my_SR, 
+rm(clean_IR, my_IR,
    sequences, sequences_PF, sequences_HL,
-   n_students,
-   SR, SR_PF, SR_HL)
+   IR, IR_PF, IR_HL)
 
 ```
-#Experiments
+
+##calculate appropriate measures:
+```{r}
+n_students <- length(unique(d_sequence_transactions$`Student ID`))
+
+sequence_rules <- pass_rules_df %>%
+  separate(LHS, into=c("LHS Course ID", "LHS Score"), sep="_", remove= FALSE) %>%
+  separate(RHS, into=c("RHS Course ID", "RHS Score"), sep="_", remove= FALSE) %>%
+  mutate(`RHS Course ID`= substr(`RHS Course ID`, start=4, stop=10))%>%
+  left_join(lookup_table, by = c("RHS Course ID"="Course ID")) %>%
+
+  # Compute statistics
+  group_by(LHS,`RHS Course ID`) %>%
+  mutate(Prob_both = sum(support), 
+         Conf_corr = support/Prob_both,
+         n_rule = support * n_students,
+         n_both =Prob_both * n_students,
+         lift_diff= Conf_corr - Prop_low,
+         lift_corr=Conf_corr / Prop_low) %>%
+  ungroup() %>%
+
+  # Filter and edit output
+  filter(str_detect(`RHS Score`, pattern = "low"),
+         str_detect(`LHS Score`, pattern = "low"),
+         n_rule >= 5,
+         Conf_corr > 0.2) %>%
+  select(LHS, RHS, support, n_rule, Prob_both, n_both, Prop_low, Conf_corr, lift_corr, lift_diff) %>%
+  mutate(support = round(support,3),
+         Prob_both =round(Prob_both,3),
+         Prop_low =round(Prop_low,3),
+         Conf_corr= round(Conf_corr,3),
+         lift_diff= round(lift_diff,3),
+         lift_corr= round(lift_corr,3)) %>%
+  arrange(lift_diff)
+
+```
+##Save data
+```{r}
+save(sequence_rules,
+     file = "sequence_rules.RDATA")
+```
+
+##Arrange data for plots:
+```{r}
+for_plots <-  manual_confidence_rules %>%
+  group_by(LHS)%>%
+  mutate(LHS_count=n())
+```
 #Visualizing rules
@@
 ```{r}
-
 distributed_transcript <- d_transcript %>%
@@
          g9  = g8|g9,
-         g10 = g9|g10
+         g10 = g9|g10,
          ) %>%
@@
   #arrange(`Student ID`, `Course ID`) 
+```
 
-```
+##Not ready to move up:

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
finish cleaning ready for KNIT

--- 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-```{r library, message = F}
+```{r library, message = FALSE, warning = FALSE}
 library(arulesSequences)
@@
 ### Adding not taken courses
-```{r}
+```{r transactions not taken}
 d_transactions_not_taken <- expand.grid(
@@
 ###Expanded Transcripts
-```{r}
+```{r transactions expanded}
 
-d_transcript_expanded <- d_transcript %>%
-  filter(!is.na(Grade), Grade>=0) %>%
-  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
+d_transactions_expanded <- d_transactions %>%
+  mutate(Round_grade = round(Grade, 0),
          Values = T) %>%
   spread(key = "Round_grade", value = Values) %>%
-  mutate(g1  = g0|g1,
-         g2  = g1|g2,
-         g3  = g2|g3,
-         g4  = g3|g4,
-         g5  = g4|g5,
-         g6  = g5|g6,
-         g7  = g6|g7,
-         g8  = g7|g8,
-         g9  = g8|g9,
-         g10 = g9|g10
+  mutate(`1`  = `0`|`1`,
+         `2`  = `1`|`2`,
+         `3`  = `2`|`3`,
+         `4`  = `3`|`4`,
+         `5`  = `4`|`5`,
+         `6`  = `5`|`6`,
+         `7`  = `6`|`7`,
+         `8`  = `7`|`8`,
+         `9`  = `8`|`9`,
+         `10`  = `9`|`10`
          ) %>%
-  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
-  select(-Gr_bool )%>%
-  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
-  select(-Trash) %>%
-  mutate(Grade= as.numeric(Grade_new))%>%
-  select(-Grade_new)
-
-#changing to transactions
-d_transactions_expanded <- d_course %>%
-
-  # Exclude 
-  filter(
-    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
-    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
-                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
-    ) %>%
-
-  # Join with transcripts.
-  select(- Period) %>%
-  inner_join(d_transcript_expanded, by = "Course ID") %>%
-
-  # Identifying sequences
-  rename(sequenceID = `Student ID`) %>%
-
-  # Identifying time of event (sequence)
-  mutate(
-    Period  = substr(Period, 1, 1),
-    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
+  gather(key = "Grade_round", value = "Gr_bool", `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, na.rm = TRUE, convert = TRUE) %>%
+  select(-Gr_bool) %>%
+  arrange(
+    sequenceID,
+    item
   ) %>%
@@
   mutate(
-    PF = case_when( Grade <  pass_grade ~ "fail",
-                    Grade >= pass_grade ~ "pass"),
-    HL = case_when( Grade <  high_grade ~ "low",
-                    Grade >= high_grade ~ "high"),
+    PF = case_when( Grade_round <  pass_grade ~ "fail",
+                    Grade_round >= pass_grade ~ "pass"),
+    HL = case_when( Grade_round <  high_grade ~ "low",
+                    Grade_round >= high_grade ~ "high"),
 
-    item_PF = paste(`Course ID`, PF, sep = "_"),
-    item_HL = paste(`Course ID`, HL, sep = "_")
-    ) %>%
-  rename(
-    item = `Course ID`
+    item_PF = paste(item, PF, sep = "_"),
+    item_HL = paste(item, HL, sep = "_")
     )
-
-rm(d_transcript_expanded)
 ```
@@
 
+transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
+transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
+transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
+
 #
@@
 ### Sequences for CSPADE
-```{r}
+```{r making sequences}
 
@@
 
+sequences_expanded     <- make_sequence(data = d_transactions_expanded, item = item)
+sequences_expanded_PF  <- make_sequence(data = d_transactions_expanded, item = item_PF)
+sequences_expanded_HL  <- make_sequence(data = d_transactions_expanded, item = item_HL)
+
 #
@@
 ### Apriori Algorithm
-```{r}
+```{r function clean AR}
 
@@
 
+AR_expanded <- my_apriori(transactions_expanded)
+# creating vector of fail course
+course_id_fail <- d_transactions_expanded %>%
+  filter(PF == "fail") %>%
+  distinct(`item_PF`)
+
+AR_expanded_PF <- my_apriori(transactions_expanded_PF,
+                    appearance = list(both = course_id_fail$`item_PF`))
+
+# creating vector of low score course
+course_id_low <- d_transactions_expanded %>%
+  filter(HL == "low") %>%
+  distinct(`item_HL`)
+
+AR_expanded_HL <- my_apriori(transactions_expanded_HL,
+                    appearance = list(both = course_id_low$`item_HL`))
+
 #
@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
+     AR_expanded, AR_expanded_PF, AR_expanded_HL,
      file = "App/AR.RDATA")
@@
    course_id_fail, course_id_low,
-   AR_taken, AR_PF, AR_HL, AR_not_taken)
+   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded, AR_expanded_PF, AR_expanded_HL)
 
@@
 ### CSPADE Algorithm
-```{r}
+```{r function clean SR}
 # Transform rules from ruleInduction into a readable data frame
@@
 We apply cspade followed by rule induction
-```{r}
+```{r cspade and rule induction, cache = TRUE}
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
@@
 
+SR_expanded   <- my_SR(data = sequences_expanded   )
+SR_expanded_PF <- my_SR(data = sequences_expanded_PF)
+SR_expanded_HL <- my_SR(data = sequences_expanded_HL)
 #Saving sequence rules
@@
     SR_PF = SR_PF,
-    SR_HL = SR_HL
+    SR_HL = SR_HL,
+
+    SR_expanded    = SR_expanded,
+    SR_expanded_PF = SR_expanded_PF,
+    SR_expanded_HL = SR_expanded_HL
     )
@@
    sequences, sequences_PF, sequences_HL,
+   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL,
    n_students,
-   SR, SR_PF, SR_HL)
+   SR, SR_PF, SR_HL,
+   SR_expanded, SR_expanded_PF, SR_expanded_HL)
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 # Data Exploration
+
+We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level).
+We save the results in the environment `Transcript Statistics`.
+
 ```{r statistic summary}

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
SR save change

@@
 #Saving sequence rules
-SR <- list(
+save(
     SR = SR,
@@
     SR_expanded_PF = SR_expanded_PF,
-    SR_expanded_HL = SR_expanded_HL
-    )
+    SR_expanded_HL = SR_expanded_HL,
 
-save(SR, file = "App/SR.RDATA")
+    file = "App/SR.RDATA")
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
AR expanded taken

@@
 
-AR_expanded <- my_apriori(transactions_expanded)
+AR_expanded_taken <- my_apriori(transactions_expanded)
 # creating vector of fail course
@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
-     AR_expanded, AR_expanded_PF, AR_expanded_HL,
+     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
      file = "App/AR.RDATA")
@@
    course_id_fail, course_id_low,
-   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded, AR_expanded_PF, AR_expanded_HL)
+   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
 

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
SR expanded_taken renamed

@@
 #Generating sequence rules
-SR   <- my_SR(data = sequences   )
+SR_taken   <- my_SR(data = sequences   )
 SR_PF      <- my_SR(data = sequences_PF)
@@
 
-SR_expanded   <- my_SR(data = sequences_expanded   )
+SR_expanded_taken   <- my_SR(data = sequences_expanded   )
 SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)
@@
 save(
-    SR = SR,
-    SR_PF = SR_PF,
-    SR_HL = SR_HL,
+    SR_taken, SR_PF, SR_HL,
 
-    SR_expanded    = SR_expanded,
-    SR_expanded_PF = SR_expanded_PF,
-    SR_expanded_HL = SR_expanded_HL,
+    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL,
 
@@
    n_students,
-   SR, SR_PF, SR_HL,
-   SR_expanded, SR_expanded_PF, SR_expanded_HL)
+   SR_taken, SR_PF, SR_HL,
+   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)
 

### 2019-01-30 App/server.R
include more chocies for button "item"

@@ -3,6 +3,7 @@
 library(shiny)
 library(dplyr)
 load("AR.RDATA")
+load("SR.RDATA")
 
 # Server
 function(input, output) {

### 2019-01-30 App/ui.R

@@ -30,10 +30,13 @@ fluidPage(
         inputId = "item",
         label   = "Type of item in rules",
         choices = c(
-          "Course taken"      = "taken",
-          "Failed grade"      = "PF",
-          "Low grade (< 6.5)" = "HL",
-          "Course taken & not taken" = "not_taken"
+          "Course taken"                = "taken",
+          "Failed grade"                = "PF",
+          "Low grade (< 6.5)"           = "HL",
+          "Course taken & not taken"    = "not_taken",
+          "Expanded"                    = "expanded_taken",
+          "Expanded (Failed grade)"     = "expanded_PF",
+          "Expanded (low grade (< 6.5)" = "expanded_PF"
           
         ),
         selected = "taken"

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
knit updated
to do list

@@
 ### CSPADE Algorithm
+##TODO: FILTER FAILS AND LOW GRADE
+Change name confidence corrected to confidence, confidence to confidence old, same for lift
 ```{r function clean SR}
@@
 We apply cspade followed by rule induction
-```{r cspade and rule induction, cache = TRUE}
+```{r cspade and rule induction, cache = F}
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
renames confidenc.corr, and lift for the app. Also adds filters for pass/fail, low/high on the rhs

@@
 ### CSPADE Algorithm
-##TODO: FILTER FAILS AND LOW GRADE
-Change name confidence corrected to confidence, confidence to confidence old, same for lift
+##TODO: FILTER FAILS AND LOW GRADE, paste item: e.g."COR1002_8"
+
 ```{r function clean SR}
@@
     group_by(lhs,`RHS Course ID`) %>%
+    rename(confidence = "confidence.old", lift="lift.old")%>%
     mutate(
       lhs.rhsCourse.support = sum(support),
-      confidence.corr = support / lhs.rhsCourse.support,
+      confidence = support / lhs.rhsCourse.support,
       count = support * n_students,
@@
 
-      # TODO: coñpute rhs.support
-      # lift.corr = confidence.corr / rhs.support
+      # TODO: compute rhs.support
+      # lift = confidence.corr / rhs.support
 
@@
       c("support",
-        "confidence", "lift"),
+        "confidence","confidence.old", "lift.old"),
       funs(round(., 5))
@@
 }
+# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
+# creating vector of fail course
+course_id_fail <- d_transactions %>%
+  filter(PF == "fail") %>%
+  distinct(`item_PF`)
 
-#Generating sequence rules
+AR_PF <- my_apriori(transactions_PF,
+                    appearance = list(both = course_id_fail$`item_PF`))
+
+# creating vector of low score course
+course_id_low <- d_transactions %>%
+  filter(HL == "low") %>%
+  distinct(`item_HL`)
+
+AR_HL <- my_apriori(transactions_HL,
+                    appearance = list(both = course_id_low$`item_HL`))
+# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
+#Generating sequence rules:
 SR_taken   <- my_SR(data = sequences   )
-SR_PF      <- my_SR(data = sequences_PF)
-SR_HL      <- my_SR(data = sequences_HL)
+#pass/fail filter
+SR_PF      <- my_SR(data = sequences_PF) %>% 
+  filter(`RHS Quality`=="fail")
+#high/low filter
+SR_HL      <- my_SR(data = sequences_HL)%>% 
+  filter(`RHS Quality`=="low")
 
 SR_expanded_taken   <- my_SR(data = sequences_expanded   )
-SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)
-SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)
+SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% 
+  filter(`RHS Quality`=="fail")
+SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% 
+  filter(`RHS Quality`=="low")
 #Saving sequence rules

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
adds item_grade, e.g. "COR1002_8"

@@
     item_PF = paste(`Course ID`, PF, sep = "_"),
-    item_HL = paste(`Course ID`, HL, sep = "_")
+    item_HL = paste(`Course ID`, HL, sep = "_"),
+    item_Grade = paste(`Course ID`, Grade, sep = "_")
     ) %>%
@@
     item_PF = paste(item, PF, sep = "_"),
-    item_HL = paste(item, HL, sep = "_")
+    item_HL = paste(item, HL, sep = "_"),
+    item_Grade = paste(item, Grade_round, sep = "_")
     )
@@
 ### CSPADE Algorithm
-##TODO: FILTER FAILS AND LOW GRADE, paste item: e.g."COR1002_8"
+##TODO:paste item: e.g."COR1002_8"
 

### 2019-01-31 App/ui.R
include explanation on confidence and lift

@@ -73,7 +73,17 @@ fluidPage(
         max   = 100,
         step  = 0.01,
         value = c(0, 100)
-      )
+      ),
+      
+      # Horizontal line
+      tags$hr(),
+      
+      # Text
+      helpText("For rules concerning failed courses or course with low grade, we compute the confidence and lift in the following way:"),
+      helpText("Confidence(A_fail -> B_fail) = P( (A_fail -> B_fail) | (A_fail -> B) ). In other words, given a student has failed course A and is taking course B, what is the probability that (s)he will fail course B"),
+      helpText("Lift(A_fail - B_fail) = Confidence(A_fail -> B_fail) / Probability(B_fail | B). In other words, we compare the confidence of the rule and the probability of failing course_B *given we take course B*.")
+      
+      
       
     ),
     

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 transactions_HL               <- make_transaction(item = item_HL)
+transactions_Grade            <- make_transaction(item = item_Grade)
 transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)
@@
 transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
+transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
 
@@
 sequences_HL       <- make_sequence(item = item_HL)
+sequences_Grade    <- make_sequence(item = item_Grade)
 
@@
 sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
+sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)
 
@@
 rm(clean_AR, my_apriori,
-   transactions, transactions_PF, transactions_HL,
+   transactions, transactions_PF, transactions_HL, transactions_Grade,
    course_id_fail, course_id_low,
@@
 ### CSPADE Algorithm
-##TODO:paste item: e.g."COR1002_8"
+##TODO: add AR_grade, SR_grade
 
@@
 rm(clean_SR, my_SR, 
-   sequences, sequences_PF, sequences_HL,
-   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL,
+   sequences, sequences_PF, sequences_HL, sequences_Grade,
+   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
    n_students,

### 2019-01-31 App/ui.R
editing

@@ -58,7 +58,7 @@ fluidPage(
       # Input: Slider for the Cconfidence
       sliderInput(
         inputId = "confidence",
-        label = "Confidence (corrected)",
+        label = "Confidence",
         min   = 0,
         max   = 1,
         step  = 0.01,
@@ -68,7 +68,7 @@ fluidPage(
       # Input: Slider for the Confidence
       sliderInput(
         inputId = "lift",
-        label = "Lift (corrected)",
+        label = "Lift",
         min   = 0,
         max   = 100,
         step  = 0.01,
@@ -82,8 +82,6 @@ fluidPage(
       helpText("For rules concerning failed courses or course with low grade, we compute the confidence and lift in the following way:"),
       helpText("Confidence(A_fail -> B_fail) = P( (A_fail -> B_fail) | (A_fail -> B) ). In other words, given a student has failed course A and is taking course B, what is the probability that (s)he will fail course B"),
       helpText("Lift(A_fail - B_fail) = Confidence(A_fail -> B_fail) / Probability(B_fail | B). In other words, we compare the confidence of the rule and the probability of failing course_B *given we take course B*.")
-      
-      
       
     ),
     

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
corrects bug in rename. Rounds grades for item_Grade

@@
     item_HL = paste(`Course ID`, HL, sep = "_"),
-    item_Grade = paste(`Course ID`, Grade, sep = "_")
+    item_Grade = paste(`Course ID`, round(Grade,0), sep = "_")
     ) %>%
@@
 # Checking transactions
-#inspect(head(transactions, 10))
+#inspect(head(transactions_Grade, 10))
 
@@
     group_by(lhs,`RHS Course ID`) %>%
-    rename(confidence = "confidence.old", lift="lift.old")%>%
+    rename(confidence.old = "confidence", lift.old="lift")%>%
     mutate(
@@
 }
-# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
-# creating vector of fail course
-course_id_fail <- d_transactions %>%
-  filter(PF == "fail") %>%
-  distinct(`item_PF`)
 
-AR_PF <- my_apriori(transactions_PF,
-                    appearance = list(both = course_id_fail$`item_PF`))
-
-# creating vector of low score course
-course_id_low <- d_transactions %>%
-  filter(HL == "low") %>%
-  distinct(`item_HL`)
-
-AR_HL <- my_apriori(transactions_HL,
-                    appearance = list(both = course_id_low$`item_HL`))
-# <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- <- 
 #Generating sequence rules:
 SR_taken   <- my_SR(data = sequences   )
-#pass/fail filter
+
+##pass/fail filter
 SR_PF      <- my_SR(data = sequences_PF) %>% 
   filter(`RHS Quality`=="fail")
-#high/low filter
+
+##high/low filter
 SR_HL      <- my_SR(data = sequences_HL)%>% 
@@
 SR_expanded_taken   <- my_SR(data = sequences_expanded   )
+##pass/fail filter
 SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% 
   filter(`RHS Quality`=="fail")
+##high/low filter
 SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% 
   filter(`RHS Quality`=="low")
+
 #Saving sequence rules

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
restructures into smaller chunks

@@
 We apply Apriori algorithm:
-```{r AR apriori}
-
+```{r my_apriori function}
 # Run the apriori algorithm with desired parameters
@@
 }
+```
 
-#
+```{r AR apriori}
+
 # Generating asocciation rules
@@
 
+```
+We save and remove objects:
+```{r saving and rm}
 #
@@
 
+# Remove objects
 rm(clean_AR, my_apriori,
@@
    AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
-
 ```
@@
 We apply cspade followed by rule induction
-```{r cspade and rule induction, cache = F}
+```{r my_SR function}
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
@@
 }
+```
 
+We generate sequence rules:
+```{r cspade and rule induction, cache = F}
 #Generating sequence rules:
@@
 
+```
+We save and remove objects:
+```{r saving and rm SR}
 #Saving sequence rules

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
finish adding grades. updated RDATA files

@@
 
+AR_Grade <- my_apriori(transactions_Grade)
+
 AR_not_taken <- my_apriori(transactions_Taken)
@@
 
+AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
+
 ```
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_not_taken, 
-     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL,
+save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
+     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade,
      file = "App/AR.RDATA")
@@
    course_id_fail, course_id_low,
-   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)
+   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
+   AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade)
 ```
@@
 
+SR_Grade   <- my_SR(data = sequences_Grade )
+
 SR_expanded_taken   <- my_SR(data = sequences_expanded   )
@@
 
+SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
+
 ```
@@
 save(
-    SR_taken, SR_PF, SR_HL,
+    SR_taken, SR_PF, SR_HL, SR_Grade,
 
-    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL,
+    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade,
 
@@
    n_students,
-   SR_taken, SR_PF, SR_HL,
-   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)
+   SR_taken, SR_PF, SR_HL, SR_Grade,
+   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade)
 

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
update to do list
corrects lift and confidence for app

@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade,
+     AR_expanded_taken, 
+     #AR_expanded_PF, AR_expanded_HL, 
+     AR_expanded_Grade,
      file = "App/AR.RDATA")
@@
    AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-   AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade)
+   AR_expanded_taken, 
+   #AR_expanded_PF, AR_expanded_HL, 
+   AR_expanded_Grade)
 ```
@@
 ### CSPADE Algorithm
-##TODO: add AR_grade, SR_grade
+##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail,
 
@@
     group_by(lhs,`RHS Course ID`) %>%
-    rename(confidence.old = "confidence", lift.old="lift")%>%
     mutate(
@@
       count = support * n_students,
-      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students
-
+      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
+      lift = NA
       # TODO: compute rhs.support
@@
 
-    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade,
+    SR_expanded_taken, 
+    #SR_expanded_PF, SR_expanded_HL, 
+    SR_expanded_Grade,
 
@@
    sequences, sequences_PF, sequences_HL, sequences_Grade,
-   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
+   sequences_expanded, 
+   #sequences_expanded_PF, sequences_expanded_HL, 
+   sequences_expanded_Grade,
    n_students,
    SR_taken, SR_PF, SR_HL, SR_Grade,
-   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade)
+   SR_expanded_taken, 
+  # SR_expanded_PF, SR_expanded_HL, 
+   SR_expanded_Grade)
 

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
removes ._expanded_PF and ._expanded_HL

@@
 transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
-transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
-transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
+#transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
+#transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
 transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
@@
 sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
-sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
-sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
+#sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
+#sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
 sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)
@@
 # creating vector of fail course
-course_id_fail <- d_transactions_expanded %>%
-  filter(PF == "fail") %>%
-  distinct(`item_PF`)
-
-AR_expanded_PF <- my_apriori(transactions_expanded_PF,
-                    appearance = list(both = course_id_fail$`item_PF`))
+#course_id_fail <- d_transactions_expanded %>%filter(PF == "fail") %>%distinct(`item_PF`)
+#AR_expanded_PF <- my_apriori(transactions_expanded_PF,appearance = list(both = course_id_fail$`item_PF`))
 
 # creating vector of low score course
-course_id_low <- d_transactions_expanded %>%
-  filter(HL == "low") %>%
-  distinct(`item_HL`)
-
-AR_expanded_HL <- my_apriori(transactions_expanded_HL,
-                    appearance = list(both = course_id_low$`item_HL`))
+#course_id_low <- d_transactions_expanded %>%filter(HL == "low") %>%distinct(`item_HL`)
+#AR_expanded_HL <- my_apriori(transactions_expanded_HL, appearance = list(both = course_id_low$`item_HL`))
 
@@
 ##pass/fail filter
-SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% 
-  filter(`RHS Quality`=="fail")
+#SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% filter(`RHS Quality`=="fail")
 ##high/low filter
-SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% 
-  filter(`RHS Quality`=="low")
+#SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% filter(`RHS Quality`=="low")
 

### 2019-01-31 App/ui.R
editing

@@ -1,18 +1,15 @@
 
-# Setup
-library(shiny)
 
 fluidPage(
   
   # App title
-  titlePanel("Sequence Rules"),
+  titlePanel("Association Rules and Sequence Rules"),
   
   # Sidebar layout
   sidebarLayout(
     
     # Sidebar panel for inputs
     sidebarPanel(
-      
       
       # Input: button for the type of rules
       radioButtons(

### 2019-01-31 App/server.R
editing

@@ -11,13 +11,15 @@ function(input, output) {
   output$rules <- renderDataTable(
     
     expr = {
-      rules <- get(
-        paste(input$rules, input$item, sep = "_")
-        )
       
-      rules %>%
+      # Use chosen data set
+      get(
+        paste(input$rules, input$item, sep = "_")
+        ) %>%
+        
+        # filter rows based on the ranges of the three buttons
         filter(
-          between(count     , input$count[1]     , input$count[2]),
+          between(count     , input$count[1]     , input$count[2]     ),
           between(confidence, input$confidence[1], input$confidence[2]),
           between(lift      , input$lift[1]      , input$lift[2]      )
         )
@@ -28,6 +30,7 @@ function(input, output) {
       pageLength = 10,
       lengthMenu = c(10, 25, 50, 100)
       )
+    
     )
   
   

### 2019-01-31 App/ui.R

@@ -1,5 +1,4 @@
 
-
 fluidPage(
   
   # App title

### 2019-01-31 App/server.R
editing

@@ -1,10 +1,14 @@
 
+
+#
 # Setup
 library(shiny)
 library(dplyr)
 load("AR.RDATA")
 load("SR.RDATA")
 
+
+#
 # Server
 function(input, output) {
   
@@ -32,6 +36,5 @@ function(input, output) {
       )
     
     )
-  
   
 }

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 
-transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
+#transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
 #transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
@@
 
-sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
+#sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
 #sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
@@
 
-AR_expanded_taken <- my_apriori(transactions_expanded)
+#AR_expanded_taken <- my_apriori(transactions_expanded)
 # creating vector of fail course
@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-     AR_expanded_taken, 
+     #AR_expanded_taken, 
      #AR_expanded_PF, AR_expanded_HL, 
@@
    AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-   AR_expanded_taken, 
+   #AR_expanded_taken, 
    #AR_expanded_PF, AR_expanded_HL, 
@@
       c("support",
-        "confidence","confidence.old", "lift.old"),
+        "confidence", "lift"),
       funs(round(., 5))
@@
 
-SR_expanded_taken   <- my_SR(data = sequences_expanded   )
+#SR_expanded_taken   <- my_SR(data = sequences_expanded   )
 ##pass/fail filter
@@
 
-    SR_expanded_taken, 
+    #SR_expanded_taken, 
     #SR_expanded_PF, SR_expanded_HL, 
@@
    sequences, sequences_PF, sequences_HL, sequences_Grade,
-   sequences_expanded, 
+   #sequences_expanded, 
    #sequences_expanded_PF, sequences_expanded_HL, 
@@
    SR_taken, SR_PF, SR_HL, SR_Grade,
-   SR_expanded_taken, 
+   #SR_expanded_taken, 
   # SR_expanded_PF, SR_expanded_HL, 

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
sequences lift=1

@@
       lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
-      lift = NA
+      lift = 1 #dummy variable
       # TODO: compute rhs.support

### 2019-01-31 App/ui.R
editing

@@ -26,11 +26,11 @@ fluidPage(
         inputId = "item",
         label   = "Type of item in rules",
         choices = c(
-          "Course taken"                = "taken",
-          "Failed grade"                = "PF",
-          "Low grade (< 6.5)"           = "HL",
-          "Grade"                       = "Grade",
-          "Course taken & not taken"    = "not_taken"
+          "Taken"                    = "taken",
+          "Failed grade"             = "PF",
+          "Low grade (< 6.5)"        = "HL",
+          "Grade (grade x or lower)" = "expanded_Grade",
+          "Taken & not taken"        = "not_taken"
         ),
         selected = "taken"
       ),
@@ -43,9 +43,9 @@ fluidPage(
         inputId = "count",
         label = "Count",
         min   = 5,
-        max   = 1000,
+        max   = 1500,
         step  = 1,
-        value = c(5, 1000)
+        value = c(5, 1500)
         ),
       
       # Input: Slider for the Cconfidence

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
@@
       lhs.rhsCourse.support = sum(support),
-      confidence = support / lhs.rhsCourse.support,
+      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
+                             T ~ (support / lhs.rhsCourse.support)),
       count = support * n_students,
       lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
-      lift = NA
+      lift = 1 #dummy variable
       # TODO: compute rhs.support

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
update knitted- filters rhs-lhs course different grade

@@
 
-```{r AR apriori}
+```{r AR apriori, cache = TRUE}
 
@@
 We generate sequence rules:
-```{r cspade and rule induction, cache = F}
+```{r SR taken, cache = TRUE}
 #Generating sequence rules:
 SR_taken   <- my_SR(data = sequences   )
+```
 
+```{r SR PF, cache = TRUE}
 ##pass/fail filter
@@
   filter(`RHS Quality`=="fail")
+```
 
+```{r SR HL, cache = TRUE}
 ##high/low filter
@@
   filter(`RHS Quality`=="low")
+```
 
+```{r SR grade, cache = TRUE}
 SR_Grade   <- my_SR(data = sequences_Grade )
+```
+
+```{r SR grade exp, cache = TRUE}
+#Grades filter 
+SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade ) %>%
+  filter(!`LHS Course ID`==`RHS Course ID`)
+```
+
+```{r cspade and rule induction, cache = F}
 
@@
 
-SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
+```
 
-```
 We save and remove objects:

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
delets lhs rhs columns (not executed)

@@
 ### CSPADE Algorithm
-##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail,
+##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
 
@@
       # lift = confidence.corr / rhs.support
-
      ) %>%
@@
       funs(round(., 5))
-    )
+    ) %>%
+    filter(!`LHS Course ID`==`RHS Course ID`) %>%
+    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
 
@@
 SR_PF      <- my_SR(data = sequences_PF) %>% 
-  filter(`RHS Quality`=="fail")
+  filter(str_detect(rhs,"fail"))
 ```
@@
 SR_HL      <- my_SR(data = sequences_HL)%>% 
-  filter(`RHS Quality`=="low")
+  filter(str_detect(rhs,"low"))
 ```
@@
 #Grades filter 
-SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade ) %>%
-  filter(!`LHS Course ID`==`RHS Course ID`)
+SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
 ```
@@
    SR_expanded_Grade)
-
 ```

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
Deletes commented out sections of AR and SR

@@
 
-#transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
-#transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
-#transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
 transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
@@
 
-#sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
-#sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
-#sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
 sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)
@@
 
-#AR_expanded_taken <- my_apriori(transactions_expanded)
-# creating vector of fail course
-#course_id_fail <- d_transactions_expanded %>%filter(PF == "fail") %>%distinct(`item_PF`)
-#AR_expanded_PF <- my_apriori(transactions_expanded_PF,appearance = list(both = course_id_fail$`item_PF`))
-
-# creating vector of low score course
-#course_id_low <- d_transactions_expanded %>%filter(HL == "low") %>%distinct(`item_HL`)
-#AR_expanded_HL <- my_apriori(transactions_expanded_HL, appearance = list(both = course_id_low$`item_HL`))
-
 AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
@@
 save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-     #AR_expanded_taken, 
-     #AR_expanded_PF, AR_expanded_HL, 
      AR_expanded_Grade,
@@
    AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade,  
-   #AR_expanded_taken, 
-   #AR_expanded_PF, AR_expanded_HL, 
    AR_expanded_Grade)
@@
 
-```{r cspade and rule induction, cache = F}
-
-#SR_expanded_taken   <- my_SR(data = sequences_expanded   )
-##pass/fail filter
-#SR_expanded_PF      <- my_SR(data = sequences_expanded_PF)%>% filter(`RHS Quality`=="fail")
-##high/low filter
-#SR_expanded_HL      <- my_SR(data = sequences_expanded_HL)%>% filter(`RHS Quality`=="low")
-
-```
-
 We save and remove objects:
@@
     SR_taken, SR_PF, SR_HL, SR_Grade,
-
-    #SR_expanded_taken, 
-    #SR_expanded_PF, SR_expanded_HL, 
     SR_expanded_Grade,
-
     file = "App/SR.RDATA")
@@
    sequences, sequences_PF, sequences_HL, sequences_Grade,
-   #sequences_expanded, 
-   #sequences_expanded_PF, sequences_expanded_HL, 
    sequences_expanded_Grade,
@@
    SR_taken, SR_PF, SR_HL, SR_Grade,
-   #SR_expanded_taken, 
-  # SR_expanded_PF, SR_expanded_HL, 
+
    SR_expanded_Grade)

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
knit results

@@
 
-    item_taken= paste(item, taken, sep = "_")
+    item_taken= paste(item, taken, sep = "_"),
+    item_taken_grade= case_when(
+      is.na(Grade) ~ paste(item, taken, sep = "_"),
+      T            ~ paste(item, PF)
+    )
 
@@
 ```{r SR taken, cache = TRUE}
+
 #Generating sequence rules:
@@
 ```{r SR PF, cache = TRUE}
+
 ##pass/fail filter
@@
 ```{r SR HL, cache = TRUE}
+
 ##high/low filter
@@
 ```{r SR grade, cache = TRUE}
+
 SR_Grade   <- my_SR(data = sequences_Grade )
@@
 ```{r SR grade exp, cache = TRUE}
+
 #Grades filter 

### 2019-01-31 Pillar 2 - Topic Modeling.Rmd
minor editing

@@
 ```{r import data}
-load("data_pillar_2.RDATA")
+load("output/data_pillar_2.RDATA")
+
+# Only keep course descriptions and overviews from most recent year
+d_description <- d_description %>%
+  filter(
+    `Academic Year` == "2018-2019"
+  )
+
+d_overview <- d_overview %>%
+  filter(
+    `Academic Year` == "2018-2019"
+  )
 ```
@@
 ```{r compute_tf_idf, cache = TRUE}
-compute_tf_idf <- function(data) data %>%
-                                   count(`Course ID`, word) %>%
-                                   bind_tf_idf(term = word, document = `Course ID`, n = n)
+compute_tf_idf <- function(data){
 
-tf_idf_description <- compute_tf_idf(filter(d_description, `Academic Year` == "2018-2019"))
-tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Academic Year` == "2018-2019"))
+  data %>%
+    count(
+      `Course ID`,
+      word
+      ) %>%
+    bind_tf_idf(
+      term = word, 
+      document = `Course ID`,
+      n = n
+      )
+
+}
+
+tf_idf_description <- compute_tf_idf(d_description)
+tf_idf_overview    <- compute_tf_idf(d_overview)
 tf_idf_manual      <- compute_tf_idf(d_manual)
@@
 
+  #
   # Barplot
   g <- data %>%
-    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
-    geom_col(show.legend = F) +
-    labs(x = NULL, y = "tf-idf") +
+    ggplot(
+      aes(
+        x = reorder_within(word, tf_idf, facet), 
+        y = tf_idf
+        )
+      ) +
+    geom_col(
+      show.legend = FALSE
+      ) +
+    labs(
+      x = NULL,
+      y = "tf-idf"
+      ) +
     scale_x_reordered() +
-    facet_wrap(~ facet, scales = "free", ncol = n_col) +
+    facet_wrap(
+      facets = ~ facet, 
+      scales = "free",
+      ncol = n_col
+      ) +
     coord_flip()
 
-  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)
+  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
 
+  #
   # Word Cloud
   g <- data %>%
-    group_by(facet) %>%
-      mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
-    ggplot(aes(size = freq^0.7, label = word, color = freq^0.7)) +
-    geom_text_wordcloud_area(area_corr_power = 1,
+    group_by(
+      facet
+      ) %>%
+    mutate(
+      freq = tf_idf / sum(tf_idf)
+      ) %>% # normalization within facet
+    ggplot(
+      aes(
+        size = freq ^ 0.7, 
+        label = word, 
+        color = freq ^ 0.7
+        )
+      ) +
+    geom_text_wordcloud_area(
+      area_corr_power = 1,
       eccentricity    = 1,
-                             rm_outside      = T) +
-    scale_radius(range = c(2, 10), limits = c(0, NA)) +
-    scale_color_gradient(low = "red", high = "blue") +
-    facet_wrap(~ facet, ncol = n_col) + 
+      rm_outside      = T
+      ) +
+    scale_radius(
+      range = c(2, 10),
+      limits = c(0, NA)
+      ) +
+    scale_color_gradient(
+      low = "red", 
+      high = "blue"
+      ) +
+    facet_wrap(
+      facet = ~ facet,
+      ncol = n_col
+      ) + 
     theme(
@@
       panel.background = element_rect(fill = "white"),
-      plot.title       = element_text(hjust=0.5)
+      plot.title       = element_text(hjust = 0.5)
     )
 
-  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)
+  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
 
@@
 ```{r tf-idf course, cache = TRUE}
-prepare_tf_idf_course <- function(data) data %>%
-                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
-                                          rename(facet = `Course ID`) %>%
-                                          group_by(facet) %>%
-                                            filter(n >= 2) %>%
-                                            top_n(10, tf_idf) %>%
-                                          ungroup
+prepare_tf_idf_course <- function(data){
+
+  data %>%
+
+    # Selection 25 courses randomly
+    filter(
+      `Course ID` %in% sample(
+        x = unique(.$`Course ID`),
+        size = 25, 
+        replace = FALSE
+        )
+      ) %>%
+
+    # Select top 10 words per course 
+    group_by(
+      `Course ID`
+      ) %>%
+    filter(
+      n >= 2
+      ) %>%
+    top_n(
+      n = 10,
+      wt = tf_idf
+      ) %>%
+    ungroup %>%
+
+    # Prepare data for function `plot_tf_idf()`
+    rename(
+      facet = `Course ID`
+      )
+
+  }
 
@@
 ```{r tf-idf cluster, cache = TRUE}
-prepare_tf_idf_cluster <- function(data) data %>%
-                                           left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
-                                           filter(!is.na(Cluster)) %>%
-                                           rename(facet = Cluster) %>%
-                                           group_by(facet, word) %>%
-                                             summarise(tf_idf = sum(tf_idf),
-                                                       n = sum(n)) %>%
-                                             filter(n >= 10) %>%
-                                             top_n(10, tf_idf) %>%
-                                           ungroup
+prepare_tf_idf_cluster <- function(data){
+
+  data %>%
+
+    # Include the variable Cluster
+    left_join(
+      select(d_course, `Course ID`, Cluster),
+      by = "Course ID"
+      ) %>%
+    filter(
+      !is.na(Cluster)
+      ) %>%
+
+    # Select top 10 words per cluster
+    group_by(
+      Cluster, 
+      word
+      ) %>%
+    summarise(
+      tf_idf = sum(tf_idf),
+      n = sum(n)
+      ) %>%
+    filter(
+      n >= 10
+      ) %>%
+    top_n(
+      n = 10, 
+      wt = tf_idf
+      ) %>%
+    ungroup %>%
+
+    # Prepare data for function `plot_tf_idf()`
+    rename(
+      facet = Cluster
+      )
+
+}
 
@@
 ```{r tf-idf concentration, cache = TRUE}
-prepare_tf_idf_concentration <- function(data) data %>%
-                                                 left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
-                                                 filter(!is.na(Concentration)) %>%
-                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-                                                 rename(facet = Concentration) %>%
-                                                 group_by(facet, word) %>%
-                                                   summarise(tf_idf = sum(tf_idf),
-                                                             n = sum(n)) %>%
-                                                   filter(n >= 10) %>%
-                                                   top_n(10, tf_idf) %>%
-                                                 ungroup
+prepare_tf_idf_concentration <- function(data){
+
+  data %>%
+
+    # Include the variable Concentration
+    left_join(
+      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
+      by = "Course ID"
+      ) %>%
+    filter(
+      !is.na(Concentration)
+      ) %>%
+    gather(
+      key = X,
+      value = Concentration,
+      Concentration, `Concentration (additional)`,
+      na.rm = TRUE
+      ) %>%
+
+    # Select top 10 words per cluster
+    group_by(
+      Concentration, 
+      word
+      ) %>%
+    summarise(
+      tf_idf = sum(tf_idf),
+      n = sum(n)
+      ) %>%
+    filter(
+      n >= 10
+      ) %>%
+    top_n(
+      n = 10,
+      wt = tf_idf
+      ) %>%
+    ungroup %>%
+
+    # Prepare data for function `plot_tf_idf()`
+    rename(
+      facet = Concentration
+      )
+
+}
 

### 2019-01-31 App/ui.R

@@ -43,9 +43,9 @@ fluidPage(
         inputId = "count",
         label = "Count",
         min   = 5,
-        max   = 1500,
+        max   = 3000,
         step  = 1,
-        value = c(5, 1500)
+        value = c(5, 3000)
         ),
       
       # Input: Slider for the Cconfidence

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
lhs correction to keep only low and fail

@@
 SR_PF      <- my_SR(data = sequences_PF) %>% 
-  filter(str_detect(rhs,"fail"))
+  filter(str_detect(lhs,"fail"), 
+         str_detect(rhs,"fail"))
 ```
@@
 SR_HL      <- my_SR(data = sequences_HL)%>% 
-  filter(str_detect(rhs,"low"))
+  filter(str_detect(lhs,"low"), 
+         str_detect(rhs,"low"))
 ```

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
editing

--- 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
@@
   )
+
 ```
@@
 ```
+
+```{r}
+d_support <- d_transactions %>%
+  mutate(
+    grade_round = round(Grade)
+  ) %>%
+  group_by(
+    item
+    ) %>%
+  summarise(
+    rate.fail = mean(PF == "fail"),
+    rate.low  = mean(HL == "low"),
+    rate.0    = mean(grade_round == 0),
+    # continue with other grades
+    )
+```
+
 ### Transactions for Apriori

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
including rhs.support to AR_taken

@@
     item_PF = paste(`Course ID`, PF, sep = "_"),
-    item_HL = paste(`Course ID`, HL, sep = "_"),
-    item_Grade = paste(`Course ID`, round(Grade,0), sep = "_")
+    item_HL = paste(`Course ID`, HL, sep = "_")
     ) %>%
@@
       is.na(Grade) ~ paste(item, taken, sep = "_"),
-      T            ~ paste(item, PF)
+      TRUE            ~ paste(item, PF)
       )
-
     )
@@
 ```{r}
+
+n_students <- d_transactions %>%
+  select(sequenceID) %>%
+  n_distinct()
+
+d_support_take <- d_transactions %>%
+  distinct(
+    item,
+    sequenceID
+    ) %>%
+  group_by(
+    item
+    ) %>%
+  summarise(
+    count     = n(),
+    rate.take = count / n_students
+    )
+
 d_support <- d_transactions %>%
@@
     rate.low  = mean(HL == "low"),
-    rate.0    = mean(grade_round == 0),
-    # continue with other grades
+    rate.0    = mean(grade_round <= 0),
+    rate.1    = mean(grade_round <= 1),
+    rate.2    = mean(grade_round <= 2),
+    rate.3    = mean(grade_round <= 3),
+    rate.4    = mean(grade_round <= 4),
+    rate.5    = mean(grade_round <= 5),
+    rate.6    = mean(grade_round <= 6),
+    rate.7    = mean(grade_round <= 7),
+    rate.8    = mean(grade_round <= 8),
+    rate.9    = mean(grade_round <= 9),
+    rate.10   = mean(grade_round <= 10)
     )
+
 ```
@@
 transactions_HL               <- make_transaction(item = item_HL)
-transactions_Grade            <- make_transaction(item = item_Grade)
 transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)
-
 transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
@@
 sequences_HL       <- make_sequence(item = item_HL)
-sequences_Grade    <- make_sequence(item = item_Grade)
 
@@
     ) %>%
+
+    # Clean variable `rules`
     mutate(
       rules = str_remove_all(rules, pattern = "[{]"),
-      rules = str_remove_all(rules, pattern = "[}]"),
-      `rhs.support` = confidence / lift
+      rules = str_remove_all(rules, pattern = "[}]")
     ) %>%
-    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
+    separate(rules, into = c("lhs", "rhs"), sep=" => ") %>%
+
+    # Editing output
     mutate_at(
-      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
+      c("support", "lhs.support", "confidence", "lift"),
       funs(round(., 5))
@@
       support, count, lhs.support,
-      confidence, rhs.support,
+      confidence,
       lift
@@
 # Generating asocciation rules
-AR_taken <- my_apriori(transactions)
+AR_taken <- my_apriori(transactions) %>%
+  left_join(
+    select(d_support_take, item, rate.take),
+    by = c("rhs" = "item")
+    ) %>%
+  mutate(
+    rhs.support = round(rate.take, 5)
+    ) %>%
+  select(
+    - rate.take
+    ) %>%
+  left_join(
+    select(d_support_take, item, rate.take),
+    by = c("lhs" = "item")
+    ) %>%
+  mutate(
+    lhs.support = round(rate.take, 5)
+    ) %>%
+  select(
+    - rate.take
+    ) %>%
+  select(lhs, rhs, support, count, confidence, rhs.support, lift)
 
@@
 SR_PF      <- my_SR(data = sequences_PF) %>% 
-  filter(str_detect(rhs,"fail"))
+  filter(
+    str_detect(rhs, "fail"),
+    str_detect(lhs, "fail")
+    )
 ```
@@
 SR_HL      <- my_SR(data = sequences_HL)%>% 
-  filter(str_detect(rhs,"low"))
+  filter(
+    str_detect(rhs, "low"),
+    str_detect(lhs, "low")
+    )
 ```

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
update functions to make transactions and sequences

@@
 
+# Number of students
 n_students <- d_transactions %>%
@@
 
+# Probability of taken a course
 d_support_take <- d_transactions %>%
@@
 
+# Probability of failing, having a low grade of a grade less than x in a course
 d_support <- d_transactions %>%
@@
 
-  data <- data %>%
+  data %>%
     group_by(
@@
     ) %>%
-    ungroup
-
-  transactions <- as(
-    data$list_item,
-    "transactions"
-    )
-
-  return(transactions)
+    ungroup %>%
+    pull(
+      list_item
+      ) %>%
+    as("transactions")
 
@@
 
-  data <- data %>%
+  sequences <- data %>%
     filter(!is.na(eventID))%>% #this is here casue we have courses that were never taken.
@@
     ) %>%
-    ungroup
-
-  sequences <- as(
-    data$list_item,
-    "transactions"
-    )
+    ungroup %>%
+    pull(
+      list_item
+      ) %>%
+    as("transactions")
 
@@
 # Checking sequences
-#inspect(head(sequences, 10))
+# inspect(head(sequences, 10))
 
@@
 ### Apriori Algorithm
+
+The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
+```{r my_apriori function}
+
+my_apriori <- function(data, appearance = NULL){
+
+  data %>%
+    apriori(
+      parameter = list(
+
+        # Chosen parameters
+        supp = 0,    # min support
+        smax = 1,    # max support
+        conf = 0,    # min confidence
+        minlen = 2,  # min length of 
+        maxlen = 2,  # max length of rule
+        ext = TRUE,
+        arem = "diff",
+        aval = TRUE,
+        minval = 0
+        ),
+
+      # impose restriction on what could be on the lhs and rhs of the rule
+      appearance = appearance
+
+      )
+
+}
+```
+
+The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
 ```{r function clean AR}
 
-# Transform AR from apriori into a readable data frame
 clean_AR <- function(AR){
@@
     as("data.frame") %>%
+
+    # Exclude rules with support of `0`
     filter(
@@
     ) %>%
-    separate(rules, into = c("lhs", "rhs"), sep=" => ") %>%
+    separate(rules, into = c("lhs", "rhs"), sep = " => ") %>%
 
@@
 
-We apply Apriori algorithm:
-```{r my_apriori function}
-# Run the apriori algorithm with desired parameters
-my_apriori <- function(data, appearance = NULL){
+The function `compute_support()` computes the support of the lhs and rhs of the rules.
+
+```{r}
+compute_support <- function(AR, type_rule){
+
+  type_rule_enquo <- enquo(type_rule)
+
+  AR %>%
+    left_join(
+      select(d_support, item, !!type_rule_enquo),
+      by = c("rhs" = "item")
+      ) %>%
+    mutate(
+      rhs.support = round(!!type_rule_enquo, 5)
+      ) %>%
+    select(
+      - !!type_rule_enquo
+      ) %>%
+    left_join(
+      select(d_support, item, !!type_rule_enquo),
+      by = c("lhs" = "item")
+      ) %>%
+    mutate(
+      lhs.support = round(!!type_rule_enquo, 5)
+      ) %>%
+    select(
+      - !!type_rule_enquo
+      ) %>%
+    select(
+      lhs, rhs, support, count, confidence, rhs.support, lift
+    )
+
+}
+```
+
+We encapsulate the three functions `my_apriori()`, `clean_AR()` and `compute_support` into the function `make_AR()`.
+
+```{r}
+make_AR <- function(data, appearance, type_rule){
 
   data %>%
-    apriori(
-      parameter = list(
-        supp = 0,    # min support
-        smax = 1,    # max support
-        conf = 0,    # min confidence
-        minlen = 2,  # min length of 
-        maxlen = 2,  # max length of rule
-        ext = TRUE,
-        arem = "diff",
-        aval = TRUE,
-        minval = 0
-        ),
-      appearance = appearance,
-      control = list(
-        verbose = FALSE
-        )
-      ) %>%
-    clean_AR
+    my_apriori(appearance = appearance) %>%
+    clean_AR() %>%
+    compute_support(type_rule = type_rule)
 
@@
 ```{r AR apriori, cache = TRUE}
+
+AR_take <- make_AR(transactions)
 
@@
 ##high/low filter
-SR_HL      <- my_SR(data = sequences_HL)%>% 
+SR_HL      <- my_SR(data = sequences_HL) %>% 
   filter(

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
previously taken courses per student per period

@@
 
+### Preceding courses
+```{r}
+d_cumulative_transcript <-  d_transactions        %>%
+  select(sequenceID, item, eventID)  %>%
+  arrange(sequenceID, eventID, item) %>%
+  group_by(sequenceID, eventID)      %>%
+  summarize_all(paste, collapse=" ") %>%
+  arrange(sequenceID, eventID)       %>%
+  mutate(
+    Cumulative_transcript=lag(Reduce(paste, item, accumulate=T)),
+    Cumulative_transcript= str_split(Cumulative_transcript," ")
+                                     )
+```
+
+###Computing probabilities
 ```{r}

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
include lhs and rhs support for AR (taken, fail, low)

--- 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ---
+
+```{r TODO}
+# TODO: compute corrected confidence for AR
+# TODO: compute lhs.support, for grade, not taken and  
+```
 
@@
 
-my_apriori <- function(data, appearance = NULL){
+my_apriori <- function(data, appearance){
 
@@
 
-      # impose restriction on what could be on the lhs and rhs of the rule
-      appearance = appearance
+      # impose restriction on lhs and rhs
+      appearance = appearance,
+
+      control = list(
+        verbose = FALSE
+      )
 
@@
 ```{r}
-compute_support <- function(AR, type_rule){
+compute_support <- function(AR, data_support, type_rule){
 
@@
   AR %>%
+
+    # include lhs.support
+    mutate(
+      lhs_course = str_remove_all(lhs, pattern = "_fail|_low")
+      ) %>%
     left_join(
-      select(d_support, item, !!type_rule_enquo),
-      by = c("rhs" = "item")
+      select(data_support, item, !!enquo(type_rule)),
+      by = c("lhs_course" = "item")
+      ) %>%
+    mutate(
+      lhs.support = round(!!type_rule_enquo, 5)
+      )  %>%
+    select(
+      - !!type_rule_enquo
+      ) %>%
+
+    # include rhs.support
+    mutate(
+      rhs_course = str_remove_all(rhs, pattern = "_fail|_low")
+      ) %>%
+    left_join(
+      select(data_support, item, !!type_rule_enquo),
+      by = c("rhs_course" = "item")
       ) %>%
@@
       ) %>%
-    left_join(
-      select(d_support, item, !!type_rule_enquo),
-      by = c("lhs" = "item")
-      ) %>%
-    mutate(
-      lhs.support = round(!!type_rule_enquo, 5)
-      ) %>%
+
+    # order variable
     select(
-      - !!type_rule_enquo
-      ) %>%
-    select(
-      lhs, rhs, support, count, confidence, rhs.support, lift
+      lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
     )
@@
 ```{r}
-make_AR <- function(data, appearance, type_rule){
+make_AR <- function(data, appearance = NULL,
+                    data_support, type_rule){
 
@@
     my_apriori(appearance = appearance) %>%
-    clean_AR() %>%
-    compute_support(type_rule = type_rule)
+    clean_AR %>%
+    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))
 
@@
 
-AR_take <- make_AR(transactions)
+#
+# AR taken
+AR_taken <- transactions %>%
+  make_AR(
+    data_support = d_support_take, 
+    type_rule = rate.take
+    )
 
-# Generating asocciation rules
-AR_taken <- my_apriori(transactions) %>%
-  left_join(
-    select(d_support_take, item, rate.take),
-    by = c("rhs" = "item")
-    ) %>%
-  mutate(
-    rhs.support = round(rate.take, 5)
-    ) %>%
-  select(
-    - rate.take
-    ) %>%
-  left_join(
-    select(d_support_take, item, rate.take),
-    by = c("lhs" = "item")
-    ) %>%
-  mutate(
-    lhs.support = round(rate.take, 5)
-    ) %>%
-  select(
-    - rate.take
-    ) %>%
-  select(lhs, rhs, support, count, confidence, rhs.support, lift)
+#
+# AR fail
+AR_PF <- transactions_PF %>%
+  make_AR(
+    appearance = list(
 
-# creating vector of fail course
-course_id_fail <- d_transactions %>%
+      # impose lhs and rhs to be fail
+      both = d_transactions %>%
         filter(PF == "fail") %>%
-  distinct(`item_PF`)
+        distinct(`item_PF`) %>%
+        pull
+    ),
 
-AR_PF <- my_apriori(transactions_PF,
-                    appearance = list(both = course_id_fail$`item_PF`))
+    data_support = d_support,
+    type_rule = rate.fail
+  )
 
-# creating vector of low score course
-course_id_low <- d_transactions %>%
+#
+# AR low
+AR_PF <- transactions_HL %>%
+  make_AR(
+    appearance = list(
+
+      # impose lhs and rhs to be fail
+      both = d_transactions %>%
         filter(HL == "low") %>%
-  distinct(`item_HL`)
+        distinct(`item_HL`) %>%
+        pull
+    ),
 
-AR_HL <- my_apriori(transactions_HL,
-                    appearance = list(both = course_id_low$`item_HL`))
+    data_support = d_support,
+    type_rule = rate.low
+  )
 
-AR_Grade <- my_apriori(transactions_Grade)
+# TODO
 
-AR_not_taken <- my_apriori(transactions_Taken)
+# AR_not_taken <- my_apriori(transactions_Taken)
 
-AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
+# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
 

### 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
AR_not_taken

@@
     count     = n(),
-    rate.take = count / n_students
+    rate.take = count / n_students,
+    rate.not  = 1 - rate.take
     )
@@
     mutate(
-      lhs_course = str_remove_all(lhs, pattern = "_fail|_low")
+      lhs_course = str_remove_all(lhs, pattern = "_fail|_low|_not taken")
       ) %>%
@@
     mutate(
-      rhs_course = str_remove_all(rhs, pattern = "_fail|_low")
+      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
       ) %>%
@@
     select(
-      lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
+      lhs_course, lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
     )
@@
 
-      # impose lhs and rhs to be fail
+      # impose lhs and rhs to be low
       both = d_transactions %>%
@@
 
+#
+# AR not taken
+AR_not_taken <- transactions_Taken %>%
+  make_AR(
+    appearance = list(
+
+      # impose lhs and rhs to be not taken
+      both = d_transactions_not_taken %>%
+        filter(taken == "not taken") %>%
+        distinct(`item_taken`) %>%
+        pull
+    ),
+
+    data_support = d_support_take,
+    type_rule = rate.not
+  )
+
 # TODO
-
-# AR_not_taken <- my_apriori(transactions_Taken)
 

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
minor update
rewrite code programmatically

@@
 # TODO: compute corrected confidence for AR
-# TODO: compute lhs.support, for grade, not taken and  
+# TODO: compute lhs.support, for grade
 ```
@@
 ```{r library, message = FALSE, warning = FALSE}
+library(tidyverse)
 library(arulesSequences)
-
-library(tidyverse)
 ```
@@
   select(- Period) %>%
-  inner_join(d_transcript, by = "Course ID") %>%
+  inner_join(
+    d_transcript,
+    by = "Course ID"
+    ) %>%
 
-  # Identifying sequences
+  # Identifying sequenceID
   rename(sequenceID = `Student ID`) %>%
 
-  # Identifying time of event (sequence)
+  # Identifying evenID
   mutate(
@@
 
-  # Identifying item
+  # Identifying itemID
   mutate(
@@
 
+    item    = `Course ID`,
     item_PF = paste(`Course ID`, PF, sep = "_"),
     item_HL = paste(`Course ID`, HL, sep = "_")
-    ) %>%
-  rename(
-    item = `Course ID`
     )
@@
       is.na(Grade) ~ "not taken",
-      TRUE         ~ "taken"),
+      TRUE         ~ "taken"
+      ),
 
-    item_taken= paste(item, taken, sep = "_"),
-    item_taken_grade= case_when(
-      is.na(Grade) ~ paste(item, taken, sep = "_"),
-      TRUE            ~ paste(item, PF)
-      )
+    taken_grade = case_when(
+      is.na(Grade) ~ "not taken",
+      Grade < 5.5  ~ "fail",
+      TRUE         ~ "pass"
+      ),
+
+    item_taken       = paste(item, taken      , sep = "_"),
+    item_taken_grade = paste(item, taken_grade, sep = "_")
+
     )
@@
 
-d_transactions_expanded <- d_transactions %>%
-  mutate(Round_grade = round(Grade, 0),
-         Values = T) %>%
-  spread(key = "Round_grade", value = Values) %>%
-  mutate(`1`  = `0`|`1`,
+d_transactions_grade <- d_transactions %>%
+
+  # Spread along rounded grades
+  mutate(
+    Round_grade = round(Grade, 0),
+    Values = TRUE
+    ) %>%
+  spread(
+    key   = Round_grade, 
+    value = Values
+    ) %>%
+
+  # fill grades inferior to obtained grade with TRUE
+  mutate(
+    `1`  = `0`|`1`,
     `2`  = `1`|`2`,
@@
     ) %>%
-  gather(key = "Grade_round", value = "Gr_bool", `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, na.rm = TRUE, convert = TRUE) %>%
-  select(-Gr_bool) %>%
+
+  # Gather along rounded grades
+  gather(
+    key = Grade_round,
+    value = "Gr_bool",
+    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
+    na.rm = TRUE, 
+    convert = TRUE
+    ) %>%
+  select(
+    -Gr_bool
+    )%>%
+
+  # Arrange per sequenceID and item for making sequences
   arrange(
@@
   mutate(
-    PF = case_when( Grade_round <  pass_grade ~ "fail",
-                    Grade_round >= pass_grade ~ "pass"),
-    HL = case_when( Grade_round <  high_grade ~ "low",
-                    Grade_round >= high_grade ~ "high"),
-
-    item_PF = paste(item, PF, sep = "_"),
-    item_HL = paste(item, HL, sep = "_"),
     item_Grade = paste(item, Grade_round, sep = "_")

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
new headers
updating cumulative transcript, adds columns "courses_not_taken", "courses_all"

--- 2019-02-01 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ---
-
-```{r TODO}
-# TODO: compute corrected confidence for AR
-# TODO: compute lhs.support, for grade, not taken and  
-```
 
@@
   mutate(
-    Cumulative_transcript=lag(Reduce(paste, item, accumulate=T)),
-    Cumulative_transcript= str_split(Cumulative_transcript," ")
-                                     )
+    course_all  = paste(unique(d_transactions$item), collapse = " "),
+    course_all  = str_split(course_all, pattern = " "),
+
+    course_now  = str_split(item, pattern = " "),
+
+    course_past     = Reduce(paste, item, accumulate=T),
+    course_past     = lag(course_past),
+    course_past     = str_split(course_past, pattern = " ")) %>%
+  ungroup() %>%
+    mutate(
+    course_past_now = purrr::map2(.x = course_past,
+                                      .y = course_now,
+                                      .f = union),
+    course_not = purrr::map2( .x = course_all,
+                              .y = course_past_now,
+                              .f = setdiff)
+    ) %>%
+  mutate(item = str_split(item, pattern = " "))
 ```
@@
 
-my_apriori <- function(data, appearance){
+my_apriori <- function(data, appearance = NULL){
 
@@
 
-      # impose restriction on lhs and rhs
-      appearance = appearance,
-
-      control = list(
-        verbose = FALSE
-      )
+      # impose restriction on what could be on the lhs and rhs of the rule
+      appearance = appearance
 
@@
 ```{r}
-compute_support <- function(AR, data_support, type_rule){
+compute_support <- function(AR, type_rule){
 
@@
   AR %>%
-
-    # include lhs.support
+    left_join(
+      select(d_support, item, !!type_rule_enquo),
+      by = c("rhs" = "item")
+      ) %>%
     mutate(
-      lhs_course = str_remove_all(lhs, pattern = "_fail|_low")
+      rhs.support = round(!!type_rule_enquo, 5)
+      ) %>%
+    select(
+      - !!type_rule_enquo
       ) %>%
     left_join(
-      select(data_support, item, !!enquo(type_rule)),
-      by = c("lhs_course" = "item")
+      select(d_support, item, !!type_rule_enquo),
+      by = c("lhs" = "item")
       ) %>%
@@
       ) %>%
-
-    # include rhs.support
-    mutate(
-      rhs_course = str_remove_all(rhs, pattern = "_fail|_low")
-      ) %>%
-    left_join(
-      select(data_support, item, !!type_rule_enquo),
-      by = c("rhs_course" = "item")
-      ) %>%
-    mutate(
-      rhs.support = round(!!type_rule_enquo, 5)
-      ) %>%
     select(
-      - !!type_rule_enquo
-      ) %>%
-
-    # order variable
-    select(
-      lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
+      lhs, rhs, support, count, confidence, rhs.support, lift
     )
@@
 ```{r}
-make_AR <- function(data, appearance = NULL,
-                    data_support, type_rule){
+make_AR <- function(data, appearance, type_rule){
 
@@
     my_apriori(appearance = appearance) %>%
-    clean_AR %>%
-    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))
+    clean_AR() %>%
+    compute_support(type_rule = type_rule)
 
@@
 
-#
-# AR taken
-AR_taken <- transactions %>%
-  make_AR(
-    data_support = d_support_take, 
-    type_rule = rate.take
-    )
+AR_take <- make_AR(transactions)
 
-#
-# AR fail
-AR_PF <- transactions_PF %>%
-  make_AR(
-    appearance = list(
+# Generating asocciation rules
+AR_taken <- my_apriori(transactions) %>%
+  left_join(
+    select(d_support_take, item, rate.take),
+    by = c("rhs" = "item")
+    ) %>%
+  mutate(
+    rhs.support = round(rate.take, 5)
+    ) %>%
+  select(
+    - rate.take
+    ) %>%
+  left_join(
+    select(d_support_take, item, rate.take),
+    by = c("lhs" = "item")
+    ) %>%
+  mutate(
+    lhs.support = round(rate.take, 5)
+    ) %>%
+  select(
+    - rate.take
+    ) %>%
+  select(lhs, rhs, support, count, confidence, rhs.support, lift)
 
-      # impose lhs and rhs to be fail
-      both = d_transactions %>%
+# creating vector of fail course
+course_id_fail <- d_transactions %>%
   filter(PF == "fail") %>%
-        distinct(`item_PF`) %>%
-        pull
-    ),
+  distinct(`item_PF`)
 
-    data_support = d_support,
-    type_rule = rate.fail
-  )
+AR_PF <- my_apriori(transactions_PF,
+                    appearance = list(both = course_id_fail$`item_PF`))
 
-#
-# AR low
-AR_PF <- transactions_HL %>%
-  make_AR(
-    appearance = list(
+# creating vector of low score course
+course_id_low <- d_transactions %>%
+  filter(HL == "low") %>%
+  distinct(`item_HL`)
 
-      # impose lhs and rhs to be fail
-      both = d_transactions %>%
-        filter(HL == "low") %>%
-        distinct(`item_HL`) %>%
-        pull
-    ),
+AR_HL <- my_apriori(transactions_HL,
+                    appearance = list(both = course_id_low$`item_HL`))
 
-    data_support = d_support,
-    type_rule = rate.low
-  )
+AR_Grade <- my_apriori(transactions_Grade)
 
-# TODO
+AR_not_taken <- my_apriori(transactions_Taken)
 
-# AR_not_taken <- my_apriori(transactions_Taken)
-
-# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
+AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
 

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+### take, fail, low grade
 ```{r AR data prep 1}
@@
 
-### Adding not taken courses
+### take / not take, pass / fail / not take
 ```{r transactions not taken}
@@
 ```
-###Expanded Transcripts
+
+### Grade
 ```{r transactions expanded}

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
rename item

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-    taken = case_when(
+    TNT = case_when(
       is.na(Grade) ~ "not taken",
@@
 
-    taken_grade = case_when(
+    TPF = case_when(
       is.na(Grade) ~ "not taken",
@@
 
-    item_taken       = paste(item, taken      , sep = "_"),
-    item_taken_grade = paste(item, taken_grade, sep = "_")
+    item_TNT = paste(item, TNT, sep = "_"),
+    item_TPF = paste(item, TPF, sep = "_")
 
@@
 
-  # Arrange per sequenceID and item for making sequences
-  arrange(
-    sequenceID,
-    item
-    ) %>%
-
   # Identifying item
   mutate(
-    item_Grade = paste(item, Grade_round, sep = "_")
+    item_G = paste(item, Grade_round, sep = "_")
     )
@@
 
-# Probability of failing, having a low grade of a grade less than x in a course
+# Probability of failing, having a low grade, having a grade less than x per course
 d_support <- d_transactions %>%
@@
 ### Transactions for Apriori
-```{r making transactions}
+```{r making transactions, message = FALSE}
 
@@
 transactions_HL  <- make_transaction(item = item_HL)
-transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)
-transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
+#transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
+transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
+transactions_G   <- make_transaction(data = d_transactions_grade    , item = item_G  )
 
@@
     ) %>%
-    as.data.frame()
+    as.data.frame
 
@@
 sequences_HL  <- make_sequence(item = item_HL)
-
-sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)
+#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
+#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
+sequences_G   <- make_sequence(data = d_transactions_grade    , item = item_G  )
 
@@
 # Checking sequences
-# inspect(head(sequences, 10))
+# inspect(head(sequences_G, 10))
 
@@
     apriori(
-      parameter = list(
 
       # Chosen parameters
+      parameter = list(
         supp = 0,    # min support
@@
 
+      # no printing during execution
       control = list(
@@
 
-    # Exclude rules with support of `0`
+    # Exclude rules with no support
     filter(
@@
       ) %>%
-    separate(rules, into = c("lhs", "rhs"), sep = " => ") %>%
-
-    # Editing output
-    mutate_at(
-      c("support", "lhs.support", "confidence", "lift"),
-      funs(round(., 5))
-    ) %>%
-    select(
-      lhs, rhs,
-      support, count, lhs.support,
-      confidence,
-      lift
-    ) %>%
-    arrange(
-      desc(count)
+    separate(
+      rules,
+      into = c("lhs", "rhs"), 
+      sep  = " => "
       )
@@
     left_join(
-      select(data_support, item, !!enquo(type_rule)),
+      select(data_support, item, !!type_rule_enquo),
       by = c("lhs_course" = "item")
@@
     mutate(
-      lhs.support = round(!!type_rule_enquo, 5)
+      lhs.support = !!type_rule_enquo
       )  %>%
@@
     mutate(
-      rhs.support = round(!!type_rule_enquo, 5)
+      rhs.support = !!type_rule_enquo
       ) %>%
@@
 
-    # order variable
+    # Editing output
+    mutate_at(
+      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
+      funs(round(., 5))
+    ) %>%
     select(
-      lhs_course, lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
+      lhs, rhs,
+      support, count, lhs.support,
+      confidence, rhs.support,
+      lift
+    ) %>%
+    arrange(
+      desc(count)
     )
@@
   make_AR(
-    appearance = list(
 
     # impose lhs and rhs to be fail
+    appearance = list(
       both = d_transactions %>%
         filter(PF == "fail") %>%
-        distinct(`item_PF`) %>%
+        distinct(item_PF) %>%
         pull
@@
   make_AR(
-    appearance = list(
 
     # impose lhs and rhs to be low
+    appearance = list(
       both = d_transactions %>%
@@
   make_AR(
-    appearance = list(
 
     # impose lhs and rhs to be not taken
+    appearance = list(
       both = d_transactions_not_taken %>%
-        filter(taken == "not taken") %>%
-        distinct(`item_taken`) %>%
+        filter(TNT == "not taken") %>%
+        distinct(`item_TNT`) %>%
         pull

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
name chunks

@@
 The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
-```{r my_apriori function}
+```{r my_apriori}
 
@@
 The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-```{r function clean AR}
+```{r clean_AR}
 
@@
 
-```{r}
+```{r compute_support}
 compute_support <- function(AR, data_support, type_rule){
@@
 
-```{r}
+```{r make_AR}
 make_AR <- function(data, appearance = NULL,
@@
 
-```{r AR apriori, cache = TRUE}
+```{r AR, cache = TRUE}
 

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
association rules with grades

@@
 # TODO: compute corrected confidence for AR
-# TODO: compute lhs.support, for grade
+# TODO: support of AR_TFP
 ```
@@
 transactions_HL  <- make_transaction(item = item_HL)
-#transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
+transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
 transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
@@
         maxlen = 2,  # max length of rule
-        ext = TRUE,
-        arem = "diff",
-        aval = TRUE,
-        minval = 0
+        ext = TRUE
         ),
@@
       - !!type_rule_enquo
-      ) %>%
+      )
 
-    # Editing output
+}
+```
+
+```{r editing_AR}
+editing_AR <- function(AR){
+
+  AR %>%
     mutate_at(
-      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
+      c("support", "lhs.support", 
+        "confidence", "rhs.support",
+        "lift"
+        ),
       funs(round(., 5))
@@
     clean_AR %>%
-    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))
+    compute_support(
+      data_support = data_support,
+      type_rule = !!enquo(type_rule)
+      ) %>%
+    editing_AR
 
@@
 # AR low
-AR_PF <- transactions_HL %>%
+AR_HL <- transactions_HL %>%
   make_AR(
@@
 # AR not taken
-AR_not_taken <- transactions_Taken %>%
+AR_TNT <- transactions_TNT %>%
   make_AR(
@@
 
-# TODO
+#
+# AR not taken / fail / pass
 
-# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
+AR_TPF <- transactions_TPF %>%
+  make_AR(
+
+    # impose lhs and rhs to be not taken
+    appearance = list(
+      rhs = d_transactions_not_taken %>%
+        filter(TPF == "fail") %>%
+        distinct(`item_TPF`) %>%
+        pull
+    ),
+
+    data_support = d_support_take,
+    type_rule = rate.not
+  )
 
 ```
+
+```{r AR grade (by hand)}
+
+#
+# d_support
+d_support_grade <- d_support %>%
+  gather(
+    key   = grade_round,
+    value = support.grade,
+    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
+    ) %>%
+  mutate( 
+    grade_round = substr(grade_round, start = 6, stop = 7),
+    grade_round = as.numeric(grade_round)
+    ) %>%
+  select(-c(rate.fail, rate.low))
+
+# Make RA
+AR_G <- transactions_G %>%
+  my_apriori(appearance = NULL) %>%
+  clean_AR %>%
+
+  # include lhs.support by hand
+  separate(
+    lhs, 
+    into = c("lhs_course", "lhs_grade_round"), 
+    sep = "_",
+    remove = FALSE,
+    convert = TRUE
+    ) %>%
+  left_join(
+    d_support_grade,
+    by = c("lhs_course" = "item", "lhs_grade_round" = "grade_round")
+    ) %>%
+  mutate(
+    lhs.support = support.grade
+    ) %>%
+  select(
+    - support.grade
+    ) %>%
+
+  # include rhs.support by hand
+  separate(
+    rhs, 
+    into = c("rhs_course", "rhs_grade_round"), 
+    sep = "_",
+    remove = FALSE,
+    convert = TRUE
+    ) %>%
+  left_join(
+    d_support_grade,
+    by = c("rhs_course" = "item", "rhs_grade_round" = "grade_round")
+    ) %>%
+  mutate(
+    rhs.support = support.grade
+    ) %>%
+  select(
+    - support.grade
+    ) %>%
+
+    editing_AR
+
+```
+
 We save and remove objects:
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
-     AR_expanded_Grade,
+save(AR_taken, AR_PF, AR_HL, AR_TNT, AR_TPF, AR_G,
      file = "App/AR.RDATA")
@@
 rm(clean_AR, my_apriori,
-   transactions, transactions_PF, transactions_HL, transactions_Grade,
-   course_id_fail, course_id_low,
-   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade,  
-   AR_expanded_Grade)
+   transactions, transactions_PF, transactions_HL, transactions_G,
+   AR_taken, AR_PF, AR_HL, AR_TNT, AR_G)
 ```

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
cleaned code

@@
 ```{r transactions not taken}
-d_transactions_not_taken <- expand.grid(
+d_transactions_TPF <- expand.grid(
 
@@
 
-    TNT = case_when(
-      is.na(Grade) ~ "not taken",
-      TRUE         ~ "taken"
-      ),
-
     TPF = case_when(
       is.na(Grade)       ~ "not taken",
-      Grade < 5.5  ~ "fail",
+      Grade < pass_grade ~ "fail",
       TRUE               ~ "pass"
@@
 
-    item_TNT = paste(item, TNT, sep = "_"),
     item_TPF = paste(item, TPF, sep = "_")
@@
 
+rm(high_grade, pass_grade)
 ```
@@
 
-d_transactions_grade <- d_transactions %>%
+d_transactions_G <- d_transactions %>%
 
@@
     key = Grade_round,
-    value = "Gr_bool",
+    value = X,
     `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
@@
   select(
-    -Gr_bool
+    -X
     )%>%
@@
 
+rm(n_students)
 ```
@@
 transactions_HL  <- make_transaction(item = item_HL)
-transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
-transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
-transactions_G   <- make_transaction(data = d_transactions_grade    , item = item_G  )
+transactions_TPF <- make_transaction(data = d_transactions_TPF, item = item_TPF)
+transactions_G   <- make_transaction(data = d_transactions_G  , item = item_G  )
 
@@
 ```{r compute_support}
-compute_support <- function(AR, data_support, type_rule){
+compute_metrics <- function(AR, data_support, type_rule){
 
@@
   AR %>%
-
-    # include lhs.support
-    mutate(
-      lhs_course = str_remove_all(lhs, pattern = "_fail|_low|_not taken")
-      ) %>%
-    left_join(
-      select(data_support, item, !!type_rule_enquo),
-      by = c("lhs_course" = "item")
-      ) %>%
-    mutate(
-      lhs.support = !!type_rule_enquo
-      )  %>%
-    select(
-      - !!type_rule_enquo
-      ) %>%
 
@@
       rhs.support = !!type_rule_enquo
-      ) %>%
-    select(
-      - !!type_rule_enquo
       )
@@
     clean_AR %>%
-    compute_support(
+    compute_metrics(
       data_support = data_support,
@@
 #
-# AR not taken
-AR_TNT <- transactions_TNT %>%
-  make_AR(
-
-    # impose lhs and rhs to be not taken
-    appearance = list(
-      both = d_transactions_not_taken %>%
-        filter(TNT == "not taken") %>%
-        distinct(`item_TNT`) %>%
-        pull
-    ),
-
-    data_support = d_support_take,
-    type_rule = rate.not
-  )
-
-#
 # AR not taken / fail / pass
@@
     appearance = list(
-      rhs = d_transactions_not_taken %>%
+      rhs = d_transactions_TNT %>%
         filter(TPF == "fail") %>%
@@
 
-  # include lhs.support by hand
+  # include rhs.support by hand
   separate(
-    lhs, 
-    into = c("lhs_course", "lhs_grade_round"), 
+    rhs, 
+    into = c("item", "grade_round"), 
     sep = "_",
@@
     d_support_grade,
-    by = c("lhs_course" = "item", "lhs_grade_round" = "grade_round")
-    ) %>%
-  mutate(
-    lhs.support = support.grade
-    ) %>%
-  select(
-    - support.grade
-    ) %>%
-
-  # include rhs.support by hand
-  separate(
-    rhs, 
-    into = c("rhs_course", "rhs_grade_round"), 
-    sep = "_",
-    remove = FALSE,
-    convert = TRUE
-    ) %>%
-  left_join(
-    d_support_grade,
-    by = c("rhs_course" = "item", "rhs_grade_round" = "grade_round")
+    by = c("item", "grade_round")
     ) %>%
@@
     rhs.support = support.grade
-    ) %>%
-  select(
-    - support.grade
     ) %>%

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
filter AR after apriori

@@
 ```{r TODO}
-# TODO: compute corrected confidence for AR
-# TODO: support of AR_TFP
+# TODO: corrected confidence for AR
 ```
@@
 
-###Computing probabilities
+### Computing Support
 ```{r}
@@
 
-rm(n_students)
 ```
@@
 #sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
-sequences_G   <- make_sequence(data = d_transactions_grade    , item = item_G  )
+sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )
 
@@
 
-my_apriori <- function(data, appearance){
+my_apriori <- function(data){
 
@@
         minlen = 2,  # min length of 
-        maxlen = 2,  # max length of rule
-        ext = TRUE
+        maxlen = 2  # max length of rule
         ),
-
-      # impose restriction on lhs and rhs
-      appearance = appearance,
 
@@
     mutate_at(
-      c("support", "lhs.support", 
+      c("support", 
         "confidence", "rhs.support",
@@
       lhs, rhs,
-      support, count, lhs.support,
+      support, count,
       confidence, rhs.support,
@@
 ```{r make_AR}
-make_AR <- function(data, appearance = NULL,
+make_AR <- function(data,
                     data_support, type_rule){
@@
   data %>%
-    my_apriori(appearance = appearance) %>%
+    my_apriori %>%
     clean_AR %>%
@@
   make_AR(
-
-    # impose lhs and rhs to be fail
-    appearance = list(
-      both = d_transactions %>%
-        filter(PF == "fail") %>%
-        distinct(item_PF) %>%
-        pull
-    ),
-
     data_support = d_support,
     type_rule = rate.fail
+    ) %>%
+
+  # lhs and rhs must be fail
+  filter(
+    str_detect(lhs, "fail"),
+    str_detect(rhs, "fail")
     )
@@
   make_AR(
-
-    # impose lhs and rhs to be low
-    appearance = list(
-      both = d_transactions %>%
-        filter(HL == "low") %>%
-        distinct(`item_HL`) %>%
-        pull
-    ),
-
     data_support = d_support,
     type_rule = rate.low
+    ) %>%
+
+    # lhs and rhs must be low
+  filter(
+    str_detect(lhs, "low"),
+    str_detect(rhs, "low")
     )
@@
   make_AR(
+    data_support = d_support_take, 
+    type_rule = rate.take
+  ) %>%
 
-    # impose lhs and rhs to be not taken
-    appearance = list(
-      rhs = d_transactions_TNT %>%
-        filter(TPF == "fail") %>%
-        distinct(`item_TPF`) %>%
-        pull
-    ),
-
-    data_support = d_support_take,
-    type_rule = rate.not
+  # lhs and rhs must be low
+  filter(
+    str_detect(rhs, "fail")
     )
 
+rm(transactions, transactions_PF, transactions_HL, transactions_TPF)
 ```
@@
 
+rm(d_support_grade, transactions_G)
 ```
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_TNT, AR_TPF, AR_G,
+save(AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
      file = "App/AR.RDATA")
@@
 # Remove objects
-rm(clean_AR, my_apriori,
-   transactions, transactions_PF, transactions_HL, transactions_G,
-   AR_taken, AR_PF, AR_HL, AR_TNT, AR_G)
+rm(my_apriori, clean_AR, compute_metrics, make_AR,
+   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G)
 ```
@@
 # Transform rules from ruleInduction into a readable data frame
-n_students <- length(unique(d_transactions$sequenceID))
 

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
creates data frame with all courses taken before each course

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # TODO: compute corrected confidence for AR
-# TODO: support of AR_TFP
+# TODO: compute lhs.support, for grade
 ```
@@
 ```{r transactions not taken}
-d_transactions_TPF <- expand.grid(
+d_transactions_not_taken <- expand.grid(
 
@@
 
-    TPF = case_when(
+    taken = case_when(
       is.na(Grade) ~ "not taken",
-      Grade < pass_grade ~ "fail",
+      TRUE         ~ "taken"
+      ),
+
+    taken_grade = case_when(
+      is.na(Grade) ~ "not taken",
+      Grade < 5.5  ~ "fail",
       TRUE         ~ "pass"
@@
 
-    item_TPF = paste(item, TPF, sep = "_")
+    item_taken       = paste(item, taken      , sep = "_"),
+    item_taken_grade = paste(item, taken_grade, sep = "_")
 
@@
 
-rm(high_grade, pass_grade)
 ```
@@
 
-d_transactions_G <- d_transactions %>%
+d_transactions_grade <- d_transactions %>%
 
@@
     key = Grade_round,
-    value = X,
+    value = "Gr_bool",
     `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
@@
   select(
-    -X
+    -Gr_bool
     )%>%
+
+  # Arrange per sequenceID and item for making sequences
+  arrange(
+    sequenceID,
+    item
+    ) %>%
 
@@
   mutate(
-    item_G = paste(item, Grade_round, sep = "_")
+    item_Grade = paste(item, Grade_round, sep = "_")
     )
 ```
-
-### Preceding courses
+### Additional General Dataframes for courses
+#### Transcript with Preceding courses per student
 ```{r}
@@
 
+#### Courses that were taken before each course
+```{r}
+d_past_student_course <- d_cumulative_transcript %>%
+  select(sequenceID, eventID, item, course_past)%>%
+  unnest(item, .drop=F)
+
+d_past_course <- expand.grid(
+
+  # Expand along students (sequenceID) and courses (itemID)
+  sequenceID = unique(d_transactions$sequenceID),
+  item       = unique(d_transactions$item),
+  stringsAsFactors = FALSE
+  ) %>%
+  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
+  arrange(sequenceID) %>%
+  ungroup() %>%
+  drop_na(eventID) %>%
+  unnest(course_past) %>%
+  distinct() %>%
+  group_by(item) %>%
+  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
+  mutate(full_past    = str_split(full_past, pattern = " "),
+         full_past    = map(.f= unique, .x=full_past),
+         total_past_courses = map(.f=length, .x=full_past))
+```
+
 ###Computing probabilities
@@
 
-# Probability of failing, having a low grade, having a grade less than x per course
+# Probability of failing, having a low grade of a grade less than x in a course
 d_support <- d_transactions %>%
@@
 ### Transactions for Apriori
-```{r making transactions, message = FALSE}
+```{r making transactions}
 
@@
 transactions_HL               <- make_transaction(item = item_HL)
-transactions_TPF <- make_transaction(data = d_transactions_TPF, item = item_TPF)
-transactions_G   <- make_transaction(data = d_transactions_G  , item = item_G  )
+transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)
+transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)
 
@@
     ) %>%
-    as.data.frame
+    as.data.frame()
 
@@
 sequences_HL       <- make_sequence(item = item_HL)
-#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
-#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
-sequences_G   <- make_sequence(data = d_transactions_grade    , item = item_G  )
+
+sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)
 
@@
 # Checking sequences
-# inspect(head(sequences_G, 10))
+# inspect(head(sequences, 10))
 
@@
 The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
-```{r my_apriori}
+```{r my_apriori function}
 
@@
     apriori(
+      parameter = list(
 
         # Chosen parameters
-      parameter = list(
         supp = 0,    # min support
@@
         maxlen = 2,  # max length of rule
-        ext = TRUE
+        ext = TRUE,
+        arem = "diff",
+        aval = TRUE,
+        minval = 0
         ),
@@
 
-      # no printing during execution
       control = list(
@@
 The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-```{r clean_AR}
+```{r function clean AR}
 
@@
 
-    # Exclude rules with no support
+    # Exclude rules with support of `0`
     filter(
@@
     ) %>%
-    separate(
-      rules,
-      into = c("lhs", "rhs"), 
-      sep  = " => "
+    separate(rules, into = c("lhs", "rhs"), sep = " => ") %>%
+
+    # Editing output
+    mutate_at(
+      c("support", "lhs.support", "confidence", "lift"),
+      funs(round(., 5))
+    ) %>%
+    select(
+      lhs, rhs,
+      support, count, lhs.support,
+      confidence,
+      lift
+    ) %>%
+    arrange(
+      desc(count)
     )
@@
 
-```{r compute_support}
-compute_metrics <- function(AR, data_support, type_rule){
+```{r}
+compute_support <- function(AR, data_support, type_rule){
 
@@
   AR %>%
+
+    # include lhs.support
+    mutate(
+      lhs_course = str_remove_all(lhs, pattern = "_fail|_low|_not taken")
+      ) %>%
+    left_join(
+      select(data_support, item, !!enquo(type_rule)),
+      by = c("lhs_course" = "item")
+      ) %>%
+    mutate(
+      lhs.support = round(!!type_rule_enquo, 5)
+      )  %>%
+    select(
+      - !!type_rule_enquo
+      ) %>%
 
@@
     mutate(
-      rhs.support = !!type_rule_enquo
-      )
-
-}
-```
-
-```{r editing_AR}
-editing_AR <- function(AR){
-
-  AR %>%
-    mutate_at(
-      c("support", "lhs.support", 
-        "confidence", "rhs.support",
-        "lift"
-        ),
-      funs(round(., 5))
+      rhs.support = round(!!type_rule_enquo, 5)
       ) %>%
     select(
-      lhs, rhs,
-      support, count, lhs.support,
-      confidence, rhs.support,
-      lift
+      - !!type_rule_enquo
       ) %>%
-    arrange(
-      desc(count)
+
+    # order variable
+    select(
+      lhs_course, lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
     )
@@
 
-```{r make_AR}
+```{r}
 make_AR <- function(data, appearance = NULL,
@@
     clean_AR %>%
-    compute_metrics(
-      data_support = data_support,
-      type_rule = !!enquo(type_rule)
-      ) %>%
-    editing_AR
+    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))
 
@@
 
-```{r AR, cache = TRUE}
+```{r AR apriori, cache = TRUE}
 
@@
   make_AR(
+    appearance = list(
 
       # impose lhs and rhs to be fail
-    appearance = list(
       both = d_transactions %>%
         filter(PF == "fail") %>%
-        distinct(item_PF) %>%
+        distinct(`item_PF`) %>%
         pull
@@
 # AR low
-AR_HL <- transactions_HL %>%
+AR_PF <- transactions_HL %>%
   make_AR(
+    appearance = list(
 
       # impose lhs and rhs to be low
-    appearance = list(
       both = d_transactions %>%
@@
 #
-# AR not taken / fail / pass
-
-AR_TPF <- transactions_TPF %>%
+# AR not taken
+AR_not_taken <- transactions_Taken %>%
   make_AR(
+    appearance = list(
 
       # impose lhs and rhs to be not taken
-    appearance = list(
-      rhs = d_transactions_TNT %>%
-        filter(TPF == "fail") %>%
-        distinct(`item_TPF`) %>%
+      both = d_transactions_not_taken %>%
+        filter(taken == "not taken") %>%
+        distinct(`item_taken`) %>%
         pull
@@
 
-```
+# TODO
 
-```{r AR grade (by hand)}
-
-#
-# d_support
-d_support_grade <- d_support %>%
-  gather(
-    key   = grade_round,
-    value = support.grade,
-    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
-    ) %>%
-  mutate( 
-    grade_round = substr(grade_round, start = 6, stop = 7),
-    grade_round = as.numeric(grade_round)
-    ) %>%
-  select(-c(rate.fail, rate.low))
-
-# Make RA
-AR_G <- transactions_G %>%
-  my_apriori(appearance = NULL) %>%
-  clean_AR %>%
-
-  # include rhs.support by hand
-  separate(
-    rhs, 
-    into = c("item", "grade_round"), 
-    sep = "_",
-    remove = FALSE,
-    convert = TRUE
-    ) %>%
-  left_join(
-    d_support_grade,
-    by = c("item", "grade_round")
-    ) %>%
-  mutate(
-    rhs.support = support.grade
-    ) %>%
-
-    editing_AR
+# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
 
 ```
-
 We save and remove objects:
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_TNT, AR_TPF, AR_G,
+save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
+     AR_expanded_Grade,
      file = "App/AR.RDATA")
@@
 rm(clean_AR, my_apriori,
-   transactions, transactions_PF, transactions_HL, transactions_G,
-   AR_taken, AR_PF, AR_HL, AR_TNT, AR_G)
+   transactions, transactions_PF, transactions_HL, transactions_Grade,
+   course_id_fail, course_id_low,
+   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade,  
+   AR_expanded_Grade)
 ```

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
corrected confidence and lift

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r TODO}
-# TODO: corrected confidence for AR
+
 ```
@@
 
-### Computing Support
+### Support
 ```{r}
@@
 
-    # include rhs.support
+    # rhs.support
     mutate(
-      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
+      rhs_course = str_remove_all(rhs, pattern = "_fail|_pass|_low|_not taken")
       ) %>%
@@
 #
-# AR taken
+# AR taken (confidence and lift already correct)
 AR_taken <- transactions %>%
@@
 
-  # lhs and rhs must be fail
+  # Confidence and Lift
+  separate(
+    rhs,
+    sep = "_",
+    into = c("rhs_course", "rhs_outcome"),
+    remove = FALSE
+    ) %>%
+  group_by(
+    lhs, rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support),
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / rhs.support
+    ) %>%
+  ungroup %>%
+
+  # lhs and rhs must be fail, count >= 5
   filter(
     str_detect(lhs, "fail"),
-    str_detect(rhs, "fail")
+    str_detect(rhs, "fail"),
+    count >= 5
+    ) %>%
+  select(
+    - c(rhs_outcome, rhs_course)
   )
@@
 
-    # lhs and rhs must be low
+  # Confidence and Lift
+  separate(
+    rhs,
+    sep = "_",
+    into = c("rhs_course", "rhs_outcome"),
+    remove = FALSE
+    ) %>%
+  group_by(
+    lhs, rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support),
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / rhs.support
+    ) %>%
+  ungroup %>%
+
+  # lhs and rhs must be fail, count >= 5
   filter(
     str_detect(lhs, "low"),
-    str_detect(rhs, "low")
+    str_detect(rhs, "low"),
+    count >= 5
+    ) %>%
+  select(
+    - c(rhs_outcome, rhs_course)
   )
@@
   make_AR(
-    data_support = d_support_take, 
-    type_rule = rate.take
+    data_support = d_support, 
+    type_rule = rate.fail
   ) %>%
 
-  # lhs and rhs must be low
+  # Confidence and Lift
+  separate(
+    rhs,
+    sep = "_",
+    into = c("rhs_course", "rhs_outcome"),
+    remove = FALSE
+    ) %>%
+  mutate(
+    rhs.take = str_detect(rhs, "fail|pass")
+    ) %>%
+  group_by(
+    lhs, rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support * rhs.take),
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / (rhs.support + 1e-4) # some courses have a failure rate of 0%.
+    ) %>%
+  ungroup %>%
+
+  # lhs and rhs must be fail, count >= 5
   filter(
-    str_detect(rhs, "fail")
+    str_detect(lhs, "not taken"),
+    str_detect(rhs, "fail"),
+    count >= 5
+    ) %>%
+  select(
+    - c(rhs_outcome, rhs_course, rhs.take)
   )
@@
 
-# Make RA
+# Make AR
 AR_G <- transactions_G %>%

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
-
-### Preceding courses
+### Additional General Dataframes for courses
+#### Transcript with Preceding courses per student
 ```{r}
@@
 
+#### Courses that were taken before each course
+```{r}
+d_past_student_course <- d_cumulative_transcript %>%
+  select(sequenceID, eventID, item, course_past)%>%
+  unnest(item, .drop=F)
+
+d_past_course <- expand.grid(
+
+  # Expand along students (sequenceID) and courses (itemID)
+  sequenceID = unique(d_transactions$sequenceID),
+  item       = unique(d_transactions$item),
+  stringsAsFactors = FALSE
+  ) %>%
+  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
+  arrange(sequenceID) %>%
+  ungroup() %>%
+  drop_na(eventID) %>%
+  unnest(course_past) %>%
+  distinct() %>%
+  group_by(item) %>%
+  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
+  mutate(full_past    = str_split(full_past, pattern = " "),
+         full_past    = map(.f= unique, .x=full_past),
+         total_past_courses = map(.f=length, .x=full_past))
+```
+
 ### Computing Support
+
 ```{r}

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+#### Courses that were taken before each course
+```{r}
+d_past_student_course <- d_cumulative_transcript %>%
+  select(sequenceID, eventID, item, course_past)%>%
+  unnest(item, .drop=F)
+
+d_past_course <- expand.grid(
+
+  # Expand along students (sequenceID) and courses (itemID)
+  sequenceID = unique(d_transactions$sequenceID),
+  item       = unique(d_transactions$item),
+  stringsAsFactors = FALSE
+  ) %>%
+  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
+  arrange(sequenceID) %>%
+  ungroup() %>%
+  drop_na(eventID) %>%
+  unnest(course_past) %>%
+  distinct() %>%
+  group_by(item) %>%
+  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
+  mutate(full_past    = str_split(full_past, pattern = " "),
+         full_past    = map(.f= unique, .x=full_past),
+         total_past_courses = map(.f=length, .x=full_past))
+```
+
 ### Support
+
 ```{r}

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
minor editing

--- 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
@@
     confidence          = support / lhs.rhsTake.support,
-    lift                = confidence / (rhs.support + 1e-4) # some courses have a failure rate of 0%.
+    lift                = confidence / (rhs.support + 1e-4) # increase denominator by smal value to avoid dividing by 0.
     ) %>%

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code

@@
   select(sequenceID) %>%
-  n_distinct()
+  n_distinct
 
-# Probability of taken a course
+# Probability of taking a course
 d_support_take <- d_transactions %>%
@@
     ) %>%
-  group_by(
+  count(
     item
     ) %>%
-  summarise(
-    count     = n(),
-    rate.take = count / n_students,
-    rate.not  = 1 - rate.take
-    )
+  mutate(
+    rate.take = n / n_students,
+    rate.not  = 1 - rate.take)
 

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
use ceiling(grade) instead of round(grade)

@@
   mutate(
-    Round_grade = round(Grade, 0),
+    grade_ceil = ceiling(Grade),
     Values     = TRUE
@@
   spread(
-    key   = Round_grade, 
+    key   = grade_ceil, 
     value = Values
@@
   gather(
-    key   = Grade_round,
+    key   = grade_ceil,
     value = X,
@@
     -X
-    )%>%
+    ) %>%
 
@@
   mutate(
-    item_G = paste(item, Grade_round, sep = "_")
+    item_G = paste(item, grade_ceil, sep = "_")
     )
@@
     rate.take = n / n_students,
-    rate.not  = 1 - rate.take)
+    rate.not  = 1 - rate.take
+    )
 
@@
 d_support <- d_transactions %>%
-  mutate(
-    grade_round = round(Grade)
-  ) %>%
   group_by(
@@
     rate.low  = mean(HL == "low"),
-    rate.0    = mean(grade_round <= 0),
-    rate.1    = mean(grade_round <= 1),
-    rate.2    = mean(grade_round <= 2),
-    rate.3    = mean(grade_round <= 3),
-    rate.4    = mean(grade_round <= 4),
-    rate.5    = mean(grade_round <= 5),
-    rate.6    = mean(grade_round <= 6),
-    rate.7    = mean(grade_round <= 7),
-    rate.8    = mean(grade_round <= 8),
-    rate.9    = mean(grade_round <= 9),
-    rate.10   = mean(grade_round <= 10)
+    rate.0    = mean(Grade <= 0),
+    rate.1    = mean(Grade <= 1),
+    rate.2    = mean(Grade <= 2),
+    rate.3    = mean(Grade <= 3),
+    rate.4    = mean(Grade <= 4),
+    rate.5    = mean(Grade <= 5),
+    rate.6    = mean(Grade <= 6),
+    rate.7    = mean(Grade <= 7),
+    rate.8    = mean(Grade <= 8),
+    rate.9    = mean(Grade <= 9),
+    rate.10   = mean(Grade <= 10)
     )

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code

@@
 
+#
 # Number of students
@@
 
+#
 # Probability of taking a course
@@
 
+#
 # Probability of failing, having a low grade, having a grade less than x per course
@@
 
-#
-# For convenience
 make_transaction <- function(data = d_transactions, item = item){
@@
 # Checking transactions
-#inspect(head(transactions_Grade, 10))
+# inspect(head(transactions, 10))
 
@@
 
-#
-# For convenience
 make_sequence <- function(data = d_transactions, item = item){
@@
   sequences <- data %>%
-    filter(!is.na(eventID))%>% #this is here casue we have courses that were never taken.
+    filter(
+      !is.na(eventID) #this is here casue we have courses that were never taken.
+      ) %>% 
     group_by(
@@
 
+  # indicating sequence ID and event ID for each transaction
   sequences@itemsetInfo <- select(
@@
 
-      # Chosen parameters
+      # include all AR possible
       parameter = list(
@@
         conf   = 0, # min confidence
-        minlen = 2,  # min length of 
+        minlen = 2, # min length of rule
         maxlen = 2  # max length of rule
@@
 
-  type_rule_enquo <- enquo(type_rule)
-
   AR %>%
@@
     left_join(
-      select(data_support, item, !!type_rule_enquo),
+      select(data_support, item, !!enquo(type_rule)),
       by = c("rhs_course" = "item")
@@
     mutate(
-      rhs.support = !!type_rule_enquo
+      rhs.support = !!enquo(type_rule)
       )
@@
 
-We encapsulate the three functions `my_apriori()`, `clean_AR()` and `compute_support` into the function `make_AR()`.
+We encapsulate the four functions `my_apriori()`, `clean_AR()`, `compute_support()` and `editing_AR()` into the function `make_AR()`.
 
 ```{r make_AR}
-make_AR <- function(data,
-                    data_support, type_rule){
+make_AR <- function(data, data_support, type_rule){
 
@@
 
-```{r AR, cache = TRUE}
-
-#
-# AR taken (confidence and lift already correct)
+```{r AR take}
 AR_taken <- transactions %>%
@@
 
-#
-# AR fail
+rm(transactions)
+```
+
+```{r AR fail}
 AR_PF <- transactions_PF %>%
+
   make_AR(
@@
 
-  # Confidence and Lift
+  # Confidence and Lift by hand
   separate(
@@
 
-#
-# AR low
+rm(transactions_PF)
+```
+
+```{r AR low}
 AR_HL <- transactions_HL %>%
+
   make_AR(
@@
 
-#
-# AR not taken / fail / pass
+rm(transactions_HL)
+```
 
+```{r AR TPF}
 AR_TPF <- transactions_TPF %>%
@@
     confidence          = support / lhs.rhsTake.support,
-    lift                = confidence / (rhs.support + 1e-4) # increase denominator by smal value to avoid dividing by 0.
+    lift                = confidence / rhs.support
     ) %>%
@@
 
-rm(transactions, transactions_PF, transactions_HL, transactions_TPF)
+rm(transactions_TPF)
 ```

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code
d_support_G

@@
 # Probability of taking a course
-d_support_take <- d_transactions %>%
+d_support_TNT <- d_transactions %>%
   distinct(
@@
 # Probability of failing, having a low grade, having a grade less than x per course
-d_support <- d_transactions %>%
+d_support_PF_HL <- d_transactions %>%
   group_by(
@@
     rate.fail = mean(PF == "fail"),
-    rate.low  = mean(HL == "low"),
-    rate.0    = mean(Grade <= 0),
-    rate.1    = mean(Grade <= 1),
-    rate.2    = mean(Grade <= 2),
-    rate.3    = mean(Grade <= 3),
-    rate.4    = mean(Grade <= 4),
-    rate.5    = mean(Grade <= 5),
-    rate.6    = mean(Grade <= 6),
-    rate.7    = mean(Grade <= 7),
-    rate.8    = mean(Grade <= 8),
-    rate.9    = mean(Grade <= 9),
-    rate.10   = mean(Grade <= 10)
+    rate.low  = mean(HL == "low")
+    )
+
+#
+# Probability oh having a grade equal or lower than x
+d_support_G <- d_transactions %>%
+  group_by(
+    item
+    ) %>%
+  summarise(
+    `0`    = mean(Grade <= 0),
+    `1`    = mean(Grade <= 1),
+    `2`    = mean(Grade <= 2),
+    `3`    = mean(Grade <= 3),
+    `4`    = mean(Grade <= 4),
+    `5`    = mean(Grade <= 5),
+    `6`    = mean(Grade <= 6),
+    `7`    = mean(Grade <= 7),
+    `8`    = mean(Grade <= 8),
+    `9`    = mean(Grade <= 9),
+    `10`   = mean(Grade <= 10)
+    ) %>%
+  gather(
+    key   = grade_ceil,
+    value = support.grade,
+    `0` : `10`,
+    convert = TRUE
     )
@@
 
-```{r AR grade (by hand)}
+```{r AR grade}
+AR_G <- transactions_G %>%
 
-#
-# d_support
-d_support_grade <- d_support %>%
-  gather(
-    key   = grade_round,
-    value = support.grade,
-    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
-    ) %>%
-  mutate( 
-    grade_round = substr(grade_round, start = 6, stop = 7),
-    grade_round = as.numeric(grade_round)
-    ) %>%
-  select(-c(rate.fail, rate.low))
-
-# Make AR
-AR_G <- transactions_G %>%
   my_apriori(appearance = NULL) %>%

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 #
-# Probability of failing, having a low grade, having a grade less than x per course
+# Probability of failing, having a low grade
 d_support_PF_HL <- d_transactions %>%

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

@@
 ### Grade
-```{r transactions expanded}
+```{r transactions grade}
 
@@
     value = X,
-    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
+    `0` :`10`, 
     na.rm   = TRUE, 

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
not_taken --> fail rules

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
   mutate(
-    grade_ceil = ceiling(Grade),
+    Round_grade = round(Grade, 0),
     Values = TRUE
@@
   spread(
-    key   = grade_ceil, 
+    key   = Round_grade, 
     value = Values
@@
   gather(
-    key   = grade_ceil,
+    key = Grade_round,
     value = X,
@@
     -X
-    ) %>%
+    )%>%
 
@@
   mutate(
-    item_G = paste(item, grade_ceil, sep = "_")
+    item_G = paste(item, Grade_round, sep = "_")
     )
@@
 ```
+### Manual rules
+```{r}
+not_take_fail_rules <- d_cumulative_transcript     %>%
+  select(sequenceID, eventID, item, course_not)    %>%
+  unnest(item, .drop = F)                          %>%
+  unnest(course_not)                               %>%
+  left_join(
+    select(d_transactions, 
+           sequenceID, eventID, item, PF), 
+    by= c("sequenceID", "eventID", "item")
+    )                                              %>%
+  select(sequenceID,eventID, course_not, item, PF) %>%
+  rename(
+    lhs="course_not", 
+    rhs.x = "item", 
+    rhs.PF = "PF")                                 %>%
+  mutate(num_transactions = n())                   %>%
+  group_by(lhs)                                    %>%
+  mutate(
+    num_lhs = n(),
+    support_lhs         = num_lhs / num_transactions
+    )                                              %>%
+  group_by(rhs.x)                                  %>%
+  mutate(
+    num_rhs.x           = n(),
+    support_rhs.x       = num_rhs.x / num_transactions
+         )                                         %>%
+  group_by(rhs.x,rhs.PF)                           %>%
+  mutate(
+    num_rhs.PF          = n(),
+    support_rhs.PF      = num_rhs.PF / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x)                             %>%
+  mutate(
+    num_rule_x          = n(),
+    support_rule_rhs.x  = num_rule_x / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x, rhs.PF)                     %>%
+  mutate(
+    num_rule_PF          = n(),
+    support_rule_rhs.PF  = num_rule_PF / num_transactions,
+    support_rhs_bounded  = num_rule_PF / num_rule_x
+         )                                         %>%
+  ungroup()                                        %>%
+  mutate(
+    confidence                   = support_rule_rhs.PF / support_lhs,
+    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
+    lift                         = confidence / support_rhs.PF,
+    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
+  )
+```
 
@@
 
-#
 # Number of students
@@
   select(sequenceID) %>%
-  n_distinct
+  n_distinct()
 
-#
-# Probability of taking a course
-d_support_TNT <- d_transactions %>%
+# Probability of taken a course
+d_support_take <- d_transactions %>%
   distinct(
@@
     ) %>%
-  count(
+  group_by(
     item
     ) %>%
-  mutate(
-    rate.take = n / n_students,
+  summarise(
+    count     = n(),
+    rate.take = count / n_students,
     rate.not  = 1 - rate.take
@@
 
-#
-# Probability of failing, having a low grade
-d_support_PF_HL <- d_transactions %>%
+# Probability of failing, having a low grade, having a grade less than x per course
+d_support <- d_transactions %>%
+  mutate(
+    grade_round = round(Grade)
+  ) %>%
   group_by(
@@
     rate.fail = mean(PF == "fail"),
-    rate.low  = mean(HL == "low")
-    )
-
-#
-# Probability oh having a grade equal or lower than x
-d_support_G <- d_transactions %>%
-  group_by(
-    item
-    ) %>%
-  summarise(
-    `0`    = mean(Grade <= 0),
-    `1`    = mean(Grade <= 1),
-    `2`    = mean(Grade <= 2),
-    `3`    = mean(Grade <= 3),
-    `4`    = mean(Grade <= 4),
-    `5`    = mean(Grade <= 5),
-    `6`    = mean(Grade <= 6),
-    `7`    = mean(Grade <= 7),
-    `8`    = mean(Grade <= 8),
-    `9`    = mean(Grade <= 9),
-    `10`   = mean(Grade <= 10)
-    ) %>%
-  gather(
-    key   = grade_ceil,
-    value = support.grade,
-    `0` : `10`,
-    convert = TRUE
+    rate.low  = mean(HL == "low"),
+    rate.0    = mean(grade_round <= 0),
+    rate.1    = mean(grade_round <= 1),
+    rate.2    = mean(grade_round <= 2),
+    rate.3    = mean(grade_round <= 3),
+    rate.4    = mean(grade_round <= 4),
+    rate.5    = mean(grade_round <= 5),
+    rate.6    = mean(grade_round <= 6),
+    rate.7    = mean(grade_round <= 7),
+    rate.8    = mean(grade_round <= 8),
+    rate.9    = mean(grade_round <= 9),
+    rate.10   = mean(grade_round <= 10)
     )
@@
 
+#
+# For convenience
 make_transaction <- function(data = d_transactions, item = item){
@@
 # Checking transactions
-# inspect(head(transactions, 10))
+#inspect(head(transactions_Grade, 10))
 
@@
 
+#
+# For convenience
 make_sequence <- function(data = d_transactions, item = item){
@@
   sequences <- data %>%
-    filter(
-      !is.na(eventID) #this is here casue we have courses that were never taken.
-      ) %>% 
+    filter(!is.na(eventID))%>% #this is here casue we have courses that were never taken.
     group_by(
@@
 
-  # indicating sequence ID and event ID for each transaction
   sequences@itemsetInfo <- select(
@@
 
-      # include all AR possible
+      # Chosen parameters
       parameter = list(
@@
         conf = 0,    # min confidence
-        minlen = 2, # min length of rule
+        minlen = 2,  # min length of 
         maxlen = 2  # max length of rule
@@
 
+  type_rule_enquo <- enquo(type_rule)
+
   AR %>%
@@
     left_join(
-      select(data_support, item, !!enquo(type_rule)),
+      select(data_support, item, !!type_rule_enquo),
       by = c("rhs_course" = "item")
@@
     mutate(
-      rhs.support = !!enquo(type_rule)
+      rhs.support = !!type_rule_enquo
       )
@@
 
-We encapsulate the four functions `my_apriori()`, `clean_AR()`, `compute_support()` and `editing_AR()` into the function `make_AR()`.
+We encapsulate the three functions `my_apriori()`, `clean_AR()` and `compute_support` into the function `make_AR()`.
 
 ```{r make_AR}
-make_AR <- function(data, data_support, type_rule){
+make_AR <- function(data,
+                    data_support, type_rule){
 
@@
 
-```{r AR take}
+```{r AR, cache = TRUE}
+
+#
+# AR taken (confidence and lift already correct)
 AR_taken <- transactions %>%
@@
 
-rm(transactions)
-```
-
-```{r AR fail}
+#
+# AR fail
 AR_PF <- transactions_PF %>%
-
   make_AR(
@@
 
-  # Confidence and Lift by hand
+  # Confidence and Lift
   separate(
@@
 
-rm(transactions_PF)
-```
-
-```{r AR low}
+#
+# AR low
 AR_HL <- transactions_HL %>%
-
   make_AR(
@@
 
-rm(transactions_HL)
-```
+#
+# AR not taken / fail / pass
 
-```{r AR TPF}
 AR_TPF <- transactions_TPF %>%
@@
     confidence          = support / lhs.rhsTake.support,
-    lift                = confidence / rhs.support
+    lift                = confidence / (rhs.support + 1e-4) # some courses have a failure rate of 0%.
     ) %>%
@@
 
-rm(transactions_TPF)
+rm(transactions, transactions_PF, transactions_HL, transactions_TPF)
 ```
 
-```{r AR grade}
+```{r AR grade (by hand)}
+
+#
+# d_support
+d_support_grade <- d_support %>%
+  gather(
+    key   = grade_round,
+    value = support.grade,
+    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
+    ) %>%
+  mutate( 
+    grade_round = substr(grade_round, start = 6, stop = 7),
+    grade_round = as.numeric(grade_round)
+    ) %>%
+  select(-c(rate.fail, rate.low))
+
+# Make AR
 AR_G <- transactions_G %>%
-
   my_apriori(appearance = NULL) %>%

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
          total_past_courses = map(.f=length, .x=full_past))
+```
+### Manual rules
+```{r}
+not_take_fail_rules <- d_cumulative_transcript     %>%
+  select(sequenceID, eventID, item, course_not)    %>%
+  unnest(item, .drop = F)                          %>%
+  unnest(course_not)                               %>%
+  left_join(
+    select(d_transactions, 
+           sequenceID, eventID, item, PF), 
+    by= c("sequenceID", "eventID", "item")
+    )                                              %>%
+  select(sequenceID,eventID, course_not, item, PF) %>%
+  rename(
+    lhs="course_not", 
+    rhs.x = "item", 
+    rhs.PF = "PF")                                 %>%
+  mutate(num_transactions = n())                   %>%
+  group_by(lhs)                                    %>%
+  mutate(
+    num_lhs = n(),
+    support_lhs         = num_lhs / num_transactions
+    )                                              %>%
+  group_by(rhs.x)                                  %>%
+  mutate(
+    num_rhs.x           = n(),
+    support_rhs.x       = num_rhs.x / num_transactions
+         )                                         %>%
+  group_by(rhs.x,rhs.PF)                           %>%
+  mutate(
+    num_rhs.PF          = n(),
+    support_rhs.PF      = num_rhs.PF / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x)                             %>%
+  mutate(
+    num_rule_x          = n(),
+    support_rule_rhs.x  = num_rule_x / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x, rhs.PF)                     %>%
+  mutate(
+    num_rule_PF          = n(),
+    support_rule_rhs.PF  = num_rule_PF / num_transactions,
+    support_rhs_bounded  = num_rule_PF / num_rule_x
+         )                                         %>%
+  ungroup()                                        %>%
+  mutate(
+    confidence                   = support_rule_rhs.PF / support_lhs,
+    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
+    lift                         = confidence / support_rhs.PF,
+    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
+  )
 ```

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
confidence and lift of AR grade

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ### Support
-
 ```{r}
@@
 ```{r my_apriori}
-
 my_apriori <- function(data){
@@
 ```{r clean_AR}
-
 clean_AR <- function(AR){
@@
   make_AR(
-    data_support = d_support_take, 
+    data_support = d_support_TNT, 
     type_rule = rate.take
@@
   make_AR(
-    data_support = d_support,
+    data_support = d_support_PF_HL,
     type_rule = rate.fail
@@
   make_AR(
-    data_support = d_support,
+    data_support = d_support_PF_HL,
     type_rule = rate.low
@@
 AR_TPF <- transactions_TPF %>%
+
   make_AR(
-    data_support = d_support, 
+    data_support = d_support_PF_HL, 
     type_rule = rate.fail
@@
 
-  my_apriori(appearance = NULL) %>%
+  my_apriori %>%
   clean_AR %>%
 
-  # include rhs.support by hand
+  # separate rhs and lhs
   separate(
     rhs,
-    into = c("item", "grade_round"), 
+    into = c("rhs_course", "rhs_grade"),
     sep = "_",
@@
     ) %>%
+  separate(
+    lhs,
+    into = c("lhs_course", "lhs_grade"),
+    sep = "_",
+    remove = FALSE,
+    convert = TRUE
+    ) %>%
+
+  # rhs.support
   left_join(
-    d_support_grade,
-    by = c("item", "grade_round")
+    d_support_G,
+    by = c("rhs_course" = "item", "rhs_grade" = "grade_ceil")
     ) %>%
@@
 
+  # Confidence and lift
+    separate(
+    rhs,
+    sep = "_",
+    into = c("rhs_course", "rhs_outcome"),
+    remove = FALSE
+    ) %>%
+  group_by(
+    lhs, 
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = max(support),
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / rhs.support
+    ) %>%
+  ungroup %>%
+
+  # exclude rules with same course on lhs and rhs
+  filter(
+    lhs_course != rhs_course,
+    count >= 10
+    ) %>%
+
+  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
+  group_by(
+    lhs_course, 
+    rhs_course
+    ) %>%
+  top_n(
+    1,
+    lift
+    ) %>%
+
   editing_AR
 
-rm(d_support_grade, transactions_G)
+#rm(d_support_grade, transactions_G)
 ```

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
clean AR_G

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-  # exclude rules with same course on lhs and rhs
+  # reduce number of rules
   filter(
-    lhs_course != rhs_course,
-    count >= 10
+    lhs_course != rhs_course, # exclude rules with same course on lhs and rhs
+    count >= 5,               
+    rhs_grade == 6            
     ) %>%
@@
     ) %>%
+  ungroup %>%
 

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
debuged until CSPADE

@@
 ---
-
-```{r TODO}
-
-```
 
@@
 sequences_HL  <- make_sequence(item = item_HL)
-#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
-#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
+#sequences_TPF <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
 sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )
@@
 
-rm(make_sequence)
+rm(make_sequence,
+   d_transactions, d_transactions_TPF, d_transactions_G)
 ```
@@
 
-rm(transactions)
+rm(transactions, d_support_TNT)
 ```
@@
 
-rm(transactions_TPF)
+rm(transactions_TPF, d_support_PF_HL)
 ```
@@
 
-#rm(d_support_grade, transactions_G)
+rm(transactions_G, d_support_G)
 ```
@@
 # Remove objects
-rm(my_apriori, clean_AR, compute_metrics, make_AR,
-   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G)
+rm(my_apriori, clean_AR, compute_metrics, editing_AR, make_AR,
+   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
+   n_students)
 ```

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
does nothing

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 d_past_student_course <- d_cumulative_transcript %>%
-  select(sequenceID, eventID, item, course_past)%>%
+  select(sequenceID, eventID, item, course_past) %>%
   unnest(item, .drop=F)
@@
 ### Support
+
 ```{r}
@@
 ```{r my_apriori}
+
 my_apriori <- function(data){
@@
 ```{r clean_AR}
+
 clean_AR <- function(AR){
@@
   make_AR(
-    data_support = d_support_TNT, 
+    data_support = d_support_take, 
     type_rule = rate.take
@@
   make_AR(
-    data_support = d_support_PF_HL,
+    data_support = d_support,
     type_rule = rate.fail
@@
   make_AR(
-    data_support = d_support_PF_HL,
+    data_support = d_support,
     type_rule = rate.low
@@
 AR_TPF <- transactions_TPF %>%
-
   make_AR(
-    data_support = d_support_PF_HL, 
+    data_support = d_support, 
     type_rule = rate.fail
@@
 
-  my_apriori %>%
+  my_apriori(appearance = NULL) %>%
   clean_AR %>%
 
-  # separate rhs and lhs
+  # include rhs.support by hand
   separate(
     rhs, 
-    into = c("rhs_course", "rhs_grade"),
+    into = c("item", "grade_round"), 
     sep = "_",
@@
     ) %>%
-  separate(
-    lhs,
-    into = c("lhs_course", "lhs_grade"),
-    sep = "_",
-    remove = FALSE,
-    convert = TRUE
-    ) %>%
-
-  # rhs.support
   left_join(
-    d_support_G,
-    by = c("rhs_course" = "item", "rhs_grade" = "grade_ceil")
+    d_support_grade,
+    by = c("item", "grade_round")
     ) %>%
@@
 
-  # Confidence and lift
-    separate(
-    rhs,
-    sep = "_",
-    into = c("rhs_course", "rhs_outcome"),
-    remove = FALSE
-    ) %>%
-  group_by(
-    lhs, 
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = max(support),
-    confidence          = support / lhs.rhsTake.support,
-    lift                = confidence / rhs.support
-    ) %>%
-  ungroup %>%
-
-  # exclude rules with same course on lhs and rhs
-  filter(
-    lhs_course != rhs_course,
-    count >= 10
-    ) %>%
-
-  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
-  group_by(
-    lhs_course, 
-    rhs_course
-    ) %>%
-  top_n(
-    1,
-    lift
-    ) %>%
-
     editing_AR
 
-#rm(d_support_grade, transactions_G)
+rm(d_support_grade, transactions_G)
 ```

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
use of lists to simplify environment

--- 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 load("Output/data_pillar_1.RDATA")
+```
+
+```{r}
+pass_grade <- 5.5
+high_grade <- 6.5
 ```
@@
 ```{r AR data prep 1}
+d_transactions <- list()
 
-#
-# Threshold: pass grade, high grade
-pass_grade <- 5.5
-high_grade <- 6.5
-
-#
-# Transactions
-d_transactions <- d_course %>%
+d_transactions$taken_PF_HL <- d_course %>%
 
@@
 ```{r transactions not taken}
-d_transactions_TPF <- expand.grid(
+d_transactions$TPF <- expand.grid(
 
   # Expand along students (sequenceID) and courses (itemID)
-  sequenceID = unique(d_transactions$sequenceID),
-  item       = unique(d_transactions$item),
+  sequenceID = unique(d_transactions$taken_PF_HL$sequenceID),
+  item       = unique(d_transactions$taken_PF_HL$item),
   stringsAsFactors = FALSE
@@
   left_join(
-    d_transactions, 
+    d_transactions$taken_PF_HL, 
     by = c("sequenceID", "item")
@@
 
-d_transactions_G <- d_transactions %>%
+d_transactions$G <- d_transactions$taken_PF_HL %>%
 
@@
 # Number of students
-n_students <- d_transactions %>%
+n_students <- d_transactions$taken_PF_HL %>%
   select(sequenceID) %>%
@@
 #
+# Support
+d_support <- list()
+
 # Probability of taking a course
-d_support_TNT <- d_transactions %>%
+d_support$TNT <- d_transactions$taken_PF_HL %>%
   distinct(
@@
 # Probability of failing, having a low grade
-d_support_PF_HL <- d_transactions %>%
+d_support$PF_HL <- d_transactions$taken_PF_HL %>%
   group_by(
@@
 # Probability oh having a grade equal or lower than x
-d_support_G <- d_transactions %>%
+d_support$G <- d_transactions$taken_PF_HL %>%
   group_by(
@@
 
-make_transaction <- function(data = d_transactions, item = item){
+make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){
 
@@
     summarise(
-      list_item = list(!!enquo(item))
+      list_item = list(unique(!!enquo(item)))
     ) %>%
@@
 # Making transactions
-transactions     <- make_transaction(item = item   )
-transactions_PF  <- make_transaction(item = item_PF)
-transactions_HL  <- make_transaction(item = item_HL)
-transactions_TPF <- make_transaction(data = d_transactions_TPF, item = item_TPF)
-transactions_G   <- make_transaction(data = d_transactions_G  , item = item_G  )
+transactions <- list()
+
+transactions$taken <- make_transaction(item = item   )
+transactions$PF    <- make_transaction(item = item_PF)
+transactions$HL    <- make_transaction(item = item_HL)
+transactions$TPF   <- make_transaction(data = d_transactions$TPF, item = item_TPF)
+transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )
 
@@
 
-make_sequence <- function(data = d_transactions, item = item){
+make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){
 
@@
 # Making sequences
-sequences     <- make_sequence(item = item   )
-sequences_PF  <- make_sequence(item = item_PF)
-sequences_HL  <- make_sequence(item = item_HL)
+sequences <- list()
+
+sequences$taken <- make_sequence(item = item   )
+sequences$PF    <- make_sequence(item = item_PF)
+sequences$HL    <- make_sequence(item = item_HL)
 #sequences_TPF <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
-sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )
+sequences$G   <- make_sequence(data = d_transactions$G    , item = item_G  )
 
@@
 
-rm(make_sequence,
-   d_transactions, d_transactions_TPF, d_transactions_G)
+rm(make_sequence, d_transactions)
 ```
@@
 
-```{r editing_AR}
-editing_AR <- function(AR){
-
-  AR %>%
-    mutate_at(
-      c("support", 
-        "confidence", "rhs.support",
-        "lift"
-        ),
-      funs(round(., 5))
-    ) %>%
-    select(
-      lhs, rhs,
-      support, count,
-      confidence, rhs.support,
-      lift
-    ) %>%
-    arrange(
-      desc(count)
-    )
-
-}
-```
-
-We encapsulate the four functions `my_apriori()`, `clean_AR()`, `compute_support()` and `editing_AR()` into the function `make_AR()`.
+We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
 
@@
       type_rule = !!enquo(type_rule)
-      ) %>%
-    editing_AR
+      )
 
@@
 ```{r AR take}
-AR_taken <- transactions %>%
+AR <- list()
+
+AR$taken <- transactions$taken %>%
   make_AR(
-    data_support = d_support_TNT, 
+    data_support = d_support$TNT, 
     type_rule = rate.take
@@
 
-rm(transactions, d_support_TNT)
 ```
@@
 ```{r AR fail}
-AR_PF <- transactions_PF %>%
+AR$PF <- transactions$PF %>%
 
   make_AR(
-    data_support = d_support_PF_HL,
+    data_support = d_support$PF_HL,
     type_rule = rate.fail
@@
     str_detect(lhs, "fail"),
-    str_detect(rhs, "fail"),
-    count >= 5
-    ) %>%
-  select(
-    - c(rhs_outcome, rhs_course)
+    str_detect(rhs, "fail")
     )
-
-rm(transactions_PF)
 ```
@@
 ```{r AR low}
-AR_HL <- transactions_HL %>%
+AR$HL <- transactions$HL %>%
 
   make_AR(
-    data_support = d_support_PF_HL,
+    data_support = d_support$PF_HL,
     type_rule = rate.low
@@
     str_detect(lhs, "low"),
-    str_detect(rhs, "low"),
-    count >= 5
-    ) %>%
-  select(
-    - c(rhs_outcome, rhs_course)
+    str_detect(rhs, "low")
     )
-
-rm(transactions_HL)
 ```
@@
 ```{r AR TPF}
-AR_TPF <- transactions_TPF %>%
+AR$TPF <- transactions$TPF %>%
 
   make_AR(
-    data_support = d_support_PF_HL, 
+    data_support = d_support$PF_HL, 
     type_rule = rate.fail
@@
   mutate(
-    rhs.take = str_detect(rhs, "fail|pass")
+    rhs.taken = str_detect(rhs, "fail|pass")
     ) %>%
@@
   mutate(
-    lhs.rhsTake.support = sum(support * rhs.take),
+    lhs.rhsTake.support = sum(support * rhs.taken),
     confidence          = support / lhs.rhsTake.support,
@@
     str_detect(lhs, "not taken"),
-    str_detect(rhs, "fail"),
-    count >= 5
-    ) %>%
-  select(
-    - c(rhs_outcome, rhs_course, rhs.take)
+    str_detect(rhs, "fail")
     )
-
-rm(transactions_TPF, d_support_PF_HL)
 ```
@@
 ```{r AR grade}
-AR_G <- transactions_G %>%
+AR$G <- transactions$G %>%
 
@@
   left_join(
-    d_support_G,
+    d_support$G,
     by = c("rhs_course" = "item", "rhs_grade" = "grade_ceil")
@@
   # Confidence and lift
-  separate(
-    rhs,
-    sep = "_",
-    into = c("rhs_course", "rhs_outcome"),
-    remove = FALSE
-    ) %>%
   group_by(
@@
     lhs_course != rhs_course, # exclude rules with same course on lhs and rhs        
-    count >= 5,               
     rhs_grade == 6            
@@
     ) %>%
-  ungroup %>%
+  ungroup
+```
 
-  editing_AR
+```{r edit_AR}
+edit_AR <- function(AR){
 
-rm(transactions_G, d_support_G)
+  AR %>%
+    filter(
+      count >= 5
+      ) %>%
+    mutate_if(
+      is.numeric,
+      funs(round(., 5))
+    ) %>%
+    select(
+      lhs, rhs,
+      support, count,
+      confidence, rhs.support,
+      lift, 
+      everything(),
+      - matches("rate|course|grade|outcome|taken")
+    ) %>%
+    arrange(
+      desc(count)
+    )
+
+}
+
+AR <- lapply(
+  X   = AR,
+  FUN = edit_AR
+    )
 ```
@@
 # Save association rules
-save(AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
+save(AR,
      file = "App/AR.RDATA")
@@
 # Remove objects
-rm(my_apriori, clean_AR, compute_metrics, editing_AR, make_AR,
-   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
-   n_students)
+rm(my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
+   AR)
 ```

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
list for sequences

@@
     summarise(
-      list_item = list(!!enquo(item))
+      list_item = list(unique(!!enquo(item)))
     ) %>%
+    ungroup %>%
     arrange(
@@
     ) %>%
-    ungroup %>%
     pull(
@@
 # Save association rules
-save(AR,
-     file = "App/AR.RDATA")
+save(
+  AR,
+  file = "App/AR.RDATA"
+  )
 
 # Remove objects
-rm(my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
-   AR)
+rm(
+  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
+  AR
+  )
 ```

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
re-organize and re-name headers

@@
 
-# Association Rules and Sequence Rules
+# Creating Transactions and Sequences
 For a first exploration of arules, we conceptualise our framework like this:
@@
 
-## Data Prep: Creating Transactions and Sequences
 First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts. 
-
-### take, fail, low grade
+## Data Preparation
+### Take, fail, low grade
 ```{r AR data prep 1}
@@
 
-### take / not take, pass / fail / not take
+### Take / not take, pass / fail / not take
 ```{r transactions not taken}
@@
 ```
-### Additional General Dataframes for courses
+## Additional General Dataframes for courses
 #### Transcript with Preceding courses per student
@@
 
-### Support
+## Transactions
+```{r making transactions, message = FALSE}
+
+make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){
+
+  data %>%
+    group_by(
+      sequenceID
+    ) %>%
+    summarise(
+      list_item = list(unique(!!enquo(item)))
+    ) %>%
+    ungroup %>%
+    pull(
+      list_item
+      ) %>%
+    as("transactions")
+
+}
+
+#
+# Making transactions
+transactions <- list()
+
+transactions$taken <- make_transaction(item = item   )
+transactions$PF    <- make_transaction(item = item_PF)
+transactions$HL    <- make_transaction(item = item_HL)
+transactions$TPF   <- make_transaction(data = d_transactions$TPF, item = item_TPF)
+transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )
+
+#
+# Checking transactions
+# inspect(head(transactions, 10))
+
+rm(make_transaction)
+```
+
+## Sequences
+```{r making sequences}
+
+make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){
+
+  sequences <- data %>%
+    filter(
+      !is.na(eventID) #this is here casue we have courses that were never taken.
+      ) %>% 
+    group_by(
+      sequenceID,
+      eventID
+    ) %>%
+    summarise(
+      list_item = list(unique(!!enquo(item)))
+    ) %>%
+    ungroup %>%
+    arrange(
+      sequenceID,
+      eventID
+    ) %>%
+    pull(
+      list_item
+      ) %>%
+    as("transactions")
+
+  # indicating sequence ID and event ID for each transaction
+  sequences@itemsetInfo <- select(
+    data,
+    sequenceID,
+    eventID
+    ) %>%
+    as.data.frame
+
+  return(sequences)
+
+}
+
+#
+# Making sequences
+sequences <- list()
+
+sequences$taken <- make_sequence(item = item   )
+sequences$PF    <- make_sequence(item = item_PF)
+sequences$HL    <- make_sequence(item = item_HL)
+#sequences_TPF  <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
+sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )
+
+#
+# Checking sequences
+# inspect(head(sequences_G, 10))
+
+rm(make_sequence, d_transactions)
+```
+
+## Support
 ```{r}
@@
     )
-
 ```
 
-### Transactions for Apriori
-```{r making transactions, message = FALSE}
+# Mining Rules
+## Association Rule
 
-make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){
-
-  data %>%
-    group_by(
-      sequenceID
-    ) %>%
-    summarise(
-      list_item = list(unique(!!enquo(item)))
-    ) %>%
-    ungroup %>%
-    pull(
-      list_item
-      ) %>%
-    as("transactions")
-
-}
-
-#
-# Making transactions
-transactions <- list()
-
-transactions$taken <- make_transaction(item = item   )
-transactions$PF    <- make_transaction(item = item_PF)
-transactions$HL    <- make_transaction(item = item_HL)
-transactions$TPF   <- make_transaction(data = d_transactions$TPF, item = item_TPF)
-transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )
-
-#
-# Checking transactions
-# inspect(head(transactions, 10))
-
-rm(make_transaction)
-```
-
-### Sequences for CSPADE
-```{r making sequences}
-
-make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){
-
-  sequences <- data %>%
-    filter(
-      !is.na(eventID) #this is here casue we have courses that were never taken.
-      ) %>% 
-    group_by(
-      sequenceID,
-      eventID
-    ) %>%
-    summarise(
-      list_item = list(unique(!!enquo(item)))
-    ) %>%
-    ungroup %>%
-    arrange(
-      sequenceID,
-      eventID
-    ) %>%
-    pull(
-      list_item
-      ) %>%
-    as("transactions")
-
-  # indicating sequence ID and event ID for each transaction
-  sequences@itemsetInfo <- select(
-    data,
-    sequenceID,
-    eventID
-    ) %>%
-    as.data.frame
-
-  return(sequences)
-
-}
-
-#
-# Making sequences
-sequences <- list()
-
-sequences$taken <- make_sequence(item = item   )
-sequences$PF    <- make_sequence(item = item_PF)
-sequences$HL    <- make_sequence(item = item_HL)
-#sequences_TPF  <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
-sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )
-
-#
-# Checking sequences
-# inspect(head(sequences_G, 10))
-
-rm(make_sequence, d_transactions)
-```
-
-## Mining Rules
-### Apriori Algorithm
+### Functions
 
@@
 The function `compute_support()` computes the support of the lhs and rhs of the rules.
-
 ```{r compute_support}
@@
 We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
-
 ```{r make_AR}
@@
 
+### take -> taken
 ```{r AR take}
@@
 
+### fail -> fail
 ```{r AR fail}
@@
 
+### low grade -> low grade
 ```{r AR low}
@@
 
+### not take -> fail
 ```{r AR TPF}
@@
 
+### less than x grade -> less than 6
 ```{r AR grade}
@@
 
+### Editing AR
 ```{r edit_AR}
@@
 
+### Save Association Rules
 We save and remove objects:
@@
 
-### CSPADE Algorithm
+## Sequence Rules
 ##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
trivial change
re-organize sections

@@
 ```
-## Additional General Dataframes for courses
-#### Transcript with Preceding courses per student
+
+### Transcript with Preceding courses per student
 ```{r}
@@
 
-#### Courses that were taken before each course
+### Courses that were taken before each course
 ```{r}
@@
 sequences$HL    <- make_sequence(item = item_HL)
-#sequences_TPF  <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
+#sequences_TPF  <- make_sequence(data = d_transactions$TPF, item = item_TPF) # compute ad hoc
 sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )
@@
   my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
-  AR
+  AR, transaction
   )
@@
 ## Sequence Rules
-##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
+
+###TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
 

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
computes SR_TPF manually

@@
 
+SR_TPF are manually computed
+```{r}
+# current, past, not_yet
+SR_TPF <- d_cumulative_transcript                  %>%
+  select(sequenceID, eventID, item, course_not)    %>%
+  unnest(item, .drop = F)                          %>%
+  unnest(course_not)                               %>%
+  left_join(
+    select(d_transactions, 
+           sequenceID, eventID, item, PF), 
+    by= c("sequenceID", "eventID", "item")
+    )                                              %>%
+  select(sequenceID,eventID, course_not, item, PF) %>%
+  rename(
+    lhs="course_not", 
+    rhs.x = "item", 
+    rhs.PF = "PF")                                 %>%
+  mutate(num_transactions = n())                   %>%
+  group_by(lhs)                                    %>%
+  mutate(
+    num_lhs = n(),
+    support_lhs         = num_lhs / num_transactions
+    )                                              %>%
+  group_by(rhs.x)                                  %>%
+  mutate(
+    num_rhs.x           = n(),
+    support_rhs.x       = num_rhs.x / num_transactions
+         )                                         %>%
+  group_by(rhs.x,rhs.PF)                           %>%
+  mutate(
+    num_rhs.PF          = n(),
+    support_rhs.PF      = num_rhs.PF / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x)                             %>%
+  mutate(
+    num_rule_x          = n(),
+    support_rule_rhs.x  = num_rule_x / num_transactions
+  )                                                %>%
+  group_by(lhs, rhs.x, rhs.PF)                     %>%
+  mutate(
+    num_rule_PF          = n(),
+    support_rule_rhs.PF  = num_rule_PF / num_transactions,
+    support_rhs_bounded  = num_rule_PF / num_rule_x
+         )                                         %>%
+  ungroup()                                        %>%
+  mutate(
+    confidence                   = support_rule_rhs.PF / support_lhs,
+    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
+    lift                         = confidence / support_rhs.PF,
+    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
+  )
+```
+
 We save and remove objects:

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
include summary at type level

@@
 
+# Type level
+statistics_type <- d_transcript %>%
+  inner_join(d_course, by = "Course ID") %>%
+  filter(!is.na(Type)) %>%
+  group_by(Type) %>%
+  provide_statistics()
+
 # Concentration evel
@@
 
-rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
-     statistics_concentration, statistics_year, statistics_level)
+#rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
+#     statistics_concentration, statistics_year, statistics_level)
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplified d_cumulative_transcript

@@
 ```{r}
-d_cumulative_transcript <-  d_transactions        %>%
-  select(sequenceID, item, eventID)  %>%
-  arrange(sequenceID, eventID, item) %>%
-  group_by(sequenceID, eventID)      %>%
-  summarize_all(paste, collapse=" ") %>%
-  arrange(sequenceID, eventID)       %>%
+
+#
+# List of all courses
+course_all <- unique(d_transactions$taken_PF_HL$item)
+
+#
+# courses taken so far and not taken so far
+d_cumulative_transcript <- d_transactions$taken_PF_HL %>%
+
+  group_by(
+    sequenceID,
+    eventID
+    ) %>%
+  summarize(
+    course_current = list(
+      unique(item)
+      )
+    ) %>%
+
+  group_by(
+    sequenceID
+    ) %>%
   mutate(
-    course_all  = paste(unique(d_transactions$item), collapse = " "),
-    course_all  = str_split(course_all, pattern = " "),
+    course_past = Reduce(
+      f = paste, 
+      x = course_current, 
+      accumulate = TRUE
+      ) %>%
+      lag
+    ) %>%
 
-    course_now  = str_split(item, pattern = " "),
+  rowwise %>% # equivalent to "group by row"
+  mutate(
+    course_so_far     = list(union  (course_past, course_current)),
+    course_not_so_far = list(setdiff(course_all , course_so_far ))
+    ) %>%
+  ungroup
 
-    course_past     = Reduce(paste, item, accumulate=T),
-    course_past     = lag(course_past),
-    course_past     = str_split(course_past, pattern = " ")) %>%
-  ungroup() %>%
-    mutate(
-    course_past_now = purrr::map2(.x = course_past,
-                                      .y = course_now,
-                                      .f = union),
-    course_not = purrr::map2( .x = course_all,
-                              .y = course_past_now,
-                              .f = setdiff)
-    ) %>%
-  mutate(item = str_split(item, pattern = " "))
+rm(course_all)
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
minor update

@@
 ### Transcript with Preceding courses per student
-```{r}
+```{r d_transcript_cum}
 
@@
 # courses taken so far and not taken so far
-d_cumulative_transcript <- d_transactions$taken_PF_HL %>%
+d_transcript_cum <- d_transactions$taken_PF_HL %>%
 

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for confidence/lift

@@
     )
-
 ```
@@
     ) %>%
+
   group_by(
-    lhs, rhs_course
+    lhs,
+    rhs_course
     ) %>%
   mutate(
-    lhs.rhsTake.support = sum(support),
+    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
+    ) %>%
+  ungroup %>%
+
+  mutate(
     confidence = support / lhs.rhsTake.support,
@@
     ) %>%
-  ungroup %>%
 
-  # lhs and rhs must be fail, count >= 5
+  # lhs and rhs must be fail
   filter(
@@
     ) %>%
+
   group_by(
-    lhs, rhs_course
+    lhs, 
+    rhs_course
     ) %>%
   mutate(
-    lhs.rhsTake.support = sum(support),
+    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
+    ) %>%
+  ungroup %>%
+
+  mutate(
     confidence = support / lhs.rhsTake.support,
@@
     ) %>%
-  ungroup %>%
 
@@
   group_by(
-    lhs, rhs_course
+    lhs,
+    rhs_course
     ) %>%
     mutate(
-    lhs.rhsTake.support = sum(support * rhs.taken),
+    lhs.rhsTake.support = sum(support * rhs.taken) # Proba of lhs and taking rhs course
+    ) %>%
+  ungroup %>%
+
+  mutate(
     confidence = support / lhs.rhsTake.support,

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
corrects confidence in TPF sequences

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-# Type level
-statistics_type <- d_transcript %>%
-  inner_join(d_course, by = "Course ID") %>%
-  filter(!is.na(Type)) %>%
-  group_by(Type) %>%
-  provide_statistics()
-
 # Concentration evel
@@
 
-#rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
-#     statistics_concentration, statistics_year, statistics_level)
+rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
+     statistics_concentration, statistics_year, statistics_level)
 ```
@@
 ```{r}
+d_cumulative_transcript <-  d_transactions        %>%
+  select(sequenceID, item, eventID)  %>%
+  arrange(sequenceID, eventID, item) %>%
+  group_by(sequenceID, eventID)      %>%
+  summarize_all(paste, collapse=" ") %>%
+  arrange(sequenceID, eventID)       %>%
+  mutate(
+    course_all  = paste(unique(d_transactions$item), collapse = " "),
+    course_all  = str_split(course_all, pattern = " "),
 
-#
-# List of all courses
-course_all <- unique(d_transactions$taken_PF_HL$item)
+    course_now  = str_split(item, pattern = " "),
 
-#
-# courses taken so far and not taken so far
-d_cumulative_transcript <- d_transactions$taken_PF_HL %>%
-
-  group_by(
-    sequenceID,
-    eventID
+    course_past     = Reduce(paste, item, accumulate=T),
+    course_past     = lag(course_past),
+    course_past     = str_split(course_past, pattern = " ")) %>%
+  ungroup() %>%
+    mutate(
+    course_past_now = purrr::map2(.x = course_past,
+                                      .y = course_now,
+                                      .f = union),
+    course_not = purrr::map2( .x = course_all,
+                              .y = course_past_now,
+                              .f = setdiff)
     ) %>%
-  summarize(
-    course_current = list(
-      unique(item)
-      )
-    ) %>%
-
-  group_by(
-    sequenceID
-    ) %>%
-  mutate(
-    course_past = Reduce(
-      f = paste, 
-      x = course_current, 
-      accumulate = TRUE
-      ) %>%
-      lag
-    ) %>%
-
-  rowwise %>% # equivalent to "group by row"
-  mutate(
-    course_so_far     = list(union  (course_past, course_current)),
-    course_not_so_far = list(setdiff(course_all , course_so_far ))
-    ) %>%
-  ungroup
-
-rm(course_all)
+  mutate(item = str_split(item, pattern = " "))
 ```
@@
     confidence                   = support_rule_rhs.PF / support_lhs,
-    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
+    confidence_bounded           = num_rule_PF/num_rule_x, #support_rhs_bounded / support_lhs, #not sure about this 
     lift                         = confidence / support_rhs.PF,

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code summary statistics

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-# For convenience
-provide_statistics <- function(data){
+#
+# function providing statistics
+provide_statistics <- function(data, var){
 
   data %>%
+    filter(
+      !is.na(!!enquo(var))
+      ) %>%
+    group_by(
+      !!enquo(var)
+      ) %>%
     summarise(
@@
 
+#
+# Generating Statistics
+statistics <- list()
+
 # Student level
-statistics_student <- d_transcript %>%
-  group_by(`Student ID`) %>%
-  provide_statistics()
+statistics$student <- d_transcript %>%
+  provide_statistics(`Student ID`)
 
 # Course level
-statistics_course <- d_transcript %>%
-  inner_join(d_course, by = c("Course ID")) %>%
-  group_by(`Course ID`) %>%
-  provide_statistics()
+statistics$course <- d_transcript %>%
+  inner_join(
+    d_course,
+    by = c("Course ID")
+    ) %>%
+  provide_statistics(`Course ID`)
 
@@
 statistics_cluster <- d_transcript %>%
-  inner_join(d_course, by = "Course ID") %>%
-  filter(!is.na(Cluster)) %>%
-  group_by(Cluster) %>%
-  provide_statistics()
+  inner_join(
+    d_course, 
+    by = "Course ID"
+    ) %>%
+  provide_statistics(Cluster)
 
@@
 statistics_type <- d_transcript %>%
-  inner_join(d_course, by = "Course ID") %>%
-  filter(!is.na(Type)) %>%
-  group_by(Type) %>%
-  provide_statistics()
+  inner_join(
+    d_course, by = "Course ID"
+    ) %>%
+  provide_statistics(Type)
 
@@
   gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-  group_by(Concentration) %>%
-  provide_statistics()
+  provide_statistics(Concentration)
 
@@
 statistics_year <- d_transcript %>%
-  group_by(Year_numerical) %>%
-  provide_statistics()
+  provide_statistics(Year_numerical)
 
@@
   inner_join(d_course, by = c("Course ID")) %>%
-  filter(!is.na(Level)) %>%
-  group_by(Level) %>%
-  provide_statistics()
+  provide_statistics(Level)
 
@@
 # output
-save(statistics_student, statistics_course, statistics_cluster,
-     statistics_concentration, statistics_year, statistics_level, file = "Output/Transcript Statistics.RDATA")
+save(
+  statistics,
+  file = "Output/Transcript Statistics.RDATA"
+  )
 
-#rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
-#     statistics_concentration, statistics_year, statistics_level)
+rm(statistics)
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code summary statistics

@@
 statistics_concentration <- d_transcript %>%
-  inner_join(d_course, by = "Course ID") %>%
-  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+  inner_join(
+    d_course,
+    by = "Course ID"
+    ) %>%
+  gather(
+    key = X, 
+    value = Concentration, 
+    Concentration, `Concentration (additional)`,
+    na.rm = TRUE
+    ) %>%
   provide_statistics(Concentration)

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r}
-d_past_student_course <- d_cumulative_transcript %>%
-  select(sequenceID, eventID, item, course_past) %>%
-  unnest(item, .drop=F)
+d_transcript_cum_current <- d_transcript_cum %>%
+  unnest(
+    course_current,
+    .drop = FALSE
+    )
+
+d_transcript_cum_current %>%
+  unnest(
+    course_past,
+    .drop = FALSE
+    )
 

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
first SR by hand

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
     course_past = Reduce(
-      f = paste, 
+      f = c, 
       x = course_current, 
@@
       ) %>%
-      lag
+      lag(
+        default = as.character(NA)
+        )
     ) %>%
@@
 
-### Courses that were taken before each course
 ```{r}
-d_past_student_course <- d_cumulative_transcript %>%
-  select(sequenceID, eventID, item, course_past) %>%
-  unnest(item, .drop=F)
-
-d_past_course <- expand.grid(
-
-  # Expand along students (sequenceID) and courses (itemID)
-  sequenceID = unique(d_transactions$sequenceID),
-  item       = unique(d_transactions$item),
-  stringsAsFactors = FALSE
-  ) %>%
-  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
-  arrange(sequenceID) %>%
-  ungroup() %>%
-  drop_na(eventID) %>%
-  unnest(course_past) %>%
-  distinct() %>%
-  group_by(item) %>%
-  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
-  mutate(full_past    = str_split(full_past, pattern = " "),
-         full_past    = map(.f= unique, .x=full_past),
-         total_past_courses = map(.f=length, .x=full_past))
+
+#
+# SR by hand
+
+# rhs = current course
+d_transcript_cum_current <- d_transcript_cum %>%
+  unnest(
+    course_current,
+    .drop = FALSE
+    ) %>%
+  rename(
+    rhs = course_current
+    )
+
+# lhs = course past
+d_transcript_cum_current %>%
+  filter(!is.na(course_past)) %>%
+  unnest(
+    course_past,
+    .drop = FALSE
+    ) %>%
+  rename(
+    lhs = course_past
+    ) %>%
+  count(
+    lhs, 
+    rhs
+    )
+
+# lhs = course not so far
+d_transcript_cum_current %>%
+  unnest(
+    course_not_so_far,
+    .drop = FALSE
+    ) %>%
+  rename(
+    lhs = course_not_so_far
+    ) %>%
+  count(
+    lhs, 
+    rhs
+    )
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
adds comment on cspade

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
     parameter = list(
+      #include as many item sequences as possible
       support = 0,   # min support of a sequence
@@
     ruleInduction(
-      confidence = 0, #we need to play with the parameters.
+      #include as many rules as possible
+      confidence = 0,
       control    = list(verbose = FALSE)
@@
 #Generating sequence rules:
-SR_taken   <- my_SR(data = sequences   )
+SR_taken   <- my_SR(data = sequences$taken )
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
corrects make_sequences, creates SR

@@
 
-  sequences <- data %>%
-    filter(
-      !is.na(eventID) #this is here casue we have courses that were never taken.
-      ) %>% 
-    group_by(
-      sequenceID,
-      eventID
-    ) %>%
-    summarise(
-      list_item = list(unique(!!enquo(item)))
-    ) %>%
-    ungroup %>%
+    # make transactions
+  data_temp <- data %>%
     arrange(
@@
     ) %>%
+    filter(
+      !is.na(eventID) #this is here casue we have courses that were never taken.
+      ) %>% 
+    group_by(
+      sequenceID,
+      eventID
+    ) %>%
+    summarise(
+      list_item = list(unique(!!enquo(item)))
+    ) %>%
+    ungroup
+
+  sequences <- data_temp %>%
     pull(
@@
   # indicating sequence ID and event ID for each transaction
-  sequences@itemsetInfo <- select(
-    data,
+  sequences@itemsetInfo <- data_temp %>%
+    select(
       sequenceID,
@@
 # Checking sequences
-# inspect(head(sequences_G, 10))
-
-rm(make_sequence, d_transactions)
+ inspect(head(sequences$G, 10))
+
+rm(make_sequence #, d_transactions
+   )
 ```
@@
       ) %>%
-    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
+    separate(rule, into = c("lhs", "rhs"), sep=" = ")  %>%
     select(
@@
 #Generating sequence rules:
-SR_taken   <- my_SR(data = sequences$taken )
+SR_taken   <- my_SR(data = sequences$taken)
 ```
@@
 ##pass/fail filter
-SR_PF      <- my_SR(data = sequences_PF) %>%
+SR_PF      <- my_SR(data = sequences$PF) %>%
   filter(
@@
 ##high/low filter
-SR_HL      <- my_SR(data = sequences_HL) %>% 
+SR_HL      <- my_SR(data = sequences$HL) %>% 
   filter(
@@
 
-SR_Grade   <- my_SR(data = sequences_Grade )
+SR_G   <- my_SR(data = sequences$G )
 ```
@@
 #Grades filter 
-SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
+#SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
 ```
@@
 # current, past, not_yet
-SR_TPF <- d_cumulative_transcript                  %>%
-  select(sequenceID, eventID, item, course_not)    %>%
-  unnest(item, .drop = F)                          %>%
-  unnest(course_not)                               %>%
+SR_TPF <- d_transcript_cum                         %>%
+  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
+  unnest(course_current, .drop = F)                %>%
+  unnest(course_not_so_far)                        %>%
   left_join(
@@
            sequenceID, eventID, item, PF), 
-    by= c("sequenceID", "eventID", "item")
-    )                                              %>%
-  select(sequenceID,eventID, course_not, item, PF) %>%
+    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "item" = "course_so_far")
+    )                                              %>%
+  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
   rename(
-    lhs="course_not", 
-    rhs.x = "item", 
+    lhs="course_not_so_far", 
+    rhs.x = "course_current", 
     rhs.PF = "PF")                                 %>%
@@
 save(
-    SR_taken, SR_PF, SR_HL, SR_Grade,
-    SR_expanded_Grade,
+    SR_taken, SR_PF, SR_HL, SR_G,
+    #SR_TPF,
+    #SR_expanded_Grade,
     file = "App/SR.RDATA")
@@
 #clean unnecessary objects
-rm(clean_SR, my_SR, 
-   sequences, sequences_PF, sequences_HL, sequences_Grade,
-   sequences_expanded_Grade,
-   n_students,
-   SR_taken, SR_PF, SR_HL, SR_Grade,
-
-   SR_expanded_Grade)
-```
+# rm(clean_SR, my_SR, 
+#    sequences,
+#    #sequences_expanded_Grade,
+#    n_students,
+#    SR_taken, SR_PF, SR_HL, SR_G,
+#    SR_TPF
+#    #SR_expanded_Grade
+#    )
+```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
     toc: TRUE
+editor_options: 
+  chunk_output_type: console
 ---
@@
     parameter = list(
-      #include as many item sequences as possible
       support = 0, # min support of a sequence
@@
     ruleInduction(
-      #include as many rules as possible
-      confidence = 0,
+      confidence = 0, #we need to play with the parameters.
       control    = list(verbose = FALSE)
@@
 #Generating sequence rules:
-SR_taken   <- my_SR(data = sequences$taken )
+SR_taken   <- my_SR(data = sequences   )
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
updates SR_TPF

@@
   left_join(
-    select(d_transactions, 
+    select(d_transactions$TPF, 
            sequenceID, eventID, item, PF), 
-    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "item" = "course_so_far")
+    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "course_current" = "item")
     )                                              %>%
@@
     SR_taken, SR_PF, SR_HL, SR_G,
-    #SR_TPF,
+    SR_TPF,
     #SR_expanded_Grade,

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
separate rhs and lhs in clean_AR

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
-    # Clean variable `rules`
-    mutate(
-      rules = str_remove_all(rules, pattern = "[{]"),
-      rules = str_remove_all(rules, pattern = "[}]")
+    # separate rule
+    mutate(
+      rules = str_remove_all(rules, pattern = "[{]|[}]")
       ) %>%
@@
       sep  = " => "
+      ) %>%
+
+    # separate rhs and lhs
+    separate(
+      rhs,
+      into    = c("rhs_course", "rhs_outcome"),
+      sep     = "_",
+      remove  = FALSE,
+      convert = TRUE
+      ) %>%
+    separate(
+      lhs,
+      into    = c("lhs_course", "lhs_outcome"),
+      sep     = "_",
+      remove  = FALSE,
+      convert = TRUE
       )
@@
     # rhs.support
-    mutate(
-      rhs_course = str_remove_all(rhs, pattern = "_fail|_pass|_low|_not taken")
-      ) %>%
     left_join(
@@
   # Confidence and Lift by hand
-  separate(
-    rhs,
-    sep = "_",
-    into = c("rhs_course", "rhs_outcome"),
-    remove = FALSE
-    ) %>%
-
   group_by(
@@
   # Confidence and Lift
-  separate(
-    rhs,
-    sep = "_",
-    into = c("rhs_course", "rhs_outcome"),
-    remove = FALSE
-    ) %>%
   mutate(
@@
 
-  # separate rhs and lhs
-  separate(
-    rhs,
-    into = c("rhs_course", "rhs_grade"),
-    sep = "_",
-    remove = FALSE,
-    convert = TRUE
-    ) %>%
-  separate(
-    lhs,
-    into = c("lhs_course", "lhs_grade"),
-    sep = "_",
-    remove = FALSE,
-    convert = TRUE
-    ) %>%
-
   # rhs.support
@@
     d_support$G,
-    by = c("rhs_course" = "item", "rhs_grade" = "grade_ceil")
+    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
     ) %>%
@@
     lhs_course != rhs_course, # exclude rules with same course on lhs and rhs        
-    rhs_grade == 6            
+    rhs_outcome == 6            
     ) %>%
@@
 
-###TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail
-
-```{r function clean SR}
-# Transform rules from ruleInduction into a readable data frame
-
-clean_SR<- function(rules){
-
-  rules %>%
-    as("data.frame") %>%
-    mutate(
-      rule = str_remove_all(rule, pattern = "[<]"),
-      rule = str_remove_all(rule, pattern = "[{]"),
-      rule = str_remove_all(rule, pattern = "[}]"),
-      rule = str_remove_all(rule, pattern = "[>]")
-      ) %>%
-    separate(rule, into = c("lhs", "rhs"), sep=" = ")  %>%
-    select(
-      lhs, rhs,
-      support,
-      confidence,
-      lift
-    ) %>%
-    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
-    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
-    # Compute statistic
-    group_by(lhs,`RHS Course ID`) %>%
-    mutate(
-      lhs.rhsCourse.support = sum(support),
-      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
-                             T ~ (support / lhs.rhsCourse.support)),
-      count = support * n_students,
-      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
-      lift = 1 #dummy variable
-      # TODO: compute rhs.support
-      # lift = confidence.corr / rhs.support
-     ) %>%
-    ungroup() %>%
-    mutate_at(
-      c("support",
-        "confidence", "lift"),
-      funs(round(., 5))
-    ) %>%
-    filter(!`LHS Course ID`==`RHS Course ID`) %>%
-    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
-
-}
-```
-We apply cspade followed by rule induction
+### Functions
+
 ```{r my_SR function}
 # Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
-my_SR<- function(data){
+my_cspade <- function(data){
+
   data %>%
+
     cspade(
+
       parameter = list(
@@
         ),
+
       control = list(
@@
         )
-    ) %>%
-    ruleInduction(
-      #include as many rules as possible
+
+      )
+
+}
+```
+
+```{r}
+my_ruleInduction <- function(rules){
+
+  rules %>%
+
+    ruleinduction(
       confidence = 0,
       control    = list(verbose = FALSE)
-      ) %>%
-    clean_SR
-}
+      )
+
+}
+```
+
+```{r function clean SR}
+# Transform rules from ruleInduction into a readable data frame
+
+clean_SR <- function(rules){
+
+  rules %>%
+
+    as("data.frame") %>%
+
+    # Exclude rules with no support
+    filter(
+      count >= 1
+      ) %>%
+
+    # Isolate RHS and LHS
+    mutate(
+      rule = str_remove_all(rule, pattern = "[<]"),
+      rule = str_remove_all(rule, pattern = "[{]"),
+      rule = str_remove_all(rule, pattern = "[}]"),
+      rule = str_remove_all(rule, pattern = "[>]")
+      ) %>%
+
+    separate(
+      rule,
+      into = c("lhs", "rhs"),
+      sep = " = "
+      ) %>%
+    separate(
+      lhs,
+      into = c("LHS Course ID", "LHS Quality"),
+      sep = "_",
+      remove= FALSE
+      ) %>%
+    separate(
+      rhs, 
+      into = c("RHS Course ID", "RHS Quality"),
+      sep = "_", 
+      remove = FALSE
+    )
+}
+
+    # Compute statistic
+    group_by(lhs,`RHS Course ID`) %>%
+    mutate(
+      lhs.rhsCourse.support = sum(support),
+      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
+                             T ~ (support / lhs.rhsCourse.support)),
+      count = support * n_students,
+      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
+      lift = 1 #dummy variable
+      # TODO: compute rhs.support
+      # lift = confidence.corr / rhs.support
+     ) %>%
+    ungroup() %>%
+    mutate_at(
+      c("support",
+        "confidence", "lift"),
+      funs(round(., 5))
+    ) %>%
+    filter(!`LHS Course ID`==`RHS Course ID`) %>%
+    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
+
+```
+
+```{r}
+
 ```

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify clean_SR

@@
     course_current = list(
-      unique(item)
+      unique(item_PF)
       )
@@
     lhs, 
-    rhs
+    rhs,
+    sort = TRUE
     )
@@
     lhs, 
-    rhs
-    )
+    rhs,
+    sort = TRUE
+    ) %>%
+  filter(str_detect(rhs, "fail"))
 ```
@@
   AR %>%
+
     filter(
@@
       ) %>%
+
     mutate_if(
@@
     ) %>%
+
     select(
@@
     ) %>%
+
     arrange(
@@
     filter(
-      count >= 1
-      ) %>%
-
-    # Isolate RHS and LHS
-    mutate(
-      rule = str_remove_all(rule, pattern = "[<]"),
-      rule = str_remove_all(rule, pattern = "[{]"),
-      rule = str_remove_all(rule, pattern = "[}]"),
-      rule = str_remove_all(rule, pattern = "[>]")
-      ) %>%
-
+      support > 0
+      ) %>%
+
+    # separate rule
+    mutate(
+      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
+      ) %>%
     separate(
@@
       ) %>%
+
+    # separate lhs and rhs
     separate(
       lhs,
-      into = c("LHS Course ID", "LHS Quality"),
+      into    = c("lhs_course", "lhs_outcome"),
       sep     = "_",
-      remove= FALSE
+      remove  = FALSE,
+      convert = TRUE
       ) %>%
@@
       rhs,
-      into = c("RHS Course ID", "RHS Quality"),
+      into    = c("rhs_course", "rhs_outcome"),
       sep     = "_",
-      remove = FALSE
-    )
-}
-
+      remove  = FALSE,
+      convert = TRUE
+      )
+
+}
+```
+
+```{r SR metrics}
     # Compute statistic
@@
     ungroup() %>%
+```
+
+```{r SR edit}
     mutate_at(
@@
     select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
-
-```
-
-```{r}
-
 ```

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
adds a space

@@
     ) %>%
-    filter(!`LHS Course ID`==`RHS Course ID`) %>%
+    filter(!`LHS Course ID` == `RHS Course ID`) %>%
     select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
generate SR

--- 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 # Cluster level
-statistics_cluster <- d_transcript %>%
+statistics$cluster <- d_transcript %>%
   inner_join(
@@
 # Type level
-statistics_type <- d_transcript %>%
+statistics$type <- d_transcript %>%
   inner_join(
@@
 # Concentration evel
-statistics_concentration <- d_transcript %>%
+statistics$concentration <- d_transcript %>%
   inner_join(
@@
 # Year level
-statistics_year <- d_transcript %>%
+statistics$year <- d_transcript %>%
   provide_statistics(Year_numerical)
@@
 # Level level
-statistics_level <- d_transcript %>%
+statistics$level <- d_transcript %>%
   # TODO: filter for student who completed their studies
@@
 
-### take -> taken
+### take -> take
 ```{r AR take}
@@
 
-### less than x grade -> less than 6
+### grade less than or equal to x -> grade less than or equal to 6
 ```{r AR grade}
@@
 ## Sequence Rules
-
 ### Functions
@@
 
+```{r}
+make_SR <- function(data){
+
+  data %>%
+    my_cspade %>%
+    my_ruleInduction %>%
+    clean_SR
+
+}
+
+```
+
+### take -> take
+```{r}
+SR <- list()
+
+SR$taken <- sequences$taken %>%
+  my_SR
+```
+
+### fail -> fail
+```{r}
+SR$PF <- sequences$PF %>%
+
+  my_SR %>%
+
+  # lhs and rhs are fail
+  filter(
+    str_detect(lhs, "fail"),
+    str_detect(rhs, "fail")
+    )
+```
+
+### low grade -> low grade
+```{r}
+SR$HL <- sequences$HL %>%
+
+  my_SR %>%
+
+  # lhs and rhs are low
+  filter(
+    str_detect(lhs, "low"),
+    str_detect(rhs, "low")
+    )
+```
+
+### not take -> fail
+```{r}
+# by hand
+```
+
+### grade less than or equal to x -> grade less than or equal to 6
+```{r}
+SR$G <- sequences$G %>%
+
+  my_SR %>%
+
+  # rhs is grade less than 6
+  filter(
+    str_detect(rhs, "6")
+    )
+```
+
+### Editing AR
+```{r SR edit}
+    mutate_at(
+      c("support",
+        "confidence", "lift"),
+      funs(round(., 5))
+    ) %>%
+    filter(!`LHS Course ID`==`RHS Course ID`) %>%
+    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
+```
+
+### Save Sequences Rules
+
 ```{r SR metrics}
@@
     ungroup() %>%
-```
-
-```{r SR edit}
-    mutate_at(
-      c("support",
-        "confidence", "lift"),
-      funs(round(., 5))
-    ) %>%
-    filter(!`LHS Course ID`==`RHS Course ID`) %>%
-    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
-```
-
-We generate sequence rules:
-```{r SR taken, cache = TRUE}
-
-#Generating sequence rules:
-SR_taken   <- my_SR(data = sequences$taken)
-```
-
-```{r SR PF, cache = TRUE}
-
-##pass/fail filter
-SR_PF      <- my_SR(data = sequences$PF) %>%
-  filter(
-    str_detect(rhs, "fail"),
-    str_detect(lhs, "fail")
-    )
-```
-
-```{r SR HL, cache = TRUE}
-
-##high/low filter
-SR_HL      <- my_SR(data = sequences$HL) %>% 
-  filter(
-    str_detect(rhs, "low"),
-    str_detect(lhs, "low")
-    )
-```
-
-```{r SR grade, cache = TRUE}
-
-SR_G   <- my_SR(data = sequences$G )
-```
-
-```{r SR grade exp, cache = TRUE}
-
-#Grades filter 
-#SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
 ```

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debug

@@
 
-### Transcript with Preceding courses per student
+### Transcript with preceding courses (for SR by hand)
 ```{r d_transcript_cum}
@@
 rm(course_all)
-```
-
-```{r}
-
-#
-# SR by hand
-
-# rhs = current course
-d_transcript_cum_current <- d_transcript_cum %>%
-  unnest(
-    course_current,
-    .drop = FALSE
-    ) %>%
-  rename(
-    rhs = course_current
-    )
-
-# lhs = course past
-d_transcript_cum_current %>%
-  filter(!is.na(course_past)) %>%
-  unnest(
-    course_past,
-    .drop = FALSE
-    ) %>%
-  rename(
-    lhs = course_past
-    ) %>%
-  count(
-    lhs, 
-    rhs,
-    sort = TRUE
-    )
-
-# lhs = course not so far
-d_transcript_cum_current %>%
-  unnest(
-    course_not_so_far,
-    .drop = FALSE
-    ) %>%
-  rename(
-    lhs = course_not_so_far
-    ) %>%
-  count(
-    lhs, 
-    rhs,
-    sort = TRUE
-    ) %>%
-  filter(str_detect(rhs, "fail"))
 ```
@@
 SR$taken <- sequences$taken %>%
-  my_SR
+  make_SR
 ```
@@
 
-  my_SR %>%
+  make_SR %>%
 
@@
 ```{r}
-# by hand
+
+#
+# SR by hand
+
+# rhs = current course
+d_transcript_cum_current <- d_transcript_cum %>%
+  unnest(
+    course_current,
+    .drop = FALSE
+    ) %>%
+  rename(
+    rhs = course_current
+    )
+
+# lhs = course not so far
+d_transcript_cum_current %>%
+  unnest(
+    course_not_so_far,
+    .drop = FALSE
+    ) %>%
+  rename(
+    lhs = course_not_so_far
+    ) %>%
+  count(
+    lhs, 
+    rhs,
+    sort = TRUE
+    ) %>%
+  filter(str_detect(rhs, "fail"))
 ```

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debugging ruleInduction

@@
 
-    ruleinduction(
+    ruleInduction(
       confidence = 0,
@@
 
-### Editing AR
+### Editing SR
 ```{r SR edit}

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
save files update
extend make_SR

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
   data %>%
+
     apriori(
@@
 The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-```{r clean_AR}
-clean_AR <- function(AR){
-
-  AR %>%
+
+```{r function clean_rules}
+clean_rules <- function(rules){
+
+  rules %>%
+
     as("data.frame") %>%
@@
     filter(
-      count >= 1
+      support > 0
       ) %>%
@@
     mutate(
-      rules = str_remove_all(rules, pattern = "[{]|[}]")
+      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
       ) %>%
     separate(
-      rules,
+      rule,
       into = c("lhs", "rhs"),
-      sep  = " => "
-      ) %>%
-
-    # separate rhs and lhs
+      sep = " = "
+      ) %>%
+
+    # separate lhs and rhs
+    separate(
+      lhs,
+      into    = c("lhs_course", "lhs_outcome"),
+      sep     = "_",
+      remove  = FALSE,
+      convert = TRUE
+      ) %>%
     separate(
@@
       convert = TRUE
-      ) %>%
-    separate(
-      lhs,
-      into    = c("lhs_course", "lhs_outcome"),
-      sep     = "_",
-      remove  = FALSE,
-      convert = TRUE
       )
@@
 ```{r compute_support}
-compute_metrics <- function(AR, data_support, type_rule){
+compute_rhs.support <- function(AR, data_support, type_rule){
 
@@
 
-    # rhs.support
     left_join(
@@
     my_apriori %>%
-    clean_AR %>%
-    compute_metrics(
+    clean_rules %>%
+    compute_rhs.support(
       data_support = data_support,
@@
   my_apriori %>%
-  clean_AR %>%
+  clean_rules %>%
 
@@
       parameter = list(
-        #include as many item sequences as possible
-        support = 0,   # min support of a sequence
-        maxsize = 1,   # max number of items of an element of a sequence
-        maxlen  = 2,   # max number of element of a sequence
-        mingap  = 1,   # min time difference between consecutive element of a sequence
-        maxgap  = 1e4  # max time difference between consecutive element of a sequence
-        #maxwin  = 1e4 # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
+
+        # only include subsequences of the type {one item} => {one item}
+        maxlen  = 2,   # max length of sequence
+        maxsize = 1,   # max number item for element
+
+        # include all such subsequences
+        support = 0,   # min suppor
+        mingap  = 1,   # min time difference between consecutive element
+        maxgap  = 1e4  # max time difference between consecutive element
+
         ),
@@
 
-```{r function clean SR}
-# Transform rules from ruleInduction into a readable data frame
-
-clean_SR <- function(rules){
-
-  rules %>%
-
-    as("data.frame") %>%
-
-    # Exclude rules with no support
-    filter(
-      support > 0
-      ) %>%
-
-    # separate rule
-    mutate(
-      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
-      ) %>%
-    separate(
-      rule,
-      into = c("lhs", "rhs"),
-      sep = " = "
-      ) %>%
-
-    # separate lhs and rhs
-    separate(
-      lhs,
-      into    = c("lhs_course", "lhs_outcome"),
-      sep     = "_",
-      remove  = FALSE,
-      convert = TRUE
-      ) %>%
-    separate(
-      rhs,
-      into    = c("rhs_course", "rhs_outcome"),
-      sep     = "_",
-      remove  = FALSE,
-      convert = TRUE
-      )
-
-}
-```
-
 ```{r}
-make_SR <- function(data){
+make_SR <- function(data, data_support, type_rule){
 
@@
     my_ruleInduction %>%
-    clean_SR
-
-}
-
+    clean_rules %>%
+    compute_rhs.support(
+      data_support = data_support,
+      type_rule = !!enquo(type_rule)
+      )
+
+}
 ```
@@
 SR$taken <- sequences$taken %>%
-  make_SR
+  make_SR(
+    data_support = d_support$TNT, 
+    type_rule = rate.take
+  )
 ```
@@
 
-  make_SR %>%
+  make_SR(
+    data_support = d_support$PF_HL,
+    type_rule = rate.fail
+  ) %>%
 
@@
 
-  make_SR %>%
+  make_SR(
+    data_support = d_support$PF_HL,
+    type_rule = rate.low
+  ) %>%
 

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 save(
-    SR_taken, SR_PF, SR_HL, SR_G,
+    SR,
     SR_TPF,

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
update edit_rules

@@
     mutate(
-      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
+      rules = str_remove_all(rules, pattern = "[<]|[{]|[}]|[>]")
       ) %>%
     separate(
-      rule,
+      rules,
       into = c("lhs", "rhs"),
@@
   mutate(
-    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
+    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
     ) %>%
@@
     mutate(
-    lhs.rhsTake.support = sum(support * rhs.taken) # Proba of lhs and taking rhs course
+    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
     ) %>%
@@
     lhs.rhsTake.support = max(support),
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
     confidence          = support / lhs.rhsTake.support,
@@
 ```{r edit_AR}
-edit_AR <- function(AR){
+edit_rules <- function(AR){
 
@@
     select(
-      lhs, rhs,
-      support, count,
+      lhs       , rhs,
+      support   , count,
       confidence, rhs.support,
       lift,
-      everything(),
-      - matches("rate|course|grade|outcome|taken")
+      matches("rhsTake")
     ) %>%
@@
   X   = AR,
-  FUN = edit_AR
+  FUN = edit_rules
   )
@@
 rm(
-  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
+  my_apriori, make_AR,
   AR, transaction
@@
     ruleInduction(
+
+      # keep all subsequences
       confidence = 0,
+
       control    = list(verbose = FALSE)
+
       )
@@
 ```{r SR edit}
-    mutate_at(
-      c("support",
-        "confidence", "lift"),
-      funs(round(., 5))
-    ) %>%
-    filter(!`LHS Course ID`==`RHS Course ID`) %>%
-    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
+SR <- lapply(
+  X   = SR,
+  FUN = edit_rules
+  )
 ```

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
save SR

@@
 ### Save Sequences Rules
+```{r}
+#
+# Save Sequence rules
+save(
+  SR,
+  file = "App/SR.RDATA"
+)
+
+# Remove objects
+rm(
+  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
+  SR, sequences
+)
+```
 
@@
 ```
-
-We save and remove objects:
-```{r saving and rm SR}
-#Saving sequence rules
-save(
-    SR,
-    SR_TPF,
-    #SR_expanded_Grade,
-    file = "App/SR.RDATA")
-
-#clean unnecessary objects
-# rm(clean_SR, my_SR, 
-#    sequences,
-#    #sequences_expanded_Grade,
-#    n_students,
-#    SR_taken, SR_PF, SR_HL, SR_G,
-#    SR_TPF
-#    #SR_expanded_Grade
-#    )
-```

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debuggs to match both "rule" and "rules" as variable

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
     # separate rule
-    mutate(
-      rules = str_remove_all(rules, pattern = "[<]|[{]|[}]|[>]")
+    rename_at(
+      vars(matches("rule")),
+      function(x) substr(x, 1, 4)
+    ) %>%
+    mutate(
+      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
       ) %>%
     separate(
-      rules,
+      rule,
       into = c("lhs", "rhs"),

### 2019-02-13 All Packages installation script.R
creates script to install all packages used in the project

@@ -1,0 +1,3 @@
+#installs all packages needed
+install.packages(c("tidyverse","tidytext","ggwordcloud","topicmodels","lemon","ggthemes","rlang","ldatuning"))#pillar 2
+install.packages(c("arules","arulesSequences"))#pillar 1

### 2019-02-13 All Packages installation script.R
nothing

@@ -1,3 +1,4 @@
 #installs all packages needed
 install.packages(c("tidyverse","tidytext","ggwordcloud","topicmodels","lemon","ggthemes","rlang","ldatuning"))#pillar 2
 install.packages(c("arules","arulesSequences"))#pillar 1
+

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
SR conf & lift by hand

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+  # Confidenca and lift by hand
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+  ) %>%
+  ungroup %>%
+
+  mutate(
+    confidence = support / lhs.rateTake.support,
+    lift       = confidence / rhs.support
+    )
+
   # lhs and rhs are fail
@@
 
+    # Confidenca and lift by hand
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+  ) %>%
+  ungroup %>%
+
+  mutate(
+    confidence = support / lhs.rateTake.support,
+    lift       = confidence / rhs.support
+    )
+
   # lhs and rhs are low
@@
 ### not take -> fail
-```{r}
+```{r, eval = FALSE}
 
@@
 ### grade less than or equal to x -> grade less than or equal to 6
-```{r}
+```{r, eval = FALSE}
 SR$G <- sequences$G %>%
@@
 rm(
+  SR, sequences,
   my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
-  SR, sequences
-)
-```
-
-```{r SR metrics}
-    # Compute statistic
-    group_by(lhs,`RHS Course ID`) %>%
-    mutate(
-      lhs.rhsCourse.support = sum(support),
-      confidence = case_when(is.na(`RHS Quality`) ~ confidence,
-                             T ~ (support / lhs.rhsCourse.support)),
-      count = support * n_students,
-      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
-      lift = 1 #dummy variable
-      # TODO: compute rhs.support
-      # lift = confidence.corr / rhs.support
-     ) %>%
-    ungroup() %>%
+  n_students
+)
 ```
@@
 SR_TPF are manually computed
-```{r}
+```{r, eval = FALSE}
 # current, past, not_yet

### 2019-02-13 Pillar 2 - Topic Modeling.Rmd

@@
 
-## Ideal Number of Topics
+## Ideal Number of Topics (RUN ON UM COMPUTER)
 
 ```{r LDA number topics, eval = FALSE}
+
+my_control <- list(
+
+  nstart = 10,
+  seed   = 1 : 10,
+  best   = TRUE,
+
+  burnin = 500
+  iter   = 2000,
+  thin   = 100
+
+)
+
 result <- FindTopicsNumber(
@@
   method = "Gibbs",
-  control = list(seed = 123),
-  mc.cores = 1L,
-  verbose = TRUE
+  control = my_control,
+  mc.cores = 1L
 

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
attempt to knit

@@
 ### grade less than or equal to x -> grade less than or equal to 6
-```{r AR grade}
+```{r AR grade, cache = TRUE}
 AR$G <- transactions$G %>%
@@
   mutate(
-    confidence = support / lhs.rateTake.support,
+    confidence = support / lhs.rhsTake.support,
     lift       = confidence / rhs.support
-    )
+    ) %>%
 

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
- label chuncks - conf & lift of SR grade

@@
 
+    mutate(
+      count = support * n_students
+    ) %>%
+
     filter(
@@
 
-```{r my_SR function}
-# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
+```{r my_cspade function}
 my_cspade <- function(data){
@@
 
-```{r}
+```{r my_ruleInduction}
 my_ruleInduction <- function(rules){
@@
 
-```{r}
+```{r make_SR}
 make_SR <- function(data, data_support, type_rule){
@@
 ### take -> take
-```{r}
+```{r SR taken}
 SR <- list()
@@
 SR$taken <- sequences$taken %>%
+
   make_SR(
@@
 ### fail -> fail
-```{r}
+```{r SR PF}
 SR$PF <- sequences$PF %>%
@@
 ### low grade -> low grade
-```{r}
+```{r SR HL, cache = TRUE}
 SR$HL <- sequences$HL %>%
@@
 ### not take -> fail
-```{r, eval = FALSE}
+```{r SR TPF, eval = FALSE}
 
@@
 ### grade less than or equal to x -> grade less than or equal to 6
-```{r, eval = FALSE}
+```{r SR G, cache = TRUE}
 SR$G <- sequences$G %>%
 
-  make_SR %>%
-
-  # rhs is grade less than 6
+  my_cspade %>%
+  clean_rules %>%
+
+  # rhs.support
+  left_join(
+    d_support$G,
+    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
+    ) %>%
+  mutate(
+    rhs.support = support.grade
+    ) %>%
+
+  # Confidence & lift
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = max(support),
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / rhs.support
+    ) %>%
+  ungroup %>%
+
+  # Reduce number of rules
   filter(
-    str_detect(rhs, "6")
-    )
+    # exclude rules with same course on lhs and rhs
+    lhs_course != rhs_course,
+    # rhs is grade less than or equal to 6
+    rhs_outcome == 6
+    ) %>%
+
+  # for each combination of course (lhs and rhs), keep AR with highest lift (most informative)
+  group_by(
+    lhs_course,
+    rhs_course
+    ) %>%
+  top_n(
+    n = 1,
+    lift
+    ) %>%
+  ungroup
 ```
@@
 ### Save Sequences Rules
-```{r}
+```{r SR save}
 #

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debug
adds comments

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
-
-### take -> take
+###Apply Functions
+We apply make_AR to get different sets of rules:
+
+#### take -> take
 ```{r AR take}
@@
 
-### fail -> fail
+#### fail -> fail
 ```{r AR fail}
@@
 
-### low grade -> low grade
+#### low grade -> low grade
 ```{r AR low}
@@
 
-### not take -> fail
+#### not take -> fail
 ```{r AR TPF}
@@
 
-### grade less than or equal to x -> grade less than or equal to 6
+#### grade less than or equal to x -> grade less than or equal to 6
 ```{r AR grade, cache = TRUE}
@@
 ### Editing AR
+The function edit_rules makes AR easier to read.
+It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
 ```{r edit_AR}
@@
   AR %>%
+
+    mutate(
+      count = support * n_students
+    ) %>%
 

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
   my_cspade %>%
+  my_ruleInduction %>%
   clean_rules %>%

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
comments

@@
 ### Functions
-
+The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
 ```{r my_cspade function}
@@
 ```
-
+The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
 ```{r my_ruleInduction}
@@
 ```
-
+We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
 ```{r make_SR}

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
comments (restuctures section)

@@
 ```
-
-### take -> take
+###Apply Functions
+We apply make_SR to get different types of sequential rules:
+#### take -> take
 ```{r SR taken}
@@
 
-### fail -> fail
+#### fail -> fail
 ```{r SR PF}
@@
 
-### low grade -> low grade
+#### low grade -> low grade
 ```{r SR HL, cache = TRUE}
@@
 
-### not take -> fail
+#### not take -> fail
 ```{r SR TPF, eval = FALSE}
@@
 
-### grade less than or equal to x -> grade less than or equal to 6
+#### grade less than or equal to x -> grade less than or equal to 6
 ```{r SR G, cache = TRUE}

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
breaks up section

@@
 ### Editing SR
+We apply `edit_rules` to SR in order to get easily readable rules. 
 ```{r SR edit}
@@
 )
-
+```
+We remove objects
+```{r remove SR}
+#
 # Remove objects

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
reverses section split

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 
+#
 # Remove objects

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
SR by hand

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r d_transcript_cum}
-
 #
@@
 
+  # item_take
+  mutate(
+    item_take = paste(item, "take", sep = "_")
+  ) %>%
+
+  # course current
   group_by(
@@
     ) %>%
-  summarize(
-    course_current = list(
-      unique(item_PF)
-      )
-    ) %>%
-
+  summarize_at(
+    c("item", "item_take", "item_PF", "item_HL"),
+    function(x) list(unique(x))
+    ) %>%
+  ungroup %>%
+
+  # course current all
+  rowwise %>%
+  mutate(
+    course_current = list(c(item, item_take, item_PF, item_HL))
+    ) %>%
+  ungroup %>%
+
+  # course past
   group_by(
@@
     ) %>%
-
-  rowwise %>% # equivalent to "group by row"
-  mutate(
-    course_so_far     = list(union  (course_past, course_current)),
-    course_not_so_far = list(setdiff(course_all , course_so_far ))
-    ) %>%
-  ungroup
+  ungroup %>%
+
+  # course so far, course not so far
+  rowwise %>%
+  mutate(
+    course_past_current = list(union  (course_past, course_current      )),
+    course_not_yet      = list(setdiff(course_all , course_past_current )),
+    course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),
+    course_so_far       = list(union  (course_past, course_not_yet))
+    ) %>%
+  ungroup %>%
+
+  # lhs: past, rhs: present
+  select(
+    sequenceID,
+    lhs = course_so_far,
+    rhs = course_current
+  )
 
@@
 ```
-###Apply Functions
-We apply make_AR to get different sets of rules:
-
-#### take -> take
+
+### take -> take
 ```{r AR take}
@@
 
-#### fail -> fail
+### fail -> fail
 ```{r AR fail}
@@
 
-#### low grade -> low grade
+### low grade -> low grade
 ```{r AR low}
@@
 
-#### not take -> fail
+### not take -> fail
 ```{r AR TPF}
@@
 
-#### grade less than or equal to x -> grade less than or equal to 6
+### grade less than or equal to x -> grade less than or equal to 6
 ```{r AR grade, cache = TRUE}
@@
 ### Editing AR
-The function edit_rules makes AR easier to read.
-It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
 ```{r edit_AR}
@@
   )
-
 ```
@@
 ### Functions
-The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
+
 ```{r my_cspade function}
@@
 ```
-The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
+
 ```{r my_ruleInduction}
@@
 ```
-We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
+
 ```{r make_SR}
@@
 ```
-###Apply Functions
-We apply make_SR to get different types of sequential rules:
-#### take -> take
+
+### take -> take
 ```{r SR taken}
@@
 
-#### fail -> fail
+### fail -> fail
 ```{r SR PF}
@@
 
-#### low grade -> low grade
+### low grade -> low grade
 ```{r SR HL, cache = TRUE}
@@
 
-#### not take -> fail
+### not take -> fail
 ```{r SR TPF, eval = FALSE}
-
-#
-# SR by hand
-
-# rhs = current course
-d_transcript_cum_current <- d_transcript_cum %>%
+#
+# SR
+
+x <- d_transcript_cum %>%
+
+  # rhs
   unnest(
-    course_current,
+    rhs,
     .drop = FALSE
     ) %>%
-  rename(
-    rhs = course_current
-    )
-
-# lhs = course not so far
-d_transcript_cum_current %>%
+  filter(
+    str_detect(rhs, "low")
+    ) %>%
+
+  # lhs
   unnest(
-    course_not_so_far,
+    lhs,
     .drop = FALSE
     ) %>%
-  rename(
-    lhs = course_not_so_far
-    ) %>%
+  filter(
+    str_detect(lhs, "not")
+    ) %>%
+
+  # support
   count(
     lhs,
-    rhs,
-    sort = TRUE
-    ) %>%
-  filter(str_detect(rhs, "fail"))
-```
-
-#### grade less than or equal to x -> grade less than or equal to 6
+    rhs
+    )
+```
+
+### grade less than or equal to x -> grade less than or equal to 6
 ```{r SR G, cache = TRUE}

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r SR TPF, eval = FALSE}
-
-#
-# SR by hand
-
-# rhs = current course
-d_transcript_cum_current <- d_transcript_cum %>%
+#
+# SR
+
+x <- d_transcript_cum %>%
+
+  # rhs
   unnest(
-    course_current,
+    rhs,
     .drop = FALSE
     ) %>%
-  rename(
-    rhs = course_current
-    )
-
-# lhs = course not so far
-d_transcript_cum_current %>%
+  filter(
+    str_detect(rhs, "low")
+    ) %>%
+
+  # lhs
   unnest(
-    course_not_so_far,
+    lhs,
     .drop = FALSE
     ) %>%
-  rename(
-    lhs = course_not_so_far
-    ) %>%
+  filter(
+    str_detect(lhs, "not")
+    ) %>%
+
+  # support
   count(
     lhs,
-    rhs,
-    sort = TRUE
-    ) %>%
-  filter(str_detect(rhs, "fail"))
+    rhs
+    )
 ```

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
remove old chunk

@@
 ```
-
-SR_TPF are manually computed
-```{r, eval = FALSE}
-# current, past, not_yet
-SR_TPF <- d_transcript_cum                         %>%
-  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
-  unnest(course_current, .drop = F)                %>%
-  unnest(course_not_so_far)                        %>%
-  left_join(
-    select(d_transactions$TPF, 
-           sequenceID, eventID, item, PF), 
-    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "course_current" = "item")
-    )                                              %>%
-  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
-  rename(
-    lhs="course_not_so_far", 
-    rhs.x = "course_current", 
-    rhs.PF = "PF")                                 %>%
-  mutate(num_transactions = n())                   %>%
-  group_by(lhs)                                    %>%
-  mutate(
-    num_lhs = n(),
-    support_lhs         = num_lhs / num_transactions
-    )                                              %>%
-  group_by(rhs.x)                                  %>%
-  mutate(
-    num_rhs.x           = n(),
-    support_rhs.x       = num_rhs.x / num_transactions
-         )                                         %>%
-  group_by(rhs.x,rhs.PF)                           %>%
-  mutate(
-    num_rhs.PF          = n(),
-    support_rhs.PF      = num_rhs.PF / num_transactions
-  )                                                %>%
-  group_by(lhs, rhs.x)                             %>%
-  mutate(
-    num_rule_x          = n(),
-    support_rule_rhs.x  = num_rule_x / num_transactions
-  )                                                %>%
-  group_by(lhs, rhs.x, rhs.PF)                     %>%
-  mutate(
-    num_rule_PF          = n(),
-    support_rule_rhs.PF  = num_rule_PF / num_transactions,
-    support_rhs_bounded  = num_rule_PF / num_rule_x
-         )                                         %>%
-  ungroup()                                        %>%
-  mutate(
-    confidence                   = support_rule_rhs.PF / support_lhs,
-    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
-    lift                         = confidence / support_rhs.PF,
-    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
-  )
-```

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for summary statistics

@@
       ) %>%
+
     summarise(
+      Count           = n(),
       Min             = min(Grade),
@@
       Median          = median(Grade),
+      IQR             = IQR(Grade),
       SD              = sd(Grade),
-      `Failure Rate`  = mean(Fail),
-      `Failure Count` = sum(Fail),
-      Count           = n()
-      ) %>%
+      `Low Rate`      = mean(Grade < high_grade),
+      `Fail Rate`  = mean(Grade < pass_grade)
+      ) %>%
+
     mutate_at(
-      vars(Mean, SD, `Failure Rate`),
+      vars(Mean, SD, `Low Rate`, `Fail Rate`),
       round,
       digits = 2
+    )
+
+}
+
+# for convenience
+join_d_course <- function(data){
+
+  data %>%
+    inner_join(
+    d_course,
+    by = c("Course ID")
     )
@@
 statistics$course <- d_transcript %>%
-  inner_join(
-    d_course,
-    by = c("Course ID")
-    ) %>%
+  join_d_course %>%
   provide_statistics(`Course ID`)
@@
 statistics$cluster <- d_transcript %>%
-  inner_join(
-    d_course, 
-    by = "Course ID"
-    ) %>%
+  join_d_course %>%
   provide_statistics(Cluster)
@@
 statistics$type <- d_transcript %>%
-  inner_join(
-    d_course, by = "Course ID"
-    ) %>%
+  join_d_course %>%
   provide_statistics(Type)
@@
 statistics$concentration <- d_transcript %>%
-  inner_join(
-    d_course,
-    by = "Course ID"
-    ) %>%
+  join_d_course %>%
   gather(
@@
   # TODO: filter for student who completed their studies
-  inner_join(d_course, by = c("Course ID")) %>%
+  join_d_course %>%
   provide_statistics(Level)

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
comments until make_sequences function

--- 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
-
+We set the thresholds for passing and obtaining a high grade.
 ```{r}
@@
 For a first exploration of arules, we conceptualise our framework like this:
-transaction = student
+sequence = student
 item     = course
 
-First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts. 
 ## Data Preparation
+First we transform our data into transaction data.
+For this, we first create a vector of mandatory courses that we exclude from transcripts.
+Furthermore, for courses that span more than one period, we consider only the starting point.
+
 ### Take, fail, low grade
+For our first transactions we add variables that code whether a course has been passed/failed, or passed with a high grade/low grade.
+We assign the `Student ID` to the variable `sequenceID`, and the timing of a course (Year,period) to the `eventID`.
+We identify three different sets of items (course, course_pass/course_fail, course_high/course_low) for the creation of different rules further on.
 ```{r AR data prep 1}
@@
 ### Take / not take, pass / fail / not take
+For our second set of transactions, we come up with all possible combinations of courses and students, then categorise each as, not taken, passed or failed.
+Items are the courses with their pass/fail/not taken categories (course_pass/course_fail/course_not taken).
 ```{r transactions not taken}
@@
 ### Grade
+For our last set of transactions we would like to have cumulative probabilities so we can interpret a prediction of a grade 8 as the probability of getting an 8 or lower. 
+For this, we add additional rows to the transcripts, corresponding to all the grades above the grade that a student got for a course (e.g.
+if student_A got a grade_8 for course_B, we would add two rows: student_A/course_B/grade_9 and student_A/course_B/grade_10).
+Items in these transactions correspond to course_grade.
 ```{r transactions grade}
@@
 ### Transcript with preceding courses (for SR by hand)
+For our analysis in sequential rule mining, we extract the history of each student, and create a transcript per student, per period, which contains information on the current courses, the courses taken before the current courses, courses taken so far (including current courses) and the courses not taken so far.
 ```{r d_transcript_cum}
+
 #
@@
 
-  # item_take
-  mutate(
-    item_take = paste(item, "take", sep = "_")
-  ) %>%
-
-  # course current
   group_by(
@@
     ) %>%
-  summarize_at(
-    c("item", "item_take", "item_PF", "item_HL"),
-    function(x) list(unique(x))
-    ) %>%
-  ungroup %>%
-
-  # course current all
-  rowwise %>%
-  mutate(
-    course_current = list(c(item, item_take, item_PF, item_HL))
-    ) %>%
-  ungroup %>%
-
-  # course past
+  summarize(
+    course_current = list(
+      unique(item_PF)
+      )
+    ) %>%
+
   group_by(
@@
     ) %>%
-  ungroup %>%
-
-  # course so far, course not so far
-  rowwise %>%
-  mutate(
-    course_past_current = list(union  (course_past, course_current      )),
-    course_not_yet      = list(setdiff(course_all , course_past_current )),
-    course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),
-    course_so_far       = list(union  (course_past, course_not_yet))
-    ) %>%
-  ungroup %>%
-
-  # lhs: past, rhs: present
-  select(
-    sequenceID,
-    lhs = course_so_far,
-    rhs = course_current
-  )
+
+  rowwise %>% # equivalent to "group by row"
+  mutate(
+    course_so_far     = list(union  (course_past, course_current)),
+    course_not_so_far = list(setdiff(course_all , course_so_far ))
+    ) %>%
+  ungroup
 
@@
 ## Transactions
+The function make_transactions takes a data.frame and the item label and converts it into an object of class transaction. 
+We create transactions with the different types of data we prepared above (i.e. taken, pass/fail, high/low, NotTaken/pass/fail, Grades).
 ```{r making transactions, message = FALSE}
@@
 ## Sequences
+The function make_sequence takes a data.frame and the item label and converts it into an object of class sequences (used for extracting sequential rules).
+We create sequences with the different types of data we prepared above (i.e. taken, pass/fail, high/low, Grades).
 ```{r making sequences}
@@
 ```{r SR TPF, eval = FALSE}
-#
-# SR
-
-x <- d_transcript_cum %>%
-
-  # rhs
+
+#
+# SR by hand
+
+# rhs = current course
+d_transcript_cum_current <- d_transcript_cum %>%
   unnest(
-    rhs,
+    course_current,
     .drop = FALSE
     ) %>%
-  filter(
-    str_detect(rhs, "low")
-    ) %>%
-
-  # lhs
+  rename(
+    rhs = course_current
+    )
+
+# lhs = course not so far
+d_transcript_cum_current %>%
   unnest(
-    lhs,
+    course_not_so_far,
     .drop = FALSE
     ) %>%
-  filter(
-    str_detect(lhs, "not")
-    ) %>%
-
-  # support
+  rename(
+    lhs = course_not_so_far
+    ) %>%
   count(
     lhs, 
-    rhs
-    )
+    rhs,
+    sort = TRUE
+    ) %>%
+  filter(str_detect(rhs, "fail"))
 ```

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ### Transcript with preceding courses (for SR by hand)
+For our analysis in sequential rule mining, we extract the history of each student, and create a transcript per student, per period, which contains information on the current courses, the courses taken before the current courses, courses taken so far (including current courses) and the courses not taken so far.
 ```{r d_transcript_cum}

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
spelling mistake

@@
 ## Support
+We calculate the support for all rules manually.
 ```{r}
@@
 #
-# Probability oh having a grade equal or lower than x
+# Probability of having a grade equal or lower than x
 d_support$G <- d_transactions$taken_PF_HL %>%

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
comment support
comments

@@
 ## Support
-We calculate the support for all rules manually.
+We calculate manually the probabilities of:
+a) taking a course
+b) failing a course
+c) getting a low grade
+d) getting a grade equal or lower than x (a certain grade).
 ```{r}
@@
 
-The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-
+The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe.
 ```{r function clean_rules}
@@
 ```
-The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
+The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade, with a specified confidence.
 ```{r my_ruleInduction}

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
Major re-organization of script: functions to make rules before making rules

--- 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```
-We set the thresholds for passing and obtaining a high grade.
-```{r}
+
+```{r for convenience}
 pass_grade <- 5.5
 high_grade <- 6.5
+
+join_d_course <- function(data){
+
+  data %>%
+    inner_join(
+    d_course,
+    by = c("Course ID")
+    )
+
+}
+
+join_d_transcript <- function(data){
+
+  data %>%
+    inner_join(
+    d_transcript,
+    by = c("Course ID")
+    )
+
+}
 ```
@@
 
-```{r statistic summary}
+```{r statistic summary, cache = TRUE}
 
@@
 
-# for convenience
-join_d_course <- function(data){
-
-  data %>%
-    inner_join(
-    d_course,
-    by = c("Course ID")
-    )
-
-}
-
 #
@@
 
-# Concentration evel
+# Concentration level
 statistics$concentration <- d_transcript %>%
@@
   provide_statistics(Level)
-
-#
-# output
+```
+
+```{r, include = FALSE}
 save(
@@
   )
-
-rm(statistics)
+```
+
+```{r, include = FALSE}
+rm(statistics, provide_statistics)
 ```
@@
 For a first exploration of arules, we conceptualise our framework like this:
-sequence = student
+transaction = student
 item = course
 
+First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts. 
 ## Data Preparation
-First we transform our data into transaction data.
-For this, we first create a vector of mandatory courses that we exclude from transcripts.
-Furthermore, for courses that span more than one period, we consider only the starting point.
 
 ### Take, fail, low grade
-For our first transactions we add variables that code whether a course has been passed/failed, or passed with a high grade/low grade.
-We assign the `Student ID` to the variable `sequenceID`, and the timing of a course (Year,period) to the `eventID`.
-We identify three different sets of items (course, course_pass/course_fail, course_high/course_low) for the creation of different rules further on.
-```{r AR data prep 1}
+```{r d_transaction taken_PF_HL}
 d_transactions <- list()
@@
     Type != "Mandatory",  # (i) mandatory courses e.g. COR, CAP, etc
-    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
-                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
-    ) %>%
-
-  # Join with transcripts.
-  select(- Period) %>%
-  inner_join(
-    d_transcript,
-    by = "Course ID"
-    ) %>%
+    ! Letters %in% c(
+      "SKI", "PRO",       # (ii) skills & projects (taken by majority of students)
+      "SAS", "SAH", "SAC" # (iii) courses of semester abroad (uninformative)
+      )
+    ) %>%
+
+  # Join with transcripts
+  select(
+    - Period
+    ) %>%
+  join_d_transcript %>%
 
   # Identifying sequenceID
-  rename(sequenceID = `Student ID`) %>%
+  rename(
+    sequenceID = `Student ID`
+    ) %>%
 
@@
   mutate(
-    PF = case_when( Grade <  pass_grade ~ "fail",
-                    Grade >= pass_grade ~ "pass"),
-    HL = case_when( Grade <  high_grade ~ "low",
-                    Grade >= high_grade ~ "high"),
+    PF = case_when(
+      Grade <  pass_grade ~ "fail",
+      Grade >= pass_grade ~ "pass"
+      ),
+    HL = case_when(
+      Grade <  high_grade ~ "low",
+      Grade >= high_grade ~ "high"
+      ),
 
     item    = `Course ID`,
-    item_PF = paste(`Course ID`, PF, sep = "_"),
-    item_HL = paste(`Course ID`, HL, sep = "_")
-    )
-
+    item_PF = paste(item, PF, sep = "_"),
+    item_HL = paste(item, HL, sep = "_")
+    )
+```
+
+```{r for convenience II}
+course_all  <- unique(d_transactions$taken_PF_HL$item      )
+student_all <- unique(d_transactions$taken_PF_HL$sequenceID)
+n_students  <- length(student_all)
 ```
@@
 ### Take / not take, pass / fail / not take
-For our second set of transactions, we come up with all possible combinations of courses and students, then categorise each as, not taken, passed or failed.
-Items are the courses with their pass/fail/not taken categories (course_pass/course_fail/course_not taken).
-```{r transactions not taken}
+```{r d_transactions TPF}
 d_transactions$TPF <- expand.grid(
@@
   # Expand along students (sequenceID) and courses (itemID)
-  sequenceID = unique(d_transactions$taken_PF_HL$sequenceID),
-  item       = unique(d_transactions$taken_PF_HL$item),
+  sequenceID       = student_all,
+  item             = course_all,
   stringsAsFactors = FALSE
@@
 
-  # Create 
+  # Create item
   mutate(
@@
       Grade <  pass_grade ~ "fail",
-      TRUE               ~ "pass"
+      Grade >= pass_grade ~ "pass"
       ),
@@
     )
-
-rm(high_grade, pass_grade)
 ```
@@
 ### Grade
-For our last set of transactions we would like to have cumulative probabilities so we can interpret a prediction of a grade 8 as the probability of getting an 8 or lower. 
-For this, we add additional rows to the transcripts, corresponding to all the grades above the grade that a student got for a course (e.g.
-if student_A got a grade_8 for course_B, we would add two rows: student_A/course_B/grade_9 and student_A/course_B/grade_10).
-Items in these transactions correspond to course_grade.
 ```{r transactions grade}
-
 d_transactions$G <- d_transactions$taken_PF_HL %>%
 
-  # Spread along rounded grades
+  # Spread along ceiling grades
   mutate(
@@
 
-  # fill grades inferior to obtained grade with TRUE
+  # grade x or lower
   mutate(
@@
 ### Transcript with preceding courses (for SR by hand)
-For our analysis in sequential rule mining, we extract the history of each student, and create a transcript per student, per period, which contains information on the current courses, the courses taken before the current courses, courses taken so far (including current courses) and the courses not taken so far.
-```{r d_transcript_cum}
-#
-# List of all courses
-course_all <- unique(d_transactions$taken_PF_HL$item)
-
-#
-# courses taken so far and not taken so far
+```{r d_transcript_cum, cache = TRUE, warning = FALSE}
 d_transcript_cum <- d_transactions$taken_PF_HL %>%
@@
   mutate(
+
     course_past_current = list(union  (course_past, course_current      )),
+
     course_not_yet      = list(setdiff(course_all , course_past_current )),
     course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),
+
     course_so_far       = list(union  (course_past, course_not_yet))
+
     ) %>%
@@
   )
-
-rm(course_all)
 ```
@@
 ## Transactions
-The function make_transactions takes a data.frame and the item label and converts it into an object of class transaction. 
-We create transactions with the different types of data we prepared above (i.e. taken, pass/fail, high/low, NotTaken/pass/fail, Grades).
-```{r making transactions, message = FALSE}
-
+```{r making transactions, cache = TRUE}
 make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){
@@
 
-#
-# Checking transactions
 # inspect(head(transactions, 10))
-
-rm(make_transaction)
 ```
@@
 ## Sequences
-The function make_sequence takes a data.frame and the item label and converts it into an object of class sequences (used for extracting sequential rules).
-We create sequences with the different types of data we prepared above (i.e. taken, pass/fail, high/low, Grades).
-```{r making sequences}
-
+```{r making sequences, cache = TRUE}
 make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){
 
-    # make transactions
   data_temp <- data %>%
@@
     filter(
-      !is.na(eventID) #this is here casue we have courses that were never taken.
+      !is.na(eventID) # exclude courses that were never taken.
       ) %>% 
@@
 
-  # indicating sequence ID and event ID for each transaction
+  # indicate sequence ID and event ID for each transaction
   sequences@itemsetInfo <- data_temp %>%
@@
 sequences$HL    <- make_sequence(item = item_HL)
-#sequences_TPF  <- make_sequence(data = d_transactions$TPF, item = item_TPF) # compute ad hoc
 sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )
 
-#
-# Checking sequences
- inspect(head(sequences$G, 10))
-
-rm(make_sequence #, d_transactions
-   )
+#inspect(head(sequences$G, 10))
 ```
@@
 ```{r}
-
-#
-# Number of students
-n_students <- d_transactions$taken_PF_HL %>%
-  select(sequenceID) %>%
-  n_distinct
-
-#
-# Support
 d_support <- list()
 
-#
 # Probability of taking a course
@@
 
+```{r, include = FALSE}
+save(
+  transactions, sequences,
+  d_transcript_cum,
+  d_support, n_students,
+  file = "Output/Transaction and Sequences.RDATA"
+  )
+```
+
+```{r, include = FALSE}
+rm(
+
+  high_grade, pass_grade, 
+  course_all, student_all, n_students,
+
+  d_transactions, d_support, d_transcript_cum,
+
+  make_transaction, transactions, 
+  make_sequence, sequences
+  )
+```
+
 # Mining Rules
-## Association Rule
-
-### Functions
+
+```{r}
+load("Output/Transaction and Sequences.RDATA")
+```
+
+## Functions
+
+### my_aprior, my_cspade and my_ruleInduction
 
@@
 
+The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
+```{r my_cspade function}
+my_cspade <- function(data){
+
+  data %>%
+
+    cspade(
+
+      parameter = list(
+
+        # only include subsequences of the type {one item} => {one item}
+        maxlen  = 2,   # max length of sequence
+        maxsize = 1,   # max number item for element
+
+        # include all such subsequences
+        support = 0,   # min suppor
+        mingap  = 1,   # min time difference between consecutive element
+        maxgap  = 1e4  # max time difference between consecutive element
+
+        ),
+
+      control = list(
+        verbose = FALSE
+        )
+
+      )
+
+}
+```
+
+The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
+```{r my_ruleInduction}
+my_ruleInduction <- function(rules){
+
+  rules %>%
+
+    ruleInduction(
+
+      # keep all subsequences
+      confidence = 0,
+
+      control    = list(verbose = FALSE)
+
+      )
+
+}
+```
+
+### clean_rules
 The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-
 ```{r function clean_rules}
@@
 
+### compute_rhs.support
 The function `compute_support()` computes the support of the lhs and rhs of the rules.
@@
 ```
+
+### make_AR and  make_SR (wrapers)
 
@@
 ```
-###Apply Functions
-We apply make_AR to get different sets of rules:
-
-#### take -> take
-```{r AR take}
-AR <- list()
-
-AR$taken <- transactions$taken %>%
-  make_AR(
-    data_support = d_support$TNT, 
-    type_rule = rate.take
-    )
-```
-
-#### fail -> fail
-```{r AR fail}
-AR$PF <- transactions$PF %>%
-
-  make_AR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.fail
-    ) %>%
-
-  # Confidence and Lift by hand
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
-
-  # lhs and rhs must be fail
-  filter(
-    str_detect(lhs, "fail"),
-    str_detect(rhs, "fail")
-    )
-```
-
-#### low grade -> low grade
-```{r AR low}
-AR$HL <- transactions$HL %>%
-
-  make_AR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.low
-    ) %>%
-
-  # Confidence and Lift by hand
-  group_by(
-    lhs, 
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
-
-  # lhs and rhs must be fail, count >= 5
-  filter(
-    str_detect(lhs, "low"),
-    str_detect(rhs, "low")
-    )
-```
-
-#### not take -> fail
-```{r AR TPF}
-AR$TPF <- transactions$TPF %>%
-
-  make_AR(
-    data_support = d_support$PF_HL, 
-    type_rule = rate.fail
-  ) %>%
-
-  # Confidence and Lift
-  mutate(
-    rhs.taken = str_detect(rhs, "fail|pass")
-    ) %>%
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-    mutate(
-    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
-
-  # lhs and rhs must be fail, count >= 5
-  filter(
-    str_detect(lhs, "not taken"),
-    str_detect(rhs, "fail")
-    )
-```
-
-#### grade less than or equal to x -> grade less than or equal to 6
-```{r AR grade, cache = TRUE}
-AR$G <- transactions$G %>%
-
-  my_apriori %>%
-  clean_rules %>%
-
-  # rhs.support
-  left_join(
-    d_support$G,
-    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
-    ) %>%
-  mutate(
-    rhs.support = support.grade
-    ) %>%
-
-  # Confidence and lift
-  group_by(
-    lhs, 
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = max(support),
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
-    confidence          = support / lhs.rhsTake.support,
-    lift                = confidence / rhs.support
-    ) %>%
-  ungroup %>%
-
-  # reduce number of rules
-  filter(
-    lhs_course != rhs_course, # exclude rules with same course on lhs and rhs
-    rhs_outcome == 6            
-    ) %>%
-
-  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
-  group_by(
-    lhs_course, 
-    rhs_course
-    ) %>%
-  top_n(
-    1,
-    lift
-    ) %>%
-  ungroup
-```
-
-### Editing AR
-The function edit_rules makes AR easier to read.
-It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
-```{r edit_AR}
-edit_rules <- function(AR){
-
-  AR %>%
-
-    mutate(
-      count = support * n_students
-    ) %>%
-
-    filter(
-      count >= 5
-      ) %>%
-
-    mutate_if(
-      is.numeric,
-      funs(round(., 5))
-    ) %>%
-
-    select(
-      lhs       , rhs,
-      support   , count,
-      confidence, rhs.support,
-      lift,
-      matches("rhsTake")
-    ) %>%
-
-    arrange(
-      desc(count)
-    )
-
-}
-
-AR <- lapply(
-  X   = AR,
-  FUN = edit_rules
-  )
-```
-
-### Save Association Rules
-We save and remove objects:
-```{r saving and rm}
-#
-# Save association rules
-save(
-  AR,
-  file = "App/AR.RDATA"
-  )
-
-# Remove objects
-rm(
-  my_apriori, make_AR,
-  AR, transaction
-  )
-
-```
-
-## Sequence Rules
-### Functions
-The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
-```{r my_cspade function}
-my_cspade <- function(data){
-
-  data %>%
-
-    cspade(
-
-      parameter = list(
-
-        # only include subsequences of the type {one item} => {one item}
-        maxlen  = 2,   # max length of sequence
-        maxsize = 1,   # max number item for element
-
-        # include all such subsequences
-        support = 0,   # min suppor
-        mingap  = 1,   # min time difference between consecutive element
-        maxgap  = 1e4  # max time difference between consecutive element
-
-        ),
-
-      control = list(
-        verbose = FALSE
-        )
-
-      )
-
-}
-```
-The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
-```{r my_ruleInduction}
-my_ruleInduction <- function(rules){
-
-  rules %>%
-
-    ruleInduction(
-
-      # keep all subsequences
-      confidence = 0,
-
-      control    = list(verbose = FALSE)
-
-      )
-
-}
-```
+
 We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
@@
 ```
-###Apply Functions
+
+## Association Rule
+We apply make_AR to get different sets of rules:
+
+### take -> take
+```{r AR take, cache = TRUE, warning = FALSE}
+AR <- list()
+
+AR$taken <- transactions$taken %>%
+  make_AR(
+    data_support = d_support$TNT, 
+    type_rule = rate.take
+    )
+```
+
+### fail -> fail
+```{r AR fail, cache = TRUE}
+AR$PF <- transactions$PF %>%
+
+  make_AR(
+    data_support = d_support$PF_HL,
+    type_rule = rate.fail
+    ) %>%
+
+  # Confidence and Lift by hand
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+    ) %>%
+  ungroup %>%
+
+  mutate(
+    confidence = support / lhs.rhsTake.support,
+    lift       = confidence / rhs.support
+    ) %>%
+
+  # lhs and rhs must be fail
+  filter(
+    str_detect(lhs, "fail"),
+    str_detect(rhs, "fail")
+    )
+```
+
+### low grade -> low grade
+```{r AR low, cache = TRUE}
+AR$HL <- transactions$HL %>%
+
+  make_AR(
+    data_support = d_support$PF_HL,
+    type_rule = rate.low
+    ) %>%
+
+  # Confidence and Lift by hand
+  group_by(
+    lhs, 
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+    ) %>%
+  ungroup %>%
+
+  mutate(
+    confidence = support / lhs.rhsTake.support,
+    lift       = confidence / rhs.support
+    ) %>%
+
+  # lhs and rhs must be fail, count >= 5
+  filter(
+    str_detect(lhs, "low"),
+    str_detect(rhs, "low")
+    )
+```
+
+### not take -> fail
+```{r AR TPF, cache = TRUE}
+AR$TPF <- transactions$TPF %>%
+
+  make_AR(
+    data_support = d_support$PF_HL, 
+    type_rule = rate.fail
+  ) %>%
+
+  # Confidence and Lift
+  mutate(
+    rhs.taken = str_detect(rhs, "fail|pass")
+    ) %>%
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+    mutate(
+    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+    ) %>%
+  ungroup %>%
+
+  mutate(
+    confidence = support / lhs.rhsTake.support,
+    lift       = confidence / rhs.support
+    ) %>%
+
+  # lhs and rhs must be fail, count >= 5
+  filter(
+    str_detect(lhs, "not taken"),
+    str_detect(rhs, "fail")
+    )
+```
+
+### grade less than or equal to x -> grade less than or equal to 6
+```{r AR grade, cache = TRUE}
+AR$G <- transactions$G %>%
+
+  my_apriori %>%
+
+  clean_rules %>%
+
+  # rhs.support
+  left_join(
+    d_support$G,
+    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
+    ) %>%
+  mutate(
+    rhs.support = support.grade
+    ) %>%
+
+  # Confidence and lift
+  group_by(
+    lhs, 
+    rhs_course
+    ) %>%
+  mutate(
+    lhs.rhsTake.support = max(support),
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
+    confidence          = support / lhs.rhsTake.support,
+    lift                = confidence / rhs.support
+    ) %>%
+  ungroup %>%
+
+  # reduce number of rules
+  filter(
+    lhs_course  != rhs_course, # exclude rules with same course on lhs and rhs
+    rhs_outcome == 6            
+    ) %>%
+
+  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
+  group_by(
+    lhs_course, 
+    rhs_course
+    ) %>%
+  top_n(
+    1,
+    lift
+    ) %>%
+  ungroup
+```
+
+## Sequence Rules
 We apply make_SR to get different types of sequential rules:
-#### take -> take
-```{r SR taken}
+
+### take -> take
+```{r SR taken, cache = TRUE}
 SR <- list()
@@
 
-#### fail -> fail
-```{r SR PF}
+### fail -> fail
+```{r SR PF, cache = TRUE}
 SR$PF <- sequences$PF %>%
@@
 
-#### grade less than or equal to x -> grade less than or equal to 6
+### grade less than or equal to x -> grade less than or equal to 6
 ```{r SR G, cache = TRUE}
@@
 
-### Editing SR
-We apply `edit_rules` to SR in order to get easily readable rules. 
-```{r SR edit}
+## Editing rules
+The function edit_rules makes AR easier to read.
+It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
+```{r edit_rules}
+edit_rules <- function(AR){
+
+  AR %>%
+
+    mutate(
+      count = support * n_students
+    ) %>%
+
+    filter(
+      count >= 5
+      ) %>%
+
+    mutate_if(
+      is.numeric,
+      funs(round(., 5))
+    ) %>%
+
+    select(
+      lhs       , rhs,
+      support   , count,
+      confidence, rhs.support,
+      lift,
+      matches("rhsTake")
+    ) %>%
+
+    arrange(
+      desc(count)
+    )
+
+}
+```
+
+```{r edit rules}
+AR <- lapply(
+  X   = AR,
+  FUN = edit_rules
+  )
+
 SR <- lapply(
@@
 
-### Save Sequences Rules
-```{r SR save}
-#
-# Save Sequence rules
+```{r show rules}
+print(AR$TPF)
+print(SR$HL)
+```
+
+```{r save rules, include = FALSE}
 save(
-  SR,
-  file = "App/SR.RDATA"
-)
-
-#
-# Remove objects
-rm(
-  SR, sequences,
-  my_cspade, my_ruleInduction, clean_rules, compute_rhs.support, edit_rules, make_SR,
-  n_students
-)
-```
+  AR, SR,
+  file = "App/rules.RDATA"
+  )
+```

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
function to compute confidence and lift

@@
   select(
-    sequenceID,
     lhs = course_so_far,
@@
 
+### compute_conf_lift
+
+```{r}
+compute_conf_lift <- function(rules){
+
+  rules %>%
+
+  # support (and count) of doing lhs and taking course of rhs
+  group_by(
+    lhs,
+    rhs_course
+    ) %>%
+    mutate(
+      lhs.rhsTake.support = sum(support),
+      lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+      ) %>%
+    ungroup %>%
+
+    mutate(
+      confidence = support / lhs.rhsTake.support,
+      lift       = confidence / rhs.support
+      )
+
+}
+```
+
 ### make_AR and  make_SR (wrapers)
@@
 
-  # Confidence and Lift by hand
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
+  compute_conf_lift %>%
 
@@
 
-  # Confidence and Lift by hand
-  group_by(
-    lhs, 
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
+  compute_conf_lift %>%
 
@@
   # Confidence and Lift
-  mutate(
-    rhs.taken = str_detect(rhs, "fail|pass")
-    ) %>%
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-    mutate(
-    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
+  filter(
+    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
+    ) %>%
+  compute_conf_lift %>%
 
@@
   filter(
-    str_detect(lhs, "not taken"),
+    str_detect(lhs, "not"),
     str_detect(rhs, "fail")
@@
     lhs.rhsTake.support = max(support),
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+    ) %>%
+  ungroup %>%
+
+  mutate(
     confidence = support / lhs.rhsTake.support,
@@
 
-  # Confidenca and lift by hand
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-  ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
+  compute_conf_lift %>%
 
@@
 
-    # Confidenca and lift by hand
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-  ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
+  compute_conf_lift %>%
 
@@
 
-#### not take -> fail
-```{r SR TPF, eval = FALSE}
-#
-# SR
-
-x <- d_transcript_cum %>%
+### not take -> fail
+```{r SR TPF, cache = TRUE}
+SR$TPF <- d_transcript_cum %>%
 
@@
   filter(
-    str_detect(rhs, "low")
+    str_detect(rhs, "pass|fail")
     ) %>%
@@
 
-  # support
+  # rule
+  unite(
+    col = "rule",
+    lhs, rhs,
+    sep = " => "
+    ) %>%
+
+  # rule support
   count(
-    lhs,
-    rhs
+    rule
+    ) %>%
+  mutate(
+    support = n / n_students
+    ) %>%
+
+  # regular fucntions
+  clean_rules %>%
+
+  compute_rhs.support(
+    data_support = d_support$PF_HL,
+    type_rule    = rate.fail
+    ) %>%
+
+  compute_conf_lift %>%
+
+  # lhs not, rhs low
+  filter(
+    str_detect(rhs, "fail")
     )
@@
     lhs.rhsTake.support = max(support),
+    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
+    ) %>%
+  ungroup %>%
+
+  mutate(
     confidence = support / lhs.rhsTake.support,
@@
 ```{r edit_rules}
-edit_rules <- function(AR){
-
-  AR %>%
+edit_rules <- function(rules){
+
+  rules %>%
 
@@
 print(AR$TPF)
-print(SR$HL)
+print(SR$TPF)
 ```

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
new type of rules: not => low

@@
 ### Take / not take, pass / fail / not take
-```{r d_transactions TPF}
-d_transactions$TPF <- expand.grid(
+```{r d_transactions T_PF_HL}
+d_transactions$T_PF_HL <- expand.grid(
 
@@
     TPF = case_when(
-      is.na(Grade)        ~ "not taken",
+      is.na(Grade)        ~ "not",
       Grade <  pass_grade ~ "fail",
@@
       ),
-
-    item_TPF = paste(item, TPF, sep = "_")
+    THL = case_when(
+      is.na(Grade)        ~ "not",
+      Grade <  high_grade ~ "low",
+      Grade >= high_grade ~ "high"
+      ),
+
+    item_TPF = paste(item, TPF, sep = "_"),
+
+    item_THL = paste(item, THL, sep = "_")
 
@@
 transactions$HL    <- make_transaction(item = item_HL)
-transactions$TPF   <- make_transaction(data = d_transactions$TPF, item = item_TPF)
+transactions$TPF   <- make_transaction(data = d_transactions$T_PF_HL, item = item_TPF)
+transactions$THL   <- make_transaction(data = d_transactions$T_PF_HL, item = item_THL)
 transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )
 
-# inspect(head(transactions, 10))
+# inspect(head(transactions$taken, 10))
 ```
@@
   make_sequence, sequences
+
   )
@@
 
-### not take -> fail
+### not -> fail
 ```{r AR TPF, cache = TRUE}
@@
   filter(
+    str_detect(lhs, "not"),
     str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
@@
 
+  # rhs must be fail, count >= 5
+  filter(
+    str_detect(rhs, "fail")
+    )
+```
+
+### not -> low
+```{r AR THL, cache = TRUE}
+AR$THL <- transactions$THL %>%
+
+  make_AR(
+    data_support = d_support$PF_HL, 
+    type_rule = rate.low
+    ) %>%
+
+  # only keep lhs is not and rhs is low or high to compute Confidence and Lift
+  filter(
+    str_detect(lhs, "not"),
+    str_detect(rhs, "low|high")
+    ) %>%
+  compute_conf_lift %>%
+
   # lhs and rhs must be fail, count >= 5
   filter(
-    str_detect(lhs, "not"),
-    str_detect(rhs, "fail")
+    str_detect(rhs, "low")
     )
@@
 ### grade less than or equal to x -> grade less than or equal to 6
+
 ```{r AR grade, cache = TRUE}
@@
 ### take -> take
-```{r SR taken, cache = TRUE}
+```{r SR taken, cache = TRUE, warning = FALSE}
 SR <- list()
@@
 
-### not take -> fail
+### not -> fail
 ```{r SR TPF, cache = TRUE}
@@
 
+### not -> low
+```{r SR THL, cache = TRUE}
+SR$THL <- d_transcript_cum %>%
+
+  # rhs
+  unnest(
+    rhs,
+    .drop = FALSE
+    ) %>%
+  filter(
+    str_detect(rhs, "high|low")
+    ) %>%
+
+  # lhs
+  unnest(
+    lhs,
+    .drop = FALSE
+    ) %>%
+  filter(
+    str_detect(lhs, "not")
+    ) %>%
+
+  # rule
+  unite(
+    col = "rule",
+    lhs, rhs,
+    sep = " => "
+    ) %>%
+
+  # rule support
+  count(
+    rule
+    ) %>%
+  mutate(
+    support = n / n_students
+    ) %>%
+
+  # regular fucntions
+  clean_rules %>%
+
+  compute_rhs.support(
+    data_support = d_support$PF_HL,
+    type_rule    = rate.low
+    ) %>%
+
+  compute_conf_lift %>%
+
+  # lhs not, rhs low
+  filter(
+    str_detect(rhs, "low")
+    )
+```
+
 ### grade less than or equal to x -> grade less than or equal to 6
@@
     filter(
-      count >= 5
+      count >= 10
       ) %>%
@@
 ```{r show rules}
-print(AR$TPF)
-print(SR$TPF)
+print(AR$THL)
+print(SR$THL)
 ```

### 2019-02-14 App/ui.R

@@ -13,7 +13,7 @@ fluidPage(
       # Input: button for the type of rules
       radioButtons(
         inputId = "rules",
-        label = "Type of rules",
+        label   = "Type of rules",
         choices = c(
           "Association rules" = "AR",
           "Sequence rules"    = "SR"
@@ -30,6 +30,7 @@ fluidPage(
           "fail => fail"                   = "PF",
           "Low grade (< 6.5) => low grade" = "HL",
           "not taken or fail => fail"      = "TPF",
+          "not taken or fail => low"       = "THL",
           "less than => less than"         = "G"
         ),
         selected = "taken"

### 2019-02-15 Data Preparation.Rmd
save cached results in folder `Cache`

@@
     toc: TRUE
+editor_options: 
+  chunk_output_type: console
 ---
+
+```{r setup, include = T}
+knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
+```
 
@@
 # Variable Engineering
-## Program Data
+## Course Data
 The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
@@
   if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
-                                                 as.tibble(cbind(observation,
+                                                 as_tibble(cbind(observation,
                                                                  AoD)))
@@
 ```{r}
+
 d_transcript <- d_transcript %>%
+
+  # Remove variables with only one value
+  select_if(
+    function(x) n_distinct(x) > 1
+  ) %>%
+
+  # Remove variables with more than 99% NA
+  select_if(
+    function(x) mean(is.na(x)) < 0.99
+  )
+
+d_transcript <- d_transcript %>%
+
   # only keep one observation (with the final grade) per student-course
-  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
+  filter(
+    `Appraisal (Description)` == "Grade supervisor",
+    `Appraisal Type`=="7055"
+    ) %>%
   select(`Student Number`,

### 2019-02-15 trial transcript exploration.R

@@ -1,0 +1,94 @@
+d_transcript %>%
+  count(`Student Number`, sort = TRUE)
+
+d_transcript %>%
+  count(`Module (Abbrev.)`, sort = TRUE)
+
+d_transcript %>%
+  count(`Module (Desc.)`, sort = TRUE)
+
+d_transcript %>%
+  count(`Program (Abbreviation)`, sort = TRUE) # looks like UCM is 7501
+
+d_transcript %>%
+  count(`Program (Description)`, sort = TRUE) # counts match
+
+d_transcript %>%
+  count(`Academic Year`) # 2007 - increase - 2009 - decrease - 2013 - increase - 2017
+
+d_transcript %>%
+  count(`Academic Session`, sort = TRUE) # decrease from 100 to 200 and from 400 to 500 caused by drop out?
+
+d_transcript %>%
+  count(`Appraisal Type`, sort = TRUE) # there are five main appraisal types (7055, 10, 7050, 7005, 7000)
+
+d_transcript %>%
+  count(`Appraisal (Description)`, sort = TRUE) # also five main appraisal description, but the counts do not match
+
+d_transcript %>%
+  count(`Number rep. attemp`)
+
+x <- d_transcript %>%
+  count(`Grade symbol`) # there are grades superior to 10
+
+d_transcript %>%
+  count(`Appraisal date`, sort = TRUE) # are these dates deadlines for grade submition?
+
+d_transcript %>%
+  count(`Attempted credits`, sort = TRUE) # mostly 0. Surprising.
+
+d_transcript %>%
+  count(`Earned Credits`, sort = TRUE) # mostly 0. Surprising.
+
+d_transcript %>%
+  count(`Individual Work`, sort = TRUE) # mostly NA
+
+d_transcript %>%
+  count(`Academic Work ID`, sort = TRUE) # unique id for each student-course combination
+
+d_transcript %>%
+  count(`Booking Status (Desc.)`) # what is booked?
+
+d_transcript %>%
+  count(`Object ID`, sort = TRUE) # moslty 0
+
+d_transcript %>%
+  count(`Appraiser ID`, sort = TRUE) 
+
+d_transcript %>%
+  count(`Appraiser Name`, sort = TRUE) # counts match
+
+
+
+
+# Remark 1: course code are unique, course title are not
+d_transcript %>%
+  distinct(
+    `Module (Abbrev.)`,
+    `Module (Desc.)`
+  ) %>%
[…]

### 2019-02-15 Baby Recommender.Rmd
Matches students to rules

---
title: "Pillar A1"
author: "DARS"
date: "2/15/2019"
output: pdf_document
---

```{r library}
library(tidyverse)
```

#Setup
This contains AR and SR
```{r setup}
load("App/rules.RDATA")
```

First we gather a sample of students to provide recommendations to:
```{r sample}

student <- "6060984"

students <- unique(d_transcript$`Student ID`)
size = floor(length(students)/10)

#
##Sample student IDs
set.seed(123)
s1 <- sample(
  x    = students,
  size = size 
)
#
##Transcripts of selected students
target_transcript <- d_transcript    %>%
  mutate(Period= substr(Period,1,1)) %>%
  filter(
    `Student ID` %in% s1
  )

```

For a single student:
```{r truncated transcript}

course_sample_size <- 5

student <- "6087742"

student_transcript <- target_transcript %>% 
    filter(`Student ID` == student) %>%
  arrange(Year_numerical, Period)

length_student_transcript <- nrow(student_transcript)

#
##Truncated student transcript
sample_transcript      <- student_transcript[1:course_sample_size,]
prospective_courses <- student_transcript[(course_sample_size+1):(course_sample_size+3),] %>% 
  select(`Student ID`, `Course ID`)
```

##Matching rules to students:
###Taken
```{r will take}
taken_match <- AR$taken %>%
  left_join(sample_transcript, by = c("lhs"="Course ID"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

recommendations <- taken_match[1:5,] %>% select(rhs)

```

###PF
Note we need to take the d_transactions, not the transcripts! cause we need the columns item_PF
```{r will take}
AR$PF
taken_redFlag <- AR$PF %>%
  left_join(prospective_courses, by = c("lhs"="Course ID"))%>%
  drop_na() %>%
  group_by(rhs) %>%
  mutate(RHS_vote= n())%>%
  arrange(desc(RHS_vote))

```

###HL
```{r will take}
AR$HL

```

### 2019-02-15 Baby Recommender.Rmd
loads d_transactions
replaces d_transcript with d_transaction

@@
 load("App/rules.RDATA")
+load("Output/transaction_df.RDATA")
 ```
 
-First we gather a sample of students to provide recommendations to:
+First we gather a sample of students to provide recommendations to. We use `d_transactions$taken_PF_HL`
 ```{r sample}
@@
 
-students <- unique(d_transcript$`Student ID`)
+students <- unique(d_transactions$taken_PF_HL$sequenceID)
 size = floor(length(students)/10)
@@
 ##Transcripts of selected students
-target_transcript <- d_transcript    %>%
-  mutate(Period= substr(Period,1,1)) %>%
+target_transcript <- d_transactions$taken_PF_HL %>%
   filter(
-    `Student ID` %in% s1
-  )
+    sequenceID %in% s1
+  ) %>%
+  select(-`Period (additional)`, -`Period (additional bis)`, -`Concentration (additional)`)
 
@@
 
-student <- "6087742"
+student <- "6036972"
 
 student_transcript <- target_transcript %>% 
-    filter(`Student ID` == student) %>%
+    filter(sequenceID == student) %>%
   arrange(Year_numerical, Period)
@@
 sample_transcript      <- student_transcript[1:course_sample_size,]
-prospective_courses <- student_transcript[(course_sample_size+1):(course_sample_size+3),] %>% 
-  select(`Student ID`, `Course ID`)
+prospective_courses <- student_transcript[(course_sample_size+1):(course_sample_size+2),] #%>% 
+  #select(sequenceID, `Course ID`)
 ```
@@
 taken_match <- AR$taken %>%
-  left_join(sample_transcript, by = c("lhs"="Course ID"))%>%
+  left_join(sample_transcript, by = c("lhs"="item"))%>%
   drop_na() %>%
@@
 ```
-
+####Check
+```{r evaluation}
+recommendations %>%
+  left_join(prospective_courses, by= c("rhs"="Course ID")) %>%
+  drop_na()
+```
 ###PF
 Note we need to take the d_transactions, not the transcripts! cause we need the columns item_PF
-```{r will take}
-AR$PF
-taken_redFlag <- AR$PF %>%
-  left_join(prospective_courses, by = c("lhs"="Course ID"))%>%
+```{r prospective red flag}
+prospective_RedFlag <- AR$PF %>%
+  left_join(prospective_courses, by = c("lhs"="item_PF"))%>%
   drop_na() %>%
@@
 ###HL
-```{r will take}
-AR$HL
+```{r expected low result}
+expect_low_result <- AR$HL  %>%
+  left_join(prospective_courses, by = c("lhs"="item_HL"))%>%
+  drop_na() %>%
+  group_by(rhs) %>%
+  mutate(RHS_vote= n())%>%
+  arrange(desc(RHS_vote))
 

### 2019-02-15 Baby Recommender.Rmd
SR recommendations

@@
 
+#CHECKING WHAT DATA SET TO USE
+```{r}
+(nrow(d_transcript)-nrow(d_transactions$taken_PF_HL))
+
+s.1 <- data.frame(`Student ID` = unique(d_transactions$taken_PF_HL$sequenceID), first = 1)
+s.2 <- data.frame(`Student ID` = unique(d_transcript$`Student ID`), first = 2)
+(nrow(s.1)-nrow(s.2))
+
+missing_students <- full_join(s.1,s.2, by = "Student.ID") %>% 
+  filter(is.na(first.x)) %>%
+  select(Student.ID)
+```
+
 #Setup
@@
 ```{r sample}
-
-student <- "6060984"
-
 students <- unique(d_transactions$taken_PF_HL$sequenceID)
@@
 )
+
 #
@@
 ```
+
 ###PF
-Note we need to take the d_transactions, not the transcripts! cause we need the columns item_PF
 ```{r prospective red flag}
@@
 ```
-
 ###HL
@@
   arrange(desc(RHS_vote))
+```
+
+##Matching sequences to students
+###Taken
+```{r will take}
+d_suggestions<- SR$taken %>%
+  left_join(sample_transcript, by = c("lhs"="item"))%>%
+  drop_na() %>%
+  group_by(rhs) %>%
+  mutate(RHS_vote= n())%>%
+  arrange(desc(RHS_vote))
+
+recommendations <- taken_match[1:5,] %>% select(rhs)
 
 ```
+####Check
+```{r evaluation}
+recommendations %>%
+  left_join(prospective_courses, by= c("rhs"="Course ID")) %>%
+  drop_na()
+```
+
+###PF
+```{r prospective red flag}
+d_prospective_RedFlag <- SR$PF %>%
+  left_join(prospective_courses, by = c("lhs"="item_PF"))%>%
+  drop_na() %>%
+  group_by(rhs) %>%
+  mutate(RHS_vote= n())%>%
+  arrange(desc(RHS_vote))
+
+d_prospective_RedFlag
+
+```
+###HL
+```{r expected low result}
+d_expect_low_result <- AR$HL  %>%
+  left_join(prospective_courses, by = c("lhs"="item_HL"))%>%
+  drop_na() %>%
+  group_by(rhs) %>%
+  mutate(RHS_vote= n())%>%
+  arrange(desc(RHS_vote))
+
+d_expect_low_result
+```

### 2019-02-15 Baby Recommender.Rmd
inspect missing studentes

@@
   filter(is.na(first.x)) %>%
-  select(Student.ID)
+  pull(Student.ID)
+
+View(d_transcript%>%
+  filter(`Student ID` %in% missing_students)) #students lost mostly only have external and core courses, there are a few internal courses missing: e.g. SSC1001
+
 ```

### 2019-02-15 Data Preparation.Rmd
clean students transcripts

@@
 ```{r}
+d_transcript <- d_transcript %>%
 
-d_transcript <- d_transcript %>%
+  # for simplicity, only keep courses of UCM program
+  filter(
+    `Program (Abbreviation)` == "7501",
+    !str_detect(`Module (Abbrev.)`, "EXT")
+    ) %>%
+
+  # folowing guidelines of Richard Vos, only consider: `Appraisal (Description)` == "Grade supervisor" and 
+  filter(
+    `Appraisal (Description)` == "Grade supervisor",
+    `Appraisal Type`          == "7055" # removes ~ 15 observations
+
+  ) %>%
 
@@
     function(x) mean(is.na(x)) < 0.99
+    ) %>%
+
+  # Select: Student ID, course ID, when course taken and grade 
+  select(
+    `Student ID` = `Student Number`,
+    `Course ID`  = `Module (Abbrev.)`,
+    `Academic Year`,
+    Period       = `Academic Session`,
+    Grade        = `Grade symbol`
+    ) %>%
+
+  # Clean grade variable
+  mutate(
+
+    Grade = case_when(
+      is.na(Grade)  ~ "0",
+      Grade == "NG" ~ "0",
+      TRUE          ~ str_replace(
+        Grade,
+        pattern     = ",",
+        replacement = "."
       )
+    ) %>% 
+      as.numeric
 
-d_transcript <- d_transcript %>%
+  ) %>%
 
-  # only keep one observation (with the final grade) per student-course
-  filter(
-    `Appraisal (Description)` == "Grade supervisor",
-    `Appraisal Type`=="7055"
-    ) %>%
-  select(`Student Number`,
-         `Module (Abbrev.)`,
-         `Module (Desc.)`,
-         `Program (Abbreviation)`,
-         `Grade symbol`,
-         `Academic Year`,
-         `Academic Session`,
-         `Number rep. attemp`) %>%
-  rename(`Student ID` = `Student Number`,
-         `Course ID` = `Module (Abbrev.)`,
-         `Course Title` = `Module (Desc.)`,
-         Grade = `Grade symbol`,
-         `Study Program` = `Program (Abbreviation)`,
-         Year_numerical = `Academic Year`,
-         Period = `Academic Session`,
-         `Number Repeated Attempt` = `Number rep. attemp`) %>%
-  distinct
-```
+  # if student took resit (recorder in same year and period), only keep failing grade
+  # group_by(
+  #   `Student ID`,
+  #   `Course ID`,
+  #   Year,
+  #   Period
+  #   ) %>%
+  # summarize(
+  #   Grade = min(Grade)
+  #   ) %>%
+  # ungroup %>%
 
-Each faculty had a different code for their calendars, we want to standardise them so we can compare.
-We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R.
-Vos) and save it under a variable `Period`.
-We also create another variable:
-```{r}
-d_transcript <- d_transcript %>%
-  mutate(Period = case_when(Period == 1   ~ "1 to 6"  ,
+  # Clean Time variables
+  mutate(
+
+    Period = case_when(
+      Period == 1   ~ "1 to 6"  ,
       Period == 2   ~ "1 to 3"  ,
       Period == 3   ~ "4 to 6"  ,
-                            Period == 680 ~ "5"     , # exception
-                            Period == 350 ~ "3 to 5", # exception
-                            Period == 403 ~ "4 to 5", # exception
-                            Period == 900 ~ "1 to 6", # exception
       between(Period, 100, 199) ~ "1",
@@
       between(Period, 500, 599) ~ "5",
-                            between(Period, 600, 660) ~ "6",
-                            between(Period, 901, 999) ~ "1")
-         ) %>%
-  mutate(`Academic Year`= paste(Year_numerical, Year_numerical + 1, sep = "-"))
-```
+      between(Period, 600, 660) ~ "6"
+      ),
 
-### Keeping UCM program only
+    time = paste(
+      `Academic Year`, substr(Period, 1, 1),
+      sep = ""
+      ),
 
-```{r}
-d_transcript <- d_transcript %>%
-  filter(`Study Program` == "7501") %>%
-  select(- `Study Program`)
-```
+    `Academic Year`= paste(
+      `Academic Year`, `Academic Year` + 1,
+      sep = "-")
 
-### Clean Grade Variable
-
-```{r clean grade variable}
-d_transcript <- d_transcript %>%
-  mutate(Grade = case_when(Grade == "NG" ~ "NA",
-                           TRUE          ~ Grade),
-         Grade = str_replace(string = Grade, pattern = ",",replace = "."),
-         Grade = as.numeric(Grade)) %>%
-  filter(!is.na(Grade)) %>%
-  mutate(Fail = Grade < 5.5)
+    )
 ```
@@
 ```
-
-# TODO
-
-## Estimating concentrations
-For our analysis we would also like to know what the concentration of each student is.
-However, this is not given, so we will have to estimate.
-We know that the maximimum amount of courses a student can take outside of their concentration is 2.
-Therefore, if any student has more than two courses in one concetration, this should count towards the concentration.
-We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration.
-However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided".
-Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"
-
-```{r, eval = FALSE}
-d_concentration <- d_course %>%
-  select(Code, Concentration, `Concentration (additional)`) %>%
-  gather(key = X, value = Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
-  select(Concentration, `Student ID Number`) %>%
-  count(Concentration, `Student ID Number`) %>%
-  spread(key = Concentration, value = n, fill = 0) %>%
-  mutate(n_course = HUM + SCI + SSC,
-         `Student Concentration` = case_when(
-           n_course < 20 ~ "not enough courses",
-           HUM > 5 & SSC > 5 & SCI > 5 ~ "confused",
-           HUM > 5 & SSC > 5           ~ "HUM/SCI",
-           HUM > 5                     ~ "HUM",
-                     SSC > 5 & SCI > 5 ~ "SSC/SCI",
-                     SSC > 5           ~ "SSC",
-                               SCI > 5 ~ "SCI"
-  ))
-
-  transmute(student_Concentration = case_when(
-    (HUM  >  2    &   SSC >  2   &  SCI <= 2) ~ "HUM/SSC",
-    (HUM  >  2    &   SSC <= 2   &  SCI >  2) ~ "HUM/SCI",
-    (HUM  >  2    &   SSC <= 2   &  SCI <= 2) ~ "HUM",
-    (HUM  <= 2    &   SSC >  2   &  SCI >  2)  ~ "SSC/SCI",
-    (HUM  <= 2    &   SSC >  2   &  SCI <= 2) ~ "SSC",
-    (HUM  <= 2    &   SSC <= 2   &  SCI >  2)  ~ "SCI",
-    (HUM  <  2    &   SSC <  2   &  SCI <  2) ~ "UNDECIDED",
-    (HUM  >  2    &   SSC >  2   &  SCI >  2) ~ "CONFUSED", #normal cases ^
-    (HUM > SCI    &   HUM > SSC)              ~ "HUM",
-    (SSC > SCI    &   SSC > HUM)              ~ "SSC",
-    (SCI > HUM    &   SCI > SSC)              ~ "HUM",
-    TRUE ~ "oops"
-  ))
-```
-
-Since we will need to check each student with an "oops" concentration to see what happened, lets separate this data for later:
-```{r, eval = FALSE}
-checkup <- filter(d_student_concentration, student_Concentration == "oops") 
-```
-
-###Getting UCM_YEAR
-In order to compare the trajectories of students, we would like to know if the courses were taken in their first, second, third, or whatever year.
-However, we only have the calendar years.
-Lets find out to what year of study each calendar year corresponds per student.
-
-First, lets find out, which year was a student's first year and which year was a student's last year (we will also create a variable `Subs_year` that we will substract later to transform from Calendar Year to UCM Year, and a second variable `LengthUCM` that shows us how many years each student stayed at the college):
-```{r, eval = FALSE}
-d_year <- d_grade %>%
-  select(ID, Code, Year, Period, Grade,`Booking Status Description`, `Course concentration`) %>%
-  group_by(ID) %>%
-  summarise(FirstYear=min(Year), LastYear=max(Year)) %>%
-  mutate(LengthUCM = LastYear-FirstYear, Subs_year=FirstYear-1)
-```
-
-Now, lets make a dataframe of students against years, where the year appears in the corresponding cell if a student was in the college at that time:
-
-```{r, eval = FALSE}
-d_year1 <- d_grade %>%
-  select(ID, Code, Year, Period, Grade, `Booking Status Description`, `Course concentration`) %>%  
-  group_by( ID, Year) %>%
-  summarise(Count = n())%>%
-  mutate(Present = case_when(Count > 0 ~ Year))%>%
-  select(-Count) %>%
-  spread(Year,Present, fill = 0)
-```
-
-Now we have collected all the years a student has been at the college in a single row (one row per student), and we also know what is the first and last year of each student.
-Let's join these dataframes:
-
-```{r, eval = FALSE}
-d_time <- left_join(d_year1, d_year)
-```
-
-Ideally, we would like to have a dataframe of students against calendar years filled with the corresponding UCM year (e.g.
-if the year 2017 was the first year of student 45, we would like to see the cell corresponding to student 45 and year 2017 marked with a "1").
-
-```{r, eval = FALSE}
-var_years <- as.character(2007:2017)
-d_time <- d_time %>% 
-  mutate_at(
-    vars(var_years),
-    funs(. - Subs_year)) %>%
-  mutate_at(
-    vars(var_years),
-    funs(case_when(. < 0 ~ 9999999999, #HORRIBLE FIX
-                   T     ~ .)))
-d_time[d_time == 9999999999] <- NA
-```
-
-Now, lets get the data as we want it for our analysis.
-For our analysis we would like to know what course a student took, when, whether they passed or failed, what grade they got, what the concentration of the student is, and what the concentration of the course is (we will convert grades to numeric here).
-Then, we would like to know on what year of their studies the student took the course.For this we will create a years dictionary and join it with our student data:
-
-```{r, eval = FALSE}
-d_students <- d_grade %>%
-  select(ID, Code, Year, Period, Grade, Attempt,`Booking Status Description`, `Course concentration`) %>%
-  arrange(ID, Year, Period)%>%
-  left_join(d_student_concentration, by="ID") %>%
-  mutate(Grade = as.numeric( sub(",",".", Grade))) %>%
-  replace_na(list(Grade=-1))
-# Years dictionary:
-year_dic <- d_time %>%
-  select(-FirstYear,-LastYear,-LengthUCM,-Subs_year)%>%
-  gather(Cal_Year,UCM_Year,var_years)%>%
-  drop_na(.) %>%
-  mutate(Year=as.integer(Cal_Year))%>%
-  select(-Cal_Year)
-#adding the ucm year to transcripts:
-d_students <- d_students %>%
-  left_join(year_dic, by=c("ID","Year"))
-#removing repeated values:
-d_students <- d_students[!duplicated(d_students),]
-```
-
-###Removing master Program data and Cleaning Capstone Data 
-We noticed that we had the data for people who stayed at this university for their masters. To filter these courses out we find out in which year people took their capstone courses.
-
-For this we keep only the capstones. We expect some people to have repeated capstones:
-```{r, eval = FALSE}
-capstone_count <- d_students %>%
-  filter(Code=="CAP3000") %>%
-  group_by(ID)%>%
-  summarise(Count=n())
-capstone_count
-```
-However, what is surptising is that some people have two different passed capstones:
-
-```{r, eval = FALSE}
-passed_capstone_count <- d_students %>%
-  filter(Code=="CAP3000", `Booking Status Description`=="Completed with Success") %>%
-  group_by(ID) %>%
-  summarise(Count=n(), Max = max(Grade), Min = min(Grade), Attempts= max(Attempt))
-```
-
-We can check the grades for people who had repeated passed capstones (lets just bring them to the top of the list):
-```{r, eval = FALSE}
-passed_capstone_count %>%
-  arrange(desc(Count), desc(Min), Attempts)
-```
-There are 1712 people who did capstone.
-We see that most students who have two passed Capstones, have in reality only 1, since the other capstone had a failing grade and the passing grade was on the second attempt (count starts at 0) was indeed failed.
-However there are two students who indeed have two different passed Capstones: one is student 282995 who has two different passing grades(because of a change in grading system at the collegue during the year 2008-2009), the other is student 544450 who has the same grade passed at two different moment in time.
-
-We can check if there are any students with passing capstone who do not have a grade of at least 5.5. We do this by looking at the lowest Max values:
-```{r, eval = FALSE}
-passed_capstone_count %>%
-  arrange(Max)
-```
-We see the lowest grade for a passing capstone is 5.6, so this is fine.
-
-Now lets just keep the highest value for each student and correct for student 282995:
-```{r, eval = FALSE}
-passed_capstone_grades <- passed_capstone_count %>%
-  mutate(`Booking Status Description`= "Completed with Success", Code="CAP3000", Grade= case_when(ID== 282995~7.7,
-                                                                                  T~Max)) %>%
-  select( ID, Code, Grade,`Booking Status Description`)
-passed_capstone_grades
-```
-
-####Capstone Year
-Now we can figure out the Capstone Year.
-
-First we get the years for which there is a corresponding passing capstone grade, and check for repetition:
-```{r, eval = FALSE}
-capstone_finish_year <- inner_join(passed_capstone_grades, d_students) 
-head(capstone_finish_year)
-count_before <- passed_capstone_grades %>%
-  group_by(ID) %>%
-  summarise(counts_of_id= n())
-count_after <- capstone_finish_year %>%
-  group_by(ID) %>%
-  summarise(counts_of_id= n())%>%
-  filter(counts_of_id > 1)  #these students have repeated capstones.
-count_after
-
-```
-From count_after we see that student 544450 has two passed capstones at different moments in time, we already knew this and we must ask Richard why this is the case.
-However, since both capstones where passed in 2010, this creates no problem for our current purposes.
-However, let's remove the later version.
-We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
-```{r, eval = FALSE}
-to_remove <- capstone_finish_year%>%
-  filter(ID==544450)
-to_remove <- to_remove[duplicated(to_remove$ID),]
-capstone_finish_year <- capstone_finish_year%>%
-  anti_join(to_remove) %>%
-  rename(`Capstone Year`= Year)%>%
-  select(ID,`Capstone Year`)
-
-capstone_finish_year
-```
-
-Lets create a dataframe where we include the capstone year.
-Then, if a course is given later than the capstone year, we want to remove it.
-Therefore, lets substitute na values with the year 9999 (or will ucm be open in the year 9999?).
-```{r, eval = FALSE}
-d_transcripts <- d_students %>%
-  group_by(ID) %>%
-  left_join(capstone_finish_year) %>%
-  ungroup() %>%
-  replace_na(list(`Capstone Year`=9999)) %>%
-  mutate(`After Graduation`=`Capstone Year`-`Year`)
-d_transcripts
-```
-Now we will remove all courses with negative `After Graduation`:
-```{r, eval = FALSE}
-master_courses <- d_transcripts%>%
-  filter(`After Graduation`<0)
-d_transcripts <- d_transcripts %>%
-  anti_join(master_courses)
-head(d_transcripts)
-```
-
-One last thing.
-The variable `Booking Status Description` shows whether a student passed or failed the course.
-However, some mistakes in the way the data was handled meant that the course status of some students was never confirmed.
-We need to ASK RICHARD, but for the moment, we will just look at the grades of those courses which were not confirmed to change into pass and fail.
-
-```{r, eval = FALSE}
-booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
-  mutate(`Booking Status Description`= case_when(Grade<5.5~"Completed Unsuccessfully",
-                                                 Grade>5.5~"Completed with Success"))
-clean_transcripts <- d_transcripts %>% 
-  left_join(booked, by= c("ID", "Code", "Year", "Period", "Grade", "Attempt", "Course concentration", "student_Concentration", "Capstone Year", "After Graduation"), suffix=c("-old", "-new"))%>%
-  select(-`After Graduation`)%>%
-  mutate(Pass= case_when(
-    (`Booking Status Description-new`=="Completed with Success")~"Pass",
-    (`Booking Status Description-new`=="Completed Unsuccessfully")~"Fail",
-    (`Booking Status Description-old`=="Completed with Success")~"Pass",
-    (`Booking Status Description-old`=="Completed Unsuccessfully")~"Fail",
-    T~"error in clean_transcripts"
-  )) %>%
-  select(-`Booking Status Description-new`,-`Booking Status Description-old`,-"UCM_Year-new")
-```
-####Ordering in Time
-We would like to have a column `Time` that codes for both year and period (e.g.
-Year_1 Period_2 should be 1.2), as well as a column `Periods` with the year and period as numbers (e.g.
-Year_2 Period_1 should be period 7).
-
-CHECK: we still have students who's first record is of their last year. This appears as UCM_Year=1.
-
-```{r, eval = FALSE}
-a_clean_transcripts <- clean_transcripts%>%
-  separate(Period, 
-           c("T1","T2","T3","T4","T5","T6"), 
-           sep="," 
-           ) %>%
-  gather( key = "Time", value = "Period", T1,T2,T3,T4,T5,T6) %>%
-  drop_na(Period) %>%
-  select(-Time) %>%
-  mutate(Periods = (`UCM_Year-old` - 1) * 6 + 
-           as.numeric(Period)
-         )
-
-a_clean_transcripts$Time= paste(a_clean_transcripts$`UCM_Year-old`,
-                                a_clean_transcripts$Period, 
-                                sep="."
-                                )
-#FINAL DATA:
-d_transcript <-a_clean_transcripts%>%
-  select(-`UCM_Year-old`,-Period)
-```
-NOTES: The data is now arranged so as to respect the order in time for each individual student.
-However, the comparison is still tricky as people who finished in 2008 will have CAP recorded as taken on their first year since this is all the data we have.
-COMMENT SOFIA: save a_clean_transcript as d_transcript
-
-[^1]: We do not include all assessments and all AoDs on the plots in order to keep them readable.
-
-[^2]: We are currently cleaning the dataset containing the transcripts of all the students of the college (alumni and current students) in order to integrate it to the analysis.

### 2019-02-15 other code.R

@@ -1,0 +1,255 @@
+# TODO
+
+## Estimating concentrations
+For our analysis we would also like to know what the concentration of each student is. However, this is not given, so we will have to estimate. We know that the maximimum amount of courses a student can take outside of their concentration is 2. Therefore, if any student has more than two courses in one concetration, this should count towards the concentration. We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration. However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided". Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops" 
+
+```{r, eval = FALSE}
+d_concentration <- d_course %>%
+  select(Code, Concentration, `Concentration (additional)`) %>%
+  gather(key = X, value = Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
+  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
+  select(Concentration, `Student ID Number`) %>%
+  count(Concentration, `Student ID Number`) %>%
+  spread(key = Concentration, value = n, fill = 0) %>%
+  mutate(n_course = HUM + SCI + SSC,
+         `Student Concentration` = case_when(
+           n_course < 20 ~ "not enough courses",
+           HUM > 5 & SSC > 5 & SCI > 5 ~ "confused",
+           HUM > 5 & SSC > 5           ~ "HUM/SCI",
+           HUM > 5                     ~ "HUM",
+           SSC > 5 & SCI > 5 ~ "SSC/SCI",
+           SSC > 5           ~ "SSC",
+           SCI > 5 ~ "SCI"
+         ))
+
+transmute(student_Concentration = case_when(
+  (HUM  >  2    &   SSC >  2   &  SCI <= 2) ~ "HUM/SSC",
+  (HUM  >  2    &   SSC <= 2   &  SCI >  2) ~ "HUM/SCI",
+  (HUM  >  2    &   SSC <= 2   &  SCI <= 2) ~ "HUM",
+  (HUM  <= 2    &   SSC >  2   &  SCI >  2)  ~ "SSC/SCI",
+  (HUM  <= 2    &   SSC >  2   &  SCI <= 2) ~ "SSC",
[…]

### 2019-02-15 Pillar 2 - Topic Modeling.Rmd
save cached results in folder `Cache`
find ideal # topics for topic model

@@
 
-## Ideal Number of Topics (RUN ON UM COMPUTER)
-
-```{r LDA number topics, eval = FALSE}
-
-my_control <- list(
-
-  nstart = 10,
-  seed   = 1 : 10,
-  best   = TRUE,
-
-  burnin = 500
-  iter   = 2000,
-  thin   = 100
-
-)
-
-result <- FindTopicsNumber(
-
-  d_description_cast,
-  topics = seq(from = 20, to = 150, by = 5),
-  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
-  method = "Gibbs",
-  control = my_control,
-  mc.cores = 1L
-
-)
-
-save(result,
-     file = "LDA_ntopics.RDATA")
-```
-
-```{r LDA number topics plot}
-load("LDA_ntopics.RDATA")
-FindTopicsNumber_plot(result)
-```
-
-## Fitting Model
 ```{r my_cast_tdm}
@@
 ```
+
+## Ideal Number of Topics (RUN ON UM COMPUTER)
+
+```{r}
+my_control <- list(
+
+  nstart = 10,
+  seed   = 1 : 10,
+  best   = TRUE,
+
+  burnin = 500,
+  iter   = 2000,
+  thin   = 100
+
+)
+```
+
+```{r}
+my_FindTopicsNumber <- function(data_cast, n_topics){
+
+  FindTopicsNumber(
+
+  dtm = data_cast,
+  topics = n_topics,
+  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  method = "Gibbs",
+  control = my_control,
+  mc.cores = 1L
+
+  )
+
+}
+```
+
+```{r}
+start.time <- Sys.time()
+
+result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+save(result_descrition,
+     file = "Output/LDA_ntopics_description.RDATA")
+
+print(time.taken)
+```
+
+```{r}
+start.time <- Sys.time()
+
+result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+save(result_overview ,
+     file = "Output/LDA_ntopics_overview.RDATA")
+
+print(time.taken)
+```
+
+```{r, eval = F}
+start.time <- Sys.time()
+
+result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+save(result_manual,
+     file = "Output/LDA_ntopics_manual.RDATA")
+
+print(time.taken)
+```
+
+from 20, to 40, by 5 topics takes
+22min for overview
+11min for description
+5.5hrs for manuals
+
+```{r LDA number topics plot}
+
+load("Output/LDA_ntopics_description.RDATA")
+
+load("Output/LDA_ntopics_overview.RDATA")
+
+load("Output/LDA_ntopics_manual.RDATA")
+
+result_descrition %>%
+  select(-Griffiths2004) %>%
+  FindTopicsNumber_plot
+
+result_overview %>%
+  select(-Griffiths2004) %>%
+  FindTopicsNumber_plot
+
+result_manual %>%
+  select(-Griffiths2004) %>%
+  FindTopicsNumber_plot
+
+```
+
+## Fitting Model
 
@@
 ### Functions
-```{r LDA prepare}
+```{r LDA prepare, eval = F}
 prepare_data_LDA_beta <- function(results){
@@
 
-```{r LDA visualize}
+```{r LDA visualize, eval = F}
 visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
@@
 
-```{r LDA visualize all distrib}
+```{r LDA visualize all distrib, eval = F}
 visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){
@@
 
-```{r LDA visualize all level}
+```{r LDA visualize all level, eval = F}
 visualize_LDA_all_level <- function(data, id_plot = "test"){
@@
 ### Plots
-```{r LDA plot, cache = TRUE}
+```{r LDA plot, cache = TRUE, eval = F}
 load("LDA.RDATA")
@@
 
-```{r label, eval = FALSE}
+```{r label, eval = FALSE, eval = F}
 tidy(LDA_manual_10, "beta") %>%

### 2019-02-15 Pillar 1 - Sequential Pattern Mining.Rmd
save cached results in folder `Cache`

@@
 
+```{r setup, include = T}
+knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
+```
+
 ```{r library, message = FALSE, warning = FALSE}
@@
 ```
-
+####Save d_transactions
+```{r save d_transaction}
+save(
+  d_transactions,
+  file = "Output/transaction_df.RDATA"
+  )
+```
 ### Transcript with preceding courses (for SR by hand)

### 2019-02-15 trial transcript exploration.R
delete EDA

@@ -1,94 +1,0 @@
-d_transcript %>%
-  count(`Student Number`, sort = TRUE)
-
-d_transcript %>%
-  count(`Module (Abbrev.)`, sort = TRUE)
-
-d_transcript %>%
-  count(`Module (Desc.)`, sort = TRUE)
-
-d_transcript %>%
-  count(`Program (Abbreviation)`, sort = TRUE) # looks like UCM is 7501
-
-d_transcript %>%
-  count(`Program (Description)`, sort = TRUE) # counts match
-
-d_transcript %>%
-  count(`Academic Year`) # 2007 - increase - 2009 - decrease - 2013 - increase - 2017
-
-d_transcript %>%
-  count(`Academic Session`, sort = TRUE) # decrease from 100 to 200 and from 400 to 500 caused by drop out?
-
-d_transcript %>%
-  count(`Appraisal Type`, sort = TRUE) # there are five main appraisal types (7055, 10, 7050, 7005, 7000)
-
-d_transcript %>%
-  count(`Appraisal (Description)`, sort = TRUE) # also five main appraisal description, but the counts do not match
-
-d_transcript %>%
-  count(`Number rep. attemp`)
-
-x <- d_transcript %>%
-  count(`Grade symbol`) # there are grades superior to 10
-
-d_transcript %>%
-  count(`Appraisal date`, sort = TRUE) # are these dates deadlines for grade submition?
-
-d_transcript %>%
-  count(`Attempted credits`, sort = TRUE) # mostly 0. Surprising.
-
-d_transcript %>%
-  count(`Earned Credits`, sort = TRUE) # mostly 0. Surprising.
-
-d_transcript %>%
-  count(`Individual Work`, sort = TRUE) # mostly NA
-
-d_transcript %>%
-  count(`Academic Work ID`, sort = TRUE) # unique id for each student-course combination
-
-d_transcript %>%
-  count(`Booking Status (Desc.)`) # what is booked?
-
-d_transcript %>%
-  count(`Object ID`, sort = TRUE) # moslty 0
-
-d_transcript %>%
-  count(`Appraiser ID`, sort = TRUE) 
-
-d_transcript %>%
-  count(`Appraiser Name`, sort = TRUE) # counts match
-
-
-
-
-# Remark 1: course code are unique, course title are not
-d_transcript %>%
-  distinct(
-    `Module (Abbrev.)`,
-    `Module (Desc.)`
-  ) %>%
[…]

### 2019-02-15 Data Preparation.Rmd
minor change

@@
     ),
+
   read_csv(
@@
     )
+
   )
@@
 
-### Selecting Variables
-
 Our dataframe contains many variables and rows that are either empty or meaningless for our analysis.
@@
 
-  # folowing guidelines of Richard Vos, only consider: `Appraisal (Description)` == "Grade supervisor" and 
+  # folowing guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type`          == "7055"
   filter(
@@
     `Appraisal Type`          == "7055" # removes ~ 15 observations
-
   ) %>%

### 2019-02-15 Data Preparation.Rmd
debug

@@
     `Course ID`    = `Module (Abbrev.)`,
-    `Academic Year`,
+    Year_numerical =`Academic Year`,
     Period         = `Academic Session`,
@@
     time = paste(
-      `Academic Year`, substr(Period, 1, 1),
+      Year_numerical, substr(Period, 1, 1),
       sep = ""
@@
     `Academic Year`= paste(
-      `Academic Year`, `Academic Year` + 1,
+      Year_numerical, Year_numerical + 1,
       sep = "-")

### 2019-02-18 App/server.R
test

@@ -1,4 +1,4 @@
-
+#test
 
 #
 # Setup

### 2019-02-18 App/server.R
test close

@@ -1,4 +1,4 @@
-#test
+
 
 #
 # Setup

### 2019-02-18 Baby Recommender.Rmd
rearranges sections, expands to all students

@@
   ) %>%
-  select(-`Period (additional)`, -`Period (additional bis)`, -`Concentration (additional)`)
+  select(-`Period (additional)`, -`Period (additional bis)`, -`Concentration (additional)`) %>%
+  select(sequenceID, eventID, item, item_PF, item_HL, Grade)
+
+#c("Course ID", "Course Title.x", "Cluster", "n_ILO", "n_assessment", "Assessments Covered", "n_AoD", "AoD Covered", "Concentration", "Missing from ILO File", "Most Recent Catalogue", "Type", "Letters", "Number", "Level", "sequenceID", "Course Title.y", "Grade", "Year_numerical", "Period", "Number Repeated Attempt", "Academic Year", "Fail", "eventID", "PF", "HL", "item", "item_PF", "item_HL")
 
@@
 
-For a single student:
+For all students
 ```{r truncated transcript}
 
-course_sample_size <- 5
-
-student <- "6036972"
-
-student_transcript <- target_transcript %>% 
-    filter(sequenceID == student) %>%
-  arrange(Year_numerical, Period)
-
-length_student_transcript <- nrow(student_transcript)
+course_sample_size <- 8
 
 #
+##Truncated prospective transcript
+prospective_transcript <-target_transcript %>% 
+  group_by(sequenceID) %>%
+  top_n(course_sample_size, eventID)
+#
 ##Truncated student transcript
-sample_transcript      <- student_transcript[1:course_sample_size,]
-prospective_courses <- student_transcript[(course_sample_size+1):(course_sample_size+2),] #%>% 
-  #select(sequenceID, `Course ID`)
+sample_transcript <- prospective_transcript %>% 
+  group_by(sequenceID) %>%
+  top_n(5, eventID) %>%
+  arrange(sequenceID)
+
+#
+##Only prospective courses
+prospective_transcript <- prospective_transcript %>%
+  anti_join(sample_transcript, by = c("sequenceID", "eventID", "item", "item_PF", "item_HL", "Grade"))  %>%
+  arrange(sequenceID)
+
 ```
 
+# TO DO: basic- doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
 ##Matching rules to students:
@@
 ```{r will take}
+# very basic, doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
 taken_match <- AR$taken %>%
-  left_join(sample_transcript, by = c("lhs"="item"))%>%
+  full_join(sample_transcript, by = c("lhs"="item"))%>%
   drop_na() %>%
-  group_by(rhs) %>%
-  mutate(RHS_vote= n())%>%
-  arrange(desc(RHS_vote))
+  group_by(sequenceID, rhs) %>%
+  summarise(RHS_vote= n())  %>%
+  arrange(sequenceID,desc(RHS_vote))
 
-recommendations <- taken_match[1:5,] %>% select(rhs)
+recommendations <- taken_match %>%
+  group_by(sequenceID)         %>%
+  filter(row_number(RHS_vote) %in% 1:3) %>% #can use top_n
+  arrange(sequenceID)          %>%
+  select(sequenceID, RHS_vote, everything())
+
+recommendations
 
@@
 recommendations %>%
-  left_join(prospective_courses, by= c("rhs"="Course ID")) %>%
+  full_join(prospective_transcript, 
+            by= c("sequenceID"="sequenceID","rhs"="item")
+            ) %>% # this should not be left join.
   drop_na()
@@
 ```
+
+TEST: For a single student:
+```{r truncated transcript}
+
+course_sample_size <- 5
+
+student <- "6036972"
+
+student_transcript <- target_transcript %>% 
+    filter(sequenceID == student) %>%
+  arrange(Year_numerical, Period)
+
+length_student_transcript <- nrow(student_transcript)
+
+#
+##Truncated student transcript
+sample_transcript      <- student_transcript[1:course_sample_size,]
+prospective_courses <- student_transcript[(course_sample_size+1):(course_sample_size+2),] #%>% 
+  #select(sequenceID, `Course ID`)
+```

### 2019-02-18 Pillar 1 - Sequential Pattern Mining.Rmd

@@
   data %>%
+
+    mutate(
+      Grade = case_when(
+        Grade >= 5.5 ~ Grade,
+        T            ~ as.numeric(NA)
+        )
+      ) %>%
+
     filter(
@@
       Count           = n(),
-      Min             = min(Grade),
-      Max             = max(Grade),
-      Mean            = mean(Grade),
-      Median          = median(Grade),
-      IQR             = IQR(Grade),
-      SD              = sd(Grade),
-      `Low Rate`      = mean(Grade < high_grade),
-      `Fail Rate`     = mean(Grade < pass_grade)
+      Min             = min(Grade, na.rm = TRUE),
+      Max             = max(Grade, na.rm = TRUE),
+      Mean            = mean(Grade, na.rm = TRUE),
+      Median          = median(Grade, na.rm = TRUE),
+      IQR             = IQR(Grade, na.rm = TRUE),
+      SD              = sd(Grade, na.rm = TRUE),
+      `Low Rate`      = mean(is.na(Grade) | Grade < high_grade),
+      `Fail Rate`     = mean(is.na(Grade))
       ) %>%
@@
     mutate_at(
-      vars(Mean, SD, `Low Rate`, `Fail Rate`),
+      vars(Mean, SD, `Low Rate`, `Fail Rate`, IQR),
       round,
@@
 
+For convenience:
 ```{r for convenience II}
@@
     grade_ceil = ceiling(Grade),
-    Values     = TRUE
+    Values     = TRUE,
+    id         = 1 : n() # to ensure each row is unique
     ) %>%

### 2019-02-18 Baby Recommender.Rmd

@@
 ```
+
+#TO DO: prepare variables at begining
 
@@
 ```{r will take}
-# very basic, doesn't look at confidence or lift, we need to do the filtering for meaningful rules first. Exclude taken already from the rhs.
+# very basic, doesn't look at confidence or lift:
+#(*) Do the filtering for meaningful rules first. 
+#(**)Exclude taken already from the rhs.
 taken_match <- AR$taken %>%
+  #DO FILTERING FOR MEANINGFUL RULES HERE
   full_join(sample_transcript, by = c("lhs"="item"))%>%
-  drop_na() %>%
+  select(sequenceID, lhs, rhs) %>%
+  drop_na() %>% #we lose 20 courses here -->20 rules or students are not matched with the transcripts
   group_by(sequenceID, rhs) %>%
@@
   group_by(sequenceID)         %>%
-  filter(row_number(RHS_vote) %in% 1:3) %>% #can use top_n
+  filter(row_number() %in% 1:3) %>% #can use top_n
   arrange(sequenceID)          %>%
@@
             by= c("sequenceID"="sequenceID","rhs"="item")
-            ) %>% # this should not be left join.
+            ) %>%
   drop_na()
@@
   left_join(prospective_courses, by = c("lhs"="item_PF"))%>%
-  drop_na() %>%
+  select(sequenceID, lhs, rhs) %>%
+  drop_na() %>% #we eliminate rules that don't match students
   group_by(rhs) %>%
@@
 
+prospective_RedFlag
 ```
@@
   left_join(prospective_courses, by = c("lhs"="item_HL"))%>%
-  drop_na() %>%
+  select(sequenceID, lhs, rhs) %>%
+  drop_na() %>% #we eliminate rules that don't match students
   group_by(rhs) %>%
@@
   arrange(desc(RHS_vote))
+
+expect_low_result
 ```
 
+###
+```{r merging all}
+#
+#setup: cleaning before merge
+RedFlag <- prospective_RedFlag %>%
+  select(sequenceID,lhs, rhs) %>%
+  separate(rhs, into = c("prospective_item","expected_PF") ) %>%
+  mutate(transcript_type = "RedFlag",
+         Precedent_PF= lhs)%>%
+  select(-lhs)
+
+Low_Results <- expect_low_result %>%
+  select(sequenceID,lhs, rhs) %>%
+  separate(rhs, into = c("prospective_item","expected_HL") ) %>%
+  mutate(transcript_type = "LowResults" ,
+          Precedent_HL= lhs)%>%
+  select(-lhs)
+
+prosp_transcript <- prospective_transcript %>%
+  select(sequenceID, item) %>%
+  mutate(transcript_type = "StudentChoice" )
+
+#
+#Join
+recommender <- recommendations %>%
+  mutate(transcript_type ="Recommendations" #,
+         #Reason = paste("votes = ", RHS_vote, sep = "") #this should be moved to the end and be calculated with a case_when
+         ) %>% 
+  full_join(prosp_transcript, by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "item") )             %>%
+  full_join(RedFlag,          by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "prospective_item") ) %>%
+  full_join(Low_Results,      by = c("sequenceID" = "sequenceID", "transcript_type" = "transcript_type", "rhs" = "prospective_item") ) %>%
+  mutate(Reason = case_when(
+   transcript_type=="Recommendations"~ RHS_vote,
+   transcript_type=="RedFlag"        ~ expected_PF,
+   transcript_type=="LowResults"     ~ expencted_,
+   transcript_type=="StudentChoice"
+  ))
+
+```
 ##Matching sequences to students

### 2019-02-18 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 
-```{r setup, include = T}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
@@
 ```{r edit_rules}
-edit_rules <- function(rules){
+filter_rules <- function(rules){
 
@@
       count >= 10
-      ) %>%
-
-    mutate_if(
-      is.numeric,
-      funs(round(., 5))
-    ) %>%
-
-    select(
-      lhs       , rhs,
-      support   , count,
-      confidence, rhs.support,
-      lift,
-      matches("rhsTake")
-    ) %>%
-
-    arrange(
-      desc(count)
       )
@@
   X   = AR,
-  FUN = edit_rules
+  FUN = filter_rules
   )
@@
   X   = SR,
-  FUN = edit_rules
+  FUN = filter_rules
   )
@@
   AR, SR,
-  file = "App/rules.RDATA"
-  )
-```
+  file = "App/rules/rules.RDATA"
+  )
+```

### 2019-02-18 App/Recommender System/server.R
replace fake student with actual student (student id)

@@ -2,31 +2,52 @@ function(input, output) {
   
   output$red_flags <- renderUI({
     
-    n_course <- 25
     
     student <- list(
       
-      # transcript: tibble with course and grade
-      transcript = tibble(
-        
-        course = sample(
-          x       = course_all,
-          size    = n_course,
-          replace = FALSE
-        ),
-        
-        grade = rnorm(
-          n    = n_course,
-          mean = 5,
-          sd   = 2
-        )
-        
-      ),
-      
+      # transcript of student: tibble with course and grade
+      transcript = d_transcript %>%
+        filter(
+          `Student ID` == input$student
+          ) %>%
+        select(
+          course = `Course ID`,
+          grade  = Grade
+          ),
+
       # interest of student (to be used with topic model)
       interest = c("key", "words", "related", "to", "topics")
       
     )
+
+    
+    
+    # # fake student
+    # n_course <- 25
+    # 
+    # student <- list(
+    #   
+    #   # transcript: tibble with course and grade
+    #   transcript = tibble(
+    #     
+    #     course = sample(
+    #       x       = course_all,
+    #       size    = n_course,
+    #       replace = FALSE
+    #     ),
+    #     
+    #     grade = rnorm(
+    #       n    = n_course,
+    #       mean = 5,
+    #       sd   = 2
+    #     )
+    #     
+    #   ),
+    #   
+    #   # interest of student (to be used with topic model)
+    #   interest = c("key", "words", "related", "to", "topics")
+    #   
+    # )
     
     
     course_low <-  student$transcript %>%
@@ -62,15 +83,15 @@ function(input, output) {
           ":<br/>",
           "You obtained less than 6.5/10 in ",
           lhs_course,
-          "and ",
+          " and ",
           round(confidence * 100, digits = 1),
           "% of the ",
           lhs.rhsTake.count,
           " students who have taken ", 
           rhs_course,
-          "after obtaining a similar grade in ",
+          " after obtaining a similar grade in ",
           lhs_course,
-          "did not do well in ",
+          " did not do well in ",
           rhs_course,
           ".",
           sep = ""

### 2019-02-18 Pillar_2_-_Topic_Modeling.Rmd

--- 2019-02-15 Pillar 2 - Topic Modeling.Rmd
@@
 ---
+
+```{r setup, include = T}
+knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
+```
 
@@
 
-```{r}
+```{r controls}
 my_control <- list(
@@
 
-```{r}
+```{r function my_FindTopicsNumber }
 my_FindTopicsNumber <- function(data_cast, n_topics){
@@
 
-```{r}
+```{r description topics, cache = TRUE}
 start.time <- Sys.time()
@@
 
-save(result_descrition,
+save(result_description,
      file = "Output/LDA_ntopics_description.RDATA")
@@
 
-```{r}
+```{r overview topics, cache = TRUE}
 start.time <- Sys.time()
@@
 
-```{r, eval = F}
+```{r manual topics, cache = TRUE}
 start.time <- Sys.time()
@@
 
-result_descrition %>%
+result_description %>%
   select(-Griffiths2004) %>%

### 2019-02-18 Topic Scores.Rmd

---
title: "Topic Scores"
author: "DARS"
date: "2/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
load("Output/LDA.RDATA")
load("Output/data_pillar_1.RDATA")
load("Output/LDA_overview_5.RDATA")
```

## function get gamma and beta
```{r getting functions}
get_beta <- function(results){

  tidy(results, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
      arrange(topic, desc(beta))

}

get_gamma <- function(results){

  tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
      arrange(topic, desc(gamma))

}

```
##getting gamma and beta data 
```{r getting beta and gamma}
beta_descriptions <- LDA_overview_5 %>%
  get_beta

gamma_descriptions <- LDA_overview_5 %>%
  get_gamma
```

## simulating students and key words
```{r student simulation}
set.seed(126)

terms <- unique(beta_descriptions$term)

student <- list()
student$kw <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
```

##getting top courses per student
```{r topic score student}
student$topic_score <- beta_descriptions%>%
  filter(term %in% student$kw) %>%
  group_by(topic)%>% #maybe we can do this with transcripts afterwards
  summarize(B_score= sum(beta))%>%
  ungroup()%>%
  mutate(Total_b      = sum(B_score),
         B_proportion = B_score/Total_b) %>%
  arrange(desc(B_score))

```

##Getting courses
```{r course_score}

student$course_score <- gamma_descriptions     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )

student$course_score
```
###Other comparison functions
```{r other functions}
#
##Binary

```
### Comparing results
```{r}
bla %>%
  mutate(no= row_number())

b <- gamma_descriptions %>%
  full_join(student$topic_score, by="topic") %>%
  mutate(X = gamma*Beta_score) %>%
  arrange(desc(X))%>%
  mutate(no= row_number())

a %>% full_join(b, by="no") %>%
  mutate(equal= case_when(document.x==document.y~T,
                          T~F))
```

### 2019-02-19 Topic Scores.Rmd
comments

@@
 ---
+#Set up
+##Libraries
+```{r libraries}
+```
+##Raw Data
+```{r setup, include=FALSE}
+#
+##d_course and d_transcript
+load("Output/data_pillar_1.RDATA")
 
-```{r setup, include=FALSE}
-load("Output/LDA.RDATA")
-load("Output/data_pillar_1.RDATA")
-load("Output/LDA_overview_5.RDATA")
+#
+##LDA_models
+load("Output/LDA_overview.RDATA")
+
+#
+##Topic Models test for ideal number of topics
+load("Output/LDA_ntopics_description.RDATA")
+load("Output/LDA_ntopics_overview.RDATA")
+
 ```
 
-## function get gamma and beta
+## Getting Functions (gamma and beta) 
 ```{r getting functions}
@@
 ```
-##getting gamma and beta data 
+
+##Getting applied (gamma and beta) 
 ```{r getting beta and gamma}
-beta_descriptions <- LDA_overview_5 %>%
+beta_descriptions <- LDA_model %>%
   get_beta
 
-gamma_descriptions <- LDA_overview_5 %>%
+gamma_descriptions <- LDA_model %>%
   get_gamma
@@
 ```{r student simulation}
-set.seed(126)
-
 terms <- unique(beta_descriptions$term)
@@
 student <- list()
-student$kw <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
+student$kw_policy <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
+student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
 ```
@@
 student$topic_score <- beta_descriptions%>%
-  filter(term %in% student$kw) %>%
+  filter(term %in% student$kw_climate) %>%
   group_by(topic)%>% #maybe we can do this with transcripts afterwards
@@
 
-student$course_score
+View(student$course_score)
 ```
@@
 ##Binary
+product <- function(a = gamma, b = B_score){
+  X = a*b
+}
 

### 2019-02-19 Topic Scores.Rmd
course content recommendations based on key words

@@
 ```{r getting beta and gamma}
-beta_descriptions <- LDA_model %>%
+# k=10, 20, 35
+beta_description <- lapply(
+  LDA_model,
   get_beta
+)
 
-gamma_descriptions <- LDA_model %>%
+gamma_descriptions <- lapply(
+  LDA_model,
   get_gamma
+)
+
 ```
+##Inspect topics
+```{r inspect topics}
+topics <- beta_description$k35 %>%
+  group_by(topic) %>%
+  top_n(10, beta)
 
+#
+##View
+View(topics)
+
+```
 ## simulating students and key words
 ```{r student simulation}
-terms <- unique(beta_descriptions$term)
+terms <- unique(beta_description$k35$term)
 
 student <- list()
-student$kw_policy <- c("international", "economic", "conflict", "develop", "policy") #sample(terms, 5)
+student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war") #sample(terms, 5)
 student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
@@
 ```{r topic score student}
-student$topic_score <- beta_descriptions%>%
-  filter(term %in% student$kw_climate) %>%
+student$topic_score <- beta_description$k35%>%
+  filter(term %in% student$kw_policy) %>%
   group_by(topic)%>% #maybe we can do this with transcripts afterwards
@@
 
-student$course_score <- gamma_descriptions     %>%
+student$course_score <- gamma_descriptions$k35     %>%
   full_join(student$topic_score, by = "topic") %>%
@@
     )
-
+```
+###View
+```{r View course}
+View(student$topic_score)
 View(student$course_score)

### 2019-02-19 Topic Scores.Rmd
cuts rough code

@@
 ```
-###Other comparison functions
-```{r other functions}
-#
-##Binary
-product <- function(a = gamma, b = B_score){
-  X = a*b
-}
-
-```
-### Comparing results
-```{r}
-bla %>%
-  mutate(no= row_number())
-
-b <- gamma_descriptions %>%
-  full_join(student$topic_score, by="topic") %>%
-  mutate(X = gamma*Beta_score) %>%
-  arrange(desc(X))%>%
-  mutate(no= row_number())
-
-a %>% full_join(b, by="no") %>%
-  mutate(equal= case_when(document.x==document.y~T,
-                          T~F))
-```

### 2019-02-19 App/Recommender System/server.R
print a message if no red flag

@@ -1,3 +1,6 @@
+library(tidyverse)
+library(stringr)
+
 function(input, output) {
   
   output$red_flags <- renderUI({
@@ -97,17 +100,26 @@ function(input, output) {
           sep = ""
         )
         
-      ) %>%
+      )
+    
+    if(nrow(red_flags) == 0){
       
-      pull %>%
+      "No red flag"
       
-      sort %>% 
+    }else{
       
-      paste0(
-        collapse = "<br/><br/>"
+      red_flags  %>%
+        
+        pull %>%
+        
+        sort %>% 
+        
+        paste0(
+          collapse = "<br/><br/>"
         ) %>% 
-      
-      HTML
+        
+        HTML
+    }
     
     
   })

### 2019-02-19 App/Recommender System/ui.R
provide key words

@@ -4,9 +4,11 @@
 
 # libraries
 library(tidyverse)
+library(tidytext)
 library(shiny)
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
+load("LDA_overview.RDATA")
 
 # set seed
 set.seed(1)
@@ -31,22 +33,6 @@ course_following_semester <- sample(
   size    = 60,
   replace = FALSE
   ) %>% sort
-
-pass_grade <- 5.5
-high_grade <- 6.5
-
-# 
-augment_student_transcript <- function(transcript){
-  
-  transcript %>%
-    
-    mutate(
-      fail       = grade < pass_grade,
-      low        = grade < high_grade,
-      grade_ceil = ceiling(grade)
-    )
-  
-}
 
 
 
@@ -115,7 +101,12 @@ navbarPage(
         checkboxGroupInput(
           inputId  = "key_words",
           label    = "Academic Interest",
-          choices  = c("List", "of", "Key", "Words"),
+          choices  = c(
+            "climate", "sustainability", "change", "development", "develop","sustain", "sustainable",
+            "//",
+            "international", "economic", "conflict", "develop", "policy", "war"
+            ),
+          selected = c("international", "economic", "conflict", "develop", "policy", "war"),
           inline   = TRUE
           ),
         
@@ -141,7 +132,7 @@ navbarPage(
           label   = "Additional Key Word 5"
           )
         
-      ),
+        ),
       
       # Main panel for displaying outputs
       mainPanel(
@@ -149,12 +140,12 @@ navbarPage(
         # Output: dataset
         htmlOutput(
           outputId = "course_recommendation"
-        )
+          )
         
-      )
+        )
       
-    )
+      )
     
-  )
+    )
   
   )

### 2019-02-19 App/Recommender System/server.R
re-locate functions to server

@@ -1,10 +1,31 @@
 library(tidyverse)
+library(tidytext)
 library(stringr)
+
+load("rules.RDATA")
+load("data_pillar_1.RDATA")
+load("LDA_overview.RDATA")
+
+
 
 function(input, output) {
   
   output$red_flags <- renderUI({
     
+    pass_grade <- 5.5
+    high_grade <- 6.5
+    
+    augment_student_transcript <- function(transcript){
+      
+      transcript %>%
+        
+        mutate(
+          fail       = grade < pass_grade,
+          low        = grade < high_grade,
+          grade_ceil = ceiling(grade)
+        )
+      
+    }
     
     student <- list(
       
@@ -120,6 +141,114 @@ function(input, output) {
         
         HTML
     }
+    
+    
+  })
+  
+  output$course_recommendation <- renderUI({
+    
+    
+    #
+    # Set up
+    get_beta <- function(results){
+      
+      tidytext::tidy(results, matrix = "beta") %>%
+        mutate(topic = paste("Topic", topic)) %>%
+        arrange(topic, desc(beta))
+      
+    }
+    
+    get_gamma <- function(results){
+      
+      tidytext::tidy(results, matrix = "gamma") %>%
+        mutate(topic = paste("Topic", topic)) %>%
+        arrange(topic, desc(gamma))
+      
+    }
+    
+    beta_description <- lapply(
+      LDA_model,
+      get_beta
+      )
+    
+    gamma_descriptions <- lapply(
+      LDA_model,
+      get_gamma
+      )
+    
+    key_words <- c(
+      input$key_words,
+      input$key_word_1,
+      input$key_word_2,
+      input$key_word_3,
+      input$key_word_4,
+      input$key_word_5
+      )
+    
+    
+    #
+    # Topic Score
+    student$topic_score <- beta_description$k35 %>%
+      filter(
+        term %in% key_words
+        ) %>%
+      group_by(
+        topic
+        )%>% #maybe we can do this with transcripts afterwards
+      summarize(
+        topic_score = sum(beta)
+        )%>%
+      ungroup() %>%
+      mutate(topic_score_proportion = topic_score / sum(topic_score))
+    
+    
+    #
+    # Course Score
+    student$course_score <- gamma_descriptions$k35 %>%
+      full_join(
+        student$topic_score,
+        by = "topic"
+        ) %>%
+      group_by(
+        document
+        ) %>%
+      summarise(
+        course_score = sum(gamma * B_proportion)
[…]

### 2019-02-19 test_delete_later_sofia.Rmd

--- 2019-02-19 Topic Scores.Rmd
@@
 ```{r libraries}
+library(tidyverse)
 ```
@@
 ```{r topic score student}
-student$topic_score <- beta_description$k35%>%
+standardize <- function (col) {
+  col/sum(col)
+}
+
+#
+##key word Contributions to Topic
+ contribution_to_topics <- beta_description$k35                       %>%
   filter(term %in% student$kw_policy)       %>%
-  group_by(topic)%>% #maybe we can do this with transcripts afterwards
-  summarize(B_score= sum(beta))%>%
-  ungroup()%>%
-  mutate(Total_b      = sum(B_score),
-         B_proportion = B_score/Total_b) %>%
-  arrange(desc(B_score))
+  arrange(topic, desc(beta))                %>%
+  spread(key=topic, value=beta)             %>%
+  mutate_at(.vars = vars(num_range("Topic ",1:35)),
+            .funs = standardize)
 
@@
 
-##Getting courses
+##Topic contribution to course
 ```{r course_score}
 
-student$course_score <- gamma_descriptions$k35     %>%
+#
+## Topic contribution to course
+gamma_descriptions$k35     %>%
   full_join(student$topic_score, by = "topic") %>%
+  group_by(document, topic)                           %>%
+  summarise(total_gamma= sum(gamma))
   mutate(X = gamma * B_proportion)             %>%
@@
     )
+
 ```

### 2019-02-19 Topic Scores.Rmd
figuring out course to keyword mapping

@@
 ```{r topic score student}
-student$topic_score <- beta_description$k35%>%
+student$topic_score <- beta_description$k35 %>%
   filter(term %in% student$kw_policy)       %>%
-  group_by(topic)%>% #maybe we can do this with transcripts afterwards
-  summarize(B_score= sum(beta))%>%
-  ungroup()%>%
+  group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
+  summarize(B_score= sum(beta))             %>%
+  ungroup()                                 %>%
   mutate(Total_b      = sum(B_score),

### 2019-02-19 test_delete_later_sofia.Rmd
figuring out course to keyword mapping

@@
 ```{r course_score}
+my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
+  pull(document)
 
@@
 gamma_descriptions$k35     %>%
+  filter(document %in% my_courses)%>%
+  arrange(document, gamma)
   full_join(student$topic_score, by = "topic") %>%

### 2019-02-19 App/Recommender System/server.R
updating variable name

@@ -213,7 +213,7 @@ function(input, output) {
         document
         ) %>%
       summarise(
-        course_score = sum(gamma * B_proportion)
+        course_score = sum(gamma * topic_score_proportion)
         ) %>%
       ungroup
       

### 2019-02-19 test_delete_later_sofia.Rmd
topic contribution to course

--- 2019-02-19 test_delete_later_sofia.Rmd
@@
 student <- list()
-student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war") #sample(terms, 5)
+student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
 student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
@@
   mutate_at(.vars = vars(num_range("Topic ",1:35)),
-            .funs = standardize)
+            .funs = standardize)                                      %>%
+   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))
 
@@
 ```{r course_score}
+#
+##Extracts recommended courses
+my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
+  pull(document)
 
@@
 ## Topic contribution to course
-gamma_descriptions$k35     %>%
-  full_join(student$topic_score, by = "topic") %>%
-  group_by(document, topic)                           %>%
-  summarise(total_gamma= sum(gamma))
-  mutate(X = gamma * B_proportion)             %>%
+key_words <- gamma_descriptions$k35                             %>%
+  filter(document %in% my_courses)                 %>%
+  arrange(document, gamma)                         %>%
+  full_join(contribution_to_topics, by = "topic" ) %>%
+  arrange(document, desc(gamma), desc(beta_rank) ) %>%
+  group_by(document #, 
+           #gamma
+           )                                       %>%
+  filter(row_number() %in% 1:3)                    %>%  #makes most sense with just 1 kw # group_by(document) %>% filter(row_number() %in% 1:9) 
   group_by(document)                               %>%
-  summarise(course_score = sum(X))             %>%
-  arrange(desc(course_score))                  %>%
-  left_join(
-    select(d_course, `Course ID`, `Course Title`),
-    by = c("document" = "Course ID")
-    )
+  summarise(key_words = list(Reduce(f= c,
+                               x = term)))
 

### 2019-02-19 Topic Scores.Rmd
explanations

@@
 ```
+
 ###View
@@
 ```
+
+##Explaining outcome
+###key words contribution to topic b_score
+```{r topic score student}
+#
+## standardizing function (within topic)
+standardize <- function (col) {
+  col/sum(col)
+}
+
+#
+##key word Contributions to Topic
+ kw_to_topics <- beta_description$k35                                 %>%
+  filter(term %in% student$kw_policy)                                 %>%
+  arrange(topic, desc(beta))                                          %>%
+  spread(key=topic, value=beta)                                       %>%
+  mutate_at(.vars = vars(num_range("Topic ",1:35)),
+            .funs = standardize)                                      %>%
+   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))
+```
+
+##Topic contribution to course
+```{r course_score}
+#
+##Extracts recommended courses n = 5
+my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
+  pull(document)
+
+#
+## Topic contribution to course
+key_words <- gamma_descriptions$k35                             %>%
+  filter(document %in% my_courses)                 %>%
+  arrange(document, gamma)                         %>%
+  full_join(kw_to_topics, by = "topic" ) %>%
+  arrange(document, desc(gamma), desc(beta_rank) ) %>%
+  group_by(document #, 
+           #gamma
+           )                                       %>%
+  filter(row_number() %in% 1:3)                    %>%  #makes most sense with just 1 kw # group_by(document) %>% filter(row_number() %in% 1:9) 
+  group_by(document)                               %>%
+  summarise(key_words = list(Reduce(f= c,
+                               x = term)))
+
+```

### 2019-02-19 Topic Scores.Rmd
simplify code

@@
   arrange(topic, desc(beta))                                          %>%
-  spread(key=topic, value=beta)                                       %>%
-  mutate_at(.vars = vars(num_range("Topic ",1:35)),
-            .funs = standardize)                                      %>%
-   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))
+  group_by(topic)                                                     %>%
+  mutate(beta_sum=sum(beta),
+         beta_rank=beta/beta_sum)                                     %>%
+  select(-beta_sum, -beta)
 ```

### 2019-02-19 Pillar 1 - Sequential Pattern Mining.Rmd
constrains on sequence rules "not take => low" and "not take => fail"

@@
   filter(
-    str_detect(rhs, "fail")
+    str_detect(rhs, "fail"),
+    lift > 1,
+    confidence >= 0.40
     )
@@
 
-  # lhs not, rhs low
-  filter(
-    str_detect(rhs, "low")
+  # constraints to respect
+  filter(
+    str_detect(rhs, "low"),
+    lift > 1,
+    confidence >= 0.40
     )
@@
   )
-```
+
+save(
+  AR, SR,
+  file = "App/Recommender System/rules.RDATA"
+  )
+```

### 2019-02-20 Topic Scores.Rmd
selects key words

@@
 
-##Topic contribution to course
+###Topic contribution to course
 ```{r course_score}
@@
                                x = term)))
+```
 
+##Selectig keywords
+```{r}
+top_kw <- beta_description$k35 %>%
+  group_by(topic) %>%
+  top_n(3, beta) %>%
+  pull(term)
+
+kw <- unique(top_kw)
+
+kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl",
+    #unsure:
+               "theory", "search", "perspective"
+                )
+kw <- setdiff(kw, kw_stopwords)
 ```

### 2019-02-20 test_delete_later_sofia.Rmd
test key word selection

@@
 ```
+
 ##Raw Data
@@
 student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
+
 ```
@@
 ##key word Contributions to Topic
- contribution_to_topics <- beta_description$k35                       %>%
+ contribution_to_topics #<- 
+beta_description$k35                       %>%
+  filter(term %in% student$kw_policy)                                 %>%
+  arrange(topic, desc(beta))                                          %>%
+  group_by(topic) %>%
+  #this is new
+  mutate(beta_sum=sum(beta),
+         beta_rank=beta/beta_sum) %>%
+  select(-beta_sum, -beta)
+  #
+  spread(key=topic, value=beta)                                       %>%
+  mutate_at(.vars = vars(num_range("Topic ",1:35)),
+            .funs = standardize)                                      %>%
+   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))
+
+  beta_description$k35                       %>%
   filter(term %in% student$kw_policy)                                 %>%
@@
 ```
+
+###Selecting key words
+```{r}
+test <- beta_description$k35 %>%
+  group_by(topic) %>%
+  top_n(3, beta) %>%
+  group_by(topic) %>%
+  summarise(key_words= list(Reduce(f= c, x = term)))
+
+kw <- unique(Reduce(x = test$key_words, f= c))
+
+kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl")
+
+setdiff(kw, kw_stopwords)
+
+```

### 2019-02-20 test_delete_later_sofia.Rmd
clean

@@
 ```{r}
-test <- beta_description$k35 %>%
+top_kw <- beta_description$k35 %>%
   group_by(topic) %>%
   top_n(3, beta) %>%
-  group_by(topic) %>%
-  summarise(key_words= list(Reduce(f= c, x = term)))
+  pull(term)
 
-kw <- unique(Reduce(x = test$key_words, f= c))
+kw <- unique(top_kw)
 
-kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl")
-
-setdiff(kw, kw_stopwords)
+kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl",
+    #unsure:
+               "theory", "search", "perspective"
+                )
+kw <- setdiff(kw, kw_stopwords)
 

### 2019-02-20 App/Recommender System/server.R
include red flag based on grades

@@ -12,46 +12,32 @@ function(input, output) {
   
   output$red_flags <- renderUI({
     
-    pass_grade <- 5.5
-    high_grade <- 6.5
     
-    augment_student_transcript <- function(transcript){
+    #
+    # Set up
+    
+    # Student profile
+    student <- list()
+     
+    # Student transcript
+    student$transcript <- d_transcript %>%
       
-      transcript %>%
-        
-        mutate(
-          fail       = grade < pass_grade,
-          low        = grade < high_grade,
-          grade_ceil = ceiling(grade)
+      filter(
+        `Student ID` == input$student
+        ) %>%
+      
+      select(
+        course = `Course ID`,
+        grade  = Grade
+        ) %>%
+      
+      mutate(
+        fail       = grade < 5.5,
+        low        = grade < 6.5,
+        grade_ceil = ceiling(grade)
         )
-      
-    }
     
-    student <- list(
-      
-      # transcript of student: tibble with course and grade
-      transcript = d_transcript %>%
-        
-        filter(
-          `Student ID` == input$student
-          ) %>%
-        
-        select(
-          course = `Course ID`,
-          grade  = Grade
-          ) %>%
-        
-        augment_student_transcript,
-
-      # interest of student (to be used with topic model)
-      interest = c("key", "words", "related", "to", "topics")
-      
-    )
-    
-    course_all <- unique(d_course$`Course ID`)
-    
-    student$course_not_taken <- setdiff(course_all, student$transcript$course)
-
+    # Courses with low score
     student$course_low <- student$transcript %>%
       filter(
         low
@@ -60,29 +46,39 @@ function(input, output) {
         course
         )
     
+    # Courses with fail score
     student$course_fail <- student$transcript %>%
       filter(
         fail
-      ) %>%
+        ) %>%
       pull(
         course
+        )
+    
+    # Course not taken
+    student$course_not_taken <- setdiff(
+      x = d_course$`Course ID`, # list of all courses offered
+      y = student$transcript$course
       )
     
     
-    rule_not <- SR$THL %>%
+    
+    #
+    # Red Flags
+    
+    # rules
+    rules <- list()
+    
+    # rules not
+    rules$not <- SR$THL %>%
       
-      select(
-        rhs_course,
-        lhs_course,
-        confidence,
-        lhs.rhsTake.count
-        ) %>%
-      
+      # select appropriate rules
       filter(
-        rhs_course %in% input$course_chosen,
[…]

### 2019-02-20 Pillar 1 - Sequential Pattern Mining.Rmd
filter rules based on count, lift and confidence

@@
   filter(
-    str_detect(rhs, "fail"),
-    lift > 1,
-    confidence >= 0.40
+    str_detect(rhs, "fail")
     )
@@
   filter(
-    str_detect(rhs, "low"),
-    lift > 1,
-    confidence >= 0.40
+    str_detect(rhs, "low")
     )
@@
     # rhs is grade less than or equal to 6
-    rhs_outcome == 6
-    ) %>%
-
-  # for each combination of course (lhs and rhs), keep AR with highest lift (most informative)
-  group_by(
-    lhs_course,
-    rhs_course
-    ) %>%
-  top_n(
-    n = 1,
-    lift
-    ) %>%
-  ungroup
+    rhs_outcome <= 6,
+    lhs_outcome <= 7
+    )
 ```
@@
     filter(
-      count >= 10
+      count      >= 10,
+      lift       >= 1,
+      confidence >= 0.4
       )

### 2019-02-20 App/Recommender System/server.R
debug

@@ -249,6 +249,7 @@ function(input, output) {
         ) %>% 
         
         HTML
+      
     }
     
     
@@ -341,7 +342,7 @@ function(input, output) {
       
       # Recommendations
       top_n(
-        n  = 5,
+        n  = 1,
         wt = course_score
         ) %>%
       

### 2019-02-20 App/Recommender System/ui.R
minor change

@@ -6,6 +6,7 @@
 library(tidyverse)
 library(tidytext)
 library(shiny)
+
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
 load("LDA_overview.RDATA")
@@ -65,8 +66,8 @@ navbarPage(
         checkboxGroupInput(
           inputId  = "course_chosen",
           label    = "Tentative Courses for following period",
-          choices  = course_following_semester,
-          selected = course_following_semester,
+          choices  = course_all,
+          selected = course_all,
           inline   = TRUE
           )
         

### 2019-02-20 Topic Scores.Rmd
deletes empty lines
simplifying key words

@@
 ```{r}
-top_kw <- beta_description$k35 %>%
+top_words <- beta_description$k35 %>%
   group_by(topic) %>%
   top_n(3, beta) %>%
-  pull(term)
+  pull(term)%>%
+  unique
 
-kw <- unique(top_kw)
-
-kw_stopwords =c("student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue", "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford", "cuss", "lecture", "pbl",
+kw_stopwords =c(
+  "student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue",
+  "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford",
+  "cuss", "lecture", "pbl",
     #unsure:
@@
                 )
-kw <- setdiff(kw, kw_stopwords)
+kw <- setdiff(top_words, kw_stopwords)
 ```

### 2019-02-20 App/Recommender System/ui.R
key words load

@@ -9,6 +9,7 @@ library(shiny)
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
 load("LDA_overview.RDATA")
+load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN 
 
 # set seed
 set.seed(1)
@@ -34,7 +35,7 @@ course_following_semester <- sample(
   replace = FALSE
   ) %>% sort
 
-
+key_words <- kw
 
 #
 # ui

### 2019-02-20 Topic Scores.Rmd
save key words

@@
 kw <- setdiff(top_words, kw_stopwords)
+
+save(kw, file="App/Recommender System/LDA_keyword_DELETE_.RDATA")
 ```

### 2019-02-20 App/Recommender System/server.R
recommend 3 courses instead of 1

@@ -342,7 +342,7 @@ function(input, output) {
       
       # Recommendations
       top_n(
-        n  = 1,
+        n  = 3,
         wt = course_score
         ) %>%
       

### 2019-02-20 App/Recommender System/ui.R
choices, predetermined key words

@@ -103,11 +103,7 @@ navbarPage(
         checkboxGroupInput(
           inputId  = "key_words",
           label    = "Academic Interest",
-          choices  = c(
-            "climate", "sustainability", "change", "development", "develop","sustain", "sustainable",
-            "//",
-            "international", "economic", "conflict", "develop", "policy", "war"
-            ),
+          choices  = kw,
           selected = c("international", "economic", "conflict", "develop", "policy", "war"),
           inline   = TRUE
           ),

### 2019-02-21 LDA_evaluation_script.R
cleaning before export

@@ -68,5 +68,38 @@ LDA_model$k35 <- LDA(
   method  = "Gibbs",
   control = my_control_individual
 )
+#Preparing for export
 
-save(LDA_model,file="Output/LDA_overview.RDATA")
+#Functions
+get_beta <- function(results){
+  
+  tidytext::tidy(results, matrix = "beta") %>%
+    mutate(topic = paste("Topic", topic)) %>%
+    arrange(topic, desc(beta))
+  
+}
+
+get_gamma <- function(results){
+  
+  tidytext::tidy(results, matrix = "gamma") %>%
+    mutate(topic = paste("Topic", topic)) %>%
+    arrange(topic, desc(gamma))
+  
+}
+#Applying functions
+clean_models <- list()
+
+clean_models$beta_distribution <- lapply(
+  LDA_model,
+  get_beta
+)
+
+clean_models$gamma_distribution <- lapply(
+  LDA_model,
+  get_gamma
+)
+  
+#saving
+save(clean_models,
+  #LDA_model,
+     file="Output/LDA_overview.RDATA")

### 2019-02-21 App/Recommender System/server.R
Clean LDA, instead of LDA import

@@ -262,31 +262,34 @@ function(input, output) {
     # Set up
     
     # Topic model
-    get_beta <- function(results){
-      
-      tidytext::tidy(results, matrix = "beta") %>%
-        mutate(topic = paste("Topic", topic)) %>%
-        arrange(topic, desc(beta))
-      
-    }
+    # get_beta <- function(results){
+    #   
+    #   tidytext::tidy(results, matrix = "beta") %>%
+    #     mutate(topic = paste("Topic", topic)) %>%
+    #     arrange(topic, desc(beta))
+    #   
+    # }
+    # 
+    # get_gamma <- function(results){
+    #   
+    #   tidytext::tidy(results, matrix = "gamma") %>%
+    #     mutate(topic = paste("Topic", topic)) %>%
+    #     arrange(topic, desc(gamma))
+    #   
+    # }
+    # 
+    # beta_distribution <- lapply(
+    #   LDA_model,
+    #   get_beta
+    #   )
+    # 
+    # gamma_distribution <- lapply(
+    #   LDA_model,
+    #   get_gamma
+    #   )
     
-    get_gamma <- function(results){
-      
-      tidytext::tidy(results, matrix = "gamma") %>%
-        mutate(topic = paste("Topic", topic)) %>%
-        arrange(topic, desc(gamma))
-      
-    }
-    
-    beta_distribution <- lapply(
-      LDA_model,
-      get_beta
-      )
-    
-    gamma_distribution <- lapply(
-      LDA_model,
-      get_gamma
-      )
+    beta_distribution <- clean_models$beta_distribution 
+    gamma_distribution <- clean_models$gamma_distribution
     
     # Key words
     key_words_additional <- c(

### 2019-02-21 LDA_evaluation_script.R
savinf into file

@@ -102,4 +102,4 @@ clean_models$gamma_distribution <- lapply(
 #saving
 save(clean_models,
   #LDA_model,
-     file="Output/LDA_overview.RDATA")
+     file="App/Recommender System/LDA_overview.RDATA")

### 2019-02-21 App/Recommender System/server.R
adds hunspell

@@ -1,6 +1,7 @@
 library(tidyverse)
 library(tidytext)
 library(stringr)
+library(hunspell)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
@@ -314,6 +315,8 @@ function(input, output) {
     
     #
     # Course recommendation
+    student <- list()
+    
     student$topic_score <- beta_distribution$k35 %>%
       
       # Topic score

### 2019-02-21 App/Recommender System/server.R
makes text bold and italic

@@ -394,9 +394,9 @@ function(input, output) {
       
       transmute(
         recommendation = paste(
-          "Course Recommendation", 
-          document, `Course Title`,
-          "because you selected the key words:" , key_words
+          "Course Recommendation", "<em>","<b>",
+          document, `Course Title`,"</b>","</em>",
+          "because you selected the key words:" ,"<b>", key_words,"</b>"
           )
         ) %>%
       

### 2019-02-21 Pillar 1 - Sequential Pattern Mining.Rmd
filter rules for course recommender app

@@
 
-  # reduce number of rules
-  filter(
-    lhs_course  != rhs_course, # exclude rules with same course on lhs and rhs
-    rhs_outcome == 6            
-    ) %>%
-
-  # for each combination of courses (lhs and rhs), keep AR with highest lift (most informative AR)
-  group_by(
-    lhs_course, 
-    rhs_course
-    ) %>%
-  top_n(
-    1,
-    lift
-    ) %>%
-  ungroup
+  # Reduce number of rules
+  filter(
+    # exclude rules with same course on lhs and rhs
+    lhs_course != rhs_course,
+    # rhs is grade less than or equal to 6
+    rhs_outcome <= 6,
+    lhs_outcome <= 7
+    )
 ```
@@
 ```{r edit_rules}
+edit_rules <- function(rules){
+
+  rules %>%
+
+    mutate(
+      count = support * n_students
+      ) %>%
+
+    select(
+      lhs, rhs,
+      support, count,
+      confidence,
+      matches("rhsTake.support"),
+      lift,
+      matches("rhsTake.count")
+      ) %>%
+
+     mutate_if(
+       is.numeric,
+       round,
+       digits = 3
+       ) %>%
+
+    arrange(
+      desc(count)
+      )
+
+}
+```
+
+```{r edit rules}
+AR <- lapply(
+  X   = AR,
+  FUN = edit_rules
+  )
+
+SR <- lapply(
+  X   = SR,
+  FUN = edit_rules
+  )
+```
+
+```{r}
+save(
+  AR, SR,
+  file = "App/rules/rules.RDATA"
+  )
+```
+
+```{r show rules}
+print(AR$THL)
+print(SR$THL)
+```
+
+```{r}
 filter_rules <- function(rules){
@@
   rules %>%
-
-    mutate(
-      count = support * n_students
-      ) %>%
 
@@
       )
-
-}
-```
-
-```{r edit rules}
+}
+```
+
+```{r}
 AR <- lapply(
@@
 
-```{r show rules}
-print(AR$THL)
-print(SR$THL)
-```
-
 ```{r save rules, include = FALSE}
@@
   AR, SR,
-  file = "App/rules/rules.RDATA"
-  )
-
-save(
-  AR, SR,
   file = "App/Recommender System/rules.RDATA"

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
output experiment

@@
 
-  burnin = 500,
-  iter   = 2000,
+  burnin = 100,
+  iter   = 5000,
   thin   = 100
@@
   control = my_control,
-  mc.cores = 1L
+  mc.cores = 4L
 
@@
 
-```{r}
+```{r description topics, cache = TRUE}
 start.time <- Sys.time()
 
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
 
@@
 
-save(result_descrition,
-     file = "Output/LDA_ntopics_description.RDATA")
+save(result_description,
+     file = "Output/LDA_ntopics.RDATA")
 
@@
 
-```{r}
+```{r overview topics, cache = TRUE}
 start.time <- Sys.time()
 
-result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
 
@@
 
-save(result_overview ,
-     file = "Output/LDA_ntopics_overview.RDATA")
+save(result_overview , result_description,
+     file = "Output/LDA_ntopics.RDATA")
 
@@
 
-```{r, eval = F}
+```{r manual topics, cache = TRUE}
 start.time <- Sys.time()
 
-result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))
+result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))
 
@@
 
-save(result_manual,
-     file = "Output/LDA_ntopics_manual.RDATA")
+save(result_manual, result_overview , result_description,
+     file = "Output/LDA_ntopics.RDATA")
 
@@
 
-load("Output/LDA_ntopics_description.RDATA")
+load("Output/LDA_ntopics.RDATA")
 
-load("Output/LDA_ntopics_overview.RDATA")
-
-load("Output/LDA_ntopics_manual.RDATA")
-
-result_descrition %>%
+result_description %>%
   select(-Griffiths2004) %>%
@@
 ```{r LDA fit, cache = TRUE}
-n_topics <- 5
+n_topics <- 35
 levels   <- c("description", "overview", "manual")
@@
     method  = "Gibbs",
-    control = list(
-      nstart  = 10,
-      seed    = c(1:10),
-      best    = TRUE,
-
-      burnin  = 4000,
-      iter    = 5000,
-      thin    = 500,
-
-      verbose = 1e3,
-      save    = 1e3,
-      keep    = 1e3)
+    control = my_control
     )
@@
 save(list = list_nam,
-     file = "LDA.RDATA")
+     file = "Output/topic_model.RDATA")
+
+save(list = list_nam,
+     file = "App/Recommender System/topic_model.RDATA")
 ```

### 2019-02-26 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 ```{r edit_rules}
-edit_rules <- function(rules){
+edit_rules_rulesApp <- function(rules){
 
@@
 ```{r edit rules}
-AR <- lapply(
+AR_rulesAPP <- lapply(
   X   = AR,
-  FUN = edit_rules
-  )
-
-SR <- lapply(
+  FUN = edit_rules_rulesApp
+  )
+
+SR_rulesAPP <- lapply(
   X   = SR,
-  FUN = edit_rules
+  FUN = edit_rules_rulesApp
   )
@@
 save(
-  AR, SR,
+  AR_rulesAPP, SR_rulesAPP,
   file = "App/rules/rules.RDATA"
@@
 ```{r}
-filter_rules <- function(rules){
+edit_rules_RSAPP <- function(rules){
 
   rules %>%
+
+    mutate(
+      count = support * n_students
+      ) %>%
 
@@
       )
+
 }
@@
 ```{r}
-AR <- lapply(
+AR_RSAPP <- lapply(
   X   = AR,
-  FUN = filter_rules
-  )
-
-SR <- lapply(
+  FUN = edit_rules_RSAPP
+  )
+
+SR_RSAPP <- lapply(
   X   = SR,
-  FUN = filter_rules
+  FUN = edit_rules_RSAPP
   )
@@
 save(
-  AR, SR,
+  AR_RSAPP, SR_RSAPP,
   file = "App/Recommender System/rules.RDATA"

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
commenting section on LDA.

--- 2019-02-15 Pillar 2 - Topic Modeling.Rmd
@@
 # Setup
+We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
+`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
+For `d_description` and `d_overview`, we keep only the most recent year.
 ```{r import data}
@@
 ## Functions for Generating Barplots and Word Clouds
-
+The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
 ```{r compute_tf_idf, cache = TRUE}
@@
 
+The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
 ```{r plot_tf_idf}
@@
 ## Course Level
+The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
+We apply the function to `id_plot` and pipe it to produce graphs.
 ```{r tf-idf course, cache = TRUE}
@@
 # LDA
-
+The function `my_cast_tdm` casts our dataframes into a tdm.
 ```{r my_cast_tdm}
@@
 ## Ideal Number of Topics (RUN ON UM COMPUTER)
+To decide the number of topics to discover, we run (four) three different tests.
 
-```{r}
+First we set the control for the test.
+```{r controls}
 my_control <- list(
@@
 ```
-
-```{r}
+The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
+```{r function my_FindTopicsNumber }
 my_FindTopicsNumber <- function(data_cast, n_topics){
@@
 ```
-
-```{r}
+We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
+```{r description topics, cache = TRUE}
 start.time <- Sys.time()
@@
 
-```{r}
+We run the test for overview, documeting its duration. 
+```{r overview topics, cache = TRUE}
 start.time <- Sys.time()

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd

--- 2019-02-26 Pillar 2 - Topic Modeling.Rmd
@@
 ## Ideal Number of Topics (RUN ON UM COMPUTER)
+To decide the number of topics to discover, we run (four) three different tests.
 
+First we set the control for the test.
 ```{r controls}
@@
 ```
-
+The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
 ```{r function my_FindTopicsNumber }
@@
 ```
-
+We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
 ```{r description topics, cache = TRUE}
@@
 
+We run the test for overview, documeting its duration. 
 ```{r overview topics, cache = TRUE}

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
delets Griffths2004

@@
   topics = n_topics,
-  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
   method = "Gibbs",
@@
 
+We run the test for manuals, documenting its duration.
 ```{r manual topics, cache = TRUE}
@@
 
+We examine the result of the experiment by plotting them on a graph.
 ```{r LDA number topics plot}
@@
 result_description %>%
-  select(-Griffiths2004) %>%
   FindTopicsNumber_plot
@@
 result_overview %>%
-  select(-Griffiths2004) %>%
   FindTopicsNumber_plot
@@
 result_manual %>%
-  select(-Griffiths2004) %>%
   FindTopicsNumber_plot
@@
 
+From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics.
 ```{r LDA fit, cache = TRUE}

### 2019-02-27 App/Rules/server.R
removes redundant variable

@@ -24,7 +24,7 @@ function(input, output) {
           between(confidence, input$confidence[1], input$confidence[2]),
           between(lift      , input$lift[1]      , input$lift[2]      )
         ) %>%
-        select(-lhs_course,-lhs_outcome, -rhs_course, -rhs_outcome)
+        select(-lhs_course,-lhs_outcome, -rhs_course, -rhs_outcome, -rhs.support)
       
     },
     

### 2019-02-27 Pillar 1 - Sequential Pattern Mining.Rmd
removes previous irrelevant updata

@@
 
-We create a function, which, when given the code of a course, returns its title.
-```{r function find_course}
-find_course <- function(code){
-
-  dataset <- d_transcript %>%
-    filter(`Course ID`== code)
-
-  title <- dataset$`Course Title`[1]
-
-  return(title)
-
-}
-
-# Example
-find_course("HUM1005")
-```
-
 # Data Exploration
@@
       ) %>%
+
     group_by(
@@
       lhs, rhs,
-      support, count,
+      matches("rhsTake.count"), count,
+      matches("rhsTake.support"),
       confidence,
-      matches("rhsTake.support"),
-      lift,
-      matches("rhsTake.count")
+      support, 
+      lift
       ) %>%
@@
 ```{r show rules}
-print(AR$THL)
-print(SR$THL)
+print(AR_rulesAPP$THL)
+print(SR_rulesAPP$THL)
 ```

### 2019-02-27 App/Rules/server.R

@@ -23,8 +23,7 @@ function(input, output) {
           between(count     , input$count[1]     , input$count[2]     ),
           between(confidence, input$confidence[1], input$confidence[2]),
           between(lift      , input$lift[1]      , input$lift[2]      )
-        ) %>%
-        select(-lhs_course,-lhs_outcome, -rhs_course, -rhs_outcome, -rhs.support)
+        )
       
     },
     

### 2019-02-27 App/Rules/ui.R
labels updates

@@ -15,10 +15,10 @@ fluidPage(
         inputId = "rules",
         label   = "Type of rules",
         choices = c(
-          "Association rules" = "AR",
-          "Sequence rules"    = "SR"
+          "Association rules" = "AR_rulesAPP",
+          "Sequence rules"    = "SR_rulesAPP"
         ),
-        selected = "AR"
+        selected = "AR_rulesAPP"
       ),
       
       # Input: button for the type of rules

### 2019-02-27 Data Preparation.Rmd
use list to manipulate textual data (instead of multiple dataframes)

@@
 
-```{r setup, include = T}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
@@
 ```{r import list}
-lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
-lists <- list(
-  Assessment      = lists_brut$Assessment,
-  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
-  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
-  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
-  )
+lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
+  map(na.omit)
+
+lists <- list()
+
+lists$Assessment      <- lists_brut$Assessment
+lists$AoD             <- lists_brut$Aim
+
+# selection of most important types of assessment an AoD to keep plots clear
+lists$Assessment_plot <- lists$Assessment[lists_brut$`Assessment for Plot` == 1]
+lists$AoD_plot        <- lists$AoD       [lists_brut$`Aim for Plot`        == 1]
+
 rm(lists_brut)
@@
 ```{r import d_course d_assessment and d_ILO, cache = TRUE}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848')
-print(d_course)
+d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
+  print
 
 d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-  select(- `Comment on Assessment`) %>%
-  gather(Assessment, assessment_covered, - `Course ID`, factor_key = T) %>%
-  filter(assessment_covered == 1) %>%
-  select(- assessment_covered) %>%
-  arrange(`Course ID`)
-print(d_assessment)
+  mutate_if(
+    .predicate = is.numeric,
+    as.logical
+    ) %>%
+  gather(
+    key   = Assessment, 
+    value = assessment_covered,
+    Paper : Participation
+    ) %>%
+  filter(
+    assessment_covered
+    ) %>%
+  select(
+    - c(assessment_covered, `Comment on Assessment`)
+    ) %>%
+  arrange(
+    `Course ID`
+    ) %>%
+  print
 
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
-  select(- c(Comments, Comments_for_Jeroen)) %>%
-  gather(AoD, AoD_covered, -c(`Course ID`, Objectives), factor_key = T) %>%
-  filter(AoD_covered == 1) %>%
-  select(- AoD_covered) %>%
-  rename(ILO = Objectives) %>%
-  arrange(`Course ID`)
-print(d_ILO)
+d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
+
+d_AoD_ILO <- d_ILO %>%
+  rename(
+    ILO = Objectives
+    ) %>%
+  mutate_if(
+    .predicate = is.numeric,
+    as.logical
+    ) %>%
+  gather(
+    key   = AoD, 
+    value = AoD_covered,
+    `Matrix Complete` : `Intercultural Skills`
+    ) %>%
+  filter(
+    AoD_covered
+    ) %>%
+  select(
+    - c(AoD_covered, Comments, Comments_for_Jeroen)
+    ) %>%
+  print
 ```
@@
 ```{r import corpus_catalogues, cache = TRUE}
-corpus_catalogues <- Corpus(x             = DirSource("./Input/Catalogues"),
-                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
+d_text <- list()
+
+d_text$catalogues <- Corpus(
+  x             = DirSource("./Input/Catalogues"),
+  readerControl = list(reader = readPDF(control = list(text = "-layout")))
+  )
 ```
@@
 ```{r import corpus_manuals, cache = TRUE}
-corpus_manuals <- Corpus(x             = DirSource("./Input/Manuals 2017-18"),
-                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
+d_text$manuals <- Corpus(
+  x             = DirSource("./Input/Manuals 2017-18"),
+  readerControl = list(reader = readPDF(control = list(text = "-layout")))
+  )
 ```
+
 ## Student Data
@@
 ```{r import d_transcript, cache = TRUE}
-d_transcript <- rbind(
-  read_csv(
-    "./Input/Raw Grades/grades1.csv",
+d_transcript1 <- read_csv(
+  file = "Input/Raw Grades/grades1.csv",
   col_types = cols(
-      `Program (Abbreviation)` = col_character(),
-      `Appraisal Status` = col_character(),
-      `Module Booking Reason (Description)` = col_character(),
-      `Object name` = col_character(),
-      `Start date` = col_character(),
-      `End Date` = col_character()
-      )
-    ),
-
-  read_csv(
-    "./Input/Raw Grades/grades2.csv",
-    col_types = cols(
-      `Program (Abbreviation)` = col_character(),
-      `Appraisal Status` = col_character(),
-      `Module Booking Reason (Description)` = col_character(), 
-      `Object name` = col_character(), 
-      `Start date` = col_character(), 
-      `End Date` = col_character()
+    `Program (Abbreviation)`              = "c",
+    `Appraisal Status`                    = "c",
+    `Module Booking Reason (Description)` = "c"
     )
@@
 
+d_transcript2 <- read_csv(
+  file = "Input/Raw Grades/grades2.csv",
+  col_types = cols(
+    `Program (Abbreviation)`              = "c",
+    `Appraisal Status`                    = "c",
+      `Object name`                       = "c",
+      `Start date`                        = "c",
+      `End Date`                          = "c"
     )
+  )
+
+d_transcript <- rbind(d_transcript1, d_transcript2)
+
+rm(d_transcript1, d_transcript2)
 ```
@@
 ```{r d_AoD_ILO}
-d_AoD_ILO <- distinct(d_ILO, `Course ID`, AoD)
-print(d_AoD_ILO)
+d_AoD_ILO
 ```
@@
 ```{r map_assessment_AoD}
-map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
-                                  mutate_all(as.logical))
-rownames(map_assessment_AoD) <- lists$Assessment
-
-# Print section of matrix
-print(map_assessment_AoD[1:5, 8:12])
+map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
+  mutate_if(
+    .predicate = is.numeric,
+    .f         = as.logical
+    ) %>%
+  gather(
+    key   = AoD, 
+    value = AoD_covered,
+    `Matrix Complete` : `Intercultural Skills`
+    ) %>%
+  filter(
+    AoD_covered
+    ) %>%
+  select(
+    - AoD_covered
+    ) %>%
+  arrange(
+    Assessment
+  ) %>%
+  print
 ```
@@
 ```{r d_AoD_assessment}
-d_AoD_assessment <- tibble(`Course ID` = character(0),
-                           Assessment  = character(0),
-                           AoD         = character(0))
+d_AoD_assessment <- d_assessment %>%
+  left_join(
+    map_assessment_AoD,
+    by = "Assessment"
+    ) %>%
+  print
 
-for(i in 1 : nrow(d_assessment)){
-
-  observation <- d_assessment[i, ]
-
-  assessments <- observation$Assessment
-  AoD_covered <- map_assessment_AoD[assessments, ]
-  AoD         <- lists$AoD[AoD_covered]
-
-  if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
-                                                 as_tibble(cbind(observation,
-                                                                 AoD)))
-}
-rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
-```
-
-Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
-```{r d_AoD_assessment distinct}
-d_AoD_assessment <- distinct(d_AoD_assessment, `Course ID`, AoD)
-print(d_AoD_assessment)
+rm(map_assessment_AoD)
 ```
@@
 ```{r rbind d_AoD_ILO and d_AoD_assessment}
-d_AoD <- rbind(d_AoD_ILO,
-               d_AoD_assessment) %>%
+d_AoD <- rbind(
+  d_AoD_ILO        %>% select(`Course ID`, AoD),
+  d_AoD_assessment %>% select(`Course ID`, AoD)
+  ) %>%
   distinct %>%
-  arrange(`Course ID`)
+  arrange(
+    `Course ID`
+    ) %>%
+  print
 
-rm(d_AoD_ILO, d_AoD_assessment)
-print(d_AoD)
+rm(d_AoD_assessment, d_AoD_ILO)
 ```
@@
 d_ILO_detail <- d_ILO %>%
-  distinct(`Course ID`, ILO) %>%
-  count(`Course ID`) %>%
-  rename(n_ILO = n)
+  count(
+    `Course ID`, 
+    sort = TRUE
+    ) %>%
+  rename(
+    n_ILO = n
+    ) %>%
+  print
 
 d_assessment_detail <- d_assessment %>%
-  group_by(`Course ID`) %>%
-  summarise(n_assessment = n(),
-            `Assessments Covered` = paste(Assessment, collapse = ", "))
+  group_by(
+    `Course ID`
+    ) %>%
+  summarise(
+    n_assessment = n(),
+    `Assessments Covered` = paste(Assessment, collapse = ", ")
+    ) %>%
+  print
 
 d_AoD_detail <- d_AoD %>%
-  group_by(`Course ID`) %>%
-  summarise(n_AoD = n(),
-            `AoD Covered` = paste(AoD, collapse = ", "))
-
-d_course_detail <- d_ILO_detail %>%
-  full_join(d_assessment_detail, by = "Course ID") %>%
-  full_join(d_AoD_detail       , by = "Course ID")
-
-rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
-print(d_course_detail)
+  group_by(
+    `Course ID`
+    ) %>%
+  summarise(
+    n_AoD = n(),
+    `AoD Covered` = paste(AoD, collapse = ", ")
+    ) %>%
+  print
 ```
@@
 d_course <- d_course %>%
-  full_join(d_course_detail, by = "Course ID") %>%
-  select(`Course ID`, `Course Title`, Cluster,
+  left_join(d_ILO_detail       , by = "Course ID") %>%
+  left_join(d_assessment_detail, by = "Course ID") %>%
+  left_join(d_AoD_detail       , by = "Course ID") %>%
+  select(
+    `Course ID`, `Course Title`, Cluster,
     n_ILO,
@@
     n_AoD, `AoD Covered`,
-         everything())
+    everything()
+    ) %>%
+  print
 
-rm(d_course_detail)
-print(d_course)
+rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
 ```
@@
 ```{r create UGR2000}
-d_course <- d_course %>%
-  rbind(filter(., `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-          mutate(`Course ID` = case_when(`Course ID` == "UGR3001" ~ "UGR2001",
+
+d_course_UGR_2000 <- d_course %>%
+  filter(
+    `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")
+    ) %>%
+  mutate(
+    `Course ID` = case_when(
+      `Course ID` == "UGR3001" ~ "UGR2001",
       `Course ID` == "UGR3002" ~ "UGR2002",
       `Course ID` == "UGR3003" ~ "UGR2003",
-                                  `Course ID` == "UGR3005" ~ "UGR2005")))
+      `Course ID` == "UGR3005" ~ "UGR2005"
+      )
+    ) %>%
+  print
 
-print(filter(d_course, `Course ID` %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
-                                          "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
+d_course <- d_course %>%
+  rbind(
+    d_course_UGR_2000
+    )
+
+print(
+  d_course %>%
+    filter(
+      str_detect(`Course ID`, "UGR")
+      )
+  )
+
+rm(d_course_UGR_2000)
 ```
@@
 d_course <- d_course %>%
+  separate(
+    col     = `Course ID`,
+    into    = c("Letters", "Number"),
+    sep     = 3,
+    remove  = FALSE,
+    convert = TRUE
+    ) %>%
   mutate(
-    Letters = substring(`Course ID`, 1, 3),
-    Number  = as.numeric(substring(`Course ID`, 4, 7)),
-    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
+    Level   = case_when(
+      between(Number, 1000, 1999) ~ "Introductory",
       between(Number, 2000, 2999) ~ "Intermediate",
-                        between(Number, 3000, 3999) ~ "Advanced"    ))
-
-print(select(d_course, `Course ID`, Letters, Number, Level))
+      between(Number, 3000, 3999) ~ "Advanced"    )
+    ) %>%
+  select(`Course ID`, Letters, Number, Level, everything()
+    ) %>%
+  print
 ```
@@
 ```{r extracting overview, cache = TRUE}
-# Setup
-n_catalogue <- length(corpus_catalogues)
-academic_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
-d_description <- tibble(`Course ID`     = character(0),
-                        `Academic Year` = character(0),
-                        Overview        = character(0),
-                        Description     = NA)
+#
+# Set up
+years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
 
-course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
-  paste(collapse = "|")
-
-content_to_exclude <- c(
+headers <- c(
   "^Core Courses \\(COR\\)",
@@
   "^Social Sciences \\(SSC\\)",
-  "^Skills Trainings \\(SKI\\)", "^Skills Training \\(SKI\\)",
-  "^Project \\(PRO\\)", "^Projects \\(PRO\\)",
-  "^Undergraduate Research \\(UGR\\)",
-  " UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research"
+  "^Skills Trainings? \\(SKI\\)",
+  "^Projects? \\(PRO\\)",
+  "^Undergraduate Research", "UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research",
+  "Appendix"
   ) %>%
@@
 
-# Loop 1
-for(n in 1 : n_catalogue){
+overview_start <- c(
+  "COR",
+  "HUM", "SCI", "SSC", 
+  "SKI", "PRO",
+  "UGR", "CAP"
+  ) %>% 
+  paste(collapse = "|")
 
-  cat <- content(corpus_catalogues[[n]])
+is_start_overview_section  <- function(string) string %>% str_detect(pattern = "^Core Courses \\(COR\\)")
+is_end_overview_section    <- function(string) string %>% str_detect(pattern = "Appendix")
+is_header                  <- function(string) string %>% str_detect(pattern = headers)
 
-  # Overview section in catalogue
-  page_overview_start <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
-  page_overview_end   <- grep(pattern = "Appendix", x = cat) - 1
-    if(length(page_overview_end) == 0) page_overview_end <- length(cat)
-  cat_overview <- cat[page_overview_start : page_overview_end]
+extract_code               <- function(string) string %>% str_sub(start = 1, end = 7)
+is_overview_start          <- function(string) string %>% extract_code %>% str_detect(pattern = overview_start)
+paste_if_two_page_overview <- function(page, page_following){
 
-  # Course description only
-  pages_to_exclude <- grep(pattern = content_to_exclude, x = cat_overview)
-  cat_overview <- cat_overview[! 1 : length(cat_overview) %in% pages_to_exclude]
+  # if the page is the start of an overview,
+  if(page %>% is_overview_start){
 
-  # First pages of course overviews
-  first_three_letters <- substr(cat_overview, start = 1, stop = 3)
-  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)
+    # then, if the following page is also the start of an overview, the overview is simply the current page
+    if(page_following %>% is_overview_start | is.na(page_following)){
 
-  # Loop 2
-  for(page in first_pages_overview){
+      page
 
-    # Extract description
-    overview <- if((page + 1) %in% first_pages_overview) cat_overview[page]
-                else paste(cat_overview[page : (page + 1)], collapse = " ")
+    # if the following page is also the start of an overview, the overview spans over the current and the following page
+    }else{
 
-    # Save overview
-    code <- substr(overview, start = 1, stop = 7)
-    year <- academic_years[n]
-    d_description <- d_description %>%
-      add_row(
-        `Course ID` = code,
-        `Academic Year` = year,
-        Overview = overview,
-        Description = NA
+    paste(page, page_following)
+
+    }
+
+  # if the page is not the start of an overview, return an NA
+  }else{
+
+    NA_character_
+
+  }
+
+}
+
+#
+# Loop
+
+for(i in seq_along(d_text$catalogues)){
+
+  catalogue_all <- d_text$catalogues %>%
+
+    # extract catalogue from corpus
+    .[[i]] %>%
+    content %>%
+
+    # create a tibble
+    tibble(
+      page = .
+      ) %>%
+
+    # identify start and end of overview section of catalogue
+    mutate(
+      page_n                    = row_number(), 
+      is_start_overview_section = page %>% is_start_overview_section,
+      is_end_overview_section   = page %>% is_end_overview_section
       )
 
-  } # close for-loop (page)
+  # Check that there is one and only one is_start_overview_section and no more than 1 is_end_overview_section.
+  if(sum(catalogue_all$is_start_overview_section) == 0) print("error: no overview_section_start"      )
+  if(sum(catalogue_all$is_start_overview_section) >  1) print("error: multiple overview_section_start")
+  if(sum(catalogue_all$is_end_overview_section  ) >  1) print("error: multiple overview_section_end"  )
 
-} # close for-loop (n)
+  # Extract overview section from catalogue
+  catalogue_overview <- catalogue_all %>%
 
-rm(corpus_catalogues,
-   n_catalogue, academic_years, course_code, content_to_exclude,
-   n, cat,
-   page_overview_start, page_overview_end,
-   pages_to_exclude, cat_overview,
-   first_three_letters, first_pages_overview,
-   page, overview, code, year)
-print(d_description)
-```
+    # identify and filter the pages that are in the overview section (is_overview_section)  
+    mutate(
+      is_after_start_overview_section = cumany( is_start_overview_section),
+      is_before_end_overview_section  = cumall(!is_end_overview_section  ),
+      is_overview_section             = is_after_start_overview_section & is_before_end_overview_section
+      ) %>%
 
-##### Extracting Descriptions
+    filter(
+      is_overview_section
+      ) %>%
 
-Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
-The description section contains a brief description (200-500 words) of the content of the course.
-To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
-The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
-The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
-Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
-A handful overviews do not contain a *Literature* section.
-For these, the section *Instructional Format* marks the end of the description section.
+    # exlude headers (is_to_exclude) as well as the first and the last page 
+    filter(
+      ! page %>% is_header
+      ) %>%
 
-```{r extracting description, cache = TRUE}
+    select(
+      - c(
+        is_start_overview_section, is_end_overview_section,
+        is_after_start_overview_section, is_before_end_overview_section,
+        is_overview_section
+        )
+      )
 
-# Setup
-symbol_to_line <- c("\r\n", "\n") %>%
-  paste(collapse = "|")
-start_descrip <- c("^Description", "^Course Description") %>%
-  paste(collapse = "|")
-end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
-                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
-  paste(collapse = "|")
-
-# Loop
-for(course in 1 : nrow(d_description)){
-
-  overview <- d_description$Overview[course]
-
-  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
-  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
-  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
-  # for overviews w/o Literature section, find section Instructional Format.
-  if(is_empty(line_end)){
-    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
-    print(paste("line_end irregular for", d_description$`Course ID`[course],
-                "in catalogue", d_description$`Calendar Year`[course]))
-    } # close if-statement
-
-  description <- paste(overview_by_line[line_start : line_end], collapse = " ")
-
-  d_description$Description[course] <- description
+  d_text$overview[[i]] <- catalogue_overview %>%
+    transmute(
+      text          = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
+      `Course ID` = text %>% extract_code,
+      year          = years[i]
+    )
 
 }
-rm(symbol_to_line, start_descrip, end_descrip,
-   course, overview, overview_by_line, line_start, line_end, description)
-print(d_description)
+
+d_text <- d_text[c("overview", "manuals")]
+d_text$overview <- bind_rows(d_text$overview)
+
+rm(
+  is_end_overview_section, is_header, is_overview_start, is_start_overview_section, paste_if_two_page_overview,
+  headers, i, overview_start, years,
+  catalogue_all, catalogue_overview
+  )
 ```
@@
 ```{r d_manual}
-d_manual <- tidy(corpus_manuals) %>%
-  select(id, text) %>%
-  mutate(`Course ID` = substring(id, 1, 7)) %>%
-  select(-id) %>%
-  rename(Manual = text)
-
-rm(corpus_manuals)
-print(d_manual)
+d_text$manuals <- d_text$manuals %>%
+  tidy %>%
+  select(
+    id, text
+    ) %>%
+  mutate(
+    `Course ID` = id %>% extract_code
+    ) %>%
+  select(
+    -id
+    ) %>%
+  print
 ```
@@
 ```{r tidy d_description}
-d_overview <- d_description %>%
-  select(`Course ID`, `Academic Year`, Overview) %>%
-  unnest_tokens(output = word, input = Overview)
+tidy_text <- function(df){
 
-d_description <- d_description %>%
-  select(`Course ID`, `Academic Year`, Description) %>%
-  unnest_tokens(output = word, input = Description)
+  df %>%
+    unnest_tokens(
+      output = word,
+      input  = text
+      )
 
-d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
+}
+
+d_text <- d_text %>% map(tidy_text)
 ```
@@
 stem_hunspell <- function(term) {
+
   stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
+
   n_stems <- length(stems)            # number of stems
+
   if (n_stems == 0) term              # if no stems, return original term
   else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
+
 }
 
-dictionary <- select(d_overview, `Course ID`, word) %>%
-  rbind(d_manual) %>% 
-  distinct(word) %>%
-  mutate(word_stem = purrr::map_chr(.x = word,
-                                    .f = stem_hunspell))
+dictionary <- d_text$overview$word %>%
+  union(
+    d_text$manuals$word
+    ) %>%
+  tibble(
+    word = .
+    ) %>%
+  mutate(
+    word_stem = word %>% map_chr(stem_hunspell)
+    )
+
+# TODO: "destem" terms by hand: cuss => discuss
+filter(dictionary, word_stem == "cuss")
 
@@
 ```{r stemming data sets}
-stem_with_dictionary <- function(data) data %>%
-                                         left_join(dictionary, by = "word") %>%
-                                         rename(word_original = word,
-                                                word = word_stem)
+stem_with_dictionary <- function(data){
 
-d_description <- stem_with_dictionary(d_description)
-d_overview <- stem_with_dictionary(d_overview)
-d_manual <- stem_with_dictionary(d_manual)
+  data %>%
+    left_join(
+      dictionary,
+      by = "word"
+      ) %>%
+    rename(
+      word_original = word,
+      word          = word_stem
+      )
+
+}
+
+d_text <- d_text %>% map(stem_with_dictionary)
 
 rm(stem_hunspell, stem_with_dictionary)
-print(d_description) # See starting - start
 ```
@@
 # Own stop words
-sw_own <- c("______________________________________________________________________________",
-            as.character(1:10))
+sw_own <- tibble(
+    word = c(
+      as.character(1 : 1e3)
+      )
+    )
 
-remove_sw <- function(data) data %>%
-  filter(! word %in% c(stop_words$word, sw_own))
+remove_sw <- function(data){
 
-d_description <- remove_sw(d_description)
-d_overview <- remove_sw(d_overview)
-d_manual <- remove_sw(d_manual)
+  data %>%
+    anti_join(
+      stop_words,
+      by = "word"
+      ) %>%
+    anti_join(
+      sw_own,
+      by = "word"
+      )
+
+}
+
+d_text <- d_text %>% 
+  map(remove_sw) %>% 
+  print
 
 rm(sw_own, remove_sw)
-print(d_description) # stop words (on, the, of, etc, are excluded)
 ```
@@
 ```{r}
-save(d_course, d_transcript,
+save(d_course, lists, d_AoD, d_assessment, d_ILO,
+     file = "Output/data_general.RDATA")
+save(d_transcript,
      file = "Output/data_pillar_1.RDATA")
-save(lists, d_course, d_AoD, d_assessment, d_transcript,
-     d_overview, d_description, d_manual,
+save(d_text,
      file = "Output/data_pillar_2.RDATA")
 ```
+
+# Extra
+
+## Extracting Descriptions
+
+Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
+The description section contains a brief description (200-500 words) of the content of the course.
+To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
+The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
+The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
+Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
+A handful overviews do not contain a *Literature* section.
+For these, the section *Instructional Format* marks the end of the description section.
+
+```{r extracting description, eval = FALSE}
+
+# Setup
+symbol_to_line <- c("\r\n", "\n") %>%
+  paste(collapse = "|")
+start_descrip <- c("^Description", "^Course Description") %>%
+  paste(collapse = "|")
+end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
+                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
+  paste(collapse = "|")
+
+# Loop
+for(course in 1 : nrow(d_description)){
+
+  overview <- d_description$Overview[course]
+
+  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
+  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
+  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
+  # for overviews w/o Literature section, find section Instructional Format.
+  if(is_empty(line_end)){
+    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
+    print(paste("line_end irregular for", d_description$`Course ID`[course],
+                "in catalogue", d_description$`Calendar Year`[course]))
+    } # close if-statement
+
+  description <- paste(overview_by_line[line_start : line_end], collapse = " ")
+
+  d_description$Description[course] <- description
+
+}
+rm(symbol_to_line, start_descrip, end_descrip,
+   course, overview, overview_by_line, line_start, line_end, description)
+print(d_description)
+```

### 2019-02-27 Topic Scores.Rmd
.DS_Store and empty line
minor changes to make code more interactive

@@
 beta_description <- lapply(
-  LDA_model,
+  clean_models,
   get_beta
@@
 ```{r inspect topics}
-topics <- beta_description$k35 %>%
+topics <- clean_models$beta_distribution$k10 %>%
   group_by(topic) %>%
@@
 student <- list()
-student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
-student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
+student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy")
+student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable")
 ```
@@
 ```{r topic score student}
-student$topic_score <- beta_description$k35 %>%
-  filter(term %in% student$kw_policy)       %>%
+student$topic_score <- clean_models$beta_distribution$k35 %>%
+  filter(term %in% student$kw_climate)       %>%
   group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
@@
          B_proportion = B_score/Total_b)    %>%
-  arrange(desc(B_score))
+  arrange(desc(B_score)) %>%
+  print
 
@@
 
-student$course_score <- gamma_descriptions$k35     %>%
+student$course_score <- clean_models$gamma_distribution$k35     %>%
   full_join(student$topic_score, by = "topic")     %>%
@@
     by = c("document" = "Course ID")
-    )
+    ) %>%
+  print
 ```

### 2019-02-27 compare SR by hand and with CSPADE.R
use a list to manipulate textual data (instead of multiple dataframes)

@@ -1,0 +1,50 @@
+SR$PF <- d_transcript_cum %>%
+  
+  # rhs
+  unnest(
+    rhs,
+    .drop = FALSE
+  ) %>%
+  filter(
+    str_detect(rhs, "pass|fail")
+  ) %>%
+  
+  # lhs
+  unnest(
+    lhs,
+    .drop = FALSE
+  ) %>%
+  filter(
+    str_detect(lhs, "pass|fail")
+  ) %>%
+  
+  # rule
+  unite(
+    col = "rule",
+    lhs, rhs,
+    sep = " => "
+  ) %>%
+  
+  # rule support
+  count(
+    rule
+  ) %>%
+  mutate(
+    support = n / n_students
+  ) %>%
+  
+  # regular fucntions
+  clean_rules %>%
+  
+  compute_rhs.support(
+    data_support = d_support$PF_HL,
+    type_rule    = rate.fail
+  ) %>%
+  
+  compute_conf_lift %>%
+  
+  # lhs not, rhs low
+  filter(
+    str_detect(lhs, "fail"),
+    str_detect(rhs, "fail"),
+  )

### 2019-02-27 Pillar 2 - Topic Modeling.Rmd
Comment on recommender Systems
tidy github output

--- 2019-02-26 Pillar 2 - Topic Modeling.Rmd
@@
 
-```{r setup, include = T}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
@@
 
-```{r library, message = F}
+```{r library, message = FALSE}
 library(tidyverse)
@@
 # Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
-For `d_description` and `d_overview`, we keep only the most recent year.
 ```{r import data}
@@
 ## Functions for Generating Barplots and Word Clouds
-The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
+
 ```{r compute_tf_idf, cache = TRUE}
@@
 
-The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
 ```{r plot_tf_idf}
@@
 ## Course Level
-The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
-We apply the function to `id_plot` and pipe it to produce graphs.
 ```{r tf-idf course, cache = TRUE}
@@
 # LDA
-The function `my_cast_tdm` casts our dataframes into a tdm.
+
 ```{r my_cast_tdm}
@@
 ## Ideal Number of Topics (RUN ON UM COMPUTER)
-To decide the number of topics to discover, we run (four) three different tests.
 
-First we set the control for the test.
 ```{r controls}
@@
 ```
-The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
+
 ```{r function my_FindTopicsNumber }
@@
 ```
-We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
+
 ```{r description topics, cache = TRUE}
@@
 
-We run the test for overview, documeting its duration. 
 ```{r overview topics, cache = TRUE}

### 2019-02-28 Pillar 2 - Topic Modeling.Rmd
output LDA models UCM computers

--- 2019-02-26 Pillar 2 - Topic Modeling.Rmd
@@
 ```{r LDA fit, cache = TRUE}
-n_topics <- 35
+n_topics <- c(35, 35, 40)
 levels   <- c("description", "overview", "manual")
@@
 
-for(level in levels){
+for(i in seq_along(n_topics)){
 
-  dataset   <- get(paste("d", level, "cast", sep = "_"))
+  dataset   <- get(paste("d", levels[i], "cast", sep = "_"))
 
@@
     x       = dataset,
-    k       = n_topics,
+    k       = n_topics[i],
     method  = "Gibbs",
@@
 
-  nam <- paste("LDA", level, n_topics, sep = "_")
+  nam <- paste("LDA", levels[i], n_topics[i], sep = "_")
 

### 2019-02-28 Topic Scores.Rmd
update names upload files

--- 2019-02-20 Topic Scores.Rmd
@@
 ##LDA_models
-load("Output/LDA_overview.RDATA")
-
-#
-##Topic Models test for ideal number of topics
-load("Output/LDA_ntopics_description.RDATA")
-load("Output/LDA_ntopics_overview.RDATA")
+#load("Output/LDA_overview.RDATA") #replace with underneath
+load("Output/topic_model.RDATA")
 
@@
 ```
+### Saving files for APP
+```{r keywords}
+load("Output/topic_model.RDATA")
+
+save(list_nam, kw,
+     file = "App/Recommender System/topic_model.RDATA")
+
+rm(list_nam)
+```

### 2019-02-28 App/Recommender System/ui.R
note on names that need to change

@@ -9,8 +9,10 @@ library(shiny)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
-load("LDA_overview.RDATA")
-load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN 
+load("LDA_overview.RDATA")        #Replace with LDA final model (below) 
+#load("topic_model.RDATA")
+
+load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN LDA model 
 
 # set seed
 set.seed(1)

### 2019-02-28 Pillar 2 - Topic Modeling.Rmd

--- 2019-02-26 Pillar 2 - Topic Modeling.Rmd
@@
 
-From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics.
+From the results we see that the ideal number of topics is somewhere between 35 and 40.
+We train our models on 35 topics.
+Then we save them in the `Output`folder and in the ``Recommender System` folder.
 ```{r LDA fit, cache = TRUE}
-n_topics <- 35
+n_topics <- c(35, 35, 40)
 levels   <- c("description", "overview", "manual")

### 2019-02-28 Topic Scores.Rmd
cleaning code

--- 2019-02-27 Topic Scores.Rmd
@@
 #
-##d_course and d_transcript
+##Import d_course and d_transcript
+load("Output/data_general.RDATA")
 load("Output/data_pillar_1.RDATA")
@@
 #
-##LDA_models
-load("Output/LDA_overview.RDATA")
+##Import LDA_models
+load("Output/topic_model.RDATA")
 
-#
-##Topic Models test for ideal number of topics
-load("Output/LDA_ntopics_description.RDATA")
-load("Output/LDA_ntopics_overview.RDATA")
+rm(lists, d_AoD, d_assessment, d_ILO)
+```
+##Models in list:
+```{r models in list}
+LDA_models <- list()
+LDA_models$description <- LDA_description_35
+LDA_models$overview <- LDA_overview_35
+LDA_models$manual <- LDA_manual_40
 
+rm(LDA_description_35, LDA_overview_35, LDA_manual_40)
 ```
@@
   tidy(results, matrix = "beta")           %>%
-    mutate(topic = paste("Topic", topic)) %>%
-      arrange(topic, desc(beta))
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(beta) )
 
@@
   tidy(results, matrix = "gamma")          %>%
-    mutate(topic = paste("Topic", topic)) %>%
-      arrange(topic, desc(gamma))
-
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(gamma) )
 }
@@
 ```{r getting beta and gamma}
-# k=10, 20, 35
-beta_description <- lapply(
-  clean_models,
+distribution <- list()
+
+distribution$beta <- lapply(
+  LDA_models,
   get_beta
@@
 
-gamma_descriptions <- lapply(
-  LDA_model,
+distribution$gamma <- lapply(
+  LDA_models,
   get_gamma
@@
 ```
+
 ##Inspect topics
 ```{r inspect topics}
-topics <- clean_models$beta_distribution$k10 %>%
+inspect_topics <- function(d_beta = distribution$beta){
+  d_beta %>%
     group_by(topic) %>%
@@
 
+}
+
+topics <- lapply(
+  distribution$beta,
+  inspect_topics
+)
+
 #
 ##View
-View(topics)
+#View(topics$manual)
 
-```
-## simulating students and key words
-```{r student simulation}
-terms <- unique(beta_description$k35$term)
-
-student <- list()
-student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy")
-student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable")
-```
-
-##getting top courses per student
-```{r topic score student}
-student$topic_score <- clean_models$beta_distribution$k35 %>%
-  filter(term %in% student$kw_climate)       %>%
-  group_by(topic)                           %>% #maybe we can do this with transcripts afterwards
-  summarize(B_score= sum(beta))             %>%
-  ungroup()                                 %>%
-  mutate(Total_b      = sum(B_score),
-         B_proportion = B_score/Total_b)    %>%
-  arrange(desc(B_score)) %>%
-  print
-
-```
-
-##Getting courses
-```{r course_score}
-
-student$course_score <- clean_models$gamma_distribution$k35     %>%
-  full_join(student$topic_score, by = "topic")     %>%
-  mutate(X = gamma * B_proportion)                 %>%
-  group_by(document)                               %>%
-  summarise(course_score = sum(X))                 %>%
-  arrange(desc(course_score))                      %>%
-  left_join(
-    select(d_course, `Course ID`, `Course Title`),
-    by = c("document" = "Course ID")
-    ) %>%
-  print
-```
-
-###View
-```{r View course}
-View(student$topic_score)
-View(student$course_score)
-```
-
-##Explaining outcome
-###key words contribution to topic b_score
-```{r topic score student}
-#
-## standardizing function (within topic)
-standardize <- function (col) {
-  col/sum(col)
-}
-
-#
-##key word Contributions to Topic
- kw_to_topics <- beta_description$k35                                 %>%
-  filter(term %in% student$kw_policy)                                 %>%
-  arrange(topic, desc(beta))                                          %>%
-  group_by(topic)                                                     %>%
-  mutate(beta_sum=sum(beta),
-         beta_rank=beta/beta_sum)                                     %>%
-  select(-beta_sum, -beta)
-```
-
-###Topic contribution to course
-```{r course_score}
-#
-##Extracts recommended courses n = 5
-my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
-  pull(document)
-
-#
-## Topic contribution to course
-key_words <- gamma_descriptions$k35                             %>%
-  filter(document %in% my_courses)                 %>%
-  arrange(document, gamma)                         %>%
-  full_join(kw_to_topics, by = "topic" ) %>%
-  arrange(document, desc(gamma), desc(beta_rank) ) %>%
-  group_by(document #, 
-           #gamma
-           )                                       %>%
-  filter(row_number() %in% 1:3)                    %>%  #makes most sense with just 1 kw # group_by(document) %>% filter(row_number() %in% 1:9) 
-  group_by(document)                               %>%
-  summarise(key_words = list(Reduce(f= c,
-                               x = term)))
 ```
@@
 ```{r}
-top_words <- beta_description$k35 %>%
+get_top_words <- function(d_beta, n = 3){
+  d_beta %>%
     group_by(topic) %>%
-  top_n(3, beta) %>%
+    top_n(n, beta) %>%
     pull(term)%>%
     unique
+}
 
-kw_stopwords =c(
-  "student", "skill", "academic", "bate", "participant", "gain", "primarily", "main", "2016", "action", "level", "issue",
-  "concept", "close", "day", "edition", "primary", "project", "method", "apply", "busy", "address", "role", "post", "oxford",
-  "cuss", "lecture", "pbl",
-    #unsure:
-  "theory", "search", "perspective"
+kw <- lapply(
+  distribution$beta,
+  get_top_words
 )
-kw <- setdiff(top_words, kw_stopwords)
+```
+###Convenience vectors
+```{r}
+# set seed
+set.seed(1)
 
-save(kw, file="App/Recommender System/LDA_keyword_DELETE_.RDATA")
+#
+## All courses
+course_all <- d_course %>%
+  inner_join(
+    d_transcript,
+    by = "Course ID"
+  ) %>%
+  distinct(
+    `Course ID`
+  ) %>%
+  # remove semester abroad, skills and projects
+  filter(
+    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
+  ) %>%
+  pull
+
+#
+##courses following_semester
+course_following_semester <- sample(
+  x       = course_all,
+  size    = 60,
+  replace = FALSE
+  ) %>% sort
 ```
+
+### Saving files for APP
+```{r keywords}
+save(distribution, kw, course_all, course_following_semester,
+     file = "App/Recommender System/topic_model.RDATA")
+```

### 2019-02-28 App/Recommender System/server.R
outsources convenience vectors

@@ -5,7 +5,8 @@ library(hunspell)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
-load("LDA_overview.RDATA")
+#load("LDA_overview.RDATA")
+load("topic_model.RDATA")
 
 
 
@@ -262,35 +263,8 @@ function(input, output) {
     #
     # Set up
     
-    # Topic model
-    # get_beta <- function(results){
-    #   
-    #   tidytext::tidy(results, matrix = "beta") %>%
-    #     mutate(topic = paste("Topic", topic)) %>%
-    #     arrange(topic, desc(beta))
-    #   
-    # }
-    # 
-    # get_gamma <- function(results){
-    #   
-    #   tidytext::tidy(results, matrix = "gamma") %>%
-    #     mutate(topic = paste("Topic", topic)) %>%
-    #     arrange(topic, desc(gamma))
-    #   
-    # }
-    # 
-    # beta_distribution <- lapply(
-    #   LDA_model,
-    #   get_beta
-    #   )
-    # 
-    # gamma_distribution <- lapply(
-    #   LDA_model,
-    #   get_gamma
-    #   )
-    
-    beta_distribution <- clean_models$beta_distribution 
-    gamma_distribution <- clean_models$gamma_distribution
+    beta_distribution <- distribution$beta$manual 
+    gamma_distribution <- distribution$gamma$manual
     
     # Key words
     key_words_additional <- c(
@@ -317,7 +291,7 @@ function(input, output) {
     # Course recommendation
     student <- list()
     
-    student$topic_score <- beta_distribution$k35 %>%
+    student$topic_score <- beta_distribution %>%
       
       # Topic score
       filter(
@@ -333,7 +307,7 @@ function(input, output) {
       
       # Course score
       full_join(
-        gamma_distribution$k35,
+        gamma_distribution,
         by = "topic"
         ) %>%
       group_by(
@@ -352,12 +326,12 @@ function(input, output) {
       
       # Key words per recommendation
       left_join(
-        gamma_distribution$k35,
+        gamma_distribution,
         by = "document"
       ) %>%
       
       left_join(
-        beta_distribution$k35,
+        beta_distribution,
         by = "topic"
         ) %>%
      

### 2019-02-28 App/Recommender System/ui.R

@@ -9,35 +9,10 @@ library(shiny)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
-load("LDA_overview.RDATA")        #Replace with LDA final model (below) 
-#load("topic_model.RDATA")
+#load("LDA_overview.RDATA")        #Replace with LDA final model (below) 
+load("topic_model.RDATA")
 
-load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN LDA model 
-
-# set seed
-set.seed(1)
-
-# for convenience
-course_all <- d_course %>%
-  inner_join(
-    d_transcript,
-    by = "Course ID"
-  ) %>%
-  distinct(
-    `Course ID`
-  ) %>%
-  # remove semester abroad, skills and projects
-  filter(
-    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
-  ) %>%
-  pull
-
-course_following_semester <- sample(
-  x       = course_all,
-  size    = 60,
-  replace = FALSE
-  ) %>% sort
-
+#load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN LDA model above
 
 
 #
@@ -105,7 +80,7 @@ navbarPage(
         checkboxGroupInput(
           inputId  = "key_words",
           label    = "Academic Interest",
-          choices  = sort(kw),
+          choices  = sort(kw$manual),
           selected = c("international", "economic", "conflict", "develop", "policy"),
           inline   = TRUE
           ),

### 2019-02-28 Data Preparation.Rmd
d_course saved in pillar1 data

@@
      file = "Output/data_general.RDATA")
-save(d_transcript,
+save(d_transcript, d_course,
      file = "Output/data_pillar_1.RDATA")

### 2019-02-28 Topic Scores.Rmd
change name of file

@@
 ```
+
 ##Models in list:
@@
 save(distribution, kw, course_all, course_following_semester,
-     file = "App/Recommender System/topic_model.RDATA")
+     file = "App/Recommender System/data_topic_models.RDATA")
 ```

### 2019-02-28 App/Recommender System/server.R
clean load area

@@ -5,8 +5,7 @@ library(hunspell)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
-#load("LDA_overview.RDATA")
-load("topic_model.RDATA")
+load("topic_model.RDATA") #NOT SAME AS FILE IN OUTPUT #contains distribution, kw, course_all, course_following_semester.
 
 
 

### 2019-02-28 App/Recommender System/ui.R
clean load area

@@ -9,10 +9,7 @@ library(shiny)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
-#load("LDA_overview.RDATA")        #Replace with LDA final model (below) 
-load("topic_model.RDATA")
-
-#load("LDA_keyword_DELETE_.RDATA") #TO DELETE, THIS SHOULD BE INCLUDED IN LDA model above
+load("topic_model.RDATA") #contains distribution, kw, course_all, course_following_semester.
 
 
 #

### 2019-03-01 Data Preparation.Rmd
add d_course and d_transcript to Pillar_2

--- 2019-02-27 Data Preparation.Rmd
@@
      file = "Output/data_pillar_1.RDATA")
-save(d_text,
+save(d_text, d_course, d_transcript,
      file = "Output/data_pillar_2.RDATA")

### 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
comment for jerry

@@
 ---
+
+COMMENTS: 
+Q. Jerry -> For preprocessing (selecting vocabulary), how do we assign words that appear in only one document to a topic? Does it make sense to remove them?
 
@@
 # Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
+We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
 `d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
@@
 
+To prepare the output of pillar two, we will need d_course. Thus we load the environment `output/data_pillar_1.RDATA`. It contains the datasets d_course and d_transcript.
+```{r}
+#
+##Import d_course and d_transcript
+load("Output/data_pillar_1.RDATA")
+```
 # TF-IDF

### 2019-03-01 App/Recommender System/server.R
new error message for not found students

@@ -13,7 +13,7 @@ function(input, output) {
   #
   ##Set up
   
-  #Return student function
+  # Helper function: Return student
   student_trans <- function(d_student){
  
     # Student profile
@@ -239,8 +239,9 @@ function(input, output) {
         wt = confidence
         )
     
-    
-    if(nrow(rules) == 0){
+    if(nrow(student$transcript)==0){
+      "ERROR: id not found- we need new students ID's before running this"
+    }else if(nrow(rules) == 0){
       
       "No red flag"
       
@@ -263,6 +264,8 @@ function(input, output) {
     
   })
   
+  #
+  ##Course Recommendation
   output$course_recommendation <- renderUI({
     
     

### 2019-03-01 Data Preparation.Rmd
use list and `map()` functions to simplify code

--- 2019-02-27 Data Preparation.Rmd
@@
 ```{r import list}
-lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
+list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
   map(na.omit)
 
-lists <- list()
-
-lists$Assessment      <- lists_brut$Assessment
-lists$AoD             <- lists_brut$Aim
-
 # selection of most important types of assessment an AoD to keep plots clear
-lists$Assessment_plot <- lists$Assessment[lists_brut$`Assessment for Plot` == 1]
-lists$AoD_plot        <- lists$AoD       [lists_brut$`Aim for Plot`        == 1]
-
-rm(lists_brut)
+list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %>% print
+list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %>% print
 ```
@@
     ) %>%
+
+  # Transform data into tidy format to facilitate manipulation
   gather(
@@
     ) %>%
-  arrange(
-    `Course ID`
-    ) %>%
   print
@@
 
-d_AoD_ILO <- d_ILO %>%
+d_AoD_from_ILO <- d_ILO %>%
   rename(
@@
 ```{r import corpus_catalogues, cache = TRUE}
+# helper function
+read_in_pdfs <- function(file){
+
+  Corpus(
+    x             = DirSource(file),
+    readerControl = list(reader = readPDF(control = list(text = "-layout")))
+    ) %>%
+
+    # turn corpus into a list to facilitate manipulation
+    as.list %>%
+    unname
+
+}
+
 d_text <- list()
 
-d_text$catalogues <- Corpus(
-  x             = DirSource("./Input/Catalogues"),
-  readerControl = list(reader = readPDF(control = list(text = "-layout")))
-  )
+d_text$catalogues <- "./Input/Catalogues" %>%
+  read_in_pdfs %>%
+  map(function(x) x$content)
 ```
@@
 ```{r import corpus_manuals, cache = TRUE}
-d_text$manuals <- Corpus(
-  x             = DirSource("./Input/Manuals 2017-18"),
-  readerControl = list(reader = readPDF(control = list(text = "-layout")))
-  )
+extract_code <- function(string) string %>% str_sub(start = 1, end = 7) # helper functions
+
+d_text$manuals <- "./Input/Manuals 2017-18" %>%
+  read_in_pdfs %>%
+
+  # turn list into a tibble to facilitate manipulation
+  tibble(manuals = .) %>%
+
+  transmute(
+    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
+    year        = "2017-2018",
+    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
+    ) %>%
+  print
 ```
@@
 ```{r import d_transcript, cache = TRUE}
-d_transcript1 <- read_csv(
-  file = "Input/Raw Grades/grades1.csv",
-  col_types = cols(
+col_parsing <- cols(
+  `Student Number`                      = "c",
   `Program (Abbreviation)`              = "c",
   `Appraisal Status`                    = "c",
-    `Module Booking Reason (Description)` = "c"
-    )
-  )
-
-d_transcript2 <- read_csv(
-  file = "Input/Raw Grades/grades2.csv",
-  col_types = cols(
-    `Program (Abbreviation)`              = "c",
-    `Appraisal Status`                    = "c",
+  `Module Booking Reason (Description)` = "c",
   `Object name`                         = "c",
@@
   )
-  )
 
-d_transcript <- rbind(d_transcript1, d_transcript2)
+read_csv_own_parsing <- function(file) file %>% read_csv( col_types = col_parsing) # helper function
 
-rm(d_transcript1, d_transcript2)
+d_transcript <- list("Input/Raw Grades/grades1.csv", "Input/Raw Grades/grades2.csv") %>%
+  map(read_csv_own_parsing) %>%
+  bind_rows
+
+rm(col_parsing, read_csv_own_parsing)
 ```
@@
 ```{r d_AoD_ILO}
-d_AoD_ILO
+d_AoD_from_ILO
 ```
@@
 ```{r d_AoD_assessment}
-d_AoD_assessment <- d_assessment %>%
+d_AoD_from_assessment <- d_assessment %>%
   left_join(
@@
 d_AoD <- rbind(
-  d_AoD_ILO        %>% select(`Course ID`, AoD),
-  d_AoD_assessment %>% select(`Course ID`, AoD)
+  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
+  d_AoD_from_assessment %>% select(`Course ID`, AoD)
   ) %>%
@@
 
-rm(d_AoD_assessment, d_AoD_ILO)
+rm(d_AoD_from_assessment, d_AoD_from_ILO)
 ```
@@
 ```{r d_course detail}
-d_ILO_detail <- d_ILO %>%
-  count(
-    `Course ID`, 
-    sort = TRUE
-    ) %>%
-  rename(
-    n_ILO = n
-    ) %>%
-  print
+# helper function
+count_and_paste <- function(data, var, colnam1, colnam2){
 
-d_assessment_detail <- d_assessment %>%
+  data %>%
     group_by(
@@
       ) %>%
-  summarise(
-    n_assessment = n(),
-    `Assessments Covered` = paste(Assessment, collapse = ", ")
-    ) %>%
-  print
+    summarize(
+      !!ensym(colnam1) := n_distinct(!!enquo(var)),
+      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
+    )
 
-d_AoD_detail <- d_AoD %>%
-  group_by(
-    `Course ID`
-    ) %>%
-  summarise(
-    n_AoD = n(),
-    `AoD Covered` = paste(AoD, collapse = ", ")
-    ) %>%
-  print
+}
+
+# helper function
+join_by_course_ID <- function(data1, data2){
+
+  data1 %>%
+    left_join(
+      y = data2,
+      by = "Course ID"
+    )
+
+}
 ```
@@
 d_course <- d_course %>%
-  left_join(d_ILO_detail       , by = "Course ID") %>%
-  left_join(d_assessment_detail, by = "Course ID") %>%
-  left_join(d_AoD_detail       , by = "Course ID") %>%
+  join_by_course_ID( d_AoD %>% count_and_paste(AoD, n_AoD, `AoD Covered`) %>% print) %>%
+  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`) ) %>%
+  join_by_course_ID( d_ILO %>% count_and_paste(Objectives, n_ILO, `ILO Covered`        ) ) %>%
   select(
@@
 
-rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
+rm(count_and_paste, join_by_course_ID)
 ```
@@
 ```{r create UGR2000}
-
-d_course_UGR_2000 <- d_course %>%
+UGR_2000 <- d_course %>%
   filter(
@@
 d_course <- d_course %>%
-  rbind(
-    d_course_UGR_2000
-    )
+  rbind(UGR_2000)
 
-print(
-  d_course %>%
-    filter(
-      str_detect(`Course ID`, "UGR")
-      )
-  )
+print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )
 
-rm(d_course_UGR_2000)
+rm(UGR_2000)
 ```
@@
 # Set up
-years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
+years <- paste0(2014:2018, "-", 2015:2019)
 
@@
   "^Projects? \\(PRO\\)",
-  "^Undergraduate Research", "UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research",
+  "^Undergraduate Research", "UCM Undergraduate\r\n ? ?Research",
   "Appendix"
@@
 
+#
+# helper functions
 is_start_overview_section  <- function(string) string %>% str_detect(pattern = "^Core Courses \\(COR\\)")
@@
 
-extract_code               <- function(string) string %>% str_sub(start = 1, end = 7)
 is_overview_start          <- function(string) string %>% extract_code %>% str_detect(pattern = overview_start)
@@
 
-  # if the page is the start of an overview,
   if(page %>% is_overview_start){
 
-    # then, if the following page is also the start of an overview, the overview is simply the current page
-    if(page_following %>% is_overview_start | is.na(page_following)){
+    if(page_following %>% is_overview_start | is.na(page_following))   page # include possibility of `is.na(page_following)` for last page of overview section
+    else                                                               paste(page, page_following)
 
-      page
-
-    # if the following page is also the start of an overview, the overview spans over the current and the following page
-    }else{
-
-    paste(page, page_following)
-
-    }
-
-  # if the page is not the start of an overview, return an NA
-  }else{
-
-    NA_character_
-
-  }
+  }else                                                                NA_character_   # if the page is not the start of an overview, return an NA
 
@@
 #
-# Loop
+# main function
+extract_overview <- function(page){
 
-for(i in seq_along(d_text$catalogues)){
-
-  catalogue_all <- d_text$catalogues %>%
-
-    # extract catalogue from corpus
-    .[[i]] %>%
-    content %>%
-
-    # create a tibble
-    tibble(
-      page = .
-      ) %>%
+  # create tibble to facilitate manipulation
+  page %>% 
+    tibble(page = .) %>%
 
@@
     mutate(
-      page_n                    = row_number(), 
       is_start_overview_section = page %>% is_start_overview_section,
       is_end_overview_section   = page %>% is_end_overview_section
-      )
+      ) %>%
 
-  # Check that there is one and only one is_start_overview_section and no more than 1 is_end_overview_section.
-  if(sum(catalogue_all$is_start_overview_section) == 0) print("error: no overview_section_start"      )
-  if(sum(catalogue_all$is_start_overview_section) >  1) print("error: multiple overview_section_start")
-  if(sum(catalogue_all$is_end_overview_section  ) >  1) print("error: multiple overview_section_end"  )
+    # I have checked that there is one and only one is_start_overview_section and no more than 1 is_end_overview_section
+      # if(sum(catalogue_all$is_start_overview_section) == 0) print("error: no overview_section_start"      )
+      # if(sum(catalogue_all$is_start_overview_section) >  1) print("error: multiple overview_section_start")
+      # if(sum(catalogue_all$is_end_overview_section  ) >  1) print("error: multiple overview_section_end"  )
 
-  # Extract overview section from catalogue
-  catalogue_overview <- catalogue_all %>%
-
-    # identify and filter the pages that are in the overview section (is_overview_section)  
+    # filter the overview section
     mutate(
@@
       ) %>%
+    filter(is_overview_section) %>%
 
-    filter(
-      is_overview_section
-      ) %>%
+    # exclude headers to only keep the overviews themselves
+    filter(! page %>% is_header) %>%
 
-    # exlude headers (is_to_exclude) as well as the first and the last page 
-    filter(
-      ! page %>% is_header
-      ) %>%
-
-    select(
-      - c(
-        is_start_overview_section, is_end_overview_section,
-        is_after_start_overview_section, is_before_end_overview_section,
-        is_overview_section
-        )
-      )
-
-  d_text$overview[[i]] <- catalogue_overview %>%
+    # paste current page and following page (`lead(page)`) if overview is two page long
     transmute(
       text        = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
-      `Course ID` = text %>% extract_code,
-      year          = years[i]
+      `Course ID` = text %>% extract_code
       )
@@
 
+d_text$overview <- d_text$catalogues %>%
+
+  # extract the individual course overviews for each catalogue
+  map(extract_overview) %>%
+
+  # add the year to each observation to keep track of the evolution of the catalogue oevr time
+  map2(
+    .y = years,
+    .f = function(x, year) x %>% mutate(year = year)
+    ) %>%
+
+  # turn list into a tibble to facilitate manipulation
+  bind_rows(d_text$overview) %>%
+  print
+
 d_text <- d_text[c("overview", "manuals")]
-d_text$overview <- bind_rows(d_text$overview)
 
 rm(
-  is_end_overview_section, is_header, is_overview_start, is_start_overview_section, paste_if_two_page_overview,
-  headers, i, overview_start, years,
-  catalogue_all, catalogue_overview
+  headers, overview_start,
+  is_start_overview_section, is_end_overview_section, is_header, is_overview_start,
+  paste_if_two_page_overview, extract_overview,
+  years
   )
@@
 Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
-```{r d_manual}
-d_text$manuals <- d_text$manuals %>%
-  tidy %>%
-  select(
-    id, text
-    ) %>%
-  mutate(
-    `Course ID` = id %>% extract_code
-    ) %>%
-  select(
-    -id
-    ) %>%
-  print
-```
 
@@
 ```{r tidy d_description}
+# helper function
 tidy_text <- function(df){
@@
 
-d_text <- d_text %>% map(tidy_text)
+d_text <- d_text %>% map(tidy_text) %>% print
+
+rm(tidy_text)
 ```
@@
 Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
-```{r stemming dictionary, cache = TRUE}
+```{r dictionary, cache = TRUE}
+# helper function
 stem_hunspell <- function(term) {
@@
 ```{r stemming data sets}
+# helper function
 stem_with_dictionary <- function(data){
@@
 
-d_text <- d_text %>% map(stem_with_dictionary)
+d_text <- d_text %>% map(stem_with_dictionary) %>% print
 
@@
 
-d_text <- d_text %>% 
-  map(remove_sw) %>% 
-  print
+d_text <- d_text %>% map(remove_sw) %>% print
 

### 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd

--- 2019-02-27 Pillar_2_-_Topic_Modeling.Rmd
@@
 # Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
-For `d_description` and `d_overview`, we keep only the most recent year.
+We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
 ```{r import data}

### 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
old version

@@
 
+##OLD Version:
 ```{r LDA fit, cache = TRUE}
@@
 ```
-
+#end of old version
 ## Visualization

### 2019-03-01 Data Preparation.Rmd
update name

--- 2019-03-01 Data Preparation.Rmd
@@
 ```{r}
-save(d_course, lists, d_AoD, d_assessment, d_ILO,
+save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
      file = "Output/data_general.RDATA")

### 2019-03-01 Pillar 2 - Topic Modeling.Rmd
eval=f

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
+knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
+                      eval = FALSE)
 ```
 
-```{r library, message = FALSE}
+```{r library, message = FALSE, eval = TRUE}
 library(tidyverse)
@@
 For `d_description` and `d_overview`, we keep only the most recent year.
-```{r import data}
+```{r import data, eval = TRUE}
 load("output/data_pillar_2.RDATA")
@@
 # Only keep course descriptions and overviews from most recent year
-d_description <- d_description %>%
-  filter(
-    `Academic Year` == "2018-2019"
-  )
-
-d_overview <- d_overview %>%
-  filter(
-    `Academic Year` == "2018-2019"
-  )
+d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
 ```
@@
 The function `my_cast_tdm` casts our dataframes into a tdm.
-```{r my_cast_tdm}
+```{r my_cast_tdmxxxxx}
 my_cast_tdm <- function(data, level) data %>%
@@
 First we set the control for the test.
-```{r controls}
+```{r controls, eval = TRUE}
 my_control <- list(
@@
 
-  burnin = 100,
+  burnin = 1000,
   iter   = 5000,
@@
 Then we save them in the `Output`folder and in the ``Recommender System` folder.
-```{r LDA fit, cache = TRUE}
+
+#NEW
+# LDA
+The function `my_cast_tdm` casts our dataframes into a tdm.
+```{r my_cast_tdm, eval = TRUE}
+my_cast_tdm <- function(data) data %>%
+  count(`Course ID`, word) %>%
+  cast_dtm(`Course ID`, word, n)
+
+d_cast <- d_text %>% map(my_cast_tdm)
+
+rm(my_cast_tdm)
+```
+
+```{r my_LDA, eval= TRUE}
+
+#my_LDA
+my_LDA <- function(n_topics, corpus){
+
+  LDA_model <- LDA(
+    x       = corpus,
+    k       = n_topics,
+    method  = "Gibbs",
+    control = my_control
+    )
+}
+
+```
+
+```{r LDA fit, cache = TRUE, eval = TRUE}
+topic_model <- tibble(
+
+  n_topic = seq(from = 2, to = 80, by = 2)
+
+  ) %>%
+
+  mutate(
+    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
+    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
+  )
+```
+
+```{r saving models, eval= TRUE}
+save(topic_model,
+     file = "Output/topic_model.RDATA")
+
+save(topic_model,
+     file = "App/Recommender System/topic_model.RDATA")
+```
+
+```{r LDA fitxxxxxxx, cache = TRUE}
 n_topics <- c(35, 35, 40)

### 2019-03-01 Data Preparation.Rmd
clean d_student

--- 2019-03-01 Data Preparation.Rmd
@@
 ## Student Data
+
+* Is `Academic Work ID` a unique ID number?
+
+* questions...
+
 (In this section we use: `d_transcript`- contains the transcript information of students as was provided.
@@
 ```{r}
+#
+# Set up
+UCM_course <- d_text$overview$`Course ID` %>%
+  unique %>% 
+  paste(collapse = "|")
+
+# helper function
+is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)
+
 d_transcript <- d_transcript %>%
 
-  # for simplicity, only keep courses of UCM program
+  # for simplicity, we only keep *UCM courses* taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (7501)
   filter(
-    `Program (Abbreviation)` == "7501",
-    !str_detect(`Module (Abbrev.)`, "EXT")
+    `Module (Abbrev.)` %>% is_offered_at_UCM,
+    `Program (Abbreviation)` == "7501"
   ) %>%
 
-  # folowing guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type`          == "7055"
+  # The dataset has multiple rows for each student - course following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
   filter(
@@
   # Remove variables with only one value
-  select_if(
-    function(x) n_distinct(x) > 1
-    ) %>%
-
-  # Remove variables with more than 99% NA
-  select_if(
-    function(x) mean(is.na(x)) < 0.99
+  discard(
+    function(x) n_distinct(x) == 1
   ) %>%
@@
 
-    Grade = case_when(
-      is.na(Grade)  ~ "0",
-      Grade == "NG" ~ "0",
-      TRUE          ~ str_replace(
-        Grade,
-        pattern     = ",",
-        replacement = "."
-      )
-    ) %>% 
+    Grade = if_else(is.na(Grade) | Grade == "NG", "0", Grade) %>% str_replace(",", ".") %>% 
       as.numeric
@@
   ) %>%
-
-  # if student took resit (recorder in same year and period), only keep failing grade
-  # group_by(
-  #   `Student ID`,
-  #   `Course ID`,
-  #   Year,
-  #   Period
-  #   ) %>%
-  # summarize(
-  #   Grade = min(Grade)
-  #   ) %>%
-  # ungroup %>%
 
@@
 
-    time = paste(
-      Year_numerical, substr(Period, 1, 1),
-      sep = ""
-      ),
+    time = str_c(Year_numerical, substr(Period, 1, 1), sep = ""),
 
-    `Academic Year`= paste(
-      Year_numerical, Year_numerical + 1,
-      sep = "-")
+    `Academic Year`= str_c(Year_numerical, Year_numerical + 1, sep = "-")
 
-    )
-```
+  ) %>%
 
-```{r}
-print(d_transcript)
+  select(
+    - Year_numerical,
+    - Period
+    ) %>%
+
+  add_count(
+    `Student ID`, `Course ID`, time,
+    sort = TRUE
+    ) %>%
+  print
+
+  # if student took resit (recorder in same year and period !!!NOT TRUE!!!), only keep failing grade 
+  # group_by(
+  #   `Student ID`,
+  #   `Course ID`,
+  #   Year,
+  #   Period
+  #   ) %>%
+  # summarize(
+  #   Grade = min(Grade)
+  #   ) %>%
+  # ungroup
 ```

### 2019-03-11 Data Preparation.Rmd

--- 2019-03-01 Data Preparation.Rmd
@@
 
+##### Extracting Descriptions
+
+Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
+The description section contains a brief description (200-500 words) of the content of the course.
+To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
+The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
+The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
+Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
+A handful overviews do not contain a *Literature* section.
+For these, the section *Instructional Format* marks the end of the description section.
+
+```{r extracting description, eval = FALSE}
+
+# Setup
+symbol_to_line <- c("\r\n", "\n") %>% paste(collapse = "|")
+start_descrip  <- c("^Description", "^Course Description") %>% paste(collapse = "|")
+end_descrip    <- c("^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all") %>%  paste(collapse = "|")
+
+# helper functions
+split              <- function(string) string %>% str_split(pattern = "\r\n|\n")
+
+is_start_descrip   <- function(x) x %>% str_detect(pattern = start_descrip           )
+is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )
+is_end_descrip_bis <- function(x) x %>% str_detect(pattern = "^Instructional format$")
+
+# main function
+extract_description <- function(page){
+
+  page %>%
+    split %>%
+    tibble(line = .) %>%
+
+    mutate(
+      is_start_descrip = line %>% is_start_descrip,
+      is_end_descrip   = line %>% is_end_descrip
+    ) %>%
+
+    mutate(
+      is_end_descrip = if_else(any(is_end_descrip), is_end_descrip, line %>% is_end_descrip_bis)
+    ) %>%
+
+    # filter the description section
+    mutate(
+      is_after_start_descrip = cumany( is_start_descrip),
+      is_before_end_descrip  = cumall(!is_end_descrip  ),
+      is_descrip             = is_after_start_descrip & is_before_end_descrip
+      ) %>%
+    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%
+
+    summarise(description = str_c(line, collapse = " ")) %>%
+    pull
+
+}
+
+d_text$overview %>%
+  mutate(
+    description = overview %>% map(extract_description)
+  )
+```
+
 #### Extracting Text: Course Manuals
@@
 ```
-
-# Extra
-
-## Extracting Descriptions
-
-Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
-The description section contains a brief description (200-500 words) of the content of the course.
-To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
-The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
-The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
-Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
-A handful overviews do not contain a *Literature* section.
-For these, the section *Instructional Format* marks the end of the description section.
-
-```{r extracting description, eval = FALSE}
-
-# Setup
-symbol_to_line <- c("\r\n", "\n") %>%
-  paste(collapse = "|")
-start_descrip <- c("^Description", "^Course Description") %>%
-  paste(collapse = "|")
-end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
-                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
-  paste(collapse = "|")
-
-# Loop
-for(course in 1 : nrow(d_description)){
-
-  overview <- d_description$Overview[course]
-
-  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
-  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
-  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
-  # for overviews w/o Literature section, find section Instructional Format.
-  if(is_empty(line_end)){
-    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
-    print(paste("line_end irregular for", d_description$`Course ID`[course],
-                "in catalogue", d_description$`Calendar Year`[course]))
-    } # close if-statement
-
-  description <- paste(overview_by_line[line_start : line_end], collapse = " ")
-
-  d_description$Description[course] <- description
-
-}
-rm(symbol_to_line, start_descrip, end_descrip,
-   course, overview, overview_by_line, line_start, line_end, description)
-print(d_description)
-```

### 2019-03-11 Data Preparation.Rmd
Extract course description from course overview

@@
   print
+
+rm(read_in_pdfs)
 ```
@@
 # Set up
+
+collapse_or <- function(string) string %>% str_c(collapse = "|")
+
 years <- paste0(2014:2018, "-", 2015:2019)
@@
   ) %>%
-  paste(collapse = "|")
+  collapse_or
 
@@
   ) %>% 
-  paste(collapse = "|")
+  collapse_or
 
@@
 # main function
-extract_overview <- function(page){
+extract_overview <- function(catalogue){
 
   # create tibble to facilitate manipulation
-  page %>% 
+  catalogue %>% 
     tibble(page = .) %>%
@@
       `Course ID` = text %>% extract_code
-      )
+      ) %>%
+    filter(!is.na(text))
 
@@
 
-  # add the year to each observation to keep track of the evolution of the catalogue oevr time
+  # add the year to each observation to keep track of the evolution of the catalogue over time
   map2(
@@
 
+#
 # Setup
-symbol_to_line <- c("\r\n", "\n") %>% paste(collapse = "|")
-start_descrip  <- c("^Description", "^Course Description") %>% paste(collapse = "|")
-end_descrip    <- c("^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all") %>%  paste(collapse = "|")
+symbol_to_line <- c("\r\n", "\n") %>% collapse_or
+start_descrip  <- c("^Description", "^Course Description") %>% collapse_or
+end_descrip    <- c(
+  "^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all",
+  "^Instructional format$"
+  ) %>% collapse_or
 
+#
 # helper functions
-split              <- function(string) string %>% str_split(pattern = "\r\n|\n")
+split              <- function(string) string %>% str_split(pattern = "\r\n|\n") %>% .[[1]]
 
@@
 is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )
-is_end_descrip_bis <- function(x) x %>% str_detect(pattern = "^Instructional format$")
 
+#
 # main function
-extract_description <- function(page){
+extract_description <- function(overview){
 
-  page %>%
+  overview %>%
   split %>%
@@
     is_start_descrip = line %>% is_start_descrip,
-      is_end_descrip   = line %>% is_end_descrip
-    ) %>%
-
-    mutate(
-      is_end_descrip = if_else(any(is_end_descrip), is_end_descrip, line %>% is_end_descrip_bis)
+    is_end_descrip   = line %>% is_end_descrip # several ends (matching literature and instructional format) is ok because we choose the first (cumany)
   ) %>%
@@
 
-d_text$overview %>%
+d_text$description <- d_text$overview %>%
   mutate(
-    description = overview %>% map(extract_description)
+    text = text %>% map_chr(possibly(extract_description, "ERROR"))
     )

### 2019-03-11 Data Preparation.Rmd
filter out terms composed of 1 or 2 letters
split big chunk that cleans student data into three smaller chunks for clarity

@@
       by = "word"
+      ) %>%
+    filter(
+      nchar(word) > 2
       )
@@
 Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
+
 ```{r}
@@
 is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)
+```
 
+```{r}
 d_transcript <- d_transcript %>%
@@
 
-  # The dataset has multiple rows for each student - course following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
+  # The dataset has multiple rows for each student - course. Following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
   filter(
@@
     `Appraisal Type`          == "7055" # removes ~ 15 observations
-  ) %>%
+  )
+```
+
+```{r}
+d_transcript <- d_transcript %>%
 
@@
     Grade          = `Grade symbol`
-  ) %>%
+  )
+```
+
+```{r}
+
+d_transcript <- d_transcript %>%
 
@@
 
-    Grade = if_else(is.na(Grade) | Grade == "NG", "0", Grade) %>% str_replace(",", ".") %>% 
+    Grade = if_else(is.na(Grade) | Grade == "NG", "0", Grade) %>% 
+      str_replace(",", ".") %>% 
       as.numeric
@@
     - Period
-    ) %>%
+    )
+```
 
+```{r}
+d_transcript %>%
+
+  # highlight issue: there are several rows with unique student ID - course ID - time combination.
   add_count(
@@
   print
-
-  # if student took resit (recorder in same year and period !!!NOT TRUE!!!), only keep failing grade 
-  # group_by(
-  #   `Student ID`,
-  #   `Course ID`,
-  #   Year,
-  #   Period
-  #   ) %>%
-  # summarize(
-  #   Grade = min(Grade)
-  #   ) %>%
-  # ungroup
 ```

### 2019-03-11 Pillar 2 - Topic Modeling.Rmd
applies get gamma and get betta before saving

@@
 
+```{r getting gamma and beta, eval = TRUE}
+get_beta <- function(results){
+
+  tidy(results, matrix = "beta")           %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(beta) )
+
+}
+
+get_gamma <- function(results){
+
+  tidy(results, matrix = "gamma")          %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(gamma) )
+}
+
+```
+
+```{r applying get_gamma and get_beta, eval = TRUE}
+topic_model_gb <- topic_model %>%
+  transmute(
+    n_topic    = n_topic,
+    g_overview = TM_overview %>% map( .f = get_gamma),
+    g_manual   = TM_manual   %>% map( .f = get_gamma),
+    b_overview = TM_overview %>% map( .f = get_beta),
+    b_manual   = TM_manual   %>% map( .f = get_beta)
+      )
+```
+
+```{r saving tidy models, eval= TRUE}
+save(topic_model_gb,
+     file = "Output/topic_model_gb.RDATA")
+
+save(topic_model_gb,
+     file = "App/Recommender System/topic_model_gb.RDATA")
+```
+
 ```{r saving models, eval= TRUE}

### 2019-03-11 Data Preparation.Rmd
remove words occuring only once or twice in the corpus

@@
       ) %>%
+
+    # remove words of 1 or 2 letters
     filter(
       nchar(word) > 2
-      )
+      ) %>%
+
+    # Remove words occuring once or twice in corpus (usually names, website links or typos)
+    add_count(word) %>%
+    filter(n > 2) %>%
+    select(-n)
 

### 2019-03-11 Data Preparation.Rmd
debug incoherence between data preparation and pillar 1

@@
     `Course ID`    = `Module (Abbrev.)`,
-    Year_numerical =`Academic Year`,
+    Year_numerical = `Academic Year`,
     Period         = `Academic Session`,
@@
 
-  ) %>%
-
-  select(
-    - Year_numerical,
-    - Period
   )

### 2019-03-12 Data Preparation.Rmd
split long chunks into smaller chunks for clarity

@@
 knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
-```
 
-```{r libraries, message = FALSE}
 library(tidyverse)
@@
 
-## Setup
+## List of AoD's and Assessments
 First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
@@
 We also any imported emtpy cells.
-```{r import list}
+```{r list_AoD_assessment}
 list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
@@
 
-```{r import d_course d_assessment and d_ILO, cache = TRUE}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
-  print
+```{r d_course}
+d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>% print
+```
 
+```{r d_assessment}
 d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
@@
     .predicate = is.numeric,
-    as.logical
+    .funs      = as.logical
     ) %>%
@@
   print
+```
 
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
-
+```{r d_AoD_from_ILO}
 d_AoD_from_ILO <- d_ILO %>%
@@
 ## Textual Data
-### Course Catalogues
 In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
 The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
-```{r import corpus_catalogues, cache = TRUE}
+```{r catalogues, cache = TRUE}
 # helper function
@@
 
-### Course Manuals
 To expand our topic modeling of course content, we analyse the material in the course manuals.
@@
 
-```{r import corpus_manuals, cache = TRUE}
-extract_code <- function(string) string %>% str_sub(start = 1, end = 7) # helper functions
+```{r manuals, cache = TRUE}
+# helper functions
+extract_code <- function(string) string %>% str_sub(start = 1, end = 7)
 
@@
 
-```{r import d_transcript, cache = TRUE}
+```{r d_transcript, cache = TRUE}
 col_parsing <- cols(
@@
 
-d_transcript <- list("Input/Raw Grades/grades1.csv", "Input/Raw Grades/grades2.csv") %>%
+d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
   map(read_csv_own_parsing) %>%
@@
 ## Textual Data
-### Extracting Text
+### Extracting Overviews
 In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.
 
-#### Extractin Text: Course Catalogues
 (For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
-
-##### Extracting Overviews
 
@@
 
-```{r extracting overview, cache = TRUE}
-#
+```{r overview set up}
 # Set up
-
 collapse_or <- function(string) string %>% str_c(collapse = "|")
-
-years <- paste0(2014:2018, "-", 2015:2019)
 
@@
 
-#
-# helper functions
+years <- paste0(2014:2018, "-", 2015:2019)
+```
+
+```{r overview helper functions}
+# helper functions in order of use
 is_start_overview_section  <- function(string) string %>% str_detect(pattern = "^Core Courses \\(COR\\)")
@@
 
-#
-# main function
+add_year <- function(x, yr) x %>% mutate(year = yr)
+```
+
+```{r extract_overview}
 extract_overview <- function(catalogue){
@@
 }
+```
 
+```{r overview, cache = TRUE}
 d_text$overview <- d_text$catalogues %>%
 
-  # extract the individual course overviews for each catalogue
   map(extract_overview) %>%
@@
   # add the year to each observation to keep track of the evolution of the catalogue over time
-  map2(
-    .y = years,
-    .f = function(x, year) x %>% mutate(year = year)
-    ) %>%
+  map2(years, add_year) %>%
 
@@
 
+# only keep the overviews and manuals for clarity
 d_text <- d_text[c("overview", "manuals")]
@@
 
-##### Extracting Descriptions
-
+### Extracting Descriptions
 Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
@@
 
-```{r extracting description, eval = FALSE}
-
-#
+```{r description set up}
 # Setup
@@
   ) %>% collapse_or
+```
 
-#
+```{r description helper function}
 # helper functions
-split              <- function(string) string %>% str_split(pattern = "\r\n|\n") %>% .[[1]]
+split              <- function(string) string %>% str_split (pattern = symbol_to_line) %>% .[[1]]
 
-is_start_descrip   <- function(x) x %>% str_detect(pattern = start_descrip           )
-is_end_descrip     <- function(x) x %>% str_detect(pattern = end_descrip             )
+is_start_descrip   <- function(string) string %>% str_detect(pattern = start_descrip )
+is_end_descrip     <- function(string) string %>% str_detect(pattern = end_descrip   )
+```
 
-#
-# main function
+```{r extract_description, eval = FALSE}
 extract_description <- function(overview){
@@
       is_start_descrip = line %>% is_start_descrip,
-    is_end_descrip   = line %>% is_end_descrip # several ends (matching literature and instructional format) is ok because we choose the first (cumany)
+      is_end_descrip   = line %>% is_end_descrip # Having several ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
       ) %>%
@@
 }
-
-d_text$description <- d_text$overview %>%
-  mutate(
-    text = text %>% map_chr(possibly(extract_description, "ERROR"))
-    )
 ```
 
-#### Extracting Text: Course Manuals
-(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))
-
-Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
+```{r description}
+d_text$description <- d_text$overview %>%
+  mutate(text = text %>% map_chr(extract_description))
+```
 
 ### Tidy Text Format
-
 To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
-```{r tidy d_description}
+```{r tidy_text}
 # helper function
@@
 }
+```
 
+```{r tidy d_text}
 d_text <- d_text %>% map(tidy_text) %>% print
@@
 Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
-```{r dictionary, cache = TRUE}
+
+```{r stem}
 # helper function
-stem_hunspell <- function(term) {
+stem <- function(term) {
 
@@
 }
+```
 
-dictionary <- d_text$overview$word %>%
-  union(
-    d_text$manuals$word
-    ) %>%
-  tibble(
-    word = .
-    ) %>%
-  mutate(
-    word_stem = word %>% map_chr(stem_hunspell)
-    )
+```{r dictionary, cache = TRUE}
+dictionary <- union(d_text$overview$word, d_text$manuals$word) %>%
 
-# TODO: "destem" terms by hand: cuss => discuss
-filter(dictionary, word_stem == "cuss")
+  tibble(word = .) %>%
+
+  mutate(word_stem = word %>% map_chr(stem))
 
@@
 ```
+
+```{r destem}
+# TODO: "destem" terms by hand: cuss => discuss
+filter(dictionary, word_stem == "cuss")
+```
+
 Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.
@@
 Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
-```{r stemming data sets}
+```{r stem_with_dictionary}
 # helper function
@@
   data %>%
-    left_join(
-      dictionary,
-      by = "word"
-      ) %>%
+
+    left_join(dictionary, by = "word") %>%
+
     rename(
@@
 }
+```
 
-d_text <- d_text %>% map(stem_with_dictionary) %>% print
+```{r stem d_text}
+d_text <- d_text %>% map(stem_with_dictionary)
 
@@
 Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
-```{r}
+```{r sw_own}
 # Own stop words
-sw_own <- tibble(
-    word = c(
-      as.character(1 : 1e3)
-      )
-    )
+sw_own <- 1 : 1e3 %>% as.character %>% tibble( word = .)
+```
 
+```{r remove_sw}
+# helper function
 remove_sw <- function(data){
@@
   data %>%
-    anti_join(
-      stop_words,
-      by = "word"
-      ) %>%
-    anti_join(
-      sw_own,
-      by = "word"
-      ) %>%
+
+    anti_join(stop_words, by = "word") %>%
+
+    anti_join(sw_own, by = "word") %>%
 
     # remove words of 1 or 2 letters
-    filter(
-      nchar(word) > 2
-      ) %>%
+    filter(nchar(word) > 2) %>%
 
@@
 }
+```
 
+```{r sw d_text}
 d_text <- d_text %>% map(remove_sw) %>% print
@@
 
-```{r}
-#
+```{r d_transcript set up}
 # Set up
@@
   paste(collapse = "|")
+```
 
+```{r d_transcript helper function}
 # helper function
@@
 
-```{r}
+```{r d_transcript row selection}
 d_transcript <- d_transcript %>%
 
-  # for simplicity, we only keep *UCM courses* taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (7501)
+  # for simplicity, we only keep 
+  # *UCM courses*  (courses present in the UCM catalogue)
+  # taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
+
   filter(
@@
 
-  # The dataset has multiple rows for each student - course. Following guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type` == "7055"
+  # The dataset has multiple rows for each student - course.
+  # Following guidelines of Richard Vos, we only consider: 
+  # `Appraisal (Description)` == "Grade supervisor"
+  # and `Appraisal Type` == "7055"
+
   filter(
@@
 
-```{r}
+```{r d_transcript column selection}
 d_transcript <- d_transcript %>%
 
-  # Remove variables with only one value
-  discard(
-    function(x) n_distinct(x) == 1
-  ) %>%
+  # Remove variables with only one value (~10)
+  discard(function(x) n_distinct(x) == 1) %>%
 
-  # Select: Student ID, course ID, when course taken and grade 
+  # Select: Student ID, course ID, when a course is taken and the grade 
   select(
@@
 
-```{r}
+```{r clean_grade}
+clean_grade <- function(grade){
 
+  if(is.na(grade) | grade == "NG") grade <- "0"
+
+  grade %>% str_replace(",", ".") %>% as.numeric
+
+}
+```
+
+```{rclean_period}
+clean_period <- function(period){
+
+  # Course spanning over multiple period are recorder with a 1, 2 or 3
+  if(period == 1) return("1 to 6")
+  if(period == 2) return("1 to 3")
+  if(period == 3) return("4 to 6")
+
+  # Course spanning over a single period are recorded in the 100's, 200's, etc.
+  # The digit of the hundred indicates the period.
+  period %/% 100 %>% as.character
+
+}
+```
+
+```{r clean_year}
+clean_year <- function(year) str_c(year, year + 1, sep = "-")
+```
+
+```{r clean d_transcript}
 d_transcript <- d_transcript %>%
 
-  # Clean grade variable
   mutate(
 
-    Grade = if_else(is.na(Grade) | Grade == "NG", "0", Grade) %>% 
-      str_replace(",", ".") %>% 
-      as.numeric
+    # Clean grade, period and year
+    Grade          = Grade  %>% map_dbl(clean_grade ),
+    Period         = Period %>% map_chr(clean_period),
+    `Academic Year`= Year_numerical %>% map_chr(clean_year),
 
-  ) %>%
+    # extract first period in which course spanning over mutliple periods is given
+    period_numerical = substr(Period, 1, 1),
 
-  # Clean Time variables
-  mutate(
-
-    Period = case_when(
-      Period == 1   ~ "1 to 6"  ,
-      Period == 2   ~ "1 to 3"  ,
-      Period == 3   ~ "4 to 6"  ,
-      between(Period, 100, 199) ~ "1",
-      between(Period, 200, 299) ~ "2",
-      between(Period, 300, 399) ~ "3",
-      between(Period, 400, 499) ~ "4",
-      between(Period, 500, 599) ~ "5",
-      between(Period, 600, 660) ~ "6"
-    ),
-
-    time = str_c(Year_numerical, substr(Period, 1, 1), sep = ""),
-
-    `Academic Year`= str_c(Year_numerical, Year_numerical + 1, sep = "-")
+    # Combine year and period to have be able to order the course in time using a single variable
+    time = str_c(Year_numerical, period_numerical)
 
@@
 
-```{r}
+```{r issue d_transcript}
 d_transcript %>%
@@
   print
+
+#TODO: list issues here
 ```

### 2019-03-12 Data Preparation.Rmd

@@
 list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
+
   map(na.omit)
@@
 d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-  mutate_if(
-    .predicate = is.numeric,
-    .funs      = as.logical
-    ) %>%
+
+  mutate_if(is.numeric, as.logical) %>%
 
@@
     ) %>%
-  filter(
-    assessment_covered
-    ) %>%
-  select(
-    - c(assessment_covered, `Comment on Assessment`)
-    ) %>%
+
+  filter(assessment_covered) %>%
+
+  select(- c(assessment_covered, `Comment on Assessment`)) %>%
+
   print
+```
+
+```{r d_ILO}
+d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
 ```
@@
 d_AoD_from_ILO <- d_ILO %>%
-  rename(
-    ILO = Objectives
-    ) %>%
-  mutate_if(
-    .predicate = is.numeric,
-    .funs      = as.logical
-    ) %>%
+
+  rename(ILO = Objectives) %>%
+
+  mutate_if(is.numeric, as.logical) %>%
 
@@
     ) %>%
-  filter(
-    AoD_covered
-    ) %>%
-  select(
-    - c(AoD_covered, Comments, Comments_for_Jeroen)
-    ) %>%
+
+  filter(AoD_covered) %>%
+
+  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %>%
+
   print
@@
 The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
-```{r catalogues, cache = TRUE}
+
+```{r read_in_pdfs}
 # helper function
@@
     as.list %>%
+
     unname
@@
 }
+```
 
+```{r catalogues, cache = TRUE}
 d_text <- list()
@@
 
-```{r manuals, cache = TRUE}
+```{r extract_code}
 # helper functions
 extract_code <- function(string) string %>% str_sub(start = 1, end = 7)
+```
 
+```{r manuals, cache = TRUE}
 d_text$manuals <- "./Input/Manuals 2017-18" %>%
+
   read_in_pdfs %>%
@@
     ) %>%
+
   print
@@
 
-```{r d_transcript, cache = TRUE}
+```{r read_csv_own_parsing}
+# set up
 col_parsing <- cols(
@@
 
-read_csv_own_parsing <- function(file) file %>% read_csv( col_types = col_parsing) # helper function
+# helper function
+read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
+```
 
+```{r d_transcript, cache = TRUE}
 d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
@@
 map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
-  mutate_if(
-    .predicate = is.numeric,
-    .f         = as.logical
-    ) %>%
+
+  mutate_if(is.numeric, as.logical) %>%
 
@@
     ) %>%
-  filter(
-    AoD_covered
-    ) %>%
-  select(
-    - AoD_covered
-    ) %>%
-  arrange(
-    Assessment
-    ) %>%
+
+  filter(AoD_covered) %>%
+
+  select(- AoD_covered) %>%
+
+  arrange(Assessment) %>%
+
   print
@@
 d_AoD_from_assessment <- d_assessment %>%
-  left_join(
-    map_assessment_AoD,
-    by = "Assessment"
-    ) %>%
+
+  left_join(map_assessment_AoD, by = "Assessment") %>%
+
   print
@@
   ) %>%
+
   distinct %>%
-  arrange(
-    `Course ID`
-    ) %>%
+
+  arrange(`Course ID`) %>%
+
   print
@@
 # helper function
-count_and_paste <- function(data, var, colnam1, colnam2){
+count_and_paste <- function(df, var, colnam1, colnam2){
 
-  data %>%
-    group_by(
-      `Course ID`
-      ) %>%
+  df %>%
+
+    group_by(`Course ID`) %>%
+
     summarize(
@@
 # helper function
-join_by_course_ID <- function(data1, data2){
-
-  data1 %>%
-    left_join(
-      y = data2,
-      by = "Course ID"
-    )
-
-}
+join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
 ```
@@
 d_course <- d_course %>%
+
   join_by_course_ID( d_AoD %>% count_and_paste(AoD, n_AoD, `AoD Covered`) %>% print) %>%
+
   join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`) ) %>%
+
   join_by_course_ID( d_ILO %>% count_and_paste(Objectives, n_ILO, `ILO Covered`        ) ) %>%
+
   select(
@@
 UGR_2000 <- d_course %>%
-  filter(
-    `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")
-    ) %>%
+
+  filter( `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
+
   mutate(
@@
     ) %>%
+
   print
 
-d_course <- d_course %>%
-  rbind(UGR_2000)
+d_course <- d_course %>% rbind(UGR_2000)
 
+# print UGR course
 print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )
@@
 d_course <- d_course %>%
+
   separate(
@@
     ) %>%
+
   mutate(
@@
     ) %>%
+
   select(`Course ID`, Letters, Number, Level, everything()
     ) %>%
+
   print
@@
 
-```{r extract_description, eval = FALSE}
+```{r extract_description}
 extract_description <- function(overview){
@@
       is_start_descrip = line %>% is_start_descrip,
-      is_end_descrip   = line %>% is_end_descrip # Having several ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
+      is_end_descrip   = line %>% is_end_descrip # Having multiple ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
       ) %>%
@@
       ) %>%
+
     filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%
@@
     summarise(description = str_c(line, collapse = " ")) %>%
+
     pull
@@
 
-```{rclean_period}
+```{r clean_period}
 clean_period <- function(period){
@@
 ```{r}
-save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
-     file = "Output/data_general.RDATA")
-save(d_transcript,
-     file = "Output/data_pillar_1.RDATA")
-save(d_text, d_course, d_transcript,
-     file = "Output/data_pillar_2.RDATA")
+save(
+  d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
+  file = "Output/data_general.RDATA"
+  )
+
+save(d_transcript, file = "Output/data_pillar_1.RDATA")
+
+save(d_text, d_transcript, file = "Output/data_pillar_2.RDATA")
 ```

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
debug incoherence between data preparation and pillar 1
Simplify code of provide_statistics

@@
 knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
-```
-
-```{r library, message = FALSE, warning = FALSE}
+
 library(tidyverse)
@@
 
-# Setup
+# Load data
 We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
 ```{r loading data}
+load("Output/data_general.RDATA")
 load("Output/data_pillar_1.RDATA")
@@
 
-```{r for convenience}
+# Descriptive statistics
+We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level).
+We save the results in the environment `Transcript Statistics`.
+
+```{r statistics set up}
 pass_grade <- 5.5
 high_grade <- 6.5
-
-join_d_course <- function(data){
-
-  data %>%
-    inner_join(
-    d_course,
-    by = c("Course ID")
-    )
-
-}
-
-join_d_transcript <- function(data){
-
-  data %>%
-    inner_join(
-    d_transcript,
-    by = c("Course ID")
-    )
-
-}
-```
-
-# Data Exploration
-
-We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level).
-We save the results in the environment `Transcript Statistics`.
-
-```{r statistic summary, cache = TRUE}
-
-#
-# function providing statistics
-provide_statistics <- function(data, var){
-
-  data %>%
-
-    mutate(
-      Grade = case_when(
-        Grade >= 5.5 ~ Grade,
-        T            ~ as.numeric(NA)
-        )
-      ) %>%
-
-    filter(
-      !is.na(!!enquo(var))
-      ) %>%
-    group_by(
-      !!enquo(var)
-      ) %>%
+```
+
+```{r join_d_df}
+# helper function
+join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
+join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))
+```
+
+```{r provide_statistics}
+# helper function
+provide_statistics <- function(var, df = d_transcript, high_gr = high_grade, pass_gr = pass_grade, join = TRUE){
+
+  if(join) df <- df %>% join_d_course
+
+  df %>%
+
+    filter(!is.na(!!enquo(var))) %>%
+
+    group_by(!!enquo(var)) %>%
 
@@
       Count           = n(),
-      Min             = min(Grade, na.rm = TRUE),
-      Max             = max(Grade, na.rm = TRUE),
-      Mean            = mean(Grade, na.rm = TRUE),
-      Median          = median(Grade, na.rm = TRUE),
-      IQR             = IQR(Grade, na.rm = TRUE),
-      SD              = sd(Grade, na.rm = TRUE),
-      `Low Rate`      = mean(is.na(Grade) | Grade < high_grade),
-      `Fail Rate`     = mean(is.na(Grade))
-      ) %>%
-
-    mutate_at(
-      vars(Mean, SD, `Low Rate`, `Fail Rate`, IQR),
-      round,
-      digits = 2
-    )
-
-}
-
-#
-# Generating Statistics
+      Min             = min   (Grade),
+      Max             = max   (Grade),
+      Mean            = mean  (Grade),
+      Median          = median(Grade),
+      IQR             = IQR   (Grade),
+      SD              = sd    (Grade),
+      `Low Rate`      = mean  (Grade < high_grade),
+      `Fail Rate`     = mean  (Grade < pass_grade)
+    ) %>%
+
+    mutate_if(is.numeric, round, digits = 2)
+
+}
+```
+
+```{r statistics}
 statistics <- list()
@@
 # Student level
-statistics$student <- d_transcript %>%
-  provide_statistics(`Student ID`)
+statistics$student <- provide_statistics(`Student ID`)
 
 # Course level
-statistics$course <- d_transcript %>%
-  join_d_course %>%
-  provide_statistics(`Course ID`)
+statistics$course  <- provide_statistics(`Course ID`)
 
 # Cluster level
-statistics$cluster <- d_transcript %>%
-  join_d_course %>%
-  provide_statistics(Cluster)
+statistics$cluster <- provide_statistics(Cluster)
 
 # Type level
-statistics$type <- d_transcript %>%
-  join_d_course %>%
-  provide_statistics(Type)
+statistics$type    <- provide_statistics(Type)
 
@@
     ) %>%
-  provide_statistics(Concentration)
+  provide_statistics(Concentration, df = ., join = FALSE)
 
 # Year level
-statistics$year <- d_transcript %>%
-  provide_statistics(Year_numerical)
+statistics$year <- provide_statistics(Year_numerical)
 
 # Level level
-statistics$level <- d_transcript %>%
-  # TODO: filter for student who completed their studies
-  join_d_course %>%
-  provide_statistics(Level)
-```
-
-```{r, include = FALSE}
-save(
-  statistics,
-  file = "Output/Transcript Statistics.RDATA"
-  )
-```
-
-```{r, include = FALSE}
+statistics$level <- provide_statistics(Level) # TODO: filter for student who completed their studies
+```
+
+```{r save statistics, include = FALSE}
+save(statistics, file = "Output/Transcript Statistics.RDATA")
 rm(statistics, provide_statistics)

### 2019-03-12 Misc Code.Rmd
Create RMD for code that is no longer useful

---
title: "Misc Code"
author: "Raphaël Morsomme"
date: "March 12, 2019"
output: pdf_document
---

# Estimating concentrations
For our analysis we would also like to know what the concentration of each student is. However, this is not given, so we will have to estimate. We know that the maximimum amount of courses a student can take outside of their concentration is 2. Therefore, if any student has more than two courses in one concetration, this should count towards the concentration. We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration. However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided". Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"

```{r, eval = FALSE}
d_concentration <- d_course %>%
  select(Code, Concentration, `Concentration (additional)`) %>%
  gather(key = X, value = Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  left_join(d_transcript, by = c("Code" = "Course Code")) %>%
  select(Concentration, `Student ID Number`) %>%
  count(Concentration, `Student ID Number`) %>%
  spread(key = Concentration, value = n, fill = 0) %>%
  mutate(n_course = HUM + SCI + SSC,
         `Student Concentration` = case_when(
           n_course < 20 ~ "not enough courses",
           HUM > 5 & SSC > 5 & SCI > 5 ~ "confused",
           HUM > 5 & SSC > 5           ~ "HUM/SCI",
           HUM > 5                     ~ "HUM",
           SSC > 5 & SCI > 5 ~ "SSC/SCI",
           SSC > 5           ~ "SSC",
           SCI > 5 ~ "SCI"
         ))

transmute(student_Concentration = case_when(
  (HUM  >  2    &   SSC >  2   &  SCI <= 2) ~ "HUM/SSC",
  (HUM  >  2    &   SSC <= 2   &  SCI >  2) ~ "HUM/SCI",
  (HUM  >  2    &   SSC <= 2   &  SCI <= 2) ~ "HUM",
  (HUM  <= 2    &   SSC >  2   &  SCI >  2)  ~ "SSC/SCI",
  (HUM  <= 2    &   SSC >  2   &  SCI <= 2) ~ "SSC",
  (HUM  <= 2    &   SSC <= 2   &  SCI >  2)  ~ "SCI",
  (HUM  <  2    &   SSC <  2   &  SCI <  2) ~ "UNDECIDED",
  (HUM  >  2    &   SSC >  2   &  SCI >  2) ~ "CONFUSED", #normal cases ^
  (HUM > SCI    &   HUM > SSC)              ~ "HUM",
  (SSC > SCI    &   SSC > HUM)              ~ "SSC",
  (SCI > HUM    &   SCI > SSC)              ~ "HUM",
  TRUE ~ "oops"
))
```

Since we will need to check each student with an "oops" concentration to see what happened, lets separate this data for later:
  ```{r, eval = FALSE}
checkup <- filter(d_student_concentration, student_Concentration == "oops") 
```

###Getting UCM_YEAR
In order to compare the trajectories of students, we would like to know if the courses were taken in their first, second, third, or whatever year. However, we only have the calendar years. Lets find out to what year of study each calendar year corresponds per student.

First, lets find out, which year was a student's first year and which year was a student's last year (we will also create a variable `Subs_year` that we will substract later to transform from Calendar Year to UCM Year, and a second variable `LengthUCM` that shows us how many years each student stayed at the college):
  ```{r, eval = FALSE}
d_year <- d_grade %>%
  select(ID, Code, Year, Period, Grade,`Booking Status Description`, `Course concentration`) %>%
  group_by(ID) %>%
  summarise(FirstYear=min(Year), LastYear=max(Year)) %>%
  mutate(LengthUCM = LastYear-FirstYear, Subs_year=FirstYear-1)
```

Now, lets make a dataframe of students against years, where the year appears in the corresponding cell if a student was in the college at that time:

  ```{r, eval = FALSE}
d_year1 <- d_grade %>%
  select(ID, Code, Year, Period, Grade, `Booking Status Description`, `Course concentration`) %>%  
  group_by( ID, Year) %>%
  summarise(Count = n())%>%
  mutate(Present = case_when(Count > 0 ~ Year))%>%
  select(-Count) %>%
  spread(Year,Present, fill = 0)
```

Now we have collected all the years a student has been at the college in a single row (one row per student), and we also know what is the first and last year of each student. Let's join these dataframes:

```{r, eval = FALSE}
d_time <- left_join(d_year1, d_year)
```

Ideally, we would like to have a dataframe of students against calendar years filled with the corresponding UCM year (e.g. if the year 2017 was the first year of student 45, we would like to see the cell corresponding to student 45 and year 2017 marked with a "1").

```{r, eval = FALSE}
var_years <- as.character(2007:2017)
d_time <- d_time %>% 
mutate_at(
vars(var_years),
funs(. - Subs_year)) %>%
mutate_at(
vars(var_years),
funs(case_when(. < 0 ~ 9999999999, #HORRIBLE FIX
T     ~ .)))
d_time[d_time == 9999999999] <- NA
```

Now, lets get the data as we want it for our analysis. For our analysis we would like to know what course a student took, when, whether they passed or failed, what grade they got, what the concentration of the student is, and what the concentration of the course is (we will convert grades to numeric here). Then, we would like to know on what year of their studies the student took the course.For this we will create a years dictionary and join it with our student data:

```{r, eval = FALSE}
d_students <- d_grade %>%
select(ID, Code, Year, Period, Grade, Attempt,`Booking Status Description`, `Course concentration`) %>%
arrange(ID, Year, Period)%>%
left_join(d_student_concentration, by="ID") %>%
mutate(Grade = as.numeric( sub(",",".", Grade))) %>%
replace_na(list(Grade=-1))
# Years dictionary:
year_dic <- d_time %>%
select(-FirstYear,-LastYear,-LengthUCM,-Subs_year)%>%
gather(Cal_Year,UCM_Year,var_years)%>%
drop_na(.) %>%
mutate(Year=as.integer(Cal_Year))%>%
select(-Cal_Year)
#adding the ucm year to transcripts:
d_students <- d_students %>%
left_join(year_dic, by=c("ID","Year"))
#removing repeated values:
d_students <- d_students[!duplicated(d_students),]
```

###Removing master Program data and Cleaning Capstone Data 
We noticed that we had the data for people who stayed at this university for their masters. To filter these courses out we find out in which year people took their capstone courses.

For this we keep only the capstones. We expect some people to have repeated capstones:
```{r, eval = FALSE}
capstone_count <- d_students %>%
filter(Code=="CAP3000") %>%
group_by(ID)%>%
summarise(Count=n())
capstone_count
```
However, what is surptising is that some people have two different passed capstones:

```{r, eval = FALSE}
passed_capstone_count <- d_students %>%
filter(Code=="CAP3000", `Booking Status Description`=="Completed with Success") %>%
group_by(ID) %>%
summarise(Count=n(), Max = max(Grade), Min = min(Grade), Attempts= max(Attempt))
```

We can check the grades for people who had repeated passed capstones (lets just bring them to the top of the list):
```{r, eval = FALSE}
passed_capstone_count %>%
arrange(desc(Count), desc(Min), Attempts)
```
There are 1712 people who did capstone. We see that most students who have two passed Capstones, have in reality only 1, since the other capstone had a failing grade and the passing grade was on the second attempt (count starts at 0) was indeed failed. However there are two students who indeed have two different passed Capstones: one is student 282995 who has two different passing grades(because of a change in grading system at the collegue during the year 2008-2009), the other is student 544450 who has the same grade passed at two different moment in time.

We can check if there are any students with passing capstone who do not have a grade of at least 5.5. We do this by looking at the lowest Max values:
```{r, eval = FALSE}
passed_capstone_count %>%
arrange(Max)
```
We see the lowest grade for a passing capstone is 5.6, so this is fine.

Now lets just keep the highest value for each student and correct for student 282995:
```{r, eval = FALSE}
passed_capstone_grades <- passed_capstone_count %>%
mutate(`Booking Status Description`= "Completed with Success", Code="CAP3000", Grade= case_when(ID== 282995~7.7,
T~Max)) %>%
select( ID, Code, Grade,`Booking Status Description`)
passed_capstone_grades
```

####Capstone Year
Now we can figure out the Capstone Year.

First we get the years for which there is a corresponding passing capstone grade, and check for repetition:
```{r, eval = FALSE}
capstone_finish_year <- inner_join(passed_capstone_grades, d_students) 
head(capstone_finish_year)
count_before <- passed_capstone_grades %>%
group_by(ID) %>%
summarise(counts_of_id= n())
count_after <- capstone_finish_year %>%
group_by(ID) %>%
summarise(counts_of_id= n())%>%
filter(counts_of_id > 1)  #these students have repeated capstones.
count_after

```
From count_after we see that student 544450 has two passed capstones at different moments in time, we already knew this and we must ask Richard why this is the case. However, since both capstones where passed in 2010, this creates no problem for our current purposes. However, let's remove the later version.
We will also rename `Year` to `Capstone Year` and keep only the columns `Capstone Year` and `ID`
```{r, eval = FALSE}
to_remove <- capstone_finish_year%>%
  filter(ID==544450)
to_remove <- to_remove[duplicated(to_remove$ID),]
capstone_finish_year <- capstone_finish_year%>%
  anti_join(to_remove) %>%
  rename(`Capstone Year`= Year)%>%
  select(ID,`Capstone Year`)

capstone_finish_year
```

Lets create a dataframe where we include the capstone year. Then, if a course is given later than the capstone year, we want to remove it. Therefore, lets substitute na values with the year 9999 (or will ucm be open in the year 9999?).
```{r, eval = FALSE}
d_transcripts <- d_students %>%
  group_by(ID) %>%
  left_join(capstone_finish_year) %>%
  ungroup() %>%
  replace_na(list(`Capstone Year`=9999)) %>%
  mutate(`After Graduation`=`Capstone Year`-`Year`)
d_transcripts
```
Now we will remove all courses with negative `After Graduation`:
  ```{r, eval = FALSE}
master_courses <- d_transcripts%>%
  filter(`After Graduation`<0)
d_transcripts <- d_transcripts %>%
  anti_join(master_courses)
head(d_transcripts)
```

One last thing. The variable `Booking Status Description` shows whether a student passed or failed the course. However, some mistakes in the way the data was handled meant that the course status of some students was never confirmed. We need to ASK RICHARD, but for the moment, we will just look at the grades of those courses which were not confirmed to change into pass and fail.

```{r, eval = FALSE}
booked <- filter(d_transcripts, d_transcripts$`Booking Status Description`=="Booked")%>%
  mutate(`Booking Status Description`= case_when(Grade<5.5~"Completed Unsuccessfully",
                                                 Grade>5.5~"Completed with Success"))
clean_transcripts <- d_transcripts %>% 
  left_join(booked, by= c("ID", "Code", "Year", "Period", "Grade", "Attempt", "Course concentration", "student_Concentration", "Capstone Year", "After Graduation"), suffix=c("-old", "-new"))%>%
  select(-`After Graduation`)%>%
  mutate(Pass= case_when(
    (`Booking Status Description-new`=="Completed with Success")~"Pass",
    (`Booking Status Description-new`=="Completed Unsuccessfully")~"Fail",
    (`Booking Status Description-old`=="Completed with Success")~"Pass",
    (`Booking Status Description-old`=="Completed Unsuccessfully")~"Fail",
    T~"error in clean_transcripts"
  )) %>%
  select(-`Booking Status Description-new`,-`Booking Status Description-old`,-"UCM_Year-new")
```
####Ordering in Time
We would like to have a column `Time` that codes for both year and period (e.g. Year_1 Period_2 should be 1.2), as well as a column `Periods` with the year and period as numbers (e.g. Year_2 Period_1 should be period 7).

CHECK: we still have students who's first record is of their last year. This appears as UCM_Year=1.

```{r, eval = FALSE}
a_clean_transcripts <- clean_transcripts%>%
separate(Period, 
c("T1","T2","T3","T4","T5","T6"), 
sep="," 
) %>%
gather( key = "Time", value = "Period", T1,T2,T3,T4,T5,T6) %>%
drop_na(Period) %>%
select(-Time) %>%
mutate(Periods = (`UCM_Year-old` - 1) * 6 + 
as.numeric(Period)
)

a_clean_transcripts$Time= paste(a_clean_transcripts$`UCM_Year-old`,
a_clean_transcripts$Period, 
sep="."
)
#FINAL DATA:
d_transcript <-a_clean_transcripts%>%
select(-`UCM_Year-old`,-Period)
```
NOTES: The data is now arranged so as to respect the order in time for each individual student. However, the comparison is still tricky as people who finished in 2008 will have CAP recorded as taken on their first year since this is all the data we have. 
COMMENT SOFIA: save a_clean_transcript as d_transcript

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for d_transactions$taken_PF_HL

@@
 
+# Set up
+
+```{r helper function}
+# helper function
+join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
+join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))
+
+paste_ <- function(...) paste(..., sep = "_")
+```
+
 # Descriptive statistics
@@
 high_grade <- 6.5
-```
-
-```{r join_d_df}
-# helper function
-join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
-join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))
 ```
@@
 
-  # Exclude 
-  filter(
-    Type != "Mandatory",  # (i) mandatory courses e.g. COR, CAP, etc
-    ! Letters %in% c(
-      "SKI", "PRO",       # (ii) skills & projects (taken by majority of students)
-      "SAS", "SAH", "SAC" # (iii) courses of semester abroad (uninformative)
-      )
+  # Exclude courses taken by majority of students (uninformative)
+  filter(
+    Type != "Mandatory",
+    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
     ) %>%
@@
   # Join with transcripts
-  select(
-    - Period
-    ) %>%
+  select(- Period) %>% # remove Period to avoid duplicates
   join_d_transcript %>%
 
-  # Identifying sequenceID
+  # sequenceID and event ID
   rename(
-    sequenceID = `Student ID`
-    ) %>%
-
-  # Identifying evenID
-  mutate(
-    Period  = substr(Period, 1, 1),
-    eventID = as.numeric(paste(Year_numerical, Period, sep = ""))
-    ) %>%
-
-  # Identifying itemID
-  mutate(
-    PF = case_when(
-      Grade <  pass_grade ~ "fail",
-      Grade >= pass_grade ~ "pass"
-      ),
-    HL = case_when(
-      Grade <  high_grade ~ "low",
-      Grade >= high_grade ~ "high"
-      ),
-
+    sequenceID = `Student ID`,
+    eventID = time
+    ) %>%
+
+  # itemID
+  mutate(
     item    = `Course ID`,
-    item_PF = paste(item, PF, sep = "_"),
-    item_HL = paste(item, HL, sep = "_")
+    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
+    item_PF = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
     )

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
create constants in the setup section for clarity

@@
 
+```{r constants}
+# Some old courses are present
+course_all  <- unique(d_transcript$`Course ID` )
+student_all <- unique(d_transcript$`Student ID`)
+n_students  <- length(student_all)
+```
+
 ```{r helper function}
 # helper function
-join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID"))
-join_d_transcript <- function(df) df %>% left_join(d_transcript, by = c("Course ID"))
+join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID")) # left_join to keep all courses present in d_transcript
+join_d_transcript <- function(df) df %>% right_join(d_transcript, by = c("Course ID")) # right_joint to keep all courses present in d_transcript
 
@@
 ```{r for convenience II}
-course_all  <- unique(d_transactions$taken_PF_HL$item      )
-student_all <- unique(d_transactions$taken_PF_HL$sequenceID)
-n_students  <- length(student_all)
+
 ```

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
include data loading in set up section for clarity
compute descriptive stats at the Academic Year (e.g. 2018-2019) level instead of Year_numerical (e.g. 2017) level.

@@
 
-# Load data
+# Set up
 We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
@@
 ```
-
-# Set up
 
@@
 # Year level
-statistics$year <- provide_statistics(Year_numerical)
+statistics$year <- provide_statistics(`Academic Year`)
 
@@
     )
-```
-
-For convenience:
-```{r for convenience II}
-
 ```

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
typo

@@
     item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
-    item_PF = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
+    item_HL = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
     )

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Use tidyr::complete instead of expand.grid + join for simplicity

@@
 ```{r d_transactions T_PF_HL}
-d_transactions$T_PF_HL <- expand.grid(
-
-  # Expand along students (sequenceID) and courses (itemID)
-  sequenceID       = student_all,
-  item             = course_all,
-  stringsAsFactors = FALSE
-  ) %>%
-
-  # Join with d_transactions
-  left_join(
-    d_transactions$taken_PF_HL, 
-    by = c("sequenceID", "item")
-    ) %>%
-
-  # Create item
-  mutate(
-
-    TPF = case_when(
-      is.na(Grade)        ~ "not",
-      Grade <  pass_grade ~ "fail",
-      Grade >= pass_grade ~ "pass"
-      ),
-    THL = case_when(
-      is.na(Grade)        ~ "not",
-      Grade <  high_grade ~ "low",
-      Grade >= high_grade ~ "high"
-      ),
-
-    item_TPF = paste(item, TPF, sep = "_"),
-
-    item_THL = paste(item, THL, sep = "_")
-
+d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%
+
+  # Expand along students (sequenceID) and courses (itemID) to make missing combinations of student - course explicit
+  complete(sequenceID, item) %>%
+
+  # create a new type of item: "not taken"
+  mutate(
+    item_TPF = if_else(is.na(item_PF), paste_(item, "not"), item_PF),
+    item_THL = if_else(is.na(item_HL), paste_(item, "not"), item_HL)
     )

### 2019-03-12 Pillar 2 - Topic Modeling.Rmd
integrates Topic Scores code

--- 2019-03-01 Pillar 2 - Topic Modeling.Rmd
@@
 
+```{r getting gamma and beta, eval = TRUE}
+get_beta <- function(results){
+
+  tidy(results, matrix = "beta")           %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(beta) )
+
+}
+
+get_gamma <- function(results){
+
+  tidy(results, matrix = "gamma")          %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(gamma) )
+}
+
+```
+
+```{r applying get_gamma and get_beta, eval = TRUE}
+topic_model_gb <- topic_model %>%
+  transmute(
+    n_topic    = n_topic,
+    g_overview = TM_overview %>% map( .f = get_gamma),
+    g_manual   = TM_manual   %>% map( .f = get_gamma),
+    b_overview = TM_overview %>% map( .f = get_beta),
+    b_manual   = TM_manual   %>% map( .f = get_beta)
+      )
+```
+#Saving DELETE LATER
+```{r saving tidy models, eval= TRUE}
+save(topic_model_gb,
+     file = "Output/topic_model_gb.RDATA")
+
+save(topic_model_gb,
+     file = "App/Recommender System/topic_model_gb.RDATA")
+```
+#Saving DELETE LATER
 ```{r saving models, eval= TRUE}
@@
 
+##Distributions of best models
+```{r Distributions, eval = TRUE}
+#select number of topics
+n_topics_overview <- 36
+n_topics_manual   <- 40
+
+#Crop models
+TM_overview <- topic_model_gb %>%
+  filter(n_topic== n_topics_overview)
+
+TM_manual   <- topic_model_gb %>%
+  filter(n_topic== n_topics_manual)
+
+#Distributions
+distribution <- list()
+
+distribution$beta$overview  <- TM_overview %>% pull(b_overview)
+distribution$beta$manual    <- TM_manual   %>% pull(b_manual)
+
+distribution$gamma$overview <- TM_overview %>% pull(g_overview)
+distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)
+
+```
+##Inspect topics
+THE TOPICS ARE SUPPER STRANGE!
+```{r inspect topics, eval = T}
+
+inspect_topics <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(10, beta)
+
+}
+
+topics <-  lapply(
+  distribution$beta,
+  inspect_topics
+)
+```
+##Selectig keywords
+```{r key words, eval = TRUE}
+get_top_words <- function(d_beta, n = 3){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(n, beta) %>%
+    pull(term)%>%
+    unique
+}
+
+kw <- lapply(
+  distribution$beta,
+  get_top_words
+)
+```
+##Convenience vectors for APP
+```{r for convenience, eval = T}
+# set seed
+set.seed(1)
+
+#
+## All courses
+course_all <- d_course %>%
+  inner_join(
+    d_transcript,
+    by = "Course ID"
+  ) %>%
+  distinct(
+    `Course ID`
+  ) %>%
+  # remove semester abroad, skills and projects
+  filter(
+    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
+  ) %>%
+  pull
+
+#
+##courses following_semester
+course_following_semester <- sample(
+  x       = course_all,
+  size    = 60,
+  replace = FALSE
+  ) %>% sort
+```
+## Saving files for APP
+```{r app files}
+save(distribution, kw, course_all, course_following_semester,
+     file = "App/Recommender System/data_topic_models.RDATA")
+```
+###Previous code DELETE LATER
 ```{r LDA fitxxxxxxx, cache = TRUE}

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Create d_transcript_augmented in set up section for simplicity

@@
 # helper function
-join_d_course     <- function(df) df %>% left_join(d_course    , by = c("Course ID")) # left_join to keep all courses present in d_transcript
-join_d_transcript <- function(df) df %>% right_join(d_transcript, by = c("Course ID")) # right_joint to keep all courses present in d_transcript
+join_d_course     <- function(df) df %>% left_join(d_course, by = c("Course ID"))
 
 paste_ <- function(...) paste(..., sep = "_")
+```
+
+```{r d_course_informative}
+d_transcript_augmented <- d_transcript %>%
+
+  join_d_course %>%
+
+  # Exclude courses taken by majority of students (uninformative)
+  filter(
+    Type != "Mandatory",
+    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
+    )
 ```
@@
 
-d_transactions$taken_PF_HL <- d_course %>%
-
-  # Exclude courses taken by majority of students (uninformative)
-  filter(
-    Type != "Mandatory",
-    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
-    ) %>%
-
-  # Join with transcripts
-  select(- Period) %>% # remove Period to avoid duplicates
-  join_d_transcript %>%
+d_transactions$taken_PF_HL <- d_transcript_augmented %>%
 

### 2019-03-12 Data Preparation.Rmd
correct type of time var in d_transcript df
add TODO list

@@
 ---
+
+TODO:
+
+* when student takes a course multiple times:
+    * keep lowest grade
+    * keep highest grade 
+    * or keep both (much more complex)
 
@@
     # Combine year and period to have be able to order the course in time using a single variable
-    time = str_c(Year_numerical, period_numerical)
+    time = str_c(Year_numerical, period_numerical) %>% as.numeric,
+
+    grade_ceil = ceiling(Grade)
 

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Create d_transcript_augmented in set up section for simplicity
Simplify code for d_transactions$G
Use cumany() instead of spread - gather

@@
 # helper function
-join_d_course     <- function(df) df %>% left_join(d_course, by = c("Course ID"))
+join_d_course     <- function(df) df %>% left_join(select(d_course, - Period), by = c("Course ID"))
 
@@
 
-  # Spread along ceiling grades
-  mutate(
-    grade_ceil = ceiling(Grade),
-    Values     = TRUE,
-    id         = 1 : n() # to ensure each row is unique
-    ) %>%
-  spread(
-    key   = grade_ceil, 
-    value = Values
-    ) %>%
-
-  # grade x or lower
-  mutate(
-    `1`  = `0`|`1`,
-    `2`  = `1`|`2`,
-    `3`  = `2`|`3`,
-    `4`  = `3`|`4`,
-    `5`  = `4`|`5`,
-    `6`  = `5`|`6`,
-    `7`  = `6`|`7`,
-    `8`  = `7`|`8`,
-    `9`  = `8`|`9`,
-    `10` = `9`|`10`
-    ) %>%
-
-  # Gather along rounded grades
-  gather(
-    key   = grade_ceil,
-    value = X,
-    `0` :`10`, 
-    na.rm   = TRUE, 
-    convert = TRUE
-    ) %>%
-  select(
-    -X
-    ) %>%
-
-  # Identifying item
-  mutate(
-    item_G = paste(item, grade_ceil, sep = "_")
-    )
+  mutate(row_of_origin = TRUE) %>%
+
+  complete(
+    nesting(sequenceID, eventID, item, Grade), grade_ceil,
+    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
+    ) %>%
+
+  group_by(sequenceID, eventID, item, Grade) %>%
+
+  distinct(sequenceID, eventID, item, grade_ceil, Grade, row_of_origin) %>% # reminder that we should get rid of duplicates oin d_transcript
+
+  arrange(grade_ceil) %>%
+
+  filter(cumany(row_of_origin)) %>% # only keep grades larger than ceil_grade
+
+  ungroup()
 ```

### 2019-03-13 DELETE LATER.R
saving results from previous experiment

@@ -1,0 +1,4 @@
+load("Output/LDA_ntopics.RDATA")
+
+save(result_manual, result_overview , result_description,
+     file = "Output/LDA_ntopics.RDATA")

### 2019-03-13 DELETE LATER.R
recovery script

@@ -1,4 +1,10 @@
+#saved in workspace
 load("Output/LDA_ntopics.RDATA")
 
+save(result_manual, result_overview , result_description,
+     file = "Output/LDA_ntopics_Find.RDATA")
+
+#recovery
+load("Output/LDA_ntopics_Find.RDATA")
 save(result_manual, result_overview , result_description,
      file = "Output/LDA_ntopics.RDATA")

### 2019-03-13 Data Preparation.Rmd
add an example of issue with d_transcript

@@
 
-  # highlight issue: there are several rows with unique student ID - course ID - time combination.
+  # multiple rows with unique student ID - course ID - time combination.
   add_count(
     `Student ID`, `Course ID`, time,
+    sort = TRUE
+    ) %>%
+  print
+
+d_transcript %>%
+
+  # multiple rows with unique student ID - course ID - time combination - grade.
+  add_count(
+    `Student ID`, `Course ID`, time, Grade,
     sort = TRUE

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute course_all, etc from d_transcript_augmented to exclude uninformative courses

@@
 
-```{r constants}
-# Some old courses are present
-course_all  <- unique(d_transcript$`Course ID` )
-student_all <- unique(d_transcript$`Student ID`)
-n_students  <- length(student_all)
-```
-
 ```{r helper function}
@@
     )
+```
+
+```{r constants}
+course_all  <- unique(d_transcript_augmented$`Course ID` )
+student_all <- unique(d_transcript_augmented$`Student ID`)
+n_students  <- length(student_all)
 ```

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
Use purrr to simplify the code d_transcript_cum
reduced code length by half

@@
   # item_take
-  mutate(
-    item_take = paste(item, "take", sep = "_")
-  ) %>%
-
-  # course current
-  group_by(
-    sequenceID,
-    eventID
-    ) %>%
-  summarize_at(
-    c("item", "item_take", "item_PF", "item_HL"),
-    function(x) list(unique(x))
-    ) %>%
-
-  # course current all
-  rowwise %>%
-  mutate(
-    course_current = list(c(item, item_take, item_PF, item_HL))
-    ) %>%
-
-  # course past
-  group_by(
-    sequenceID
-    ) %>%
-  mutate(
-    course_past = Reduce(
-      f = c,
-      x = course_current,
-      accumulate = TRUE
-      ) %>%
-      lag(
-        default = as.character(NA)
-        )
-    ) %>%
-
-  # course so far, course not so far
-  rowwise %>%
-  mutate(
-
-    course_past_current = list(union  (course_past, course_current      )),
-
-    course_not_yet      = list(setdiff(course_all , course_past_current )),
-    course_not_yet      = list(paste(course_not_yet, "not", sep = "_"   )),
-
-    course_so_far       = list(union  (course_past, course_not_yet))
-
-    ) %>%
+  mutate(item_take = paste_(item, "take")) %>%
+
+  # current courses
+  group_by(sequenceID, eventID) %>%
+
+  summarize_at(vars(matches("item")), ~ unique(.) %>% list) %>%
+
+  mutate(course_current = list(item, item_take, item_PF, item_HL) %>% pmap(~ c(...) %>% unique)) %>%
+
+  # courses so far, past courses and course not taken yet
+  group_by(sequenceID) %>%
+
+  arrange(eventID) %>%
+
+  mutate(
+    course_so_far  = course_current %>% accumulate(union),
+    course_past    = course_so_far  %>% lag(default = NA_character_),
+    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
+    ) %>%
+
   ungroup %>%
 
-  # lhs: past, rhs: present
-  select(
-    lhs = course_so_far,
+  # lhs: past courses and courses not taken yet, rhs: current courses
+  mutate(
+    lhs = list(course_past, course_not_yet) %>% pmap(union),
     rhs = course_current

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

@@
 ```
-####Save d_transactions
+
+#### Save d_transactions
 ```{r save d_transaction}
-save(
-  d_transactions,
-  file = "Output/transaction_df.RDATA"
-  )
-```
+save(d_transactions, file = "Output/transaction_df.RDATA")
+```
+
 ### Transcript with preceding courses (for SR by hand)
-```{r d_transcript_cum, cache = TRUE, warning = FALSE}
+```{r d_transcript_cum, cache = TRUE}
 d_transcript_cum <- d_transactions$taken_PF_HL %>%

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd
re-arranges structure to compute things (e.g. perplexity) manually

@@
 ```
+
+###With Package built in Function
 The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
@@
 
-## Fitting Model
-
-From the results we see that the ideal number of topics is somewhere between 35 and 40.
-We train our models on 35 topics.
-Then we save them in the `Output`folder and in the ``Recommender System` folder.
-
-#NEW
-# LDA
+### Manually
 The function `my_cast_tdm` casts our dataframes into a tdm.
@@
 
+The function `my_LDA` fits an LDA model on the DTM using the previous controls.
 ```{r my_LDA, eval= TRUE}
@@
 ```
+####10-fold Cross-validation
+TO BE FINISHED
+```{r manual evaluation, cache = TRUE, eval = TRUE}
+set.seed(1234)
 
+#number of topics for trials
+n_topic = seq(from = 2, to = 80, by = 2)
+
+#create folds
+create_folds <- function(my_dtm){
+  #find number of documents (D)
+  D <- nrow(my_dtm)
+
+  #Assign documents to a fold
+  folding <- sample(rep(seq_len(10), ceiling(D))[seq_len(D)])
+}
+
+#
+##Create folds
+###Find number of documents
+D_overview <- nrow(d_cast$overview)
+D_manual <- nrow(d_cast$manual)
+
+###Assigning random numbers (1:10) to each row of our DTM
+folding_overview <- sample(rep(seq_len(10), ceiling(D_overview))[seq_len(D_overview)])
+folding_manual   <- sample(rep(seq_len(10), ceiling(D_manual))[seq_len(D_manual)])
+
+for(k in n_topics){
+  for(chain in 1:10){
+    ###Divide into training and testing sets
+      #overview
+    training_set_overview <- d_cast$overview[folding!=chain,]
+    test_set_overview     <- d_cast$overview[folding==chain,]
+      #manual
+    training_set_manual   <- d_cast$manual[folding!=chain,]
+    test_set_manual       <- d_cast$manual[folding==chain,]
+
+  }
+}
+
+```
+## Fitting Model
+From the results we see that the ideal number of topics is somewhere between 35 and 40.
+We train our models on 35 topics.
+Then we save them in the `Output`folder and in the ``Recommender System` folder.
+
+#NEW
+# LDA
 ```{r LDA fit, cache = TRUE, eval = TRUE}
@@
 ```
+##Model Evaluation
+Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
+```{r}
 
+#Extracting LDA model n_topics = 2
+test1 <- topic_model$TM_overview[1]
+
+#Getting A single LDA Model:
+test2 <- test1[[1]]
+
+#getting perplexity
+perplexity(test2, d_cast$overview, estimate_theta=FALSE)
+
+Topic <- topics(test2)
+Terms <- terms(test2,5)
+
+lL <- list()
+for(i in 1:length(topic_model$n_topic)){
+
+  tmp <- topic_model$TM_overview[i]
+  lL[[paste("n", 2*i)]] <- tmp[[1]]@loglikelihood
+
+}
+
+test1[[1]]@loglikelihood
+
+log_like <- logLik(test1[[1]])
+
+```
+##Get Beta/Gamma functions
 ```{r getting gamma and beta, eval = TRUE}
@@
 
+##Apply beta and gamma
 ```{r applying get_gamma and get_beta, eval = TRUE}
@@
       )
-```
-#Saving DELETE LATER
-```{r saving tidy models, eval= TRUE}
-save(topic_model_gb,
-     file = "Output/topic_model_gb.RDATA")
-
-save(topic_model_gb,
-     file = "App/Recommender System/topic_model_gb.RDATA")
-```
-#Saving DELETE LATER
-```{r saving models, eval= TRUE}
-save(topic_model,
-     file = "Output/topic_model.RDATA")
-
-save(topic_model,
-     file = "App/Recommender System/topic_model.RDATA")
 ```
@@
 ```
-###Previous code DELETE LATER
-```{r LDA fitxxxxxxx, cache = TRUE}
-n_topics <- c(35, 35, 40)
-levels   <- c("description", "overview", "manual")
-list_nam <- character(0)
-
-for(i in seq_along(n_topics)){
-
-  dataset   <- get(paste("d", levels[i], "cast", sep = "_"))
-
-  LDA_model <- LDA(
-    x       = dataset,
-    k       = n_topics[i],
-    method  = "Gibbs",
-    control = my_control
-    )
-
-  nam <- paste("LDA", levels[i], n_topics[i], sep = "_")
-
-  assign(
-    x     = nam,
-    value = LDA_model
-  )
-
-  list_nam <- c(list_nam, nam)
-
-}
-
-save(list = list_nam,
-     file = "Output/topic_model.RDATA")
-
-save(list = list_nam,
-     file = "App/Recommender System/topic_model.RDATA")
-```
 
@@
 ### Functions 
+This part is adapted 
 ```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(results){
+prepare_data_LDA_beta <- function(d_beta){
 
-  tidy(results, matrix = "beta") %>%
+  data.frame(d_beta) %>%
     mutate(topic = paste("Topic", topic)) %>%
@@
 
-}
+} #repetition??? of inspect topics?
 
-prepare_data_LDA_gamma <- function(results, level = Course){
+prepare_data_LDA_gamma <- function(d_gamma, level = Course){
 
-  data_gamma <- tidy(results, matrix = "gamma") %>%
+  data_gamma <- data.frame(d_gamma) %>%
     mutate(topic = paste("Topic", topic)) %>%
@@
 # Bet Distribution
-LDA_description_120 %>% prepare_data_LDA_beta
+test <- list()
+
+a <-  names(distribution)[1]
+test[[a]] <- lapply(distribution[[a]],
+                      prepare_data_LDA_beta)
 
 # Gamma Distribution
-LDA_description_120 %>% prepare_data_LDA_gamma(level = Cluster)
+b <- names(distribution)[2]
+test[[b]] <- lapply(distribution[[b]],
+                    prepare_data_LDA_gamma)
+
+rm(a,b #,test
+   )
 ```
-
+This part is not adapted
 ```{r LDA visualize, eval = F}

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd
perplexity

@@
 ####10-fold Cross-validation
-TO BE FINISHED
+NOT NEEDED TO BE FINISHED
 ```{r manual evaluation, cache = TRUE, eval = TRUE}
@@
 
-#NEW
-# LDA
 ```{r LDA fit, cache = TRUE, eval = TRUE}
@@
 ##Model Evaluation
+###Perplexity
 Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
@@
 
-#Extracting LDA model n_topics = 2
-test1 <- topic_model$TM_overview[1]
+#perplexity Function
+my_perplexity <- function(model, d_cast){
+  perplexity(model, d_cast, estimate_theta = FALSE)
+}
 
-#Getting A single LDA Model:
-test2 <- test1[[1]]
+#Get perplexity
+topic_test <- topic_model %>%
+  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
+         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
+```
+###log_likelihood
+```{r useless stuff}
+#Useless stuff:
 
-#getting perplexity
-perplexity(test2, d_cast$overview, estimate_theta=FALSE)
+my_loglike <- function(model){
+  return(model@loglikelihood)
+}
+topic_test %>% mutate(loglike_overview = map(.x = TM_overview, .f = my_loglike)) %>% select(n_topic, loglike_overview)
 
-Topic <- topics(test2)
-Terms <- terms(test2,5)
+  for( i in 1:length(topic_model$TM_overview)){
+    tmp <- 
+  }
+}
 
@@
 ```
+#App
 ##Selectig keywords
@@
 
-## Visualization
+# Visualization
 ### Functions 

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute item_g var in d_transactions$G

@@
 
+  mutate(item_g = paste_(item, grade_ceil)) %>%
+
   ungroup()
@@
 ```{r making transactions, cache = TRUE}
-make_transaction <- function(data = d_transactions$taken_PF_HL, item = item){
+make_transaction <- function(data, item){
 
   data %>%
-    group_by(
-      sequenceID
-    ) %>%
-    summarise(
-      list_item = list(unique(!!enquo(item)))
-    ) %>%
+
+    group_by(sequenceID) %>%
+    summarise(list_item = list(unique(!!item))) %>%
     ungroup %>%
-    pull(
-      list_item
-      ) %>%
+
+    pull(list_item) %>%
+
     as("transactions")
@@
 
-#
-# Making transactions
-transactions <- list()
-
-transactions$taken <- make_transaction(item = item   )
-transactions$PF    <- make_transaction(item = item_PF)
-transactions$HL    <- make_transaction(item = item_HL)
-transactions$TPF   <- make_transaction(data = d_transactions$T_PF_HL, item = item_TPF)
-transactions$THL   <- make_transaction(data = d_transactions$T_PF_HL, item = item_THL)
-transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )
-
-# inspect(head(transactions$taken, 10))
+transactions <- tribble(
+  ~ ID   ,  ~ data                    , ~ item,
+  "taken", d_transactions$taken_PF_HL, quo(item),
+  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
+  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
+  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
+  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
+  "G"    , d_transactions$G          , quo(item_g)
+  ) %>%
+
+  mutate(transactions = list(data, item) %>% pmap(make_transaction))
+
+inspect(head(transactions$transactions[[2]], 10))
 ```

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code of make_sequence and use purrr to compute several types of sequences

@@
     pull(list_item) %>%
-
     as("transactions")
@@
 ```{r making sequences, cache = TRUE}
-make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){
+make_sequence <- function(data, item){
 
   data_temp <- data %>%
-    arrange(
-      sequenceID,
-      eventID
-    ) %>%
-    filter(
-      !is.na(eventID) # exclude courses that were never taken.
-      ) %>%
-
-    group_by(
-      sequenceID,
-      eventID
-    ) %>%
-    summarise(
-      list_item = list(unique(!!enquo(item)))
-    ) %>%
+
+    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
+
+    arrange(sequenceID, eventID) %>%
+    group_by(sequenceID, eventID) %>%
+    summarise(list_item = list(unique(!!enquo(item)))) %>%
     ungroup
 
-  sequences <- data_temp %>%
-    pull(
-      list_item
-      ) %>%
-    as("transactions")
-
-  # indicate sequence ID and event ID for each transaction
-  sequences@itemsetInfo <- data_temp %>%
-    select(
-      sequenceID,
-      eventID
-      ) %>%
-    as.data.frame
+  # extract transactions
+  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
+
+  # add attributes fro sequence ID and event ID
+  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
 
@@
 
-#
-# Making sequences
-sequences <- list()
-
-sequences$taken <- make_sequence(item = item   )
-sequences$PF    <- make_sequence(item = item_PF)
-sequences$HL    <- make_sequence(item = item_HL)
-sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )
-
-#inspect(head(sequences$G, 10))
+sequences <- tribble(
+  ~ ID   ,  ~ data                    , ~ item,
+  "taken", d_transactions$taken_PF_HL, quo(item),
+  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
+  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
+  "G"    , d_transactions$G          , quo(item_g)
+  ) %>%
+
+  mutate(sequences = list(data, item) %>% pmap(make_sequence))
+
+inspect(head(sequences$sequences[[2]], 10))
 ```

### 2019-03-13 Topic Scores.Rmd

@@
 ```{r libraries}
-library(tidyverse)
+library(tidyverse) #already in Pillar2
 ```
@@
 ##Raw Data
-```{r setup, include=FALSE}
+```{r setup1, include=FALSE}
 #
 ##Import d_course and d_transcript
-load("Output/data_general.RDATA")
-load("Output/data_pillar_1.RDATA")
+load("Output/data_pillar_1.RDATA") #check if included in pillar 2
+```
 
+```{r setup2, include = FALSE}
 #
 ##Import LDA_models
-load("Output/topic_model.RDATA")
+start.time <- Sys.time()
+load("Output/topic_model_gb.RDATA") #this takes a long time, won't be needed in pillar 2
+end.time <- Sys.time()
+print(start.time-end.time)
+```
 
-rm(lists, d_AoD, d_assessment, d_ILO)
+Cropping model and getting distributions:
+```{r}
+#select number of topics
+n_topics_overview <- 36
+n_topics_manual   <- 40
+
+#Crop models
+TM_overview <- topic_model_gb %>%
+  filter(n_topic== n_topics_overview)
+
+TM_manual   <- topic_model_gb %>%
+  filter(n_topic== n_topics_manual)
+
+#Distributions
+distribution <- list()
+
+distribution$beta$overview  <- TM_overview %>% pull(b_overview)
+distribution$beta$manual    <- TM_manual   %>% pull(b_manual)
+
+distribution$gamma$overview <- TM_overview %>% pull(g_overview)
+distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)
+
 ```
@@
 ##Models in list:
-```{r models in list}
+```{r models in list, eval = FALSE}
 LDA_models <- list()
-LDA_models$description <- LDA_description_35
-LDA_models$overview <- LDA_overview_35
-LDA_models$manual <- LDA_manual_40
+#LDA_models$description <- LDA_description_35 #this is the old code
 
-rm(LDA_description_35, LDA_overview_35, LDA_manual_40)
+LDA_models$overview <- topic_model %>% 
+  filter (n_topic == 36) %>%
+  pull(TM_overview)
+
+LDA_models$manual <- topic_model %>% 
+  filter (n_topic == 40) %>%
+  pull(TM_manual)
+
+#rm(topic_model)
 ```
 
-## Getting Functions (gamma and beta) 
-```{r getting functions}
+## Getting Functions (gamma and beta) this is silenced because we clean before importing
+```{r getting functions, eval = FALSE}
 get_beta <- function(results){
@@
 ##Getting applied (gamma and beta) 
-```{r getting beta and gamma}
+```{r getting beta and gamma, eval = FALSE}
 distribution <- list()
@@
 ##Inspect topics
+THE TOPICS ARE SUPPER STRANGE!
 ```{r inspect topics}
-inspect_topics <- function(d_beta = distribution$beta){
-  d_beta %>%
+
+inspect_topics <- function(d_beta){
+  data.frame(d_beta) %>%
     group_by(topic) %>%
@@
 #View(topics$manual)
-
 ```
@@
 get_top_words <- function(d_beta, n = 3){
-  d_beta %>%
+  data.frame(d_beta) %>%
     group_by(topic) %>%

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
simplify computation of d_support$TNT
base computation of d_support$TNT on transcript_augmented instead of transactions (more appropriate)

@@
 First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
+
+## Support
+
+```{r d_support TNT}
+d_support <- list()
+
+# Probability of taking a course
+d_support$TNT <- d_transcript_augmented %>%
+
+  group_by(`Course ID`) %>%
+
+  mutate(rate.take = n_distinct(`Student ID`) / n_students)
+```
+
 ## Data Preparation
@@
 ## Support
+
 ```{r}
-d_support <- list()
-
-# Probability of taking a course
-d_support$TNT <- d_transactions$taken_PF_HL %>%
-  distinct(
-    item,
-    sequenceID
-    ) %>%
-  count(
-    item
-    ) %>%
-  mutate(
-    rate.take = n / n_students,
-    rate.not  = 1 - rate.take
-    )
-
 #

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute rate.fail and rate.low together with rate.take

@@
 
-# Probability of taking a course
-d_support$TNT <- d_transcript_augmented %>%
+# Probability of taking / failing / obtaining of low grade a course
+d_support$TPH <- d_transcript_augmented %>%
 
@@
 
-  mutate(rate.take = n_distinct(`Student ID`) / n_students)
+  mutate(
+    rate.take = n_distinct(`Student ID`) / n_students,
+    rate.fail = mean(Grade < pass_grade),
+    rate.low  = mean(Grade < high_grade)
+    )
 ```
@@
 # Probability of failing, having a low grade
-d_support$PF_HL <- d_transactions$taken_PF_HL %>%
-  group_by(
-    item
-    ) %>%
-  summarise(
-    rate.fail = mean(PF == "fail"),
-    rate.low  = mean(HL == "low")
-    )
 

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd

@@
 
+#cross-validate
+cross_validate <- function(my_dtm){
+  #Number of documents (D)
+  D <- nrow(my_dtm)
+
+  #Assign documents to a fold
+  folding <- sample(rep(1:10, ceiling(D))[seq_len(D)])
+
+  for(k in n_topics) {
+    for(chain in 1:10){
+      train_set <- my_dtm[folding != chain, ]
+      test_set  <- my_dtm[folding == chain, ]
+
+      training <- my_LDA(k, train_set)
+      testing  <- my_LDA(k, train_set)
+    }
+  }
+}
+
 #
@@
 ```
+
 ##Model Evaluation
@@
 ```
+
 ###log_likelihood
 ```{r useless stuff}
-#Useless stuff:
+# #my_loglikelihood function
+# my_loglike <- function(model){
+#   return(model@loglikelihood)
+# }
+# 
+# #get loglikelihood
+# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
+#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))
 
-my_loglike <- function(model){
-  return(model@loglikelihood)
-}
-topic_test %>% mutate(loglike_overview = map(.x = TM_overview, .f = my_loglike)) %>% select(n_topic, loglike_overview)
-
-  for( i in 1:length(topic_model$TM_overview)){
-    tmp <- 
-  }
-}
-
-lL <- list()
-for(i in 1:length(topic_model$n_topic)){
-
-  tmp <- topic_model$TM_overview[i]
-  lL[[paste("n", 2*i)]] <- tmp[[1]]@loglikelihood
-
-}
-
-test1[[1]]@loglikelihood
-
-log_like <- logLik(test1[[1]])
+#Log likelihood:
+test3 <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
+                               logLik_manual   = map(.x = TM_manual,   .f = logLik))
 
 ```
+
+###Plots
+```{r}
+#perplexity
+plot(topic_test$n_topic, topic_test$perplex_overview)
+plot(topic_test$n_topic, topic_test$perplex_manual)
+
+#log likelihood
+plot(test3$n_topic, test3$logLik_overview)
+plot(test3$n_topic, test3$logLik_manual)
+```
+
 ##Get Beta/Gamma functions

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute rate.grade based on d_transcript_augmented for constistency

@@
 
-## Data Preparation
-
-### Take, fail, low grade
-```{r d_transaction taken_PF_HL}
-d_transactions <- list()
-
-d_transactions$taken_PF_HL <- d_transcript_augmented %>%
-
-  # sequenceID and event ID
-  rename(
-    sequenceID = `Student ID`,
-    eventID = time
-    ) %>%
-
-  # itemID
-  mutate(
-    item    = `Course ID`,
-    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
-    item_HL = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
-    )
-```
-
-### Take / not take, pass / fail / not take
-```{r d_transactions T_PF_HL}
-d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%
-
-  # Expand along students (sequenceID) and courses (itemID) to make missing combinations of student - course explicit
-  complete(sequenceID, item) %>%
-
-  # create a new type of item: "not taken"
-  mutate(
-    item_TPF = if_else(is.na(item_PF), paste_(item, "not"), item_PF),
-    item_THL = if_else(is.na(item_HL), paste_(item, "not"), item_HL)
-    )
-```
-
-### Grade
-```{r transactions grade}
-d_transactions$G <- d_transactions$taken_PF_HL %>%
-
-  mutate(row_of_origin = TRUE) %>%
-
-  complete(
-    nesting(sequenceID, eventID, item, Grade), grade_ceil,
-    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
-    ) %>%
-
-  group_by(sequenceID, eventID, item, Grade) %>%
-
-  distinct(sequenceID, eventID, item, grade_ceil, Grade, row_of_origin) %>% # reminder that we should get rid of duplicates oin d_transcript
-
-  arrange(grade_ceil) %>%
-
-  filter(cumany(row_of_origin)) %>% # only keep grades larger than ceil_grade
-
-  mutate(item_g = paste_(item, grade_ceil)) %>%
-
-  ungroup()
-```
-
-#### Save d_transactions
-```{r save d_transaction}
-save(d_transactions, file = "Output/transaction_df.RDATA")
-```
-
-### Transcript with preceding courses (for SR by hand)
-```{r d_transcript_cum, cache = TRUE}
-d_transcript_cum <- d_transactions$taken_PF_HL %>%
-
-  # item_take
-  mutate(item_take = paste_(item, "take")) %>%
-
-  # current courses
-  group_by(sequenceID, eventID) %>%
-
-  summarize_at(vars(matches("item")), ~ unique(.) %>% list) %>%
-
-  mutate(course_current = list(item, item_take, item_PF, item_HL) %>% pmap(~ c(...) %>% unique)) %>%
-
-  # courses so far, past courses and course not taken yet
-  group_by(sequenceID) %>%
-
-  arrange(eventID) %>%
-
-  mutate(
-    course_so_far  = course_current %>% accumulate(union),
-    course_past    = course_so_far  %>% lag(default = NA_character_),
-    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
-    ) %>%
-
-  ungroup %>%
-
-  # lhs: past courses and courses not taken yet, rhs: current courses
-  mutate(
-    lhs = list(course_past, course_not_yet) %>% pmap(union),
-    rhs = course_current
-    )
-```
-
-## Transactions
-```{r making transactions, cache = TRUE}
-make_transaction <- function(data, item){
-
-  data %>%
-
-    group_by(sequenceID) %>%
-    summarise(list_item = list(unique(!!item))) %>%
-    ungroup %>%
-
-    pull(list_item) %>%
-    as("transactions")
-
-}
-
-transactions <- tribble(
-  ~ ID   ,  ~ data                    , ~ item,
-  "taken", d_transactions$taken_PF_HL, quo(item),
-  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
-  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
-  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
-  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
-  "G"    , d_transactions$G          , quo(item_g)
-  ) %>%
-
-  mutate(transactions = list(data, item) %>% pmap(make_transaction))
-
-inspect(head(transactions$transactions[[2]], 10))
-```
-
-## Sequences
-```{r making sequences, cache = TRUE}
-make_sequence <- function(data, item){
-
-  data_temp <- data %>%
-
-    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
-
-    arrange(sequenceID, eventID) %>%
-    group_by(sequenceID, eventID) %>%
-    summarise(list_item = list(unique(!!enquo(item)))) %>%
-    ungroup
-
-  # extract transactions
-  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
-
-  # add attributes fro sequence ID and event ID
-  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
-
-  return(sequences)
-
-}
-
-sequences <- tribble(
-  ~ ID   ,  ~ data                    , ~ item,
-  "taken", d_transactions$taken_PF_HL, quo(item),
-  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
-  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
-  "G"    , d_transactions$G          , quo(item_g)
-  ) %>%
-
-  mutate(sequences = list(data, item) %>% pmap(make_sequence))
-
-inspect(head(sequences$sequences[[2]], 10))
-```
-
-## Support
-
-```{r}
-#
-# Probability of failing, having a low grade
-
-#
-# Probability oh having a grade equal or lower than x
-d_support$G <- d_transactions$taken_PF_HL %>%
-  group_by(
-    item
-    ) %>%
+```{r d_support G}
+d_support$G <- d_transcript_augmented %>%
+
+  group_by(`Course ID`) %>%
+
   summarise(
@@
   ) %>%
-  gather(
-    key   = grade_ceil,
-    value = support.grade,
-    `0` : `10`,
-    convert = TRUE
-    )
+
+  gather(grade_ceil, rate.grade, `0` : `10`, convert = TRUE)
+```
+
+## Data Preparation
+
+### Take, fail, low grade
+```{r d_transaction taken_PF_HL}
+d_transactions <- list()
+
+d_transactions$taken_PF_HL <- d_transcript_augmented %>%
+
+  # sequenceID and event ID
+  rename(
+    sequenceID = `Student ID`,
+    eventID = time
+    ) %>%
+
+  # itemID
+  mutate(
+    item    = `Course ID`,
+    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
+    item_HL = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
+    )
+```
+
+### Take / not take, pass / fail / not take
+```{r d_transactions T_PF_HL}
+d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%
+
+  # Expand along students (sequenceID) and courses (itemID) to make missing combinations of student - course explicit
+  complete(sequenceID, item) %>%
+
+  # create a new type of item: "not taken"
+  mutate(
+    item_TPF = if_else(is.na(item_PF), paste_(item, "not"), item_PF),
+    item_THL = if_else(is.na(item_HL), paste_(item, "not"), item_HL)
+    )
+```
+
+### Grade
+```{r transactions grade}
+d_transactions$G <- d_transactions$taken_PF_HL %>%
+
+  mutate(row_of_origin = TRUE) %>%
+
+  complete(
+    nesting(sequenceID, eventID, item, Grade), grade_ceil,
+    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
+    ) %>%
+
+  group_by(sequenceID, eventID, item, Grade) %>%
+
+  distinct(sequenceID, eventID, item, grade_ceil, Grade, row_of_origin) %>% # reminder that we should get rid of duplicates oin d_transcript
+
+  arrange(grade_ceil) %>%
+
+  filter(cumany(row_of_origin)) %>% # only keep grades larger than ceil_grade
+
+  mutate(item_g = paste_(item, grade_ceil)) %>%
+
+  ungroup()
+```
+
+#### Save d_transactions
+```{r save d_transaction}
+save(d_transactions, file = "Output/transaction_df.RDATA")
+```
+
+### Transcript with preceding courses (for SR by hand)
+```{r d_transcript_cum, cache = TRUE}
+d_transcript_cum <- d_transactions$taken_PF_HL %>%
+
+  # item_take
+  mutate(item_take = paste_(item, "take")) %>%
+
+  # current courses
+  group_by(sequenceID, eventID) %>%
+
+  summarize_at(vars(matches("item")), ~ unique(.) %>% list) %>%
+
+  mutate(course_current = list(item, item_take, item_PF, item_HL) %>% pmap(~ c(...) %>% unique)) %>%
+
+  # courses so far, past courses and course not taken yet
+  group_by(sequenceID) %>%
+
+  arrange(eventID) %>%
+
+  mutate(
+    course_so_far  = course_current %>% accumulate(union),
+    course_past    = course_so_far  %>% lag(default = NA_character_),
+    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
+    ) %>%
+
+  ungroup %>%
+
+  # lhs: past courses and courses not taken yet, rhs: current courses
+  mutate(
+    lhs = list(course_past, course_not_yet) %>% pmap(union),
+    rhs = course_current
+    )
+```
+
+## Transactions
+```{r making transactions, cache = TRUE}
+make_transaction <- function(data, item){
+
+  data %>%
+
+    group_by(sequenceID) %>%
+    summarise(list_item = list(unique(!!item))) %>%
+    ungroup %>%
+
+    pull(list_item) %>%
+    as("transactions")
+
+}
+
+transactions <- tribble(
+  ~ ID   ,  ~ data                    , ~ item,
+  "taken", d_transactions$taken_PF_HL, quo(item),
+  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
+  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
+  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
+  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
+  "G"    , d_transactions$G          , quo(item_g)
+  ) %>%
+
+  mutate(transactions = list(data, item) %>% pmap(make_transaction))
+
+inspect(head(transactions$transactions[[2]], 10))
+```
+
+## Sequences
+```{r making sequences, cache = TRUE}
+make_sequence <- function(data, item){
+
+  data_temp <- data %>%
+
+    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
+
+    arrange(sequenceID, eventID) %>%
+    group_by(sequenceID, eventID) %>%
+    summarise(list_item = list(unique(!!enquo(item)))) %>%
+    ungroup
+
+  # extract transactions
+  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
+
+  # add attributes fro sequence ID and event ID
+  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
+
+  return(sequences)
+
+}
+
+sequences <- tribble(
+  ~ ID   ,  ~ data                    , ~ item,
+  "taken", d_transactions$taken_PF_HL, quo(item),
+  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
+  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
+  "G"    , d_transactions$G          , quo(item_g)
+  ) %>%
+
+  mutate(sequences = list(data, item) %>% pmap(make_sequence))
+
+inspect(head(sequences$sequences[[2]], 10))
 ```

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
stop caching manually transactions and sequences

@@
 ```{r, include = FALSE}
-save(
-  transactions, sequences,
-  d_transcript_cum,
-  d_support, n_students,
-  file = "Output/Transaction and Sequences.RDATA"
-  )
-```
-
-```{r, include = FALSE}
 rm(
-
-  high_grade, pass_grade, 
-  course_all, student_all, n_students,
-
+  high_grade, pass_grade, course_all, student_all, n_students,
   d_transactions, d_support, d_transcript_cum,
-
-  make_transaction, transactions, 
-  make_sequence, sequences
-
+  make_transaction, transactions, make_sequence, sequences
   )
@@
 # Mining Rules
-
-```{r}
-load("Output/Transaction and Sequences.RDATA")
-```
 

### 2019-03-14 Data Preparation.Rmd
add an issue with d_transcript
create df tailored to pillar 1

@@
 
+d_transcript %>%
+
+  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
+  filter(`Student ID` == "6087587") %>%
+  arrange(`Course ID`) %>%
+  pull(`Course ID`)
+
 #TODO: list issues here
+```
+
+## df tailored to pillar 1
+```{r}
+d_transcript_augmented <- d_transcript %>%  left_join(select(d_course, - Period), by = c("Course ID"))
+
+d_transcript_informative <- d_transcript_augmented %>%
+
+  # Exclude courses taken by majority of students (uninformative)
+  filter(
+    Type != "Mandatory",
+    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
+    ) %>%
+
+  select(`Student ID`, `Course ID`, time, grade_ceil)
 ```
@@
 ```{r}
-save(
-  d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
-  file = "Output/data_general.RDATA"
-  )
+save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")
 
-save(d_transcript, file = "Output/data_pillar_1.RDATA")
+save(d_transcript_augmented, d_transcript_informative, file = "Output/data_pillar_1.RDATA")
 

### 2019-03-14 Data Preparation.Rmd
remove missing value from textual data

@@
     filter(n > 2) %>%
-    select(-n)
+    select(-n) %>%
+
+    # remove NA
+    filter(!is.na(word))
 

### 2019-03-14 Pillar 1 - Sequential Pattern Mining.Rmd

@@
 
-## Transactions
-```{r making transactions, cache = TRUE}
+## Transactions and sequences
+```{r make_transaction}
 make_transaction <- function(data, item){
@@
 }
-
-transactions <- tribble(
-  ~ ID   ,  ~ data                    , ~ item,
-  "taken", d_transactions$taken_PF_HL, quo(item),
-  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
-  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
-  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
-  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
-  "G"    , d_transactions$G          , quo(item_g)
-  ) %>%
-
-  mutate(transactions = list(data, item) %>% pmap(make_transaction))
-
-inspect(head(transactions$transactions[[2]], 10))
 ```
 
-## Sequences
-```{r making sequences, cache = TRUE}
+```{r make_sequence}
 make_sequence <- function(data, item){
+
+  if(item == sym("item_TPF") | item == sym("item_THL")) return("Compute sequences that include courses nto taken yet by hand")
 
@@
 }
+```
 
-sequences <- tribble(
+```{r transactions, cache = TRUE}
+transactions <- tribble(
   ~ ID   ,  ~ data                   , ~ item,
-  "taken", d_transactions$taken_PF_HL, quo(item),
-  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
-  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
-  "G"    , d_transactions$G          , quo(item_g)
+  "taken", d_transactions$taken_PF_HL, sym("item"),
+  "PF"   , d_transactions$taken_PF_HL, sym("item_PF"),
+  "HL"   , d_transactions$taken_PF_HL, sym("item_HL"),
+  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"),
+  "THL"  , d_transactions$T_PF_HL    , sym("item_TPF"),
+  "G"    , d_transactions$G          , sym("item_g")
   ) %>%
 
-  mutate(sequences = list(data, item) %>% pmap(make_sequence))
+  mutate(
+    transactions = list(data, item) %>% pmap(make_transaction),
+    sequences    = list(data, item) %>% pmap(make_sequence   )
+    )
 
-inspect(head(sequences$sequences[[2]], 10))
+inspect(head(transactions$transactions[[3]], 10))
+inspect(head(transactions$sequences   [[3]], 10))
 ```

### 2019-03-14 App/Recommender System/server.R
student id and font size

@@ -253,7 +253,8 @@ function(input, output, session) {
         )
     
     if(nrow(student$transcript)==0){
-      "ERROR: id not found- we need new students ID's before running this"
+      #"ERROR: id not found- we need new students ID's before running this"
+      "ERROR: Student ID not found"
     }else if(nrow(rules) == 0){
       
       "No red flag"

### 2019-03-14 App/Recommender System/ui.R

@@ -33,8 +33,8 @@ navbarPage(
         # Input: student id number
         textInput(
           inputId = "student",
-          label   = "Student ID",
-          value   = "6087587"
+          label   = "Student ID"#,
+          #value   = "6087587"
           ),
         
         uiOutput('resetable_input'),
@@ -117,7 +117,12 @@ navbarPage(
         # Output: dataset
         htmlOutput(
           outputId = "course_recommendation"
-          )
+          ),
+        tags$head(tags$style("#course_recommendation{color: black;
+                                 font-size: 20px;
+                                 }"
+        )
+        )
         
         )
       

### 2019-03-15 DELETE LATER- cross validation.R
cross validation test

@@ -1,0 +1,67 @@
+
+dtm <- AssociatedPress
+
+#
+##crossv_sets
+crossv_sets <- function(dtm){
+  #Setup
+  n_documents <- nrow(dtm)
+  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant
+  
+  #functions
+  create_trainset <- function(Fold){
+    train_set = dtm[folding != Fold,]
+  }
+  
+  create_testset <- function(Fold){
+    test_set  = dtm[folding == Fold,]
+  }
+  
+  #create folds
+  folds <-  data.frame(Fold = 1:10) %>%
+    mutate(train_set = map(Fold, .f = create_trainset),
+           test_set  = map(Fold, .f = create_testset))
+  #
+  ##Output
+  return(folds)
+}
+
+#
+##Testing Application:
+a_test <- d_cast$overview[1:10,]
+
+a <- crossv_sets(a_test)
+  
+b <- a %>% 
+  
+  mutate(n_topic = 2) %>%
+  
+  mutate(model = list(n_topic, train_set) %>% pmap(my_LDA, control = my_control_fast))
+
+#
+## Developing next function
+crossv_model <-  function(sets_dtm) {
+  b <- sets_dtm %>%
+    mutate(n_topic = 2) %>% #we want 
+}
+
+
+
+
+
+
+topic_model <- tibble(
+  
+  n_topic = seq(from = 2, to = 80, by = 2)
+  
+) %>%
+  
+  mutate(
+    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
+    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
+  )
+
+
+
+
+save(d_course, d_transcript, file = "tmp_import_APP.RDATA")

### 2019-03-15 DELETE LATER.R
instructions

@@ -1,4 +1,4 @@
-#saved in workspace
+#saved in workspace  #YOU MUST DELETE n_topics_Find.RDATA
 load("Output/LDA_ntopics.RDATA")
 
 save(result_manual, result_overview , result_description,

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
app changes

@@
 library(ldatuning) # ideal number of topics in LDA
+
+library(modelr) #cross_validation
 ```
@@
 
+```{r}
+my_control_fast <- list(
+
+  nstart = 1,
+  seed   = 1,
+  best   = TRUE,
+
+  burnin = 5,
+  iter   = 10,
+  thin   = 2
+
+)
+```
+
 ###With Package built in Function
@@
 #my_LDA
-my_LDA <- function(n_topics, corpus){
+my_LDA <- function(n_topics, corpus, control = my_control){
 
@@
     method  = "Gibbs",
-    control = my_control
+    control = control
     )
@@
 
-#create folds
-create_folds <- function(my_dtm){
-  #find number of documents (D)
-  D <- nrow(my_dtm)
+this_control <- list(
 
-  #Assign documents to a fold
-  folding <- sample(rep(seq_len(10), ceiling(D))[seq_len(D)])
+  nstart = 10,
+  seed   = 1 : 10,
+  best   = FALSE, #this is different
+
+  burnin = 1000,
+  iter   = 5000,
+  thin   = 100
+
+)
+
+#
+##cross-validate
+
+#crossv_sets returns data.frame with 10-folds divided into train (DTM) and test sets(DTM)
+crossv_sets <- function(dtm){
+  #Setup
+  n_documents <- nrow(dtm)
+  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant
+
+  #functions
+  create_trainset <- function(Fold){
+    train_set = dtm[folding != Fold,]
   }
 
-#cross-validate
+  create_testset <- function(Fold){
+    test_set  = dtm[folding == Fold,]
+  }
+
+  #create folds
+  folds <-  data.frame(Fold = 1:10) %>%
+    mutate(train_set = map(Fold, .f = create_trainset),
+           test_set  = map(Fold, .f = create_testset))
+  return(folds)
+}
+
 cross_validate <- function(my_dtm){
@@
     for(chain in 1:10){
+      #Sets
       train_set <- my_dtm[folding != chain, ]
@@
 
-      training <- my_LDA(k, train_set)
-      testing  <- my_LDA(k, train_set)
+      #LDA
+      training      <- LDA(train_set, k = k, control = my_control, method = "Gibbs")
+
+      #best_training <- training@fitted[[which.max(logLik(training))]]
+      return(perplexity(training, newdata = test_set))
+      #testing  <- my_LDA(test_set, model = best_training, control = list())
     }
@@
 ```{r key words, eval = TRUE}
-get_top_words <- function(d_beta, n = 3){
+get_top_words <- function(d_beta, n = 5){
   data.frame(d_beta) %>%
@@
 )
+```
+####stopwords for keywords
+THIS NEEDS CLEANING!!!!!!!!!!!!!!!!!!!!!!!!!
+```{r}
+#kw$overview
+not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
+                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
+
+remove_words <- function(x){
+  setdiff(x, not_include)
+}
+
+kw1 <- lapply(
+  kw,
+  remove_words
+)
+
 ```
@@
      file = "App/Recommender System/data_topic_models.RDATA")
+save(kw1, file="App/Recommender System/tmp_data.RDATA")#DELETE LATER
 ```

### 2019-03-15 App/Recommender System/server.R

@@ -6,6 +6,7 @@ library(hunspell)
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
 load("data_topic_models.RDATA") #contains distribution, kw, course_all, course_following_semester.
+load("tmp_data.RDATA") #delete later
 
 
 

### 2019-03-15 App/Recommender System/ui.R

@@ -10,6 +10,7 @@ library(shiny)
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
 load("data_topic_models.RDATA") #contains distribution, kw, course_all, course_following_semester.
+load("tmp_data.RDATA") #delete later
 
 
 #
@@ -81,7 +82,7 @@ navbarPage(
         checkboxGroupInput(
           inputId  = "key_words",
           label    = "Academic Interest",
-          choices  = sort(kw$overview),      #***********************************************SELECT: overview/manual
+          choices  = sort(kw1$overview),      #***********************************************SELECT: kw-kw1 overview/manual
           #selected = c("international", "economic", "conflict", "develop", "policy"),
           inline   = TRUE
           ),

### 2019-03-15 App/Recommender System/server.R
deletes useless import

@@ -6,7 +6,6 @@ library(hunspell)
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
 load("data_topic_models.RDATA") #contains distribution, kw, course_all, course_following_semester.
-load("tmp_data.RDATA") #delete later
 
 
 

### 2019-03-15 Misc Code.Rmd
Adding cross validation to miscelaneaous file

@@
 COMMENT SOFIA: save a_clean_transcript as d_transcript
+
+###Cross Validation
+
+```{r}
+#
+##crossv_sets
+crossv_sets <- function(dtm){
+  #Setup
+  n_documents <- nrow(dtm)
+  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant
+
+  #functions
+  create_trainset <- function(Fold){
+    train_set = dtm[folding != Fold,]
+  }
+
+  create_testset <- function(Fold){
+    test_set  = dtm[folding == Fold,]
+  }
+
+  #create folds
+  folds <-  data.frame(Fold = 1:10) %>%
+    mutate(train_set = map(Fold, .f = create_trainset),
+           test_set  = map(Fold, .f = create_testset))
+  #
+  ##Output
+  return(folds)
+}
+
+#
+##Testing Application:
+a_test <- d_cast$overview[1:10,]
+
+a <- crossv_sets(a_test)
+
+b <- a %>%
+
+  mutate(n_topic = 2) %>%
+
+  mutate(model = list(n_topic, train_set) %>% pmap(my_LDA, control = my_control_fast))
+
+```

### 2019-03-15 DELETE LATER- cross validation.R
delete section

@@ -38,30 +38,3 @@ b <- a %>%
   
   mutate(model = list(n_topic, train_set) %>% pmap(my_LDA, control = my_control_fast))
 
-#
-## Developing next function
-crossv_model <-  function(sets_dtm) {
-  b <- sets_dtm %>%
-    mutate(n_topic = 2) %>% #we want 
-}
-
-
-
-
-
-
-topic_model <- tibble(
-  
-  n_topic = seq(from = 2, to = 80, by = 2)
-  
-) %>%
-  
-  mutate(
-    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
-    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
-  )
-
-
-
-
-save(d_course, d_transcript, file = "tmp_import_APP.RDATA")

### 2019-03-15 DELETE LATER- cross validation.R
delete file

@@ -1,40 +1,0 @@
-
-dtm <- AssociatedPress
-
-#
-##crossv_sets
-crossv_sets <- function(dtm){
-  #Setup
-  n_documents <- nrow(dtm)
-  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant
-  
-  #functions
-  create_trainset <- function(Fold){
-    train_set = dtm[folding != Fold,]
-  }
-  
-  create_testset <- function(Fold){
-    test_set  = dtm[folding == Fold,]
-  }
-  
-  #create folds
-  folds <-  data.frame(Fold = 1:10) %>%
-    mutate(train_set = map(Fold, .f = create_trainset),
-           test_set  = map(Fold, .f = create_testset))
-  #
-  ##Output
-  return(folds)
-}
-
-#
-##Testing Application:
-a_test <- d_cast$overview[1:10,]
-
-a <- crossv_sets(a_test)
-  
-b <- a %>% 
-  
-  mutate(n_topic = 2) %>%
-  
-  mutate(model = list(n_topic, train_set) %>% pmap(my_LDA, control = my_control_fast))
-

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
section added for presentation

@@
 ```
-####stopwords for keywords
-THIS NEEDS CLEANING!!!!!!!!!!!!!!!!!!!!!!!!!
-```{r}
+####TEMPORTARY: stopwords for keywords
+This section is for presentations
+```{r stopwords for kw}
 #kw$overview

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
control update

@@
   burnin = 1000,
-  iter   = 5000,
+  iter   = 15000,
   thin   = 100
@@
 ```
+From the results we see that the ideal number of topics is somewhere between 35 and 40.
 
-### Manually
+## Fitting Model
 The function `my_cast_tdm` casts our dataframes into a tdm.
@@
 ```
-####10-fold Cross-validation
-NOT NEEDED TO BE FINISHED
-```{r manual evaluation, cache = TRUE, eval = TRUE}
-set.seed(1234)
 
-#number of topics for trials
-n_topic = seq(from = 2, to = 80, by = 2)
-
-this_control <- list(
-
-  nstart = 10,
-  seed   = 1 : 10,
-  best   = FALSE, #this is different
-
-  burnin = 1000,
-  iter   = 5000,
-  thin   = 100
-
-)
-
-#
-##cross-validate
-
-#crossv_sets returns data.frame with 10-folds divided into train (DTM) and test sets(DTM)
-crossv_sets <- function(dtm){
-  #Setup
-  n_documents <- nrow(dtm)
-  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant
-
-  #functions
-  create_trainset <- function(Fold){
-    train_set = dtm[folding != Fold,]
-  }
-
-  create_testset <- function(Fold){
-    test_set  = dtm[folding == Fold,]
-  }
-
-  #create folds
-  folds <-  data.frame(Fold = 1:10) %>%
-    mutate(train_set = map(Fold, .f = create_trainset),
-           test_set  = map(Fold, .f = create_testset))
-  return(folds)
-}
-
-cross_validate <- function(my_dtm){
-  #Number of documents (D)
-  D <- nrow(my_dtm)
-
-  #Assign documents to a fold
-  folding <- sample(rep(1:10, ceiling(D))[seq_len(D)])
-
-  for(k in n_topics) {
-    for(chain in 1:10){
-      #Sets
-      train_set <- my_dtm[folding != chain, ]
-      test_set  <- my_dtm[folding == chain, ]
-
-      #LDA
-      training      <- LDA(train_set, k = k, control = my_control, method = "Gibbs")
-
-      #best_training <- training@fitted[[which.max(logLik(training))]]
-      return(perplexity(training, newdata = test_set))
-      #testing  <- my_LDA(test_set, model = best_training, control = list())
-    }
-  }
-}
-
-#
-##Create folds
-###Find number of documents
-D_overview <- nrow(d_cast$overview)
-D_manual <- nrow(d_cast$manual)
-
-###Assigning random numbers (1:10) to each row of our DTM
-folding_overview <- sample(rep(seq_len(10), ceiling(D_overview))[seq_len(D_overview)])
-folding_manual   <- sample(rep(seq_len(10), ceiling(D_manual))[seq_len(D_manual)])
-
-for(k in n_topics){
-  for(chain in 1:10){
-    ###Divide into training and testing sets
-      #overview
-    training_set_overview <- d_cast$overview[folding!=chain,]
-    test_set_overview     <- d_cast$overview[folding==chain,]
-      #manual
-    training_set_manual   <- d_cast$manual[folding!=chain,]
-    test_set_manual       <- d_cast$manual[folding==chain,]
-
-  }
-}
-
-```
-## Fitting Model
-From the results we see that the ideal number of topics is somewhere between 35 and 40.
-We train our models on 35 topics.
-Then we save them in the `Output`folder and in the ``Recommender System` folder.
-
+Next we train our model with different number of topics.
 ```{r LDA fit, cache = TRUE, eval = TRUE}
@@
 
-  n_topic = seq(from = 2, to = 80, by = 2)
+  n_topic = seq(from = 2, to = 150, by = 2)
 

### 2019-03-15 Pillar 2 - Topic Modeling.Rmd
n_topics from 5 to 250 by 5
lables
eval = T for run on UM computer

@@
 
-```{r}
+```{r fast control}
 my_control_fast <- list(
@@
 
-  n_topic = seq(from = 2, to = 150, by = 2)
+  n_topic = seq(from = 5, to = 250, by = 5)
 
@@
 Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
-```{r}
+```{r perplexity function, eval = TRUE}
 
@@
 #Get perplexity
-topic_test <- topic_model %>%
+test_perplexity <- topic_model %>%
   mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
@@
 ###log_likelihood
-```{r useless stuff}
+```{r log likelihood, eval = TRUE}
 # #my_loglikelihood function
@@
 #Log likelihood:
-test3 <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
+test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                                logLik_manual   = map(.x = TM_manual,   .f = logLik))
@@
 ###Plots
-```{r}
+```{r perplexity plots, eval = TRUE}
 #perplexity
@@
 ```
-
+##Saving filed for different sessions
+```{r saving, eval = TRUE}
+save(topic_model_gb, 
+     file = "Output/topic_model_gb.RDATA")
+```
+#Distributions
+#NOTE: We need to select how many topics to use
 ##Distributions of best models
-```{r Distributions, eval = TRUE}
+```{r Distributions, eval = FALSE}
 #select number of topics
@@
 THE TOPICS ARE SUPPER STRANGE!
-```{r inspect topics, eval = T}
+```{r inspect topics, eval = FALSE}
 
@@
 ##Selectig keywords
-```{r key words, eval = TRUE}
+```{r key words}
 get_top_words <- function(d_beta, n = 5){
@@
 ##Convenience vectors for APP
-```{r for convenience, eval = T}
+```{r for convenience}
 # set seed
@@
      file = "App/Recommender System/data_topic_models.RDATA")
-save(kw1, file="App/Recommender System/tmp_data.RDATA")#DELETE LATER
 ```

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
Delete useless library
graphing functions (works with d_text)

@@
 
-library(modelr) #cross_validation
 ```
@@
 ```
+#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
+Include d_course
+```{r d_course}
+load("Output/data_general.RDATA")
+d_course <- d_course %>% select(`Course ID`, Cluster) %>% distinct
 
+rm(d_AoD, d_assessment, d_ILO)
+```
 # TF-IDF
@@
 ```{r compute_tf_idf, cache = TRUE}
+#
+##Function
 compute_tf_idf <- function(data){
@@
 
-tf_idf_description <- compute_tf_idf(d_description)
-tf_idf_overview    <- compute_tf_idf(d_overview)
-tf_idf_manual      <- compute_tf_idf(d_manual)
+#
+##Application
+tf_idf <- map(d_text, .f = compute_tf_idf)
 
+#
+##Clean workspace
 rm(compute_tf_idf)
@@
 set.seed(123)
-tf_idf_description %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_description")
-
-set.seed(123)
-tf_idf_overview %>%
+tf_idf$overview %>%
   prepare_tf_idf_course %>%
@@
 set.seed(123)
-tf_idf_manual %>%
+tf_idf$manual %>%
   prepare_tf_idf_course %>%
@@
 
-tf_idf_description %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_description")
-
-tf_idf_overview %>%
+tf_idf$overview %>%
   prepare_tf_idf_cluster %>%
@@
 
-tf_idf_manual %>%
+tf_idf$manual %>%
   prepare_tf_idf_cluster %>%

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
rearrange sections

@@
 load("Output/data_general.RDATA")
-d_course <- d_course %>% select(`Course ID`, Cluster) %>% distinct
 
@@
 
-tf_idf_description %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_description")
-
-tf_idf_overview %>%
+tf_idf$overview %>%
   prepare_tf_idf_concentration %>%
@@
 
-tf_idf_manual %>%
+tf_idf$manual %>%
   prepare_tf_idf_concentration %>%
@@
 
-rm(prepare_tf_idf_concentration, plot_tf_idf,
-   tf_idf_description, tf_idf_overview, tf_idf_manual)
+rm(prepare_tf_idf_concentration, plot_tf_idf)
 ```
@@
 # LDA
-The function `my_cast_tdm` casts our dataframes into a tdm.
-```{r my_cast_tdmxxxxx}
-my_cast_tdm <- function(data, level) data %>%
+##Setup
+###Cast DTM
+The function `my_cast_dtm` casts our dataframes into a DTM.
+```{r my_cast_dtm, eval = TRUE}
+my_cast_dtm <- function(data) data %>%
   count(`Course ID`, word) %>%
@@
 
-d_description_cast <- my_cast_tdm(d_description)
-d_overview_cast <- my_cast_tdm(d_overview)
-d_manual_cast <- my_cast_tdm(d_manual)
+d_cast <- d_text %>% map(my_cast_dtm)
 
-rm(my_cast_tdm)
+rm(my_cast_dtm)
 ```
-
-## Ideal Number of Topics (RUN ON UM COMPUTER)
-To decide the number of topics to discover, we run (four) three different tests.
-
-First we set the control for the test.
+###Controls
+The control parameters we use are:
 ```{r controls, eval = TRUE}
@@
 ```
-
+The control parameters we use for fast testing are:
 ```{r fast control}
@@
 
-###With Package built in Function
+##Ideal Number of Topics Package Test
+To decide the number of topics to discover, we run three different tests.
 The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
removes repeated code (my_cast_dtm)

@@
 ## Fitting Model
-The function `my_cast_tdm` casts our dataframes into a tdm.
-```{r my_cast_tdm, eval = TRUE}
-my_cast_tdm <- function(data) data %>%
-  count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
-
-d_cast <- d_text %>% map(my_cast_tdm)
-
-rm(my_cast_tdm)
-```
-
 The function `my_LDA` fits an LDA model on the DTM using the previous controls.
 ```{r my_LDA, eval= TRUE}
-
-#my_LDA
 my_LDA <- function(n_topics, corpus, control = my_control){
@@
 
-Next we train our model with different number of topics.
+We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
 ```{r LDA fit, cache = TRUE, eval = TRUE}
@@
 ###Perplexity
-Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
+Perplexity is a measure of how well a probability model predicts a sample. (Thus may want to do cross validation.) 
 ```{r perplexity function, eval = TRUE}

### 2019-03-18 Pillar 2 - Topic Modeling.Rmd
typo in test likelihood

@@
 
-rm(d_AoD, d_assessment, d_ILO)
+rm(d_AoD, d_assessment, d_ILO, list_AoD_assessment)
 ```
@@
 ```
+#DELETE LATERRRRRR- HELPER IMPORT
+```{r}
+load("Output/topic_model.RDATA")
+```
 
@@
 ```{r log likelihood, eval = TRUE}
-# #my_loglikelihood function
-# my_loglike <- function(model){
-#   return(model@loglikelihood)
-# }
-# 
-# #get loglikelihood
-# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
-#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))
-
 #Log likelihood:
-test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
+test_likelihood <- topic_model %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                                          logLik_manual   = map(.x = TM_manual,   .f = logLik))
@@
 #perplexity
-plot(topic_test$n_topic, topic_test$perplex_overview)
-plot(topic_test$n_topic, topic_test$perplex_manual)
+plot(test_perplexity$n_topic, test_perplexity$perplex_overview)
+plot(test_perplexity$n_topic, test_perplexity$perplex_manual)
 
 #log likelihood
-plot(test3$n_topic, test3$logLik_overview)
-plot(test3$n_topic, test3$logLik_manual)
+plot(test_likelihood$n_topic, test_likelihood$logLik_overview)
+plot(test_likelihood$n_topic, test_likelihood$logLik_manual)
 ```
@@
 ##Saving filed for different sessions
+For internal use:
+```{r}
+# save(topic_model, file = "Output/topic_model.RDATA" )
+```
+For different sessions:
 ```{r saving, eval = TRUE}
@@
 ##Inspect topics
-THE TOPICS ARE SUPPER STRANGE!
 ```{r inspect topics, eval = FALSE}

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
Extracting and Plotting Functions for models

@@
 We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
+##Functions for models (get gamma, get beta, extract_dtm)
+```{r getting gamma and beta, eval = TRUE}
+#extract dtm
+extract_dtm <- function(wt) d_cast[[wt]]
+
+# #get beta
+# get_beta <- function(results){
+#   
+#   tidy(results, matrix = "beta")           %>%
+#     mutate(topic = paste("Topic", topic) ) %>%
+#       arrange(topic, desc(beta) )
+#   
+# }
+# 
+# #get gamma
+# get_gamma <- function(results){
+#   
+#   tidy(results, matrix = "gamma")          %>%
+#     mutate(topic = paste("Topic", topic) ) %>%
+#       arrange(topic, desc(gamma) )
+# }
+
+get_distributions <- function(model, distrib_str){ #input gamma or beta
+  tidy(model, matrix = distrib_str)        %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(!!sym(distrib_str)))
+}
+
+#perplexity Function
+my_perplexity <- function(model, d_cast){
+  perplexity(model, d_cast, estimate_theta = FALSE)
+}
+
+my_logLik <-  function (model)
+
+```
+
 ```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_model <- tibble(
 
-  n_topic = seq(from = 5, to = 250, by = 5)
+test_topic_model <- tibble( #change to topic_model
+  #repeat each topic number twice
+  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5
 
   ) %>%
+  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
+         `Topic ID` = paste(Origin, n_topic, sep = "_"),
+         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
 
-  mutate(
-    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
-    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
+         #fit model
+         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),
+
+         #Gamma distribution
+         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+
+         #Beta distribution
+         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
+
+         #Perplexity
+         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
+
+         #Loglikelihood
+         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik) #this removes the degrees of freedom data
          )
+
 ```
@@
 ##Model Evaluation
-###Perplexity
-Perplexity is a measure of how well a probability model predicts a sample. (Thus may want to do cross validation.) 
-```{r perplexity function, eval = TRUE}
-
-#perplexity Function
-my_perplexity <- function(model, d_cast){
-  perplexity(model, d_cast, estimate_theta = FALSE)
-}
-
-#Get perplexity
-test_perplexity <- topic_model %>%
-  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
-         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
-```
-
-###log_likelihood
-```{r log likelihood, eval = TRUE}
-#Log likelihood:
-test_likelihood <- topic_model %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
-                                         logLik_manual   = map(.x = TM_manual,   .f = logLik))
-
-```
-
 ###Plots
 ```{r perplexity plots, eval = TRUE}
-#perplexity
-plot(test_perplexity$n_topic, test_perplexity$perplex_overview)
-plot(test_perplexity$n_topic, test_perplexity$perplex_manual)
+#plot evaluation
+plot_evaluation <- function(){
 
-#log likelihood
-plot(test_likelihood$n_topic, test_likelihood$logLik_overview)
-plot(test_likelihood$n_topic, test_likelihood$logLik_manual)
-```
+  #data
+  test_topic_model %>%
 
-##Get Beta/Gamma functions
-```{r getting gamma and beta, eval = TRUE}
-get_beta <- function(results){
+    #Wrangling
+    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
 
-  tidy(results, matrix = "beta")           %>%
-    mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(beta) )
+    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
+
+    #Graphics
+    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
+    geom_point() +
+    facet_wrap(`Eval Type` ~ Origin, scales = "free") +
+    theme_minimal()
 
@@
 
-get_gamma <- function(results){
-
-  tidy(results, matrix = "gamma")          %>%
-    mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(gamma) )
-}
-
+plot_evaluation()
 ```
@@
 n_topics_manual   <- 40
+
+extract_overview <- function() topic_model_gb %>% filter(n_topic == n_topics_overview)
+extract_manual   <- function() topic_model_gb %>% filter(n_topic == n_topics_manual  )
+
+df %>% mutate(var_new = list(var_old1, var_old2) %>% pmap(my_function))
+
+data <- tribble(
+  ~ ID,
+  "overview",
+  "manual"
+  ) %>%
+  mutate(df = if_else(ID == "overview", extract_overview(), extract_manual))
 

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
deleting redundant code

@@
 #extract dtm
-extract_dtm <- function(wt) d_cast[[wt]]
+extract_dtm <- function(origin) d_cast[[origin]]
 
-# #get beta
-# get_beta <- function(results){
-#   
-#   tidy(results, matrix = "beta")           %>%
-#     mutate(topic = paste("Topic", topic) ) %>%
-#       arrange(topic, desc(beta) )
-#   
-# }
-# 
-# #get gamma
-# get_gamma <- function(results){
-#   
-#   tidy(results, matrix = "gamma")          %>%
-#     mutate(topic = paste("Topic", topic) ) %>%
-#       arrange(topic, desc(gamma) )
-# }
-
+#extract Distributions (Gamma/Beta)
 get_distributions <- function(model, distrib_str){ #input gamma or beta
@@
 #perplexity Function
-my_perplexity <- function(model, d_cast){
-  perplexity(model, d_cast, estimate_theta = FALSE)
+my_perplexity <- function(model, dtm){
+  perplexity(model, dtm, estimate_theta = FALSE)
 }
-
-my_logLik <-  function (model)
 
@@
 
+#View(test_topic_model)
+test_topic_model
 ```
@@
 ```{r perplexity plots, eval = TRUE}
-#plot evaluation
+#Function
 plot_evaluation <- function(){
@@
 
+#Plot
 plot_evaluation()
@@
 
-##Apply beta and gamma
-```{r applying get_gamma and get_beta, eval = TRUE}
-topic_model_gb <- topic_model %>%
-  transmute(
-    n_topic    = n_topic,
-    g_overview = TM_overview %>% map( .f = get_gamma),
-    g_manual   = TM_manual   %>% map( .f = get_gamma),
-    b_overview = TM_overview %>% map( .f = get_beta),
-    b_manual   = TM_manual   %>% map( .f = get_beta)
-      )
-```
 ##Saving filed for different sessions
@@
 ```
-For different sessions:
-```{r saving, eval = TRUE}
-save(topic_model_gb, 
-     file = "Output/topic_model_gb.RDATA")
-```
+
 #Distributions

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
get topic terms

@@
 ```
-#DELETE LATERRRRRRRRRRRRRRRRRRRRRRRRRRRRRR
-Include d_course
-```{r d_course}
-load("Output/data_general.RDATA")
 
-rm(d_AoD, d_assessment, d_ILO, list_AoD_assessment)
-```
 # TF-IDF
@@
 We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
-##Functions for models (get gamma, get beta, extract_dtm)
+###Functions for models (get gamma, get beta, extract_dtm)
 ```{r getting gamma and beta, eval = TRUE}
@@
 ```
-
+###Training Models
 ```{r LDA fit, cache = TRUE, eval = TRUE}
@@
 #Function
-plot_evaluation <- function(){
+plot_evaluation <- function(origin){
 
@@
     select(n_topic, Origin, Perplexity, LogLikelihood) %>%
-
     gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
+    filter(Origin == origin) %>%
 
@@
     geom_point() +
-    facet_wrap(`Eval Type` ~ Origin, scales = "free") +
+    geom_line() +
+    facet_grid(rows = vars(`Eval Type`), scales = "free") +
     theme_minimal()
@@
 #Plot
-plot_evaluation()
+plot_evaluation("overview")
+plot_evaluation("manuals")
 ```
 
-##Saving filed for different sessions
+##Saving model_data:
 For internal use:
 ```{r}
-# save(topic_model, file = "Output/topic_model.RDATA" )
+# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
 ```
@@
 #Distributions
-#NOTE: We need to select how many topics to use
+#NOTE: select how many topics to use
+
 ##Distributions of best models
@@
 
-inspect_topics <- function(d_beta){
+# FUNCTION
+#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
+get_top_match <- function(d_distribution){
+  print(!!sym(d_distribution))
+}
+Hi <- "hello"
+get_top_match(Hi)
+
+get_top_terms_topic <- function(d_beta){
   data.frame(d_beta) %>%
     group_by(topic) %>%
-    top_n(10, beta)
+    top_n(10, beta) %>%
+    select(topic, term) %>%
+    group_by(topic) %>%
+    summarise(top_words = list(term))
 
@@
 
-topics <-  lapply(
-  distribution$beta,
-  inspect_topics
-)
+get_top_topics_course <- function(d_gamma){
+  data.frame(d_gamma) %>%
+    group_by(document) %>%
+    top_n(5, gamma) %>%
+    select(document, topic) %>%
+    summarise(top_topic = list(topic))
+}
+
+get_kw <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(10, beta) %>%
+    select(topic, term) %>%
+    group_by(topic) %>%
+    summarise(top_words = list(term)) %>%
+    select(top_words) %>%
+    collapse(top_words)
+}
+#Saving to models
+test_topic_model <-  test_topic_model %>%
+  mutate(top_terms_topic = map(Beta, .f = get_top_terms_topic))
+
+test_topic_model <- test_topic_model %>%
+  mutate(top_topic_course = map(Gamma, .f = get_top_topics_course))
+
 ```
@@
 
+go_down <- function(my_list, i){
+  my_list[[i]]
+}
+
+get_key_words <-  function(d_top_words){
+
+  select(top_words) %>%
+    top_n(5)
+}
+
+View(test_topic_model)
+
+a <- test_topic_model[["top_terms_topic"]]
+
+d_top_words <- a[1]
+
+#mutate(kw = get_key_words(top_terms_topic)) 
+d_top_words <- a$top_terms_topic
+
 kw <- lapply(
@@
 )
+
 ```

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
all transformations in one tibble

@@
 ```
+
+The following functions allow us to inspect the distributions and get kw
+```{r}
+# FUNCTION
+#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
+
+# get_top_match <- function(d_distribution){
+#   print(!!sym(d_distribution))
+# }
+
+get_top_terms_topic <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(10, beta) %>%
+    select(topic, term) %>%
+    group_by(topic) %>%
+    summarise(top_words = list(term))
+
+}
+
+get_top_topics_course <- function(d_gamma){
+  data.frame(d_gamma) %>%
+    group_by(document) %>%
+    top_n(5, gamma) %>%
+    select(document, topic) %>%
+    summarise(top_topic = list(topic))
+}
+
+get_kw <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(3, beta) %>%
+    ungroup()%>%
+    pull(term)%>%
+    unique()
+}
+
+```
 ###Training Models
@@
          #Loglikelihood
-         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik) #this removes the degrees of freedom data
+         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
+
+         #
+         ##Inspect
+
+         #top words per topic
+         top_terms_topic = map(Beta, .f = get_top_terms_topic),
+
+         #top topics per course
+         top_topic_course = map(Gamma, .f = get_top_topics_course),
+
+         #selecting keywords
+         kw = map(Beta, .f = get_kw)
          )
@@
 
-#Distributions
-#NOTE: select how many topics to use
-
-##Distributions of best models
-```{r Distributions, eval = FALSE}
-#select number of topics
-n_topics_overview <- 36
-n_topics_manual   <- 40
-
-extract_overview <- function() topic_model_gb %>% filter(n_topic == n_topics_overview)
-extract_manual   <- function() topic_model_gb %>% filter(n_topic == n_topics_manual  )
-
-df %>% mutate(var_new = list(var_old1, var_old2) %>% pmap(my_function))
-
-data <- tribble(
-  ~ ID,
-  "overview",
-  "manual"
-  ) %>%
-  mutate(df = if_else(ID == "overview", extract_overview(), extract_manual))
-
-#Crop models
-TM_overview <- topic_model_gb %>%
-  filter(n_topic== n_topics_overview)
-
-TM_manual   <- topic_model_gb %>%
-  filter(n_topic== n_topics_manual)
-
-#Distributions
-distribution <- list()
-
-distribution$beta$overview  <- TM_overview %>% pull(b_overview)
-distribution$beta$manual    <- TM_manual   %>% pull(b_manual)
-
-distribution$gamma$overview <- TM_overview %>% pull(g_overview)
-distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)
-
-```
-##Inspect topics
-```{r inspect topics, eval = FALSE}
-
-# FUNCTION
-#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
-get_top_match <- function(d_distribution){
-  print(!!sym(d_distribution))
-}
-Hi <- "hello"
-get_top_match(Hi)
-
-get_top_terms_topic <- function(d_beta){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(10, beta) %>%
-    select(topic, term) %>%
-    group_by(topic) %>%
-    summarise(top_words = list(term))
-
-}
-
-get_top_topics_course <- function(d_gamma){
-  data.frame(d_gamma) %>%
-    group_by(document) %>%
-    top_n(5, gamma) %>%
-    select(document, topic) %>%
-    summarise(top_topic = list(topic))
-}
-
-get_kw <- function(d_beta){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(10, beta) %>%
-    select(topic, term) %>%
-    group_by(topic) %>%
-    summarise(top_words = list(term)) %>%
-    select(top_words) %>%
-    collapse(top_words)
-}
-#Saving to models
-test_topic_model <-  test_topic_model %>%
-  mutate(top_terms_topic = map(Beta, .f = get_top_terms_topic))
-
-test_topic_model <- test_topic_model %>%
-  mutate(top_topic_course = map(Gamma, .f = get_top_topics_course))
-
-```
 #App
-##Selectig keywords
-```{r key words}
-get_top_words <- function(d_beta, n = 5){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(n, beta) %>%
-    pull(term)%>%
-    unique
-}
-
-go_down <- function(my_list, i){
-  my_list[[i]]
-}
-
-get_key_words <-  function(d_top_words){
-
-  select(top_words) %>%
-    top_n(5)
-}
-
-View(test_topic_model)
-
-a <- test_topic_model[["top_terms_topic"]]
-
-d_top_words <- a[1]
-
-#mutate(kw = get_key_words(top_terms_topic)) 
-d_top_words <- a$top_terms_topic
-
-kw <- lapply(
-  distribution$beta,
-  get_top_words
-)
-
-```
 ####TEMPORTARY: stopwords for keywords
@@
 ```
-
 # Visualization
@@
 
-rm(a,b #,test
-   )
+rm(a,b #,test)
 ```

### 2019-03-20 Pillar 2 - Topic Modeling.Rmd
starting to clean lda fit test

@@
 library(ggthemes)
-library(rlang)
+library(rlang) #quote
 library(ldatuning) # ideal number of topics in LDA
@@
   method = "Gibbs",
-  control = my_control,
+  control = my_control_fast,
   mc.cores = 4L
@@
 ```
-We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
-```{r description topics, cache = TRUE}
+
+```{r package test on topics, cache = TRUE}
 start.time <- Sys.time()
 
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
+result_topic_test <- map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 15, by = 5))
 
@@
 
-save(result_description,
-     file = "Output/LDA_ntopics.RDATA")
+#save(result_topic_test,
+#     file = "Output/LDA_ntopics.RDATA")
 
@@
 
-save(result_overview , result_description,
+save(result_overview ,
      file = "Output/LDA_ntopics.RDATA")
@@
 
-save(result_manual, result_overview , result_description,
+save(result_manual, result_overview ,
      file = "Output/LDA_ntopics.RDATA")
@@
 # FUNCTION
-#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
-
+# #get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
+# 
 #  get_top_match <- function(d_distribution){
-#   print(!!sym(d_distribution))
+#    
+#   #save user input as string
+#   name_selected <- deparse(substitute(d_distribution))
+#   beta_gamma_sym <- tolower(name_selected)
+#   
+#   #prepare variables for grouping
+#   grouping <- ifelse(name_selected == "Beta", "topic", "document")
+#   top_num <- ifelse(name_selected  == "Beta", 10, 5) #select how many terms or topics(respectively) to show
+#   
 #  }
@@
 
-##Model Evaluation
-###Plots
+##Plots - Model Evaluation
 ```{r perplexity plots, eval = TRUE}

### 2019-03-21 Pillar 1 - Sequential Pattern Mining.Rmd
create less verbose code with purrr::pmap

@@
 library(arulesSequences)
+library(magrittr)
 ```
+
+TODO: simplify support into one df: var1 = course id, var2 = type, var3 = rate
+
+AR with not taken on lhs is not useful.
 
@@
 ```{r loading data}
-load("Output/data_general.RDATA")
 load("Output/data_pillar_1.RDATA")
@@
 ```{r helper function}
-# helper function
-join_d_course     <- function(df) df %>% left_join(select(d_course, - Period), by = c("Course ID"))
-
 paste_ <- function(...) paste(..., sep = "_")
@@
 
-```{r d_course_informative}
-d_transcript_augmented <- d_transcript %>%
+```{r constants}
+course_all  <- unique(d_transcript_informative$`Course ID` )
+student_all <- unique(d_transcript_informative$`Student ID`)
+n_students  <- length(student_all)
 
-  join_d_course %>%
-
-  # Exclude courses taken by majority of students (uninformative)
-  filter(
-    Type != "Mandatory",
-    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
-    )
-```
-
-```{r constants}
-course_all  <- unique(d_transcript_augmented$`Course ID` )
-student_all <- unique(d_transcript_augmented$`Student ID`)
-n_students  <- length(student_all)
+pass_grade <- 5.5
+high_grade <- 6.5
 ```
@@
 
-```{r statistics set up}
-pass_grade <- 5.5
-high_grade <- 6.5
-```
-
 ```{r provide_statistics}
 # helper function
-provide_statistics <- function(var, df = d_transcript, high_gr = high_grade, pass_gr = pass_grade, join = TRUE){
-
-  if(join) df <- df %>% join_d_course
+provide_statistics <- function(var, df = d_transcript_augmented, high_gr = high_grade, pass_gr = pass_grade){
 
@@
 # Concentration level
-statistics$concentration <- d_transcript %>%
-  join_d_course %>%
+statistics$concentration <- d_transcript_augmented %>%
   gather(
@@
     ) %>%
-  provide_statistics(Concentration, df = ., join = FALSE)
+  provide_statistics(Concentration, df = .)
 
@@
 
-# Creating Transactions and Sequences
-For a first exploration of arules, we conceptualise our framework like this:
-transaction = student
-item = course
-
-First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
-
-## Support
-
+# Support
 ```{r d_support TNT}
@@
 # Probability of taking / failing / obtaining of low grade a course
-d_support$TPH <- d_transcript_augmented %>%
+d_support$TPH <- d_transcript_informative %>%
 
@@
 
-  mutate(
+  summarise(
     rate.take = n_distinct(`Student ID`) / n_students,
@@
 ```{r d_support G}
-d_support$G <- d_transcript_augmented %>%
+d_support$G <- d_transcript_informative %>%
 
@@
 
-## Data Preparation
+# transactions and sequences
+For a first exploration of arules, we conceptualise our framework like this:
+transaction = student
+item = course
 
-### Take, fail, low grade
-```{r d_transaction taken_PF_HL}
+First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
+
+```{r d_transactions}
 d_transactions <- list()
+```
 
-d_transactions$taken_PF_HL <- d_transcript_augmented %>%
+## taken_PF_HL
+```{r taken_PF_HL}
+d_transactions$taken_PF_HL <- d_transcript_informative %>%
 
@@
 
-### Take / not take, pass / fail / not take
-```{r d_transactions T_PF_HL}
+## T_PF_HL (not taken pass/fail high/low)
+```{r T_PF_HL}
 d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%
@@
 
-### Grade
+## Grade
 ```{r transactions grade}
@@
 
-  mutate(row_of_origin = TRUE) %>%
+  mutate(row_of_origin = TRUE) %>%     # non-missing row_of_origin are TRUE
 
@@
     nesting(sequenceID, eventID, item, Grade), grade_ceil,
-    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
+    fill = list(row_of_origin = FALSE) # missing row_of_origin are FALSE
     ) %>%
@@
 
-#### Save d_transactions
-```{r save d_transaction}
-save(d_transactions, file = "Output/transaction_df.RDATA")
+## making transactions and sequence
+```{r make_transaction}
+make_transaction <- function(data, item){
+
+  data %>%
+
+    group_by(sequenceID) %>%
+    summarise(list_item = list(unique(!!item))) %>%
+    ungroup %$%
+
+    as(list_item, "transactions")
+
+}
 ```
 
-### Transcript with preceding courses (for SR by hand)
+```{r make_sequence}
+make_sequence <- function(ID, data, item){
+
+  if(ID %in% c("TPF", "THL")) return("Compute sequences including courses not taken yet by hand")
+
+  data_temp <- data %>%
+
+    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
+
+    arrange(sequenceID, eventID) %>%
+    group_by(sequenceID, eventID) %>%
+    summarise(list_item = list(unique(!!enquo(item)))) %>%
+    ungroup
+
+  # extract transactions
+  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
+
+  # add attributes fro sequence ID and event ID
+  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
+
+  return(sequences)
+
+}
+```
+
+```{r data_general}
+data_general <- tribble(
+  ~ ID   ,  ~ data                   , ~ item         , ~ data_support, ~ var_support    , ~ suffix_lhs , ~ suffix_rhs ,
+  "taken", d_transactions$taken_PF_HL, sym("item"    ), d_support$TPH , sym("rate.take" ), NA_character_, NA_character_,
+  "PF"   , d_transactions$taken_PF_HL, sym("item_PF" ), d_support$TPH , sym("rate.fail" ), "fail"       , "fail"       ,
+  "HL"   , d_transactions$taken_PF_HL, sym("item_HL" ), d_support$TPH , sym("rate.low"  ), "low"        , "low"        ,
+  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"), d_support$TPH , sym("rate.fail" ), "not"        , "fail"       ,
+  "THL"  , d_transactions$T_PF_HL    , sym("item_THL"), d_support$TPH , sym("rate.low"  ), "not"        , "low"        ,   
+  "G"    , d_transactions$G          , sym("item_g"  ), d_support$G   , sym("rate.grade"), "_7"         , "_7"
+  )
+```
+
+```{r transactions sequences}
+data_general <- data_general %>%
+
+  mutate(
+    transactions = list(    data, item) %>% pmap(make_transaction),
+    sequences    = list(ID, data, item) %>% pmap(make_sequence)
+    ) %>%
+
+  select(-data) # for memory requirement
+
+arules::inspect(head(data_general$transactions[[3]], 10))
+arules::inspect(head(data_general$sequences   [[3]], 10))
+```
+
+# Transcript with preceding courses
 ```{r d_transcript_cum, cache = TRUE}
@@
     rhs = course_current
-    )
-```
-
-## Transactions and sequences
-```{r make_transaction}
-make_transaction <- function(data, item){
-
-  data %>%
-
-    group_by(sequenceID) %>%
-    summarise(list_item = list(unique(!!item))) %>%
-    ungroup %>%
-
-    pull(list_item) %>%
-    as("transactions")
-
-}
-```
-
-```{r make_sequence}
-make_sequence <- function(data, item){
-
-  if(item == sym("item_TPF") | item == sym("item_THL")) return("Compute sequences that include courses nto taken yet by hand")
-
-  data_temp <- data %>%
-
-    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
-
-    arrange(sequenceID, eventID) %>%
-    group_by(sequenceID, eventID) %>%
-    summarise(list_item = list(unique(!!enquo(item)))) %>%
-    ungroup
-
-  # extract transactions
-  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
-
-  # add attributes fro sequence ID and event ID
-  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
-
-  return(sequences)
-
-}
-```
-
-```{r transactions, cache = TRUE}
-transactions <- tribble(
-  ~ ID   ,  ~ data                   , ~ item,
-  "taken", d_transactions$taken_PF_HL, sym("item"),
-  "PF"   , d_transactions$taken_PF_HL, sym("item_PF"),
-  "HL"   , d_transactions$taken_PF_HL, sym("item_HL"),
-  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"),
-  "THL"  , d_transactions$T_PF_HL    , sym("item_TPF"),
-  "G"    , d_transactions$G          , sym("item_g")
     ) %>%
 
-  mutate(
-    transactions = list(data, item) %>% pmap(make_transaction),
-    sequences    = list(data, item) %>% pmap(make_sequence   )
-    )
-
-inspect(head(transactions$transactions[[3]], 10))
-inspect(head(transactions$sequences   [[3]], 10))
+  select(lhs, rhs) # for memory requirement
 ```
@@
 rm(
-  high_grade, pass_grade, course_all, student_all, n_students,
-  d_transactions, d_support, d_transcript_cum,
-  make_transaction, transactions, make_sequence, sequences
+  high_grade, pass_grade, course_all, student_all,
+  make_transaction, make_sequence
   )
@@
 
-## Functions
+## Helper functions
 
-### my_aprior, my_cspade and my_ruleInduction
+```{r}
+count_min   <- 1
+support_min <- count_min / n_students
+
+confidence_min <- 1e-3
+```
+
+```{r separate_lhs}
+separate_lhs <- function(df) df %>% separate(col = lhs , into = c("lhs_course", "lhs_outcome"), remove  = FALSE, convert = TRUE)
+```
+
+```{r separate_rhs}
+separate_rhs <- function(df) df %>% separate(col = rhs , into = c("rhs_course", "rhs_outcome"), remove  = FALSE, convert = TRUE)
+```
+
+```{r choose_lhs}
+choose_lhs <- function(rules, suffix) rules %>% filter(str_detect(lhs, suffix))
+```
+
+```{r choose_rhs}
+choose_rhs <- function(rules, suffix) rules %>% filter(str_detect(rhs, suffix))
+```
+
+### Aprior, CSPADE and rule induction
 
@@
 ```{r my_apriori}
-my_apriori <- function(data){
+my_apriori <- function(data, supp_min = support_min, conf_min = confidence_min){
 
@@
       parameter = list(
-        supp   = 0, # min support
+        supp   = supp_min, # min support
         smax   = 1, # max support
-        conf   = 0, # min confidence
+        conf   = conf_min, # min confidence
         minlen = 2, # min length of rule
@@
       # no printing during execution
-      control = list(
-        verbose = FALSE
-        )
+      control = list(verbose = FALSE)
 
@@
 ```{r my_cspade function}
-my_cspade <- function(data){
+my_cspade <- function(data, supp_min = support_min){
 
@@
         # include all such subsequences
-        support = 0,   # min suppor
+        support = supp_min,   # min suppor
         mingap  = 1,   # min time difference between consecutive element
@@
 
-      control = list(
-        verbose = FALSE
-        )
+      control = list(verbose = FALSE)
 
@@
 ```{r my_ruleInduction}
-my_ruleInduction <- function(rules){
+my_ruleInduction <- function(rules, conf_min = confidence_min){
+
+  rules %>% ruleInduction(confidence = conf_min, control = list(verbose = FALSE))
+
+}
+```
+
+### Separate rules
+The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
+```{r separate_rule}
+separate_rule <- function(rules){
 
@@
 
-    ruleInduction(
+    as("data.frame") %>%
 
-      # keep all subsequences
-      confidence = 0,
+    # separate rule
+    rename_at(vars(matches("rule")), ~ substr(., 1, 4)) %>%
 
-      control    = list(verbose = FALSE)
+    mutate(rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")) %>%
 
+    separate(col = rule, into = c("lhs", "rhs"), sep = " = ") %>%
+
+    # separate lhs and rhs
+    separate_lhs %>%
+    separate_rhs
+
+}
+```
+
+### Compute metrics
+
+```{r}
+compute_count <- function(rules) rules %>% mutate(count = support * n_students)
+```
+
+```{r compute_rhs.support}
+compute_rhs.support <- function(rules, ID, data_support, var_support){
+
+  if(ID == "G") by_var <- c("rhs_course" = "Course ID", "rhs_outcome" = "grade_ceil")
+  else          by_var <- c("rhs_course" = "Course ID"                              )
+
+  rules %>%
+
+    left_join(data_support, by = by_var) %>%
+
+    mutate(rhs.support = !!enquo(var_support)) %>%
+
+    select(- matches("rate"))
+
+}
+```
+
+```{r compute_lhs.rhsTake}
+compute_lhs.rhsTake <- function(rules, ID){
+
+  if(ID == "G") rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = max(support)) %>% ungroup
+  else          rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = sum(support)) %>% ungroup
+
+  rules %>% mutate(lhs.rhsTake.count = lhs.rhsTake.support * n_students)
+
+}
+```
+
+```{r compute_confidence}
+compute_confidence <- function(rules, ID){
+
+  if(ID != "taken") rules <- rules %>% mutate(confidence = support / lhs.rhsTake.support)
+
+  rules
+
+}
+```
+
+```{r compute_lift}
+compute_lift <- function(rules) rules %>% mutate(lift = confidence / rhs.support)
+```
+
+```{r compute_metrics}
+compute_metrics <- function(rules, ID, data_support, var_support){
+
+  rules %>% # rules with support
+
+    compute_count %>%
+
+    compute_rhs.support(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
+
+    compute_lhs.rhsTake(ID = ID) %>%
+
+    compute_confidence(ID = ID) %>%
+
+    compute_lift %>%
+
+    arrange(desc(support))
+
+}
+```
+
+### informative_rules
+```{r informative_rules}
+informative_rules <- function(rules, ID, suffix_lhs, suffix_rhs){
+
+  if(ID != "taken") rules <- rules %>% choose_lhs(suffix_lhs) %>% choose_rhs(suffix_rhs)
+
+  rules %>% filter(lhs_course != rhs_course)
+
+}
+```
+
+## make_AR, make_SR (wrapers)
+We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
+```{r make_AR_regular}
+make_AR <- function(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs){
+
+  transactions %>%
+
+    my_apriori %>%
+
+    separate_rule %>%
+
+    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
+
+    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)
+
+}
+```
+
+We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
+```{r make_SR_regular}
+make_SR_regular <- function(sequences){
+
+  sequences %>%
+
+    my_cspade %>%
+
+    my_ruleInduction %>%
+
+    separate_rule
+
+}
+```
+
+```{r make_SR_TPF_THL}
+make_SR_TPF_THL <- function(ID){
+
+  if(ID == "TPF") suffix_rhs_take <- "pass|fail"
+  else            suffix_rhs_take <- "low|high"
+
+  d_transcript_cum %>%
+
+    # unnest rhs first for memory requirement
+
+    # rhs
+    unnest(rhs, .drop = FALSE) %>% 
+    choose_rhs(suffix_rhs_take) %>% # keep both pass & fail, or high & low, to compute support support.lhs_rhsTake
+
+    # lhs
+    unnest(lhs, .drop = FALSE) %>% 
+    choose_lhs("not") %>%
+    separate_lhs %>%
+
+    # rule support
+    count(lhs, rhs) %>%
+    rename(count = n) %>%
+    mutate(support = count / n_students) %>%
+
+    separate_lhs %>%
+    separate_rhs
+
+}
+```
+
+```{r make_SR}
+make_SR <- function(ID, sequences, data_support, var_support, suffix_lhs, suffix_rhs){
+
+  if(ID %in% c("TPF", "THL")) sequences <- make_SR_TPF_THL(ID = ID)
+  else                        sequences <- make_SR_regular(sequences)
+
+   sequences %>%
+
+    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
+
+    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)
+
+}
+```
+
+## Mine Rules
+We apply `make_AR` to get different sets of rules:
+
+```{r make rules}
+data_general <- data_general %>%
+
+  mutate(
+    AR = list(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_AR),
+    SR = list(ID, sequences   , data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_SR)
+    )
+```
+
+```{r gather data_general}
+rules_clean <- data_general %>%
+
+  gather(key = type_rule, value = rules, AR, SR) %>%
+
+  select(ID, type_rule, rules)
+```
+
+# Editing Rules
+
+The function edit_rules makes AR easier to read.
+It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
+
+## App - Recommender System
+
+```{r edit_RS}
+edit_RS <- function(rules){
+
+  rules %>%
+
+    filter(
+       count      >= 20,
+       lift       >  1,
+       confidence >= 0.4
        )
@@
 
-### clean_rules
-The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-```{r function clean_rules}
-clean_rules <- function(rules){
+```{r rules_RS}
+rules_clean <- rules_clean %>% mutate(rules_RS = rules %>% map(edit_RS))
+```
+
+## App - Rules
+
+```{r edit_rules}
+edit_rules <- function(rules){
 
   rules %>%
-
-    as("data.frame") %>%
-
-    # Exclude rules with no support
-    filter(
-      support > 0
-      ) %>%
-
-    # separate rule
-    rename_at(
-      vars(matches("rule")),
-      function(x) substr(x, 1, 4)
-    ) %>%
-    mutate(
-      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
-      ) %>%
-    separate(
-      rule,
-      into = c("lhs", "rhs"),
-      sep = " = "
-      ) %>%
-
-    # separate lhs and rhs
-    separate(
-      lhs,
-      into    = c("lhs_course", "lhs_outcome"),
-      sep     = "_",
-      remove  = FALSE,
-      convert = TRUE
-      ) %>%
-    separate(
-      rhs,
-      into    = c("rhs_course", "rhs_outcome"),
-      sep     = "_",
-      remove  = FALSE,
-      convert = TRUE
-      )
-
-}
-```
-
-### compute_rhs.support
-The function `compute_support()` computes the support of the lhs and rhs of the rules.
-```{r compute_support}
-compute_rhs.support <- function(AR, data_support, type_rule){
-
-  AR %>%
-
-    left_join(
-      select(data_support, item, !!enquo(type_rule)),
-      by = c("rhs_course" = "item")
-      ) %>%
-    mutate(
-      rhs.support = !!enquo(type_rule)
-      )
-
-}
-```
-
-### compute_conf_lift
-
-```{r}
-compute_conf_lift <- function(rules){
-
-  rules %>%
-
-  # support (and count) of doing lhs and taking course of rhs
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-    mutate(
-      lhs.rhsTake.support = sum(support),
-      lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-      ) %>%
-    ungroup %>%
-
-    mutate(
-      confidence = support / lhs.rhsTake.support,
-      lift       = confidence / rhs.support
-      )
-
-}
-```
-
-### make_AR and  make_SR (wrapers)
-
-We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
-```{r make_AR}
-make_AR <- function(data, data_support, type_rule){
-
-  data %>%
-    my_apriori %>%
-    clean_rules %>%
-    compute_rhs.support(
-      data_support = data_support,
-      type_rule = !!enquo(type_rule)
-      )
-
-}
-```
-
-We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
-```{r make_SR}
-make_SR <- function(data, data_support, type_rule){
-
-  data %>%
-    my_cspade %>%
-    my_ruleInduction %>%
-    clean_rules %>%
-    compute_rhs.support(
-      data_support = data_support,
-      type_rule = !!enquo(type_rule)
-      )
-
-}
-```
-
-## Association Rule
-We apply make_AR to get different sets of rules:
-
-### take -> take
-```{r AR take, cache = TRUE, warning = FALSE}
-AR <- list()
-
-AR$taken <- transactions$taken %>%
-  make_AR(
-    data_support = d_support$TNT, 
-    type_rule = rate.take
-    )
-```
-
-### fail -> fail
-```{r AR fail, cache = TRUE}
-AR$PF <- transactions$PF %>%
-
-  make_AR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.fail
-    ) %>%
-
-  compute_conf_lift %>%
-
-  # lhs and rhs must be fail
-  filter(
-    str_detect(lhs, "fail"),
-    str_detect(rhs, "fail")
-    )
-```
-
-### low grade -> low grade
-```{r AR low, cache = TRUE}
-AR$HL <- transactions$HL %>%
-
-  make_AR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.low
-    ) %>%
-
-  compute_conf_lift %>%
-
-  # lhs and rhs must be fail, count >= 5
-  filter(
-    str_detect(lhs, "low"),
-    str_detect(rhs, "low")
-    )
-```
-
-### not -> fail
-```{r AR TPF, cache = TRUE}
-AR$TPF <- transactions$TPF %>%
-
-  make_AR(
-    data_support = d_support$PF_HL, 
-    type_rule = rate.fail
-    ) %>%
-
-  # Confidence and Lift
-  filter(
-    str_detect(lhs, "not"),
-    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
-    ) %>%
-  compute_conf_lift %>%
-
-  # rhs must be fail, count >= 5
-  filter(
-    str_detect(rhs, "fail")
-    )
-```
-
-### not -> low
-```{r AR THL, cache = TRUE}
-AR$THL <- transactions$THL %>%
-
-  make_AR(
-    data_support = d_support$PF_HL, 
-    type_rule = rate.low
-    ) %>%
-
-  # only keep lhs is not and rhs is low or high to compute Confidence and Lift
-  filter(
-    str_detect(lhs, "not"),
-    str_detect(rhs, "low|high")
-    ) %>%
-  compute_conf_lift %>%
-
-  # lhs and rhs must be fail, count >= 5
-  filter(
-    str_detect(rhs, "low")
-    )
-```
-
-### grade less than or equal to x -> grade less than or equal to 6
-
-```{r AR grade, cache = TRUE}
-AR$G <- transactions$G %>%
-
-  my_apriori %>%
-
-  clean_rules %>%
-
-  # rhs.support
-  left_join(
-    d_support$G,
-    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
-    ) %>%
-  mutate(
-    rhs.support = support.grade
-    ) %>%
-
-  # Confidence and lift
-  group_by(
-    lhs, 
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = max(support),
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
-
-  # Reduce number of rules
-  filter(
-    # exclude rules with same course on lhs and rhs
-    lhs_course != rhs_course,
-    # rhs is grade less than or equal to 6
-    rhs_outcome <= 6,
-    lhs_outcome <= 7
-    )
-```
-
-## Sequence Rules
-We apply make_SR to get different types of sequential rules:
-
-### take -> take
-```{r SR taken, cache = TRUE, warning = FALSE}
-SR <- list()
-
-SR$taken <- sequences$taken %>%
-
-  make_SR(
-    data_support = d_support$TNT, 
-    type_rule = rate.take
-  )
-```
-
-### fail -> fail
-```{r SR PF, cache = TRUE}
-SR$PF <- sequences$PF %>%
-
-  make_SR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.fail
-  ) %>%
-
-  compute_conf_lift %>%
-
-  # lhs and rhs are fail
-  filter(
-    str_detect(lhs, "fail"),
-    str_detect(rhs, "fail")
-    )
-```
-
-### low grade -> low grade
-```{r SR HL, cache = TRUE}
-SR$HL <- sequences$HL %>%
-
-  make_SR(
-    data_support = d_support$PF_HL,
-    type_rule = rate.low
-  ) %>%
-
-  compute_conf_lift %>%
-
-  # lhs and rhs are low
-  filter(
-    str_detect(lhs, "low"),
-    str_detect(rhs, "low")
-    )
-```
-
-### not -> fail
-```{r SR TPF, cache = TRUE}
-SR$TPF <- d_transcript_cum %>%
-
-  # rhs
-  unnest(
-    rhs,
-    .drop = FALSE
-    ) %>%
-  filter(
-    str_detect(rhs, "pass|fail")
-    ) %>%
-
-  # lhs
-  unnest(
-    lhs,
-    .drop = FALSE
-    ) %>%
-  filter(
-    str_detect(lhs, "not")
-    ) %>%
-
-  # rule
-  unite(
-    col = "rule",
-    lhs, rhs,
-    sep = " => "
-    ) %>%
-
-  # rule support
-  count(
-    rule
-    ) %>%
-  mutate(
-    support = n / n_students
-    ) %>%
-
-  # regular fucntions
-  clean_rules %>%
-
-  compute_rhs.support(
-    data_support = d_support$PF_HL,
-    type_rule    = rate.fail
-    ) %>%
-
-  compute_conf_lift %>%
-
-  # lhs not, rhs low
-  filter(
-    str_detect(rhs, "fail")
-    )
-```
-
-### not -> low
-```{r SR THL, cache = TRUE}
-SR$THL <- d_transcript_cum %>%
-
-  # rhs
-  unnest(
-    rhs,
-    .drop = FALSE
-    ) %>%
-  filter(
-    str_detect(rhs, "high|low")
-    ) %>%
-
-  # lhs
-  unnest(
-    lhs,
-    .drop = FALSE
-    ) %>%
-  filter(
-    str_detect(lhs, "not")
-    ) %>%
-
-  # rule
-  unite(
-    col = "rule",
-    lhs, rhs,
-    sep = " => "
-    ) %>%
-
-  # rule support
-  count(
-    rule
-    ) %>%
-  mutate(
-    support = n / n_students
-    ) %>%
-
-  # regular fucntions
-  clean_rules %>%
-
-  compute_rhs.support(
-    data_support = d_support$PF_HL,
-    type_rule    = rate.low
-    ) %>%
-
-  compute_conf_lift %>%
-
-  # constraints to respect
-  filter(
-    str_detect(rhs, "low")
-    )
-```
-
-### grade less than or equal to x -> grade less than or equal to 6
-```{r SR G, cache = TRUE}
-SR$G <- sequences$G %>%
-
-  my_cspade %>%
-  my_ruleInduction %>%
-  clean_rules %>%
-
-  # rhs.support
-  left_join(
-    d_support$G,
-    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
-    ) %>%
-  mutate(
-    rhs.support = support.grade
-    ) %>%
-
-  # Confidence & lift
-  group_by(
-    lhs,
-    rhs_course
-    ) %>%
-  mutate(
-    lhs.rhsTake.support = max(support),
-    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
-    ) %>%
-  ungroup %>%
-
-  mutate(
-    confidence = support / lhs.rhsTake.support,
-    lift       = confidence / rhs.support
-    ) %>%
-
-  # Reduce number of rules
-  filter(
-    # exclude rules with same course on lhs and rhs
-    lhs_course != rhs_course,
-    # rhs is grade less than or equal to 6
-    rhs_outcome <= 6,
-    lhs_outcome <= 7
-    )
-```
-
-## Editing rules
-The function edit_rules makes AR easier to read.
-It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
-```{r edit_rules}
-edit_rules_rulesApp <- function(rules){
-
-  rules %>%
-
-    mutate(
-      count = support * n_students
-      ) %>%
 
@@
 
-    arrange(
-      desc(count)
-      )
+    arrange(desc(count))
 
@@
 
-```{r edit rules}
-AR_rulesAPP <- lapply(
-  X   = AR,
-  FUN = edit_rules_rulesApp
-  )
-
-SR_rulesAPP <- lapply(
-  X   = SR,
-  FUN = edit_rules_rulesApp
-  )
+```{r rules_rules}
+rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
 ```
 
-```{r}
-save(
-  AR_rulesAPP, SR_rulesAPP,
-  file = "App/rules/rules.RDATA"
-  )
+```{r save rules_clean}
+save(rules_clean, file = "App/rules_clean.RDATA")
 ```
 
-```{r show rules}
-print(AR_rulesAPP$THL)
-print(SR_rulesAPP$THL)
+```{r save data_general}
+save(data_general, file = "Output/rules.RDATA")
 ```
 
-```{r}
-edit_rules_RSAPP <- function(rules){
-
-  rules %>%
-
-    mutate(
-      count = support * n_students
-      ) %>%
-
-    filter(
-       count      >= 10,
-       lift       >= 1,
-       confidence >= 0.4
-      )
-
-}
+```{r print SR}
+print(rules_clean$rules_RS[[10]])
 ```
-
-```{r}
-AR_RSAPP <- lapply(
-  X   = AR,
-  FUN = edit_rules_RSAPP
-  )
-
-SR_RSAPP <- lapply(
-  X   = SR,
-  FUN = edit_rules_RSAPP
-  )
-```
-
-```{r save rules, include = FALSE}
-save(
-  AR_RSAPP, SR_RSAPP,
-  file = "App/Recommender System/rules.RDATA"
-  )
-```

### 2019-03-21 Pillar 2 - Topic Modeling.Rmd

--- 2019-03-19 Pillar 2 - Topic Modeling.Rmd
@@
 
+#Setup
+##Libraries
 ```{r library, message = FALSE, eval = TRUE}
@@
 
-```{r function reorder_within & co., echo = FALSE}
+##Functions for internal faceting
+```{r function reorder_within & co., echo = FALSE, eval = TRUE}
 
@@
 
-# Setup
+##Loading data
 We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
-For `d_description` and `d_overview`, we keep only the most recent year.
+`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
+
+For `d_text` we keep only the most recent year.
 ```{r import data, eval = TRUE}
+#load
 load("output/data_pillar_2.RDATA")
 
-# Only keep course descriptions and overviews from most recent year
+# keep most recent year
 d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
@@
 # TF-IDF
+We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.
+
 ## Functions for Generating Barplots and Word Clouds
@@
       )
-
 }
@@
 To decide the number of topics to discover, we run three different tests.
+###Function
 The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
@@
 ```
-We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
-```{r description topics, cache = TRUE}
+###Train
+```{r package test on topics, cache = TRUE}
+#Start timer
 start.time <- Sys.time()
 
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
+#
+##apply my_FindTopicsNumber
+result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))
 
+#Stop timer
 end.time <- Sys.time()
-time.taken <- end.time - start.time
+print(end.time - start.time)
 
-save(result_description,
-     file = "Output/LDA_ntopics.RDATA")
+#
+##Save results
+#save(result_topic_test,
+#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
+```
+Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
+* Overview:     22min 
+* Description:  11min 
+* Manuals:      5.5hrs
 
-print(time.taken)
-```
-
-We run the test for overview, documeting its duration. 
-```{r overview topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_overview , result_description,
-     file = "Output/LDA_ntopics.RDATA")
-
-print(time.taken)
-```
-
-We run the test for manuals, documenting its duration.
-```{r manual topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_manual, result_overview , result_description,
-     file = "Output/LDA_ntopics.RDATA")
-
-print(time.taken)
-```
-
-from 20, to 40, by 5 topics takes
-22min for overview
-11min for description
-5.5hrs for manuals
-
+###Graph 
 We examine the result of the experiment by plotting them on a graph.
 ```{r LDA number topics plot}
+#load("Output/LDA_ntopics.RDATA")
 
-load("Output/LDA_ntopics.RDATA")
-
-result_description %>%
-  FindTopicsNumber_plot
-
-result_overview %>%
-  FindTopicsNumber_plot
-
-result_manual %>%
-  FindTopicsNumber_plot
-
+result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
 ```
@@
 
-We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
-###Functions for models (get gamma, get beta, extract_dtm)
+###Functions for models (extract_dtm, get_distributions, perplexity)
+The following functions are used as input in a map to compute and evaluate topic models. 
 ```{r getting gamma and beta, eval = TRUE}
@@
 
-The following functions allow us to inspect the distributions and get kw
+The following functions allow us to inspect the results from our models(inspect distributions and get kw):
 ```{r}
-# FUNCTION
-#get_top_match <- function(<INPUT GAMMA OR BETA DISTRIB>){<FUNCTION GENERALIZATION>}
-
  # get_top_match <- function(d_distribution){
-#   print(!!sym(d_distribution))
+ # 
+ #  #save user input as string
+ #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
+ #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
+ # 
+ #  #Compute Case (Beta or Gamma, respectively)
+ #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
+ #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
+ #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
+ # 
+ #  #
+ #  ## DATA
+ #  data.frame(d_distribution) %>%
+ #    group_by(!!sym(grouping)) %>%
+ #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
+ #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
+ #    group_by(!!sym(grouping)) %>%
+ #    summarise(top = list(!!sym(objects_to_group)))
  # }
@@
 ###Training Models
+We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
 ```{r LDA fit, cache = TRUE, eval = TRUE}
 
-test_topic_model <- tibble( #change to topic_model
-  #repeat each topic number twice
+test_topic_model <- tibble( #CHANGE NAME TO: topic_model
+
+  #repeat each topic number twice (once for overview and once for manual)
   n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5
@@
          `Topic ID` = paste(Origin, n_topic, sep = "_"),
+
+         #Document Term Matrix
          DTM        = pmap(.l = list(Origin), .f = extract_dtm),
 
-         #fit model
+         #Fit Model
          Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),
@@
 
-         #selecting keywords
+         #Select keywords
          kw = map(Beta, .f = get_kw)
@@
 
-#View(test_topic_model)
-test_topic_model
-```
-#DELETE LATERRRRRR- HELPER IMPORT
-```{r}
-load("Output/topic_model.RDATA")
+# Clean workspace
+
+# rm(extract_dtm, get_distributions, my_perplexity,
+#    get_top_terms_topic, get_top_topics_course, get_kw)
+
+# test_topic_model
 ```
 
-##Model Evaluation
-###Plots
+##Plots - Model Evaluation
+To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
 ```{r perplexity plots, eval = TRUE}
@@
 ##Saving model_data:
-For internal use:
+We save our tibble with all the information.
 ```{r}
@@
 #App
-####TEMPORTARY: stopwords for keywords
-This section is for presentations
-```{r stopwords for kw}
-#kw$overview
-not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
-                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
+For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
+##Distributions and Key words
+The function `clean_kw` removes stopwords from our key words.
+```{r function clean key words}
+clean_kw <- function(kw_list){
 
-remove_words <- function(x){
-  setdiff(x, not_include)
+  #stopwords
+  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
+                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
+                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
+                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")
+
+  #remove stopwords
+  kw <- setdiff(kw_list, kw_stopwords)
+  #return
+  return(kw[!is.na(kw)])
+
 }
 
-kw1 <- lapply(
-  kw,
-  remove_words
-)
+```
+On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
+```{r crop and clean TM for App}
+app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
+  mutate(kw = map(kw, .f = clean_kw))
+```
 
-```
-##Convenience vectors for APP
+##Convenience Vectors
+For the app we also need to have a list of all courses and an example of a prospective semester
 ```{r for convenience}
@@
   ) %>% sort
+
 ```
@@
 ```{r app files}
-save(distribution, kw, course_all, course_following_semester,
-     file = "App/Recommender System/data_topic_models.RDATA")
+# save(app_topic_model, course_all, course_following_semester,
+#      file = "App/Recommender System/data_topic_models.RDATA")
 ```

### 2019-03-22 TEMPORARY DKE Presentation code.R
presentation graphs

@@ -1,0 +1,118 @@
+#Graph Results
+
+load("Output/LDA_ntopics.RDATA")
+
+graph_results_package <- function(data) {
+  data %>%
+    select(-Griffiths2004) %>%
+    gather(key = "Metric", value = "Value", CaoJuan2009, Arun2010, Deveaud2014) %>%
+    mutate(MinMax = ifelse(Metric=="Deveaud2014", "maximize", "minimize")) %>%
+    group_by(Metric) %>%
+    mutate(Value = Value/sum(Value))%>%
+    
+    ggplot(aes(x = topics, y = Value))+
+    geom_line(aes(colour = Metric))+
+    geom_point(aes(colour = Metric))+
+    facet_wrap(~MinMax, nrow = 2, scales = "free")+
+    theme_minimal()
+}
+
+
+graph_results_package(result_manual)
+ggsave("Graphs_presentation/Find_manuals.jpg")
+graph_results_package(result_overview)
+ggsave("Graphs_presentation/Find_overview.jpg")
+
+
+#------------------------------------------
+load("Output/topic_model.RDATA")
+
+old_topic_model <- as_tibble(topic_model) %>%
+  gather(key = "Origin", value = "Model", TM_overview, TM_manual) %>%
+  mutate(Origin = str_remove(Origin,"TM_")) %>%
+  mutate(Origin = str_replace(Origin,"manual", "manuals")) %>%
+  mutate( `Topic ID` = paste(Origin, n_topic, sep = "_"),
+          
+          #Document Term Matrix
+          DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+          
+          #Gamma distribution
+          Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+          
+          #Beta distribution
+          Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
+          
+          #Perplexity
+          Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
+          
+          #Loglikelihood
+          LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
+          
+          
+          #
+          ##Inspect
+          
+          #top words per topic
+          top_terms_topic = map(Beta, .f = get_top_terms_topic),
+          
+          #top topics per course
[…]

### 2019-03-22 Pillar 2 - Topic Modeling.Rmd
minor change

@@
          #Fit Model
-         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),
+         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control
 
@@
 ```
+
+```{r adding convenience vectors}
+app_topic_model <- app_topic_model %>%
+  mutate(`All Courses`     = course_all,
+         `Sample semester` = course_following_semester)
+
+#rm(course_all, course_following_semester)
+```
 ## Saving files for APP
 ```{r app files}
-# save(app_topic_model, course_all, course_following_semester,
-#      file = "App/Recommender System/data_topic_models.RDATA")
+# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
 ```
@@
 
-rm(a,b #,test)
+test <- test_topic_model %>%
+  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
+         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
+         )
+test[["preparedBeta"]]
+rm(a,b #,test
+   )
 ```

### 2019-03-22 Pillar 1 - Sequential Pattern Mining.Rmd
remove unused variable from df rules_clean to speed up the app
App updates

@@
 ```{r rules_rules}
-rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
+rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules)) %>% select(-rules)
 ```
@@
 save(rules_clean, file = "App/rules_clean.RDATA")
+save(rules_clean, file = "App/Rules/rules_clean.RDATA")
+save(rules_clean, file = "App/Recommender System//rules_clean.RDATA")
 ```

### 2019-03-22 TEMPORARY DKE Presentation code.R
graphs updates

@@ -93,7 +93,8 @@ graph_per_origin <-  function(origin){
          x = "Number of Topics",
          y = NULL) +
     theme(plot.title = element_text(size = 20),
-          axis.title = element_text(size = 20)
+          axis.title = element_text(size = 20),
+          legend.position = "none"
           )
 }
 

### 2019-03-22 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

--- 2019-03-21 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 TODO: simplify support into one df: var1 = course id, var2 = type, var3 = rate
-
-AR with not taken on lhs is not useful.
 
@@
     rhs = course_current
-    ) %>%
+    )
+```
 
-  select(lhs, rhs) # for memory requirement
+```{r}
+save(d_transcript_cum, file = "output/d_transcript_cum.RDATA")
 ```

### 2019-03-22 compare SR by hand and with CSPADE.R
minor change

@@ -1,50 +1,0 @@
-SR$PF <- d_transcript_cum %>%
-  
-  # rhs
-  unnest(
-    rhs,
-    .drop = FALSE
-  ) %>%
-  filter(
-    str_detect(rhs, "pass|fail")
-  ) %>%
-  
-  # lhs
-  unnest(
-    lhs,
-    .drop = FALSE
-  ) %>%
-  filter(
-    str_detect(lhs, "pass|fail")
-  ) %>%
-  
-  # rule
-  unite(
-    col = "rule",
-    lhs, rhs,
-    sep = " => "
-  ) %>%
-  
-  # rule support
-  count(
-    rule
-  ) %>%
-  mutate(
-    support = n / n_students
-  ) %>%
-  
-  # regular fucntions
-  clean_rules %>%
-  
-  compute_rhs.support(
-    data_support = d_support$PF_HL,
-    type_rule    = rate.fail
-  ) %>%
-  
-  compute_conf_lift %>%
-  
-  # lhs not, rhs low
-  filter(
-    str_detect(lhs, "fail"),
-    str_detect(rhs, "fail"),
-  )

### 2019-03-22 App/Recommender System/server.R
app updates- unselect all courses

@@ -35,7 +35,7 @@ function(input, output, session) {
           inputId  = "course_chosen",
           label    = "Tentative Courses for following period",
           choices  = course_all,
-          selected = course_all,
+          #selected = course_all,
           inline   = TRUE
         ))
   })

### 2019-03-22 Pillar 1 - Topic Profile.Rmd

---
title: "Pillar 1 - Student Topic Profile"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")

library(tidyverse)
library(magrittr)
```

```{r}
load("App/Recommender System/topic_model_gb.RDATA")
load("Output/data_pillar_1.RDATA")

topic_model_gb
```

```{r}
gamma <- topic_model_gb$g_overview[[10]]
```

```{r}
gamma_spread <- gamma %>% spread(topic, gamma)
```

```{r}
d_transcript_informative %>%

  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
  filter(!is.na(`Topic 1`)) %>%

  mutate_at(vars(matches("Topic")), .funs = funs(Grade/10 * .)) %>% # weigh by grade

  group_by(`Student ID`, time) %>%
  summarize_at(vars(matches("Topic")), sum) %>%

  group_by(`Student ID`) %>%
  arrange(time) %>% 
  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t

  arrange(`Student ID`)
```

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
attach student topic profile to their transcript

@@
 ```{r}
-gamma <- topic_model_gb$g_overview[[10]]
+gamma <- topic_model_gb$g_overview[[10]] %>% spread(topic, gamma)
 ```
@@
 ```{r}
-gamma_spread <- gamma %>% spread(topic, gamma)
-```
+student_TP <- d_transcript_informative %>%
 
-```{r}
-d_transcript_informative %>%
-
-  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
+  left_join(gamma, by = c("Course ID" = "document")) %>%
   filter(!is.na(`Topic 1`)) %>%
@@
   arrange(time) %>%
+
+  mutate_at(vars(matches("Topic")), lag) %>% # topic profile of student at time t
+  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>% # topic profile of student at time t
   mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t
 
+  right_join(d_transcript_informative, by = c("Student ID", "time")) %>%
+
+  select(`Student ID`, `Course ID`, time, everything()) %>%
   arrange(`Student ID`)

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
join student topic profile to cumulative transcript
So that we can regression grade on topic profile

@@
 load("Output/data_pillar_1.RDATA")
+load("Output/d_transcript_cum.RDATA")
 
@@
 
-  mutate_at(vars(matches("Topic")), lag) %>% # topic profile of student at time t
-  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>% # topic profile of student at time t
-  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t
+  mutate_at(vars(matches("Topic")), lag) %>%
+  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>%
+  mutate_at(vars(matches("Topic")), cumsum) # topic profile at beginning of period
+```
 
-  right_join(d_transcript_informative, by = c("Student ID", "time")) %>%
+```{r}
+d_transcript_cum %>%
 
-  select(`Student ID`, `Course ID`, time, everything()) %>%
-  arrange(`Student ID`)
+  right_join(student_TP, by = c("sequenceID" = "Student ID", "eventID" = "time"))
 ```

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
Best subset selection to identify prerequisite topics for each course
Lasso is consider but has important drawbacks

@@
 library(magrittr)
+library(glmnet)
+library(leaps)
 ```
@@
 ```{r}
-gamma <- topic_model_gb$g_overview[[10]] %>% spread(topic, gamma)
+gamma        <- topic_model_gb$g_overview[[10]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
+gamma_spread <- gamma %>% spread(topic, gamma)
 ```
@@
 
-  left_join(gamma, by = c("Course ID" = "document")) %>%
-  filter(!is.na(`Topic 1`)) %>%
+  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
+  filter(!is.na(`Topic_1`)) %>%
 
@@
 ```{r}
-d_transcript_cum %>%
+d_TP_cum <- d_transcript_cum %>%
+
+  right_join(d_transcript_informative, by = c("sequenceID" = "Student ID", "eventID" = "time")) %>%
 
@@
 ```
+
+```{r}
+course_all <- unique(d_transcript_informative$`Course ID`)
+course_obj <- course_all[! course_all %>% str_detect("^...10")]
+
+find_prep <- function(objective){
+
+  data_temp <- d_TP_cum %>%
+
+    filter(`Course ID` == objective) %>%
+
+    select(Grade, matches("Topic"))
+
+  if(nrow(data_temp) <= 7) return(NULL)
+
+  #
+  # best subset selection
+  m <- regsubsets(Grade ~ ., data_temp, nvmax = 6)
+
+  coefi <- coef(m, 6)[-1]  # check that 6 is usually a good subset size
+
+  tibble(topic = names(coefi), weight = coefi) %>%
+
+    right_join(gamma, by = "topic") %>%
+
+    mutate(weight = weight %>% replace_na(0)) %>%
+
+    # double prep_score of intro courses
+    mutate(is_intro = document %>% str_detect("^...10")) %>%
+    mutate(weight = weight * (1 + is_intro)) %>%
+
+    group_by(document) %>%
+    summarize(prep_score = sum(weight * gamma)) %>%
+    mutate(objective = objective) %>%
+
+    arrange(desc(prep_score)) %>%
+
+    filter(! document %>% str_detect("^...30")) %>%
+    filter(document %in% course_all) %>%
+
+    top_n(10, prep_score)
+
+}
+
+results <- course_obj %>% map(find_prep) %>% bind_rows
+View(results)
+```
+
+```{r}
+#
+# lasso (instead of best subset selection due to the large number of predictors (number of topics))
+# disadvantage: difficult to estimate lambda a-priori
+x <- model.matrix(Grade ~ ., test)[ , -1]
+y <- test$Grade
+lambda <- 10^seq(-0.1, -2, length = 14)
+
+results <- glmnet(x, y, alpha = 1, lambda = lambda)
+coef(results)
+
+# first positive coefficient is topic 5. Topic 3 and 19 appear a little later.
+results$lambda
+```

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
Template for (STM) Topic Model, runs until evaluation

--- 2019-03-21 Pillar 2 - Topic Modeling.Rmd
@@
 ---
-title: "Pillar 2 - Topic Modeling"
+title: "Pillar 2 - (STM) Topic Modeling"
 author: "DARS"
@@
 
+#Topic Models
+library(stm)
+library(topicmodels)
+library(quanteda) #used for DTM implementation called dfm
+
 library(ggwordcloud) # Word Clouds
-library(topicmodels)
+
 library(lemon)
@@
 
-# LDA
+# STM
 ##Setup
 ###Cast DTM
-The function `my_cast_dtm` casts our dataframes into a DTM.
+The function `my_cast_dtm` casts our dataframes into a DTM (dfm from package quanteda)
 ```{r my_cast_dtm, eval = TRUE}
@@
   count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
+  cast_dfm(`Course ID`, word, n)
 
@@
 ```
-###Controls
-The control parameters we use are:
-```{r controls, eval = TRUE}
-my_control <- list(
 
-  nstart = 10,
-  seed   = 1 : 10,
-  best   = TRUE,
-
-  burnin = 1000,
-  iter   = 15000,
-  thin   = 100
-
-)
-```
-The control parameters we use for fast testing are:
-```{r fast control}
-my_control_fast <- list(
-
-  nstart = 1,
-  seed   = 1,
-  best   = TRUE,
-
-  burnin = 5,
-  iter   = 10,
-  thin   = 2
-
-)
+###STM Corpus
+We convert our DTMs into STM corpus to access to full functionality in STM package.
+```{r as STM corpus, eval = TRUE}
+stm_corpus <- d_cast %>% map(asSTMCorpus)
 ```
 
-##Ideal Number of Topics Package Test
-To decide the number of topics to discover, we run three different tests.
-###Function
-The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
-```{r function my_FindTopicsNumber }
-my_FindTopicsNumber <- function(data_cast, n_topics){
+##Fitting STM
+We will to train several models to have some flexibility in the number of topics we select.
+For this purpose we want to create two tibbles.
+One that trains on the entire data (for use), and one that we divide on training set and test set.
+###Functions
+Several functions are needed to work with tibble and tidyverse functionality:
+####My_stm Function
+The function `my_LDA` fits an LDA model on the DTM using the previous controls.
+```{r my_STM, eval= TRUE}
+my_stm <- function(n_topics, corpus){
 
-  FindTopicsNumber(
-
-  dtm = data_cast,
-  topics = n_topics,
-  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
-  method = "Gibbs",
-  control = my_control,
-  mc.cores = 4L
-
-  )
-
+  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
 }
 ```
-###Train
-```{r package test on topics, cache = TRUE}
-#Start timer
-start.time <- Sys.time()
+####My_stm_eval Function
+This function applied stm but with heldout vocab and documents. 
+```{r}
+my_stm_eval <- function(heldout, n_topic){
+  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
+}
+```
+
+####Extraction Functions
+We will be working with many lists of lists. The following functions help us extract information from lower levels of the list (e.g. access element in second list).
+```{r getting gamma and beta, eval = TRUE}
+#
+##From external Lists:
+
+#Extract DTM
+extract_dtm <- function(origin) d_cast[[origin]]
+#Extract CORPUS
+extract_corpus <- function(origin) stm_corpus[[origin]]
 
 #
-##apply my_FindTopicsNumber
-result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))
+## From STM_corpus class
 
-#Stop timer
-end.time <- Sys.time()
-print(end.time - start.time)
+#Extract documents
+extract_documents <- function(corpus) corpus$documents
+#Extract vocab
+extract_vocab     <- function(corpus) corpus$vocab
+#Extract data
+extract_data     <- function(corpus) corpus$data
 
 #
-##Save results
-#save(result_topic_test,
-#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
-```
-Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
-* Overview:     22min 
-* Description:  11min 
-* Manuals:      5.5hrs
+##From Partition
 
-###Graph 
-We examine the result of the experiment by plotting them on a graph.
-```{r LDA number topics plot}
-#load("Output/LDA_ntopics.RDATA")
+#Extract heldout docs
+extract_held_doc <- function(heldout) heldout$documents#[[1]]
+#Extract herlout vocab
+extract_held_vocab <- function(heldout) heldout$vocab#[[1]]
+#Extract missing
+extract_helout_missing <- function(heldout) heldout$missing#[[1]]
 
-result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
-```
-From the results we see that the ideal number of topics is somewhere between 35 and 40.
+#
+## MODEL HELDOUT
+my_model <- function(heldout){
 
-## Fitting Model
-The function `my_LDA` fits an LDA model on the DTM using the previous controls.
-```{r my_LDA, eval= TRUE}
-my_LDA <- function(n_topics, corpus, control = my_control){
+  docs <- heldout$documents[[1]]
+  voc  <- heldout$vocab
+  k    <- n_topics
 
-  LDA_model <- LDA(
-    x       = corpus,
-    k       = n_topics,
-    method  = "Gibbs",
-    control = control
-    )
+  Model <- stm(docs, voc, 5, init.type = "Spectral")
+
+  return(Model)
 }
 
-```
+#
+##From Model
+#tidy gamma
+my_tidy_gamma <- function(Gamma, DTM){
+  tidy(Gamma, matrix = "gamma", document_names = rownames(DTM))}
 
-###Functions for models (extract_dtm, get_distributions, perplexity)
-The following functions are used as input in a map to compute and evaluate topic models. 
-```{r getting gamma and beta, eval = TRUE}
-#extract dtm
-extract_dtm <- function(origin) d_cast[[origin]]
+#extract
 
@@
     mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(!!sym(distrib_str)))
-}
-
-#perplexity Function
-my_perplexity <- function(model, dtm){
-  perplexity(model, dtm, estimate_theta = FALSE)
-}
+      arrange(topic, desc(!!sym(distrib_str)))}
 
 ```
-
+####Inspection functions
 The following functions allow us to inspect the results from our models(inspect distributions and get kw):
 ```{r}
- # get_top_match <- function(d_distribution){
- # 
- #  #save user input as string
- #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
- #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
- # 
- #  #Compute Case (Beta or Gamma, respectively)
- #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
- #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
- #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
- # 
- #  #
- #  ## DATA
- #  data.frame(d_distribution) %>%
- #    group_by(!!sym(grouping)) %>%
- #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
- #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
- #    group_by(!!sym(grouping)) %>%
- #    summarise(top = list(!!sym(objects_to_group)))
- # }
-
 get_top_terms_topic <- function(d_beta){
@@
 }
+```
+###Model Tibbles
+####For use:
+```{r models in tibble}
+topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)
 
-```
-###Training Models
-We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
-```{r LDA fit, cache = TRUE, eval = TRUE}
+stm_model <- tibble(
+  #repeat each topic number twice (once for overview and once for manual)
+  n_topic = rep(topic_numbers, each = 2) ) %>%
 
-test_topic_model <- tibble( #CHANGE NAME TO: topic_model
-
-  #repeat each topic number twice (once for overview and once for manual)
-  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5
-
-  ) %>%
-  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
+  mutate(
+    #Identification information
+    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
     `Topic ID` = paste(Origin, n_topic, sep = "_"),
 
-         #Document Term Matrix
+    #DTM
     DTM       = pmap(.l = list(Origin), .f = extract_dtm),
+    doc_names = map(DTM, rownames),
+
+    #STM Corpus
+    Corpus           = pmap(.l = list(Origin), .f = extract_corpus), 
+    #Documents- STM corpus
+    Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
+    #Vocab- STM corpus
+    Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
+    #Data- STM corpus
+    Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
 
     #Fit Model 
-         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast),
+    Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),
 
-         #Gamma distribution
-         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+    #Evaluation
+    Exclusivity        = map(Model, exclusivity),
+    semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
+    #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),
+
+    #
+    ##Inspection
 
     #Beta distribution
-         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
-
-         #Perplexity
-         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
-
-         #Loglikelihood
-         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
-
-         #
-         ##Inspect
+    Beta = pmap(.l = list(Model),  .f = tidy),
+    #Gamma distribution
+    Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this
 
@@
     kw = map(Beta, .f = get_kw)
+
+    #END MUTATE PARENTHESIS
          )
 
-# Clean workspace
-
-# rm(extract_dtm, get_distributions, my_perplexity,
-#    get_top_terms_topic, get_top_topics_course, get_kw)
-
-# test_topic_model
 ```
 
-##Plots - Model Evaluation
-To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
-```{r perplexity plots, eval = TRUE}
-#Function
-plot_evaluation <- function(origin){
+```{r} 
+#testing 
+test_model <- stm_eval_model[1, ]
 
-  #data
-  test_topic_model %>%
+my_stm_eval(list(test_model$documents, test_model$vocab, test_model$n_topic))
 
-    #Wrangling
-    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
-    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
-    filter(Origin == origin) %>%
+my_stm_eval(documents = test_model$documents, vocab = test_model$vocab, n_topic = test_model$n_topic)
 
-    #Graphics
-    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
-    geom_point() +
-    geom_line() +
-    facet_grid(rows = vars(`Eval Type`), scales = "free") +
-    theme_minimal()
+test <- list(test_model$documents, test_model$vocab, test_model$n_topic)
+test %>% my_stm_eval
 
-}
+test <- list(stm_eval_model$documents, stm_eval_model$vocab, stm_eval_model$n_topic)
 
-#Plot
-plot_evaluation("overview")
-plot_evaluation("manuals")
+test %>% my_stm_eval
+
+test <- stm_eval_model %>% mutate(test = list(documents, vocab, n_topic) %>% pmap(list))
+
+stm_eval_model %>% mutate(test = test %>% map(my_stm_eval))
+test1<- test$test[[1]]
+
 ```
 
-##Saving model_data:
-We save our tibble with all the information.
-```{r}
-# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
+####For evaluation
+```{r models in tibble}
+topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)
+
+#
+##STM EVALUATION TIBBLE
+stm_eval_model <- tibble(
+
+  #repeat each topic number twice (once for overview and once for manual)
+  n_topic = rep(topic_numbers, each = 2)
+
+  ) %>%
+  mutate(
+    #Identification information
+    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
+    `Topic ID` = paste(Origin, n_topic, sep = "_"),
+
+    #DTM
+    DTM       = pmap(.l = list(Origin),  .f = extract_dtm),
+    Heldout   = pmap(.l = list(DTM),     .f = make.heldout, proportion = 0.5),
+
+    #Fitting Model
+    Model     = pmap(.l = list(Heldout, n_topic), .f = my_stm_eval),
+
+    #Evaluation measures
+    Exclusivity        = map(Model, exclusivity),
+
+    semantic_coherence = pmap(.l = list(Model, Heldout), 
+                              function(model,  heldout) semanticCoherence(model, heldout$documents)),
+
+    eval_heldout       = pmap(.l = list(Model, Heldout), 
+                              function(model,  heldout) eval.heldout(model, heldout$missing)),
+
+    residual           = pmap(.l = list(Model, Heldout), 
+                              function(model,  heldout) checkResiduals(model, heldout$documents, tol = 1/100)),
+
+    bound              = pmap_dbl(.l = list(Model), 
+                                  function(model) max(model$convergence$bound)),
+
+    lfact              = map_dbl(Model,       
+                                 function(model) lfactorial(model$settings$dim$K)),
+
+    lbound             = bound + lfact,
+    iterations         = map_dbl(Model,       
+                                 function(model) length(model$convergence$bound))
+    ) 
 ```
 
-#App
-For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
-##Distributions and Key words
-The function `clean_kw` removes stopwords from our key words.
-```{r function clean key words}
-clean_kw <- function(kw_list){
+##Finding Number of Topics
+We want to estimate the number of topics that exist in the data, to select a model for them.
 
-  #stopwords
-  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
-                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
-                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
-                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")
-
-  #remove stopwords
-  kw <- setdiff(kw_list, kw_stopwords)
-  #return
-  return(kw[!is.na(kw)])
-
-}
-
-```
-On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
-```{r crop and clean TM for App}
-app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
-  mutate(kw = map(kw, .f = clean_kw))
-```
-
-##Convenience Vectors
-For the app we also need to have a list of all courses and an example of a prospective semester
-```{r for convenience}
-# set seed
-set.seed(1)
-
-#
-## All courses
-course_all <- d_course %>%
-  inner_join(
-    d_transcript,
-    by = "Course ID"
-  ) %>%
-  distinct(
-    `Course ID`
-  ) %>%
-  # remove semester abroad, skills and projects
-  filter(
-    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
-  ) %>%
-  pull
-
-#
-##courses following_semester
-course_following_semester <- sample(
-  x       = course_all,
-  size    = 60,
-  replace = FALSE
-  ) %>% sort
-
-```
-## Saving files for APP
-```{r app files}
-# save(app_topic_model, course_all, course_following_semester,
-#      file = "App/Recommender System/data_topic_models.RDATA")
-```
-# Visualization
-### Functions 
-This part is adapted 
-```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(d_beta){
-
-  data.frame(d_beta) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-      group_by(topic) %>%
-        top_n(10, beta) %>%
-      ungroup %>%
-      arrange(topic, desc(beta))
-
-} #repetition??? of inspect topics?
-
-prepare_data_LDA_gamma <- function(d_gamma, level = Course){
-
-  data_gamma <- data.frame(d_gamma) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-    rename(`Course ID` = document)
-
-  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
-                                      rename(facet = `Course ID`)
-
-  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
-                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
-                                       filter(!is.na(Cluster)) %>%
-                                       rename(facet = Cluster)
-
-  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
-                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
-                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-                                             rename(facet = Concentration)
-
-  data_gamma <- data_gamma %>%
-    group_by(facet, topic) %>%
-      summarise(gamma = sum(gamma)) %>%
-    filter(gamma > 0.05) %>%
-    ungroup %>%
-    arrange(facet, desc(gamma))
-
-  return(data_gamma)
-
-}
-
-# Bet Distribution
-test <- list()
-
-a <-  names(distribution)[1]
-test[[a]] <- lapply(distribution[[a]],
-                      prepare_data_LDA_beta)
-
-# Gamma Distribution
-b <- names(distribution)[2]
-test[[b]] <- lapply(distribution[[b]],
-                    prepare_data_LDA_gamma)
-
-rm(a,b #,test)
-```
-This part is not adapted
-```{r LDA visualize, eval = F}
-visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-  ggplot(aes(x = reorder_within(term,
-                                by = beta,
-                                within = topic),
-             y = beta,
-             fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, scales = "free") +
-    scale_x_reordered() +
-    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
-    coord_flip() +
-    theme_light() +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "beta.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(facet, 
-                              by = gamma, 
-                              within = topic), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma1.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(topic, 
-                              by = gamma,
-                              within = facet), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ facet, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma2.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
+###Using search K
+`stm::searchK` helps in the search.
+The function `findK` is used to vectorise searchK so we can apply it to the different elements of our corpus list (overview, manuals, description) in one go.
+```{r findK}
+#findK function 
+findK <- function(dtm, k_topics){
+  searchK(dtm$documents, dtm$vocab, K = k_topics, init.type = "Spectral")
 }
@@
 
-```{r LDA visualize all distrib, eval = F}
-visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){
+We train models for 74 different numbers of topics (14-200 by 2).
+Time estimate: for seq(from = 50, to = 100, by = 10) #18 models trained took 4:31-3:09 = (1 hour and 22 min)
+```{r finding K}
+#select number of topics
+k_topics = seq(from = 4, to = 150, by = 2)
 
-  # Beta distribution
-  data %>% 
-    prepare_data_LDA_beta %>%
-    visualize_LDA_beta(id_plot = id_plot)
-
-  # Gamma 1 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma1(id_plot = id_plot)
-
-  # Gamma 2 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma2(id_plot = id_plot)
-
-}
+#Run findK
+findingK <- stm_corpus %>%
+  map(findK, k_topics)
+```
+We inspect the findings:
+```{r plot evaluation}
+findK_plots <- map(findingK, plot) #see how to show.
 ```
 
-```{r LDA visualize all level, eval = F}
-visualize_LDA_all_level <- function(data, id_plot = "test"){
+```{r save findK}
+#save files
+save(findingK, file= "STM_estimate_k.RDATA")
 
-  data %>% 
-    visualize_LDA_all_distrib(level = Course,
-                              id_plot = paste(id_plot, "_course"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Cluster,
-                              id_plot = paste(id_plot, "_cluster"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Concentration,
-                              id_plot = paste(id_plot, "_concentration"))
-
-}
+#clean
+rm(findK, k_topics)
 ```
-
-### Plots
-```{r LDA plot, cache = TRUE, eval = F}
-load("LDA.RDATA")
-
-LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")
-
-LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")
-
-LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
-```
-
-```{r label, eval = FALSE, eval = F}
-tidy(LDA_manual_10, "beta") %>%
-  filter(beta > 1e-3) %>%
-  bind_tf_idf(term = term, document = topic, n = beta) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf) %>%
-  arrange(topic, desc(tf_idf))
-
-  count(term, topic) %>%
-  arrange(desc(n)) %>%
-
-  filter(beta > 1e-3) %>%
-  group_by(term) %>%
-    mutate(n_topic = n(),
-           beta = beta / n_topic) %>%
-  group_by(topic) %>%
-    top_n(10, beta)
-
-  count(topic, term, wt = beta) %>%
-  (term = term, document = topic, n = n) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf)
-
-  group_by(term) %>%
-  summarise(beta = sum(beta)) %>%
-  arrange(desc(beta))
-
-labels <- list(
-  description_10 = "X"
-)
-```
-
-```{r label bis, eval = FALSE}
-visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
-              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
-                              "Sociology", "Law", "Research", "International Politics",
-                              "Philosophy", "Humanities"))
-
-visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
-              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
-                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
-                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
-                              "Math", "Management and ?"))
-visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
-              topic_names = c(
-                "Information", "Psycho", "Bio", "Chem", "Sociology",
-                "History", "skills", "Europe", "Philosophy", "IR",
-                "Conference", "Law", "Media", "Philosophy", "Economics",
-                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
-                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
-```
+###Manual selection

### 2019-03-28 topic coherence .Rmd
creates coherence script

---
title: "Coherence"
author: "DARS"
date: "3/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r test set up}
library(textmineR)
library(Matrix)

load("Output/topic_model_gb.RDATA")

```
We need to import d_cast
#Just taking overview for 36 topics:
```{r coherence}
dtm <- d_cast$overview

#convert to sparse matrix
binDTM <- sparseMatrix(i = dtm$i, j = dtm$j, x = dtm$v, dims = c(dtm$nrow, dtm$ncol), dimnames = dimnames(dtm)) #from matrix

# Matrix multiplication for cooccurrence counts
coocCounts <- t(binDTM) %*% binDTM
coocCounts[1:5, 1:5]

term_topic_probability <- topic_model_gb$b_overview[[18]] # 36 topics

#coocurance matrix
coocurrance <- Dtm2Tcm(binDTM) #requires binDTM to be numeric matrix

as_tibble(coocurrance)

#inspect
coocurrance[1:5, 1:5]

#get top 5 words
top_words_topics <-  term_topic_probability %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  summarise(words = list(term))

# top words topic 1:
rows.to.keep <- which(rownames(coocurrance) %in% top_words_topics[1,]$words[[1]]) # matrix is squared same names for cols and rows

my_co <- coocurrance[rows.to.keep,rows.to.keep]

for(word in top_words_topics[1,]$words[[1]] ){
  score <- log((my_co[word, lag(word)]+1)/(my_co[word, word]*my_co[lag(word), lag(word)]))
}

CalcProbCoherence(phi = term_topic_probability, dtm = binDTM, M = 5)

pmap(.l = list(term_topic_probability), .f = CalcProbCoherence, dtm, 5)

coherence_UMas <- function(tf_idf) {
  tf_idf

}
```

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
add plotting function

@@
 We inspect the findings:
-```{r plot evaluation}
+```{r plot evaluation- package}
 findK_plots <- map(findingK, plot) #see how to show.
@@
 ```
-###Manual selection
+###From stm_eval
+```{r manual eval plots}
+
+plot_eval <- function(origin){
+stm_eval_model %>%
+  filter(Origin == origin) %>%
+  transmute(n_topic,
+            `Lower bound` = lbound,
+             Residuals    = map_dbl(residual, "dispersion"),
+            `Semantic coherence` = map_dbl(semantic_coherence, mean),
+            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
+  gather(Metric, Value, -n_topic) %>%
+  ggplot(aes(n_topic, Value, color = Metric)) +
+  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
+  geom_point()+
+  facet_wrap(~Metric, scales = "free_y") +
+  labs(x = "Number of Topics)",
+       y = NULL,
+       title = "Model diagnostics by number of topics")
+}
+
+plot_eval("manuals")
+plot_eval("overview")
+```

### 2019-03-28 Data Preparation.Rmd
minor change
Adding d_course to pillarII
remove unused variable from df rules_clean to speed up the app
Prepare text data in a separate RMD file for clarity

--- 2019-03-13 Data Preparation.Rmd
@@
 
-TODO:
-
-* when student takes a course multiple times:
-    * keep lowest grade
-    * keep highest grade 
-    * or keep both (much more complex)
-
 ```{r setup, include = FALSE}
@@
 library(hunspell) # Stemmer
+library(magrittr)
 ```
@@
 # selection of most important types of assessment an AoD to keep plots clear
-list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %>% print
-list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %>% print
+list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %T>% print
+list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %T>% print
 ```
@@
   # Transform data into tidy format to facilitate manipulation
-  gather(
-    key   = Assessment, 
-    value = assessment_covered,
-    Paper : Participation
-    ) %>%
+  gather(key   = Assessment, value = assessment_covered, Paper : Participation) %>%
 
@@
 
-  select(- c(assessment_covered, `Comment on Assessment`)) %>%
+  select(- c(assessment_covered, `Comment on Assessment`)) %T>%
 
@@
   # Transform data into tidy format to facilitate manipulation
-  gather(
-    key   = AoD, 
-    value = AoD_covered,
-    `Matrix Complete` : `Intercultural Skills`
-    ) %>%
+  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
 
@@
 
-  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %>%
+  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %T>%
 
   print
-```
-
-## Textual Data
-In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues.
-The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
-
-```{r read_in_pdfs}
-# helper function
-read_in_pdfs <- function(file){
-
-  Corpus(
-    x             = DirSource(file),
-    readerControl = list(reader = readPDF(control = list(text = "-layout")))
-    ) %>%
-
-    # turn corpus into a list to facilitate manipulation
-    as.list %>%
-
-    unname
-
-}
-```
-
-```{r catalogues, cache = TRUE}
-d_text <- list()
-
-d_text$catalogues <- "./Input/Catalogues" %>%
-  read_in_pdfs %>%
-  map(function(x) x$content)
-```
-
-To expand our topic modeling of course content, we analyse the material in the course manuals.
-The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
-
-```{r extract_code}
-# helper functions
-extract_code <- function(string) string %>% str_sub(start = 1, end = 7)
-```
-
-```{r manuals, cache = TRUE}
-d_text$manuals <- "./Input/Manuals 2017-18" %>%
-
-  read_in_pdfs %>%
-
-  # turn list into a tibble to facilitate manipulation
-  tibble(manuals = .) %>%
-
-  transmute(
-    `Course ID` = manuals %>% map(function(x) x$meta$id) %>% map_chr(extract_code),
-    year        = "2017-2018",
-    text        = manuals %>% map(content) %>% map_chr(str_c, collapse = " ")
-    ) %>%
-
-  print
-
-rm(read_in_pdfs)
 ```
@@
 ```{r read_csv_own_parsing}
-# set up
 col_parsing <- cols(
@@
 
-# helper function
 read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
@@
 d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
+
   map(read_csv_own_parsing) %>%
+
   bind_rows
@@
 
-  arrange(Assessment) %>%
+  arrange(Assessment) %T>%
 
@@
 
-  left_join(map_assessment_AoD, by = "Assessment") %>%
+  left_join(map_assessment_AoD, by = "Assessment") %T>%
 
@@
 
-  arrange(`Course ID`) %>%
+  arrange(`Course ID`) %T>%
 
@@
 ```{r d_course detail}
-# helper function
 count_and_paste <- function(df, var, colnam1, colnam2){
@@
 
-# helper function
 join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
@@
 
-  join_by_course_ID( d_AoD %>% count_and_paste(AoD, n_AoD, `AoD Covered`) %>% print) %>%
+  join_by_course_ID( d_AoD        %>% count_and_paste(AoD       , n_AoD       , `AoD Covered`        ) %T>% print) %>%
 
@@
 
-  join_by_course_ID( d_ILO %>% count_and_paste(Objectives, n_ILO, `ILO Covered`        ) ) %>%
+  join_by_course_ID( d_ILO        %>% count_and_paste(Objectives, n_ILO       , `ILO Covered`        )           ) %>%
 
@@
     everything()
-    ) %>%
+    ) %T>%
 
@@
       )
-    ) %>%
+    ) %T>%
 
@@
 
-  select(`Course ID`, Letters, Number, Level, everything()
-    ) %>%
+  select(`Course ID`, Letters, Number, Level, everything()) %T>%
 
   print
-```
-
-## Textual Data
-### Extracting Overviews
-In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.
-
-(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
-
-We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
-To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`).
-These pages are typically headers.
-Excluding them before the analysis allows use to keep the code relatively simple.
-We also make use the fact that the overviews always start with the code of the course, i.e.
-it starts with one of the elements of `course_code`; and we use `grep` to identify the first page of each overview.
-We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.
-
-In the loop, we first determine the content of the current and following page.
-If the current page is the first page of an overview, then we identify the overview (one or two pages) and save it to the tibble `d_description`.
-To identify the overview of a course, we check if the following page is either the first page of an overview or a page to exclude.
-If it is either of these, then the overview correspond to the content of the current page; but if the following page is neiter of these, then the overview correspond to the content of the current page and that of the following page.
-
-```{r overview set up}
-# Set up
-collapse_or <- function(string) string %>% str_c(collapse = "|")
-
-headers <- c(
-  "^Core Courses \\(COR\\)",
-  "^Humanities \\(HUM\\)",
-  "^Sciences \\(SCI\\)",
-  "^Social Sciences \\(SSC\\)",
-  "^Skills Trainings? \\(SKI\\)",
-  "^Projects? \\(PRO\\)",
-  "^Undergraduate Research", "UCM Undergraduate\r\n ? ?Research",
-  "Appendix"
-  ) %>%
-  collapse_or
-
-overview_start <- c(
-  "COR",
-  "HUM", "SCI", "SSC", 
-  "SKI", "PRO",
-  "UGR", "CAP"
-  ) %>% 
-  collapse_or
-
-years <- paste0(2014:2018, "-", 2015:2019)
-```
-
-```{r overview helper functions}
-# helper functions in order of use
-is_start_overview_section  <- function(string) string %>% str_detect(pattern = "^Core Courses \\(COR\\)")
-is_end_overview_section    <- function(string) string %>% str_detect(pattern = "Appendix")
-is_header                  <- function(string) string %>% str_detect(pattern = headers)
-
-is_overview_start          <- function(string) string %>% extract_code %>% str_detect(pattern = overview_start)
-paste_if_two_page_overview <- function(page, page_following){
-
-  if(page %>% is_overview_start){
-
-    if(page_following %>% is_overview_start | is.na(page_following))  page # include possibility of `is.na(page_following)` for last page of overview section
-    else                                                              paste(page, page_following)
-
-  }else                                                               NA_character_   # if the page is not the start of an overview, return an NA
-
-}
-
-add_year <- function(x, yr) x %>% mutate(year = yr)
-```
-
-```{r extract_overview}
-extract_overview <- function(catalogue){
-
-  # create tibble to facilitate manipulation
-  catalogue %>% 
-    tibble(page = .) %>%
-
-  # identify start and end of overview section of catalogue
-    mutate(
-      is_start_overview_section = page %>% is_start_overview_section,
-      is_end_overview_section   = page %>% is_end_overview_section
-      ) %>%
-
-    # I have checked that there is one and only one is_start_overview_section and no more than 1 is_end_overview_section
-      # if(sum(catalogue_all$is_start_overview_section) == 0) print("error: no overview_section_start"      )
-      # if(sum(catalogue_all$is_start_overview_section) >  1) print("error: multiple overview_section_start")
-      # if(sum(catalogue_all$is_end_overview_section  ) >  1) print("error: multiple overview_section_end"  )
-
-    # filter the overview section
-    mutate(
-      is_after_start_overview_section = cumany( is_start_overview_section),
-      is_before_end_overview_section  = cumall(!is_end_overview_section  ),
-      is_overview_section             = is_after_start_overview_section & is_before_end_overview_section
-      ) %>%
-    filter(is_overview_section) %>%
-
-    # exclude headers to only keep the overviews themselves
-    filter(! page %>% is_header) %>%
-
-    # paste current page and following page (`lead(page)`) if overview is two page long
-    transmute(
-      text        = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
-      `Course ID` = text %>% extract_code
-      ) %>%
-    filter(!is.na(text))
-
-}
-```
-
-```{r overview, cache = TRUE}
-d_text$overview <- d_text$catalogues %>%
-
-  map(extract_overview) %>%
-
-  # add the year to each observation to keep track of the evolution of the catalogue over time
-  map2(years, add_year) %>%
-
-  # turn list into a tibble to facilitate manipulation
-  bind_rows(d_text$overview) %>%
-  print
-
-# only keep the overviews and manuals for clarity
-d_text <- d_text[c("overview", "manuals")]
-
-rm(
-  headers, overview_start,
-  is_start_overview_section, is_end_overview_section, is_header, is_overview_start,
-  paste_if_two_page_overview, extract_overview,
-  years
-  )
-```
-
-### Extracting Descriptions
-Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
-The description section contains a brief description (200-500 words) of the content of the course.
-To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
-The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
-The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
-Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
-A handful overviews do not contain a *Literature* section.
-For these, the section *Instructional Format* marks the end of the description section.
-
-```{r description set up}
-# Setup
-symbol_to_line <- c("\r\n", "\n") %>% collapse_or
-start_descrip  <- c("^Description", "^Course Description") %>% collapse_or
-end_descrip    <- c(
-  "^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all",
-  "^Instructional format$"
-  ) %>% collapse_or
-```
-
-```{r description helper function}
-# helper functions
-split              <- function(string) string %>% str_split (pattern = symbol_to_line) %>% .[[1]]
-
-is_start_descrip   <- function(string) string %>% str_detect(pattern = start_descrip )
-is_end_descrip     <- function(string) string %>% str_detect(pattern = end_descrip   )
-```
-
-```{r extract_description}
-extract_description <- function(overview){
-
-  overview %>%
-    split %>%
-    tibble(line = .) %>%
-
-    mutate(
-      is_start_descrip = line %>% is_start_descrip,
-      is_end_descrip   = line %>% is_end_descrip # Having multiple ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
-      ) %>%
-
-    # filter the description section
-    mutate(
-      is_after_start_descrip = cumany( is_start_descrip),
-      is_before_end_descrip  = cumall(!is_end_descrip  ),
-      is_descrip             = is_after_start_descrip & is_before_end_descrip
-      ) %>%
-
-    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%
-
-    summarise(description = str_c(line, collapse = " ")) %>%
-
-    pull
-
-}
-```
-
-```{r description}
-d_text$description <- d_text$overview %>%
-  mutate(text = text %>% map_chr(extract_description))
-```
-
-### Tidy Text Format
-To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
-```{r tidy_text}
-# helper function
-tidy_text <- function(df){
-
-  df %>%
-    unnest_tokens(
-      output = word,
-      input  = text
-      )
-
-}
-```
-
-```{r tidy d_text}
-d_text <- d_text %>% map(tidy_text) %>% print
-
-rm(tidy_text)
-```
-
-### Stemming
-We then use the function `hunspell_stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
-
-We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`).
-We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`.
-However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals.
-Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
-
-```{r stem}
-# helper function
-stem <- function(term) {
-
-  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
-
-  n_stems <- length(stems)            # number of stems
-
-  if (n_stems == 0) term              # if no stems, return original term
-  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
-
-}
-```
-
-```{r dictionary, cache = TRUE}
-dictionary <- union(d_text$overview$word, d_text$manuals$word) %>%
-
-  tibble(word = .) %>%
-
-  mutate(word_stem = word %>% map_chr(stem))
-
-# terms for which the stem differs from the original word
-filter(dictionary, word != word_stem)
-```
-
-```{r destem}
-# TODO: "destem" terms by hand: cuss => discuss
-filter(dictionary, word_stem == "cuss")
-```
-
-Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.
-
-Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
-```{r stem_with_dictionary}
-# helper function
-stem_with_dictionary <- function(data){
-
-  data %>%
-
-    left_join(dictionary, by = "word") %>%
-
-    rename(
-      word_original = word,
-      word          = word_stem
-      )
-
-}
-```
-
-```{r stem d_text}
-d_text <- d_text %>% map(stem_with_dictionary)
-
-rm(stem_hunspell, stem_with_dictionary)
-```
-
-### Removing Stopwords
-Finally, we want to filter out some uninformative words from our textual data.
-For this, we first store all the unwanted words in a vector `sw_owm`.
-We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`.
-Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
-```{r sw_own}
-# Own stop words
-sw_own <- 1 : 1e3 %>% as.character %>% tibble( word = .)
-```
-
-```{r remove_sw}
-# helper function
-remove_sw <- function(data){
-
-  data %>%
-
-    anti_join(stop_words, by = "word") %>%
-
-    anti_join(sw_own, by = "word") %>%
-
-    # remove words of 1 or 2 letters
-    filter(nchar(word) > 2) %>%
-
-    # Remove words occuring once or twice in corpus (usually names, website links or typos)
-    add_count(word) %>%
-    filter(n > 2) %>%
-    select(-n)
-
-}
-```
-
-```{r sw d_text}
-d_text <- d_text %>% map(remove_sw) %>% print
-
-rm(sw_own, remove_sw)
 ```
@@
 
-```{r d_transcript set up}
-# Set up
-UCM_course <- d_text$overview$`Course ID` %>%
-  unique %>% 
-  paste(collapse = "|")
-```
+```{r d_transcript helper}
+course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")
 
-```{r d_transcript helper function}
-# helper function
-is_offered_at_UCM <- function(x) x %>% str_detect(UCM_course)
+is_UCM      <- function(course_code) course_code %>% str_detect(course_letter_UCM)
+is_elective <- function(course_code) course_code %>% str_detect("HUM|SCI|SSC")
 ```
@@
   filter(
-    `Module (Abbrev.)` %>% is_offered_at_UCM,
+    `Module (Abbrev.)` %>% is_UCM,
     `Program (Abbreviation)` == "7501"
@@
 
+```{r}
+d_transcript_augmented <- d_transcript %>% left_join(select(d_course, - Period), by = c("Course ID"))
+```
+
+```{r}
+d_transcript_elective <- d_transcript_augmented %>%
+  filter(`Course ID` %>% is_elective) %>%
+  select(`Student ID`, `Course ID`, time, Grade, grade_ceil)
+```
+
+### Issues
 ```{r issue d_transcript}
@@
 
+d_transcript %>%
+
+  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
+  filter(`Student ID` == "6087587") %>%
+  arrange(`Course ID`) %>%
+  pull(`Course ID`)
+
 #TODO: list issues here
@@
 ```{r}
-save(
-  d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
-  file = "Output/data_general.RDATA"
-  )
+save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")
 
-save(d_transcript, file = "Output/data_pillar_1.RDATA")
+save(d_transcript_augmented, d_transcript_elective, file = "Output/data_pillar_1.RDATA")
 
-save(d_text, d_transcript, file = "Output/data_pillar_2.RDATA")
+save(d_course, d_transcript, file = "Output/data_pillar_2.RDATA")
 ```

### 2019-03-28 Misc Code.Rmd
do not extract course description anymore since we do not use it in any analysis

@@
 ---
+
+# Extracting description (UCM only)
+
+Since the overviews contain a lot of information that does not interest us, we extract the description section from the overviews.
+The description section contains a brief description (200-500 words) of the content of the course.
+To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends.
+The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`.
+The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`).
+Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost all overviews.
+A handful overviews do not contain a *Literature* section.
+For these, the section *Instructional Format* marks the end of the description section.
+
+```{r description set up}
+start_descrip  <- c("^Description", "^Course Description") %>% collapse_or
+end_descrip    <- c(
+  "^Recommended Literature", "^ ?Required Litera", "^ ?Literature$", "Literature \\(all",
+  "^Instructional format$"
+  ) %>% collapse_or
+```
+
+```{r description helper function}
+is_start_descrip   <- function(string) string %>% str_detect(pattern = start_descrip )
+is_end_descrip     <- function(string) string %>% str_detect(pattern = end_descrip   )
+```
+
+```{r extract_description}
+extract_description <- function(overview){
+
+  overview %>%
+
+    split %>% tibble(line = .) %>%
+
+    mutate(
+      is_start_descrip = line %>% is_start_descrip,
+      is_end_descrip   = line %>% is_end_descrip # Having multiple ends (e.g. "literature" and "instructional format") is ok because we only use the first (cumany)
+      ) %>%
+
+    # filter the description section
+    mutate(
+      is_after_start_descrip = cumany( is_start_descrip),
+      is_before_end_descrip  = cumall(!is_end_descrip  ),
+      is_descrip             = is_after_start_descrip & is_before_end_descrip
+      ) %>%
+
+    filter(is_descrip, !is_start_descrip, !is_end_descrip) %>%
+
+    summarise(description = str_c(line, collapse = " ")) %>%
+
+    pull
+
+}
+```
+
+```{r description}
+d_text$description <- d_text$overview %>% mutate(text = text %>% map_chr(extract_description))
+```
 

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
clean workspace

@@
 
-```{r} 
-#testing 
-test_model <- stm_eval_model[1, ]
-
-my_stm_eval(list(test_model$documents, test_model$vocab, test_model$n_topic))
-
-my_stm_eval(documents = test_model$documents, vocab = test_model$vocab, n_topic = test_model$n_topic)
-
-test <- list(test_model$documents, test_model$vocab, test_model$n_topic)
-test %>% my_stm_eval
-
-test <- list(stm_eval_model$documents, stm_eval_model$vocab, stm_eval_model$n_topic)
-
-test %>% my_stm_eval
-
-test <- stm_eval_model %>% mutate(test = list(documents, vocab, n_topic) %>% pmap(list))
-
-stm_eval_model %>% mutate(test = test %>% map(my_stm_eval))
-test1<- test$test[[1]]
-
-```
-
 ####For evaluation
@@
                                  function(model) length(model$convergence$bound))
+    ) 
+```
+###Saving Results
+```{r save}
+#saving
+save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
+```
+
+```{r clean workspace}
+#clean workspace
+rm(# Generating functions:
+  my_stm, my_stm_eval,
+  #Extraction Functions
+  extract_dtm, extract_corpus, extract_documents, extract_vocab, extract_data,
+  extract_held_doc, extract_held_vocab, extract_helout_missing, 
+  my_model, my_tidy_gamma,
+  get_top_terms_topic, 
+  get_top_topics_course,
+  get_kw
   )

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
titles

@@
 ```{r manual eval plots}
-
+#Function
 plot_eval <- function(origin){
@@
 
+#Create plots
 plot_eval("manuals")

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
new documents

@@
 ```
+
+#New Documents
+##Align vocabulary
+```{r}
+mod.out #is model
+
+#now we process the remaining documents
+temp<-textProcessor(documents=gadarian$open.ended.response[101:nrow(gadarian)],
+                    metadata=gadarian[101:nrow(gadarian),])
+
+newdocs <- alignCorpus(new=temp, old.vocab=mod.out$vocab)
+#we get some helpful feedback on what has been retained and lost in the print out.
+#and now we can fit our new held-out documents
+
+fitNewDocuments(model=mod.out, documents=newdocs$documents, newData=newdocs$meta,
+                origData=out$meta, prevalence=~treatment + s(pid_rep),
+                prevalencePrior="Covariate")
+
+```
+##Fit new docs
+```{r}
+#An example using the Gadarian data.  From Raw text to fitted model.
+#(for a case where documents are all not processed at once see the help
+# file for alignCorpus)
+temp<-textProcessor(documents=gadarian$open.ended.response,metadata=gadarian)
+out <- prepDocuments(temp$documents, temp$vocab, temp$meta)
+set.seed(02138)
+#Maximum EM its is set low to make this run fast, run models to convergence!
+mod.out <- stm(out$documents, out$vocab, 3, prevalence=~treatment + s(pid_rep), 
+              data=out$meta, max.em.its=5)
+fitNewDocuments(model=mod.out, documents=out$documents[1:5], newData=out$meta[1:5,],
+               origData=out$meta, prevalence=~treatment + s(pid_rep),
+               prevalencePrior="Covariate")
+
+```

### 2019-03-28 Pillar 1 - Topic Profile.Rmd

@@
 
-find_prep <- function(objective){
+find_prep <- function(objective, subset_size = 6){
 
@@
 
-  if(nrow(data_temp) <= 7) return(NULL)
+  if(nrow(data_temp) <= (subset_size + 1)) return(NULL) # perhaps use formula similar to min(8, nrow(df) / 2)
 
@@
   # best subset selection
-  m <- regsubsets(Grade ~ ., data_temp, nvmax = 6)
+  m <- regsubsets(Grade ~ ., data_temp, nvmax = subset_size)
 
-  coefi <- coef(m, 6)[-1]  # check that 6 is usually a good subset size
+  coefi <- coef(m, subset_size)[-1]  # check that 6 is usually a good subset size
 

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
test fit new docs

--- 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
@@
 #load
-load("output/data_pillar_2.RDATA")
+#load("output/data_pillar_2.RDATA")
+load("Output/d_text.RDATA")
 
 # keep most recent year
-d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
+#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
 ```
@@
 ```
+
+#New Documents
+##Align vocabulary
+```{r align vocab}
+#single case: Fasos topics
+d_text1 <- d_text #backup current code
+
+fasos_docs <- d_text$catalogues%>%filter(department == "European_studies") %>%
+  select(-department)
+
+fasos_cast <- my_cast_dtm(fasos_docs)
+
+```
+##Fit new docs
+```{r}
+model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
+  pull(Model)
+
+model <- model[[1]]
+
+# fitting:
+out <- asSTMCorpus(fasos_cast)
+
+newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
+
+fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix
+
+plot.STM(model, type ="summary")
+
+fasos_theta$theta #nice kind of makes sense
+
+```

### 2019-04-02 Pillar_2_-_Topic_Modeling.Rmd
very old topic models

--- 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
@@
 
-COMMENTS: 
-Q. Jerry -> For preprocessing (selecting vocabulary), how do we assign words that appear in only one document to a topic? Does it make sense to remove them?
-
-```{r setup, include = T}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
+                      eval = FALSE)
 ```
 
-```{r library, message = F}
+```{r library, message = FALSE, eval = TRUE}
 library(tidyverse)
@@
 # Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
-```{r import data}
+We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
+`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
+For `d_description` and `d_overview`, we keep only the most recent year.
+```{r import data, eval = TRUE}
 load("output/data_pillar_2.RDATA")
@@
 # LDA
-
-```{r my_cast_tdm}
+The function `my_cast_tdm` casts our dataframes into a tdm.
+```{r my_cast_tdmxxxxx}
 my_cast_tdm <- function(data, level) data %>%
@@
 ## Ideal Number of Topics (RUN ON UM COMPUTER)
+To decide the number of topics to discover, we run (four) three different tests.
 
-```{r controls}
+First we set the control for the test.
+```{r controls, eval = TRUE}
 my_control <- list(
 
-  nstart = 10,
-  seed   = 1 : 10,
+  nstart = 20,
+  seed   = 1 : 20,
   best   = TRUE,
 
-  burnin = 500,
-  iter   = 2000,
+  burnin = 1000,
+  iter   = 15000,
   thin   = 100
@@
 
+```{r fast control}
+my_control_fast <- list(
+
+  nstart = 1,
+  seed   = 1,
+  best   = TRUE,
+
+  burnin = 5,
+  iter   = 10,
+  thin   = 2
+
+)
+```
+
+###With Package built in Function
+The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
 ```{r function my_FindTopicsNumber }
@@
   topics = n_topics,
-  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
+  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
   method = "Gibbs",
   control = my_control,
-  mc.cores = 1L
+  mc.cores = 4L
 
@@
 
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
 
@@
 save(result_description,
-     file = "Output/LDA_ntopics_description.RDATA")
+     file = "Output/LDA_ntopics.RDATA")
 
@@
 
-result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
 
@@
 
-result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))
+result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))
 
@@
 
+We examine the result of the experiment by plotting them on a graph.
 ```{r LDA number topics plot}
 
-load("Output/LDA_ntopics_description.RDATA")
-
-load("Output/LDA_ntopics_overview.RDATA")
-
-load("Output/LDA_ntopics_manual.RDATA")
+load("Output/LDA_ntopics.RDATA")
 
 result_description %>%
-  select(-Griffiths2004) %>%
   FindTopicsNumber_plot
@@
 ```
+From the results we see that the ideal number of topics is somewhere between 35 and 40.
 
 ## Fitting Model
+The function `my_cast_tdm` casts our dataframes into a tdm.
+```{r my_cast_tdm, eval = TRUE}
+my_cast_tdm <- function(data) data %>%
+  count(`Course ID`, word) %>%
+  cast_dtm(`Course ID`, word, n)
 
-```{r LDA fit, cache = TRUE}
-n_topics <- 5
-levels   <- c("description", "overview", "manual")
-list_nam <- character(0)
+d_cast <- d_text %>% map(my_cast_tdm)
 
-for(level in levels){
+rm(my_cast_tdm)
+```
 
-  dataset   <- get(paste("d", level, "cast", sep = "_"))
+The function `my_LDA` fits an LDA model on the DTM using the previous controls.
+```{r my_LDA, eval= TRUE}
+
+#my_LDA
+my_LDA <- function(n_topics, corpus, control = my_control){
 
   LDA_model <- LDA(
-    x       = dataset,
+    x       = corpus,
     k       = n_topics,
     method  = "Gibbs",
-    control = list(
-      nstart  = 10,
-      seed    = c(1:10),
-      best    = TRUE,
+    control = control
+    )
+}
 
-      burnin  = 4000,
-      iter    = 5000,
-      thin    = 500,
+```
 
-      verbose = 1e3,
-      save    = 1e3,
-      keep    = 1e3)
+Next we train our model with different number of topics.
+```{r LDA fit, cache = TRUE, eval = TRUE}
+topic_model <- tibble(
+
+  n_topic = seq(from = 5, to = 250, by = 5)
+
+  ) %>%
+
+  mutate(
+    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
+    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
   )
+```
 
-  nam <- paste("LDA", level, n_topics, sep = "_")
+##Model Evaluation
+###Perplexity
+Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
+```{r perplexity function, eval = TRUE}
 
-  assign(
-    x     = nam,
-    value = LDA_model
-  )
+#perplexity Function
+my_perplexity <- function(model, d_cast){
+  perplexity(model, d_cast, estimate_theta = FALSE)
+}
 
-  list_nam <- c(list_nam, nam)
+#Get perplexity
+test_perplexity <- topic_model %>%
+  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
+         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
+```
+
+###log_likelihood
+```{r log likelihood, eval = TRUE}
+# #my_loglikelihood function
+# my_loglike <- function(model){
+#   return(model@loglikelihood)
+# }
+# 
+# #get loglikelihood
+# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
+#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))
+
+#Log likelihood:
+test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
+                               logLik_manual   = map(.x = TM_manual,   .f = logLik))
+
+```
+
+###Plots
+```{r perplexity plots, eval = TRUE}
+#perplexity
+plot(topic_test$n_topic, topic_test$perplex_overview)
+plot(topic_test$n_topic, topic_test$perplex_manual)
+
+#log likelihood
+plot(test3$n_topic, test3$logLik_overview)
+plot(test3$n_topic, test3$logLik_manual)
+```
+
+##Get Beta/Gamma functions
+```{r getting gamma and beta, eval = TRUE}
+get_beta <- function(results){
+
+  tidy(results, matrix = "beta")           %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(beta) )
 
@@
 
-save(list = list_nam,
-     file = "LDA.RDATA")
+get_gamma <- function(results){
+
+  tidy(results, matrix = "gamma")          %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(gamma) )
+}
+
 ```
 
-## Visualization
+##Apply beta and gamma
+```{r applying get_gamma and get_beta, eval = TRUE}
+topic_model_gb <- topic_model %>%
+  transmute(
+    n_topic    = n_topic,
+    g_overview = TM_overview %>% map( .f = get_gamma),
+    g_manual   = TM_manual   %>% map( .f = get_gamma),
+    b_overview = TM_overview %>% map( .f = get_beta),
+    b_manual   = TM_manual   %>% map( .f = get_beta)
+      )
+```
+##Saving filed for different sessions
+```{r saving, eval = TRUE}
+save(topic_model_gb, 
+     file = "Output/topic_model_gb.RDATA")
+```
+#Distributions
+#NOTE: We need to select how many topics to use
+##Distributions of best models
+```{r Distributions, eval = FALSE}
+#select number of topics
+n_topics_overview <- 36
+n_topics_manual   <- 40
+
+#Crop models
+TM_overview <- topic_model_gb %>%
+  filter(n_topic== n_topics_overview)
+
+TM_manual   <- topic_model_gb %>%
+  filter(n_topic== n_topics_manual)
+
+#Distributions
+distribution <- list()
+
+distribution$beta$overview  <- TM_overview %>% pull(b_overview)
+distribution$beta$manual    <- TM_manual   %>% pull(b_manual)
+
+distribution$gamma$overview <- TM_overview %>% pull(g_overview)
+distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)
+
+```
+##Inspect topics
+THE TOPICS ARE SUPPER STRANGE!
+```{r inspect topics, eval = FALSE}
+
+inspect_topics <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(10, beta)
+
+}
+
+topics <-  lapply(
+  distribution$beta,
+  inspect_topics
+)
+```
+#App
+##Selectig keywords
+```{r key words}
+get_top_words <- function(d_beta, n = 5){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(n, beta) %>%
+    pull(term)%>%
+    unique
+}
+
+kw <- lapply(
+  distribution$beta,
+  get_top_words
+)
+```
+####TEMPORTARY: stopwords for keywords
+This section is for presentations
+```{r stopwords for kw}
+#kw$overview
+not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
+                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
+
+remove_words <- function(x){
+  setdiff(x, not_include)
+}
+
+kw1 <- lapply(
+  kw,
+  remove_words
+)
+
+```
+##Convenience vectors for APP
+```{r for convenience}
+# set seed
+set.seed(1)
+
+#
+## All courses
+course_all <- d_course %>%
+  inner_join(
+    d_transcript,
+    by = "Course ID"
+  ) %>%
+  distinct(
+    `Course ID`
+  ) %>%
+  # remove semester abroad, skills and projects
+  filter(
+    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
+  ) %>%
+  pull
+
+#
+##courses following_semester
+course_following_semester <- sample(
+  x       = course_all,
+  size    = 60,
+  replace = FALSE
+  ) %>% sort
+```
+## Saving files for APP
+```{r app files}
+save(distribution, kw, course_all, course_following_semester,
+     file = "App/Recommender System/data_topic_models.RDATA")
+```
+
+# Visualization
 ### Functions 
+This part is adapted 
 ```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(results){
+prepare_data_LDA_beta <- function(d_beta){
 
-  tidy(results, matrix = "beta") %>%
+  data.frame(d_beta) %>%
     mutate(topic = paste("Topic", topic)) %>%

### 2019-04-02 Data Preparation - Course Catalogues.Rmd

---
title: "Data Preparation - Course Catalogues"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")

library(tidyverse)
library(tidytext)
library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
library(magrittr)
```

# Helper functions

```{r helpers}
extract_id_pdf    <- function(string) string %>% str_sub(start = 1, end = - 5)
extract_id_course <- function(string) string %>% str_sub(start = 1, end =   7)

collapse_or       <- function(string) string %>% str_c(collapse = "|")
collapse_space    <- function(string) string %>% str_c(collapse = " ")

symbol_to_line    <- c("\r\n", "\n") %>% collapse_or
split             <- function(string) string %>% str_split(pattern = symbol_to_line) %>% .[[1]]

remove_header_UCV <- function(string) string %>% str_sub(29, -1)

overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\r\n *Maastricht Science Programme")

headers_UCM_UCV <- c("^ *Core Courses",
                     "^Humanities \\(HUM\\)",
                     "^ *Life Sciences Courses",
                     "^Sciences \\(SCI\\)",
                     "^ *Social Sciences",
                     "^ *Skills Trainings",
                     "^ *Projects",
                     "^Undergraduate Research",
                     "Appendix") %>% collapse_or
is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV)

course_code_UCM_UCV <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA" # UCV
                         ) %>% collapse_or
overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV) # simplify with %in% course_code_UCM
```

# Importing course data

```{r read_in_pdfs}
read_in_pdfs <- function(file){

  Corpus(
    x             = DirSource(file),
    readerControl = list(reader = readPDF(control = list(text = "-layout")))
    ) %>%

    # turn corpus into a tibble to facilitate manipulation
    as.list %>% tibble(raw = .) %>%

    transmute(
      ID   = raw %>% map(function(x) x$meta$id) %>% map_chr(extract_id_pdf),
      text = raw %>% map(content) 
      )

}
```

## Application
```{r d_text}
d_text <- list()
```

```{r d_text$catalogues}
d_text$catalogues <- tribble(
  ~ ID              ,  ~ page_top                  , ~ before_overview                       ,
  "European_studies", "^.Bachelor European Studies", "Faculty of Arts and Social Sciences"   ,
  "Psychology"      , "^.Bachelor Psychology"      , "Faculty of Psychology and Neuroscience",
  "UCV"             , NA_character_                , NA_character_                           ,
  "UCM"             , NA_character_                , NA_character_                                   
  ) %>%

  full_join(read_in_pdfs("./Input/Catalogues/UM"), by = "ID") %>%

  mutate(year = "2018-2019") %>%
  rename(catalogue = text)
```

```{r d_text$manuals}
d_text$manuals <- read_in_pdfs("./Input/Manuals 2017-18") %>% rename(`Course ID` = ID) %>% mutate(text = text %>% map_chr(str_c, collapse = " "))
```

# Extracting course overviews

In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.

(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

We start by extracting the overviews which are 1 or 2 page long and contain important information of a course. To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`). These pages are typically headers. Excluding them before the analysis allows use to keep the code relatively simple. We also make use the fact that the overviews always start with the code of the course, i.e. it starts with one of the elements of `course_code`; and we use `grep` to identify the first page of each overview. We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.

In the loop, we first determine the content of the current and following page. If the current page is the first page of an overview, then we identify the overview (one or two pages) and save it to the tibble `d_description`. To identify the overview of a course, we check if the following page is either the first page of an overview or a page to exclude. If it is either of these, then the overview correspond to the content of the current page; but if the following page is neiter of these, then the overview correspond to the content of the current page and that of the following page.

## ES, PSY
```{r overview_ES_PSY}
overview_ES_PSY <- function(catalogue, ID, page_top, before_overview){

  catalogue %>%

    # create tibble to facilitate manipulation
    collapse_space %>% split %>% tibble(line = .) %>%

    # remove page numbers and page top to faciliate the identification of the course description starts
    mutate(page_top    = str_detect(line, page_top),
           page_number = page_top %>% lead(default = FALSE)) %>%

    filter(!page_top, !page_number) %>%

    # identify course descriptions
    mutate(overview_start = str_detect(line, before_overview) %>% lag(default = FALSE)) %>%
    mutate(overview_id    = cumsum(overview_start)) %>%

    filter(overview_id != 0) %>%

    # extract course description
    group_by(overview_id) %>% 
    summarize(text        = line %>% str_c(collapse = " "),
              `Course ID` = line %>% str_c %>% .[[1]]) %>%
    mutate(department  = ID) %>%
    select(-overview_id)

}
```

## UCM, UCV

```{r paste_if_2_page_overview}
paste_if_2_page_overview <- function(page, page_following){

  if(! page %>% overview_start) NA_character_ # if the page is not the start of an overview, return an NA

  else{
    if(page_following %>% overview_start | is.na(page_following))  page # include possibility of NA for last page of overview section
    else                                                           str_c(page, page_following)
  }

}
```

```{r overview_UCM}
overview_UCM_UCV <- function(catalogue, ID){

  if(ID == "UCV") catalogue <- catalogue %>% remove_header_UCV

  # create tibble to facilitate manipulation
  catalogue %>% tibble(page = .) %>%

  # identify start and end of overview section of catalogue
  mutate(overview_section_start = page %>% overview_section_start,
         overview_section_end   = page %>% overview_section_end  ) %>%

  # filter the overview section
  mutate(after_overview_section_start = cumany( overview_section_start),
         before_overview_section_end  = cumall(!overview_section_end  )) %>%
  filter(after_overview_section_start & before_overview_section_end    ) %>%

  # exclude headers to only keep the course overviews themselves
  filter(! page %>% is_header) %>%

  # paste current page and following page (`lead(page)`) if overview is two page long
  transmute(text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
            `Course ID` = text %>% extract_id_course) %>%
    mutate(department  = ID) %>%
    filter(!is.na(text))

}
```

## Application
```{r overview}
overview <- function(ID, catalogue, page_top, before_overview){

  if(ID %in% c("European_studies", "Psychology")){
    catalogue %>% overview_ES_PSY(ID = ID, page_top = page_top, before_overview = before_overview)

  }else if(ID %in% c("UCM", "UCV")){
    catalogue %>% overview_UCM_UCV(ID = ID)

  }else "to do"

}
```

```{r}
d_text$catalogues <- d_text$catalogues %>% mutate(overviews = list(ID, catalogue, page_top, before_overview) %>% pmap(overview))
```

```{r}
d_text$catalogues <- d_text$catalogues$overviews %>% bind_rows
```

# Clean data

## Tidy data
To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).

```{r}
tidy_text <- function(df) df %>% unnest_tokens(output = word, input = text)
```

```{r tidy d_text}
d_text <- d_text %>% map(tidy_text) %T>% print

rm(tidy_text)
```

## Stem data
We then use the function `hunspell_stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.

We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`). We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`. However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals. Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.

```{r stem}
stem <- function(term) {

  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
  n_stems <- length(stems)            
  if (n_stems == 0) term              # if no stems, return original term
  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem

}
```

```{r dictionary, cache = TRUE}
dictionary <- union(d_text$catalogues$word, d_text$manuals$word) %>%

  tibble(word = .) %>%

  mutate(word_stem = word %>% map_chr(stem))

# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)
```

```{r destem}
# TODO: "destem" terms by hand: cuss => discuss
filter(dictionary, word_stem == "cuss")
```

Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.

Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.

```{r stem_with_dictionary}
stem_with_dictionary <- function(data){

  data %>% left_join(dictionary, by = "word") %>%

    rename(word_original = word,
           word          = word_stem)

}
```

```{r stem d_text}
d_text <- d_text %>% map(stem_with_dictionary)

rm(stem, stem_with_dictionary)
```

# Remove stopwords

Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r sw_own}
sw_own <- 1 : 1e3 %>% as.character %>% tibble( word = .)
```

```{r remove_sw}
remove_sw <- function(data){

  data %>%

    anti_join(stop_words, by = "word") %>%
    anti_join(sw_own    , by = "word") %>%

    # remove words of 1 or 2 letters
    filter(nchar(word) > 2) %>%

    # Remove words occuring once or twice in corpus (usually names, website links or typos)
    add_count(word) %>%
    filter(n > 2) %>%
    select(-n) %>%

    # remove NA
    filter(!is.na(word))

}
```

```{r sw d_text}
d_text <- d_text %>% map(remove_sw) %T>% print

rm(sw_own, remove_sw)
```

# Save data

```{r}
save(d_text, file = "Output/d_text.RDATA")
```

### 2019-04-02 Pillar 1 - t-test.Rmd

---
title: "Pillar 1 - t-test"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")

library(tidyverse)
library(arulesSequences)
library(magrittr)

load("Output/data_pillar_1.RDATA")
load("output/d_transcript_cum.RDATA")
```

# Conduct t-test
```{r my_t_test}
d_transcript_cum_informative <- left_join(d_transcript_cum, d_transcript_informative, by = c("sequenceID" = "Student ID", "eventID" = "time"))

my_t_test <- function(predictor, response){

  d_transcript_cum_informative %>%

    filter(`Course ID` == response) %>%

    mutate(has_taken_pred = course_past %>% map_lgl(~ predictor %in% .)) %>% # create two groups: (i) have taken the predictor (ii) have not takne predictor

    t.test(Grade ~ has_taken_pred, data = .)

}
```

```{r d_test}
all_courses <- unique(d_transcript_informative$`Course ID`)

d_test <- crossing(predictor = all_courses, response = all_courses) %>%

  filter(predictor != response) %>%

  mutate(t_test = list(predictor, response) %>% pmap(possibly(my_t_test, otherwise = "only one sample for t test")))
```

# Exploring t-test results

20,000 combinations courses

## Combinations of course for which no t-test was possible ()

8,000 combinations for which one of the sample sizes <= 1.

```{r}
samples <- function(predictor, response){

  d_transcript_cum_informative %>%

    filter(`Course ID` == response) %>%

    summarize(
      n_total   = n(),
      n_taken     = course_past %>% map_lgl(~   predictor %in% .) %>% sum,
      n_not_taken = course_past %>% map_lgl(~ ! predictor %in% .) %>% sum
      )

}

test_impossible <- d_test %>%

  filter(t_test %>% map_lgl(~typeof(.) != "list")) %>%

  mutate(samples = list(predictor, response) %>% pmap(samples)) %>%

  unnest(samples, .drop = TRUE) %>%

  select(response, predictor, everything())
```

## Results of t-test

After filtering, 154 combinations left.

```{r}
test_tidy <- d_test %>%

  filter(t_test %>% map_lgl(~ typeof(.) != "character")) %>%

  mutate(tidied = t_test %>% map(broom::tidy)) %>% # in this case, broom::tidy and broom::glance yield the same results. broom::augment does not work.

  unnest(tidied, .drop = TRUE) %>%

  # disregard advanced-level predictor & introductory-level response
  filter(! str_detect(predictor, "30")) %>% filter(! str_detect(response, "10")) %>%

  # disregard negative estimates & non-significant tests
  filter(estimate > 0) %>% filter(p.value < 0.05) %>%

  group_by(response) %>% arrange(response, desc(estimate)) %>% select(response, predictor, everything())
```

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd

@@
   pull(Model)
-
 model <- model[[1]]
@@
 out <- asSTMCorpus(fasos_cast)
-
 newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
-
 fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix
 
+my_names <- names(newdocs$documents)
+
+fasos_theta$theta #nice kind of makes sense
 plot.STM(model, type ="summary")
 
-fasos_theta$theta #nice kind of makes sense
+rownames(fasos_theta$theta) <- my_names
 
+new_courses_theta <- fasos_theta$theta
+set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))
+new_courses_theta %>%  mutate(Topic = paste("Topic_" rownames))
 ```

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
revert to without covariates version

@@
 ```
+###As corpus
+```{r}
 
+```
 # TF-IDF
@@
 
+```{r covariates}
+#get covariates
+covariates <- tribble(
+  ~Origin,    ~Data,
+  "catalogues", d_text$catalogues %>% distinct(`Course ID`, department),
+  "manuals", d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
+)
+```
 ###STM Corpus
@@
 ```{r as STM corpus, eval = TRUE}
+
 stm_corpus <- d_cast %>% map(asSTMCorpus)
+
 ```
@@
 ```{r my_STM, eval= TRUE}
-my_stm <- function(n_topics, corpus){
+my_stm <- function(n_topics, corpus, data){
 
@@
   n_topic = rep(topic_numbers, each = 2) ) %>%
-
   mutate(
   #Identification information
-    Origin     = rep(c("overview", "manuals"), length(topic_numbers)),         
+  Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
   `Topic ID` = paste(Origin, n_topic, sep = "_"),
+  #DTM
 
-    #DTM
   DTM       = pmap(.l = list(Origin), .f = extract_dtm),
+
   doc_names = map(DTM, rownames),
-
   #STM Corpus
@@
   Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
-
   #Fit Model
@@
   Exclusivity        = map(Model, exclusivity),
+
   semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
@@
   ##Inspection
-
   #Beta distribution
   Beta = pmap(.l = list(Model),  .f = tidy),
+
   #Gamma distribution
@@
 
-    #END MUTATE PARENTHESIS
 )
@@
 ```
-
+####TESTING AND INSPECTING MODELS
+```{r model inspection}
+my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
+```
 ####For evaluation
@@
 ```
+#Vizualization
+```{r extract topic model}
+select_topic_model <- function(origin, n_topic){
+  model <- stm_model %>% 
+    filter(Origin == origin & n_topic == n_topic) %>%
+    pull(Model)
 
+  model <- model[[1]]
+  return(model)
+}
+
+test <- select_topic_model("catalogues", 10)
+
+plot.STM(test, "perspectives", topics = c(1,5))
+```
 #New Documents
@@
 ```{r align vocab}
+#back up current code
+d_text1 <- d_text
+
 #single case: Fasos topics
-d_text1 <- d_text #backup current code
-
-fasos_docs <- d_text$catalogues%>%filter(department == "European_studies") %>%
+fasos_docs <- d_text$catalogues %>%
+  filter(department == "European_studies") %>%
   select(-department)
@@
 ```{r}
-model <- stm_model %>% filter(`Topic ID`=="overview_10")%>%
-  pull(Model)
-model <- model[[1]]
-
 # fitting:
@@
 new_courses_theta <- fasos_theta$theta
+
 set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))
-new_courses_theta %>%  mutate(Topic = paste("Topic_" rownames))
+
+new_courses_theta %>%  mutate(Topic = paste("Topic_", rownames))
 ```
+#Experiment
+```{r experoment}
+estimateEffect(formula = 1:5 ~department, meta = test$meta)
+
+```

### 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
saveing models

@@
 #saving
-save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
+my_models <-  list(use = stm_model, eval = stm_eval_model)
+save(my_models , file="STM_models.RDATA")
 ```

### 2019-04-04 Messy Code/stm single case.Rmd

--- 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
@@
 ---
-title: "Pillar 2 - (STM) Topic Modeling"
+title: "STM single case"
 author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
+date: "4/2/2019"
+output: html_document
 ---
 
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
-                      eval = FALSE)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 
-##Functions for internal faceting
-```{r function reorder_within & co., echo = FALSE, eval = TRUE}
-
-# Function for ordering within facet:
-# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
-
-reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
-  new_x <- paste(x, within, sep = sep)
-  stats::reorder(new_x, by, FUN = fun)
-}
-
-scale_x_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-
-scale_y_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-```
-
 ##Loading data
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
+We load the environment `Output/d_text.RDATA`. It contains the data sets:
 `d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
@@
 #load
-#load("output/data_pillar_2.RDATA")
 load("Output/d_text.RDATA")
-
-# keep most recent year
-#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
-```
-###As corpus
-```{r}
-
-```
-# TF-IDF
-We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.
-
-## Functions for Generating Barplots and Word Clouds
-The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
-```{r compute_tf_idf, cache = TRUE}
-#
-##Function
-compute_tf_idf <- function(data){
-
-  data %>%
-    count(
-      `Course ID`,
-      word
-      ) %>%
-    bind_tf_idf(
-      term = word, 
-      document = `Course ID`,
-      n = n
-      )
-}
-
-#
-##Application
-tf_idf <- map(d_text, .f = compute_tf_idf)
-
-#
-##Clean workspace
-rm(compute_tf_idf)
-```
-
-The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
-```{r plot_tf_idf}
-plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){
-
-  #
-  # Barplot
-  g <- data %>%
-    ggplot(
-      aes(
-        x = reorder_within(word, tf_idf, facet), 
-        y = tf_idf
-        )
-      ) +
-    geom_col(
-      show.legend = FALSE
-      ) +
-    labs(
-      x = NULL,
-      y = "tf-idf"
-      ) +
-    scale_x_reordered() +
-    facet_wrap(
-      facets = ~ facet, 
-      scales = "free",
-      ncol = n_col
-      ) +
-    coord_flip()
-
-  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-  #
-  # Word Cloud
-  g <- data %>%
-    group_by(
-      facet
-      ) %>%
-    mutate(
-      freq = tf_idf / sum(tf_idf)
-      ) %>% # normalization within facet
-    ggplot(
-      aes(
-        size = freq ^ 0.7, 
-        label = word, 
-        color = freq ^ 0.7
-        )
-      ) +
-    geom_text_wordcloud_area(
-      area_corr_power = 1,
-      eccentricity    = 1,
-      rm_outside      = T
-      ) +
-    scale_radius(
-      range = c(2, 10),
-      limits = c(0, NA)
-      ) +
-    scale_color_gradient(
-      low = "red", 
-      high = "blue"
-      ) +
-    facet_wrap(
-      facet = ~ facet,
-      ncol = n_col
-      ) + 
-    theme(
-      strip.text.x     = element_text(),
-      panel.background = element_rect(fill = "white"),
-      plot.title       = element_text(hjust = 0.5)
-    )
-
-  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-}
-```
-
-## Course Level
-The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
-We apply the function to `id_plot` and pipe it to produce graphs.
-```{r tf-idf course, cache = TRUE}
-prepare_tf_idf_course <- function(data){
-
-  data %>%
-
-    # Selection 25 courses randomly
-    filter(
-      `Course ID` %in% sample(
-        x = unique(.$`Course ID`),
-        size = 25, 
-        replace = FALSE
-        )
-      ) %>%
-
-    # Select top 10 words per course 
-    group_by(
-      `Course ID`
-      ) %>%
-    filter(
-      n >= 2
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = `Course ID`
-      )
-
-  }
-
-set.seed(123)
-tf_idf$overview %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_overview")
-
-set.seed(123)
-tf_idf$manual %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_manual")
-
-rm(prepare_tf_idf_course)
-```
-
-## Cluster Level
-```{r tf-idf cluster, cache = TRUE}
-prepare_tf_idf_cluster <- function(data){
-
-  data %>%
-
-    # Include the variable Cluster
-    left_join(
-      select(d_course, `Course ID`, Cluster),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Cluster)
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Cluster, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10, 
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Cluster
-      )
-
-}
-
-tf_idf$overview %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_overview")
-
-tf_idf$manual %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_manual")
-
-rm(prepare_tf_idf_cluster)
-```
-
-## Concentration Level
-```{r tf-idf concentration, cache = TRUE}
-prepare_tf_idf_concentration <- function(data){
-
-  data %>%
-
-    # Include the variable Concentration
-    left_join(
-      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Concentration)
-      ) %>%
-    gather(
-      key = X,
-      value = Concentration,
-      Concentration, `Concentration (additional)`,
-      na.rm = TRUE
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Concentration, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Concentration
-      )
-
-}
-
-tf_idf$overview %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_overview")
-
-tf_idf$manual %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_manual")
-
-rm(prepare_tf_idf_concentration, plot_tf_idf)
 ```
@@
 ```
-###Saving Results
-```{r save}
-#saving
-save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
-```
-
-```{r clean workspace}
-#clean workspace
-rm(# Generating functions:
-  my_stm, my_stm_eval,
-  #Extraction Functions
-  extract_dtm, extract_corpus, extract_documents, extract_vocab, extract_data,
-  extract_held_doc, extract_held_vocab, extract_helout_missing, 
-  my_model, my_tidy_gamma,
-  get_top_terms_topic, 
-  get_top_topics_course,
-  get_kw
-  )
-```
-
-##Finding Number of Topics
-We want to estimate the number of topics that exist in the data, to select a model for them.
-
-###Using search K
-`stm::searchK` helps in the search.
-The function `findK` is used to vectorise searchK so we can apply it to the different elements of our corpus list (overview, manuals, description) in one go.
-```{r findK}
-#findK function 
-findK <- function(dtm, k_topics){
-  searchK(dtm$documents, dtm$vocab, K = k_topics, init.type = "Spectral")
-}
-```
-
-We train models for 74 different numbers of topics (14-200 by 2).
-Time estimate: for seq(from = 50, to = 100, by = 10) #18 models trained took 4:31-3:09 = (1 hour and 22 min)
-```{r finding K}
-#select number of topics
-k_topics = seq(from = 4, to = 150, by = 2)
-
-#Run findK
-findingK <- stm_corpus %>%
-  map(findK, k_topics)
-```
-We inspect the findings:
-```{r plot evaluation- package}
-findK_plots <- map(findingK, plot) #see how to show.
-```
-
-```{r save findK}
-#save files
-save(findingK, file= "STM_estimate_k.RDATA")
-
-#clean
-rm(findK, k_topics)
-```
-###From stm_eval
-```{r manual eval plots}
-#Function
-plot_eval <- function(origin){
-stm_eval_model %>%
-  filter(Origin == origin) %>%
-  transmute(n_topic,
-            `Lower bound` = lbound,
-             Residuals    = map_dbl(residual, "dispersion"),
-            `Semantic coherence` = map_dbl(semantic_coherence, mean),
-            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
-  gather(Metric, Value, -n_topic) %>%
-  ggplot(aes(n_topic, Value, color = Metric)) +
-  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
-  geom_point()+
-  facet_wrap(~Metric, scales = "free_y") +
-  labs(x = "Number of Topics)",
-       y = NULL,
-       title = "Model diagnostics by number of topics")
-}
-
-#Create plots
-plot_eval("manuals")
-plot_eval("overview")
-```
-#Vizualization
-```{r extract topic model}
-select_topic_model <- function(origin, n_topic){
-  model <- stm_model %>% 
-    filter(Origin == origin & n_topic == n_topic) %>%
-    pull(Model)
-
-  model <- model[[1]]
-  return(model)
-}
-
-test <- select_topic_model("catalogues", 10)
-
-plot.STM(test, "perspectives", topics = c(1,5))
-```
-#New Documents
-##Align vocabulary
-```{r align vocab}
-#back up current code
-d_text1 <- d_text
-
-#single case: Fasos topics
-fasos_docs <- d_text$catalogues %>%
-  filter(department == "European_studies") %>%
-  select(-department)
-
-fasos_cast <- my_cast_dtm(fasos_docs)
-
-```
-##Fit new docs
-```{r}
-# fitting:
-out <- asSTMCorpus(fasos_cast)
-newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
-fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix
-
-my_names <- names(newdocs$documents)
-
-fasos_theta$theta #nice kind of makes sense
-plot.STM(model, type ="summary")
-
-rownames(fasos_theta$theta) <- my_names
-
-new_courses_theta <- fasos_theta$theta
-
-set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))
-
-new_courses_theta %>%  mutate(Topic = paste("Topic_", rownames))
-```
-#Experiment
-```{r experoment}
-estimateEffect(formula = 1:5 ~department, meta = test$meta)
-
-```

### 2019-04-04 Pillar 2 - Topic Modeling.Rmd
load d_text

@@
 #load
-load("output/data_pillar_2.RDATA")
-
-# keep most recent year
-d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
+#load("output/data_pillar_2.RDATA")
+load("./Output/d_text.RDATA")
 ```
@@
 #Plot
-plot_evaluation("overview")
+plot_evaluation("catalogues")
 plot_evaluation("manuals")

### 2019-04-04 Messy Code/stm single case.Rmd
creates stm model for catalogues

@@
 #load
-load("Output/d_text.RDATA")
+load("/Users/sofia/Documents/DARS/GitDARS/Output/d_text.RDATA")
 ```
@@
 ```
-
+###covariates
 ```{r covariates}
-#get covariates
-covariates <- tribble(
-  ~Origin,    ~Data,
-  "catalogues", d_text$catalogues %>% distinct(`Course ID`, department),
-  "manuals", d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
-)
+catalogues_covariates <- d_text$catalogues %>% distinct(`Course ID`, department)
+manuals_covariates    <- d_text$manuals %>% mutate(department = "UCM") %>% distinct(`Course ID`, department)
 ```
@@
 ```{r as STM corpus, eval = TRUE}
-
-stm_corpus <- d_cast %>% map(asSTMCorpus)
+catalogues_corpus <- asSTMCorpus(d_cast$catalogues)
+manuals_corpus    <- asSTMCorpus(d_cast$manuals)
 
@@
 
-  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
+  STM_model <- stm(corpus$documents, corpus$vocab, data= data, prevalence = ~department, K = n_topics, init.type = "Spectral")
 }
@@
 ####For use:
-```{r models in tibble}
+Catalogues:
+```{r models_catalogues in tibble}
 topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)
@@
   #repeat each topic number twice (once for overview and once for manual)
-  n_topic = rep(topic_numbers, each = 2) ) %>%
+  n_topic = rep(topic_numbers, each = 1) ) %>%
   mutate(
   #Identification information
-  Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
+  Origin     = rep(c("catalogues"), length(topic_numbers)),         
   `Topic ID` = paste(Origin, n_topic, sep = "_"),
-  #DTM
-
   DTM        = pmap(.l = list(Origin), .f = extract_dtm),
-
-  doc_names = map(DTM, rownames),
-  #STM Corpus
-  Corpus           = pmap(.l = list(Origin),   .f = extract_corpus), 
-  #Documents- STM corpus
-  Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
-  #Vocab- STM corpus
-  Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
-  #Data- STM corpus
-  Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
-  #Fit Model
-  Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),
+  Model      = map(n_topic, .f = my_stm, catalogues_corpus, catalogues_covariates),
 
@@
 ```
-####TESTING AND INSPECTING MODELS
-```{r model inspection}
-my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
+
+Manuals_ models do not work:
+```{r models_manuals in tibble}
+topic_numbers <- seq(from = 5, to = 5, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)
+
+stm_model_manuals <- tibble(
+  #repeat each topic number twice (once for overview and once for manual)
+  n_topic = rep(topic_numbers, each = 1) ) %>%
+  mutate(
+  #Identification information
+  Origin     = rep(c("manuals"), length(topic_numbers)),         
+  `Topic ID` = paste(Origin, n_topic, sep = "_"),
+  DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+  Model      = map(n_topic, .f = my_stm, manuals_corpus, manuals_covariates),
+
+  #Evaluation
+  Exclusivity        = map(Model, exclusivity),
+
+  semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
+  #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),
+
+  #
+  ##Inspection
+  #Beta distribution
+  Beta = pmap(.l = list(Model),  .f = tidy),
+
+  #Gamma distribution
+  Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this
+
+  #top words per topic
+  top_terms_topic = map(Beta, .f = get_top_terms_topic),
+
+  #top topics per course
+  top_topic_course = map(Gamma, .f = get_top_topics_course),
+
+  #Select keywords
+  kw = map(Beta, .f = get_kw)
+
+)
 ```
+
+```{r}
+topic_model_manual <- 
+```
+Inspection plots:
+```{r plot STM}
+select_topic_model <- function(origin, K){
+  model <- stm_model %>% 
+    filter(Origin == origin, n_topic == K) %>%
+    pull(Model)
+
+   model <- model[[1]]
+}
+
+test <- select_topic_model("catalogues", 10)
+
+plot.STM(test, "labels", topics = c(6:10))
+
+```
+
 ####For evaluation
@@
 ```
+
+```{r}
+prep <- estimateEffect(1:10 ~ department, test, meta=catalogues_covariates, 
+                       uncertainty="Global")
+plot(prep, covariate="department", topics=c(3, 5, 10), model=test, 
+     method="difference", cov.value1="UCV", cov.value2="UCM",
+     main="Effect of UCV vs. UCM")
+```

### 2019-04-04 Pillar 2 - Topic Modeling.Rmd
Save tests and  eval =TRUE for relevant sections

@@
 We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
+`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $catalogues, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
 
@@
 
-  burnin = 1000,
-  iter   = 15000,
+  burnin = 100,
+  iter   = 2000,
   thin   = 100
@@
 The following functions allow us to inspect the results from our models(inspect distributions and get kw):
-```{r}
+```{r inspection functions, eval = TRUE}
  # get_top_match <- function(d_distribution){
@@
 ```{r LDA fit, cache = TRUE, eval = TRUE}
+topic_numbers <- seq(from = 5, to = 15, by = 5)
 
@@
 
-  #repeat each topic number twice (once for overview and once for manual)
-  n_topic = rep(seq(from = 2, to = 4, by = 1), each = 2) # from = 5, to = 250, by = 5
+  #repeat each topic number twice (once for catalogues and once for manual)
+  n_topic = rep(topic_numbers, each = 2) # from = 5, to = 250, by = 5
 
   ) %>%
-  mutate(Origin     = rep(c("overview", "manuals"), 3),         # should be 50
+  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
          `Topic ID` = paste(Origin, n_topic, sep = "_"),
@@
 
-# test_topic_model
 ```
@@
 We save our tibble with all the information.
-```{r}
+```{r save, eval = T}
+save(test_topic_model, file = "Output/test_topic_model.RDATA" )
 # save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model

### 2019-04-04 Pillar 2 - Topic Modeling.Rmd
adjust number o topics to train

@@
 ```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_numbers <- seq(from = 5, to = 15, by = 5)
+topic_numbers <- seq(from = 4, to = 150, by = 2)
 
@@
   ) %>%
-  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
+  mutate(Origin     = rep(c("catalogues", "manuals"), 74),         # should be 50
          `Topic ID` = paste(Origin, n_topic, sep = "_"),

### 2019-04-12 Pillar_2_-_Topic_Modeling.Rmd
UM Computer results

--- 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
@@
 
-COMMENTS: 
-Q. Jerry -> For preprocessing (selecting vocabulary), how do we assign words that appear in only one document to a topic? Does it make sense to remove them?
-
-```{r setup, include = T}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
+                      eval = FALSE)
 ```
 
-```{r library, message = F}
+#Setup
+##Libraries
+```{r library, message = FALSE, eval = TRUE}
 library(tidyverse)
@@
 library(ggthemes)
-library(rlang)
+library(rlang) #quote
 library(ldatuning) # ideal number of topics in LDA
+
 ```
 
-```{r function reorder_within & co., echo = FALSE}
+##Functions for internal faceting
+```{r function reorder_within & co., echo = FALSE, eval = TRUE}
 
@@
 
-# Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
-```{r import data}
-load("output/data_pillar_2.RDATA")
+##Loading data
+We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
+`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $catalogues, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
 
-# Only keep course descriptions and overviews from most recent year
-d_description <- d_description %>%
-  filter(
-    `Academic Year` == "2018-2019"
-  )
-
-d_overview <- d_overview %>%
-  filter(
-    `Academic Year` == "2018-2019"
-  )
+For `d_text` we keep only the most recent year.
+```{r import data, eval = TRUE}
+#load
+#load("output/data_pillar_2.RDATA")
+load("./Output/d_text.RDATA")
 ```
@@
       )
-
 }
 
-tf_idf_description <- compute_tf_idf(d_description)
-tf_idf_overview    <- compute_tf_idf(d_overview)
-tf_idf_manual      <- compute_tf_idf(d_manual)
+#
+##Application
+tf_idf <- map(d_text, .f = compute_tf_idf)
 
+#
+##Clean workspace
 rm(compute_tf_idf)
@@
 # LDA
-
-```{r my_cast_tdm}
-my_cast_tdm <- function(data, level) data %>%
+##Setup
+###Cast DTM
+The function `my_cast_dtm` casts our dataframes into a DTM.
+```{r my_cast_dtm, eval = TRUE}
+my_cast_dtm <- function(data) data %>%
   count(`Course ID`, word) %>%
@@
 
-d_description_cast <- my_cast_tdm(d_description)
-d_overview_cast <- my_cast_tdm(d_overview)
-d_manual_cast <- my_cast_tdm(d_manual)
+d_cast <- d_text %>% map(my_cast_dtm)
 
-rm(my_cast_tdm)
+rm(my_cast_dtm)
 ```
-
-## Ideal Number of Topics (RUN ON UM COMPUTER)
-
-```{r controls}
+###Controls
+The control parameters we use are:
+```{r controls, eval = TRUE}
 my_control <- list(
 
-  nstart = 10,
-  seed   = 1 : 10,
+  nstart = 20,
+  seed   = 1 : 20,
   best   = TRUE,
 
-  burnin = 500,
+  burnin = 100,
   iter   = 2000,
@@
 ```
+The control parameters we use for fast testing are:
+```{r fast control}
+my_control_fast <- list(
 
+  nstart = 1,
+  seed   = 1,
+  best   = TRUE,
+
+  burnin = 5,
+  iter   = 10,
+  thin   = 2
+
+)
+```
+
+##Ideal Number of Topics Package Test
+To decide the number of topics to discover, we run three different tests.
+###Function
+The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
 ```{r function my_FindTopicsNumber }
@@
 ```
-
-```{r description topics, cache = TRUE}
+###Train
+```{r package test on topics, cache = TRUE}
+#Start timer
 start.time <- Sys.time()
 
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
+#
+##apply my_FindTopicsNumber
+result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))
 
+#Stop timer
 end.time <- Sys.time()
-time.taken <- end.time - start.time
+print(end.time - start.time)
 
-save(result_description,
-     file = "Output/LDA_ntopics_description.RDATA")
+#
+##Save results
+#save(result_topic_test,
+#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
+```
+Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
+* Overview:     22min 
+* Description:  11min 
+* Manuals:      5.5hrs
 
-print(time.taken)
+###Graph 
+We examine the result of the experiment by plotting them on a graph.
+```{r LDA number topics plot}
+#load("Output/LDA_ntopics.RDATA")
+
+result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
 ```
+From the results we see that the ideal number of topics is somewhere between 35 and 40.
 
-```{r overview topics, cache = TRUE}
-start.time <- Sys.time()
+## Fitting Model
+The function `my_LDA` fits an LDA model on the DTM using the previous controls.
+```{r my_LDA, eval= TRUE}
+my_LDA <- function(n_topics, corpus, control = my_control){
 
-result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_overview ,
-     file = "Output/LDA_ntopics_overview.RDATA")
-
-print(time.taken)
-```
-
-```{r manual topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_manual,
-     file = "Output/LDA_ntopics_manual.RDATA")
-
-print(time.taken)
-```
-
-from 20, to 40, by 5 topics takes
-22min for overview
-11min for description
-5.5hrs for manuals
-
-```{r LDA number topics plot}
-
-load("Output/LDA_ntopics_description.RDATA")
-
-load("Output/LDA_ntopics_overview.RDATA")
-
-load("Output/LDA_ntopics_manual.RDATA")
-
-result_description %>%
-  select(-Griffiths2004) %>%
-  FindTopicsNumber_plot
-
-result_overview %>%
-  select(-Griffiths2004) %>%
-  FindTopicsNumber_plot
-
-result_manual %>%
-  select(-Griffiths2004) %>%
-  FindTopicsNumber_plot
+  LDA_model <- LDA(
+    x       = corpus,
+    k       = n_topics,
+    method  = "Gibbs",
+    control = control
+    )
+}
 
@@
 
-## Fitting Model
+###Functions for models (extract_dtm, get_distributions, perplexity)
+The following functions are used as input in a map to compute and evaluate topic models. 
+```{r getting gamma and beta, eval = TRUE}
+#extract dtm
+extract_dtm <- function(origin) d_cast[[origin]]
 
-```{r LDA fit, cache = TRUE}
-n_topics <- 5
-levels   <- c("description", "overview", "manual")
-list_nam <- character(0)
+#extract Distributions (Gamma/Beta)
+get_distributions <- function(model, distrib_str){ #input gamma or beta
+  tidy(model, matrix = distrib_str)        %>%
+    mutate(topic = paste("Topic", topic) ) %>%
+      arrange(topic, desc(!!sym(distrib_str)))
+}
 
-for(level in levels){
+#perplexity Function
+my_perplexity <- function(model, dtm){
+  perplexity(model, dtm, estimate_theta = FALSE)
+}
 
-  dataset   <- get(paste("d", level, "cast", sep = "_"))
+```
 
-  LDA_model <- LDA(
-    x       = dataset,
-    k       = n_topics,
-    method  = "Gibbs",
-    control = list(
-      nstart  = 10,
-      seed    = c(1:10),
-      best    = TRUE,
+The following functions allow us to inspect the results from our models(inspect distributions and get kw):
+```{r inspection functions, eval = TRUE}
+ # get_top_match <- function(d_distribution){
+ # 
+ #  #save user input as string
+ #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
+ #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
+ # 
+ #  #Compute Case (Beta or Gamma, respectively)
+ #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
+ #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
+ #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
+ # 
+ #  #
+ #  ## DATA
+ #  data.frame(d_distribution) %>%
+ #    group_by(!!sym(grouping)) %>%
+ #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
+ #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
+ #    group_by(!!sym(grouping)) %>%
+ #    summarise(top = list(!!sym(objects_to_group)))
+ # }
 
-      burnin  = 4000,
-      iter    = 5000,
-      thin    = 500,
-
-      verbose = 1e3,
-      save    = 1e3,
-      keep    = 1e3)
-    )
-
-  nam <- paste("LDA", level, n_topics, sep = "_")
-
-  assign(
-    x     = nam,
-    value = LDA_model
-  )
-
-  list_nam <- c(list_nam, nam)
+get_top_terms_topic <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(10, beta) %>%
+    select(topic, term) %>%
+    group_by(topic) %>%
+    summarise(top_words = list(term))
 
@@
 
-save(list = list_nam,
-     file = "LDA.RDATA")
+get_top_topics_course <- function(d_gamma){
+  data.frame(d_gamma) %>%
+    group_by(document) %>%
+    top_n(5, gamma) %>%
+    select(document, topic) %>%
+    summarise(top_topic = list(topic))
+}
+
+get_kw <- function(d_beta){
+  data.frame(d_beta) %>%
+    group_by(topic) %>%
+    top_n(3, beta) %>%
+    ungroup()%>%
+    pull(term)%>%
+    unique()
+}
+
+```
+###Training Models
+We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
+```{r LDA fit, cache = TRUE, eval = TRUE}
+topic_numbers <- seq(from = 4, to = 150, by = 2)
+
+test_topic_model <- tibble( #CHANGE NAME TO: topic_model
+
+  #repeat each topic number twice (once for catalogues and once for manual)
+  n_topic = rep(topic_numbers, each = 2) # from = 5, to = 250, by = 5
+
+  ) %>%
+  mutate(Origin     = rep(c("catalogues", "manuals"), 74),         # should be 50
+         `Topic ID` = paste(Origin, n_topic, sep = "_"),
+
+         #Document Term Matrix
+         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+
+         #Fit Model
+         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control
+
+         #Gamma distribution
+         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+
+         #Beta distribution
+         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
+
+         #Perplexity
+         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
+
+         #Loglikelihood
+         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
+
+         #
+         ##Inspect
+
+         #top words per topic
+         top_terms_topic = map(Beta, .f = get_top_terms_topic),
+
+         #top topics per course
+         top_topic_course = map(Gamma, .f = get_top_topics_course),
+
+         #Select keywords
+         kw = map(Beta, .f = get_kw)
+         )
+
+# Clean workspace
+
+# rm(extract_dtm, get_distributions, my_perplexity,
+#    get_top_terms_topic, get_top_topics_course, get_kw)
+
 ```
 
-## Visualization
+##Plots - Model Evaluation
+To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
+```{r perplexity plots, eval = TRUE}
+#Function
+plot_evaluation <- function(origin){
+
+  #data
+  test_topic_model %>%
+
+    #Wrangling
+    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
+    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
+    filter(Origin == origin) %>%
+
+    #Graphics
+    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
+    geom_point() +
+    geom_line() +
+    facet_grid(rows = vars(`Eval Type`), scales = "free") +
+    theme_minimal()
+
+}
+
+#Plot
+plot_evaluation("catalogues")
+plot_evaluation("manuals")
+```
+
+##Saving model_data:
+We save our tibble with all the information.
+```{r save, eval = T}
+save(test_topic_model, file = "Output/test_topic_model.RDATA" )
+# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
+```
+
+#App
+For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
+##Distributions and Key words
+The function `clean_kw` removes stopwords from our key words.
+```{r function clean key words}
+clean_kw <- function(kw_list){
+
+  #stopwords
+  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
+                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
+                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
+                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")
+
+  #remove stopwords
+  kw <- setdiff(kw_list, kw_stopwords)
+  #return
+  return(kw[!is.na(kw)])
+
+}
+
+```
+On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
+```{r crop and clean TM for App}
+app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
+  mutate(kw = map(kw, .f = clean_kw))
+```
+
+##Convenience Vectors
+For the app we also need to have a list of all courses and an example of a prospective semester
+```{r for convenience}
+# set seed
+set.seed(1)
+
+#
+## All courses
+course_all <- d_course %>%
+  inner_join(
+    d_transcript,
+    by = "Course ID"
+  ) %>%
+  distinct(
+    `Course ID`
+  ) %>%
+  # remove semester abroad, skills and projects
+  filter(
+    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
+  ) %>%
+  pull
+
+#
+##courses following_semester
+course_following_semester <- sample(
+  x       = course_all,
+  size    = 60,
+  replace = FALSE
+  ) %>% sort
+
+```
+
+```{r adding convenience vectors}
+app_topic_model <- app_topic_model %>%
+  mutate(`All Courses`     = course_all,
+         `Sample semester` = course_following_semester)
+
+#rm(course_all, course_following_semester)
+```
+## Saving files for APP
+```{r app files}
+# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
+```
+# Visualization
 ### Functions 
+This part is adapted 
 ```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(results){
+prepare_data_LDA_beta <- function(d_beta){
 
-  tidy(results, matrix = "beta") %>%
+  data.frame(d_beta) %>%
     mutate(topic = paste("Topic", topic)) %>%
@@
 # Bet Distribution
-LDA_description_120 %>% prepare_data_LDA_beta
+test <- list()
+
+a <-  names(distribution)[1]
+test[[a]] <- lapply(distribution[[a]],
+                      prepare_data_LDA_beta)
 
 # Gamma Distribution
-LDA_description_120 %>% prepare_data_LDA_gamma(level = Cluster)
+b <- names(distribution)[2]
+test[[b]] <- lapply(distribution[[b]],
+                    prepare_data_LDA_gamma)
+
+test <- test_topic_model %>%
+  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
+         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
+         )
+test[["preparedBeta"]]
+rm(a,b #,test
+   )
 ```
-
+This part is not adapted
 ```{r LDA visualize, eval = F}

### 2019-04-12 App/Recommender System/server.R
Changes aesthetics app

@@ -98,7 +98,7 @@ function(input, output, session) {
   
   #
   ##Red Flags
-  output$red_flags <- renderUI({
+  output$red_flags <- renderTable({
     #student
     student <- current_student()
     
@@ -115,27 +115,46 @@ function(input, output, session) {
         ) %>%
       
       # provide explanation
-      mutate(
-        explanation = paste(
-          "Red flag for ",
-          rhs_course,
-          ":<br/>",
-          "You have not taken ",
-          lhs_course,
-          " and ",
-          round(confidence * 100, digits = 1),
-          "% of the ",
-          lhs.rhsTake.count,
-          " students who have taken ", 
-          rhs_course,
-          " without first taking ",
-          lhs_course,
-          " obtained less than 6.5/10 in  ",
-          rhs_course,
-          ".",
-          sep = ""
-        )
+      # mutate(
+      #   explanation = paste(
+      #     "Red flag for ",
+      #     rhs_course,
+      #     ":<br/>",
+      #     "You have not taken ",
+      #     lhs_course,
+      #     " and ",
+      #     round(confidence * 100, digits = 1),
+      #     "% of the ",
+      #     lhs.rhsTake.count,
+      #     " students who have taken ", 
+      #     rhs_course,
+      #     " without first taking ",
+      #     lhs_course,
+      #     " obtained less than 6.5/10 in  ",
+      #     rhs_course,
+      #     ".",
+      #     sep = ""
+      #   )
+      # )
+    mutate(
+      `Red Flag` = rhs_course,
+      Reason = paste(
+        "You have not taken ",
+        lhs_course,
+        " and ",
+        round(confidence * 100, digits = 1),
+        "% of the ",
+        lhs.rhsTake.count,
+        " students who have taken ", 
+        rhs_course,
+        " without first taking ",
+        lhs_course,
+        " obtained less than 6.5/10 in  ",
+        rhs_course,
+        ".",
+        sep = ""
       )
+    )
     
     
     # rules low
@@ -146,27 +165,46 @@ function(input, output, session) {
         rhs_course %in% input$course_chosen
         ) %>%
       
-      mutate(
-        explanation = paste(
-          "Red flag for ",
-          rhs_course,
-          ":<br/>",
-          "You obtained less than 6.5/10 in ",
-          lhs_course,
-          " and ",
-          round(confidence * 100, digits = 1),
-          "% of the ",
-          lhs.rhsTake.count,
-          " students who have taken ", 
[…]

### 2019-04-12 App/Recommender System/ui.R

@@ -5,7 +5,9 @@
 # libraries
 library(tidyverse)
 library(tidytext)
+
 library(shiny)
+library(shinythemes)
 
 #load("rules.RDATA")
 load("data_pillar_1.RDATA")
@@ -21,6 +23,7 @@ load("rules_clean.RDATA")
 #
 # ui
 navbarPage(
+  theme = shinytheme("united"),
   
   # App title
   title = "Recommender System",
@@ -62,7 +65,7 @@ navbarPage(
       mainPanel(
         
         # Output: dataset
-        htmlOutput(
+        tableOutput(
           outputId = "red_flags"
           )
         
@@ -76,6 +79,7 @@ navbarPage(
     
     # Panel Title
     title = "Course Recommender",
+    
     
     # Sidebar layout
     sidebarLayout(
@@ -119,17 +123,13 @@ navbarPage(
       
       # Main panel for displaying outputs
       mainPanel(
-        
-        # Output: dataset
-        htmlOutput(
-          outputId = "course_recommendation"
-          ),
-        tags$head(tags$style("#course_recommendation{color: black;
-                                 font-size: 20px;
-                                 }"
-        )
-        )
-        
+        h3("Course Recommendations"),
+        mainPanel( width = 12,
+          tableOutput(outputId = "course_recommendation"), 
+          tags$head(tags$style("#course_recommendation{color: black; font-size: 20px;}")
+                    )
+                  )
+      
         )
       
       )

### 2019-04-12 Pillar_2_-_Topic_Modeling.Rmd
changes to Topic Models

@@
 
-  nstart = 20,
-  seed   = 1 : 20,
+  nstart = 10,
+  seed   = 1 : 10,
   best   = TRUE,
@@
 ```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_numbers <- seq(from = 4, to = 150, by = 2)
+initial_time <- Sys.time()
+topic_numbers <- seq(from = 4, to = 8, by = 2)
 
@@
   ) %>%
-  mutate(Origin     = rep(c("catalogues", "manuals"), 74),         # should be 50
+  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
          `Topic ID` = paste(Origin, n_topic, sep = "_"),
@@
 
+final_time <- Sys.time()
+took_how_long <- final_time - initial_time
 # Clean workspace
@@
 
+```{r print how long it takes}
+(took_how_long)
+```
 ##Plots - Model Evaluation

### 2019-04-12 Pillar 2 - Topic Modeling.Rmd
use my_control instead of my_control_fast
minor change: control seed change number

--- 2019-04-04 Pillar 2 - Topic Modeling.Rmd
@@
 
-  nstart = 10,
-  seed   = 1 : 10,
+  nstart = 20,
+  seed   = 1 : 20,
   best   = TRUE,
@@
 ```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_numbers <- seq(from = 5, to = 15, by = 5)
+initial_time <- Sys.time()
+topic_numbers <- seq(from = 4, to = 8, by = 2)
 
@@
   ) %>%
-  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
+  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
          `Topic ID` = paste(Origin, n_topic, sep = "_"),
@@
          #Fit Model
-         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control
+         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control
 

### 2019-04-12 Messy Code/Pillar 2 -(STM) Topic Modeling- Errors.Rmd

--- 2019-04-02 Pillar 2 -(STM) Topic Modeling.Rmd
@@
 ```
-###As corpus
-```{r}
 
-```
 # TF-IDF
@@
 
-  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
+  STM_model <- stm(corpus$documents, corpus$vocab, data = data, prevalence = ~department, ### ~department
+                   K = n_topics, init.type = "Spectral")
 }
@@
 extract_data     <- function(corpus) corpus$data
+
+#Extract covariates
+extract_covariates <- function(origin) covariates %>% filter(Origin == origin) %>% pull(Data)
 
@@
 
-stm_model <- tibble(
+stm_model 
+preparation_for_model <- tibble(
   #repeat each topic number twice (once for overview and once for manual)
   n_topic = rep(topic_numbers, each = 2) ) %>%
+
   mutate(
@@
     Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
-  `Topic ID` = paste(Origin, n_topic, sep = "_"),
+    `Topic ID` = paste(Origin, n_topic, sep = "_")) %>%
+
+  #left_join(covariates, by = "Origin") %>%
+
+  mutate(
     #DTM
+    DTM       = pmap(.l = list(Origin), .f = extract_dtm),
+    doc_names = map(DTM, rownames),
 
-  DTM       = pmap(.l = list(Origin), .f = extract_dtm),
-
-  doc_names = map(DTM, rownames),
     #STM Corpus
@@
     #Documents- STM corpus
-  Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
+    #Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
     #Vocab- STM corpus
-  Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
+    #Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
     #Data- STM corpus
-  Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
-  #Fit Model
-  Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),
+    #Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
+    #Covariates
+    Covariates        = pmap(.l = list(Origin),  .f = extract_covariates), # testing_model$Covariates[4][[1]][[1]]
+
+    #clean_covariates
+    clean_covariates = map(Covariates, .f = function(Covariates) Covariates[[1]]))
+
+#iteration
+this_model <- preparation_for_model %>% filter(n_topic==5, Origin=="manuals")
+
+this_n_topic <- this_model$n_topic[[1]]
+this_corpus <- this_model$Corpus[[1]]
+this_clean_covariates <- this_model$clean_covariates[[1]]
+
+this_model <- my_stm(this_n_topic, this_corpus, this_clean_covariates)
+
+    #Fit Model  n_topics, corpus, data
+    Model  = pmap(.l = list(n_topics = n_topic, corpus = Corpus, data = clean_covariates), 
+                  .f = my_stm))
 
@@
     Exclusivity        = map(Model, exclusivity),
-
     semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
@@
     ##Inspection
+
     #Beta distribution
     Beta = pmap(.l = list(Model),  .f = tidy),
-
     #Gamma distribution
@@
 
+    #END MUTATE PARENTHESIS
          )
@@
 ```
-####TESTING AND INSPECTING MODELS
-```{r model inspection}
-my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
-```
+
 ####For evaluation

### 2019-04-12 Messy Code/stm single case.Rmd

@@
 #load
-load("/Users/sofia/Documents/DARS/GitDARS/Output/d_text.RDATA")
+load("./Output/d_text.RDATA")
 ```
@@
   STM_model <- stm(corpus$documents, corpus$vocab, data= data, prevalence = ~department, K = n_topics, init.type = "Spectral")
+}
+```
+###mystm_manuals
+```{r my_STM, eval= TRUE}
+my_stm_manuals <- function(n_topics){
+
+  STM_model <- stm(manuals_corpus$documents, manuals_corpus$vocab, data = manuals_covariates, prevalence = ~department, K = n_topics, init.type = "Spectral")
 }
@@
 Manuals_ models do not work:
-```{r models_manuals in tibble}
-topic_numbers <- seq(from = 5, to = 5, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)
+```{r models_manuals in tibble, error=TRUE}
+topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)
 
-stm_model_manuals <- tibble(
-  #repeat each topic number twice (once for overview and once for manual)
-  n_topic = rep(topic_numbers, each = 1) ) %>%
-  mutate(
-  #Identification information
-  Origin     = rep(c("manuals"), length(topic_numbers)),         
-  `Topic ID` = paste(Origin, n_topic, sep = "_"),
-  DTM        = pmap(.l = list(Origin), .f = extract_dtm),
-  Model      = map(n_topic, .f = my_stm, manuals_corpus, manuals_covariates),
+model_tmp_result <- vector("list", length(topic_numbers))
 
-  #Evaluation
-  Exclusivity        = map(Model, exclusivity),
+for(i in seq_along(topic_numbers)){
+  k <- topic_numbers[[i]]
+  model_tmp_result[[i]] <- stm(documents = manuals_corpus$documents, 
+                               vocab = manuals_corpus$vocab, 
+                               K = k, 
+                               #data = manuals_covariates, 
+                               #prevalence = ~department, 
+                               init.type = "Spectral"
+                               )
+}
+stm_model_manuals <- many_models(
+  K = 5:10,
+  documents = manuals_corpus$documents,
+  vocab= manuals_corpus$vocab,
+  prevalence = ~ department, 
+  data = manuals_covariates,
+  runs = 5
+)
 
-  semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
-  #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),
-
-  #
-  ##Inspection
-  #Beta distribution
-  Beta = pmap(.l = list(Model),  .f = tidy),
-
-  #Gamma distribution
-  Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this
-
-  #top words per topic
-  top_terms_topic = map(Beta, .f = get_top_terms_topic),
-
-  #top topics per course
-  top_topic_course = map(Gamma, .f = get_top_topics_course),
-
-  #Select keywords
-  kw = map(Beta, .f = get_kw)
-
-)
 ```
@@
     filter(Origin == origin, n_topic == K) %>%
-    pull(Model)
-
-   model <- model[[1]]
+    pull(Model) %>%
+    .[[1]]
 }

### 2019-04-12 Pillar 2 - Tmp Topic Modeling.Rmd

---
title: "Pillar 2- Quick Topic Models"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
                      eval = FALSE)
```

#Setup
##Libraries
```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

```
##Loading data
We load a list `d_text` with two tibbles of textual data for catalogues and manuals. That is, for $catalogues and $manuals we have a tibble with the following columns: `Course ID`, `year`, `word_original`, `word`.

We also load the environment `Output/data_pillar_2.RDATA` containing the data sets`d_course` and `d_transcript` that we will need to prepare some imputs for our App.

```{r import data, eval = TRUE}
#load
load("./Output/d_text.RDATA")
load("./Output/data_pillar_2.RDATA") #used for app

```

###Functions for internal faceting
We create the functions for internal faceting taken from https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

# Function for ordering within facet:
# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R

reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

# LDA
In this section, we train several LDA models on our data and evaluate these to keep the best topic model for the course content data we have. We will do the model training and evaluation measures in one go using mapping functions on a tibble containing all pertinent data. In this way we ensure that we maintain the order of all the information we gather on our models.

In order to do this, we have to create all our functions before hand, to apply them in a chain later. Moreover, we will need to create a document-term matrix (DTM) for the catalogues and manuals which we will use in several steps to create and evaluate the model. Thus, we will create the DTM in a separate step as part of the set up.

###Cast DTM
The function `my_cast_dtm` casts each of our dataframes (catalogues and manuals) into a DTM.
```{r my_cast_dtm, eval = TRUE}
#
##Function-----------------------------------------------
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

#
##Application-----------------------------------------------
d_cast <- d_text %>% map(my_cast_dtm)

#
##Clean workspace-----------------------------------------------
rm(my_cast_dtm)

```
###Controls
The control parameters we will use to train our LDA model are:
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 10,
  seed   = 1 : 10, #must have length nstart
  best   = TRUE,

  burnin = 100,
  iter   = 2000,
  thin   = 2000

)
```
We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
```{r fast control}
my_control_fast <- list(

  nstart = 1,
  seed   = 1,
  best   = TRUE,

  burnin = 5,
  iter   = 10,
  thin   = 2

)
```

## Fitting Model
The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}
my_LDA <- function(n_topics, corpus, control = my_control){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = control
    )
}

```

###Extracting functions
The following functions are used as input in a map to compute and evaluate topic models. 
```{r getting gamma and beta, eval = TRUE}
#Extract DTM-----------------------------------------------
extract_dtm <- function(origin) d_cast[[origin]]

#Extract Distributions (Gamma/Beta)-----------------------------------------------
get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function-----------------------------------------------
my_perplexity <- function(model, dtm){
  perplexity(model, dtm, estimate_theta = FALSE)
}

```

###Inspection functions
The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r inspection functions, eval = TRUE}

get_top_terms_topic <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    select(topic, term) %>%
    group_by(topic) %>%
    summarise(top_words = list(term))

}

get_top_topics_course <- function(d_gamma){
  data.frame(d_gamma) %>%
    group_by(document) %>%
    top_n(5, gamma) %>%
    select(document, topic) %>%
    summarise(top_topic = list(topic))
}

get_kw <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(3, beta) %>%
    ungroup()%>%
    pull(term)%>%
    unique()
}

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models in a tibble under the name `tb_topic_model`, along with the DTM used to build the model, the corpus of origin (catalogue or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words we will use in the app.
This step takes some time, thus we also measure how long it takes to train the model.
```{r LDA fit, cache = TRUE, eval = FALSE}
#Timing_____________________________________________________________________
initial_time <- Sys.time()

#Training model______________________________________________________________
topic_numbers <-c(10, 25, 30, 35, 40, 45, 50, 55, 60) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50

tb_topic_model <- tibble(

  #repeat each topic number twice (once for catalogues and once for manual)
  n_topic = rep(topic_numbers, each = length(d_text))

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm),

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control

         #Gamma distribution
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),

         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data

         #
         ##Inspect

         #top words per topic
         top_terms_topic = map(Beta, .f = get_top_terms_topic),

         #top topics per course
         top_topic_course = map(Gamma, .f = get_top_topics_course),

         #Select keywords
         kw = map(Beta, .f = get_kw)
         )

#Timing______________________________________________________________
final_time <- Sys.time()
took_how_long <- final_time - initial_time

#View tibble______________________________________________________________
tb_topic_model

#Saving______________________________________________________________
#save(tb_topic_model, "tmp_topic_model_tibble.RDATA")#DOESNT WORK

# Clean workspace
# rm(extract_dtm, get_distributions, my_perplexity,
#    get_top_terms_topic, get_top_topics_course, get_kw)

```
###Training Models separately
For time constrains, we sometimes need to train the model only on the manuals or the catalogues, for this we add an extra filtering step in the code that filters on `which_texts`.
```{r LDA fit, cache = TRUE, eval = TRUE}
#Timing
initial_time <- Sys.time()

#Training
topic_numbers <-c(10, 25, 30, 35, 40, 45, 50, 55, 60) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
which_texts <- "catalogues"

tb_topic_model <- tibble(

  #repeat each topic number twice (once for catalogues and once for manual)
  n_topic = rep(topic_numbers, each = length(d_text))

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

         #Document Term Matrix
         DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%
  filter(Origin == which_texts) %>%
  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control

         #Gamma distribution
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),

         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data

         #
         ##Inspect

         #top words per topic
         top_terms_topic = map(Beta, .f = get_top_terms_topic),

         #top topics per course
         top_topic_course = map(Gamma, .f = get_top_topics_course),

         #Select keywords
         kw = map(Beta, .f = get_kw)
         )

#Timing
final_time <- Sys.time()
took_how_long <- final_time - initial_time

#View
#tb_topic_model

#Save
save(tb_topic_model, file = paste("./Output/", which_texts, "tmp_topic_model_tibble.RDATA", sep = "_"))

```

##Plots - Model Evaluation
To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

  #data
  tb_topic_model %>%

    #Wrangling
    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
    filter(Origin == origin) %>%

    #Graphics
    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(`Eval Type`), scales = "free") +
    theme_minimal()

}

#Plot
plot_evaluation("catalogues")
plot_evaluation("manuals")
```
##Different alphas and delta (prior of term distributions over topics)
To evaluate the impact of the initial alpha and beta on our model, we train the model using different inizialization values for alpha and delta. Note that this is only an inizialisation and the algorithm will try to extimate alpha and beta.
###Alpha
```{r alpha and beta}
sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS

fit_lda_alpha <-  function(alpha) {
  control = list(
        nstart = 10,
        seed   = 1:10,
        best   = TRUE,
        burnin = 5,
        iter   = 200, #2000
        thin   = 200, #2000
       alpha = alpha)

  topicmodels::LDA(x = sample_dtm, k = 50, method = "Gibbs", control = control)

}
# test
fit_lda(0.1)
#Evaluation
tm_eval_alpha <- tibble( alpha = seq(from = 0.001, to = 2, length = 20)) %>%
  mutate(Model = map(alpha, .f =fit_lda_alpha),
         DTM = list((testing_dtm)),
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik))
```
#Beta
```{r alpha and beta}

fit_lda_delta <-  function(delta) {
  control = list(
        nstart = 10,
        seed   = 1:10,
        best   = TRUE,
        burnin = 5,
        iter   = 200, #2000
        thin   = 200, #2000
        delta  = delta)

  topicmodels::LDA(x = sample_dtm, k = 50, method = "Gibbs", control = control)

}
# test
fit_lda_delta(0.1)

#Evaluation
tm_eval_delta <- tibble( delta = seq(from = 0.001, to = 2, length = 20)) %>%
  mutate(Model = map(delta, .f =fit_lda_delta),
         DTM = list((testing_dtm)),
         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),

         #Beta distribution
         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
         #Perplexity
         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),

         #Loglikelihood
         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik))
```

##Saving model_data:
We save the data from our intermediate step in case further analysis is needed.
```{r save, eval = T}
#save(tb_topic_model, file = "Output/tb_topic_model.RDATA" )
```

#App
For our Recommender System, we need to pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words}
clean_kw <- function(kw_list){

  #stopwords
  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")

  #remove stopwords
  kw <- setdiff(kw_list, kw_stopwords)
  #return
  return(kw[!is.na(kw)])

}

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App}
app_topic_model <- tb_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience}
# set seed
set.seed(1)

#
## All courses
course_all <- d_course %>%
  inner_join(
    d_transcript,
    by = "Course ID"
  ) %>%
  distinct(
    `Course ID`
  ) %>%
  # remove semester abroad, skills and projects
  filter(
    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
  ) %>%
  pull

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort

```

```{r adding convenience vectors}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = list(course_all),
         `Sample semester` = list(course_following_semester))

#rm(course_all, course_following_semester)
```
## Saving files for APP
We save all requirements for the app.
```{r app files}
# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```

### 2019-04-12 Data Preparation - Course Catalogues.Rmd
identify list of courses currently offered
fixes bug in UCV

@@
 
-remove_header_UCV <- function(string) string %>% str_sub(29, -1)
+remove_header_UCV <- function(string) string %>% str_sub(28, -1)
 
 overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
-overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\r\n *Maastricht Science Programme")
+overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme")
 

### 2019-04-12 Pillar 1 - Topic Profile.Rmd

--- 2019-03-25 Pillar 1 - Topic Profile.Rmd
@@
 
+__Considerations__:
+
+* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.
+* give more weight to 3000-level courses
+
+* consider following predictors:
+     * GPA (per concentration)
+
 ```{r setup, include = FALSE}
@@
 
+library(magrittr)
+library(glmnet)
+library(leaps)
 library(tidyverse)
-library(magrittr)
 ```
 
-```{r}
+```{r load}
 load("App/Recommender System/topic_model_gb.RDATA")
@@
 load("Output/d_transcript_cum.RDATA")
+load("Output/course_current.RDATA")
 
-topic_model_gb
+course_target <- course_current[! str_detect(course_current, "...10..")] 
+course_target <- setdiff(course_target, "CAP3000") # exclude capstone
+course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
 ```
 
-```{r}
-gamma <- topic_model_gb$g_overview[[10]] %>% spread(topic, gamma)
+# Course topic profile
+```{r gamma_spread}
+gamma        <- topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
+gamma_spread <- gamma %>% spread(topic, gamma)
+
+beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
+View(beta)
 ```
 
-```{r}
-student_TP <- d_transcript_informative %>%
+# Student topic profile
+```{r student_TP}
+student_TP <- d_transcript_augmented %>%
 
-  left_join(gamma, by = c("Course ID" = "document")) %>%
-  filter(!is.na(`Topic 1`)) %>%
+  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
 
+  mutate_at(vars(matches("Topic")), .funs = funs(if_else(is.na(.), 0, .))) %>% # give a value of 0 to the topics of the courses missing from the topic model.
   mutate_at(vars(matches("Topic")), .funs = funs(Grade/10 * .)) %>% # weigh by grade
@@
 
-  mutate_at(vars(matches("Topic")), lag) %>%
-  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>%
-  mutate_at(vars(matches("Topic")), cumsum) # topic profile at beginning of period
+  mutate_at(vars(matches("Topic")), lag, default = 0) %>%
+  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile at beginning of period
+
+  ungroup %>%
+
+  arrange(`Student ID`)
+```
+
+Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).
+
+# Student GPA
+
+```{r}
+d_transcript_augmented <- d_transcript_augmented %>%
+
+  mutate(is_HUM = `Course ID` %>% str_detect("HUM|SAH"),
+         is_SCI = `Course ID` %>% str_detect("SCI|SAS"),
+         is_SSC = `Course ID` %>% str_detect("SSC|SAC"),
+         is_COR = `Course ID` %>% str_detect("COR"),
+         is_SKI = `Course ID` %>% str_detect("SKI|LAN"),
+         is_PRO = `Course ID` %>% str_detect("PRO|UGR|CAP")) %>%
+
+  mutate(grade_HUM = if_else(is_HUM, Grade, NA_real_),
+         grade_SCI = if_else(is_SCI, Grade, NA_real_),
+         grade_SSC = if_else(is_SSC, Grade, NA_real_),
+         grade_COR = if_else(is_COR, Grade, NA_real_),
+         grade_SKI = if_else(is_SKI, Grade, NA_real_),
+         grade_PRO = if_else(is_PRO, Grade, NA_real_)) %>%
+
+  mutate(ECTS = case_when(
+    `Course ID` %>% str_detect("HUM|SCI|SSC|COR|PRO|SA|EXT") ~ 5  ,
+    `Course ID` %>% str_detect("SKI|LAN"                   ) ~ 2.5,
+    `Course ID` %>% str_detect("CAP|UGR"                   ) ~ 10 ,
+    TRUE                                                     ~ 5  )
+    ) %>%
+
+  mutate(ECTS_HUM = if_else(is_HUM, ECTS, NA_real_),
+         ECTS_SCI = if_else(is_SCI, ECTS, NA_real_),
+         ECTS_SSC = if_else(is_SSC, ECTS, NA_real_),
+         ECTS_COR = if_else(is_COR, ECTS, NA_real_),
+         ECTS_SKI = if_else(is_SKI, ECTS, NA_real_),
+         ECTS_PRO = if_else(is_PRO, ECTS, NA_real_)) %>%
+
+  mutate(grade_ECTS     = Grade     * ECTS,
+         grade_ECTS_HUM = grade_HUM * ECTS_HUM,
+         grade_ECTS_SCI = grade_SCI * ECTS_SCI,
+         grade_ECTS_SSC = grade_SSC * ECTS_SSC,
+         grade_ECTS_COR = grade_COR * ECTS_COR,
+         grade_ECTS_SKI = grade_SKI * ECTS_SKI,
+         grade_ECTS_PRO = grade_PRO * ECTS_PRO)
 ```
@@
 ```{r}
-d_transcript_cum %>%
+student_GPA <- d_transcript_augmented %>%
 
-  right_join(student_TP, by = c("sequenceID" = "Student ID", "eventID" = "time"))
+  group_by(`Student ID`, time) %>%
+  summarize_at(vars(matches("ECTS")), list) %>%
+
+  group_by(`Student ID`) %>%
+  arrange(time) %>%
+
+  mutate_at(vars(matches("ECTS")), purrr::accumulate, c) %>%
+
+  mutate_at(vars(matches("ECTS")), map_dbl, sum, na.rm = TRUE) %>%
+
+  mutate(GPA     = grade_ECTS     / ECTS,
+         GPA_HUM = grade_ECTS_HUM / ECTS_HUM,
+         GPA_SCI = grade_ECTS_SCI / ECTS_SCI,
+         GPA_SSC = grade_ECTS_SSC / ECTS_SSC,
+         GPA_COR = grade_ECTS_COR / ECTS_COR,
+         GPA_SKI = grade_ECTS_SKI / ECTS_SKI,
+         GPA_PRO = grade_ECTS_PRO / ECTS_PRO) %>%
+
+  mutate_at(vars(matches("GPA")), lag) %>%
+
+  mutate_at(vars(matches("GPA")), ~ if_else(is.na(.), mean(d_transcript_augmented$Grade), .)) %>% # substitute missing GPA with the mean GPA across all courses (GPA_HUM is missing if student has no taken any HUM course yet)
+
+  arrange(`Student ID`) 
 ```
+
+# Join student TP and GPA
+```{r d_TP_cum}
+student_profile <- d_transcript_augmented %>%
+
+  left_join(student_GPA, by = c("Student ID", "time")) %>%
+
+  left_join(student_TP , by = c("Student ID", "time"))
+```
+
+# Regressing grade on TP and GPA
+
+```{r find_df}
+find_df <- function(course)  student_profile %>% filter(`Course ID` == course)
+```
+
+## Lasso
+```{r my_cv.glmnet}
+my_cv.glmnet <- function(df, alpha = 1, predictors){
+
+  df <- df %>% select(Grade, matches(predictors))
+
+  y <- df[names(df) == "Grade"] %>% as.matrix
+  x <- df[names(df) != "Grade"] %>% as.matrix
+
+  nfold <- min(10, floor(nrow(df) / 3))
+
+  cv.glmnet(x, y, nfolds = nfold, type.measure = "mae", alpha = alpha)
+
+}
+```
+
+```{r}
+fit_lasso <- tibble(target = course_target) %>%
+
+  mutate(d = target %>% map(find_df),
+         n = d      %>% map_dbl(nrow)) %>%
+
+  filter(n > 20) %>%
+
+  mutate(cv = d %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
+
+  select(-d)
+```
+
+```{r}
+fit_lasso <- fit_lasso %>%
+
+  # Results from CV
+  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
+         lambda_min   = cv %>% map_dbl(~.[["lambda.min"]]),
+         lambda_1se   = cv %>% map_dbl(~.[["lambda.1se"]]),
+         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
+         cv_error     = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
+         cv_error_sd  = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])
+         ) %>%
+
+  select(- cv) %>%
+
+  # Best model
+  mutate(
+    intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
+    coefi      = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
+    df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
+    dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
+    dev_left   = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
+    dev_unexpl = dev_null - dev_left,
+    dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])
+    ) %>%
+
+  select(- m_lasso) %>%
+
+  arrange(cv_error)
+
+View(fit_lasso)
+```
+
+```{r}
+hist(fit_lasso$cv_error)
+mean(fit_lasso$cv_error); weighted.mean(fit_lasso$cv_error, fit_lasso$n)
+```
+
+Topic chosen by model are related to the course.
+```{r}
+i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ law, foreign policy, culture
+i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of western pol. thought predicted by HUM
+i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ literature, art, culture
+```
+
+## find alpha
+
+```{r}
+n_alpha <- 101
+mae   <- numeric(n_alpha)
+alphas <- seq(0, 1, length.out = n_alpha)
+
+for(i in 1 : n_alpha){
+
+  fit_lasso <- tibble(target = course_target) %>%
+
+    mutate(d = target %>% map(find_df),
+           n = d      %>% map_dbl(nrow)) %>%
+
+    filter(n > 20) %>%
+
+    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
+
+    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
+           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
+
+  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
+
+  print(i)
+
+}
+
+plot(alphas, mae) # it seems that alpha = 1 gives the best results
+```
+
+# Green flag
+
+```{r}
+fit_lasso_topic <- tibble(target = course_target) %>%
+
+  mutate(d = target %>% map(find_df),
+         n = d      %>% map_dbl(nrow)) %>%
+
+  filter(n > 20) %>%
+
+  mutate(cv = d %>% map(my_cv.glmnet, alpha = 0, predictors = "Topic")) %>%
+
+  select(-d)
+```
+
+```{r}
+fit_lasso_topic <- fit_lasso_topic %>%
+
+  # Results from CV
+  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
+         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
+         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]]))
+         ) %>%
+
+  select(- cv) %>%
+
+  # Best model
+  mutate(coefi_v = list(m_lasso, index_best) %>% pmap(~ ..1[["beta"]][,..2]),
+         coefi_v = coefi_v %>% map(~ tibble(topic = names(.), weight = .)),
+         coefi_m = list(m_lasso, lambda_min) %>% pmap(coef)) %>%
+
+  # extract coefficients
+  unnest(coefi_v)%>%
+
+  select(target, topic, weight)
+
+View(fit_lasso_topic)
+```
+
+```{r}
+d_prep <- fit_lasso_topic %>%
+
+  left_join(gamma, by = "topic") %>%
+  rename(preparation = document) %>%
+  filter(target != preparation) %>%
+
+  # exclude 3000 (advanced) courses from preparation courses
+  filter(!preparation %>% str_detect("^...30")) %>%
+
+  # double prep_score of intro courses
+  mutate(is_intro = preparation %>% str_detect("^...10")) %>%
+  mutate(weight = weight * (1 + is_intro)) %>%
+
+  # prep_score
+  mutate(prep_score = weight * gamma) %>%
+
+  # aggregate prep_score
+  group_by(target, preparation) %>%
+  summarize(prep_score = sum(prep_score)) %>%
+
+  # identify top 15 preparation courses for each course
+  group_by(target) %>%
+  top_n(15, prep_score) %>%
+  arrange(target, desc(prep_score))
+
+View(d_prep)  
+```
+
+# old code
+## CV
+```{r my_predict}
+my_predict <- function(model, newdata, id){
+
+  df    <- as.matrix(newdata)
+  coefi <- coef(model, id = id)
+  xvars <- names(coefi)[-1]
+
+  coefi[1] + df[ , xvars, drop = FALSE] %*% coefi[-1]
+
+}
+```
+
+```{r my_CV}
+my_CV <- function(df){
+
+  k <- 10
+  set.seed(2019)
+  folds <- sample( 1 : k, nrow(df), replace = TRUE)
+
+  nvmax <- 5
+  cv.errors <- matrix(NA, k, nvmax, dimnames = list(NULL, paste(1 : nvmax, "predictor(s)")))
+
+  for(j in 1 : k){
+
+    training <- df[folds != j, ]
+    test     <- df[folds == j, ]
+
+    m <- regsubsets(Grade ~ ., data = training, nvmax = nvmax)
+
+    for(i in 1 : nvmax){
+
+      pred            <- my_predict(model = m, newdata = test, id = i)
+      pred            <- pmin(10, pred)
+      pred            <- pmax(0, pred)
+      cv.errors[j, i] <- mean(abs(test$Grade - as.vector(pred)))
+
+    }
+
+  }
+
+  cv.errors
+
+}
+```
+
+## BSS
+```{r my_BSS}
+my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
+```
+
+```{r extract_coef}
+extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
+```
+
+```{r my_lm}
+my_lm <- function(df, best_coef){
+
+  best_coef %>%
+
+    paste0(collapse = " + ") %>%
+    paste0("Grade ~ ", .) %>%
+    as.formula %>%
+
+    lm(data = df)
+
+}
+```
+
+```{r model fitting}
+BSS <- tibble(target = course_obj) %>%
+
+  mutate(df = target %>% map(find_df),
+         n = df %>% map(nrow)) %>%
+
+  filter(n >= 25) %>%
+
+  mutate(BSS = df %>% map(my_BSS)) %>%
+
+  mutate(CV_error      = df %>% map(my_CV),
+         CV_error_mean = CV_error %>% map(colMeans),
+         n_pred        = CV_error_mean %>% map_dbl(which.min),
+         best_coef     = list(BSS, n_pred) %>% pmap(extract_coef),
+         best_model    = list(df, best_coef) %>% pmap(my_lm)
+         ) %>%
+
+  mutate(tidied    = best_model %>% map(broom::tidy   ),
+         glanced   = best_model %>% map(broom::glance ),
+         augmented = best_model %>% map(broom::augment)) %>%
+
+  select(target, n, tidied, glanced, augmented)
+```
+
+```{r}
+BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%
+
+  mutate(MSE = deviance / df.residual )
+
+View(BSS_glance)
+```
+
+```{r}
+course <- "HUM2021"
+
+BSS_tidy_temp <- BSS %>% filter(target == course) %>% unnest(tidied, .drop = F) %>% select(-c(glanced, augmented))
+
+View(BSS_tidy_temp)
+
+BSS_augm_temp <- BSS %>% filter(target == course) %>% unnest(augmented, .drop = FALSE) %>% select(-c(tidied, glanced))
+
+View(BSS_augm_temp)
+```

### 2019-04-15 Pillar 1 - Topic Profile.Rmd
grade prediction

@@
 
-```{r load}
+```{r load, cache.lazy = TRUE}
 load("App/Recommender System/topic_model_gb.RDATA")
 load("Output/data_pillar_1.RDATA")
-load("Output/d_transcript_cum.RDATA")
 load("Output/course_current.RDATA")
@@
 beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
-View(beta)
 ```
@@
 
-```{r}
+```{r grade_ECTS}
 d_transcript_augmented <- d_transcript_augmented %>%
@@
 
-```{r}
+```{r student_GPA, cache = T}
 student_GPA <- d_transcript_augmented %>%
@@
 # Join student TP and GPA
-```{r d_TP_cum}
-student_profile <- d_transcript_augmented %>%
+```{r student_profile}
+d_transcript_augmented <- d_transcript_augmented %>%
 
@@
 
-  left_join(student_TP , by = c("Student ID", "time"))
+  left_join(student_TP , by = c("Student ID", "time")) %>%
+
+  nest(.key = profile, matches("GPA|Topic")) %>%
+
+  mutate(profile = profile %>% map(as.matrix))
 ```
@@
 
-```{r}
+```{r fit_lasso, cache = TRUE}
 fit_lasso <- tibble(target = course_target) %>%
@@
 
-```{r}
+```{r fit_lasso extract}
 fit_lasso <- fit_lasso %>%
@@
 
-  select(- cv) %>%
-
   # Best model
   mutate(
+
     intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
@@
     df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
+
     dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
@@
     dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])
+
   ) %>%
@@
   arrange(cv_error)
-
-View(fit_lasso)
 ```
@@
 
-```{r}
+```{r, cache = T}
 n_alpha <- 101
@@
 
-  print(i)
-
 }
 
-plot(alphas, mae) # it seems that alpha = 1 gives the best results
+# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
+m <- lm(mae ~ alphas)
+plot(alphas, mae)
+abline(m, col = "red")
+m %>% summary
 ```
 
-# Green flag
+# Preparation
 
@@
   # extract coefficients
-  unnest(coefi_v)%>%
+  unnest(coefi_v) %>%
 
@@
 
+# Save
+
+```{r}
+fit_lasso_app <- fit_lasso %>% select(target, cv)
+
+d_transcript_augmented_app <- d_transcript_augmented %>%
+
+  group_by(`Student ID`) %>% # only keep most recent profile of each student
+  arrange(desc(time)) %>%
+  slice(1) %>%
+
+  select(`Student ID`, profile)
+
+save(fit_lasso_app, d_transcript_augmented_app, file = "APP/Recommender System/grade_prediction.RDATA")
+```
+
+# Predict
+
+```{r my_predict}
+my_predict <- function(model, profile){
+
+  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")
+
+}
+```
+
+```{r}
+course_ID <- c("COR1005", "HUM2005") # input$course
+student_ID <- "6087587" # input$student
+
+student_profile <- d_transcript_augmented_app %>%
+
+  filter(`Student ID` == student_ID) %>%
+
+  pull(profile) %>% .[[1]]
+
+fit_lasso_app %>%
+
+  filter(target %in% course_ID) %>%
+
+  mutate(prediction = cv %>% map_dbl(my_predict, student_profile)) %>%
+
+  mutate(flag_red    = prediction < 5.5,
+         flag_orange = prediction %>% between(5.5, 7),
+         flag_green  = prediction > 7)
+```
+
 # old code
 ## CV
-```{r my_predict}
+
+```{r my_predict, eval = F}
 my_predict <- function(model, newdata, id){
@@
 
-```{r my_CV}
+```{r my_CV, eval = F}
 my_CV <- function(df){
@@
 ## BSS
-```{r my_BSS}
+```{r my_BSS, eval = F}
 my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
@@
 
-```{r extract_coef}
+```{r extract_coef, eval = F}
 extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
@@
 
-```{r my_lm}
+```{r my_lm, eval = F}
 my_lm <- function(df, best_coef){
@@
 
-```{r model fitting}
+```{r model fitting, eval = F}
 BSS <- tibble(target = course_obj) %>%
@@
 
-```{r}
+```{r, eval = F}
 BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%
@@
 
-```{r}
+```{r, eval = F}
 course <- "HUM2021"

### 2019-04-15 Pillar 1 - Topic Profile.Rmd
Preparation courses
move old code to `Misc code` script

@@
 
-save(fit_lasso_app, d_transcript_augmented_app, file = "APP/Recommender System/grade_prediction.RDATA")
+save(fit_lasso_app, d_transcript_augmented_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
 ```
@@
 ```
-
-# old code
-## CV
-
-```{r my_predict, eval = F}
-my_predict <- function(model, newdata, id){
-
-  df    <- as.matrix(newdata)
-  coefi <- coef(model, id = id)
-  xvars <- names(coefi)[-1]
-
-  coefi[1] + df[ , xvars, drop = FALSE] %*% coefi[-1]
-
-}
-```
-
-```{r my_CV, eval = F}
-my_CV <- function(df){
-
-  k <- 10
-  set.seed(2019)
-  folds <- sample( 1 : k, nrow(df), replace = TRUE)
-
-  nvmax <- 5
-  cv.errors <- matrix(NA, k, nvmax, dimnames = list(NULL, paste(1 : nvmax, "predictor(s)")))
-
-  for(j in 1 : k){
-
-    training <- df[folds != j, ]
-    test     <- df[folds == j, ]
-
-    m <- regsubsets(Grade ~ ., data = training, nvmax = nvmax)
-
-    for(i in 1 : nvmax){
-
-      pred            <- my_predict(model = m, newdata = test, id = i)
-      pred            <- pmin(10, pred)
-      pred            <- pmax(0, pred)
-      cv.errors[j, i] <- mean(abs(test$Grade - as.vector(pred)))
-
-    }
-
-  }
-
-  cv.errors
-
-}
-```
-
-## BSS
-```{r my_BSS, eval = F}
-my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
-```
-
-```{r extract_coef, eval = F}
-extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
-```
-
-```{r my_lm, eval = F}
-my_lm <- function(df, best_coef){
-
-  best_coef %>%
-
-    paste0(collapse = " + ") %>%
-    paste0("Grade ~ ", .) %>%
-    as.formula %>%
-
-    lm(data = df)
-
-}
-```
-
-```{r model fitting, eval = F}
-BSS <- tibble(target = course_obj) %>%
-
-  mutate(df = target %>% map(find_df),
-         n = df %>% map(nrow)) %>%
-
-  filter(n >= 25) %>%
-
-  mutate(BSS = df %>% map(my_BSS)) %>%
-
-  mutate(CV_error      = df %>% map(my_CV),
-         CV_error_mean = CV_error %>% map(colMeans),
-         n_pred        = CV_error_mean %>% map_dbl(which.min),
-         best_coef     = list(BSS, n_pred) %>% pmap(extract_coef),
-         best_model    = list(df, best_coef) %>% pmap(my_lm)
-         ) %>%
-
-  mutate(tidied    = best_model %>% map(broom::tidy   ),
-         glanced   = best_model %>% map(broom::glance ),
-         augmented = best_model %>% map(broom::augment)) %>%
-
-  select(target, n, tidied, glanced, augmented)
-```
-
-```{r, eval = F}
-BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%
-
-  mutate(MSE = deviance / df.residual )
-
-View(BSS_glance)
-```
-
-```{r, eval = F}
-course <- "HUM2021"
-
-BSS_tidy_temp <- BSS %>% filter(target == course) %>% unnest(tidied, .drop = F) %>% select(-c(glanced, augmented))
-
-View(BSS_tidy_temp)
-
-BSS_augm_temp <- BSS %>% filter(target == course) %>% unnest(augmented, .drop = FALSE) %>% select(-c(tidied, glanced))
-
-View(BSS_augm_temp)
-```

### 2019-04-15 Data Preparation - Course Catalogues.Rmd
Adds MSP catalogue

@@
 
-overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses")
-overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme")
+overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses|^ *Mathematics and")
+overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme|^*Courses Available at University")
 
-headers_UCM_UCV <- c("^ *Core Courses",
+headers_UCM_UCV_MSP <- c("^ *Core Courses",
                      "^Humanities \\(HUM\\)",
@@
                      "^Undergraduate Research",
-                     "Appendix") %>% collapse_or
-is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV)
+                     "Appendix",
+                     "^ *Mathematics and") %>% collapse_or
+is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV_MSP)
 
-course_code_UCM_UCV <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
-                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA" # UCV
+course_code_UCM_UCV_MSP <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
+                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA", # UCV
+                         "BIO", "CHE", "MAT", "PHY", "NEU", "INT", "PRA" #MSP
                          ) %>% collapse_or
-overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV) # simplify with %in% course_code_UCM
+overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM
 ```
@@
   "UCV"             , NA_character_                , NA_character_                           ,
-  "UCM"             , NA_character_                , NA_character_                                   
+  "UCM"             , NA_character_                , NA_character_                           ,
+  "MSP"             , NA_character_                , NA_character_
   ) %>%
@@
 
-## UCM, UCV
+## UCM, UCV, MSP
 
@@
 ```{r overview_UCM}
-overview_UCM_UCV <- function(catalogue, ID){
+overview_UCM_UCV_MSP <- function(catalogue, ID){
 
@@
   # paste current page and following page (`lead(page)`) if overview is two page long
-  transmute(text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
+  transmute(
+    text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
     `Course ID` = text %>% extract_id_course) %>%
@@
 
-  }else if(ID %in% c("UCM", "UCV")){
-    catalogue %>% overview_UCM_UCV(ID = ID)
+  }else if(ID %in% c("UCM", "UCV", "MSP")){
+    catalogue %>% overview_UCM_UCV_MSP(ID = ID)
 
-  }else "to do"
+  } else "to do"
 
@@
 
+# Current course
+```{r}
+course_current <- d_text$catalogues %>% filter(department == "UCM") %>% distinct(`Course ID`) %>% pull
+```
+
 # Save data
@@
 ```{r}
-save(d_text, file = "Output/d_text.RDATA")
+save(course_current, file = "Output/course_current.RDATA")
+save(d_text        , file = "Output/d_text.RDATA")
 ```

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

@@
 
-```{r student_GPA, cache = T}
+```{r student_GPA, cache = TRUE}
 student_GPA <- d_transcript_augmented %>%
@@
 # Join student TP and GPA
-```{r student_profile}
-d_transcript_augmented <- d_transcript_augmented %>%
+```{r student_profile, cache = TRUE}
+student_profile <- d_transcript_augmented %>%
 
@@
 
-  left_join(student_TP , by = c("Student ID", "time")) %>%
+  left_join(student_TP , by = c("Student ID", "time"))
+```
+
+```{r}
+student_profile_nest <- student_profile %>%
 
@@
   mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min   = cv %>% map_dbl(~.[["lambda.min"]]),
-         lambda_1se   = cv %>% map_dbl(~.[["lambda.1se"]]),
+         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
+         lambda_1se   = cv %>% map_dbl(~ .[["lambda.1se"]]),
          index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
@@
 i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ literature, art, culture
-```
-
-## find alpha
-
-```{r, cache = T}
-n_alpha <- 101
-mae   <- numeric(n_alpha)
-alphas <- seq(0, 1, length.out = n_alpha)
-
-for(i in 1 : n_alpha){
-
-  fit_lasso <- tibble(target = course_target) %>%
-
-    mutate(d = target %>% map(find_df),
-           n = d      %>% map_dbl(nrow)) %>%
-
-    filter(n > 20) %>%
-
-    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
-
-    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
-           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
-
-  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-
-}
-
-# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
-m <- lm(mae ~ alphas)
-plot(alphas, mae)
-abline(m, col = "red")
-m %>% summary
 ```
@@
 
-d_transcript_augmented_app <- d_transcript_augmented %>%
+student_profile_nest_app <- student_profile_nest %>%
 
@@
 
-save(fit_lasso_app, d_transcript_augmented_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
+save(fit_lasso_app, student_profile_nest_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
 ```
@@
 
-student_profile <- d_transcript_augmented_app %>%
+student_prof <- student_profile_nest_app %>%
 
@@
 
-  mutate(prediction = cv %>% map_dbl(my_predict, student_profile)) %>%
+  mutate(prediction = cv %>% map_dbl(my_predict, student_prof)) %>%
 
@@
 ```
+
+# Extra: find best alpha
+
+Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
+
+```{r, cache = T}
+n_alpha <- 101
+mae   <- numeric(n_alpha)
+alphas <- seq(0, 1, length.out = n_alpha)
+
+for(i in 1 : n_alpha){
+
+  fit_lasso <- tibble(target = course_target) %>%
+
+    mutate(d = target %>% map(find_df),
+           n = d      %>% map_dbl(nrow)) %>%
+
+    filter(n > 20) %>%
+
+    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
+
+    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
+           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
+
+  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
+
+}
+
+# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
+m <- lm(mae ~ alphas)
+plot(alphas, mae)
+abline(m, col = "red")
+m %>% summary
+```

### 2019-04-16 Data Preparation.Rmd

@@
 
-  left_join(map_assessment_AoD, by = "Assessment") %T>%
+  left_join(map_assessment_AoD, by = "Assessment") %>%
+
+  filter(!is.na(AoD)) %T>%
 
@@
 
+##
+```{r}
+d_course <- d_course %>%
+  mutate(target = Number > 2000 & Type == "Elective" & (! str_detect(`Course ID`, "SA")))
+```
+
 ## Student Data
@@
 
+The data set `d_transcript` contains both the failed grades and the grade of the resit, and does not distinguish between them (same student, same course, same yera, same period, but different grade).
+
 ```{r d_transcript helper}
@@
   # for simplicity, we only keep 
-  # *UCM courses*  (courses present in the UCM catalogue)
-  # taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
+  # courses taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
 
-  filter(
-    `Module (Abbrev.)` %>% is_UCM,
-    `Program (Abbreviation)` == "7501"
-    ) %>%
+  filter(`Program (Abbreviation)` == "7501") %>%
 
@@
 d_transcript <- d_transcript %>%
-
-  # Remove variables with only one value (~10)
-  discard(function(x) n_distinct(x) == 1) %>%
-
-  # Select: Student ID, course ID, when a course is taken and the grade 
+  # keep variables: Student ID, course ID, when a course is taken and the grade 
   select(
@@
 
-  if(is.na(grade) | grade == "NG") grade <- "0"
+  if(grade == "NG" | is.na(grade)) return(NA)
 
@@
 
-    # Combine year and period to have be able to order the course in time using a single variable
+    # Combine year & period to chronologically order courses using a single variable
     time = str_c(Year_numerical, period_numerical) %>% as.numeric,
@@
 ```{r}
-d_transcript_augmented <- d_transcript %>% left_join(select(d_course, - Period), by = c("Course ID"))
+d_transcript <- d_transcript %>% filter(!is.na(Grade))
 ```
@@
 ```{r}
-d_transcript_elective <- d_transcript_augmented %>%
-  filter(`Course ID` %>% is_elective) %>%
-  select(`Student ID`, `Course ID`, time, Grade, grade_ceil)
+d_transcript_augmented <- d_transcript %>%
+  left_join(select(d_course, - Period), by = c("Course ID"))
 ```
@@
 
+  # ~ 10 incomplete rows for a student's profile
+  d_transcript %>% filter(`Student ID` == "0481343") %>% View
+
 #TODO: list issues here
@@
 
-save(d_transcript_augmented, d_transcript_elective, file = "Output/data_pillar_1.RDATA")
+save(d_transcript_augmented, file = "Output/data_pillar_1.RDATA")
 

### 2019-04-16 Misc Code.Rmd

@@
 ```
+
+## CV
+
+```{r my_predict, eval = F}
+my_predict <- function(model, newdata, id){
+
+  df    <- as.matrix(newdata)
+  coefi <- coef(model, id = id)
+  xvars <- names(coefi)[-1]
+
+  coefi[1] + df[ , xvars, drop = FALSE] %*% coefi[-1]
+
+}
+```
+
+```{r my_CV, eval = F}
+my_CV <- function(df){
+
+  k <- 10
+  set.seed(2019)
+  folds <- sample( 1 : k, nrow(df), replace = TRUE)
+
+  nvmax <- 5
+  cv.errors <- matrix(NA, k, nvmax, dimnames = list(NULL, paste(1 : nvmax, "predictor(s)")))
+
+  for(j in 1 : k){
+
+    training <- df[folds != j, ]
+    test     <- df[folds == j, ]
+
+    m <- regsubsets(Grade ~ ., data = training, nvmax = nvmax)
+
+    for(i in 1 : nvmax){
+
+      pred            <- my_predict(model = m, newdata = test, id = i)
+      pred            <- pmin(10, pred)
+      pred            <- pmax(0, pred)
+      cv.errors[j, i] <- mean(abs(test$Grade - as.vector(pred)))
+
+    }
+
+  }
+
+  cv.errors
+
+}
+```
+
+## BSS
+```{r my_BSS, eval = F}
+my_BSS <- function(df) regsubsets(Grade ~ ., data = df, nvmax = 7)
+```
+
+```{r extract_coef, eval = F}
+extract_coef <- function(BSS, BS) names(coef(BSS, BS))[-1]
+```
+
+```{r my_lm, eval = F}
+my_lm <- function(df, best_coef){
+
+  best_coef %>%
+
+    paste0(collapse = " + ") %>%
+    paste0("Grade ~ ", .) %>%
+    as.formula %>%
+
+    lm(data = df)
+
+}
+```
+
+```{r model fitting, eval = F}
+BSS <- tibble(target = course_obj) %>%
+
+  mutate(df = target %>% map(find_df),
+         n = df %>% map(nrow)) %>%
+
+  filter(n >= 25) %>%
+
+  mutate(BSS = df %>% map(my_BSS)) %>%
+
+  mutate(CV_error      = df %>% map(my_CV),
+         CV_error_mean = CV_error %>% map(colMeans),
+         n_pred        = CV_error_mean %>% map_dbl(which.min),
+         best_coef     = list(BSS, n_pred) %>% pmap(extract_coef),
+         best_model    = list(df, best_coef) %>% pmap(my_lm)
+         ) %>%
+
+  mutate(tidied    = best_model %>% map(broom::tidy   ),
+         glanced   = best_model %>% map(broom::glance ),
+         augmented = best_model %>% map(broom::augment)) %>%
+
+  select(target, n, tidied, glanced, augmented)
+```
+
+```{r, eval = F}
+BSS_glance <- BSS %>% unnest(glanced) %>% select(-c(tidied, augmented)) %>%
+
+  mutate(MSE = deviance / df.residual )
+
+View(BSS_glance)
+```
+
+```{r, eval = F}
+course <- "HUM2021"
+
+BSS_tidy_temp <- BSS %>% filter(target == course) %>% unnest(tidied, .drop = F) %>% select(-c(glanced, augmented))
+
+View(BSS_tidy_temp)
+
+BSS_augm_temp <- BSS %>% filter(target == course) %>% unnest(augmented, .drop = FALSE) %>% select(-c(tidied, glanced))
+
+View(BSS_augm_temp)
+```

### 2019-04-16 Pillar 2 - Tmp Topic Modeling.Rmd

@@
 ```
+###Preparation of course_title vector
+```{r course titles, eval = TRUE}
+#Clean titles
+course_titles <-  d_text$catalogues %>%
+  select(`Course ID`, `Course Title`, department) %>% 
+  distinct
 
+empty_titles <- course_titles %>% filter(`Course Title` == "")
+
+```
 ###Functions for internal faceting
@@
 We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
-```{r fast control}
+```{r fast control, eval = TRUE}
 my_control_fast <- list(
@@
 To evaluate how many topics are optimal, we graph the perplexity and log Likelihood of models against the number of topics.
-```{r perplexity plots, eval = TRUE}
+```{r perplexity plots, eval = FALSE}
 #Function
@@
 ###Alpha
-```{r alpha and beta}
+```{r alpha and beta, eval = FALSE}
 sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS
@@
 #Beta
-```{r alpha and beta}
+```{r alpha and beta, eval = FALSE}
 
@@
 We save the data from our intermediate step in case further analysis is needed.
-```{r save, eval = T}
+```{r save, eval = TRUE}
 #save(tb_topic_model, file = "Output/tb_topic_model.RDATA" )
@@
 The function `clean_kw` removes stopwords from our key words.
-```{r function clean key words}
+```{r function clean key words, eval = T}
 clean_kw <- function(kw_list){
@@
 On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
-```{r crop and clean TM for App}
+```{r crop and clean TM for App, eval = T}
 app_topic_model <- tb_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
@@
 For the app we also need to have a list of all courses and an example of a prospective semester
-```{r for convenience}
+```{r for convenience, eval = T}
 # set seed
@@
 
-```{r adding convenience vectors}
+```{r adding convenience vectors, eval = T}
 app_topic_model <- app_topic_model %>%
   mutate(`All Courses`     = list(course_all),
-         `Sample semester` = list(course_following_semester))
+         `Sample semester` = list(course_following_semester),
+         `Course Titles`   = list(course_titles) )
 
@@
 We save all requirements for the app.
-```{r app files}
-# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
+```{r app files, eval = T}
+save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
 ```

### 2019-04-16 Data Preparation - Course Catalogues.Rmd

@@
 overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM
+
+titles_end_UCM_UCV_MSP <- c("1000", "2000", "3000", #UCV
+                            "Course coordinators?",    #UCM, MSP
+                            "Coordinator", "PLEASE NOTE:", "Note:" #MSP
+                            ) %>% collapse_or
+
+title_end_location <- function(string) str_locate(string, titles_end_UCM_UCV_MSP) %>% .[,1]
+extract_course_title <- function(string) str_sub(string, 9, title_end_location(string)-2)
 ```
@@
     text           = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
-    `Course ID` = text %>% extract_id_course) %>%
+    `Course ID`    = text %>% extract_id_course,
+    `Course Title` = text %>% extract_course_title) %>%
     mutate(department  = ID) %>%

### 2019-04-16 Pillar 2 - Tmp Topic Modeling.Rmd
knit/ topic models including msp

@@
 This step takes some time, thus we also measure how long it takes to train the model.
-```{r LDA fit, cache = TRUE, eval = FALSE}
+```{r LDA fit full, cache = TRUE, eval = FALSE}
 #Timing_____________________________________________________________________
@@
 For time constrains, we sometimes need to train the model only on the manuals or the catalogues, for this we add an extra filtering step in the code that filters on `which_texts`.
-```{r LDA fit, cache = TRUE, eval = TRUE}
+```{r LDA fit separate, cache = TRUE, eval = TRUE}
 #Timing
@@
 #Training
-topic_numbers <-c(10, 25, 30, 35, 40, 45, 50, 55, 60) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
+topic_numbers <-c(50, 55, 60, 65, 70) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
 which_texts <- "catalogues"
@@
 ###Alpha
-```{r alpha and beta, eval = FALSE}
+```{r alpha, eval = FALSE}
 sample_dtm <- tb_topic_model$DTM[[1]] #1 CATALOGUES, 2 MANUALS
@@
 #Beta
-```{r alpha and beta, eval = FALSE}
+```{r beta, eval = FALSE}
 

### 2019-04-16 App/Recommender System/server.R
traffic lights without intro courses

@@ -2,6 +2,7 @@ library(tidyverse)
 library(tidytext)
 library(stringr)
 library(hunspell)
+library(DT)
 
 load("rules.RDATA")
 load("data_pillar_1.RDATA")
@@ -314,8 +315,8 @@ function(input, output, session) {
         checkboxGroupInput(
           inputId  = "course_chosen_traffic",
           label    = "Tentative Courses",
-          choices  = course_all,
-          selected = course_all,
+          choices  = course_advanced,
+          selected = course_advanced,
           inline   = TRUE
         ))
   })
@@ -328,6 +329,15 @@ function(input, output, session) {
     #read vectors
     student_ID <- student_ID_traffic()
     course_ID <- course_ID_traffic()
+    
+  
+    preparatory <- d_prep %>%
+      filter(target %in% course_ID) %>%
+      group_by(target) %>%
+      top_n(5, prep_score) %>%
+      mutate(Preparation = paste(preparation, collapse =" | ")) %>% 
+      select(target, Preparation) %>%
+      distinct
     
     #predict
     student_prof <- student_profile_nest_app %>% 
@@ -344,7 +354,8 @@ function(input, output, session) {
       mutate(flag_red    = prediction < 5.5,
              flag_orange = prediction %>% between(5.5, 7),
              flag_green  = prediction > 7) %>%
-      select(-prediction, -cv)
+      select(-cv) %>%
+     left_join(preparatory, by = "target")
     
   })
   

### 2019-04-16 tmp_runBeforeApp.R

@@ -18,8 +18,10 @@ app_model <- app_topic_model %>%
 
 course_all <- app_model$`All Courses`[[1]]
 
+course_advanced <-course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
+
 #pass model to app
-save(app_model,course_all, file = "./App/Recommender System/app_model.RDATA" )
+save(app_model,course_all,course_advanced, file = "./App/Recommender System/app_model.RDATA" )
 
 
 

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

@@
 course_target <- course_current[! str_detect(course_current, "...10..")]
-course_target <- setdiff(course_target, "CAP3000") # exclude capstone
 course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
@@
 
-# Preparation
+# Preparatory courses
 
@@
   left_join(gamma, by = "topic") %>%
-  rename(preparation = document) %>%
-  filter(target != preparation) %>%
+  rename(`Preparatory Courses` = document) %>%
+  filter(target != `Preparatory Courses`) %>%
 
   # exclude 3000 (advanced) courses from preparation courses
-  filter(!preparation %>% str_detect("^...30")) %>%
+  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%
 
   # double prep_score of intro courses
-  mutate(is_intro = preparation %>% str_detect("^...10")) %>%
+  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
   mutate(weight = weight * (1 + is_intro)) %>%
@@
   # aggregate prep_score
-  group_by(target, preparation) %>%
+  group_by(target, `Preparatory Courses`) %>%
   summarize(prep_score = sum(prep_score)) %>%

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

@@
 ```{r}
-i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ law, foreign policy, culture
-i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of western pol. thought predicted by HUM
-i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ literature, art, culture
+beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
+
+i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
+beta %>% filter(topic == "Topic 18")
+beta %>% filter(topic == "Topic 8" )
+
+i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Business Administration: topic ~ business
+beta %>% filter(topic == "Topic 19")
+
+i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
+beta %>% filter(topic == "Topic 21") 
+beta %>% filter(topic == "Topic 23")
+
+i <- 9; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
+beta %>% filter(topic == "Topic 7") 
 ```
@@
 
-View(fit_lasso_topic)
+print(fit_lasso_topic)
 ```
@@
 
-View(d_prep)
+print(d_prep)
 ```

### 2019-04-17 LDA_evaluation_script.R
Delete tmp files

@@ -1,105 +1,0 @@
-load("output/data_pillar_2.RDATA")
-
-
-#
-# Set up
- 
-library(topicmodels)
-library(tidyverse)
-library(tidytext)
-
-d_overview <- d_overview %>%
-  filter(
-    `Academic Year` == "2018-2019"
-  )
-
-my_cast_tdm <- function(data, level) data %>%
-  count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
-
-d_overview_cast <- my_cast_tdm(d_overview)
-
-my_control_individual <- list(
-  
-  nstart  = 10,
-  seed    = c(1:10),
-  best    = TRUE,
-  
-  burnin  = 500,
-  iter    = 2000,
-  thin    = 100,
-  
-  verbose = 1e2,
-  save    = 1e3,
-  keep    = 1e3
-  )
-
-
-
-#
-# Fitting topic model
-
-LDA_model <-list()
-
-# LDA_model$k5 <- LDA(
-#   x       = d_overview_cast,
-#   k       = 5,
-#   method  = "Gibbs",
-#   control = my_control_individual
-# )
-
-LDA_model$k10 <- LDA(
-  x       = d_overview_cast,
-  k       = 10,
-  method  = "Gibbs",
-  control = my_control_individual
-)
-
-LDA_model$k20 <- LDA(
-  x       = d_overview_cast,
-  k       = 20,
-  method  = "Gibbs",
-  control = my_control_individual
-)
-
-LDA_model$k35 <- LDA(
-  x       = d_overview_cast,
-  k       = 35,
-  method  = "Gibbs",
-  control = my_control_individual
-)
-#Preparing for export
-
-#Functions
-get_beta <- function(results){
-  
-  tidytext::tidy(results, matrix = "beta") %>%
-    mutate(topic = paste("Topic", topic)) %>%
-    arrange(topic, desc(beta))
-  
-}
-
-get_gamma <- function(results){
-  
-  tidytext::tidy(results, matrix = "gamma") %>%
-    mutate(topic = paste("Topic", topic)) %>%
-    arrange(topic, desc(gamma))
-  
-}
-#Applying functions
-clean_models <- list()
-
-clean_models$beta_distribution <- lapply(
-  LDA_model,
-  get_beta
-)
-
-clean_models$gamma_distribution <- lapply(
-  LDA_model,
-  get_gamma
-)
-  
-#saving
-save(clean_models,
[…]

### 2019-04-17 Messy Code/exaple stm.R

@@ -1,11 +1,0 @@
-data <- read.csv("/Users/sofia/Downloads/poliblogs2008.csv")
-processed <- textProcessor(data$documents, metadata = data)
-
-out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
-docs <- out$documents
-vocab <-  out$vocab
-meta <- out$meta
-
-poliblogPrevFit <- stm(documents = out$documents, vocab = out$vocab, K = 20, prevalence = ~rating + s(day), max.em.its = 75, data = out$meta, init.type = "Spectral")
-
-

### 2019-04-17 TEMPORARY DKE Presentation code.R

@@ -1,119 +1,0 @@
-#Graph Results
-
-load("Output/LDA_ntopics.RDATA")
-
-graph_results_package <- function(data) {
-  data %>%
-    select(-Griffiths2004) %>%
-    gather(key = "Metric", value = "Value", CaoJuan2009, Arun2010, Deveaud2014) %>%
-    mutate(MinMax = ifelse(Metric=="Deveaud2014", "maximize", "minimize")) %>%
-    group_by(Metric) %>%
-    mutate(Value = Value/sum(Value))%>%
-    
-    ggplot(aes(x = topics, y = Value))+
-    geom_line(aes(colour = Metric))+
-    geom_point(aes(colour = Metric))+
-    facet_wrap(~MinMax, nrow = 2, scales = "free")+
-    theme_minimal()
-}
-
-
-graph_results_package(result_manual)
-ggsave("Graphs_presentation/Find_manuals.jpg")
-graph_results_package(result_overview)
-ggsave("Graphs_presentation/Find_overview.jpg")
-
-
-#------------------------------------------
-load("Output/topic_model.RDATA")
-
-old_topic_model <- as_tibble(topic_model) %>%
-  gather(key = "Origin", value = "Model", TM_overview, TM_manual) %>%
-  mutate(Origin = str_remove(Origin,"TM_")) %>%
-  mutate(Origin = str_replace(Origin,"manual", "manuals")) %>%
-  mutate( `Topic ID` = paste(Origin, n_topic, sep = "_"),
-          
-          #Document Term Matrix
-          DTM        = pmap(.l = list(Origin), .f = extract_dtm),
-          
-          #Gamma distribution
-          Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
-          
-          #Beta distribution
-          Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
-          
-          #Perplexity
-          Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
-          
-          #Loglikelihood
-          LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
-          
-          
-          #
-          ##Inspect
-          
-          #top words per topic
-          top_terms_topic = map(Beta, .f = get_top_terms_topic),
-          
-          #top topics per course
[…]

### 2019-04-17 Pillar 2 - Tmp Topic Modeling.Rmd
compute app_model in Pillar 2

@@
 
+app_model <- app_topic_model %>%
+  filter(n_topic == 55)
 #rm(course_all, course_following_semester)
@@
 ```{r app files, eval = T}
-save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
+save(app_topic_model, app_model, file = "App/Recommender System/data_topic_models.RDATA")
 ```

### 2019-04-17 App/Recommender System/server.R

@@ -368,6 +368,7 @@ function(input, output, session) {
       mutate(flag_red    = prediction < 5.5,
              flag_orange = prediction %>% between(5.5, 7),
              flag_green  = prediction > 7) %>%
+      mutate_at(vars(flag_red, flag_orange, flag_green), funs(ifelse(.,., " ")))%>%
       select(-cv) %>%
      left_join(preparatory, by = "target")
   

### 2019-04-17 tmp_runBeforeApp.R
delete tmp file

@@ -1,20 +1,0 @@
-#Pass file to App
-# load("./Output/_catalogues_tmp_topic_model_tibble.RDATA")
-# save(tb_topic_model, file = "./App/Recommender System/tmp_catalogues_topic_model.RDATA")
-
-#Load necessary files to the environment
-load("./App/Recommender System/data_topic_models.RDATA") 
-
-#Inspect what number of topics to use:
-ggplot(tb_topic_model, aes(n_topic, Perplexity))+
-  geom_point()
-ggplot(tb_topic_model, aes(n_topic, LogLikelihood))+
-  geom_point()
-
-#select Model to pass to App
-app_model <- app_topic_model %>%
-  filter(n_topic == 55)
-
-#pass model to app
-save(app_model,
-     file = "./App/Recommender System/app_model.RDATA" )

### 2019-04-17 App/Recommender System/server.R
delete app_model calculation in server

@@ -21,9 +21,7 @@ load("grade_prediction.RDATA")
 function(input, output, session) {
   
   #General set up
-  app_model <- app_topic_model %>%
-    filter(n_topic == 55)
-  
+
   course_all <- app_model$`All Courses`[[1]]
   
   course_advanced <-course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]

### 2019-04-17 App/Recommender System/ui.R
delete load of useless file

@@ -7,7 +7,6 @@ library(shinythemes)
 load("data_pillar_1.RDATA")
 load("data_topic_models.RDATA") #contains distribution, kw, course_all, course_following_semester.
 load("rules_clean.RDATA")
-load("app_model.RDATA") #containes selected model, must be equal to app_model calculated in server
 
 #
 # ui

### 2019-04-17 App/Recommender System/server.R
spaces for readability of code

@@ -23,7 +23,7 @@ function(input, output, session) {
 
   course_all <- app_model$`All Courses`[[1]]
   
-  course_advanced <-course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
+  course_advanced <- course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
   
   # ---------------------------------------------------------------------------------
   ## -- RED FLAGS --
@@ -37,7 +37,7 @@ function(input, output, session) {
     filter(type_rule == "SR")
   
   #Helper function: return tibble of type_rules
-  get_type_rules <-  function(type){
+  get_type_rules <-  function(type) {
     tmp <- raw_rules %>%
       filter(ID == type) %>%
       pull(rules_RS)
@@ -48,7 +48,7 @@ function(input, output, session) {
   #Helper: resettabe input
   output$resetable_input <- renderUI({
     times <- input$reset_input
-    div(id=letters[(times %% length(letters)) + 1],
+    div(id = letters[(times %% length(letters)) + 1],
         checkboxGroupInput(
           inputId  = "course_chosen",
           label    = "Tentative Courses for following period",
@@ -60,7 +60,7 @@ function(input, output, session) {
   
   
   # Helper function: Return student
-  student_trans <- function(d_student){
+  student_trans <- function(d_student) {
  
     # Student profile
     student <- list()
@@ -134,7 +134,7 @@ function(input, output, session) {
       
     mutate(
       `Red Flag` = rhs_course,
-      Reason = paste(
+      Reason     = paste(
         "You have not taken ",
         lhs_course,
         " and ",
@@ -192,7 +192,7 @@ function(input, output, session) {
       
     mutate(
       `Red Flag` = rhs_course,
-      Reason = paste(
+      Reason     = paste(
         "You have failed ",
         lhs_course,
         " and ",
@@ -228,7 +228,7 @@ function(input, output, session) {
       
     mutate(
       `Red Flag` = rhs_course,
-      Reason = paste(
+      Reason     = paste(
         "You have obtained less than ",
             lhs_outcome,
             "/10 in ",
@@ -280,10 +280,11 @@ function(input, output, session) {
         ) %>% 
       ungroup
     
-    
-    if(nrow(student$transcript)==0){
-      #"ERROR: id not found- we need new students ID's before running this"
+    #output
+    if(nrow(student$transcript) == 0){
+      
       tibble(ERROR = "Student ID not found")
+      
     }else if(nrow(rules) == 0){
       
[…]

### 2019-04-17 Pillar 2 - Tmp Topic Modeling.Rmd
spaces for readability of code

--- 2019-04-16 Pillar 2 - Tmp Topic Modeling.Rmd
@@
 #Extract Distributions (Gamma/Beta)-----------------------------------------------
-get_distributions <- function(model, distrib_str){ #input gamma or beta
+get_distributions <- function(model, distrib_str) { #input gamma or beta
   tidy(model, matrix = distrib_str) %>%
@@
 #perplexity Function-----------------------------------------------
-my_perplexity <- function(model, dtm){
+my_perplexity <- function(model, dtm) {
   perplexity(model, dtm, estimate_theta = FALSE)
@@
 
-get_top_terms_topic <- function(d_beta){
+get_top_terms_topic <- function(d_beta) {
   data.frame(d_beta) %>%
@@
 
-get_top_topics_course <- function(d_gamma){
+get_top_topics_course <- function(d_gamma) {
   data.frame(d_gamma) %>%
@@
 
-get_kw <- function(d_beta){
+get_kw <- function(d_beta) {
   data.frame(d_beta) %>%
@@
     top_n(3, beta) %>%
-    ungroup()%>%
-    pull(term)%>%
+    ungroup() %>%
+    pull(term) %>%
     unique()
@@
 tb_topic_model <- tibble( 
+  n_topic = rep(topic_numbers, each = length(d_text)) 
+  ) %>%
 
-  #repeat each topic number twice (once for catalogues and once for manual)
-  n_topic = rep(topic_numbers, each = length(d_text))
-
-  ) %>%
   mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
@@
          DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%
+
   filter(Origin == which_texts) %>%
+
   mutate(
@@
 #Function
-plot_evaluation <- function(origin){
+plot_evaluation <- function(origin) {
 
@@
 ```{r function clean key words, eval = T}
-clean_kw <- function(kw_list){
+clean_kw <- function(kw_list) {
 
@@
 ```{r crop and clean TM for App, eval = T}
-app_topic_model <- tb_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
+app_topic_model <- tb_topic_model %>% 
+  select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
   mutate(kw = map(kw, .f = clean_kw))
@@
 ##courses following_semester
-course_following_semester <- sample(
-  x       = course_all,
+course_following_semester <- sample(x = course_all,
                                     size    = 60,
-  replace = FALSE
-  ) %>% sort
+                                    replace = FALSE) %>% 
+  sort()
 
@@
 
+app_model <- app_topic_model %>%
+  filter(n_topic == 55)
+
 #rm(course_all, course_following_semester)

### 2019-04-17 Miscellaneous code /Experiments/Ternary Plots.Rmd
moved things to different folder

---
title: "Ternary plot"
author: "DARS"
date: "4/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ternary Plots
This is a simple visualization tool to see where you are in the SCI, SSC, and HUM space.

```{r libraries}
library(tidyverse)
library(Ternary)

```

## Load
```{r load, echo=FALSE}
load("~/Documents/DARS/GitDARS/Output/data_pillar_1.RDATA")
```

```{r}
data <- d_transcript_augmented %>% 
  select(`Student ID`, `Course ID`) %>% 
  distinct() %>%
  mutate(`Course Concentration` = str_sub(`Course ID`, 1,3)) %>%
  filter(`Course Concentration` %in% c("HUM", "SSC", "SCI")) %>%
  group_by(`Student ID`) %>%
  count(`Course Concentration`) %>%
  group_by(`Student ID`) %>%
  mutate(student_total = sum(n),
         proportion = n/student_total) %>%
  select(-n,-student_total) %>%
  spread(key = `Course Concentration`, value = proportion, fill = 0)

```

```{r}
TernaryPlot()
AddToTernary(points, data)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-04-23 Pillar 2 - Tmp Topic Modeling.Rmd
evaluate over many models catalogues

@@
 #Training
-topic_numbers <-c(50, 55, 60, 65, 70) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
+topic_numbers <-seq(from = 5, to = 150, by = 5)#c(50, 55, 60, 65, 70) #seq(from = 5, to = 10, by = 2) #5 to 150 by 50
 which_texts <- "catalogues"
@@
 plot_evaluation("catalogues")
-plot_evaluation("manuals")
+#plot_evaluation("manuals")
 ```

### 2019-04-23 Miscellaneous code /Experiments/Read in articles for recommendation.Rmd
adds files to input and output materials

---
title: "Read in articles for recommendation"
author: "DARS"
date: "4/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Libraries
```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang) #quote
library(ldatuning) # ideal number of topics in LDA

library(tm)
library(hunspell) # Stemmer
library(magrittr)

```
#Load set up
```{r}
load("~/Documents/DARS/GitDARS/App/Recommender System/data_topic_models.RDATA")
load("~/Documents/DARS/GitDARS/Output/_catalogues_tmp_topic_model_tibble.RDATA")
```

We select a single model to pass it the new document
```{r load model}
my_model <- tb_topic_model %>% filter(n_topic == 55) %>% .[["Model"]]
```

We load a new document and clean it
```{r}

read_in_pdfs <- function(file) {

  Corpus(
    x             = DirSource(file),
    readerControl = list(reader = readPDF(control = list(text = "-layout")))
    ) %>%

    # turn corpus into a tibble to facilitate manipulation
    as.list %>% tibble(raw = .) %>%

    transmute(
      ID   = raw %>% map(function(x) x$meta$id),
      text = raw %>% map(content)
      )

}
```

```{r}
my_pdf <- read_in_pdfs("~/Documents/DARS/GitDARS/Input/Articles/")

my_pdf$text

my_document <- tibble( 
  ID   = my_pdf$`Narrative Media-Article.pdf`$meta$id,
  page = my_pdf$`Narrative Media-Article.pdf`$content)

my_document <- my_document %>% 
  mutate(ID = str_sub(ID, 1,-5)) %>% #remove .pdf
```

### 2019-04-23 Output/Conference/Figures.R
clean folder - remove old files

@@ -1,69 +1,0 @@
-load("Output/_catalogues_tmp_topic_model_tibble.RDATA")
-
-theme_set(theme_light())
-
-d <- tb_topic_model
-
-names(d)
-gamma <- d$Gamma[[1]]
-beta  <- d$Beta[[1]]
-
-# Figure 1: Beta. ####
-
-plot_beta <- function(topic = 1, sub = NULL){
-  
-  top <-  str_c("Topic ", topic)
-  
-  beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
-    
-    ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
-    
-    coord_flip() +
-    
-    labs(title = str_c("Main Terms of ", top),
-         subtitle = sub,
-         x = "Terms",
-         y = "Beta"
-    )
-  
-}
-
-# topic 1: "Topic 1 corresponds to engineering",
-plot_beta(1, sub = "Topic 1 corresponds to engineering")
-# topic 9: computer science, topic 
-# Topic 20: psychology
-# topic 25: history
-# topic 26: literature 
-
-
-
-# Gamma ####
-
-# SCI3003 optimization dominated by topic 1
-
-plot_gamma <- function(course = "COR1002", sub = NULL){
-  
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-    
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-    
-    coord_flip() +
-    
-    labs(title    = str_c("Main Topics of Course ", course),
-         subtitle = sub,
-         x = "Topics",
-         y = "Gamma"
-         )
-  
-}
-
-plot_gamma("HUM1014")
-plot_beta(43)
-plot_beta(26)
-

### 2019-04-23 Output/Plots/Plot script.R
re-organize conference folder

@@ -1,74 +1,0 @@
-load("Output/data_pillar_1.RDATA")
-library(tidyverse)
-
-# Set up
-height <- 4; width <- height * 1.6
-theme_set(theme_light())
-
-# Student transcript
-student_ID <- "6087587"
-
-transcript <- d_transcript_augmented %>%
-  
-  mutate(Cluster = factor(Cluster)) %>%
-  
-  filter(`Student ID` == student_ID)
-
-
-# Aod & Assessment
-
-my_barplot_AoD <- function(transcript, var){
-  
-  transcript %>%
-    
-    filter(! is.na(!!ensym(var))) %>%
-    
-    pull(!!ensym(var)) %>% 
-    
-    str_c(collapse = ", ") %>%
-    
-    str_split(", ") %>% .[[1]] %>%
-    
-    tibble(AoD = .) %>%
-    
-    ggplot(aes(reorder(AoD, AoD, function(x) length(x)))) +
-    geom_bar() +
-    coord_flip() +
-    labs(title = var, x = NULL)
-  
-}
-
-my_barplot_AoD(transcript, "AoD Covered")
-ggsave("AoD.jpeg", path = "Output/Plots", width = width, height = height)
-
-my_barplot_AoD(transcript, "Assessments Covered")
-ggsave("Assessment.jpeg", path = "Output/Plots", width = width, height = height)
-
-
-## Profile: cluster & concentration
-
-my_barplot_concentration <- function(transcript, var){
-  
-  transcript  %>%
-    
-    filter(! is.na(!!ensym(var)), ! is.na(Level)) %>%
-    
-    ggplot(aes(!!ensym(var), fill = Level)) +
-    
-    geom_bar(col = "black") +
-    
-    facet_grid(Year_numerical ~ .) + 
-    
-    scale_x_discrete(drop = FALSE) + 
-    scale_fill_discrete(drop = FALSE) +
-    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
-    labs(title = "Student's Courses", x = NULL)
-
-}
-
-my_barplot_concentration(transcript, "Concentration")
-ggsave("concentration.jpeg", path = "Output/Plots", width = width, height = height)
-
-my_barplot_concentration(transcript, "Cluster")
-ggsave("Cluster.jpeg", path = "Output/Plots", width = width, height = height)
-

### 2019-04-23 Output/Plots/Plots.R
rename file for clarity

@@ -1,0 +1,74 @@
+load("Output/data_pillar_1.RDATA")
+library(tidyverse)
+
+# Set up
+height <- 4; width <- height * 1.6
+theme_set(theme_light())
+
+# Student transcript
+student_ID <- "6087587"
+
+transcript <- d_transcript_augmented %>%
+  
+  mutate(Cluster = factor(Cluster)) %>%
+  
+  filter(`Student ID` == student_ID)
+
+
+# Aod & Assessment
+
+my_barplot_AoD <- function(transcript, var){
+  
+  transcript %>%
+    
+    filter(! is.na(!!ensym(var))) %>%
+    
+    pull(!!ensym(var)) %>% 
+    
+    str_c(collapse = ", ") %>%
+    
+    str_split(", ") %>% .[[1]] %>%
+    
+    tibble(AoD = .) %>%
+    
+    ggplot(aes(reorder(AoD, AoD, function(x) length(x)))) +
+    geom_bar() +
+    coord_flip() +
+    labs(title = var, x = NULL)
+  
+}
+
+my_barplot_AoD(transcript, "AoD Covered")
+ggsave("AoD.jpeg", path = "Output/Plots", width = width, height = height)
+
+my_barplot_AoD(transcript, "Assessments Covered")
+ggsave("Assessment.jpeg", path = "Output/Plots", width = width, height = height)
+
+
+## Profile: cluster & concentration
+
+my_barplot_concentration <- function(transcript, var){
+  
+  transcript  %>%
+    
+    filter(! is.na(!!ensym(var)), ! is.na(Level)) %>%
+    
+    ggplot(aes(!!ensym(var), fill = Level)) +
+    
+    geom_bar(col = "black") +
+    
+    facet_grid(Year_numerical ~ .) + 
+    
+    scale_x_discrete(drop = FALSE) + 
+    scale_fill_discrete(drop = FALSE) +
+    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
+    labs(title = "Student's Courses", x = NULL)
+
+}
+
+my_barplot_concentration(transcript, "Concentration")
+ggsave("concentration.jpeg", path = "Output/Plots", width = width, height = height)
+
+my_barplot_concentration(transcript, "Cluster")
+ggsave("Cluster.jpeg", path = "Output/Plots", width = width, height = height)
+

### 2019-04-23 conference figures.Rmd

---
title: "Figures for conference paper"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

load("Output/_catalogues_tmp_topic_model_tibble.RDATA")
load("Output/data_pillar_1.Rdata")

output_folder <- "Conference/Figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

```{r TM}
d     <- tb_topic_model
gamma <- d$Gamma[[1]]
beta  <- d$Beta[[1]]
```

```{r transcript}
set.seed(2019)

transcript <- d_transcript_augmented %>%

  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%

  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization

  sample_n(10) %>%

  arrange(`Academic Year`) %>%

  print
```

# Transcript

```{r fig_transcript}
transcript %>% 
  kable("latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  as_image(file = str_c(output_folder, "/transcript.pdf"))
```

# Beta

```{r plot_beta}
plot_beta <- function(topic = 1, sub = NULL){

  top <-  str_c("Topic ", topic)

  beta %>%
    filter(topic == top) %>% 
    top_n(10, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder(term, beta), y = beta)) +

    coord_flip() +

    labs(title = str_c("Main Terms of ", top),
         subtitle = sub,
         x = "Terms",
         y = "Beta"
    )

  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

}
```

```{r fig_beta}
# topic 1: engineering",
plot_beta(1, sub = "Topic 1 corresponds to the theme of engineering")
# topic 9: computer science, topic 
# Topic 20: psychology
# topic 25: history
# topic 26: literature 
```

# Gamma

```{r plot_gamma}
plot_gamma <- function(course = "COR1002", sub = NULL, course_title = course){

  gamma %>%
    filter(document == course) %>% 
    top_n(10, gamma) %>%

    ggplot() +
    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +

    coord_flip() +

    labs(title    = str_c("Main Topics of Course ", course_title),
         subtitle = sub,
         x = "Topics",
         y = "Gamma"
         )

  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
         width = plot_width, height = plot_height)

}
```

```{r fig_gamma}
plot_gamma("HUM1014", sub = "HUM1014 is characterized by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")

plot_beta(43, sub = "Topic 43 corresponds to the theme of philosophy")

plot_beta(26, sub = "Topic 26 corresponds to the theme of literature")
```

### 2019-04-24 conference figures.Rmd

@@
 load("Output/data_pillar_1.Rdata")
+load("Output/d_text.RDATA")
 
@@
 
-```{r transcript}
+```{r student_data}
 set.seed(2019)
 
-transcript <- d_transcript_augmented %>%
+student_data <- d_transcript_augmented %>%
 
@@
 
-# Transcript
+```{r}
+course_data <- d_text$catalogues %>%
 
-```{r fig_transcript}
-transcript %>% 
+  slice(50005:50014) %>%
+
+  select(`Course ID`, `Course Title`, Department = department, word) 
+```
+
+# Student data
+
+```{r fig_student_data}
+student_data %>% 
   kable("latex", booktabs = TRUE) %>%
   kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/transcript.pdf"))
+  as_image(file = str_c(output_folder, "/student_data.pdf"))
+```
+
+# Course data
+
+```{r fig_course_data}
+course_data %>%
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  as_image(file = str_c(output_folder, "/course_data.pdf"))
 ```

### 2019-04-24 conference figures.Rmd
flow chart

@@
 library(kableExtra)
+library(DiagrammeR)
 
@@
 ```
+
+# Flow chart
+
+```{r}
+test <- grViz("digraph flowchart {
+
+      node [fontname = Helvetica, shape = rectangle]
+
+      # Input Data
+      subgraph cluster0 {
+      label = 'Input Data';
+      style = filled;
+		  color = lightgrey;
+		  node [style = filled, color = black, fillcolor = white];
+      CD [label = 'Course Data']
+      SD [label = 'Student Data']
+      }
+
+      # User Input
+      subgraph cluster1 {
+      label = 'User Input';
+      style = filled;
+		  color = coral;
+		  node [style = filled, color = black, fillcolor = white];
+      ID [label = 'Student ID']
+      KW [label = 'Selected Key Words']
+      CS [label = 'Selected Courses']
+      }
+
+      # Ouput
+      subgraph cluster2 {
+      label = 'System Output';
+      style = filled;
+		  color = lightCyan;
+		  node [style = filled, color = black, fillcolor = white];
+      SUG [label = 'Course Suggestions']
+      WAR [label = 'Warnings \n and Preparatory Coursework']
+      }
+
+      # Intermediate nodes
+      node [color = black]
+      TM [label = 'Topic Model']
+      TE [label = 'Student큦 Topic Expertise']
+      AI [label = 'Student큦 Academic Interests']
+      AP [label = 'Student큦 Academic Performance']
+      PM [label = 'Predictive Models']
+      GP [label = 'Grade Prediction']
+      TR [label = 'Student큦 Transcript']
+
+      # edges
+      {TE, KW} -> AI; 
+      {ID, SD} -> TR;
+      TR -> AP;
+      {TR, TM} -> TE;
+      {PM, TE, AP, CS} -> GP;
+      GP -> WAR;
+
+      edge[label = 'LDA']
+      CD -> TM;
+
+      edge[label = 'Lasso']
+      SD -> PM;
+
+      edge[label = 'KL distance']
+      {TM, AI} -> SUG
+      }
+      ")
+
+# Save by hand
+# image format: JPEG
+# Width: 626
+# Check Maintain aspect ratio
+# File name: Conference/Figures/Flowchart
+```

### 2019-04-24 conference figures.Rmd
update flowchart

@@
 ```{r}
-test <- grViz("digraph flowchart {
+grViz("digraph flowchart {
 
@@
 		  node [style = filled, color = black, fillcolor = white];
+      rank = same;
       SUG [label = 'Course Suggestions']
-      WAR [label = 'Warnings \n and Preparatory Coursework']
+      WAR [label = 'Warnings']
+      PRE [label = 'Preparatory Coursework']
       }
@@
       TR [label = 'Student큦 Transcript']
+      x [shape=circle,width=.01,height=.01,label='']
 
       # edges
+
+      WAR SUG PRE [ group = 1 ]
+
       {TE, KW} -> AI; 
@@
       GP -> WAR;
+		  {TM, PM, WAR} -> PRE;
 
-      edge[label = 'LDA']
+      edge[label = 'LDA', decorate = TRUE]
       CD -> TM;
@@
 
-      edge[label = 'KL distance']
-      {TM, AI} -> SUG
+      edge[label = '']
+      {TM, AI} -> x [arrowhead=none]
+      edge[label = 'KL distance', decorate = TRUE]
+      x -> SUG;
+
       }

### 2019-04-24 Pillar 2 - Tmp Topic Modeling.Rmd

@@
 #Save
-save(tb_topic_model, file = paste("./Output/", which_texts, "tmp_topic_model_tibble.RDATA", sep = "_"))
+save(tb_topic_model, file = paste("./Output/", which_texts, "_tmp_topic_model_tibble.RDATA", sep = ""))
 
@@
 #plot_evaluation("manuals")
+```
+##Best model
+We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
+```{r best model}
+load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted
+
+catalogue_dtm <- tb_topic_model$DTM[[1]]
+catalogue_lda <- tb_topic_model %>% filter(n_topic == "40") %>% pull(Model) %>%.[[1]]
+
+best_lda <- LDA(x = catalogue_dtm, 
+                model = catalogue_lda, 
+                control =  list(
+                  nstart = 50,
+                  seed   = 1 : 50, #must have length nstart
+                  best   = TRUE,
+                  burnin = 100,
+                  iter   = 10000,
+                  thin   = 2000) 
+                )
 ```

### 2019-04-25 conference figures.Rmd
topic expertise

@@
 ```
+
+# Topic Expertise
+```{r}
+transcript <- tibble(Course    = paste("Course", 1:3),
+                     Grade     = c(6  , 9  , 2.5))
+
+gamma <- tibble(Course    = paste("Course", 1:3),
+                `Topic 1` = c(0  , 0.2, 0.6),
+                `Topic 2` = c(0.4, 0.2, 0.3),
+                `Topic 3` = c(0  , 0.2, 0  ),
+                `Topic 4` = c(0.4, 0.2, 0.1),
+                `Topic 5` = c(0.2, 0.2, 0  ))
+
+df1 <- gamma %>% 
+  gather(key = Topic, value = gamma, -Course) %>% 
+  arrange(Course) %>%
+
+  left_join(transcript, by = "Course") %>%
+  mutate(contribution = Grade/10 * gamma)
+
+topic_expertise <- df1 %>%
+  select(-gamma, - Grade) %>% 
+  spread(key = Topic, value = contribution)
+
+# Table
+
+transcript %>% 
+  mutate(Grade = str_c(Grade, "/10")) %>%
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))
+
+gamma %>% 
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))
+
+topic_expertise %>% 
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))
+
+# Plot
+df1 %>% 
+  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
+  geom_col() +
+  labs(x = "Topics", y = "Topic Expertise", title = "Course Contribution towards Topic Expertise")
+
+ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
+       width = plot_width, height = plot_height)
+```

### 2019-04-25 conference figures.Rmd
align the two input clusters

@@
 
-      # Input Data
-      subgraph cluster0 {
-      label = 'Input Data';
+      subgraph cluster_input {
+      label = '';
+      style = filled;
+		  color = white;
+
+      subgraph cluster_input_data {
+      label = 'Data';
       style = filled;
@@
 
-      # User Input
-      subgraph cluster1 {
+      subgraph cluster_input_user {
       label = 'User Input';
@@
 
+      }
+
+      subgraph cluster_inter_first{
+      label = '';
+      style = filled;
+		  color = white;
+      TE [label = 'Topic Expertise']
+      AP [label = 'Academic Performance']
+      }
+
+      subgraph cluster_inter_last{
+      label = '';
+      style = filled;
+		  color = white;
+      GP [label = 'Grade Prediction']
+      AI [label = 'Student´s Academic Interests']
+      }
+
       # Ouput
-      subgraph cluster2 {
+      subgraph cluster_ouput {
       label = 'System Output';
@@
       TM [label = 'Topic Model']
-      TE [label = 'Student큦 Topic Expertise']
-      AI [label = 'Student큦 Academic Interests']
-      AP [label = 'Student큦 Academic Performance']
       PM [label = 'Predictive Models']
-      GP [label = 'Grade Prediction']
-      TR [label = 'Student큦 Transcript']
-      x [shape=circle,width=.01,height=.01,label='']
+      TR [label = 'Student´s Transcript']
+
+      # Invisible node
+      node [shape = circle, width = .01, height = .01, label = '']
+      x1 x2
 
@@
 
-      WAR SUG PRE [ group = 1 ]
-
-      {TE, KW} -> AI; 
+      SD -> AP;
+      {SD, TM} -> TE;
+      {TR, KW} -> AI;
       {ID, SD} -> TR;
-      TR -> AP;
-      {TR, TM} -> TE;
-      {PM, TE, AP, CS} -> GP;
+      {PM, CS, TR} -> GP;
       GP -> WAR;
@@
 
-      edge[label = 'Lasso']
-      SD -> PM;
+      edge[label = '']
+      {AP, TE} -> x2 [arrowhead = none]
+      edge[label = ' Lasso', decorate = TRUE]
+      x2 -> PM;
 
       edge[label = '']
-      {TM, AI} -> x [arrowhead=none]
+      {TM, AI} -> x1 [arrowhead = none]
       edge[label = 'KL distance', decorate = TRUE]
-      x -> SUG;
+      x1 -> SUG;
 

### 2019-04-25 conference figures.Rmd
rescale 2 figures (2 beta distrib)

@@
 ```{r plot_beta}
-plot_beta <- function(topic = 1, sub = NULL){
+plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){
 
@@
 
+    theme(axis.text.y = element_text(size = 11)) +
+
     labs(title = str_c("Main Terms of ", top),
@@
   ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
+         width = plot_width / resize_factor, height = plot_height / resize_factor)
 
@@
 ```{r fig_gamma}
-plot_gamma("HUM1014", sub = "HUM1014 is characterized by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")
+plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")
 
-plot_beta(43, sub = "Topic 43 corresponds to the theme of philosophy")
+resize_factor <- 1.6
 
-plot_beta(26, sub = "Topic 26 corresponds to the theme of literature")
+plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)
+
+plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
 ```
@@
 		  color = white;
+      AP [label = 'Academic Performance']
+      TR [label = 'Student´s Transcript']
       TE [label = 'Topic Expertise']
-      AP [label = 'Academic Performance']
       }
@@
       PM [label = 'Predictive Models']
-      TR [label = 'Student´s Transcript']
 
@@
       edge[label = '']
-      {AP, TE} -> x2 [arrowhead = none]
+      {AP, TE} -> x1 [arrowhead = none]
       edge[label = ' Lasso', decorate = TRUE]
-      x2 -> PM;
+      x1 -> PM;
 
       edge[label = '']
-      {TM, AI} -> x1 [arrowhead = none]
+      {TM, AI} -> x2 [arrowhead = none]
       edge[label = 'KL distance', decorate = TRUE]
-      x1 -> SUG;
+      x2 -> SUG;
 

### 2019-04-25 conference figures.Rmd
CV figure

@@
 load("Output/d_text.RDATA")
+load("Output/df_logLike_catalogue.RDATA")
+load("Output/CV.RDATA")
 
@@
   as_image(file = str_c(output_folder, "/course_data.pdf"))
-```
-
-# Beta
-
-```{r plot_beta}
-plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){
-
-  top <-  str_c("Topic ", topic)
-
-  beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
-
-    coord_flip() +
-
-    theme(axis.text.y = element_text(size = 11)) +
-
-    labs(title = str_c("Main Terms of ", top),
-         subtitle = sub,
-         x = "Terms",
-         y = "Beta"
-    )
-
-  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
-         width = plot_width / resize_factor, height = plot_height / resize_factor)
-
-}
-```
-
-```{r fig_beta}
-# topic 1: engineering",
-plot_beta(1, sub = "Topic 1 corresponds to the theme of engineering")
-# topic 9: computer science, topic 
-# Topic 20: psychology
-# topic 25: history
-# topic 26: literature 
-```
-
-# Gamma
-
-```{r plot_gamma}
-plot_gamma <- function(course = "COR1002", sub = NULL, course_title = course){
-
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-
-    coord_flip() +
-
-    labs(title    = str_c("Main Topics of Course ", course_title),
-         subtitle = sub,
-         x = "Topics",
-         y = "Gamma"
-         )
-
-  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-
-}
-```
-
-```{r fig_gamma}
-plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")
-
-resize_factor <- 1.6
-
-plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)
-
-plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
 ```
@@
 
+# Model Selection (topic model)
+
+```{r}
+df_logLike_catalogue %>%
+  ggplot(aes(x = n_topic, y = LogLikelihood)) +
+  geom_vline(xintercept = 80, col = "red", alpha = 0.5, linetype = "dashed") +
+  geom_line() +
+
+  labs(title = "Model Selection", subtitle = "The maximum-likelihood model has 80 topics", x = "Number of Topics", y = "Log-Likelihood") +
+
+  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
+         width = plot_width, height = plot_height)
+```
+
+# Beta
+
+```{r plot_beta}
+plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){
+
+  top <-  str_c("Topic ", topic)
+
+  beta %>%
+    filter(topic == top) %>% 
+    top_n(10, beta) %>%
+
+    ggplot() +
+    geom_col(aes(x = reorder(term, beta), y = beta)) +
+
+    coord_flip() +
+
+    theme(axis.text.y = element_text(size = 11)) +
+
+    labs(title = str_c("Main Terms of ", top),
+         subtitle = sub,
+         x = "Terms",
+         y = "Beta"
+    )
+
+  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
+         width = plot_width / resize_factor, height = plot_height / resize_factor)
+
+}
+```
+
+```{r fig_beta}
+# topic 1: engineering",
+plot_beta(1, sub = "Topic 1 corresponds to the theme of engineering")
+# topic 9: computer science, topic 
+# Topic 20: psychology
+# topic 25: history
+# topic 26: literature 
+```
+
+# Gamma
+
+```{r plot_gamma}
+plot_gamma <- function(course = "COR1002", sub = NULL, course_title = course){
+
+  gamma %>%
+    filter(document == course) %>% 
+    top_n(10, gamma) %>%
+
+    ggplot() +
+    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
+
+    coord_flip() +
+
+    labs(title    = str_c("Main Topics of Course ", course_title),
+         subtitle = sub,
+         x = "Topics",
+         y = "Gamma"
+         )
+
+  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
+         width = plot_width, height = plot_height)
+
+}
+```
+
+```{r fig_gamma}
+plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")
+
+resize_factor <- 1.6
+
+plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)
+
+plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
+```
+
 # Topic Expertise
@@
 ```
+
+# CV
+```{r}
+fit_lasso %>%
+  ggplot(aes(y = cv_error, group = 1)) +
+  geom_boxplot() +
+  theme(axis.ticks.x = element_line(color = "white"),
+        axis.text.x = element_text(color = "white"),
+        panel.border = element_rect(color = "white"),
+        panel.grid = element_line(color = "white")
+        ) +
+
+  labs(title = "Distribution of Prediction Error", y = "Cross-Validation \n Mean Absolute Error")
+
+ggsave(filename = str_c("CV.jpeg"), path = output_folder,
+         width = plot_width/1.9, height = plot_height/1.2)
+
+fit_lasso %>%
+  summarize(Mean = mean(cv_error),
+            `Weighted mean` = weighted.mean(cv_error, n),
+            Median = median(cv_error),
+            `Standard Deviation` = sd(cv_error),
+            Minimum = min(cv_error),
+            Maximum = max(cv_error)) %>%
+  gather(key = x, value = y) %>% 
+  kable("latex", booktabs = TRUE, col.names = NULL) %>%
+  kable_styling(latex_options = c("striped", "scale_down")) %>%
+  as_image(file = str_c(output_folder, "/CV.pdf"))
+```

### 2019-04-26 conference figures.Rmd
shape of data boxes as cylinder

@@
 ```{r}
-grViz("digraph flowchart {
+grViz("digraph flowchart{
 
@@
 		  color = lightgrey;
-		  node [style = filled, color = black, fillcolor = white];
+		  node [style = filled, color = black, fillcolor = white, shape = cylinder];
       CD [label = 'Course Data']
@@
       node [shape = circle, width = .01, height = .01, label = '']
-      x1 x2
+      x1 x2 x3
 
@@
       GP -> WAR;
-		  {TM, PM, WAR} -> PRE;
+		  WAR -> PRE;
 
@@
 
+      edge[label = '']
+      {TM, PM} -> x3 [arrowhead = none]
+      edge[label = 'KL distance', decorate = TRUE]
+      x3 -> PRE;
+
       }
@@
 ```{r}
+max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]
+
 df_logLike_catalogue %>%
   ggplot(aes(x = n_topic, y = LogLikelihood)) +
-  geom_vline(xintercept = 80, col = "red", alpha = 0.5, linetype = "dashed") +
-  geom_line() +
+  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
+  geom_line(linetype = "dashed") +
+  geom_point() +
 

### 2019-04-29 App/Recommender System/server.R
Use kl distance

@@ -3,6 +3,7 @@ library(tidytext)
 library(stringr)
 library(hunspell) #for stemming
 library(glmnet)   #for grade prediction
+library(seewave)# KL distance
 
 
 #
@@ -375,7 +376,9 @@ function(input, output, session) {
   ###Set up
   use_past <- reactive({input$use_past})
  
-   # Helper function: Return student
+   # Helper functions:
+  
+  ##Return student
   student_courses <- function(d_student) {
     student_hist <- d_transcript %>%
         
@@ -386,7 +389,13 @@ function(input, output, session) {
         select(
           course = `Course ID`
         ) 
-    }
+  }
+  
+  ##KL distance
+  my_kl <- function(distribution, reference) {
+    kl.dist(reference, tibble(distribution), base = 2)[[1]]
+  }
+  
   
   #Reactive student function 
   student_past <- reactive({
@@ -426,11 +435,11 @@ function(input, output, session) {
 
     key_words            <- c(input$key_words, key_words_additional)
     
-    #Student profiles
+    #Student profiles align with courses
     student <- list()
     student$topic_score <- beta_distribution %>%
       
-      # Topic score
+      # Interest profile
       filter(
         term %in% key_words
       ) %>%
@@ -440,33 +449,35 @@ function(input, output, session) {
       summarize(
         topic_score = sum(beta)
       ) %>%
-      ungroup %>%
-      
-      # Course score
-      full_join(
-        gamma_distribution,
-        by = "topic"
-      ) %>%
-      group_by(
-        document
-      ) %>%
-      summarise(
-        course_score = sum(gamma * topic_score)
-      ) %>%
-      ungroup %>%
-      
+      ungroup %>% ############### NORMALIZE
+      mutate(student_interest = topic_score/sum(topic_score)) %>%
+      select(-topic_score) %>% 
+      full_join(gamma_distribution %>% 
+                  spread(key = document, value = gamma),
+                by = "topic")
+    
+    #KL distance
+    ref <- student$topic_score %>% select(student_interest)
+    
+    kl_dist <- student$topic_score %>% 
+      select(-topic) %>% 
+      map_dbl(my_kl, reference = ref) %>%
+      tibble(course = names(.), distance = .) %>%
+      arrange((distance))
+    
+    #recommendations
+    recommendations <- kl_dist %>% 
+      filter(course != "student_interest") %>%   
       # Recommendations
       top_n(
-        n  = 20,
-        wt = course_score
+        n  = -20,
+        wt = distance
[…]

### 2019-04-29 Pillar 2 - Tmp Topic Modeling.Rmd

--- 2019-04-23 Pillar 2 - Tmp Topic Modeling.Rmd
@@
 
-  nstart = 10,
-  seed   = 1 : 10, #must have length nstart
+  nstart = 20,
+  seed   = 1 : 20, #must have length nstart
   best   = TRUE,
 
-  burnin = 100,
-  iter   = 2000,
-  thin   = 2000
+  burnin = 1000,
+  iter   = 6000,
+  thin   = 100
 
@@
 ```{r LDA fit separate, cache = TRUE, eval = TRUE}
+
 #Timing
@@
 #Save
-save(tb_topic_model, file = paste("./Output/", which_texts, "tmp_topic_model_tibble.RDATA", sep = "_"))
+save(tb_topic_model, file = paste("./Output/", which_texts, "_tmp_topic_model_tibble.RDATA", sep = ""))
 
+```
+
+```{r time print, eval = T} 
+(took_how_long)
 ```
@@
 #plot_evaluation("manuals")
+```
+##Best model
+We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
+```{r best model, eval = F}
+load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted
+
+catalogue_dtm <- tb_topic_model$DTM[[1]]
+catalogue_lda <- tb_topic_model %>% filter(n_topic == "35") %>% pull(Model) %>%.[[1]]
+
+best_lda <- LDA(x = catalogue_dtm, 
+                model = catalogue_lda, 
+                control =  list(
+                  nstart = 50,
+                  seed   = 1 : 50, #must have length nstart
+                  best   = TRUE,
+                  burnin = 100,
+                  iter   = 10000,
+                  thin   = 2000) 
+                )
+
+save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
 ```

### 2019-04-30 conference figures.Rmd

@@
 
-      node [fontname = Helvetica, shape = rectangle]
+      fontname = Helvetica
+      size = 15
 
-      subgraph cluster_input {
-      label = '';
-      style = filled;
-		  color = white;
+      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]
 
-      subgraph cluster_input_data {
+      edge [fontname = Helvetica, decorate = TRUE]
+
+      subgraph cluster_data {
       label = 'Data';
@@
 		  color = lightgrey;
-		  node [style = filled, color = black, fillcolor = white, shape = cylinder];
+		  node [shape = cylinder];
       CD [label = 'Course Data']
@@
 		  color = coral;
-		  node [style = filled, color = black, fillcolor = white];
+
       ID [label = 'Student ID']
@@
 
-      }
+      subgraph cluster_model_fitting{
+      label = 'Model Fitting';
+      style = filled;
+		  color = LavenderBlush;
 
-      subgraph cluster_inter_first{
-      label = '';
-      style = filled;
-		  color = white;
+      TE [label = 'Topic Expertise']
       AP [label = 'Academic Performance']
-      TR [label = 'Student´s Transcript']
-      TE [label = 'Topic Expertise']
+
+      PM [label = 'Predictive Models']
+      x1 [shape = circle, width = .01, height = .01, label = '']
+      TM [label = 'Topic Model']
+
       }
@@
       subgraph cluster_inter_last{
-      label = '';
+      label = 'Intermediate Results';
       style = filled;
-		  color = white;
+		  color = Tan;
+
       GP [label = 'Grade Prediction']
@@
 		  color = lightCyan;
-		  node [style = filled, color = black, fillcolor = white];
-      rank = same;
+
       SUG [label = 'Course Suggestions']
@@
 
-      # Intermediate nodes
-      node [color = black]
-      TM [label = 'Topic Model']
-      PM [label = 'Predictive Models']
+      TR [label = 'Student´s Transcript']
 
       # Invisible node
-      node [shape = circle, width = .01, height = .01, label = '']
-      x1 x2 x3
+      x2 [shape = circle, width = .01, height = .01, label = '']
+      x3 [shape = circle, width = .01, height = .01, label = '']
 
@@
 
-      SD -> AP;
+      SD -> AP [weight = 2];
       {SD, TM} -> TE;
-      {TR, KW} -> AI;
-      {ID, SD} -> TR;
+      {TM, KW} -> AI;
+      ID -> TR;
       {PM, CS, TR} -> GP;
@@
 
-      edge[label = 'LDA', decorate = TRUE]
-      CD -> TM;
+      CD -> TM [label = '  LDA'];
 
-      edge[label = '']
       {AP, TE} -> x1 [arrowhead = none]
-      edge[label = ' Lasso', decorate = TRUE]
-      x1 -> PM;
+      x1 -> PM [label = '  Lasso'];
 
-      edge[label = '']
       {TM, AI} -> x2 [arrowhead = none]
-      edge[label = 'KL distance', decorate = TRUE]
-      x2 -> SUG;
+      x2 -> SUG [label = '  KL distance'];
 
-      edge[label = '']
       {TM, PM} -> x3 [arrowhead = none]
-      edge[label = 'KL distance', decorate = TRUE]
-      x3 -> PRE;
+      x3 -> PRE [label = '  KL distance'];
 
@@
 
-  labs(title = "Model Selection", subtitle = "The maximum-likelihood model has 80 topics", x = "Number of Topics", y = "Log-Likelihood") +
+  labs(title = "Model Selection", subtitle = str_c("The maximum-likelihood model has ", max_LL, " topics"), x = "Number of Topics", y = "Log-Likelihood") +
 

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
app_model using 65 topics

@@
 app_model <- app_topic_model %>%
-  filter(n_topic == 55)
+  filter(n_topic == 65)
 
@@
 save(app_topic_model, app_model, file = "App/Recommender System/data_topic_models.RDATA")
+save(app_model, file = "./Output/app_model.RDATA")
 ```

### 2019-04-30 test-app.R
using student expertise in app

@@ -11,7 +11,7 @@ load("./App/Recommender System/data_pillar_1.RDATA")
 load("./App/Recommender System/data_topic_models.RDATA") #contains app_model and full dataframe of topic models
 load("./App/Recommender System/rules_clean.RDATA")
 load("./App/Recommender System/grade_prediction.RDATA") 
-
+load("./App/Recommender System/student_TP.RDATA")
 ###Set up
 use_past <- T
 
@@ -28,9 +28,20 @@ student_courses <- function(d_student) {
     ) 
 }
 
+student_topics <- function(d_student){
+  
+   student_TP %>% filter(`Student ID` == d_student) %>% top_n(1, time) %>%
+    select(-time, -`Student ID`) %>%
+    gather(key = topic, value = weight) %>%
+    mutate(topic = str_replace(topic, "_", " "),
+    weight = weight/sum(weight))
+    
+}
+
 #Reactive student function 
 student_past <- student_courses("6113335")
 
+student_tp <- student_topics("6113335")
 
 #recommendations
   beta_distribution  <- app_model$Beta[[1]] 
@@ -56,17 +67,23 @@ student_past <- student_courses("6113335")
 
   kw_used <- app_model$kw[[1]] #is the same as in ui
   
-  with_guess <- student_past%>% 
-    left_join(gamma_distribution, by = c("course" = "document"))%>%
-    group_by(topic) %>%
-    summarise(topic_score = sum(gamma)) %>%
-    ungroup()%>%
-    arrange(desc(topic_score)) %>%
-    top_n(5, topic_score) %>%
+  with_guess <- student_tp %>% 
+    top_n(10, weight) %>%
     left_join(beta_distribution, by = "topic") %>%
-    group_by(term) %>%
-    summarize(topic_score = sum(beta)) %>%
-    top_n(100, topic_score) %>% pull(term)
+    group_by(topic) %>%
+    top_n(3, beta) %>% pull(term)
+  
+  # with_guess <- student_past%>% 
+  #   left_join(gamma_distribution, by = c("course" = "document"))%>%
+  #   group_by(topic) %>%
+  #   summarise(topic_score = sum(gamma)) %>%
+  #   ungroup()%>%
+  #   arrange(desc(topic_score)) %>%
+  #   top_n(5, topic_score) %>%
+  #   left_join(beta_distribution, by = "topic") %>%
+  #   group_by(term) %>%
[…]

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
65 topics

--- 2019-04-29 Pillar 2 - Tmp Topic Modeling.Rmd
@@
 We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
-```{r best model, eval = F}
+```{r best model, eval = T}
 load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted
@@
 catalogue_dtm <- tb_topic_model$DTM[[1]]
-catalogue_lda <- tb_topic_model %>% filter(n_topic == "35") %>% pull(Model) %>%.[[1]]
+catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]
 

### 2019-04-30 Pillar 1 - Topic Profile.Rmd

@@
 ```{r load, cache.lazy = TRUE}
-load("App/Recommender System/topic_model_gb.RDATA")
+#load("App/Recommender System/topic_model_gb.RDATA")
+load("App/Recommender System/data_topic_models.RDATA")
 load("Output/data_pillar_1.RDATA")
@@
 ```{r gamma_spread}
-gamma        <- topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
+gamma        <- app_model$Gamma %>% .[[1]] %>% mutate(topic = topic %>% str_replace(" ", "_"))  #topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
 gamma_spread <- gamma %>% spread(topic, gamma)
 
-beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
+beta <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta) #topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
 ```
@@
 Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).
+#Save
+```{r save student_TP}
+save(student_TP, file = "./App/Recommender System/student_TP.RDATA")
+```
 
@@
 ```{r}
+save(fit_lasso, file = "Output/CV.RDATA")
+```
+
+```{r}
 hist(fit_lasso$cv_error)
@@
 ```{r}
-beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
+beta <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
+#beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
 

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
best model formatting

--- 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
@@
 ```
+##Best model pass to app
+```{r}
+load("./Output/catalogues_tmp_topic_model_tibble.RDATA")
+load("./Output/catalogues_best_model.RDATA")
+
+best_model <- tibble( 
+  n_topic = 65
+  ) %>%
+
+  mutate(Origin     = "catalogues",
+         `Topic ID` = paste(Origin, n_topic, sep = "_"),
+
+         #Document Term Matrix
+         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+
+         #Fit Model
+         Model  = list(best_lda),
+
+         #Gamma distribution
+         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+
+         #Beta distribution
+         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
+
+         #Perplexity
+         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
+
+         #Loglikelihood
+         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
+
+         #
+         ##Inspect
+
+         #top words per topic
+         top_terms_topic = map(Beta, .f = get_top_terms_topic),
+
+         #top topics per course
+         top_topic_course = map(Gamma, .f = get_top_topics_course),
+
+         #Select keywords
+         kw = map(Beta, .f = get_kw)
+         )
+
+```
 ##Different alphas and delta (prior of term distributions over topics)
@@
 ```{r crop and clean TM for App, eval = T}
-app_topic_model <- tb_topic_model %>% 
+app_topic_model <- best_model %>% #tb_topic_model %>% 
   select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%

### 2019-04-30 App/Recommender System/server.R
Recommender System use student expertise

@@ -11,7 +11,8 @@ library(seewave)# KL distance
 load("data_pillar_1.RDATA")
 load("data_topic_models.RDATA") #contains app_model and full dataframe of topic models
 load("rules_clean.RDATA")
-load("grade_prediction.RDATA") 
+load("grade_prediction.RDATA")
+load("student_TP.RDATA")
 
 course_all <- app_model$`All Courses`[[1]]
 course_advanced <- course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
@@ -535,12 +536,6 @@ function(input, output, session) {
       left_join(beta_distribution, by = "topic") %>%
       group_by(topic) %>%
       top_n(3, beta) %>% pull(term)
-      # top_n(5, weight) %>%
-      # left_join(beta_distribution, by = "topic") %>%
-      # #group_by(term) %>%
-      # #summarize(topic_score = sum(beta)) %>%
-      # #top_n(100, topic_score) %>% 
-      # pull(term)
     
     kw_select <- if(use_past()){
       intersect(with_guess, kw_used)

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
saving correct file

--- 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
@@
 
-app_model <- app_topic_model %>%
-  filter(n_topic == 65)
+app_model <- app_topic_model #%>%
+  #filter(n_topic == 65)
 
@@
 ```{r app files, eval = T}
-save(app_topic_model, app_model, file = "App/Recommender System/data_topic_models.RDATA")
+save(app_model, file = "App/Recommender System/data_topic_models.RDATA")
 save(app_model, file = "./Output/app_model.RDATA")

### 2019-04-30 App/Recommender System/server.R
app_model.R change name of file to keep consistency across pillars

@@ -9,7 +9,7 @@ library(seewave)# KL distance
 #
 #General set up ---------------------------------------------------------------------------------
 load("data_pillar_1.RDATA")
-load("data_topic_models.RDATA") #contains app_model and full dataframe of topic models
+load("app_model.RDATA") #contains app_model and full dataframe of topic models
 load("rules_clean.RDATA")
 load("grade_prediction.RDATA")
 load("student_TP.RDATA")

### 2019-04-30 Pillar 1 - Topic Profile.Rmd
correct topic model input file

@@
 ```{r load, cache.lazy = TRUE}
-#load("App/Recommender System/topic_model_gb.RDATA")
-load("App/Recommender System/data_topic_models.RDATA")
+load("App/Recommender System/app_model.RDATA")
 load("Output/data_pillar_1.RDATA")

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd

@@
 ```{r app files, eval = T}
-save(app_model, file = "App/Recommender System/data_topic_models.RDATA")
+save(app_model, file = "App/Recommender System/app_model.RDATA")
 save(app_model, file = "./Output/app_model.RDATA")

### 2019-04-30 conference figures.Rmd

@@
 
-load("Output/_catalogues_tmp_topic_model_tibble.RDATA")
+load("Output/catalogues_best_model.RDATA")
 load("Output/data_pillar_1.Rdata")
@@
 ```{r TM}
-d     <- tb_topic_model
-gamma <- d$Gamma[[1]]
-beta  <- d$Beta[[1]]
+d     <- best_lda
+gamma <- best_lda$Gamma
+beta  <- best_lda$Beta
 ```

### 2019-04-30 conference figures.Rmd

@@
 
+# Set up
+
 ```{r setup, include = FALSE}
@@
 
-load("Output/catalogues_best_model.RDATA")
+load("Output/app_model.RDATA")
 load("Output/data_pillar_1.Rdata")
@@
 ```{r TM}
-d     <- best_lda
-gamma <- best_lda$Gamma
-beta  <- best_lda$Beta
+gamma <- app_model$Gamma[[1]]
+beta  <- app_model$Beta[[1]]
 ```
@@
 
-  select(`Course ID`, `Course Title`, Department = department, word) 
+  select(`Course ID`, `Course Title`, Department = department, word) %>%
+
+  print
 ```
@@
 
-  labs(title = "Model Selection", subtitle = str_c("The maximum-likelihood model has ", max_LL, " topics"), x = "Number of Topics", y = "Log-Likelihood") +
+  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +
 
@@
 ```{r plot_beta}
-plot_beta <- function(topic = 1, sub = NULL, resize_factor = 1){
+plot_beta <- function(topic = 1, resize_factor = 1){
 
@@
 
-    labs(title = str_c("Main Terms of ", top),
-         subtitle = sub,
+    labs(title = str_c("Topic ", topic),
          x = "Terms",
@@
 ```{r fig_beta}
-# topic 1: engineering",
-plot_beta(1, sub = "Topic 1 corresponds to the theme of engineering")
-# topic 9: computer science, topic 
-# Topic 20: psychology
-# topic 25: history
-# topic 26: literature 
+plot_beta(1)
 ```
@@
 ```{r plot_gamma}
-plot_gamma <- function(course = "COR1002", sub = NULL, course_title = course){
+plot_gamma <- function(course = "COR1002"){
 
@@
 
-    labs(title    = str_c("Main Topics of Course ", course_title),
-         subtitle = sub,
+    labs(title = course,
          x = "Topics",
@@
 ```{r fig_gamma}
-plot_gamma("HUM1014", sub = "HUM1014 is dominated by topics 43 (philosophy) and 26 (literature)", course_title = "HUM1014 Great Novels 1850 - Present")
+plot_gamma("COR1004")
 
@@
 
-plot_beta(43, sub = "Theme of philosophy", resize_factor = resize_factor)
-
-plot_beta(26, sub = "Theme of literature", resize_factor = resize_factor)
+plot_beta(4, resize_factor = resize_factor)
+plot_beta(19, resize_factor = resize_factor)
 ```
@@
 ```{r}
-transcript <- tibble(Course    = paste("Course", 1:3),
+courses <- paste("Course", 1 : 3)
+
+transcript <- tibble(Course    = courses,
                      Grade     = c(6  , 9  , 2.5))
 
-gamma <- tibble(Course    = paste("Course", 1:3),
-                `Topic 1` = c(0  , 0.2, 0.6),
-                `Topic 2` = c(0.4, 0.2, 0.3),
-                `Topic 3` = c(0  , 0.2, 0  ),
-                `Topic 4` = c(0.4, 0.2, 0.1),
-                `Topic 5` = c(0.2, 0.2, 0  ))
+gamma <- tibble(Course    = courses,
+                `Topic 1` = c(0  , 0.2, 0  ),
+                `Topic 2` = c(0.7, 0.2, 0.4),
+                `Topic 3` = c(0.2, 0.2, 0.2),
+                `Topic 4` = c(0.1, 0.2, 0.1),
+                `Topic 5` = c(0  , 0.2, 0.2))
 
@@
   geom_col() +
-  labs(x = "Topics", y = "Topic Expertise", title = "Course Contribution towards Topic Expertise")
+  labs(x = "Topics", y = "Topic Expertise")
 
@@
   geom_boxplot() +
-  theme(axis.ticks.x = element_line(color = "white"),
-        axis.text.x = element_text(color = "white"),
+  theme(axis.ticks.y = element_line(color = "white"),
+        axis.text.y  = element_text(color = "white"),
         panel.border = element_rect(color = "white"),
@@
 
-  labs(title = "Distribution of Prediction Error", y = "Cross-Validation \n Mean Absolute Error")
+  labs(y = "Cross-Validation Mean Absolute Error") +
+  coord_flip()
 
 ggsave(filename = str_c("CV.jpeg"), path = output_folder,
-         width = plot_width/1.9, height = plot_height/1.2)
+         width = plot_width/1.5, height = plot_height/3.5)
 

### 2019-05-01 App/Recommender System/server.R
minor change

@@ -398,7 +398,7 @@ function(input, output, session) {
       #mutate_at(vars(flag_red, flag_orange, flag_green), funs(ifelse(.,., " ")))%>%
       #select(-cv) %>%
      left_join(preparatory, by = "target") %>%
-      rename(Course = target, `Preparatory Coursework` = Preparation)
+      rename(Course = target, `Preparatory Courses` = Preparation)
   
   })
   

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
cleaning pillar 2

--- 2019-04-04 Pillar 2 - Topic Modeling.Rmd
@@
 
-##Functions for internal faceting
+##Loading data
+We load a list `d_text` with two tibbles of textual data for catalogues and manuals.
+That is, for $catalogues and $manuals we have a tibble with the following columns: `Course ID`, `year`, `word_original`, `word`.
+
+We also load the environment `Output/data_pillar_2.RDATA` containing the data sets`d_course` and `d_transcript` that we will need to prepare some imputs for our App.
+```{r import data, eval = TRUE}
+#load
+load("./Output/d_text.RDATA")
+load("./Output/data_pillar_2.RDATA") #used for app
+```
+##Helpers
+###Preparation of course_title vector
+```{r course titles, eval = TRUE}
+#Clean titles
+course_titles <-  d_text$catalogues %>%
+  select(`Course ID`, `Course Title`, department) %>% 
+  distinct
+
+empty_titles <- course_titles %>% filter(`Course Title` == "")
+```
+####Uniform titles
+We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title.
+```{r attatch titles}
+uniform_course_labels <- course_titles %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
+                                              T ~ `Course Title`),
+                         `Course ID` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
+                                                 T ~ "unknown"),
+                         `Course Title` = c_title
+                         ) %>% select(-c_title)
+```
+###Functions for internal faceting
 ```{r function reorder_within & co., echo = FALSE, eval = TRUE}
@@
 }
-```
-
-##Loading data
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $catalogues, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).
-
-For `d_text` we keep only the most recent year.
-```{r import data, eval = TRUE}
-#load
-#load("output/data_pillar_2.RDATA")
-load("./Output/d_text.RDATA")
 ```
@@
 ###Cast DTM
-The function `my_cast_dtm` casts our dataframes into a DTM.
+The function `my_cast_dtm` casts our dataframes (catalogues and manuals) into a DTM.
 ```{r my_cast_dtm, eval = TRUE}
+#Function
 my_cast_dtm <- function(data) data %>%
@@
 
+#Application
 d_cast <- d_text %>% map(my_cast_dtm)
 
+#Clean workspace
 rm(my_cast_dtm)
@@
 ###Controls
-The control parameters we use are:
+The control parameters we will use to train our LDA model are:
 ```{r controls, eval = TRUE}
@@
 
-  nstart = 10,
-  seed   = 1 : 10,
+  nstart = 20,
+  seed   = 1 : 20, #must have length nstart
   best   = TRUE,
 
-  burnin = 100,
-  iter   = 2000,
+  burnin = 1000,
+  iter   = 6000,
   thin   = 100
@@
 ```
-The control parameters we use for fast testing are:
-```{r fast control}
+
+We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
+```{r fast control, eval = TRUE}
 my_control_fast <- list(
@@
 ```
-
-##Ideal Number of Topics Package Test
-To decide the number of topics to discover, we run three different tests.
-###Function
-The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
-```{r function my_FindTopicsNumber }
-my_FindTopicsNumber <- function(data_cast, n_topics){
-
-  FindTopicsNumber(
-
-  dtm = data_cast,
-  topics = n_topics,
-  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
-  method = "Gibbs",
-  control = my_control,
-  mc.cores = 4L
-
-  )
-
-}
-```
-###Train
-```{r package test on topics, cache = TRUE}
-#Start timer
-start.time <- Sys.time()
-
-#
-##apply my_FindTopicsNumber
-result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))
-
-#Stop timer
-end.time <- Sys.time()
-print(end.time - start.time)
-
-#
-##Save results
-#save(result_topic_test,
-#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
-```
-Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
-* Overview:     22min 
-* Description:  11min 
-* Manuals:      5.5hrs
-
-###Graph 
-We examine the result of the experiment by plotting them on a graph.
-```{r LDA number topics plot}
-#load("Output/LDA_ntopics.RDATA")
-
-result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
-```
-From the results we see that the ideal number of topics is somewhere between 35 and 40.
 
@@
 
-###Functions for models (extract_dtm, get_distributions, perplexity)
+###Extracting functions
 The following functions are used as input in a map to compute and evaluate topic models. 
-```{r getting gamma and beta, eval = TRUE}
+```{r extracting functions, eval = TRUE}
 #extract dtm
@@
 ```{r inspection functions, eval = TRUE}
- # get_top_match <- function(d_distribution){
- # 
- #  #save user input as string
- #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
- #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
- # 
- #  #Compute Case (Beta or Gamma, respectively)
- #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
- #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
- #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
- # 
- #  #
- #  ## DATA
- #  data.frame(d_distribution) %>%
- #    group_by(!!sym(grouping)) %>%
- #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
- #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
- #    group_by(!!sym(grouping)) %>%
- #    summarise(top = list(!!sym(objects_to_group)))
- # }
 
@@
 ```
+
 ###Training Models
-We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
-```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_numbers <- seq(from = 5, to = 15, by = 5)
+The function `train_topic_model` takes the type of text input ("catalogues", "manuals", c("catalogues", "manuals")) and number of topics to be trained.
+It fits an LDA model on the data and saves the output as a tibble where
+each row corresponds to a number of topics per text input (e.g.
+catalogues_50).
+It saves the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words that will be used for the app.
 
-test_topic_model <- tibble( #CHANGE NAME TO: topic_model
+```{r function train_model, eval = TRUE}
+train_topic_model <- function(which_text, topic_numbers){
+  topic_model <- tibble( 
+    n_topic = rep(topic_numbers, each = length(d_text)) 
+    ) %>%
 
-  #repeat each topic number twice (once for catalogues and once for manual)
-  n_topic = rep(topic_numbers, each = 2) # from = 5, to = 250, by = 5
-
-  ) %>%
-  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
+    mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)), 
            `Topic ID` = paste(Origin, n_topic, sep = "_"),
@@
            #Document Term Matrix
-         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+           DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%
 
+  filter(Origin %in% which_texts) %>% ######################## was previously == instead of %in%
+
+  mutate(
          #Fit Model
@@
          )
+}
 
+```
+
+We apply the function separately and take the time it takes to fit the model.
+
+Note: The manuals take a long time to run, we keep the trainings of catalogues and manuals separate so that changes in one do not require retraining the other. 
+####Catalogues
+```{r LDA fit catalogues, cache = TRUE, eval = TRUE}
+#
+## Catalogues
+
+#Input vectors
+which_texts <- "catalogues"
+topic_numbers <-seq(from = 5, to = 150, by = 5)
+
+#Intitial time
+initial_time <- Sys.time()
+
+#Application to catalogues
+catalogues_topic_model <- train_topic_model(which_texts, topic_numbers)
+
+#Final Time
+final_time <- Sys.time()
+took_how_long <- final_time - initial_time
+print(paste(which_texts, took_how_long, sep =" "))
+
+#Save
+save(catalogues_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
+```
+
+####Manuals
+```{r LDA fit manuals, cache = TRUE, evel = TRUE }
+#
+## Manuals
+
+#Input vectors
+which_texts <- "manuals"
+
+#Intitial time
+initial_time <- Sys.time()
+
+#Application to catalogues
+manuals_topic_model <- train_topic_model(which_texts, topic_numbers)  #number of topics stayed the same cause we want to merge them.
+
+#Final Time
+final_time <- Sys.time()
+took_how_long <- final_time - initial_time
+print(paste(which_texts, took_how_long, sep =" "))
+
+#Save
+save(manuals_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
+```
+
+```{r clean workspace functions, eval = TRUE}
 # Clean workspace
-
 # rm(extract_dtm, get_distributions, my_perplexity,
 #    get_top_terms_topic, get_top_topics_course, get_kw)
+```
 
+If we trained separately but with the same number of topics, and wish to merge and save them:
+```{r merge if trained separately, eval = TRUE}
+cata <- catalogues_topic_model$n_topic
+man  <- manuals_topic_model$n_topic
+
+tb_topic_model <- tibble()
+
+if(all(cata == man)){
+  tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
+}
+
+save(tb_topic_model, file = "./Output/full_topic_model_tibble.RDATA")
 ```
@@
 #Function
-plot_evaluation <- function(origin){
+plot_evaluation <- function(origin, data = tb_topic_model){
 
   #data
-  test_topic_model %>%
+  data %>%
 
@@
 
-##Saving model_data:
-We save our tibble with all the information.
-```{r save, eval = T}
-save(test_topic_model, file = "Output/test_topic_model.RDATA" )
-# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
+##Best model
+We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with more burns and iterations
+```{r best model, eval = T}
+catalogues_tm <- tb_topic_model %>% fil
+catalogue_dtm <- tb_topic_model$DTM[[1]]
+catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]
+
+best_lda <- LDA(x = catalogue_dtm, 
+                model = catalogue_lda, 
+                control =  list(
+                  nstart = 50,
+                  seed   = 1 : 50, #must have length nstart
+                  best   = TRUE,
+                  burnin = 100,
+                  iter   = 10000,
+                  thin   = 2000) 
+                )
+
+save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
+```
+##Best model pass to app
+```{r}
+load("./Output/catalogues_tmp_topic_model_tibble.RDATA")
+load("./Output/catalogues_best_model.RDATA")
+
+best_model <- tibble( 
+  n_topic = 65
+  ) %>%
+
+  mutate(Origin     = "catalogues",
+         `Topic ID` = paste(Origin, n_topic, sep = "_"),
+
+         #Document Term Matrix
+         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
+
+         #Fit Model
+         Model  = list(best_lda),
+
+         #Gamma distribution
+         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
+
+         #Beta distribution
+         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
+
+         #Perplexity
+         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
+
+         #Loglikelihood
+         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
+
+         #
+         ##Inspect
+
+         #top words per topic
+         top_terms_topic = map(Beta, .f = get_top_terms_topic),
+
+         #top topics per course
+         top_topic_course = map(Gamma, .f = get_top_topics_course),
+
+         #Select keywords
+         kw = map(Beta, .f = get_kw)
+         )
+
 ```

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
simplify merge of catalogues and manuals

@@
 
-If we trained separately but with the same number of topics, and wish to merge and save them:
+If we trained separately and wish to merge into a single tibble: 
 ```{r merge if trained separately, eval = TRUE}
-cata <- catalogues_topic_model$n_topic
-man  <- manuals_topic_model$n_topic
-
 tb_topic_model <- tibble()
 
-if(all(cata == man)){
+if(exists("manuals_topic_model") && exists("catalogues_topic_model")){
   tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
+} else  if(exists("catalogues_topic_model")){
+  tb_topic_model <- catalogues_topic_model 
+  } else if (exists("manuals_topic_model")){
+    tb_topic_model <- catalogues_topic_model
 }
@@
 
-##Plots - Model Evaluation
+##Plots - Model Evaluation CHANGE TO CONFERENCE CODE
 To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
@@
 ##Best model
-We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with more burns and iterations
+We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
 ```{r best model, eval = T}
-catalogues_tm <- tb_topic_model %>% fil
+catalogues_tm <- tb_topic_model %>% filter()
 catalogue_dtm <- tb_topic_model$DTM[[1]]

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
clean Pillar 2

@@
 ```
-####Uniform titles
+####Uniform course labels
 We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title.
@@
 
-##Plots - Model Evaluation CHANGE TO CONFERENCE CODE
+##Model Evaluation CHANGE TO CONFERENCE CODE
+###Plots
 To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
@@
 
+###Value
+```{r best number of topics extraction}
+n_topics_best_manuals    <- manuals_topic_model    %>% top_n(1, LogLikelihood) %>% pull(n_topic)
+n_topics_best_catalogues <- catalogues_topic_model %>% top_n(1, LogLikelihood) %>% pull(n_topic)
+```
+
 ##Best model
 We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
-```{r best model, eval = T}
-catalogues_tm <- tb_topic_model %>% filter()
-catalogue_dtm <- tb_topic_model$DTM[[1]]
-catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]
+###catalogues best model
+```{r best catalogues tm, eval = T}
+catalogues_tm <- tb_topic_model %>% filter(Origin == "catalogues")
 
-best_lda <- LDA(x = catalogue_dtm, 
+catalogue_dtm <- catalogues_tm$DTM[[1]]
+
+catalogue_lda <- catalogues_tm %>% filter(n_topic == n_topics_best_catalogues) %>% pull(Model) %>%.[[1]]
+
+#Train best model 
+catalogues_best_lda <- LDA(x = catalogue_dtm, 
                 model = catalogue_lda, 
@@
 
-save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
+save(catalogues_best_lda, file = "./Output/catalogues_best_model.RDATA") 
 ```
+###manuals best model
+NOTE: BEST MANUALS NUMBER OF TOPICS TO BE DETERMINED 
+```{r best manuals tp, eval = F}
+manuals_tm    <- tb_topic_model %>% filter(Origin == "manuals")
+
+manual_dtm <- manuals_tm$DTM[[1]]
+
+manual_lda <- manuals_tm %>% filter(n_topic == n_topics_best_manuals) %>% pull(Model) %>%.[[1]]
+
+#Train best model
+manuals_best_lda <- LDA(x = manual_dtm, 
+                model = manual_lda, 
+                control =  list(
+                  nstart = 50,
+                  seed   = 1 : 50, #must have length nstart
+                  best   = TRUE,
+                  burnin = 100,
+                  iter   = 10000,
+                  thin   = 2000) 
+                )
+
+save(manuals_best_lda, file = "./Output/manuals_best_model.RDATA") 
+```
+
 ##Best model pass to app
-```{r}
-load("./Output/catalogues_tmp_topic_model_tibble.RDATA")
+```{r load best models, eval = F}
+load("./Output/full_topic_model_tibble.RDATA") #contains both manuals and catalogues
+
+#Alternatively:
+#load("./Output/catalogues_topic_model_tibble.RDATA")
+
+#Best models:
 load("./Output/catalogues_best_model.RDATA")
+load("./Output/manuals_best_model.RDATA")
+```
+
+```{r best models clean for app, eval = TRUE}
+#helper function
+get_best_lda <- function(Origin){
+  if(Origin == "catalogues"){
+
+    return (catalogues_best_lda[[1]])
+
+  } else if(Origin == "manuals"){
+
+      return(manuals_best_lda[[1]])
+    }
+}
 
 best_model <- tibble( 
-  n_topic = 65
+  n_topic = c(n_best_catalogues, n_best_manuals)
   ) %>%
 
-  mutate(Origin     = "catalogues",
+  mutate(Origin     = c("catalogues", "manuals"),
          `Topic ID` = paste(Origin, n_topic, sep = "_"),
@@
          #Fit Model
-         Model  = list(best_lda),
+         Model  = pmap(.l = list(Origin), .f = get_best_lda),
 
@@
 
+###Save best model
+```{r save best model, eval = TRUE}
+save(best_model, file = "./Output/best_model.RDATA")
+```
+
 #App
@@
 The function `clean_kw` removes stopwords from our key words.
-```{r function clean key words}
+```{r function clean key words, eval = TRUE}
 clean_kw <- function(kw_list){
@@
 On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
-```{r crop and clean TM for App}
-app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
+```{r crop and clean TM for App, eval = TRUE }
+app_topic_model <- best_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
   mutate(kw = map(kw, .f = clean_kw))
@@
 For the app we also need to have a list of all courses and an example of a prospective semester
-```{r for convenience}
+```{r for convenience, eval = TRUE}
 # set seed
@@
 ##courses following_semester
-course_following_semester <- sample(
-  x       = course_all,
+course_following_semester <- sample(x = course_all,
                                     size    = 60,
-  replace = FALSE
-  ) %>% sort
+                                    replace = FALSE) %>% sort()
 
@@
 
-```{r adding convenience vectors}
-app_topic_model <- app_topic_model %>%
-  mutate(`All Courses`     = course_all,
-         `Sample semester` = course_following_semester)
+```{r adding convenience vectors, eval = TRUE}
+app_model <- app_topic_model %>%
+  mutate(`All Courses`     = list(course_all),
+         `Sample semester` = list(course_following_semester),
+         `Course Titles`   = list(course_titles) )
 
@@
 ## Saving files for APP
-```{r app files}
-# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
+```{r app files, eval = TRUE}
+save(app_model, file = "App/Recommender System/app_model.RDATA")
+save(app_model, file = "./Output/app_model.RDATA")
 ```
-# Visualization
-### Functions 
-This part is adapted 
-```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(d_beta){
-
-  data.frame(d_beta) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-      group_by(topic) %>%
-        top_n(10, beta) %>%
-      ungroup %>%
-      arrange(topic, desc(beta))
-
-} #repetition??? of inspect topics?
-
-prepare_data_LDA_gamma <- function(d_gamma, level = Course){
-
-  data_gamma <- data.frame(d_gamma) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-    rename(`Course ID` = document)
-
-  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
-                                      rename(facet = `Course ID`)
-
-  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
-                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
-                                       filter(!is.na(Cluster)) %>%
-                                       rename(facet = Cluster)
-
-  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
-                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
-                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-                                             rename(facet = Concentration)
-
-  data_gamma <- data_gamma %>%
-    group_by(facet, topic) %>%
-      summarise(gamma = sum(gamma)) %>%
-    filter(gamma > 0.05) %>%
-    ungroup %>%
-    arrange(facet, desc(gamma))
-
-  return(data_gamma)
-
-}
-
-# Bet Distribution
-test <- list()
-
-a <-  names(distribution)[1]
-test[[a]] <- lapply(distribution[[a]],
-                      prepare_data_LDA_beta)
-
-# Gamma Distribution
-b <- names(distribution)[2]
-test[[b]] <- lapply(distribution[[b]],
-                    prepare_data_LDA_gamma)
-
-test <- test_topic_model %>%
-  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
-         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
-         )
-test[["preparedBeta"]]
-rm(a,b #,test
-   )
-```
-This part is not adapted
-```{r LDA visualize, eval = F}
-visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-  ggplot(aes(x = reorder_within(term,
-                                by = beta,
-                                within = topic),
-             y = beta,
-             fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, scales = "free") +
-    scale_x_reordered() +
-    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
-    coord_flip() +
-    theme_light() +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "beta.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(facet, 
-                              by = gamma, 
-                              within = topic), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma1.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(topic, 
-                              by = gamma,
-                              within = facet), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ facet, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma2.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-```
-
-```{r LDA visualize all distrib, eval = F}
-visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){
-
-  # Beta distribution
-  data %>% 
-    prepare_data_LDA_beta %>%
-    visualize_LDA_beta(id_plot = id_plot)
-
-  # Gamma 1 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma1(id_plot = id_plot)
-
-  # Gamma 2 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma2(id_plot = id_plot)
-
-}
-```
-
-```{r LDA visualize all level, eval = F}
-visualize_LDA_all_level <- function(data, id_plot = "test"){
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Course,
-                              id_plot = paste(id_plot, "_course"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Cluster,
-                              id_plot = paste(id_plot, "_cluster"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Concentration,
-                              id_plot = paste(id_plot, "_concentration"))
-
-}
-```
-
-### Plots
-```{r LDA plot, cache = TRUE, eval = F}
-load("LDA.RDATA")
-
-LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")
-
-LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")
-
-LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
-```
-
-```{r label, eval = FALSE, eval = F}
-tidy(LDA_manual_10, "beta") %>%
-  filter(beta > 1e-3) %>%
-  bind_tf_idf(term = term, document = topic, n = beta) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf) %>%
-  arrange(topic, desc(tf_idf))
-
-  count(term, topic) %>%
-  arrange(desc(n)) %>%
-
-  filter(beta > 1e-3) %>%
-  group_by(term) %>%
-    mutate(n_topic = n(),
-           beta = beta / n_topic) %>%
-  group_by(topic) %>%
-    top_n(10, beta)
-
-  count(topic, term, wt = beta) %>%
-  (term = term, document = topic, n = n) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf)
-
-  group_by(term) %>%
-  summarise(beta = sum(beta)) %>%
-  arrange(desc(beta))
-
-labels <- list(
-  description_10 = "X"
-)
-```
-
-```{r label bis, eval = FALSE}
-visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
-              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
-                              "Sociology", "Law", "Research", "International Politics",
-                              "Philosophy", "Humanities"))
-
-visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
-              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
-                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
-                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
-                              "Math", "Management and ?"))
-visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
-              topic_names = c(
-                "Information", "Psycho", "Bio", "Chem", "Sociology",
-                "History", "skills", "Europe", "Philosophy", "IR",
-                "Conference", "Law", "Media", "Philosophy", "Economics",
-                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
-                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
-```

### 2019-05-07 Pillar 2 - Topic Modeling.Rmd
my_control

@@
 which_texts <- "catalogues"
-topic_numbers <-seq(from = 5, to = 150, by = 5)
+topic_numbers <-seq(from = 5, to = 200, by = 5)
 

### 2019-05-15 Pillar 1 - Topic Profile.Rmd
use selected topic model

--- 2019-04-16 Pillar 1 - Topic Profile.Rmd
@@
 * extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.
+
 * give more weight to 3000-level courses
@@
      * GPA (per concentration)
+
+# Set up
 
@@
 ```{r load, cache.lazy = TRUE} 
-load("App/Recommender System/topic_model_gb.RDATA")
-load("Output/data_pillar_1.RDATA")
+load("Output/app_model.RDATA")
+load("Output/data_student.RDATA")
 load("Output/course_current.RDATA")
@@
 
-# Course topic profile
+# Topic Model
 ```{r gamma_spread}
-gamma        <- topic_model_gb$g_overview[[15]] %>% mutate(topic = topic %>% str_replace(" ", "_"))
+gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
 gamma_spread <- gamma %>% spread(topic, gamma)
-
-beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
+beta  <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
+remove(app_model)
 ```
 
-# Student topic profile
+# Students' Topic Expertise
 ```{r student_TP} 
@@
 
-# Student GPA
+# Students' Academic Performance
 
@@
 
+Remove course enrolments from 2007 from the model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.
 ```{r}
-student_profile_nest <- student_profile %>%
-
-  nest(.key = profile, matches("GPA|Topic")) %>%
-
-  mutate(profile = profile %>% map(as.matrix))
+student_profile <- student_profile %>% filter(Year_numerical != 2007)
 ```
 
+## Save
+```{r save student_TP} 
+save(student_profile, file = "Output/student_profile.RDATA")
+```
 # Regressing grade on TP and GPA
@@
 
-## Lasso
 ```{r my_cv.glmnet} 
@@
 
-  nfold <- min(10, floor(nrow(df) / 3))
+  nfold <- min(10, floor(nrow(df) / 3)) # try nfold = 10
 
@@
 
+## Model fit
 ```{r fit_lasso, cache = TRUE} 
@@
 
+## Extract results
 ```{r fit_lasso extract} 
@@
 ```{r} 
+save(fit_lasso, file = "Output/CV.RDATA")
+```
+
+```{r} 
 hist(fit_lasso$cv_error)
@@
 ```{r}
-beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)
-
-i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
-beta %>% filter(topic == "Topic 18")
-beta %>% filter(topic == "Topic 8" )
-
-i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Business Administration: topic ~ business
-beta %>% filter(topic == "Topic 19")
+i <- 1; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
+beta %>% filter(topic == "Topic 27")
+beta %>% filter(topic == "Topic 62")
 
 i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
-beta %>% filter(topic == "Topic 21") 
-beta %>% filter(topic == "Topic 23")
+beta %>% filter(topic == "Topic 29") 
+beta %>% filter(topic == "Topic 64")
 
-i <- 9; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
-beta %>% filter(topic == "Topic 7") 
+i <- 5; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
+beta %>% filter(topic == "Topic 16")
+beta %>% filter(topic == "Topic 4")
 ```
@@
 
-student_profile_nest_app <- student_profile_nest %>%
+student_profile_nest_app <- student_profile %>%
+
+  nest(.key = profile, matches("GPA|Topic")) %>%
+
+  mutate(profile = profile %>% map(as.matrix)) %>%
 

### 2019-05-15 conference figures COPA2019.Rmd
create file

--- 2019-04-30 conference figures.Rmd
@@
 
-output_folder <- "Conference/Figures"
+output_folder <- "Conference/COPA2019/paper/figures"
 plot_width <- 6
@@
 
+```{r}
+latex_table <- function(df, filename = "test"){
+
+  df %>%
+    kable("latex", booktabs = TRUE, align = "c") %>%
+    write(file = str_c(output_folder, "/", filename, ".txt"))
+}
+```
+
 ```{r fig_student_data}
-student_data %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/student_data.pdf"))
+student_data %>% latex_table("data-student")
 ```
@@
 ```{r fig_course_data}
-course_data %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/course_data.pdf"))
+course_data %>% latex_table("course-student")
 ```
@@
       edge [fontname = Helvetica, decorate = TRUE]
+
+      subgraph cluster_input {
+		  color = white;
 
@@
 
+      } #close input subgraph
+
       subgraph cluster_model_fitting{
@@
 
-      TE [label = 'Topic Expertise']
-      AP [label = 'Academic Performance']
+      SM [label = 'Student Model']
 
@@
       SUG [label = 'Course Suggestions']
-      WAR [label = 'Warnings']
-      PRE [label = 'Preparatory Coursework']
+      PR [label = 'Prediction Region']
       }
@@
 
-      SD -> AP [weight = 2];
-      {SD, TM} -> TE;
+      {SD, TM} -> SM;
       {TM, KW} -> AI;
@@
       {PM, CS, TR} -> GP;
-      GP -> WAR;
-		  WAR -> PRE;
+      GP -> PR [label = '  Conformal Prediction'];
 
@@
 
-      {AP, TE} -> x1 [arrowhead = none]
-      x1 -> PM [label = '  Lasso'];
+      SM -> PM [label = '  Lasso'];
 
@@
       x2 -> SUG [label = '  KL distance'];
-
-      {TM, PM} -> x3 [arrowhead = none]
-      x3 -> PRE [label = '  KL distance'];
 
@@
 # Save by hand
-# image format: JPEG
-# Width: 626
-# Check Maintain aspect ratio
-# File name: Conference/Figures/Flowchart
+# File name: Conference/COPA2019/paper/figures/flowchart
 ```
@@
 
-    labs(title = str_c("Topic ", topic),
+    labs(title = NULL,
          x = "Terms",
@@
 
-  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
+  ggsave(filename = str_c("Beta-", topic, ".jpeg"), path = output_folder,
          width = plot_width / resize_factor, height = plot_height / resize_factor)
@@
 }
-```
-
-```{r fig_beta}
-plot_beta(1)
 ```
@@
 
-    labs(title = course,
+    labs(title = NULL,
          x = "Topics",
@@
 
-  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
+  ggsave(filename = str_c("gamma-", course, ".jpeg"), path = output_folder,
          width = plot_width, height = plot_height)
@@
 
-resize_factor <- 1.6
+resize_factor <- 2
 
@@
   mutate(Grade = str_c(Grade, "/10")) %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))
+  latex_table("toy-transcript")
 
-gamma %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))
+gamma %>% latex_table("toy-gamma")
 
-topic_expertise %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))
+topic_expertise %>% latex_table("toy-contribution")
 
@@
   geom_col() +
+  coord_flip() +
   labs(x = "Topics", y = "Topic Expertise")
 
-ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
+ggsave(filename = str_c("toy-expertise.jpeg"), path = output_folder,
        width = plot_width, height = plot_height)

### 2019-05-15 Conference/COPA2019/paper/draft.tex
create file

 %\documentclass[wcp,gray]{jmlr} % test grayscale version
 %\documentclass[wcp]{jmlr}% former name JMLR W\&CP
\documentclass[pmlr]{jmlr}% new name PMLR (Proceedings of Machine Learning)

 % The following packages will be automatically loaded:
 % amsmath, amssymb, natbib, graphicx, url, algorithm2e

 %\usepackage{rotating}% for sideways figures and tables
\usepackage{longtable}% for long tables

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{booktabs}
 % The siunitx package is used by this sample document
 % to align numbers in a column by their decimal point.
 % Remove the next line if you don't require it.
\usepackage[load-configurations=version-1]{siunitx} % newer version
 %\usepackage{siunitx}

 % to do
 \usepackage{xcolor}
 \newcommand\todo[1]{\textcolor{red}{#1}}

% The following command is just for this sample document:
\newcommand{\cs}[1]{\texttt{\char`\\#1}}

 % Define an unnumbered theorem just for this sample document:
\theorembodyfont{\upshape}
\theoremheaderfont{\scshape}
\theorempostheader{:}
\theoremsep{\newline}
\newtheorem*{note}{Note}

 % change the arguments, as appropriate, in the following:
\jmlrvolume{1}
\jmlryear{2019}
\jmlrworkshop{}

% start article
% \titlebreak
% \footnote{}
% \textsf
% \bfseries

\title[Conformal Prediction for Students' Grades]{Conformal Prediction for Students' Grades in a Course Recommender System\titletag{\thanks{XXX}}}

 % Use \Name{Author Name} to specify the name.
 % If the surname contains spaces, enclose the surname
 % in braces, e.g. \Name{John {Smith Jones}} similarly
 % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
 % If the first letter in the forenames is a diacritic
 % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

 % Authors with different addresses:
  \author{\Name{Rapha\"{e}l Morsomme\nametag{\thanks{with a note}}} \Email{raphael.morsomme@maastrichtuniversity.nl}\\
   \addr Zwingelput 4, 6211 KH Maastricht, the Netherlands	
   \AND
   \Name{Evgueni Smirnov} \Email{smirnov@maastrichtuniversity.nl}\\
   \addr DKE's address, 6211 KH Maastricht, the Netherlands}

 % Three or more authors with the same address:
 % \author{\Name{Author Name1} \Email{an1@sample.com}\\
 %  \Name{Author Name2} \Email{an2@sample.com}\\
 %  \Name{Author Name3} \Email{an3@sample.com}\\
 %  \addr Address}

 % Authors with different addresses:
 % \author{\Name{Author Name1} \Email{abc@sample.com}\\
 % \addr Address 1
 % \AND
 % \Name{Author Name2} \Email{xyz@sample.com}\\
 % \addr Address 2
 %}

% leave editor's section empty?
%\editor{Editor's name}
 % \editors{List of editors' names}

\begin{document}

\maketitle

\begin{abstract}
Course selection can be challenging for student of Liberal Arts programs. In particular, due to the highly personalized curricula of liberal arts students, it is often difficult to assess whether or not a certain course is too advanced given their academic background. To assist students of the liberal arts program of the University College Maastricht, Morsomme and Vazquez (2019) developed a course recommender system that suggests courses whose content matches the student's academic interests, and issues warnings for courses that it deems too advanced. To accomplish the latter, we fit a sparse regression model for grade. In this paper, we use the Inductive Confidence Machine (Papadopoulos, 2002) to obtain predictive regions for future grades. We compare the results obtained with the standard regression nonconformity measure and the normalized nonconformity measure. We find that both nonconformity measures produce valid predictive regions and that the width of the predictive regions is correlated with the accuracy of the regression model.
\end{abstract}

\begin{keywords} Conformal Prediction, Recommender System, Grade Prediction, Lasso, Education \end{keywords}

\todo{Rapha\"{e}l: make all figures black and white}

\todo{question: make flowchart with two pillars (course recommendation and warnings) instead of input/model/intermediate results/output?}

\todo{connect with bibtex bibliography from citavi}

\section{Introduction}
\label{sec:intro}

difficult to assess if student ready. 
Morsomme and Vazquez include warnings based on grade prediction to help student identify course too advanced for them. Provide warning if predicted grade is a fail.

In this paper, we present an applictaion of the ICM to provide students with prediction regions instead of warnings based on a point estimate for the grade. The advantage of PR over point estimates is that it improves info position of student, tehreby enabling them to make better-informed course selection. We decide to use conformal prediction prediction to tailor the PR to the students and to use an ICM to alleviate the computational costs of transductive.

Liberal Arts program are often characterized by their open curriculum which allows student to tailor their own study program to their academic objectives. These highly personalized curricula make it difficult for students, academic advisors and course coordinators to assess whether a particular course is too advanced given the student's current academic background or whether she/he has acquired the prerequisite skills via a combination of courses. To alleviate this problem, Morsomme and Vazquez (2019) developed a course recommender system which suggest courses whose content matches the academic interests of the student and issues warnings for courses that it deems too advanced given the student's academic background. To accomplish the latter, they fit a sparse regression model to each course which takes as input a model of the student indicating the skills that she/he has acquired in previous courses and her/his academic performance in different academic disciplines in order to predict grades. Warnings are issued when the system predicts a fail grade.

This paper presents the application of an Inductive Confidence Machine (ICM) (Papadopoulos, 2002) to complement the existing course recommender system of [ref: Morsomme and Vazquez, 2019] with predictive regions for future grades tailored to the student.

To improve student info position, we complement point estimates predictions with region predictions. To tailor the prediction to each student, we use conformal prediction.

This way, the information position of students is improved; instead of providing students with a binary advice, i.e. a warning if the predicted grade is a fail and nothing if it is a passing grade, students are provided with a predictive regions indicating a range of grades they are likely to receive in the courses that they are, for instance, considering for the following term particular course.

We present previous research on grade prediction in \sectionref{sec:related} and the data in \sectionref{sec:data}
We introduce the methodology related to the course recommender system and the ICM in \sectionref{sec:methodology} and present the results in \sectionref{sec:results}

\section{Related Work (Evgueni)}
\label{sec:related}

Conclusion of the section: no previous research has applied the conformal prediction framework to students' grade prediction.

\section{Data}
\label{sec:data}

We employ two sets of data: student data and course data.

The student data consists of anonymized course enrollment information. We use the transcripts of the 2,526 students of the liberal arts program between 2008 and 2019 with a total of 79,245 course enrollments. We exclude enrollments with a missing grade which indicates that the student either dropped the course or fail the attendance requirement. In the latter case, the data set contains an observation corresponding to the resit. \tableref{tab:student-data} presents the student data. Each row contains an anonymized student ID, a course ID, a year and semester, and the obtained grade.

The course data consists of the 2018-2019 course catalogues of five departments of Maastricht University: European Studies, University College Maastricht, University College Venlo, Psychology and Science Program. These catalogues contain a one-page description of 490 courses. \tableref{tab:course-data} presents the textual data in the tidy format with one row per document-term [ref: Wickham 2014]. We process the data following common cleaning procedures [ref: Meyer, 2008]: we tokenize the individual terms, stem them with the Hunspell dictionary and remove common stop words, numbers between 1 and 1,000, and terms occurring less than 3 times in the data set.

\begin{table}[hbtp]
	\floatconts
	{tab:student-data}
	{\caption{Example of Student Data}}	
	{\begin{tabular}{ccccc}
		\toprule
		\bfseries Student ID &\bfseries Course ID &\bfseries Academic Year &\bfseries Period &\bfseries Grade\\
		\midrule
		44940 & CAP3000 & 2009-2010 & 4 & 8.8\\
		37490 & SSC2037 & 2009-2010 & 4 & 8.4\\
		71216 & HUM1003 & 2010-2011 & 4 & 6.8\\
		44212 & SSC2049 & 2010-2011 & 2 & 8.4\\
		85930 & SSC2043 & 2011-2012 & 1 & 4.3\\
		\addlinespace
		14492 & COR1004 & 2012-2013 & 2 & 8.5\\
		34750 & HUM2049 & 2013-2014 & 5 & 6.0\\
		32316 & SSC1001 & 2013-2014 & 1 & 8.5\\
		22092 & SCI1009 & 2014-2015 & 1 & 6.4\\
		19512 & COR1004 & 2016-2017 & 5 & 7.0\\
		\bottomrule
	\end{tabular}}	
\end{table}

\begin{table}[hbtp]
	\floatconts
	{tab:course-data}
	{\caption{Example of Course Data}}	
	{\begin{tabular}{cccc}
			\toprule
			\bfseries Course ID &\bfseries Course Title &\bfseries Department &\bfseries Term\\
			\midrule
			HUM3034 & World History & UCM & understand\\
			HUM3034 & World History & UCM & major\\
			HUM3034 & World History & UCM & issue\\
			HUM3034 & World History & UCM & episode\\
			HUM3034 & World History & UCM & shape\\
			\addlinespace
			HUM3034 & World History & UCM & history\\
			HUM3034 & World History & UCM & mankind\\
			HUM3034 & World History & UCM & focus\\
			HUM3034 & World History & UCM & theme\\
			HUM3034 & World History & UCM & topic\\
			\bottomrule
	\end{tabular}}	
\end{table}

\section{Methodology}
\label{sec:methodology}

\subsection{The Course Recommender System}
\label{sec:crs}

\subsubsection{Overview}
\label{sec:overview}
The course recommender system has two goals: suggesting courses whose content matches the student's academic interests and help the student assess whether she/he has acquired the necessary knowledge to succeed in the course she /he is considering for the following term. Although the former is not of direct interest for this paper, we briefly describe

\begin{figure}[htbp]
	\floatconts
	{fig:flowchart}
	{\caption{Flowchart of the Course Recommender System}}
	{\includegraphics[width=0.5\linewidth]{figures/flowchart}}
\end{figure}

\subsubsection{Topic Model}
\label{sec:tm}
We start by fitting a topic model to the course data using the Latent Dirichlet Allocation generative model and the Gibbs sampling algorithm (ref: Blei, 2003; Phan, 2008). The LDA model views a topic as a mixture of words and a document as a mixture of topics. More precisely, topics are conceptualize as a probability distribution over the vocabulary of the data, and document as a set of words, each drawn from a probability distribution over topics specific to that document. The term \textit{Dirichlet} comes from the fact that the word distribution $\beta_{t}$ for a topic $t$ is generated from a Dirichlet distribution $\beta_{t} \sim Dirichlet(\delta)$ and the topic distribution $\theta_{d}$ for a document $d$ is generated from a Dirichlet distribution $\theta_{d} \sim Dirichlet(\alpha)$ where $\delta$ and $\alpha$ act as hyper-parameters determining how concentrated the distributions of words in topics and the distributions of topics in documents are.

We follow Phan (ref: 2008) who used a Gibbs sampler to learn the distributions $\beta$ and $\theta$. The obtained topic model consists of a term distribution for each topic and a topic distribution for each course description. \figureref{fig:gamma} shows the importance of the main topics of the core course COR1004 Political Philosophy. \figureref{fig:beta} indicates that the two main topics of the course (topics 4 and 19) respectively correspond to the themes of international politics and philosophy.

The number of topics $T$ needs to be specified \textit{a-priori}. We trained 30 models with $K=5,10,\cdots,150$. As suggested by Griffiths and Steyvers (ref: 2008), we set $\alpha=50/K$ and $\delta=0.1$. We run 6,000 iterations of the Gibbs sampler with a burn in of 1,000 iterations and sample every 100 iterations. To prevent being stuck in a local optimum, we use 10 random initialization and keep the best model with respect to the log-likelihood. We choose the number of topics $K$ that yields the model with the maximum likelihood. Figure X shows that the model with 65 topics has the maximum likelihood. To increase the quality of the model, we retrain the model with 16,000 iterations of the the Gibbs sampler, a burn in of 2,000 iterations and 20 random starts and the other parameters at their original values.

\begin{figure}[htbp]
	\floatconts
	{fig:gamma}
	{\caption{Topic Distribution in the course COR1004 Political Philosophy.}}
	{\includegraphics[width=0.5\linewidth]{figures/gamma-COR1004}}
\end{figure}

\begin{figure}[htbp]
	\floatconts
	{fig:beta}
	{\caption{Word Distribution in the main two topics of COR1004 Political Philosophy. Topic 4 corresponds to international politics and Topic 19 to philosophy.}}
	{
		\subfigure[Topic 4]{\label{fig:beta-4}
			\includegraphics[width=0.2\linewidth]{figures/beta-4}}
		\qquad
		\subfigure[Topic 19]{\label{fig:beta-19}%
			\includegraphics[width=0.2\linewidth]{figures/beta-19}}
	}
\end{figure}

\begin{figure}[htbp]
	\floatconts
	{fig:ll}
	{\caption{Maximum Likelihood Model Selection: we choose the model with 65 topics.}}
	{\includegraphics[width=0.5\linewidth]{figures/model-selection}}
\end{figure}

\subsubsection{Student Model}
\label{sec:sm}
The student model consists of two elements: academic performance and level of topic-specific expertise. Academic performance corresponds to the student's general GPA as well as her/his GPA in humanities, natural sciences, social sciences, skills and projects. These are derived from the student's transcript in a straightforward way. Topic-specific expertise corresponds to the knowledge that the student has acquired in each of the topics present in the topic model in previous courses. We posit that when students takes a course they acquire knowledge about its content and that the amount of knowledge they acquire is proportional to their grade. More precisely, we assume that students who obtain 10/10 in a course acquire all the knowledge related to its content and that those who obtain 5/10 only acquire half of it. The content of a course is determined by its topic distribution in the topic model and the grade are retrieved from the student's transcript. Hence if a student has taken $n$ courses and  $g_{i}$ corresponds to her/his grade in  course $i$, for $i = 1, \cdots, n$, then the expertise of the student $e_t$ in topic $t$ simply corresponds to $$e_t = \sum_{i= 1}^{n} g_i \gamma_{i,t}$$ where $\gamma_{i,t}$ corresponds to the importance of topic $t$ in course $i$ in the topic model. \figureref{fig:toy-expertise} presents a toy example of the contribution of individual courses to a student's expertise in 5 topics.

\begin{table}[htbp]
	\floatconts
	{tab:toy}
	{\caption{Toy Example of Topic Expertise}}
	{%
		\subtable[Topic Distribution $\gamma$]{%
			\label{tab:toy-gamma}%
			\begin{tabular}{cccccc}
				\toprule
				\bfseries Course & \bfseries Topic 1 & \bfseries Topic 2 & \bfseries Topic 3 & \bfseries Topic 4 & \bfseries Topic 5\\
				\midrule
				Course 1 & 0.0 & 0.7 & 0.2 & 0.1 & 0.0\\
				Course 2 & 0.2 & 0.2 & 0.2 & 0.2 & 0.2\\
				Course 3 & 0.0 & 0.4 & 0.2 & 0.1 & 0.2\\
				\bottomrule
			\end{tabular}
		}\qquad
		\subtable[Transcript]{%
			\label{tab:toy-grade}%
			\begin{tabular}{cc}
				\toprule
				\bfseries Course & \bfseries Grade\\
				\midrule
				Course 1 & 6/10\\
				Course 2 & 9/10\\
				Course 3 & 2.5/10\\
				\bottomrule
			\end{tabular}
		}\qquad
			\subtable[Course Contribution towards Topic Expertise]{%
			\label{tab:toy-contribution}%
			\begin{tabular}{cccccc}
				\toprule
				\bfseries Course & \bfseries Topic 1 & \bfseries Topic 2 & \bfseries Topic 3 & \bfseries Topic 4 & \bfseries Topic 5\\
				\midrule
				Course 1 & 0.00 & 0.42 & 0.12 & 0.060 & 0.00\\
				Course 2 & 0.18 & 0.18 & 0.18 & 0.180 & 0.18\\
				Course 3 & 0.00 & 0.10 & 0.05 & 0.025 & 0.05\\
				\bottomrule
			\end{tabular}
		}
	}
\end{table}

\begin{figure}[htbp]
	\floatconts
	{fig:toy-expertise}
	{\caption{Contribution of Individual Courses towards a Student's Topic Expertise Profile.}}
	{\includegraphics[width=0.5\linewidth]{figures/toy-expertise}}
\end{figure}

\subsubsection{Underlying Algorithm: Sparse Regression Model}
\label{sec:sm}

We fit a sparse linear regression model for grade prediction to each of the 132 courses currently offered at the college with at least 20 student enrollments since 2008. The input consists of the 71 variables present in the student model at the start of the course: her/his 6 GPA's  (1 general and 5 discipline-specific) and 65 levels of topic-specific expertise. Since the number of predictors is relatively large, we regularize the models with the lasso penalty (ref: Tibshirany, 1998). For each course, we use 10-fold cross-validation to find the value of the lasso tuning parameter $\lambda$ that minimizes the CV mean absolute error (mae), a more robust loss function than the squared absolute error (ref: els, 2008). \figureref{fig:mae-cv} presents the distribution of the CV mae for the 132 prediction models. The model for the course \textit{PRO2004 Academic Debate} has the smallest prediction error (0.38 grade point) and the model for \textit{SCI3006 Mathematical Modelling} the largest (1.80 grade point). The mean CV mae weighted by the number of students enrolled in the course is 0.78, the median is 0.78 and the standard deviation is 0.28.

\begin{figure}[htbp]
	\floatconts
	{fig:cv-mae}
	{\caption{Distribution of Cross-Validation Error}}
	{\includegraphics[width=0.5\linewidth]{figures/cv-mae}}
\end{figure}

\subsubsection{Prediction Region for Grade}
\label{sec:warning}
Import from EDM2019

\subsection{The Inductive Confidence Machine (Evgueni)}
\label{sec:icm}

\section{Results}
\label{sec:results}

Make figures

\section{Conclusion}
\label{sec:conclusion}

valid

width correlated to accuracy of underlying algorithm i.e. CV error of lasso

\section{Comments to Evgueni}

Focus on conformal prediction instead of recommender system, lasso, topic model, etc. This way, the paper is simpler to follow.

If we want to expand on lasso, we should write a paper on lasso itself; just like we are doing with grade prediction. The same goes for topic model.

%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%

% end of paper

%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%

\section{others}

This is a sample article that uses the \textsf{jmlr} class with
the \texttt{wcp} class option.  Please follow the guidelines in
this sample document as it can help to reduce complications when
combining the articles into a book. Please avoid using obsolete
commands, such as \verb|\rm|, and obsolete packages, such as
\textsf{epsfig}.\footnote{See
\url{http://www.ctan.org/pkg/l2tabu}}

Please also ensure that your document will compile with PDF\LaTeX.
If you have an error message that's puzzling you, first check for it
at the UK TUG FAQ
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
that doesn't help, create a minimal working example (see
\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
to somewhere like TeX on StackExchange
(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
(\url{http://www.latex-community.org/forum/}).

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations should be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
align environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.

\begin{table}[t]

	\caption{\label{tab:}Student Data \label{tab:data-student}}
	\centering
	\begin{tabular}{ccccc}
		\toprule
		Student ID & Course ID & Academic Year & Period & Grade\\
		\midrule
		44940 & CAP3000 & 2009-2010 & 4 & 8.8\\
		37490 & SSC2037 & 2009-2010 & 4 & 8.4\\
		71216 & HUM1003 & 2010-2011 & 4 & 6.8\\
		44212 & SSC2049 & 2010-2011 & 2 & 8.4\\
		85930 & SSC2043 & 2011-2012 & 1 & 4.3\\
		\addlinespace
		14492 & COR1004 & 2012-2013 & 2 & 8.5\\
		34750 & HUM2049 & 2013-2014 & 5 & 6.0\\
		32316 & SSC1001 & 2013-2014 & 1 & 8.5\\
		22092 & SCI1009 & 2014-2015 & 1 & 6.4\\
		19512 & COR1004 & 2016-2017 & 5 & 7.0\\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabss}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you should use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodess}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{figures/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{figures/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|. If the figures are contained in
a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{figures/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{figures/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{figures/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{figures/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

\subsection{Algorithms}
\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the
\texttt{algorithm} environment. Within this environment, use
use an \texttt{enumerate} or nested \texttt{enumerate} environments.
For example, see \algorithmref{alg:gauss}. Note that algorithms
float like figures and tables.

\begin{algorithm}[htbp]
\floatconts
{alg:gauss}% label
{\caption{The Gauss-Seidel Algorithm}}
{% contents
\begin{enumerate}
  \item For $k=1$ to maximum number of iterations
    \begin{enumerate}
      \item For $i=1$ to $n$
        \begin{enumerate}
        \item $x_i^{(k)} = 
          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
          where $\epsilon$ is a specified stopping criteria, stop.
      \end{enumerate}
    \end{enumerate}
\end{enumerate}
}
\end{algorithm}

You can use \verb|\caption| and \verb|\label| without using
\verb|\floatconts| (as in \algorithmref{alg:moore}).

If you'd rather have the same numbering throughout the algorithm
but still want the convenient indentation of nested 
\texttt{enumerate} environments, you can use the
\texttt{enumerate*} environment provided by the \textsf{jmlr}
class. For example, see \algorithmref{alg:moore}.

\begin{algorithm}
\caption{Moore's Shortest Path}\label{alg:moore}
Given a connected graph $G$, where the length of each edge is 1:
\begin{enumerate*}
  \item Set the label of vertex $s$ to 0
  \item Set $i=0$
  \begin{enumerate*}
    \item \label{step:locate}Locate all unlabelled vertices 
          adjacent to a vertex labelled $i$ and label them $i+1$
    \item If vertex $t$ has been labelled,
    \begin{enumerate*}
      \item[] the shortest path can be found by backtracking, and 
      the length is given by the label of $t$.
    \end{enumerate*}
    otherwise
    \begin{enumerate*}
      \item[] increment $i$ and return to step~\ref{step:locate}
    \end{enumerate*}
  \end{enumerate*}
\end{enumerate*}
\end{algorithm}

Pseudo code can be displayed using the \texttt{algorithm2e}
environment. This is defined by the \textsf{algorithm2e} package
(which is automatically loaded) so check the \textsf{algorithm2e}
documentation for further details.\footnote{Either \texttt{texdoc
algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
For an example, see \algorithmref{alg:net}.

\begin{algorithm2e}
\caption{Computing Net Activation}
\label{alg:net}
 % older versions of algorithm2e have \dontprintsemicolon instead
 % of the following:
 %\DontPrintSemicolon
 % older versions of algorithm2e have \linesnumbered instead of the
 % following:
 %\LinesNumbered
\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
\KwOut{$y$, the net activation}
$y\leftarrow 0$\;
\For{$i\leftarrow 1$ \KwTo $n$}{
  $y \leftarrow y + w_i*x_i$\;
}
\end{algorithm2e}

\section{Description Lists}

The \textsf{jmlr} class also provides a description-like 
environment called \texttt{altdescription}. This has an
argument that should be the widest label in the list. Compare:
\begin{description}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{description}
with
\begin{altdescription}{differentiate}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{altdescription}

\section{Theorems, Lemmas etc}
\label{sec:theorems}

The following theorem-like environments are predefined by
the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
and \texttt{axiom}. You can use the \texttt{proof} environment
to display the proof if need be, as in \theoremref{thm:eigenpow}.

\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
with eigenvector $\vec{\xi}$.
\begin{proof}
Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
$\xi$, then
\begin{align*}
\vec{B}\vec{\xi} &= \lambda\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
&= \lambda\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^2\vec{\xi}
\end{align*}
Therefore true for $n=2$. Now assume true for $n=k$:
\begin{align*}
\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
&= \lambda^k\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^{k+1}\vec{\xi}
\end{align*}
Therefore true for $n=k+1$. Therefore, by induction, true for all
$n$.
\end{proof}
\end{theorem}

\begin{lemma}[A Sample Lemma]\label{lem:sample}
This is a lemma.
\end{lemma}

\begin{remark}[A Sample Remark]\label{rem:sample}
This is a remark.
\end{remark}

\begin{corollary}[A Sample Corollary]\label{cor:sample}
This is a corollary.
\end{corollary}

\begin{definition}[A Sample Definition]\label{def:sample}
This is a definition.
\end{definition}

\begin{conjecture}[A Sample Conjecture]\label{con:sample}
This is a conjecture.
\end{conjecture}

\begin{axiom}[A Sample Axiom]\label{ax:sample}
This is an axiom.
\end{axiom}

\begin{example}[An Example]\label{ex:sample}
This is an example.
\end{example}

\section{Color vs Grayscale}
\label{sec:color}

It's helpful if authors supply grayscale versions of their
figures in the event that the article is to be incorporated into
a black and white printed book. With external PDF, PNG or JPG
graphic files, you just need to supply a grayscale version of the
file. For example, if the file is called \texttt{myimage.png},
then the gray version should be \texttt{myimage-gray.png} or
\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
need to modify your code. The \textsf{jmlr} class checks for
the existence of the grayscale version if it is print mode 
(provided you have used \verb|\includegraphics| and haven't
specified the file extension).

You can use \verb|\ifprint| to determine which mode you are in.
For example, in \figureref{fig:nodes}, the 
\ifprint{dark gray}{purple} ellipse represents an input and the
\ifprint{light gray}{yellow} ellipse represents an output.
Another example: {\ifprint{\bfseries}{\color{red}}important text!}

You can use the class option \texttt{gray} to see how the
document will appear in gray scale mode. \textcolor{blue}{Colored
text} will automatically be converted to gray scale.

The \textsf{jmlr} class loads the \textsf{xcolor}
package, so you can also define your own colors. For example:
\ifprint
  {\definecolor{myred}{gray}{0.5}}%
  {\definecolor{myred}{rgb}{0.5,0,0}}%
\textcolor{myred}{XYZ}.

The \textsf{xcolor} class is loaded with the \texttt{x11names}
option, so you can use any of the x11 predefined colors (listed
in the \textsf{xcolor} documentation\footnote{either 
\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).

\section{Citations and Bibliography}
\label{sec:cite}

The \textsf{jmlr} class automatically loads \textsf{natbib}.
This sample file has the citations defined in the accompanying
BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
citation use \verb|\citep|. For example
\citep{guyon-elisseeff-03}. For a textual citation use
\verb|\citet|. For example \citet{guyon2007causalreport}.
Both commands may take a comma-separated list, for example
\citet{guyon-elisseeff-03,guyon2007causalreport}.

These commands have optional arguments and have a starred
version. See the \textsf{natbib} documentation for further
details.\footnote{Either \texttt{texdoc natbib} or
\url{http://www.ctan.org/pkg/natbib}}

The bibliography is displayed using \verb|\bibliography|.

\acks{Our thanks to the University College Maastricht, Maastricht University, the Institute of Data Science, and the Department of Data Science and Knowledge Engineering, in particular to Peter Vermeer for initiating the project and enabling collaboration with the University College Maastricht.}

\bibliography{jmlr-sample}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\section{Second Appendix}\label{apd:second}

This is the second appendix.

\end{document}

### 2019-05-16 Data Preparation - Misc.Rmd

--- 2019-04-16 Data Preparation.Rmd
@@
   print
-```
-
-## Student Data
-The tibble `d_transcript` contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it.
-
-```{r read_csv_own_parsing}
-col_parsing <- cols(
-  `Student Number`                      = "c",
-  `Program (Abbreviation)`              = "c",
-  `Appraisal Status`                    = "c",
-  `Module Booking Reason (Description)` = "c",
-  `Object name`                         = "c",
-  `Start date`                          = "c",
-  `End Date`                            = "c"
-  )
-
-read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
-```
-
-```{r d_transcript, cache = TRUE}
-d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
-
-  map(read_csv_own_parsing) %>%
-
-  bind_rows
-
-rm(col_parsing, read_csv_own_parsing)
 ```
@@
 
-##
+## Ttarget courses
 ```{r}
@@
 
-## Student Data
-
-* Is `Academic Work ID` a unique ID number?
-
-* questions...
-
-(In this section we use: `d_transcript`- contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond roughly to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it).
-
-Our dataframe contains many variables and rows that are either empty or meaningless for our analysis.
-First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor").
-Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
-
-The data set `d_transcript` contains both the failed grades and the grade of the resit, and does not distinguish between them (same student, same course, same yera, same period, but different grade).
-
-```{r d_transcript helper}
-course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")
-
-is_UCM      <- function(course_code) course_code %>% str_detect(course_letter_UCM)
-is_elective <- function(course_code) course_code %>% str_detect("HUM|SCI|SSC")
-```
-
-```{r d_transcript row selection}
-d_transcript <- d_transcript %>%
-
-  # for simplicity, we only keep 
-  # courses taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
-
-  filter(`Program (Abbreviation)` == "7501") %>%
-
-  # The dataset has multiple rows for each student - course.
-  # Following guidelines of Richard Vos, we only consider: 
-  # `Appraisal (Description)` == "Grade supervisor"
-  # and `Appraisal Type` == "7055"
-
-  filter(
-    `Appraisal (Description)` == "Grade supervisor",
-    `Appraisal Type`          == "7055" # removes ~ 15 observations
-    )
-```
-
-```{r d_transcript column selection}
-d_transcript <- d_transcript %>%
-  # keep variables: Student ID, course ID, when a course is taken and the grade 
-  select(
-    `Student ID`   = `Student Number`,
-    `Course ID`    = `Module (Abbrev.)`,
-    Year_numerical = `Academic Year`,
-    Period         = `Academic Session`,
-    Grade          = `Grade symbol`
-    )
-```
-
-```{r clean_grade}
-clean_grade <- function(grade){
-
-  if(grade == "NG" | is.na(grade)) return(NA)
-
-  grade %>% str_replace(",", ".") %>% as.numeric
-
-}
-```
-
-```{r clean_period}
-clean_period <- function(period){
-
-  # Course spanning over multiple period are recorder with a 1, 2 or 3
-  if(period == 1) return("1 to 6")
-  if(period == 2) return("1 to 3")
-  if(period == 3) return("4 to 6")
-
-  # Course spanning over a single period are recorded in the 100's, 200's, etc.
-  # The digit of the hundred indicates the period.
-  period %/% 100 %>% as.character
-
-}
-```
-
-```{r clean_year}
-clean_year <- function(year) str_c(year, year + 1, sep = "-")
-```
-
-```{r clean d_transcript}
-d_transcript <- d_transcript %>%
-
-  mutate(
-
-    # Clean grade, period and year
-    Grade          = Grade          %>% map_dbl(clean_grade ),
-    Period         = Period         %>% map_chr(clean_period),
-    `Academic Year`= Year_numerical %>% map_chr(clean_year),
-
-    # extract first period in which course spanning over mutliple periods is given
-    period_numerical = substr(Period, 1, 1),
-
-    # Combine year & period to chronologically order courses using a single variable
-    time = str_c(Year_numerical, period_numerical) %>% as.numeric,
-
-    grade_ceil = ceiling(Grade)
-
-    )
-```
-
-```{r}
-d_transcript <- d_transcript %>% filter(!is.na(Grade))
-```
-
-```{r}
-d_transcript_augmented <- d_transcript %>%
-  left_join(select(d_course, - Period), by = c("Course ID"))
-```
-
-### Issues
-```{r issue d_transcript}
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination.
-  add_count(
-    `Student ID`, `Course ID`, time,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination - grade.
-  add_count(
-    `Student ID`, `Course ID`, time, Grade,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
-  filter(`Student ID` == "6087587") %>%
-  arrange(`Course ID`) %>%
-  pull(`Course ID`)
-
-  # ~ 10 incomplete rows for a student's profile
-  d_transcript %>% filter(`Student ID` == "0481343") %>% View
-
-#TODO: list issues here
-```
-
 # Save Data
 ```{r}
-save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")
-
-save(d_transcript_augmented, file = "Output/data_pillar_1.RDATA")
-
-save(d_course, d_transcript, file = "Output/data_pillar_2.RDATA")
+save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
+     file = "Output/data_general.RDATA")
+save(d_course, file = "Output/data_pillar_2.RDATA")
 ```

### 2019-05-16 Data Preparation - Student Data.Rmd

--- 2019-04-16 Data Preparation.Rmd
@@
 library(tidyverse)
-library(tidytext)
-library(gsheet) # import spreadsheets from google drive
-library(tm)
-library(hunspell) # Stemmer
-library(magrittr)
 ```
@@
 # Import Data
-The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons).
-We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
-We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
-
-## List of AoD's and Assessments
-First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
-` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
-Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively).
-We also any imported emtpy cells.
-```{r list_AoD_assessment}
-list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
-
-  map(na.omit)
-
-# selection of most important types of assessment an AoD to keep plots clear
-list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %T>% print
-list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %T>% print
-```
-
-## Course Data
-We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
-The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
-The tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment; and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
-
-```{r d_course}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>% print
-```
-
-```{r d_assessment}
-d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key   = Assessment, value = assessment_covered, Paper : Participation) %>%
-
-  filter(assessment_covered) %>%
-
-  select(- c(assessment_covered, `Comment on Assessment`)) %T>%
-
-  print
-```
-
-```{r d_ILO}
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
-```
-
-```{r d_AoD_from_ILO}
-d_AoD_from_ILO <- d_ILO %>%
-
-  rename(ILO = Objectives) %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %T>%
-
-  print
-```
-
-## Student Data
 The tibble `d_transcript` contains the transcript information of students as was provided.
@@
 ```{r d_transcript, cache = TRUE}
-d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
+d_transcript <- paste0("Input/Raw Grades/grades", 1 : 2, ".csv") %>%
 
@@
 # Variable Engineering
-## Course Data
-The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
-
-### AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it.
-For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
-
-#### AoD from ILOs
-(For this section we use: `d_ILO`-indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD)
-
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r d_AoD_ILO}
-d_AoD_from_ILO
-```
-
-#### AoD from Assessment
-(For this section we use: `d_assessment`-indicates which type(s) of assessment each course contains with one row per course-assessment)
-
-In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
-We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
-`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-Thus, the first step is to import this matrix:
-
-```{r map_assessment_AoD}
-map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- AoD_covered) %>%
-
-  arrange(Assessment) %T>%
-
-  print
-```
-
-Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments.
-To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
-In the loop, we first extract a row of `d_assessment` and save it as `observation`.
-Then, we determine the corresponding assessment which we save as `assessment`.
-Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r d_AoD_assessment}
-d_AoD_from_assessment <- d_assessment %>%
-
-  left_join(map_assessment_AoD, by = "Assessment") %>%
-
-  filter(!is.na(AoD)) %T>%
-
-  print
-
-rm(map_assessment_AoD)
-```
-
-#### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
-```{r rbind d_AoD_ILO and d_AoD_assessment}
-d_AoD <- rbind(
-  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
-  d_AoD_from_assessment %>% select(`Course ID`, AoD)
-  ) %>%
-
-  distinct %>%
-
-  arrange(`Course ID`) %T>%
-
-  print
-
-rm(d_AoD_from_assessment, d_AoD_from_ILO)
-```
-
-### Courses
-(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)
-
-Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-For this we create the following three tibbles:
-1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
-2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
-3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
-Then we use a `full_join` to add these variables to the tibble `d_course`.
-```{r d_course detail}
-count_and_paste <- function(df, var, colnam1, colnam2){
-
-  df %>%
-
-    group_by(`Course ID`) %>%
-
-    summarize(
-      !!ensym(colnam1) := n_distinct(!!enquo(var)),
-      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
-      )
-
-}
-
-join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
-```
-
-```{r join d_course_detail}
-d_course <- d_course %>%
-
-  join_by_course_ID( d_AoD        %>% count_and_paste(AoD       , n_AoD       , `AoD Covered`        ) %T>% print) %>%
-
-  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`)           ) %>%
-
-  join_by_course_ID( d_ILO        %>% count_and_paste(Objectives, n_ILO       , `ILO Covered`        )           ) %>%
-
-  select(
-    `Course ID`, `Course Title`, Cluster,
-    n_ILO,
-    n_assessment, `Assessments Covered`,
-    n_AoD, `AoD Covered`,
-    everything()
-    ) %T>%
-
-  print
-
-rm(count_and_paste, join_by_course_ID)
-```
-
-The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level).
-Yet, these course are also offered at the `2000` level (intermediate level).
-We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r create UGR2000}
-UGR_2000 <- d_course %>%
-
-  filter( `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-
-  mutate(
-    `Course ID` = case_when(
-      `Course ID` == "UGR3001" ~ "UGR2001",
-      `Course ID` == "UGR3002" ~ "UGR2002",
-      `Course ID` == "UGR3003" ~ "UGR2003",
-      `Course ID` == "UGR3005" ~ "UGR2005"
-      )
-    ) %T>%
-
-  print
-
-d_course <- d_course %>% rbind(UGR_2000)
-
-# print UGR course
-print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )
-
-rm(UGR_2000)
-```
-
-Finally, we add a series of informative variable at the course level.
-```{r d_course additional info}
-d_course <- d_course %>%
-
-  separate(
-    col     = `Course ID`,
-    into    = c("Letters", "Number"),
-    sep     = 3,
-    remove  = FALSE,
-    convert = TRUE
-    ) %>%
-
-  mutate(
-    Level   = case_when(
-      between(Number, 1000, 1999) ~ "Introductory",
-      between(Number, 2000, 2999) ~ "Intermediate",
-      between(Number, 3000, 3999) ~ "Advanced"    )
-    ) %>%
-
-  select(`Course ID`, Letters, Number, Level, everything()) %T>%
-
-  print
-```
-
-##
-```{r}
-d_course <- d_course %>%
-  mutate(target = Number > 2000 & Type == "Elective" & (! str_detect(`Course ID`, "SA")))
-```
-
-## Student Data
 
 * Is `Academic Work ID` a unique ID number?
-
-* questions...
 
@@
 
-  if(grade == "NG" | is.na(grade)) return(NA)
+  if(grade == "NG" | is.na(grade)) return(NA) # conservative approach
 
@@
     Period         = Period         %>% map_chr(clean_period),
-    `Academic Year`= Year_numerical %>% map_chr(clean_year),
+    `Academic Year`= Year_numerical %>% clean_year,
 
-    # extract first period in which course spanning over mutliple periods is given
+    # extract first period for courses spanning mutliple periods
     period_numerical = substr(Period, 1, 1),
@@
 
+## Augment d_transcript with d_course
 ```{r}
+load("Output/data_general.RDATA")
 d_transcript_augmented <- d_transcript %>%
@@
 ### Issues
-```{r issue d_transcript}
+```{r issue d_transcript, eval = FALSE}
 d_transcript %>%
@@
 ```
-
+"Output/data_general.RDATA"
 # Save Data
 ```{r}
-save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")
-
-save(d_transcript_augmented, file = "Output/data_pillar_1.RDATA")
-
-save(d_course, d_transcript, file = "Output/data_pillar_2.RDATA")
+save(d_transcript, d_transcript_augmented, file = "Output/data_student.RDATA")
 ```

### 2019-05-16 Pillar 1 - Conformal Prediction.Rmd

---
title: "Pillar 1 - Conformal Prediction"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Set up

```{r setup, include = FALSE}
set.seed(1)

knitr::opts_chunk$set(fig.width = 3, fig.height = 2,
                      echo = FALSE, warning = FALSE)

library(tidyverse)
library(glmnet)

load("Output/CV.RDATA")
load("Output/data_student.RDATA")
load("Output/student_profile.RDATA")
```

# Course selection
I select courses with large and small n, and large and small CV error. I do not select courses whose lasso model contains less than 3 non-zero coefficients (df).

* COR1002: large n
* COR1004: large n and smaller CV error (mean absolute error) than COR1002

* SCI3003: small n and large CV error
* SCI2040: small n and small CV erro

* SSC3044: small CV error
* SSC3038: small CV error and n twice as large as SSC3044

* SCI2018: large CV error
* SCI2010: large CV error and n twice as large as SCI2018

```{r}
course_selection <- c("COR1002", "COR1004", "SCI3003", "SCI2040", "SSC3044", "SSC3038", "SCI2018", "SCI2010")

fit_lasso %>% 
  filter(target %in% course_selection) %>% 
  select(target, n, cv_error, df)
```

# Conformal Prediction setp by step

## Cross-validation

```{r CV helper}
create_Z <- function(course){

  student_profile %>%
    filter(`Course ID` == course) %>%
    select(Y = Grade, matches("GPA|Topic"))

}

add_fold <- function(df, n_fold = 10){

  n         <- nrow(df)
  fold_size <- ceiling(n / n_fold)
  folds     <- rep(1 : 10, fold_size) %>% sample %>% .[1 : n]

  df %>% mutate(fold = folds)

}
```

## Training, callibration and test sets

```{r split helper}
create_test <- function(df, fold_current) df %>% filter(fold == fold_current)

create_training_temp <- function(df, fold_current) df %>% filter(fold != fold_current)

add_allocation <- function(df){

  n <- nrow(df)
  n_training      <- floor(0.67 * n) # 2/3
  n_callibration  <- n - n_training  # 1/3

  allocation <- rep(x     = c("training", "callibration"), 
                    times = c(n_training, n_callibration)) %>%
  sample

  df %>% mutate(allocation = allocation)

}

create_training     <- function(df) df %>% filter(allocation == "training")

create_callibration <- function(df) df %>% filter(allocation == "callibration")
```

## Fit lasso on training set
```{r,lasso helper}
fit_target_model <- function(df){

  X <- df %>% select(matches("GPA|Topic"))
  Y <- df %>% pull(Y)

  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default

}

predict_grade <- function(df, model){

  X <- df %>% select(matches("GPA|Topic"))

  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")

  df %>% mutate(Y_hat = as.vector(Y_hat),
                error = abs(Y_hat - Y))

}

fit_error_model <- function(df){

  X <- df %>% select(matches("GPA|Topic"))
  error <- df %>% pull(error)

  cv.glmnet(x = as.matrix(X), y = error, type.measure = "mae") # lasso by default

}

predict_error <- function(df, model){

  X <- df %>% select(matches("GPA|Topic"))

  error_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")

  df %>% mutate(error_hat = as.vector(error_hat))

}
```

## Compute non-conformity scores on callibration test
```{r}
compute_ncs <- function(df) df %>% mutate(alpha = abs(Y - Y_hat) / error_hat )

compute_confidence <- function(df) df %>% mutate(confidence = rank(alpha) / nrow(.) )
```

## Evaluate coverage on test set

```{r}
compute_width <- function(df, confidence_given){

  df <- df %>% 
    distinct(alpha, confidence) %>%
    filter(confidence >= confidence_given)

  min(df$alpha)

}

compute_interval <- function(df, ncs){

  df %>% mutate(
    width       = ncs * error_hat,
    border_low  = Y_hat - width,
    border_high = Y_hat + width
    )
}

compute_hit <- function(df){
  df %>% mutate(hit = (border_low <= Y) & (Y <= border_high))
}
```

# Loop through all courses

```{r, echo = FALSE}
for(course in course_selection){

  # Set up
  callibration <- list()
  coverage     <- list()

  confidence <- seq(0.01, 0.99, 0.01)
  df_coverage <- tibble::tibble(
    confidence = confidence,
    width_mean = NA,
    coverage   = NA
    )

  # data
  Z <- create_Z(course)
  Z <- add_fold(Z)

  for(iteration in 1 : 10){

    # training, callibration and test sets
    Z_test          <- create_test(Z, fold_current = iteration)
    Z_training_temp <- create_training_temp(Z, fold_current = iteration) %>% add_allocation
    Z_training      <- create_training(Z_training_temp)
    Z_callibration  <- create_callibration(Z_training_temp)

    # fit target and error model to training set
    model_target <- fit_target_model(Z_training)
    Z_training   <- predict_grade(Z_training, model_target)
    model_error  <- fit_error_model(Z_training)

    # non-conformity scores on callibration
    Z_callibration <- Z_callibration %>% 
      predict_grade(model_target) %>%
      predict_error(model_error) %>%
      compute_ncs %>%
      compute_confidence

    # coverage on test set
    Z_test <- Z_test %>% 
      predict_grade(model_target) %>%
      predict_error(model_error)

    for(i in 1 : nrow(df_coverage)){ # loop through confidence levels

      confidence_i <- df_coverage$confidence[i]
      ncs          <- compute_width(Z_callibration, confidence_i)

      Z_test <- Z_test %>% compute_interval(ncs = ncs) %>% compute_hit

      coverage_i   <- mean(Z_test$hit)
      width_mean_i <- mean(Z_test$width)

      df_coverage$width_mean[i] <- width_mean_i
      df_coverage$coverage[i]   <- coverage_i

    }

    # Output fold
    callibration[[iteration]] <- Z_callibration %>% mutate(iteration = iteration) %>% select(iteration, confidence, alpha)
    coverage[[iteration]]     <- df_coverage %>% mutate(iteration = iteration)

  } # end CV fold

  # Output

  callibration <- bind_rows(callibration) %>% 
    mutate(iteration = as.factor(iteration))
  coverage     <- bind_rows(coverage) %>%
    mutate(iteration = as.factor(iteration))

  title_course <-  str_c(course, " (n = ", nrow(Z), ")")
  subtitle     <- "A line per CV test sets"

  print(ggplot(data = coverage) +
          geom_hline(yintercept = 1, linetype = "dashed") +
          geom_line(aes(confidence, width_mean, group = iteration, col = iteration), size = .5) +
          labs(title = title_course,
               subtitle = subtitle) +
    theme(legend.position = "none"))

  print(ggplot(data = coverage) +
          geom_abline(slope = 1, linetype = "dashed") +
          geom_line(aes(confidence, coverage, group = iteration, col = iteration), size = .5) +
          labs(title = title_course,
               subtitle = subtitle) +
    theme(legend.position = "none"))
}
```

Illustration of the effect of error_hat on interval's width (for confidence of 99%):
```{r, fig.height=4}
Z_test %>% select(Y, Y_hat, error, error_hat, width, border_low, border_high, hit)
plot(Z_test$error, Z_test$error_hat)
```

Correlation between the actual errors and the predicted errors (error_hat):
```{r}
cor(Z_test$error, Z_test$error_hat)
```

```{r, echo = FALSE, eval = F}
ggplot(data = Z_callibration) + geom_histogram(aes(Y), bins = 15)

ggplot(data = Z_callibration) + geom_histogram(aes(Y_hat), bins = 15)

ggplot(data = Z_callibration) + geom_histogram(aes(alpha), bins = 15)
```

```{r, echo = FALSE, eval = F}
ggplot(data = Z_callibration) + geom_point(aes(Y, Y_hat))

ggplot(data = Z_callibration) + geom_point(aes(Y, alpha))

ggplot(data = Z_callibration) + geom_point(aes(Y_hat, alpha))
```

### 2019-05-16 conference figures COPA2019.Rmd

@@
 
-  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
+  ggsave(filename = str_c("model-selection.jpeg"), path = output_folder,
          width = plot_width, height = plot_height)
@@
 
-ggsave(filename = str_c("CV.jpeg"), path = output_folder,
+ggsave(filename = str_c("cv-mae.jpeg"), path = output_folder,
          width = plot_width/1.5, height = plot_height/3.5)
@@
   kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/CV.pdf"))
+  as_image(file = str_c(output_folder, "/cv-mae-table.pdf"))
 ```

### 2019-05-22 Pillar 1 - Conformal Prediction.Rmd
update parameters of plots for COPA2019 editting

@@
 
+```{r setup_graph}
+theme_set(theme_light())
+
+output_folder <- "Conference/COPA2019/paper/figures"
+plot_width  <- 6
+plot_height <- plot_width / 1.6 
+```
+
 # Course selection
@@
 
-```{r}
-course_selection <- c("COR1002", "COR1004", "SCI3003", "SCI2040", "SSC3044", "SSC3038", "SCI2018", "SCI2010")
+```{r course_selection}
+course_selection <- c(
+#  "SCI3003", "SCI2040", # remove because n too small
+  "COR1002", "COR1004",  "SSC3044", "SSC3038", "SCI2018", "SCI2010")
 
-fit_lasso %>% 
+course_table <- fit_lasso %>% 
   filter(target %in% course_selection) %>% 
@@
 
-create_training_temp <- function(df, fold_current) df %>% filter(fold != fold_current)
+create_training <- function(df, fold_current) df %>% filter(fold != fold_current)
 
@@
 
-  n <- nrow(df)
-  n_training      <- floor(0.67 * n) # 2/3
-  n_callibration  <- n - n_training  # 1/3
+  n_training <- nrow(df)
+  n_proper_training <- floor(0.67 * n_training)        # 2/3
+  n_calibration     <- n_training - n_proper_training  # 1/3
 
-  allocation <- rep(x     = c("training", "callibration"), 
-                    times = c(n_training, n_callibration)) %>%
+  allocation <- rep(x     = c("proper training", "calibration"), 
+                    times = c(n_proper_training, n_calibration)) %>%
   sample
@@
 
-create_training     <- function(df) df %>% filter(allocation == "training")
+create_proper_training <- function(df) df %>% filter(allocation == "proper training")
 
-create_callibration <- function(df) df %>% filter(allocation == "callibration")
+create_calibration     <- function(df) df %>% filter(allocation == "calibration")
 ```
@@
 
-  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default
+  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default. Use mean absolute error
 
@@
 
-  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")
+  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min") # use lambda that minimizes mae
 
   df %>% mutate(Y_hat = as.vector(Y_hat),
-                error = abs(Y_hat - Y))
+                error = abs(Y_hat - Y),
+                mu    = log(error)) # take ln of absolute error
 
@@
   X  <- df %>% select(matches("GPA|Topic"))
-  error <- df %>% pull(error)
+  mu <- df %>% pull(mu)
 
-  cv.glmnet(x = as.matrix(X), y = error, type.measure = "mae") # lasso by default
+  cv.glmnet(x = as.matrix(X), y = mu, type.measure = "mae")
 
@@
 
-  error_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")
+  mu_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")
 
-  df %>% mutate(error_hat = as.vector(error_hat))
+  df %>% mutate(mu_hat = as.vector(mu_hat))
 
@@
 
-## Compute non-conformity scores on callibration test
+## Compute standardized non-conformity scores on callibration test
 ```{r}
-compute_ncs <- function(df) df %>% mutate(alpha = abs(Y - Y_hat) / error_hat )
 
-compute_confidence <- function(df) df %>% mutate(confidence = rank(alpha) / nrow(.) )
+compute_ncs              <- function(df) df %>% mutate(alpha = abs(Y - Y_hat))
+
+compute_standardized_ncs <- function(df) df %>% mutate(sigma = exp(mu_hat),
+                                                       alpha = abs(Y - Y_hat) / sigma )
+
+compute_significance     <- function(df) df %>% mutate(significance = rank(-alpha) / nrow(.) ) # !!! double check!!!
 ```
 
-## Evaluate coverage on test set
+## Evaluate error rate on test set
 
 ```{r}
-compute_width <- function(df, confidence_given){
+compute_width <- function(df, significance_given){
 
-  df <- df %>% 
-    distinct(alpha, confidence) %>%
-    filter(confidence >= confidence_given)
+  df <- df %>% filter(significance <= significance_given)
 
@@
   df %>% mutate(
-    width       = ncs * error_hat,
+    sigma       = exp(mu_hat),
+    width       = ncs * sigma,
     border_low  = Y_hat - width,
@@
 ```{r, echo = FALSE}
-for(course in course_selection){
 
 # Set up
-  callibration <- list()
-  coverage     <- list()
 
-  confidence <- seq(0.01, 0.99, 0.01)
-  df_coverage <- tibble::tibble(
-    confidence = confidence,
-    width_mean = NA,
-    coverage   = NA
-    )
+significance <- c(0.05, seq(0.1, 0.9, 0.1))
+results <- list()
+n_list <- 1
+
+for(course in course_selection){
 
@@
 
-    # training, callibration and test sets
+    # proper training, calibration and test sets
     Z_test            <- create_test(Z, fold_current = iteration)
-    Z_training_temp <- create_training_temp(Z, fold_current = iteration) %>% add_allocation
-    Z_training      <- create_training(Z_training_temp)
-    Z_callibration  <- create_callibration(Z_training_temp)
+    Z_training        <- create_training(Z, fold_current = iteration) %>% add_allocation
+    Z_proper_training <- create_proper_training(Z_training)
+    Z_calibration     <- create_calibration(Z_training)
 
-    # fit target and error model to training set
-    model_target <- fit_target_model(Z_training)
-    Z_training   <- predict_grade(Z_training, model_target)
-    model_error  <- fit_error_model(Z_training)
+    # fit target and error model to proper training set
+    model_target      <- fit_target_model(Z_proper_training)
+    Z_proper_training <- predict_grade(Z_proper_training, model_target)
+    model_error       <- fit_error_model(Z_proper_training)
 
-    # non-conformity scores on callibration
-    Z_callibration <- Z_callibration %>% 
+    # non-conformity scores on calibration
+    Z_calibration <- Z_calibration %>% 
       predict_grade(model_target) %>%
       predict_error(model_error) %>%
-      compute_ncs %>%
-      compute_confidence
+      compute_standardized_ncs %>%
+      compute_significance
 
-    # coverage on test set
+    # error on test set
     Z_test <- Z_test %>% 
@@
 
-    for(i in 1 : nrow(df_coverage)){ # loop through confidence levels
+    for(signi in significance){ # loop through significance levels
 
-      confidence_i <- df_coverage$confidence[i]
-      ncs          <- compute_width(Z_callibration, confidence_i)
+      ncs <- compute_width(Z_calibration, signi)
 
-      Z_test <- Z_test %>% compute_interval(ncs = ncs) %>% compute_hit
+      Z_test_augmented <- Z_test %>% 
+        compute_interval(ncs = ncs) %>%
+        compute_hit
 
-      coverage_i   <- mean(Z_test$hit)
-      width_mean_i <- mean(Z_test$width)
+      # save results
+      results[[n_list]] <- Z_test_augmented %>%
+        mutate(significance = signi,
+               iteration    = iteration,
+               course       = course) %>%
+        select(course, iteration, significance, width, hit,
+               Y, Y_hat, error, mu, mu_hat, sigma)
 
-      df_coverage$width_mean[i] <- width_mean_i
-      df_coverage$coverage[i]   <- coverage_i
+      n_list <- n_list + 1
 
-    }
-
-    # Output fold
-    callibration[[iteration]] <- Z_callibration %>% mutate(iteration = iteration) %>% select(iteration, confidence, alpha)
-    coverage[[iteration]]     <- df_coverage %>% mutate(iteration = iteration)
+    } # end loop significance
 
@@
 
-  # Output
-
-  callibration <- bind_rows(callibration) %>% 
-    mutate(iteration = as.factor(iteration))
-  coverage     <- bind_rows(coverage) %>%
-    mutate(iteration = as.factor(iteration))
-
-  title_course <-  str_c(course, " (n = ", nrow(Z), ")")
-  subtitle     <- "A line per CV test sets"
-
-  print(ggplot(data = coverage) +
-          geom_hline(yintercept = 1, linetype = "dashed") +
-          geom_line(aes(confidence, width_mean, group = iteration, col = iteration), size = .5) +
-          labs(title = title_course,
-               subtitle = subtitle) +
-    theme(legend.position = "none"))
-
-  print(ggplot(data = coverage) +
-          geom_abline(slope = 1, linetype = "dashed") +
-          geom_line(aes(confidence, coverage, group = iteration, col = iteration), size = .5) +
-          labs(title = title_course,
-               subtitle = subtitle) +
-    theme(legend.position = "none"))
 }
@@
 
-Illustration of the effect of error_hat on interval's width (for confidence of 99%):
+```{r}
+conformal_results <- bind_rows(results) %>%
+    mutate(iteration    = as.factor(iteration),
+           course       = as.factor(course))
+
+save(conformal_results, course_table, file = "Output/conformal.RDATA")
+```
+
+Illustration of the effect of error_hat on interval's width (for significance of 99%):
 ```{r, fig.height=4}

### 2019-05-22 Conference/COPA2019/paper/draft.tex
draft submitted to conference for review

@@
 
+% Package to make table with multi rows and columns
+\usepackage{multirow}
+
  % to do
@@
 \newcommand\todo[1]{\textcolor{red}{#1}}
-
-% The following command is just for this sample document:
-\newcommand{\cs}[1]{\texttt{\char`\\#1}}
-
- % Define an unnumbered theorem just for this sample document:
-\theorembodyfont{\upshape}
-\theoremheaderfont{\scshape}
-\theorempostheader{:}
-\theoremsep{\newline}
-\newtheorem*{note}{Note}
 
@@
 % \textsf
-% \bfseries
 
-\title[Conformal Prediction for Students' Grades]{Conformal Prediction for Students' Grades in a Course Recommender System\titletag{\thanks{XXX}}}
+\title[Conformal Prediction for Students' Grades]{Conformal Prediction for Students' Grades in a Course Recommender System}	%\titletag{\thanks{XXX}} % leave empty?
 
@@
  % Authors with different addresses:
-  \author{\Name{Rapha\"{e}l Morsomme\nametag{\thanks{with a note}}} \Email{raphael.morsomme@maastrichtuniversity.nl}\\
+  \author{\Name{Rapha\"{e}l Morsomme} \Email{raphael.morsomme@maastrichtuniversity.nl}\\ % Morsomme\nametag{\thanks{with a note}} % leave this slot empty?
    \addr Zwingelput 4, 6211 KH Maastricht, the Netherlands	
@@
    \Name{Evgueni Smirnov} \Email{smirnov@maastrichtuniversity.nl}\\
-   \addr DKE's address, 6211 KH Maastricht, the Netherlands}
+   \addr Bouillonstraat 10, 6211 LH Maastricht, the Netherlands}
 
@@
 Course selection can be challenging for student of Liberal Arts programs.
-In particular, due to the highly personalized curricula of liberal arts students, it is often difficult to assess whether or not a certain course is too advanced given their academic background.
-To assist students of the liberal arts program of the University College Maastricht, Morsomme and Vazquez (2019) developed a course recommender system that suggests courses whose content matches the student's academic interests, and issues warnings for courses that it deems too advanced.
-To accomplish the latter, we fit a sparse regression model for grade.
-In this paper, we use the Inductive Confidence Machine (Papadopoulos, 2002) to obtain predictive regions for future grades.
-We compare the results obtained with the standard regression nonconformity measure and the normalized nonconformity measure.
-We find that both nonconformity measures produce valid predictive regions and that the width of the predictive regions is correlated with the accuracy of the regression model.
+In particular, due to the highly personalized curricula of liberal arts students, it is often difficult to assess whether or not a particular course is too advanced given their academic background.
+To assist students of the liberal arts program of the University College Maastricht, \citet{Morsomme.2019} developed a course recommender system that suggests courses whose content matches the student's academic interests, and issues warnings for courses that it deems too advanced.
+
+To issue warnings, the system produces point predictions for the grades that a student will receive in the courses that she/he is considering for the following term.
+Point predictions are estimated with regression models specific to each course which take into account the academic performance of the student along with the knowledge that she/he has acquired in previous courses.
+A warning is issued if the predicted grade is a fail.
+
+In this paper, we complement the system's point predictions for grades with prediction intervals constructed using the conformal prediction framework \citep{Vovk.2005}.
+We use the Inductive Confidence Machine (ICM) \citep{Papadopoulos.2002} with standardized nonconformity scores to construct prediction intervals that are tailored to each student.
+We find that the prediction intervals constructed with the ICM are valid and that their widths are related to the accuracy of the underlying regression model.
 \end{abstract}
 
-\begin{keywords} Conformal Prediction, Recommender System, Grade Prediction, Lasso, Education \end{keywords}
+\begin{keywords} Conformal Prediction, Recommender System, Course Grade Prediction, Lasso, Education \end{keywords}
 
-\todo{Rapha\"{e}l: make all figures black and white}
+% \todo{Rapha\"{e}l: make all figures black and white}
 
-\todo{question: make flowchart with two pillars (course recommendation and warnings) instead of input/model/intermediate results/output?}
+% \todo{Rapha\"{e}l: make sure that all figures have the same font size as the main text}
 
-\todo{connect with bibtex bibliography from citavi}
+% \todo{Rapha\"{e}l: use notation Z_k = (x_k, y_k) to simplify description of conformal prediction}
 
@@
 
-difficult to assess if student ready. 
-Morsomme and Vazquez include warnings based on grade prediction to help student identify course too advanced for them. Provide warning if predicted grade is a fail.
+Liberal Arts programs are often characterized by their open curriculum which allows student to tailor their own study program to their academic objectives \citep{Surpatean.2012, Morsomme.2019}.
+These highly personalized curricula make it difficult for students, academic advisors and course coordinators to assess whether the courses that a student considers taking the following term are too advanced given her/his current academic background or whether she/he has acquired the necessary skills, perhaps through an unusual combination of courses.
+To alleviate this problem, \citet{Morsomme.2019} developed the Liberal Arts Recommender System (LARS) which suggests to students courses whose content matches their academic interests.
+In addition, LARS helps student identify courses that are too advanced for them.
+To accomplish that, the system issues \textit{point predictions} for future grade based on the past academic performance of the student and the skills she/he has acquired in previous courses.
+A warning is issued when the predicted grade is a fail.
 
-In this paper, we present an applictaion of the ICM to provide students with prediction regions instead of warnings based on a point estimate for the grade.
-The advantage of PR over point estimates is that it improves info position of student, tehreby enabling them to make better-informed course selection.
-We decide to use conformal prediction prediction to tailor the PR to the students and to use an ICM to alleviate the computational costs of transductive.
+In this paper, we present an application of conformal prediction \citep{Vovk.2005} to complement the current point estimates for future grades of LARS with prediction intervals.
+For students, the advantage of prediction intervals over point predictions is clear: their information position is improved, thereby enabling them to make better-informed course selection.
+To avoid the computational costs of transductive conformal prediction, we opt for the lighter Inductive Confidence Machine (ICM) \citep{Papadopoulos.2002}.
+Furthermore, in order to provide prediction intervals that are tailored to each student, we use a normalized nonconformity measure \citep{Papadopoulos.2011}.
 
-Liberal Arts program are often characterized by their open curriculum which allows student to tailor their own study program to their academic objectives.
-These highly personalized curricula make it difficult for students, academic advisors and course coordinators to assess whether a particular course is too advanced given the student's current academic background or whether she/he has acquired the prerequisite skills via a combination of courses.
-To alleviate this problem, Morsomme and Vazquez (2019) developed a course recommender system which suggest courses whose content matches the academic interests of the student and issues warnings for courses that it deems too advanced given the student's academic background.
-To accomplish the latter, they fit a sparse regression model to each course which takes as input a model of the student indicating the skills that she/he has acquired in previous courses and her/his academic performance in different academic disciplines in order to predict grades.
-Warnings are issued when the system predicts a fail grade.
+\sectionref{sec:related} presents previous research on grade prediction.
+\sectionref{sec:data} introduces the data and \sectionref{sec:crs} briefly describes the existing LARS.
+\sectionref{sec:prediction} presents the conformal prediction framework in which we construct the prediction intervals.
+\sectionref{sec:experiment} presents the setting and results of the experiment
+and \sectionref{sec:conclusion} concludes.
 
-This paper presents the application of an Inductive Confidence Machine (ICM) (Papadopoulos, 2002) to complement the existing course recommender system of [ref: Morsomme and Vazquez, 2019] with predictive regions for future grades tailored to the student.
-
-To improve student info position, we complement point estimates predictions with region predictions. To tailor the prediction to each student, we use conformal prediction.
-
-This way, the information position of students is improved; instead of providing students with a binary advice, i.e.
-a warning if the predicted grade is a fail and nothing if it is a passing grade, students are provided with a predictive regions indicating a range of grades they are likely to receive in the courses that they are, for instance, considering for the following term particular course.
-
-We present previous research on grade prediction in \sectionref{sec:related} and the data in \sectionref{sec:data}
-We introduce the methodology related to the course recommender system and the ICM in \sectionref{sec:methodology} and present the results in \sectionref{sec:results}
-
-\section{Related Work (Evgueni)}
+\section{Related Work}
 \label{sec:related}
 
-Conclusion of the section: no previous research has applied the conformal prediction framework to students' grade prediction.
+The task of predicting students' course grades prediction has recently received a lot of attention \citep{Polyzou.2016, Houbraken.2017}.
+The approaches to this problem are regression approaches, classification approaches, and collaborative-filtering approaches.
+The first two approaches employ general information (secondary education, age, sex etc.), past performance, temporal elements, and contextual information of the students \citep{Bydzovska.2016}.
+They train a regression/classification model on historical data which is latter used for predicting students' course grades.
+The collaborative-filtering approaches require only past course grades for future prediction in contrast with the previous two approaches \citep{Sweeney.2015, Houbraken.2017}.
+They are divided into nearest-neighbor approaches \citep{Bydzovska.2015} and matrix-factorization approaches \citep{Polyzou.2016}.
+The nearest-neighbor approaches first identify neighbors of a student in terms of study performance and then predict the course grades for this student by aggregating the course grades of the neighbors.
+The matrix factorization approaches first decompose the student-course data into student and course matrices and then predict student course grades using the product of these matrices.
 
-\section{Data}
+Although the progress in  student course grade prediction is significant, no research was performed on the problem of estimating the confidence in this type of prediction.
+As it is stated above we propose to employ conformal prediction for this problem.
+Our choice is justified by the fact that other approaches for reliable prediction such as version spaces \citep{Smirnov.2004}, meta approaches \citep{Smirnov.2006, Smirnov.2006b}, ROC-isometric approaches \citep{Vanderlooy.2006} are
+inapplicable for regression tasks.
+
+\section{Data for LARS}
 \label{sec:data}
 
-We employ two sets of data: student data and course data.
+\citet{Morsomme.2019} employed two sets of data to develop LARS: student data and course data.
 
-The student data consists of anonymized course enrollment information.
-We use the transcripts of the 2,526 students of the liberal arts program between 2008 and 2019 with a total of 79,245 course enrollments.
-We exclude enrollments with a missing grade which indicates that the student either dropped the course or fail the attendance requirement.
-In the latter case, the data set contains an observation corresponding to the resit.
-\tableref{tab:student-data} presents the student data.
+The student data consisted of anonymized course enrollment information.
+It included the transcripts of the 2,526 students of the liberal arts program between 2008 and 2019 with a total of 79,245 course enrollments.
+Course enrollments with a missing grade, which indicates that the student either dropped the course or fail the attendance requirement, were removed.
+\tableref{tab:student-data} presents an example of the student data.
 Each row contains an anonymized student ID, a course ID, a year and semester, and the obtained grade.
 
-The course data consists of the 2018-2019 course catalogues of five departments of Maastricht University: European Studies, University College Maastricht, University College Venlo, Psychology and Science Program.
-These catalogues contain a one-page description of 490 courses.
-\tableref{tab:course-data} presents the textual data in the tidy format with one row per document-term [ref: Wickham 2014].
-We process the data following common cleaning procedures [ref: Meyer, 2008]: we tokenize the individual terms, stem them with the Hunspell dictionary and remove common stop words, numbers between 1 and 1,000, and terms occurring less than 3 times in the data set.
+The course data consisted of a corpus of the 490 course descriptions present in the 2018-2019 course catalogues of five departments of Maastricht University: European Studies, University College Maastricht, University College Venlo, Psychology and Science Program.
+These catalogues contain a one-page description of each course on offer.
+\tableref{tab:course-data} presents a sample of this textual data for the course \textit{HUM3034 World History} in the tidy format with one row per document-term \citep{Wickham.2014}.
+The data was processed following common procedures \citep{Meyer.2008}: individual terms were tokenized, stemmed with the Hunspell dictionary and common stop words were removed, as well as numbers between 1 and 1,000 and terms occurring less than 3 times in the corpus.
 
@@
 	{tab:student-data}
-	{\caption{Example of Student Data}}	
+	{\caption{Example of student data}}	
 	{\begin{tabular}{ccccc}
@@
 	{tab:course-data}
-	{\caption{Example of Course Data}}	
+	{\caption{Example of course data for the course HUM3034 World History}}	
 	{\begin{tabular}{cccc}
@@
 
-\section{Methodology}
-\label{sec:methodology}
+\section{LARS}
+\label{sec:crs}
+\subsection{Overview}
+\label{sec:overview}
 
-\subsection{The Course Recommender System}
-\label{sec:crs}
+LARS is composed of two pillars: course suggestions and warning issuance (see \figureref{fig:flowchart}).
 
-\subsubsection{Overview}
-\label{sec:overview}
-The course recommender system has two goals: suggesting courses whose content matches the student's academic interests and help the student assess whether she/he has acquired the necessary knowledge to succeed in the course she /he is considering for the following term.
-Although the former is not of direct interest for this paper, we briefly describe
+In pillar 1, a topic model of the courses is fitted to the course data using the Latent Dirichlet Allocation model \citep{Blei.2003}.
+A topic model represents a topic as a mixture of words and a document as a mixture of topics.
+The key words selected by the student are then mapped to the vocabulary of the topic model to represent her/his academic interests.
+Finally, the system matches the student's academic interests to the content of the courses as represented by the topic model to identify courses of interest to the student.
+
+In pillar 2 for warning issuance, a model of each student is first created which contains information about the academic performance of the student (derived from the student data) and the expertise in specific topics (derived from the topic model) that she/he has acquired in previous courses.
+A regression model for point prediction of the grades that takes the student model as input is then fitted for each course.
+LARS uses these models to predict the grade that the student will obtain in the courses that she/he is considering for the following term and issues a warning when the predicted grade is a fail.
 
@@
 	{fig:flowchart}
-	{\caption{Flowchart of the Course Recommender System}}
+	{\caption{Original LARS (black) and our contribution (red)}}
 	{\includegraphics[width=0.5\linewidth]{figures/flowchart}}
@@
 
-\subsubsection{Topic Model}
+\subsection{Pillar 1: Course Suggestion}
+
+\subsubsection{Topic Model of the Courses}
 \label{sec:tm}
-We start by fitting a topic model to the course data using the Latent Dirichlet Allocation generative model and the Gibbs sampling algorithm (ref: Blei, 2003; Phan, 2008).
-The LDA model views a topic as a mixture of words and a document as a mixture of topics.
-More precisely, topics are conceptualize as a probability distribution over the vocabulary of the data, and document as a set of words, each drawn from a probability distribution over topics specific to that document.
-The term \textit{Dirichlet} comes from the fact that the word distribution $\beta_{t}$ for a topic $t$ is generated from a Dirichlet distribution $\beta_{t} \sim Dirichlet(\delta)$ and the topic distribution $\theta_{d}$ for a document $d$ is generated from a Dirichlet distribution $\theta_{d} \sim Dirichlet(\alpha)$ where $\delta$ and $\alpha$ act as hyper-parameters determining how concentrated the distributions of words in topics and the distributions of topics in documents are.
 
-We follow Phan (ref: 2008) who used a Gibbs sampler to learn the distributions $\beta$ and $\theta$.
-The obtained topic model consists of a term distribution for each topic and a topic distribution for each course description.
-\figureref{fig:gamma} shows the importance of the main topics of the core course COR1004 Political Philosophy.
-\figureref{fig:beta} indicates that the two main topics of the course (topics 4 and 19) respectively correspond to the themes of international politics and philosophy.
+\citet{Morsomme.2019} fitted a topic model to the course data using the Latent Dirichlet Allocation generative model \citep{Blei.2003} and the Gibbs sampling algorithm \citep{Phan.2008}.
+The LDA conceptualizes topics as a probability distribution over the vocabulary of the corpus, and document as a set of words, each drawn from a probability distribution over topics specific to that document.
+The term \textit{Dirichlet} comes from the fact that the word distribution $\beta_{t}$ of topic $t$ is generated from a Dirichlet distribution $\beta_{t} \sim Dirichlet(\delta)$ and the topic distribution $\theta_{d}$ for document $d$ is generated from a Dirichlet distribution $\theta_{d} \sim Dirichlet(\alpha)$ where $\delta$ and $\alpha$ act as hyper-parameters determining how concentrated the distributions of words in topics and the distributions of topics in documents are.
 
-The number of topics $T$ needs to be specified \textit{a-priori}.
-We trained 30 models with $K=5,10,\cdots,150$.
-As suggested by Griffiths and Steyvers (ref: 2008), we set $\alpha=50/K$ and $\delta=0.1$.
-We run 6,000 iterations of the Gibbs sampler with a burn in of 1,000 iterations and sample every 100 iterations.
-To prevent being stuck in a local optimum, we use 10 random initialization and keep the best model with respect to the log-likelihood.
-We choose the number of topics $K$ that yields the model with the maximum likelihood.
-Figure X shows that the model with 65 topics has the maximum likelihood.
-To increase the quality of the model, we retrain the model with 16,000 iterations of the the Gibbs sampler, a burn in of 2,000 iterations and 20 random starts and the other parameters at their original values.
+The authors of LARS followed \citet{Phan.2008} who use a Gibbs sampler to learn the distributions $\beta$ and $\theta$ of each topic and document, and \citet{Griffiths.2004} who select the number of topics yielding the best model with respect to the log-likelihood.
+The selected topic model contains 65 topics (see \figureref{fig:ll}) and consists of a term distribution for each topic indicating the importance of each term of the corpus in the topic and a topic distribution for each course indicating the importance of each topic in the course.
+\figureref{fig:gamma} shows the main topics of the core course \textit{COR1004 Political Philosophy} and \figureref{fig:beta} presents the terms that characterize topic 4 and topic 19, the main two topics of the course.
+We can see that the topics are easy to interpret and that the content of the course, that is, its topic distribution, corresponds to what we would expect from a course on political philosophy.
+
+\begin{figure}[htbp]
+	\floatconts
+	{fig:ll}
+	{\caption{Maximum likelihood model selection: the model with 65 topics is selected.}}
+	{\includegraphics[width=0.5\linewidth]{figures/model-selection}}
+\end{figure}
 
@@
 	{fig:gamma}
-	{\caption{Topic Distribution in the course COR1004 Political Philosophy.}}
+	{\caption{Topic distribution in the course COR1004 Political Philosophy.}}
 	{\includegraphics[width=0.5\linewidth]{figures/gamma-COR1004}}
@@
 	{fig:beta}
-	{\caption{Word Distribution in the main two topics of COR1004 Political Philosophy. Topic 4 corresponds to international politics and Topic 19 to philosophy.}}
-	{
-		\subfigure[Topic 4]{\label{fig:beta-4}
-			\includegraphics[width=0.2\linewidth]{figures/beta-4}}
-		\qquad
-		\subfigure[Topic 19]{\label{fig:beta-19}%
-			\includegraphics[width=0.2\linewidth]{figures/beta-19}}
-	}
+	{\caption{Word distribution in the main two topics of COR1004 Political Philosophy. Topic 4 corresponds to international politics and Topic 19 to philosophy.}}
+	{\includegraphics[width=0.75\linewidth]{figures/beta}}
 \end{figure}
 
-\begin{figure}[htbp]
-	\floatconts
-	{fig:ll}
-	{\caption{Maximum Likelihood Model Selection: we choose the model with 65 topics.}}
-	{\includegraphics[width=0.5\linewidth]{figures/model-selection}}
-\end{figure}
+\subsubsection{Model of a Student's Academic Interests}
 
+\citet{Morsomme.2019} employed the topic model to estimate the academic interests of a student from the key words that she/he enters into the system.
+The student's academic interest $AI_t$ in topic $t$ simply corresponds to the sum of the selected key words' importance in topic $t$ as determined by the topic model, that is,
+$$ AI_t = \sum_{i \in I^*} \beta_{t,i}, \;\;\;  \mbox{for} \;\;\;  t=1, \cdots, n,$$
+where $I^*$ is the set of key words selected by the student, $\beta_{t,i}$ corresponds to the importance of term $i$ in topic $t$ and $n$ is the number of topics present in the model (in this case $n=65$).
+The vector $AI = (AI_1, \cdots, AI_{n})^T$ therefore represents the academic interests of the student.
+
+\subsubsection{Course Matching and Suggestion}
+
+LARS uses the Kullback-Leibler (KL) divergence \citep{Kullback.1951} to identify the courses whose content best matche the academic interests of the student.
+Letting $P$ and $Q$ be two discrete probability distribution defined on the same probability space, the KL divergence between $P$ and $Q$ is defined as
+
+$$ D_{\mathrm{KL}} \left( P || Q \right) =  - \sum_{x \in X} P(x) \log\left(\dfrac{Q(x)}{P(x)}\right)$$
+
+\noindent and measures how different the probability distribution $P$ is from the reference probability distribution $Q$.
+LARS suggests to the students the $n$ courses whose topic distribution $\theta$ has the smallest KL divergence to her/his normalized academic interests $AI^* = \dfrac{AI}{\lvert AI \rvert}$.
+
+\subsection{Pillar 2: Warning Issuance}
 \subsubsection{Student Model}
 \label{sec:sm}
-The student model consists of two elements: academic performance and level of topic-specific expertise.
-Academic performance corresponds to the student's general GPA as well as her/his GPA in humanities, natural sciences, social sciences, skills and projects.
-These are derived from the student's transcript in a straightforward way.
-Topic-specific expertise corresponds to the knowledge that the student has acquired in each of the topics present in the topic model in previous courses.
-We posit that when students takes a course they acquire knowledge about its content and that the amount of knowledge they acquire is proportional to their grade.
-More precisely, we assume that students who obtain 10/10 in a course acquire all the knowledge related to its content and that those who obtain 5/10 only acquire half of it.
-The content of a course is determined by its topic distribution in the topic model and the grade are retrieved from the student's transcript.
-Hence if a student has taken $n$ courses and  $g_{i}$ corresponds to her/his grade in  course $i$, for $i = 1, \cdots, n$, then the expertise of the student $e_t$ in topic $t$ simply corresponds to $$e_t = \sum_{i= 1}^{n} g_i \gamma_{i,t}$$ where $\gamma_{i,t}$ corresponds to the importance of topic $t$ in course $i$ in the topic model.
-\figureref{fig:toy-expertise} presents a toy example of the contribution of individual courses to a student's expertise in 5 topics.
+The student model consists of two elements: academic performance and topic-specific expertise.
+Academic performance corresponds to the student's general GPA (grade point average) as well as her/his GPA in humanities, natural sciences, social sciences, skills and projects.
+These are derived from the students' transcripts in a straightforward way.
+Topic-specific expertise corresponds to the amount of knowledge that the student has acquired  in previous courses in each of the topics present in the topic model.
+\citet{Morsomme.2019}  posited that, when students take a course, they acquire knowledge about its content and that the amount of knowledge that they acquire is proportional to the obtained grade; that is, they assume that students who obtain 10/10 in a course acquire all the knowledge related to its content while those who obtain 5/10 only acquire half of it.
+The content of a course is determined by its topic distribution in the topic model and the grades are retrieved from the student's transcript.
+Furthermore, they assume that the knowledge acquired in different courses simply accumulates.
+Hence, if a student has taken $n$ courses and $g_{i}$ corresponds to her/his grade in course $i$, for $i = 1, \cdots, n$, then her/his expertise $exp_t$ in topic $t$ corresponds to
+
+\begin{equation}
+\label{eq:expertise}
+exp_t = \sum_{i= 1}^{n} g_i \theta_{i,t}
+\end{equation}
+
+\noindent where $\theta_{i,t}$ corresponds to the importance of topic $t$ in course $i$ as determined by the topic model.
+\tableref{tab:toy} and \figureref{fig:toy-expertise} present a toy example of the contribution of three individual courses toward a student's expertise in five topics.
+\tableref{tab:toy-gamma} and \tableref{tab:toy-grade} respectively show the topic distribution in each course as estimated by some topic model and the grades obtained by the student which are retrieved from her/his transcript.
+\tableref{tab:toy-contribution} uses \equationref{eq:expertise} to estimate the contribution of each course toward the student's topic expertise.
+\figureref{fig:toy-expertise} offers a graphical illustration of \tableref{tab:toy-contribution}.
 
@@
 	{tab:toy}
-	{\caption{Toy Example of Topic Expertise}}
+	{\caption{Toy example of the contribution of individual courses toward a student's topic expertise.}}
 	{%
-		\subtable[Topic Distribution $\gamma$]{%
+		\subtable[Topic distribution $\theta$]{%
 			\label{tab:toy-gamma}%
@@
 				Course 2 & 9/10\\
-				Course 3 & 2.5/10\\
+				Course 3 & 2/10\\
 				\bottomrule
@@
 		}\qquad
-			\subtable[Course Contribution towards Topic Expertise]{%
+			\subtable[Course contribution toward a student's topic expertise]{%
 			\label{tab:toy-contribution}%
@@
 				\midrule
-				Course 1 & 0.00 & 0.42 & 0.12 & 0.060 & 0.00\\
-				Course 2 & 0.18 & 0.18 & 0.18 & 0.180 & 0.18\\
-				Course 3 & 0.00 & 0.10 & 0.05 & 0.025 & 0.05\\
+				Course 1 & 0.00 & 0.42 & 0.12 & 0.06 & 0.00\\
+				Course 2 & 0.18 & 0.18 & 0.18 & 0.18 & 0.18\\
+				Course 3 & 0.00 & 0.08 & 0.04 & 0.02 & 0.04\\
+				\midrule
+				\bfseries Total & 0.18 & 0.68 & 0.34 & 0.26 & 0.22\\
 				\bottomrule
@@
 	{fig:toy-expertise}
-	{\caption{Contribution of Individual Courses towards a Student's Topic Expertise Profile.}}
+	{\caption{Toy example of the contribution of individual courses toward a student's topic expertise.}}
 	{\includegraphics[width=0.5\linewidth]{figures/toy-expertise}}
@@
 
-\subsubsection{Underlying Algorithm: Sparse Regression Model}
-\label{sec:sm}
+\subsubsection{Point Prediction for Grade and Warning Issuance}
 
-We fit a sparse linear regression model for grade prediction to each of the 132 courses currently offered at the college with at least 20 student enrollments since 2008.
-The input consists of the 71 variables present in the student model at the start of the course: her/his 6 GPA's  (1 general and 5 discipline-specific) and 65 levels of topic-specific expertise.
-Since the number of predictors is relatively large, we regularize the models with the lasso penalty (ref: Tibshirany, 1998).
-For each course, we use 10-fold cross-validation to find the value of the lasso tuning parameter $\lambda$ that minimizes the CV mean absolute error (mae), a more robust loss function than the squared absolute error (ref: els, 2008).
-\figureref{fig:mae-cv} presents the distribution of the CV mae for the 132 prediction models.
+To issue warnings, LARS produces point estimates for future grades.
+To accomplish this, it uses regression models.
+LARS separately fits a sparse linear regression model for grade prediction to each of the 132 courses currently offered at the University College Maastricht with at least 20 student enrollments since 2008.
+The input to the models consists of the 71 variables stored in the student model: 6 GPAs (1 general and 5 discipline-specific) and the level of expertise in the 65 topics of the topic model.
+The regression models output a point estimate for the grade.
+Note that each model is trained only on the data of the students enrolled in the associated course.
+Since the number of predictors is relatively large, the models are regularized with the Lasso penalty \citep{Tibshirani.1996} and the value of the Lasso tuning parameter $\lambda$ is chosen via cross-validation (CV).
+\figureref{fig:cv-mae} shows the distribution of the CV mean absolute error (mae) for the 132 prediction models.
 The model for the course \textit{PRO2004 Academic Debate} has the smallest prediction error (0.38 grade point) and the model for \textit{SCI3006 Mathematical Modelling} the largest (1.80 grade point).
 The mean CV mae weighted by the number of students enrolled in the course is 0.78, the median is 0.78 and the standard deviation is 0.28.
+
+% use cross-validation to find the value of the Lasso tuning parameter $lambda$ that minimizes the CV mean absolute error (mae), a more robust loss function than the squared absolute error \citep{Hastie.2009}
 
@@
 	{fig:cv-mae}
-	{\caption{Distribution of Cross-Validation Error}}
+	{\caption{Distribution of cross-validation error}}
 	{\includegraphics[width=0.5\linewidth]{figures/cv-mae}}
@@
 
-\subsubsection{Prediction Region for Grade}
-\label{sec:warning}
-Import from EDM2019
+In practice, the student selects the courses that she/he is considering for the following term and the system uses the regression models of these courses to provide point predictions for the future grades.
+A warning is issued when a predicted grade is a fail.
 
-\subsection{The Inductive Confidence Machine (Evgueni)}
-\label{sec:icm}
+We desire the following three requirements for pillar 2 Warning Issuance of LARS: accuracy, sparsity and transparency of the regression models for grade prediction.
+First, the grade predictions must be accurate so that students base their course selection on sound information.
+Second, we want the regression models to be sparse so that we can identify which topics are important to master in order to perform well in a given course.
+Such information would be extremely useful to course coordinators and curriculum managers alike.
+Third, in order to be transparent, grade predictions must be accompanied by an indication of their own accuracy.
+The first two requirements are fulfilled by the Lasso model \citep{Tibshirani.1996}, but the third requirement is not satisfied by LARS's current \textit{point predictions} for future grades.
+To fulfill the requirement for transparency, we propose to complement the existing point predictions of the system with \textit{prediction intervals}.
+In the following section, we use the conformal prediction framework to build prediction intervals for future grades that are tailored to each student.
 
-\section{Results}
-\label{sec:results}
+\section{Regression with Prediction Interval}
+\label{sec:prediction}
 
-Make figures
+Let $X$ be a space given by $n$ input variables $X_j$ ($j \in \{1, 2, \ldots, n\}$) and $Y$ be an output real-value variable.
+Any $i$-th instance in the labeled space  $(X \times Y)$ is given as a tuple $(x_i, y_i)$ where $x_i$ belongs to $X$, $x_{ij}$ is the value for the input variable $X_j$ for the instance $x_i$, and $y_i$ is the value for the output variable $Y$.
+We assume the existence of an unknown  probability distribution $P$ over $X \times Y$.
+A data set $D$ is a multi-set of $m$ instances $(x_i, y_{i}) \in (X \times Y)$ drawn from the probability distribution $P$ under the randomness assumption.
+Given an unlabeled test  instance $x_{m+1} \in X$,  the regression  task  is to find an estimate $\hat{y}_{m+1} \in \mathbb{R}$ of the value of the variable $Y$ for the instance $x_{m+1}$ according to the probability distribution $P$.
+A  prediction interval $\Gamma^\epsilon$ for the test instance $x_{m+1}$ is defined as the set $\{ y \in \mathbb{R}| p(y) > \epsilon\}$ that contains the true value of the output variable $Y$ for $x_{m+1}$ with probability of at least $1- \epsilon$, where $\epsilon$ is a given significance level.
+
+\subsection{Underlying Algorithm: Lasso Regression}
+\label{sec:lasso}
+
+Lasso is a parametric method for regression that allows regularization and variable selection \citep{Tibshirani.1996}.
+The method estimates the coefficients of the final regression model by minimizing:
+
+\[ \sum_{i = 1}^{m} ( y_i - \beta_0 - \sum_{j = 1}^{n} \beta_j x_{ij})^2 + \lambda \sum_{j = 1}^{n}\lvert\beta_j\rvert, \]
+
+\noindent i.e., by minimizing the  residual sum of the squares $\sum_{i = 1}^{m} ( y_i - \beta_0 - \sum_{j = 1}^{n} \beta_j x_{ij})^2$ and the Lasso penalty $\lambda \sum_{j = 1}^{n}\lvert\beta_j\rvert$.
+
+The Lasso method shrinks the coefficient estimates $\hat{\beta}_j$ toward 0.
+This reduces the variance of the model and thereby helps preserve its prediction accuracy.
+Furthermore, in contrast to the ridge regression penalty, the absolute-value constraint of Lasso encourages some of the coefficient estimates to be exactly zero and hence the regression model to be sparse.
+This facilitates the interpretation of the obtained models.
+
+\subsection{Conformal Prediction and the Inductive Conformal Machine}
+\label{sec:cp}
+
+The conformal prediction framework was proposed by \citet{Vovk.2005}.
+It allows the construction of  prediction intervals for regression tasks in the presence of finite data sets generated under the exchangeability assumption (which is weaker than the randomness assumption).
+In general, conformal predictors are conservatively valid; that is, the probability that any prediction interval $\Gamma^\epsilon$ does not contain the true value is not greater than $1 - \epsilon$.
+
+The conformal prediction framework assumes a nonconformity function $A$.
+The function outputs a nonconformity score $\alpha_k \in \mathbb{R}^+ \cup \{+\infty\}$ for any instance $(x_{k},y_{k})$ that indicates how unusual that instance is for the data set $D \cup \{(x_{m+1},y_{m+1})\}$.
+For the regression setting, a popular choice for the nonconformity score $\alpha_k$ of an instance $(x_{k},y_{k})$ is the residual $|y_k - \hat{y}_k|$, where $\hat{y}_k$ is the estimation for the variable $Y$ for the instance $x_k$ provided by some underlying regression model based on the data set $D \cup \{(x_{m+1}, y_{m+1})\}$ \citep{Papadopoulos.2002, Papadopoulos.2015}.
+In this paper we employ a normalized nonconformity score for the instance  $(x_{k},y_{k})$ corresponding to
+
+\begin{equation}
+\label{eq:norm}
+\alpha_k = \frac{\lvert y_k - \hat{y}_k\rvert}{\exp(\mu_k)}
+\end{equation}
+
+\noindent where $\mu_k$ is the prediction of the value $\ln \lvert y_k - \hat{y}_k \rvert$ from a second regression model \citep{Papadopoulos.2011}.
+The intuition behind equation (\equationref{eq:norm}) is that by taking into account the expected accuracy of the underlying regression model, we do not inflate the nonconformity score of instances that are intrinsically difficult to predict.
+
+Once the nonconformity scores have been computed for all the instances in the data set  $D \cup \{(x_{m+1},y_{m+1})\}$, the $p$-value $p_{m+1}$ for the output value  $y_{m+1}$ for the instance $x_{m+1}$ corresponds to the proportion of instances in $D \cup \{(x_{m+1},y_{m+1})\}$ whose nonconformity score is greater than or equal to that of the instance $(x_{m+1},y_{m+1})$; i.e.
+
+\begin{equation}
+\label{eq:p}
+p_{m+1} = \frac{\#\{i= 1,...,m|\alpha_i \geq \alpha_{m+1}\} }{m+1}.
+\end{equation}
+
+Depending on the validation procedure for estimating the nonconformity scores, there exist two approaches to generate valid conformal predictors.
+First, the \textit{transductive conformal predictors} (TCP) proposed by \citet{Saunders.1999} uses \textit{leave-one-out} cross-validation and is computationally expensive.
+To reduce the computational burden, the \textit{inductive conformal machine} (ICM) was proposed by \citet{Papadopoulos.2002}.
+It employs the hold-out method: the data $D$ is partitioned into a proper training set $D_t$ of size $p$ and a proper calibration set $D_c$ of size $q$ ($D = D_t \cup D_c$ and $m = p + q$).
+The proper training set $D_t$ is used to learn the nonconformity function $A$.
+The function is learned by training two regression models: the \textit{target} model and the \textit{error} model.
+The target model estimates the values $y_k$ which we need to estimate the residuals $\lvert y_k - \hat{y}_k\rvert$.
+The error model estimates the accuracy $\mu_k = \ln \lvert y_k - \hat{y_k} \rvert$ of the target model (see \equationref{eq:norm}).
+The use of the natural logarithm and exponent prevents the estimated residuals -- and hence the nonconformity scores -- to be negative.
+The regression models are then applied to the instances of the calibration set $D_c$ to compute their nonconformity scores $\alpha$.
+
+Once the nonconformity scores have been computed for the instances of the calibration set $D_c$, the $p$-value $p_{m+1}$ for the output value $y_{m+1}$ for the instance $x_{m+1}$ corresponds to the proportion of instances in $D_c$ whose nonconformity score is greater than or equal to that of the instance $(x_{m+1},y_{m+1})$; i.e.
+
+\begin{equation}
+\label{eq:e3}
+p_{m+1} = \frac{\#\{i= p+1,...,m|\alpha_i \geq \alpha_{m+1}\} }{m - p +1}. 
+\end{equation}
+
+The nonconformity scores of the calibration instances can be used for constructing a prediction interval for the test instance $x_{m+1}$.
+To accomplish this, the nonconformity scores are sorted in increasing order of magnitude: $ \alpha_{(1)}, \alpha_{(2)}, \ldots, \alpha_{(q)}$.
+The prediction interval for the test instance $x_{m+1}$ is constructed as:
+
+\begin{equation}
+\label{eq:e4}
+(\hat{y}_{m+1} - \alpha_{(s)} , \hat{y}_{m+1} + \alpha_{(s)})
+\end{equation}
+
+\noindent where  $\hat{y}_{m+1} $  is the value of the variable $Y$ for the instance $x_{m+1}$ estimated by the target regression model trained on the proper training set $D_t$, $s = \lfloor \epsilon (|q|+1) \rfloor$, and $\epsilon$ is a given significance level \citep{Papadopoulos.2011}.
+We note that the construction of prediction intervals is model-independent: prediction intervals can be constructed for any type of regression model.
+
+\section{Experiments}
+\label{sec:experiment}
+
+\subsection{Settings}
+
+We separately build a regression model for grade prediction for each of the 132 courses currently offered at the University College Maastricht with more than 20 student enrollments since 2008.
+To build these models, we use an ICM with normalized nonconformity scores.
+For each model, the data consists of the  models of the students enrolled in the associated course.
+A student model data consists of the 6 GPAs (1 general and 5 discipline-specific) of a student along with her/his level of expertise in the 65 topics of the topic model at the beginning of the course (see \sectionref{sec:sm}).
+
+We choose the target model to be a lasso-penalized linear regression model because it fulfills the requirements for accuracy and sparsity.
+We also choose the error model to be a lasso regression.
+We first fit the target model on the proper training set (66\% of the data) to estimate grades.
+We then fit the error model on the proper training set too to estimate the accuracy of the target model.
+Note that both models learn the lasso tuning parameter $\lambda$ with an internal 10-fold cross-validation on the proper training set.
+Finally, using \equationref{eq:e3,eq:e4}, we construct prediction intervals for each test instance  at several significance levels and evaluate their validity and tightness.
+We report the final results for an external 10-fold cross-validation.
+
+\subsection{Results}
+
+We present the results for a selection of six courses which cover a wide range of sample size and of cross-validation mean absolute error (CV mae) for the target model (see \tableref{tab:conformal-course}).
+\textit{SSC3044 Culture, Politics and Society in Contemporary Asia} and \textit{SSC3038 Contemporary Sociological Theory} have a small CV mae ($\le0.4$ point grade), while \textit{SCI2010 Introduction to Game Theory} and \textit{SCI2018 Calculus} have a large CV mae ($\ge1.4$).
+Since they are mandatory, the courses \textit{COR1004 Political Philosophy} and \textit{COR1002 Philosophy of Science} have a large sample size ($n\ge1900$), while \textit{SSC3044 Culture, Politics and Society in Contemporary Asia} and \textit{SCI2018 Calculus} have a much fewer observations ($n\le200$).
+
+\begin{table}[hbtp]
+	\floatconts
+	{tab:conformal-course}
+	{\caption{Selected courses for conformal prediction}}	
+	{\begin{tabular}{ccccc}
+			\toprule
+			\bfseries Course &\bfseries Sample Size &\bfseries CV mae \\
+			\midrule
+			SSC3044 & 136  & 0.38\\
+			SSC3038 & 272  & 0.40\\
+			COR1004 & 1998 & 0.67\\
+			COR1002 & 2067 & 1.00\\
+			SCI2010 & 417  & 1.41\\
+			SCI2018 & 198  & 1.62\\
+			\bottomrule
+	\end{tabular}}	
+\end{table}
+
+\tableref{tab:conformal-summary} and \figureref{fig:conformal-error} present the error rate of the prediction intervals constructed with the ICM at different significance levels for each course, that is, the proportion of intervals that do not contain the true grade of the student.
+We see that the prediction intervals are conservatively valid; that is, given a significance level, the probability that a prediction interval does not contain the true value is not greater than the significance level.
+
+\figureref{fig:conformal-width} shows the distribution of prediction interval width across different significance levels for each course.
+The dots correspond to the median of the distributions and the bars to the 10th and 90th percentiles.
+The width $1$ is highlighted for reference.
+We observe that the width varies across courses.
+The ICM produces relatively narrow intervals for the course COR1004, SSC3038 and SSC3044 which tend to be less than 1 unit wide for most levels of significance.
+But for SCI2010 and SCI2018, the interval become wide very quickly: they are wider than 1 unit at significance levels as large as $0.5$.
+In fact, the prediction interval width seems to be associated with the CV mae: courses with a small CV mae, such as SSC3044, SSC3038 and COR1004, have relatively tight intervals while those with a large CV mae, such as SCI2010 and SCI2018, have wide intervals.
+
+\begin{table}[hbtp]
+	\floatconts
+	{tab:conformal-summary}
+	{\caption{Prediction interval tightness and empirical validity of the ICM.}}	
+	{\begin{tabular}{cccccccccc}
+			\toprule
+			\multirow{2}{*}{\bfseries Course} & \multicolumn{3}{c}{\bfseries Median Width} & \multicolumn{3}{c}{\bfseries Error Rate}\\
+			& \bfseries 0.05 & \bfseries 0.1 & \bfseries 0.2 & \bfseries 0.05 & \bfseries 0.1 & \bfseries 0.2\\
+			\midrule
+			COR1002 & 2.39 & 1.93 & 1.46 & 0.05 & 0.10 & 0.20\\
+			COR1004 & 1.63 & 1.29 & 1.01 & 0.05 & 0.10 & 0.19\\
+			SCI2010 & 3.69 & 2.86 & 2.18 & 0.05 & 0.12 & 0.22\\
+			SCI2018 & 4.68 & 4.02 & 3.05 & 0.04 & 0.08 & 0.17\\
+			SSC3038 & \bfseries 0.91 & \bfseries 0.72 & \bfseries 0.50 & 0.07 & 0.14 & 0.23\\
+			SSC3044 & 1.02 & 0.84 & 0.63 & 0.04 & 0.07 & 0.12\\
+			\bottomrule
+	\end{tabular}}	
+\end{table}
+
+\begin{figure}[htbp]
+	\floatconts
+	{fig:conformal-error}
+	{\caption{Empirical validity of the ICM}}
+	{\includegraphics[width=0.8\linewidth]{figures/conformal-error}}
+\end{figure}
+
+\begin{figure}[htbp]
+	\floatconts
+	{fig:conformal-width}
+	{\caption{Tightness of prediction interval constructed with the ICM. The dots correspond to the median width and the bars to the 10th and 90th percentiles.}}
+	{\includegraphics[width=0.8\linewidth]{figures/conformal-width}}
+\end{figure}
 
@@
 
-valid
+In this paper, we complemented LARS's point predictions for course grades with prediction intervals constructed using the conformal prediction framework.
+We used the ICM with a standardized nonconformity score to construct prediction intervals that are tailored to each student.
+The results from a selection of 6 courses covering a wide range of sample size and CV mae of the underlying model indicate that the prediction intervals are conservatively valid and that their width seems to be associated with the accuracy of the underlying model.
+The courses SSC3038 and SSC3044, for example, have the tighter intervals with a median width close to 1 unit at the significance level $0.05$.
+This result shows that ICM can construct prediciton intervals that are useful for LARS and its pillar 2 for warning issuance.
 
-width correlated to accuracy of underlying algorithm i.e. CV error of lasso
+Yet, courses whose underlying model lacks accuracy end up with prediction intervals that are too wide to be useful.
+To make the intervals tighter, we will consider two approaches in our future research.
+First, we will try to improve the performance of the underlying regression model by considering methods that tend to be more accurate than Lasso regression, such as random forests or gradient boosting.
+Second, we will improve the informational efficiency of the ICM with cross-conformal prediction \citep{Vovk.2015} or its faster version \citep{Beganovic.2018}.
 
-\section{Comments to Evgueni}
+\acks{Our thanks to the University College Maastricht, Maastricht University, the Institute of Data Science, the Department of Data Science and Knowledge Engineering, and in particular to Peter Vermeer for initiating the project and enabling collaboration with the University College Maastricht.}
 
-Focus on conformal prediction instead of recommender system, lasso, topic model, etc. This way, the paper is simpler to follow.
-
-If we want to expand on lasso, we should write a paper on lasso itself; just like we are doing with grade prediction. The same goes for topic model.
-
-%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%
-
-% end of paper
-
-%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%
-
-\section{others}
-
-This is a sample article that uses the \textsf{jmlr} class with
-the \texttt{wcp} class option.  Please follow the guidelines in
-this sample document as it can help to reduce complications when
-combining the articles into a book. Please avoid using obsolete
-commands, such as \verb|\rm|, and obsolete packages, such as
-\textsf{epsfig}.\footnote{See
-\url{http://www.ctan.org/pkg/l2tabu}}
-
-Please also ensure that your document will compile with PDF\LaTeX.
-If you have an error message that's puzzling you, first check for it
-at the UK TUG FAQ
-\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
-that doesn't help, create a minimal working example (see
-\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
-to somewhere like TeX on StackExchange
-(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
-(\url{http://www.latex-community.org/forum/}).
-
-\begin{note}
-This is an numbered theorem-like environment that was defined in
-this document's preamble.
-\end{note}
-
-\subsection{Sub-sections}
-
-Sub-sections are produced using \verb|\subsection|.
-
-\subsubsection{Sub-sub-sections}
-
-Sub-sub-sections are produced using \verb|\subsubsection|.
-
-\paragraph{Sub-sub-sub-sections}
-
-Sub-sub-sub-sections are produced using \verb|\paragraph|.
-These are unnumbered with a running head.
-
-\subparagraph{Sub-sub-sub-sub-sections}
-
-Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
-These are unnumbered with a running head.
-
-\section{Cross-Referencing}
-
-Always use \verb|\label| and \verb|\ref| (or one of the commands
-described below) when cross-referencing.  For example, the next
-section is Section~\ref{sec:math}. The \textsf{jmlr} class
-provides some convenient cross-referencing commands:
-\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
-\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
-\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
-\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
-\verb|\exampleref| and \verb|\appendixref|. The argument of these
-commands may either be a single label or a comma-separated list
-of labels. Examples:
-
-Referencing sections: \sectionref{sec:math} or
-\sectionref{sec:intro,sec:math} or
-\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.
-
-Referencing equations: \equationref{eq:trigrule} or
-\equationref{eq:trigrule,eq:df} or
-\equationref{eq:trigrule,eq:f,eq:df,eq:y}.
-
-Referencing tables: \tableref{tab:operatornames} or
-\tableref{tab:operatornames,tab:example} or
-\tableref{tab:operatornames,tab:example,tab:example-booktabs}.
-
-Referencing figures: \figureref{fig:nodes} or
-\figureref{fig:nodes,fig:teximage} or
-\figureref{fig:nodes,fig:teximage,fig:subfigex} or
-\figureref{fig:circle,fig:square}.
-
-Referencing algorithms: \algorithmref{alg:gauss} or
-\algorithmref{alg:gauss,alg:moore} or
-\algorithmref{alg:gauss,alg:moore,alg:net}.
-
-Referencing theorem-like environments: \theoremref{thm:eigenpow},
-\lemmaref{lem:sample}, \remarkref{rem:sample}, 
-\corollaryref{cor:sample}, \definitionref{def:sample},
-\conjectureref{con:sample}, \axiomref{ax:sample} and
-\exampleref{ex:sample}.
-
-Referencing appendices: \appendixref{apd:first} or
-\appendixref{apd:first,apd:second}.
-
-\section{Equations}
-\label{sec:math}
-
-The \textsf{jmlr} class loads the \textsf{amsmath} package, so
-you can use any of the commands and environments defined there.
-(See the \textsf{amsmath} documentation for further
-details.\footnote{Either \texttt{texdoc amsmath} or
-\url{http://www.ctan.org/pkg/amsmath}})
-
-Unnumbered single-lined equations should be displayed using
-\verb|\[| and \verb|\]|. For example:
-\[E = m c^2\]
-Numbered single-line equations should be displayed using the
-\texttt{equation} environment. For example:
-\begin{equation}\label{eq:trigrule}
-\cos^2\theta + \sin^2\theta \equiv 1
-\end{equation}
-This can be referenced using \verb|\label| and \verb|\equationref|.
-For example, \equationref{eq:trigrule}.
-
-Multi-lined numbered equations should be displayed using the
-\texttt{align} environment.\footnote{For reasons why you 
-shouldn't use the obsolete \texttt{eqnarray} environment, see
-Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
-\begin{align}
-f(x) &= x^2 + x\label{eq:f}\\
-f'(x) &= 2x + 1\label{eq:df}
-\end{align}
-Unnumbered multi-lined equations should be displayed using the
-\texttt{align*} environment. For example:
-\begin{align*}
-f(x) &= (x+1)(x-1)\\
-&= x^2 - 1
-\end{align*}
-If you want to mix numbered with unnumbered lines use the
-align environment and suppress unwanted line numbers with
-\verb|\nonumber|. For example:
-\begin{align}
-y &= x^2 + 3x - 2x + 1\nonumber\\
-&= x^2 + x + 1\label{eq:y}
-\end{align}
-An equation that is too long to fit on a single line can be
-displayed using the \texttt{split} environment. 
-Text can be embedded in an equation using \verb|\text| or
-\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
-See the \textsf{amsmath} documentation for further details.
-
-\subsection{Operator Names}
-\label{sec:op}
-
-Predefined operator names are listed in \tableref{tab:operatornames}.
-For additional operators, either use \verb|\operatorname|,
-for example $\operatorname{var}(X)$ or declare it with
-\verb|\DeclareMathOperator|, for example
-\begin{verbatim}
-\DeclareMathOperator{\var}{var}
-\end{verbatim}
-and then use this new command. If you want limits that go above and
-below the operator (like \verb|\sum|) use the starred versions
-(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).
-
-\begin{table}[htbp]
-\floatconts
-  {tab:operatornames}%
-  {\caption{Predefined Operator Names (taken from 
-   \textsf{amsmath} documentation)}}%
-  {%
-\begin{tabular}{rlrlrlrl}
-\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
-\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
-\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
-\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
-\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
-\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
-\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
-\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
-\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
-\end{tabular}\par
-\begin{tabular}{rlrl}
-\cs{varlimsup} & $\varlimsup$ 
-& \cs{varinjlim} & $\varinjlim$\\
-\cs{varliminf} & $\varliminf$ 
-& \cs{varprojlim} & $\varprojlim$
-\end{tabular}
-}
-\end{table}
-
-\section{Vectors and Sets}
-\label{sec:vec}
-
-Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
-The \textsf{jmlr} class also provides \cs{set} to typeset a
-set. For example $\set{S}$.
-
-\section{Floats}
-\label{sec:floats}
-
-Floats, such as figures, tables and algorithms, are moving
-objects and are supposed to float to the nearest convenient
-location. Please don't force them to go in a particular place. In
-general it's best to use the \texttt{htbp} specifier and don't
-put the figure or table in the middle of a paragraph (that is
-make sure there's a paragraph break above and below the float).
-Floats are supposed to have a little extra space above and below
-them to make them stand out from the rest of the text. This extra
-spacing is put in automatically and shouldn't need modifying.
-
-To ensure consistency, please \emph{don't} try changing the format of the caption by doing
-something like:
-\begin{verbatim}
-\caption{\textit{A Sample Caption.}}
-\end{verbatim}
-or
-\begin{verbatim}
-\caption{\em A Sample Caption.}
-\end{verbatim}
-You can, of course, change the font for individual words or 
-phrases, for example:
-\begin{verbatim}
-\caption{A Sample Caption With Some \emph{Emphasized Words}.}
-\end{verbatim}
-
-\subsection{Tables}
-\label{sec:tables}
-
-Tables should go in the \texttt{table} environment. Within this
-environment use \verb|\floatconts| (defined by \textsf{jmlr})
-to set the caption correctly and center the table contents.
-
-\begin{table}[t]
-
-	\caption{\label{tab:}Student Data \label{tab:data-student}}
-	\centering
-	\begin{tabular}{ccccc}
-		\toprule
-		Student ID & Course ID & Academic Year & Period & Grade\\
-		\midrule
-		44940 & CAP3000 & 2009-2010 & 4 & 8.8\\
-		37490 & SSC2037 & 2009-2010 & 4 & 8.4\\
-		71216 & HUM1003 & 2010-2011 & 4 & 6.8\\
-		44212 & SSC2049 & 2010-2011 & 2 & 8.4\\
-		85930 & SSC2043 & 2011-2012 & 1 & 4.3\\
-		\addlinespace
-		14492 & COR1004 & 2012-2013 & 2 & 8.5\\
-		34750 & HUM2049 & 2013-2014 & 5 & 6.0\\
-		32316 & SSC1001 & 2013-2014 & 1 & 8.5\\
-		22092 & SCI1009 & 2014-2015 & 1 & 6.4\\
-		19512 & COR1004 & 2016-2017 & 5 & 7.0\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[htbp]
- % The first argument is the label.
- % The caption goes in the second argument, and the table contents
- % go in the third argument.
-\floatconts
-  {tab:example}%
-  {\caption{An Example Table}}%
-  {\begin{tabular}{ll}
-  \bfseries Dataset & \bfseries Result\\
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876
-  \end{tabular}}
-\end{table}
-
-If you want horizontal rules you can use the \textsf{booktabs}
-package which provides the commands \verb|\toprule|, 
-\verb|\midrule| and \verb|\bottomrule|. For example, see
-\tableref{tab:example-booktabs}.
-
-\begin{table}[hbtp]
-\floatconts
-  {tab:example-booktabss}
-  {\caption{A Table With Horizontal Lines}}
-  {\begin{tabular}{ll}
-  \toprule
-  \bfseries Dataset & \bfseries Result\\
-  \midrule
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876\\
-  \bottomrule
-  \end{tabular}}
-\end{table}
-
-If you want vertical lines as well, you can't use the
-\textsf{booktabs} commands as there'll be some unwanted gaps.
-Instead you can use \LaTeX's \verb|\hline|, but the rows may
-appear a bit cramped.  You can add extra space above or below a
-row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
-see \tableref{tab:example-hline}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-hline}
-  {\caption{A Table With Horizontal and Vertical Lines}}%
-  {%
-    \begin{tabular}{|l|l|}
-    \hline
-    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
-    \abovestrut{2.2ex}Data1 & 0.12345\\
-    Data2 & 0.67890\\
-    Data3 & 0.54321\\
-    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
-    \end{tabular}
-  }
-\end{table}
-
-If you want to align numbers on their decimal point, you can
-use the \textsf{siunitx} package. For example, see
-\tableref{tab:example-siunitx}. For further details see the
-\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
-siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-siunitx}
-  {\caption{A Table With Numbers Aligned on the Decimal Point}}
-  {\begin{tabular}{lS[tabformat=3.5]}
-  \bfseries Dataset & {\bfseries Result}\\
-  Data1 & 0.12345\\
-  Data2 & 10.6789\\
-  Data3 & 50.543\\
-  Data4 & 200.09876
-  \end{tabular}}
-\end{table}
-
-If the table is too wide, you can adjust the inter-column
-spacing by changing the value of \verb|\tabcolsep|. For
-example:
-\begin{verbatim}
-\setlength{\tabcolsep}{3pt}
-\end{verbatim}
-If the table is very wide but not very long, you can use the
-\texttt{sidewaystable} environment defined in the
-\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
-If the table is too long to fit on a page, you should use the
-\texttt{longtable} environment defined in the \textsf{longtable}
-package (so use \verb|\usepackage{longtable}|).
-
-\subsection{Figures}
-\label{sec:figures}
-
-Figures should go in the \texttt{figure} environment. Within this
-environment, use \verb|\floatconts| to correctly position the
-caption and center the image. Use \verb|\includegraphics|
-for external graphics files but omit the file extension. Do not
-use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
-image, it's better to use a fraction of the line width rather
-than an explicit length. For example, see \figureref{fig:nodes}.
-
-\begin{figure}[htbp]
- % Caption and label go in the first argument and the figure contents
- % go in the second argument
-\floatconts
-  {fig:nodess}
-  {\caption{Example Image}}
-  {\includegraphics[width=0.5\linewidth]{figures/nodes}}
-\end{figure}
-
-If your image is made up of \LaTeX\ code (for example, commands
-provided by the \textsf{pgf} package) you can include it using
-\cs{includeteximage} (defined by the \textsf{jmlr} class). This
-can be scaled and rotated in the same way as \cs{includegraphics}.
-For example, see \figureref{fig:teximage}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:teximage}
-  {\caption{Image Created Using \LaTeX\ Code}}
-  {\includeteximage[angle=45]{figures/teximage}}
-\end{figure}
-
-If the figure is too wide to fit on the page, you can use the
-\texttt{sidewaysfigure} environment defined in the
-\textsf{rotating} package.
-
-Don't use \verb|\graphicspath|. If the figures are contained in
-a subdirectory, specify this when you include the image, for
-example \verb|\includegraphics{figures/mypic}|.
-
-\subsubsection{Sub-Figures}
-\label{sec:subfigures}
-
-Sub-figures can be created using \verb|\subfigure|, which is
-defined by the \textsf{jmlr} class. The optional argument allows
-you to provide a subcaption. The label should be placed in the
-mandatory argument of \verb|\subfigure|. You can reference the
-entire figure, for example \figureref{fig:subfigex}, or you can
-reference part of the figure using \verb|\figureref|, for example
-\figureref{fig:circle}. Alternatively you can reference the
-subfigure using \verb|\subfigref|, for example
-\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex}
-  {\caption{An Example With Sub-Figures.}}
-  {%
-    \subfigure[A Circle]{\label{fig:circle}%
-      \includegraphics[width=0.2\linewidth]{figures/circle}}%
-    \qquad
-    \subfigure[A Square]{\label{fig:square}%
-      \includegraphics[width=0.2\linewidth]{figures/square}}
-  }
-\end{figure}
-
-By default, the sub-figures are aligned on the baseline.
-This can be changed using the second optional argument
-of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the subfigures
-\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex2}
-  {\caption{Another Example With Sub-Figures.}}
-  {%
-    \subfigure[A Small Circle][c]{\label{fig:circle2}%
-      \includegraphics[width=0.1\linewidth]{figures/circle}}%
-    \qquad
-    \subfigure[A Square][c]{\label{fig:square2}%
-      \includegraphics[width=0.2\linewidth]{figures/square}}
-  }
-\end{figure}
-
-\subsection{Sub-Tables}
-\label{sec:subtables}
-There is an analogous command \verb|\subtable| for sub-tables.
-It has the same syntax as \verb|\subfigure| described above.
-You can reference the table using \verb|\tableref|, for example
-\tableref{tab:subtabex} or you can reference part of the table,
-for example \tableref{tab:ab}. Alternatively you can reference the
-subtable using \verb|\subtabref|, for example
-\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex}
- {\caption{An Example With Sub-Tables}}
- {%
-   \subtable{%
-     \label{tab:ab}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable{%
-     \label{tab:cd}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-By default, the sub-tables are aligned on the top.
-This can be changed using the second optional argument
-of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the sub-tables
-\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex2}
- {\caption{Another Example With Sub-Tables}}
- {%
-   \subtable[][c]{%
-     \label{tab:ab2}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable[][c]{%
-     \label{tab:cd2}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-\subsection{Algorithms}
-\label{sec:algorithms}
-
-Enumerated textual algorithms can be displayed using the
-\texttt{algorithm} environment. Within this environment, use
-use an \texttt{enumerate} or nested \texttt{enumerate} environments.
-For example, see \algorithmref{alg:gauss}. Note that algorithms
-float like figures and tables.
-
-\begin{algorithm}[htbp]
-\floatconts
-{alg:gauss}% label
-{\caption{The Gauss-Seidel Algorithm}}
-{% contents
-\begin{enumerate}
-  \item For $k=1$ to maximum number of iterations
-    \begin{enumerate}
-      \item For $i=1$ to $n$
-        \begin{enumerate}
-        \item $x_i^{(k)} = 
-          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
-          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
-        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
-          where $\epsilon$ is a specified stopping criteria, stop.
-      \end{enumerate}
-    \end{enumerate}
-\end{enumerate}
-}
-\end{algorithm}
-
-You can use \verb|\caption| and \verb|\label| without using
-\verb|\floatconts| (as in \algorithmref{alg:moore}).
-
-If you'd rather have the same numbering throughout the algorithm
-but still want the convenient indentation of nested 
-\texttt{enumerate} environments, you can use the
-\texttt{enumerate*} environment provided by the \textsf{jmlr}
-class. For example, see \algorithmref{alg:moore}.
-
-\begin{algorithm}
-\caption{Moore's Shortest Path}\label{alg:moore}
-Given a connected graph $G$, where the length of each edge is 1:
-\begin{enumerate*}
-  \item Set the label of vertex $s$ to 0
-  \item Set $i=0$
-  \begin{enumerate*}
-    \item \label{step:locate}Locate all unlabelled vertices 
-          adjacent to a vertex labelled $i$ and label them $i+1$
-    \item If vertex $t$ has been labelled,
-    \begin{enumerate*}
-      \item[] the shortest path can be found by backtracking, and 
-      the length is given by the label of $t$.
-    \end{enumerate*}
-    otherwise
-    \begin{enumerate*}
-      \item[] increment $i$ and return to step~\ref{step:locate}
-    \end{enumerate*}
-  \end{enumerate*}
-\end{enumerate*}
-\end{algorithm}
-
-Pseudo code can be displayed using the \texttt{algorithm2e}
-environment. This is defined by the \textsf{algorithm2e} package
-(which is automatically loaded) so check the \textsf{algorithm2e}
-documentation for further details.\footnote{Either \texttt{texdoc
-algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
-For an example, see \algorithmref{alg:net}.
-
-\begin{algorithm2e}
-\caption{Computing Net Activation}
-\label{alg:net}
- % older versions of algorithm2e have \dontprintsemicolon instead
- % of the following:
- %\DontPrintSemicolon
- % older versions of algorithm2e have \linesnumbered instead of the
- % following:
- %\LinesNumbered
-\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
-\KwOut{$y$, the net activation}
-$y\leftarrow 0$\;
-\For{$i\leftarrow 1$ \KwTo $n$}{
-  $y \leftarrow y + w_i*x_i$\;
-}
-\end{algorithm2e}
-
-\section{Description Lists}
-
-The \textsf{jmlr} class also provides a description-like 
-environment called \texttt{altdescription}. This has an
-argument that should be the widest label in the list. Compare:
-\begin{description}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{description}
-with
-\begin{altdescription}{differentiate}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{altdescription}
-
-\section{Theorems, Lemmas etc}
-\label{sec:theorems}
-
-The following theorem-like environments are predefined by
-the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
-\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
-\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
-and \texttt{axiom}. You can use the \texttt{proof} environment
-to display the proof if need be, as in \theoremref{thm:eigenpow}.
-
-\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
-If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
-$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
-with eigenvector $\vec{\xi}$.
-\begin{proof}
-Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
-$\xi$, then
-\begin{align*}
-\vec{B}\vec{\xi} &= \lambda\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
-\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
-&= \lambda\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^2\vec{\xi}
-\end{align*}
-Therefore true for $n=2$. Now assume true for $n=k$:
-\begin{align*}
-\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
-\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
-&= \lambda^k\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^{k+1}\vec{\xi}
-\end{align*}
-Therefore true for $n=k+1$. Therefore, by induction, true for all
-$n$.
-\end{proof}
-\end{theorem}
-
-\begin{lemma}[A Sample Lemma]\label{lem:sample}
-This is a lemma.
-\end{lemma}
-
-\begin{remark}[A Sample Remark]\label{rem:sample}
-This is a remark.
-\end{remark}
-
-\begin{corollary}[A Sample Corollary]\label{cor:sample}
-This is a corollary.
-\end{corollary}
-
-\begin{definition}[A Sample Definition]\label{def:sample}
-This is a definition.
-\end{definition}
-
-\begin{conjecture}[A Sample Conjecture]\label{con:sample}
-This is a conjecture.
-\end{conjecture}
-
-\begin{axiom}[A Sample Axiom]\label{ax:sample}
-This is an axiom.
-\end{axiom}
-
-\begin{example}[An Example]\label{ex:sample}
-This is an example.
-\end{example}
-
-\section{Color vs Grayscale}
-\label{sec:color}
-
-It's helpful if authors supply grayscale versions of their
-figures in the event that the article is to be incorporated into
-a black and white printed book. With external PDF, PNG or JPG
-graphic files, you just need to supply a grayscale version of the
-file. For example, if the file is called \texttt{myimage.png},
-then the gray version should be \texttt{myimage-gray.png} or
-\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
-need to modify your code. The \textsf{jmlr} class checks for
-the existence of the grayscale version if it is print mode 
-(provided you have used \verb|\includegraphics| and haven't
-specified the file extension).
-
-You can use \verb|\ifprint| to determine which mode you are in.
-For example, in \figureref{fig:nodes}, the 
-\ifprint{dark gray}{purple} ellipse represents an input and the
-\ifprint{light gray}{yellow} ellipse represents an output.
-Another example: {\ifprint{\bfseries}{\color{red}}important text!}
-
-You can use the class option \texttt{gray} to see how the
-document will appear in gray scale mode. \textcolor{blue}{Colored
-text} will automatically be converted to gray scale.
-
-The \textsf{jmlr} class loads the \textsf{xcolor}
-package, so you can also define your own colors. For example:
-\ifprint
-  {\definecolor{myred}{gray}{0.5}}%
-  {\definecolor{myred}{rgb}{0.5,0,0}}%
-\textcolor{myred}{XYZ}.
-
-The \textsf{xcolor} class is loaded with the \texttt{x11names}
-option, so you can use any of the x11 predefined colors (listed
-in the \textsf{xcolor} documentation\footnote{either 
-\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).
-
-\section{Citations and Bibliography}
-\label{sec:cite}
-
-The \textsf{jmlr} class automatically loads \textsf{natbib}.
-This sample file has the citations defined in the accompanying
-BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
-citation use \verb|\citep|. For example
-\citep{guyon-elisseeff-03}. For a textual citation use
-\verb|\citet|. For example \citet{guyon2007causalreport}.
-Both commands may take a comma-separated list, for example
-\citet{guyon-elisseeff-03,guyon2007causalreport}.
-
-These commands have optional arguments and have a starred
-version. See the \textsf{natbib} documentation for further
-details.\footnote{Either \texttt{texdoc natbib} or
-\url{http://www.ctan.org/pkg/natbib}}
-
-The bibliography is displayed using \verb|\bibliography|.
-
-\acks{Our thanks to the University College Maastricht, Maastricht University, the Institute of Data Science, and the Department of Data Science and Knowledge Engineering, in particular to Peter Vermeer for initiating the project and enabling collaboration with the University College Maastricht.}
-
-\bibliography{jmlr-sample}
-
-\appendix
-
-\section{First Appendix}\label{apd:first}
-
-This is the first appendix.
-
-\section{Second Appendix}\label{apd:second}
-
-This is the second appendix.
+\bibliography{bibliography}
 

### 2019-05-22 conference figures COPA2019.Rmd
create plots and table for results of conformal prediction

@@
 load("Output/CV.RDATA")
+load("Output/conformal.RDATA")
 
@@
 plot_height <- plot_width / 1.6 
+```
+
+```{r latex_table}
+latex_table <- function(df, filename = "test"){
+
+  df %>%
+    kable("latex", booktabs = TRUE, align = "c") %>%
+    write(file = str_c(output_folder, "/", filename, ".txt"))
+}
 ```
@@
 
-```{r}
+```{r course_data}
 course_data <- d_text$catalogues %>%
@@
 # Student data
-
-```{r}
-latex_table <- function(df, filename = "test"){
-
-  df %>%
-    kable("latex", booktabs = TRUE, align = "c") %>%
-    write(file = str_c(output_folder, "/", filename, ".txt"))
-}
-```
 
@@
 
+## EDM2019 style
 ```{r}
@@
 
+## 2 pillar style
+```{r}
+grViz("digraph flowchart{
+
+      fontname = Helvetica
+      size = 15
+      newrank = true;
+
+      node [fontname = Helvetica, shape = rectangle, style = filled, fillcolor = white]
+      edge [fontname = Helvetica, decorate = TRUE]
+
+      subgraph cluster_input_kw {
+      label = 'User Input';
+      penwidth = 2;
+
+      KW [label = 'Selected Key Words']
+      }
+
+      subgraph cluster_data {
+      label = 'Data';
+      penwidth = 2;
+
+		  node [shape = cylinder];
+      SD [label = 'Student Data', group = 2]
+      CD [label = 'Course Data' , group = 1]
+      }
+
+      subgraph cluster_input_course {
+      label = 'User Input';
+      penwidth = 2;
+
+      CS [label = 'Selected Courses']
+      }
+
+      subgraph cluster_pillar_1{
+      label = 'Pillar 1: Course Suggestion';
+      penwidth = 2;
+
+      TM  [label = 'Topic Model \nof the Courses', group = 1]
+      AI  [label = 'Model of \nStudent´s Academic Interests']
+      x1  [shape = circle, width = .01, height = .01, label = '']
+      SUG [label = 'Course Suggestions', ]
+
+      } # close pillar 1
+
+      subgraph cluster_pillar_2{
+      label = 'Pillar 2: Warning Issuance';
+      penwidth = 2;
+
+      SM  [label = 'Student Model'    , group = 2]
+      PM  [label = 'Predictive Models', group = 2]
+      GP  [label = 'Point Prediction \nfor Grade' , group = 2]
+      WAR [label = 'Warning'          , group = 2]
+      PR  [label = 'Prediction Region', color = red, fontcolor = red]
+
+      } # close pillar 2
+
+		  { rank=same; KW; CD; SD; CS}
+		  { rank=same; TM; SM}
+      { rank=same; PR; WAR; SUG}
+
+      # edges
+      CD -> TM [label = '  LDA'];
+      {TM, KW} -> AI;
+      {TM, AI} -> x1 [arrowhead = none]
+      x1 -> SUG [label = '  KL distance'];
+
+      SD -> SM;
+      TM -> SM;
+      SM -> PM [label = '  Lasso'];
+      {PM, CS} -> GP;
+      GP -> WAR;
+      GP -> PR [label = ' Conformal Prediction', color = red, fontcolor = red];
+
+      }
+      ")
+
+# Save by hand
+# File name: Conference/COPA2019/paper/figures/flowchart
+```
+
 # Model Selection (topic model)
@@
 
+```{r reorder_within}
+reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
+  new_x <- paste(x, within, sep = sep)
+  stats::reorder(new_x, by, FUN = fun)
+}
+
+scale_x_reordered <- function(..., sep = "___") {
+  reg <- paste0(sep, ".+$")
+  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
+}
+
+scale_y_reordered <- function(..., sep = "___") {
+  reg <- paste0(sep, ".+$")
+  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
+}
+```
+
 ```{r plot_beta}
@@
   beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
+    filter(topic %in% top) %>% 
+    group_by(topic) %>%
+    top_n(9, beta) %>%
 
     ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
+    geom_col(aes(x = reorder_within(term, beta, topic), y = beta)) +
 
@@
 
-    labs(title = NULL,
-         x = "Terms",
-         y = "Beta"
-         )
+    labs(title = NULL, x = "Terms", y = "Beta") +
 
-  ggsave(filename = str_c("Beta-", topic, ".jpeg"), path = output_folder,
-         width = plot_width / resize_factor, height = plot_height / resize_factor)
+    facet_wrap( ~ topic, scales = "free_y") +
+    scale_x_reordered()
+
+  ggsave(filename = "beta.jpeg", path = output_folder,
+         width = 1.5 * plot_width / resize_factor, height = plot_height / resize_factor)
 
@@
 
-resize_factor <- 2
+resize_factor <- 1.8
 
-plot_beta(4, resize_factor = resize_factor)
-plot_beta(19, resize_factor = resize_factor)
+plot_beta(c(4,19), resize_factor = resize_factor)
 ```
@@
 transcript <- tibble(Course    = courses,
-                     Grade     = c(6  , 9  , 2.5))
+                     Grade     = c(6  , 9  , 2))
 
@@
 topic_expertise <- df1 %>%
-  select(-gamma, - Grade) %>% 
-  spread(key = Topic, value = contribution)
+  select(-gamma, - Grade)%>% 
+  spread(key = Topic, value = contribution) %>%
+  add_row(Course = "Total", `Topic 1` = 0.18, `Topic 2` = 0.68, `Topic 3` = 0.34, `Topic 4` = 0.26, `Topic 5` = 0.22)
 
@@
 df1 %>% 
+  mutate(Topic = factor(Topic, levels = str_c("Topic ", 5:1))) %>%
   ggplot(aes(x = Topic, y = contribution, fill = Course)) +
@@
 ```
+
+# Conformal
+
+## course table
+
+```{r}
+course_table %>%
+  select(- df) %>%
+  mutate(cv_error = cv_error %>% round(2)) %>%
+  latex_table("conformal-course")
+```
+
+## width
+
+```{r}
+d_width <- conformal_results %>%
+  group_by(course, significance) %>%
+  summarise(q_50 = quantile(width, 0.5), # median
+            q_10 = quantile(width, 0.1),
+            q_90 = quantile(width, 0.9))
+```
+
+```{r}
+d_width %>%
+  ggplot() +
+  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5) +
+  geom_hline(yintercept = 1, linetype = "dashed") +
+  geom_line(aes(significance, q_50, group = 1)) +
+  geom_point(aes(significance, q_50)) +
+  facet_wrap( ~ course) +
+  labs(y = "Width",
+       x = "Significance Level") +
+  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
+
+ggsave(filename = "conformal-width.jpeg", path = output_folder,
+       width = plot_width, height = plot_height)
+```
+
+## Error
+
+```{r}
+d_error <- conformal_results %>%
+  group_by(course, significance) %>%
+  summarise(error = mean(!hit))
+```
+
+```{r}
+d_error %>%
+  ggplot(aes(x = significance, y = error)) +
+  geom_abline(slope = 1, linetype = "longdash") +
+  geom_line(aes(group = 1)) +
+  geom_point() +
+  facet_wrap( ~ course) +
+  labs(y = "Error Rate",
+       x = "Significance Level") +
+  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
+
+ggsave(filename = "conformal-error.jpeg", path = output_folder,
+       width = plot_width, height = plot_height)
+```
+
+## Table
+```{r}
+conformal_results %>%
+  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
+  group_by(course, significance) %>%
+  summarize(width_med  = median(width),
+            error_rate = mean(!hit)) %>%
+
+  gather(key = "measure", value = "output", width_med, error_rate) %>%
+  mutate(output = round(output, 2)) %>%
+  unite(id, measure, significance, sep = "-") %>%
+  spread(key = id, value = output) %>%
+
+  select(course, matches("med"), matches("error")) %>%
+  latex_table("conformal-table")
+```

### 2019-06-05 Data Preparation - Course Data.Rmd
make use of useful_functions file

--- 2019-04-16 Data Preparation - Course Catalogues.Rmd
@@
 library(magrittr)
+
+load("Output/useful functions.RDATA")
 ```
@@
 extract_id_course <- function(string) string %>% str_sub(start = 1, end =   7)
-
-collapse_or       <- function(string) string %>% str_c(collapse = "|")
-collapse_space    <- function(string) string %>% str_c(collapse = " ")
 
@@
 ```{r d_text$manuals}
-d_text$manuals <- read_in_pdfs("./Input/Manuals 2017-18") %>% rename(`Course ID` = ID) %>% mutate(text = text %>% map_chr(str_c, collapse = " "))
+d_text$manuals <- read_in_pdfs("./Input/Manuals 2017-18") %>%
+  rename(`Course ID` = ID) %>%
+  mutate(text = text %>% map_chr(str_c, collapse = " "))
 ```
@@
 ```{r}
-d_text$catalogues <- d_text$catalogues %>% mutate(overviews = list(ID, catalogue, page_top, before_overview) %>% pmap(overview))
+d_text$catalogues <- d_text$catalogues %>%
+  mutate(overviews = list(ID, catalogue, page_top, before_overview) %>% pmap(overview))
 ```

### 2019-06-05 Data Preparation - Misc.Rmd
make use of useful_functions file

@@
 
-## Ttarget courses
+## Target courses
 ```{r}

### 2019-06-05 Data Preparation - Student Data.Rmd
make use of useful_functions file

@@
 knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
+
+load("Output/useful functions.RDATA")
 
@@
 ```{r d_transcript, cache = TRUE}
-d_transcript <- paste0("Input/Raw Grades/grades", 1 : 2, ".csv") %>%
+d_transcript <- str_c("Input/Raw Grades/grades", 1 : 2, ".csv") %>%
 
@@
 ```{r d_transcript helper}
-course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")
+course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% collapse_or
 

### 2019-06-05 Trials/Pillar 1 - Sequential Pattern Mining.Rmd
create folder for trials

--- 2019-03-22 Pillar 1 - Sequential Pattern Mining.Rmd
@@
 ```{r constants}
-course_all  <- unique(d_transcript_informative$`Course ID` )
-student_all <- unique(d_transcript_informative$`Student ID`)
+course_all  <- unique(d_transcript_elective$`Course ID` )
+student_all <- unique(d_transcript_elective$`Student ID`)
 n_students  <- length(student_all)
@@
 # Probability of taking / failing / obtaining of low grade a course
-d_support$TPH <- d_transcript_informative %>%
+d_support$TPH <- d_transcript_elective %>%
 
@@
 ```{r d_support G}
-d_support$G <- d_transcript_informative %>%
+d_support$G <- d_transcript_elective %>%
 
@@
 ```{r taken_PF_HL}
-d_transactions$taken_PF_HL <- d_transcript_informative %>%
+d_transactions$taken_PF_HL <- d_transcript_elective %>%
 
@@
   mutate(
-    course_so_far  = course_current %>% accumulate(union),
+    course_so_far  = course_current %>% purrr::accumulate(union),
     course_past    = course_so_far  %>% lag(default = NA_character_),

### 2019-06-05 Useful Functions.Rmd
create script of useful functions to reduce copy-pasting

--- 2019-05-15 Pillar 1 - Topic Profile.Rmd
@@
 
-__Considerations__:
+# Helper Functions
 
-* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.
-
-* give more weight to 3000-level courses
-
-* consider following predictors:
-     * GPA (per concentration)
-
-# Set up
-
-```{r setup, include = FALSE} 
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
-
-library(magrittr)
-library(glmnet)
-library(leaps)
-library(tidyverse)
-```
-
-```{r load, cache.lazy = TRUE} 
-load("Output/app_model.RDATA")
-load("Output/data_student.RDATA")
-load("Output/course_current.RDATA")
-
-course_target <- course_current[! str_detect(course_current, "...10..")]
-course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
-```
-
-# Topic Model
-```{r gamma_spread}
-gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
-gamma_spread <- gamma %>% spread(topic, gamma)
-beta  <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
-remove(app_model)
-```
-
-# Students' Topic Expertise
-```{r student_TP} 
-student_TP <- d_transcript_augmented %>%
-
-  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
-
-  mutate_at(vars(matches("Topic")), .funs = funs(if_else(is.na(.), 0, .))) %>% # give a value of 0 to the topics of the courses missing from the topic model.
-  mutate_at(vars(matches("Topic")), .funs = funs(Grade/10 * .)) %>% # weigh by grade
-
-  group_by(`Student ID`, time) %>%
-  summarize_at(vars(matches("Topic")), sum) %>%
-
-  group_by(`Student ID`) %>%
-  arrange(time) %>%
-
-  mutate_at(vars(matches("Topic")), lag, default = 0) %>%
-  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile at beginning of period
-
-  ungroup %>%
-
-  arrange(`Student ID`)
-```
-
-Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).
-
-# Students' Academic Performance
-
-```{r grade_ECTS} 
-d_transcript_augmented <- d_transcript_augmented %>%
-
-  mutate(is_HUM = `Course ID` %>% str_detect("HUM|SAH"),
-         is_SCI = `Course ID` %>% str_detect("SCI|SAS"),
-         is_SSC = `Course ID` %>% str_detect("SSC|SAC"),
-         is_COR = `Course ID` %>% str_detect("COR"),
-         is_SKI = `Course ID` %>% str_detect("SKI|LAN"),
-         is_PRO = `Course ID` %>% str_detect("PRO|UGR|CAP")) %>%
-
-  mutate(grade_HUM = if_else(is_HUM, Grade, NA_real_),
-         grade_SCI = if_else(is_SCI, Grade, NA_real_),
-         grade_SSC = if_else(is_SSC, Grade, NA_real_),
-         grade_COR = if_else(is_COR, Grade, NA_real_),
-         grade_SKI = if_else(is_SKI, Grade, NA_real_),
-         grade_PRO = if_else(is_PRO, Grade, NA_real_)) %>%
-
-  mutate(ECTS = case_when(
-    `Course ID` %>% str_detect("HUM|SCI|SSC|COR|PRO|SA|EXT") ~ 5  ,
-    `Course ID` %>% str_detect("SKI|LAN"                   ) ~ 2.5,
-    `Course ID` %>% str_detect("CAP|UGR"                   ) ~ 10 ,
-    TRUE                                                     ~ 5  )
-    ) %>%
-
-  mutate(ECTS_HUM = if_else(is_HUM, ECTS, NA_real_),
-         ECTS_SCI = if_else(is_SCI, ECTS, NA_real_),
-         ECTS_SSC = if_else(is_SSC, ECTS, NA_real_),
-         ECTS_COR = if_else(is_COR, ECTS, NA_real_),
-         ECTS_SKI = if_else(is_SKI, ECTS, NA_real_),
-         ECTS_PRO = if_else(is_PRO, ECTS, NA_real_)) %>%
-
-  mutate(grade_ECTS     = Grade     * ECTS,
-         grade_ECTS_HUM = grade_HUM * ECTS_HUM,
-         grade_ECTS_SCI = grade_SCI * ECTS_SCI,
-         grade_ECTS_SSC = grade_SSC * ECTS_SSC,
-         grade_ECTS_COR = grade_COR * ECTS_COR,
-         grade_ECTS_SKI = grade_SKI * ECTS_SKI,
-         grade_ECTS_PRO = grade_PRO * ECTS_PRO)
-```
-
-```{r student_GPA, cache = TRUE} 
-student_GPA <- d_transcript_augmented %>%
-
-  group_by(`Student ID`, time) %>%
-  summarize_at(vars(matches("ECTS")), list) %>%
-
-  group_by(`Student ID`) %>%
-  arrange(time) %>%
-
-  mutate_at(vars(matches("ECTS")), purrr::accumulate, c) %>%
-
-  mutate_at(vars(matches("ECTS")), map_dbl, sum, na.rm = TRUE) %>%
-
-  mutate(GPA     = grade_ECTS     / ECTS,
-         GPA_HUM = grade_ECTS_HUM / ECTS_HUM,
-         GPA_SCI = grade_ECTS_SCI / ECTS_SCI,
-         GPA_SSC = grade_ECTS_SSC / ECTS_SSC,
-         GPA_COR = grade_ECTS_COR / ECTS_COR,
-         GPA_SKI = grade_ECTS_SKI / ECTS_SKI,
-         GPA_PRO = grade_ECTS_PRO / ECTS_PRO) %>%
-
-  mutate_at(vars(matches("GPA")), lag) %>%
-
-  mutate_at(vars(matches("GPA")), ~ if_else(is.na(.), mean(d_transcript_augmented$Grade), .)) %>% # substitute missing GPA with the mean GPA across all courses (GPA_HUM is missing if student has no taken any HUM course yet)
-
-  arrange(`Student ID`) 
-```
-
-# Join student TP and GPA
-```{r student_profile, cache = TRUE} 
-student_profile <- d_transcript_augmented %>%
-
-  left_join(student_GPA, by = c("Student ID", "time")) %>%
-
-  left_join(student_TP , by = c("Student ID", "time"))
-```
-
-Remove course enrolments from 2007 from the model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.
 ```{r}
-student_profile <- student_profile %>% filter(Year_numerical != 2007)
-```
-
-## Save
-```{r save student_TP} 
-save(student_profile, file = "Output/student_profile.RDATA")
-```
-# Regressing grade on TP and GPA
-
-```{r find_df} 
-find_df <- function(course)  student_profile %>% filter(`Course ID` == course)
+collapse_or       <- function(string) string %>% str_c(collapse = "|")
+collapse_space    <- function(string) string %>% str_c(collapse = " ")
 ```
@@
 
-  y <- df[names(df) == "Grade"] %>% as.matrix
-  x <- df[names(df) != "Grade"] %>% as.matrix
+  y <- df %>% select(Grade             ) %>% as.matrix
+  x <- df %>% select(matches(predictors)) %>% as.matrix
 
-  nfold <- min(10, floor(nrow(df) / 3)) # try nfold = 10
+  nfold <- min(10, floor(nrow(df) / 3))
 
@@
 
-## Model fit
-```{r fit_lasso, cache = TRUE} 
-fit_lasso <- tibble(target = course_target) %>%
-
-  mutate(d = target %>% map(find_df),
-         n = d      %>% map_dbl(nrow)) %>%
-
-  filter(n > 20) %>%
-
-  mutate(cv = d %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
-
-  select(-d)
-```
-
-## Extract results
-```{r fit_lasso extract} 
-fit_lasso <- fit_lasso %>%
-
-  # Results from CV
-  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
-         lambda_1se   = cv %>% map_dbl(~ .[["lambda.1se"]]),
-         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
-         cv_error     = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
-         cv_error_sd  = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])
-         ) %>%
-
-  # Best model
-  mutate(
-
-    intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
-    coefi      = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
-    df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
-
-    dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
-    dev_left   = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
-    dev_unexpl = dev_null - dev_left,
-    dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])
-
-  ) %>%
-
-  select(- m_lasso) %>%
-
-  arrange(cv_error)
-```
-
-```{r} 
-save(fit_lasso, file = "Output/CV.RDATA")
-```
-
-```{r} 
-hist(fit_lasso$cv_error)
-mean(fit_lasso$cv_error); weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-```
-
-Topic chosen by model are related to the course.
-```{r}
-i <- 1; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
-beta %>% filter(topic == "Topic 27")
-beta %>% filter(topic == "Topic 62")
-
-i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
-beta %>% filter(topic == "Topic 29") 
-beta %>% filter(topic == "Topic 64")
-
-i <- 5; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
-beta %>% filter(topic == "Topic 16")
-beta %>% filter(topic == "Topic 4")
-```
-
-# Preparatory courses
-
-```{r} 
-fit_lasso_topic <- tibble(target = course_target) %>%
-
-  mutate(d = target %>% map(find_df),
-         n = d      %>% map_dbl(nrow)) %>%
-
-  filter(n > 20) %>%
-
-  mutate(cv = d %>% map(my_cv.glmnet, alpha = 0, predictors = "Topic")) %>%
-
-  select(-d)
-```
-
-```{r} 
-fit_lasso_topic <- fit_lasso_topic %>%
-
-  # Results from CV
-  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
-         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]]))
-         ) %>%
-
-  select(- cv) %>%
-
-  # Best model
-  mutate(coefi_v = list(m_lasso, index_best) %>% pmap(~ ..1[["beta"]][,..2]),
-         coefi_v = coefi_v %>% map(~ tibble(topic = names(.), weight = .)),
-         coefi_m = list(m_lasso, lambda_min) %>% pmap(coef)) %>%
-
-  # extract coefficients
-  unnest(coefi_v) %>%
-
-  select(target, topic, weight)
-
-print(fit_lasso_topic)
-```
-
-```{r} 
-d_prep <- fit_lasso_topic %>%
-
-  left_join(gamma, by = "topic") %>%
-  rename(`Preparatory Courses` = document) %>%
-  filter(target != `Preparatory Courses`) %>%
-
-  # exclude 3000 (advanced) courses from preparation courses
-  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%
-
-  # double prep_score of intro courses
-  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
-  mutate(weight = weight * (1 + is_intro)) %>%
-
-  # prep_score
-  mutate(prep_score = weight * gamma) %>%
-
-  # aggregate prep_score
-  group_by(target, `Preparatory Courses`) %>%
-  summarize(prep_score = sum(prep_score)) %>%
-
-  # identify top 15 preparation courses for each course
-  group_by(target) %>%
-  top_n(15, prep_score) %>%
-  arrange(target, desc(prep_score))
-
-print(d_prep)
-```
-
 # Save
@@
 ```{r}
-fit_lasso_app <- fit_lasso %>% select(target, cv)
-
-student_profile_nest_app <- student_profile %>%
-
-  nest(.key = profile, matches("GPA|Topic")) %>%
-
-  mutate(profile = profile %>% map(as.matrix)) %>%
-
-  group_by(`Student ID`) %>% # only keep most recent profile of each student
-  arrange(desc(time)) %>%
-  slice(1) %>%
-
-  select(`Student ID`, profile)
-
-save(fit_lasso_app, student_profile_nest_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
+save(list = ls(), file = "Output/useful functions.RDATA")
 ```
-
-# Predict
-
-```{r my_predict} 
-my_predict <- function(model, profile){
-
-  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")
-
-}
-```
-
-```{r} 
-course_ID  <- c("COR1005", "HUM2005") # input$course
-student_ID <- "6087587" # input$student
-
-student_prof <- student_profile_nest_app %>%
-
-  filter(`Student ID` == student_ID) %>%
-
-  pull(profile) %>% .[[1]]
-
-fit_lasso_app %>%
-
-  filter(target %in% course_ID) %>%
-
-  mutate(prediction = cv %>% map_dbl(my_predict, student_prof)) %>%
-
-  mutate(flag_red    = prediction < 5.5,
-         flag_orange = prediction %>% between(5.5, 7),
-         flag_green  = prediction > 7)
-```
-
-# Extra: find best alpha
-
-Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
-
-```{r, cache = T} 
-n_alpha <- 101
-mae     <- numeric(n_alpha)
-alphas  <- seq(0, 1, length.out = n_alpha)
-
-for(i in 1 : n_alpha){
-
-  fit_lasso <- tibble(target = course_target) %>%
-
-    mutate(d = target %>% map(find_df),
-           n = d      %>% map_dbl(nrow)) %>%
-
-    filter(n > 20) %>%
-
-    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
-
-    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
-           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
-
-  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-
-}
-
-# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
-m <- lm(mae ~ alphas)
-plot(alphas, mae)
-abline(m, col = "red")
-m %>% summary
-```

### 2019-06-05 Warning Issuance - Conformal Prediction.Rmd
create a series of scripts for warning issuance

--- 2019-05-22 Pillar 1 - Conformal Prediction.Rmd
@@
 set.seed(1)
+
+knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
 
@@
 
-  df <- df %>% filter(significance <= significance_given)
+  df <- df %>% filter(significance >= significance_given)
 
-  min(df$alpha)
+  max(df$alpha) + 0.00001
 
@@
 
-significance <- c(0.05, seq(0.1, 0.9, 0.1))
+significance <- c(0.01, 0.05, seq(0.1, 0.9, 0.1))
 results <- list()
 n_list <- 1
+
+# course <- "SSC3044"; iteration <- 1; signi <- 0.1
 
@@
 Illustration of the effect of error_hat on interval's width (for significance of 99%):
-```{r, fig.height=4}
-Z_test %>% select(Y, Y_hat, error, error_hat, width, border_low, border_high, hit)
-plot(Z_test$error, Z_test$error_hat)
+```{r, fig.height=4, eval = F}
+Z_test %>% select(Y, Y_hat, mu_hat, width, border_low, border_high, hit)
+plot(Z_test$error, Z_test$mu_hat)
 ```
@@
 Correlation between the actual errors and the predicted errors (error_hat):
-```{r}
+```{r, eval = F}
 cor(Z_test$error, Z_test$error_hat)

### 2019-06-05 Warning Issuance - Grade Prediction with Lasso.Rmd
create a series of scripts for warning issuance

---
title: "Pillar 1 - Student Topic Profile"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

__Considerations__:

* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.

* give more weight to 3000-level courses

* restrict prep courses to UCM courses

# Set up

```{r setup, include = FALSE}

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(fig.path = "Cache/Figures/")

library(glmnet)
library(tidyverse)

load("Output/useful functions.RDATA")

load("Output/student_model.RDATA")
load("Output/course_current.RDATA")
load("Output/app_model.RDATA")
```

# Data

Remove course enrollments from 2007 from the student model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.

```{r}
d_student_model <- d_student_model %>% filter(Year_numerical != 2007)
```

```{r find_df} 
find_df <- function(course)  d_student_model %>% filter(`Course ID` == course)
```

Consider courses currently on offer and with at least 20 enrollments since 2008 
```{r}
d_lasso_course <- tibble(target = course_current) %>%

  mutate(student_model = target        %>% map(find_df),
         n             = student_model %>% map_dbl(nrow)) %>%

  filter(n > 20)
```

Beta of topic model to inspect results
```{r}
beta  <- app_model$Beta[[1]] %>% group_by(topic) %>% top_n(10, beta)
gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
remove(app_model)
```

# Lasso

## Learn lambda with cross-validation

```{r fit_lasso, cache = TRUE} 
d_lasso <- d_lasso_course %>%
  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
  select(-student_model)
```

## Extract results
```{r fit_lasso extract} 
d_lasso <- d_lasso %>%

  # Results from CV
  mutate(m_lasso     = lasso_cv %>% map    (~ .[["glmnet.fit"]]),
         lambda_min  = lasso_cv %>% map_dbl(~ .[["lambda.min"]]),
         lambda_1se  = lasso_cv %>% map_dbl(~ .[["lambda.1se"]]),
         index_best  = lasso_cv %>% map_dbl(~ which.min(.[["cvm"]])),
         cv_error    = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
         cv_error_sd = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])) %>%

  # Best model
  mutate(intercept = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
         coefi     = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
         df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),

         dev_null  = m_lasso %>% map_dbl(~ .[["nulldev"]]),
         dev_left  = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
         dev_expl  = dev_null - dev_left,
         dev_ratio = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])) %>%

  arrange(cv_error)
```

## Save results
```{r} 
save(d_lasso, file = "Output/lasso.RDATA")

d_lasso_app <- d_lasso %>% select(target, lasso_cv)
save(d_lasso_app, file = "APP/Recommender System/d_lasso_app.RDATA")
```

## Explore results

### CV MAE
```{r}
d_lasso %>%
  ggplot() +
  geom_histogram(aes(cv_error), bins = 14) +
  labs(x = "CV mae", caption = "red: mean\ngreen: median") +
  geom_vline(xintercept = c(mean(d_lasso$cv_error)), col = "red", alpha = 0.5) +
  geom_vline(xintercept = c(median(d_lasso$cv_error)), col = "green", alpha = 0.5)
```

meand, median and weighted mean
```{r}
mean(d_lasso$cv_error)
median(d_lasso$cv_error)
weighted.mean(d_lasso$cv_error, d_lasso$n)
```

### Predictors
Topic chosen by model are related to the course.

Show results for good (largest deviance ratio):
SCI2040 Microbiology,
SCI1004 Introduction to Chemistry,
SSC2066 Protection of Civilians in Armed Conflicts

```{r}
show_predictors <- function(course){

  coefi <- d_lasso %>% filter(target == course) %>%
    pull(coefi) %>% .[[1]] %>%
    as.matrix %>% as_tibble(rownames = "id") %>% rename(coefi = `1`)

  coefi %>% filter(id %>% str_detect("GPA")) %>% print # GPA

  coefi_topic <- coefi %>% filter(id %>% str_detect("Topic")) %>%
    filter(coefi != 0) %>%
    filter(coefi > 0 ) %>%
    top_n(3, coefi)
  print(coefi_topic) # Topic

  main_topics <- coefi_topic %>% pull(id) %>% str_replace("_", " ")

  beta %>% filter(topic %in% main_topics) %>% head(30)

}

show_predictors("SCI2040")
show_predictors("SCI1004")
show_predictors("SSC2066")
```

## Prediction

```{r my_predict} 
my_predict <- function(model, profile){

  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")

}
```

```{r} 
course_ID  <- c("COR1005", "HUM2005") # input$course
student_ID <- "6087587" # input$student

load("APP/Recommender System/student_model_nest_app.RDATA")
load("APP/Recommender System/d_lasso_app.RDATA")

student_model <- student_model_nest_app %>%

  filter(`Student ID` == student_ID) %>%

  pull(model) %>% .[[1]]

d_lasso_app %>%

  filter(target %in% course_ID) %>%

  mutate(prediction = lasso_cv %>% map_dbl(my_predict, student_model))
```

## Extra: find best alpha

Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.

```{r, eval = F, cache = T} 
n_alpha <- 101
mae     <- numeric(n_alpha)
alphas  <- seq(0, 1, length.out = n_alpha)

for(i in 1 : n_alpha){

  fit_lasso <- tibble(target = course_target) %>%

    mutate(d = target %>% map(find_df),
           n = d      %>% map_dbl(nrow)) %>%

    filter(n > 20) %>%

    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%

    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))

  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)

}

# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
m <- lm(mae ~ alphas)
plot(alphas, mae)
abline(m, col = "red")
m %>% summary
```

### 2019-06-05 Warning Issuance - Grade Prediction with RF.Rmd
create a series of scripts for warning issuance

--- 2019-06-05 Warning Issuance - Grade Prediction with Lasso.Rmd
@@
 knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
-knitr::opts_chunk$set(fig.path = "Cache/Figures/")
+knitr::opts_chunk$set(cache.fig  = "Cache/Figures/")
+load("Output/useful functions.RDATA")
 
-library(glmnet)
+library(randomForest)
 library(tidyverse)
-
-load("Output/useful functions.RDATA")
 
@@
 
-# Lasso
-
-## Learn lambda with cross-validation
-
-```{r fit_lasso, cache = TRUE} 
-d_lasso <- d_lasso_course %>%
-  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
-  select(-student_model)
-```
-
-## Extract results
-```{r fit_lasso extract} 
-d_lasso <- d_lasso %>%
-
-  # Results from CV
-  mutate(m_lasso     = lasso_cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min  = lasso_cv %>% map_dbl(~ .[["lambda.min"]]),
-         lambda_1se  = lasso_cv %>% map_dbl(~ .[["lambda.1se"]]),
-         index_best  = lasso_cv %>% map_dbl(~ which.min(.[["cvm"]])),
-         cv_error    = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
-         cv_error_sd = list(lasso_cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])) %>%
-
-  # Best model
-  mutate(intercept = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
-         coefi     = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
-         df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
-
-         dev_null  = m_lasso %>% map_dbl(~ .[["nulldev"]]),
-         dev_left  = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
-         dev_expl  = dev_null - dev_left,
-         dev_ratio = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])) %>%
-
-  arrange(cv_error)
-```
-
-## Save results
-```{r} 
-save(d_lasso, file = "Output/lasso.RDATA")
-
-d_lasso_app <- d_lasso %>% select(target, lasso_cv)
-save(d_lasso_app, file = "APP/Recommender System/d_lasso_app.RDATA")
-```
-
-## Explore results
-
-### CV MAE
-```{r}
-d_lasso %>%
-  ggplot() +
-  geom_histogram(aes(cv_error), bins = 14) +
-  labs(x = "CV mae", caption = "red: mean\ngreen: median") +
-  geom_vline(xintercept = c(mean(d_lasso$cv_error)), col = "red", alpha = 0.5) +
-  geom_vline(xintercept = c(median(d_lasso$cv_error)), col = "green", alpha = 0.5)
-```
-
-meand, median and weighted mean
-```{r}
-mean(d_lasso$cv_error)
-median(d_lasso$cv_error)
-weighted.mean(d_lasso$cv_error, d_lasso$n)
-```
-
-### Predictors
-Topic chosen by model are related to the course.
-
-Show results for good (largest deviance ratio):
-SCI2040 Microbiology,
-SCI1004 Introduction to Chemistry,
-SSC2066 Protection of Civilians in Armed Conflicts
+# Random forest
 
 ```{r}
-show_predictors <- function(course){
+data(iris)
 
-  coefi <- d_lasso %>% filter(target == course) %>%
-    pull(coefi) %>% .[[1]] %>%
-    as.matrix %>% as_tibble(rownames = "id") %>% rename(coefi = `1`)
+iris.rf <- randomForest(iris[,-5], iris[,5], prox=TRUE)
 
-  coefi %>% filter(id %>% str_detect("GPA")) %>% print # GPA
+iris.p <- classCenter(iris[,-5], iris[,5], iris.rf$prox)
 
-  coefi_topic <- coefi %>% filter(id %>% str_detect("Topic")) %>%
-    filter(coefi != 0) %>%
-    filter(coefi > 0 ) %>%
-    top_n(3, coefi)
-  print(coefi_topic) # Topic
+plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
+bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
+main="Iris Data with Prototypes")
 
-  main_topics <- coefi_topic %>% pull(id) %>% str_replace("_", " ")
-
-  beta %>% filter(topic %in% main_topics) %>% head(30)
-
-}
-
-show_predictors("SCI2040")
-show_predictors("SCI1004")
-show_predictors("SSC2066")
-```
-
-## Prediction
-
-```{r my_predict} 
-my_predict <- function(model, profile){
-
-  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")
-
-}
+points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
 ```
@@
 ```{r}
-course_ID  <- c("COR1005", "HUM2005") # input$course
-student_ID <- "6087587" # input$student
+rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
 
-load("APP/Recommender System/student_model_nest_app.RDATA")
-load("APP/Recommender System/d_lasso_app.RDATA")
+rf2 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
 
-student_model <- student_model_nest_app %>%
+rf3 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
 
-  filter(`Student ID` == student_ID) %>%
-
-  pull(model) %>% .[[1]]
-
-d_lasso_app %>%
-
-  filter(target %in% course_ID) %>%
-
-  mutate(prediction = lasso_cv %>% map_dbl(my_predict, student_model))
+rf.all <- combine(rf1, rf2, rf3)
+print(rf.all)
 ```
 
-## Extra: find best alpha
+```{r}
+## Look at the third trees in the forest.
+getTree(randomForest(iris[,-5], iris[,5], ntree=10), 3, labelVar=TRUE)
+```
 
-Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
+```{r}
+iris.rf <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
+iris.rf <- grow(iris.rf, 50)
+print(iris.rf)
+```
 
-```{r, eval = F, cache = T} 
-n_alpha <- 101
-mae     <- numeric(n_alpha)
-alphas  <- seq(0, 1, length.out = n_alpha)
+```{r}
+set.seed(4543)
+data(mtcars)
+mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000,
+keep.forest=FALSE, importance=TRUE)
 
-for(i in 1 : n_alpha){
+importance(mtcars.rf)
+importance(mtcars.rf, type=1)
+```
 
-  fit_lasso <- tibble(target = course_target) %>%
-
-    mutate(d = target %>% map(find_df),
-           n = d      %>% map_dbl(nrow)) %>%
-
-    filter(n > 20) %>%
-
-    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
-
-    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
-           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
-
-  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-
-}
-
-# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
-m <- lm(mae ~ alphas)
-plot(alphas, mae)
-abline(m, col = "red")
-m %>% summary
+```{r}
+data(imports85)
+imp85 <- imports85[,-2] # Too many NAs in normalizedLosses.
+imp85 <- imp85[complete.cases(imp85), ]
+## Drop empty levels for factors.
+imp85[] <- lapply(imp85, function(x) if (is.factor(x)) x[, drop=TRUE] else x)
+stopifnot(require(randomForest))
+price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100)
+print(price.rf)
+numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100)
+print(numDoors.rf)
 ```

### 2019-06-05 Warning Issuance - Preparatory Course - Lasso.Rmd
create a series of scripts for warning issuance

--- 2019-06-05 Warning Issuance - Grade Prediction with Lasso.Rmd
@@
 ```{r setup, include = FALSE} 
-
 knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
@@
 
-# Lasso
+# Lasso for Preparatory courses
 
-## Learn lambda with cross-validation
-
-```{r fit_lasso, cache = TRUE} 
-d_lasso <- d_lasso_course %>%
-  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
+```{r d_lasso prep, cache = TRUE} 
+d_lasso_topic <- d_lasso_course %>%
+  mutate(lasso_cv = student_model %>% map(my_cv.glmnet, predictors = "Topic", alpha = 0)) %>%
   select(-student_model)
@@
 
-## Extract results
-```{r fit_lasso extract} 
-d_lasso <- d_lasso %>%
+```{r d_lasso extract prep} 
+d_lasso_topic <- d_lasso_topic %>%
 
@@
   mutate(intercept   = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
-         coefi     = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
+         coefi       = list(m_lasso, index_best) %>% pmap(~ ..1[["beta"]][,..2]),
+         coefi       = coefi %>% map(~ tibble(topic = names(.), coefi = .)),
+         coefi_clean = list(m_lasso, lambda_min) %>% pmap(coef),
          df        = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
@@
 
-  arrange(cv_error)
+  select(- m_lasso, - lasso_cv) %>%
+
+  arrange(cv_error) %>%
+
+  # extract coefficients
+  unnest(coefi) %>%
+  select(target, topic, coefi)
+```
+
+## Explore results
+```{r}
+d_lasso_prep <- d_lasso_topic %>%
+
+  left_join(gamma, by = "topic") %>%
+  rename(`Preparatory Courses` = document) %>%
+  filter(target != `Preparatory Courses`) %>%
+
+  # exclude 3000 (advanced) courses from preparation courses
+  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%
+
+  # double prep_score of intro courses
+  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
+  mutate(weight = coefi * (1 + is_intro)) %>%
+
+  # prep_score
+  mutate(prep_score = weight * gamma) %>%
+
+  # aggregate prep_score
+  group_by(target, `Preparatory Courses`) %>%
+  summarize(prep_score = sum(prep_score)) %>%
+
+  # identify top 15 preparation courses for each course
+  group_by(target) %>%
+  top_n(10, prep_score) %>%
+  arrange(target, desc(prep_score))
+
+head(d_lasso_prep, 20)
 ```
@@
 ```{r} 
-save(d_lasso, file = "Output/lasso.RDATA")
+save(d_lasso_topic, file = "Output/d_lasso_topic.RDATA")
+save(d_lasso_topic, file = "APP/Recommender System/d_lasso_topic.RDATA")
 
-d_lasso_app <- d_lasso %>% select(target, lasso_cv)
-save(d_lasso_app, file = "APP/Recommender System/d_lasso_app.RDATA")
+save(d_lasso_prep, file = "Output/d_lasso_prep.RDATA")
+save(d_lasso_prep, file = "APP/Recommender System/d_lasso_prep.RDATA")
 ```
-
-## Explore results
-
-### CV MAE
-```{r}
-d_lasso %>%
-  ggplot() +
-  geom_histogram(aes(cv_error), bins = 14) +
-  labs(x = "CV mae", caption = "red: mean\ngreen: median") +
-  geom_vline(xintercept = c(mean(d_lasso$cv_error)), col = "red", alpha = 0.5) +
-  geom_vline(xintercept = c(median(d_lasso$cv_error)), col = "green", alpha = 0.5)
-```
-
-meand, median and weighted mean
-```{r}
-mean(d_lasso$cv_error)
-median(d_lasso$cv_error)
-weighted.mean(d_lasso$cv_error, d_lasso$n)
-```
-
-### Predictors
-Topic chosen by model are related to the course.
-
-Show results for good (largest deviance ratio):
-SCI2040 Microbiology,
-SCI1004 Introduction to Chemistry,
-SSC2066 Protection of Civilians in Armed Conflicts
-
-```{r}
-show_predictors <- function(course){
-
-  coefi <- d_lasso %>% filter(target == course) %>%
-    pull(coefi) %>% .[[1]] %>%
-    as.matrix %>% as_tibble(rownames = "id") %>% rename(coefi = `1`)
-
-  coefi %>% filter(id %>% str_detect("GPA")) %>% print # GPA
-
-  coefi_topic <- coefi %>% filter(id %>% str_detect("Topic")) %>%
-    filter(coefi != 0) %>%
-    filter(coefi > 0 ) %>%
-    top_n(3, coefi)
-  print(coefi_topic) # Topic
-
-  main_topics <- coefi_topic %>% pull(id) %>% str_replace("_", " ")
-
-  beta %>% filter(topic %in% main_topics) %>% head(30)
-
-}
-
-show_predictors("SCI2040")
-show_predictors("SCI1004")
-show_predictors("SSC2066")
-```
-
-## Prediction
-
-```{r my_predict} 
-my_predict <- function(model, profile){
-
-  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")
-
-}
-```
-
-```{r} 
-course_ID  <- c("COR1005", "HUM2005") # input$course
-student_ID <- "6087587" # input$student
-
-load("APP/Recommender System/student_model_nest_app.RDATA")
-load("APP/Recommender System/d_lasso_app.RDATA")
-
-student_model <- student_model_nest_app %>%
-
-  filter(`Student ID` == student_ID) %>%
-
-  pull(model) %>% .[[1]]
-
-d_lasso_app %>%
-
-  filter(target %in% course_ID) %>%
-
-  mutate(prediction = lasso_cv %>% map_dbl(my_predict, student_model))
-```
-
-## Extra: find best alpha
-
-Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
-
-```{r, eval = F, cache = T} 
-n_alpha <- 101
-mae     <- numeric(n_alpha)
-alphas  <- seq(0, 1, length.out = n_alpha)
-
-for(i in 1 : n_alpha){
-
-  fit_lasso <- tibble(target = course_target) %>%
-
-    mutate(d = target %>% map(find_df),
-           n = d      %>% map_dbl(nrow)) %>%
-
-    filter(n > 20) %>%
-
-    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
-
-    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
-           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
-
-  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-
-}
-
-# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
-m <- lm(mae ~ alphas)
-plot(alphas, mae)
-abline(m, col = "red")
-m %>% summary
-```

### 2019-06-05 Warning Issuance - Student Model.Rmd
create a series of scripts for warning issuance

---
title: "Pillar 1 - Student Topic Profile"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

__Considerations__:

* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.

* give more weight to 3000-level courses

* consider following predictors:
     * GPA (per concentration)

# Set up

```{r setup, include = FALSE}

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(fig.path = "Cache/Figures/")

library(leaps)
library(tidyverse)

load("Output/app_model.RDATA")
load("Output/data_student.RDATA")
```

# Topic Model
```{r gamma_spread}
gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
gamma_spread <- gamma %>% spread(topic, gamma)
remove(app_model)
```

# Students' Topic Expertise
```{r student_TP} 
student_TP <- d_transcript_augmented %>%
  left_join(gamma_spread, by = c("Course ID" = "document")) %>%

  # Knowledge acquired in each course
  mutate_at(vars(matches("Topic")), funs(if_else(is.na(.), 0, .))) %>% # give a value of 0 to the topics of the courses missing from the topic model.
  mutate_at(vars(matches("Topic")), funs(Grade/10 * .)) %>% # weigh by grade

  # Knowledge acquired in each period
  group_by(`Student ID`, time) %>%
  summarize_at(vars(matches("Topic")), sum) %>%

  # Cumulative knowledge acquired over time
  group_by(`Student ID`) %>%
  arrange(time) %>%
  mutate_at(vars(matches("Topic")), lag, default = 0) %>% # knowledge only acquired at the END of the course
  mutate_at(vars(matches("Topic")), cumsum) %>%
  ungroup %>%

  arrange(`Student ID`, time)
```

Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).

# Students' Academic Performance

```{r grade_ECTS} 
d_transcript_augmented <- d_transcript_augmented %>%

  mutate(is_HUM = `Course ID` %>% str_detect("HUM|SAH"),
         is_SCI = `Course ID` %>% str_detect("SCI|SAS"),
         is_SSC = `Course ID` %>% str_detect("SSC|SAC"),
         is_COR = `Course ID` %>% str_detect("COR"),
         is_SKI = `Course ID` %>% str_detect("SKI|LAN"),
         is_PRO = `Course ID` %>% str_detect("PRO|UGR|CAP")) %>%

  mutate(grade_HUM = if_else(is_HUM, Grade, NA_real_),
         grade_SCI = if_else(is_SCI, Grade, NA_real_),
         grade_SSC = if_else(is_SSC, Grade, NA_real_),
         grade_COR = if_else(is_COR, Grade, NA_real_),
         grade_SKI = if_else(is_SKI, Grade, NA_real_),
         grade_PRO = if_else(is_PRO, Grade, NA_real_)) %>%

  mutate(ECTS = case_when(`Course ID` %>% str_detect("HUM|SCI|SSC|COR|PRO|SA|EXT") ~ 5  ,
                          `Course ID` %>% str_detect("SKI|LAN"                   ) ~ 2.5,
                          `Course ID` %>% str_detect("CAP|UGR"                   ) ~ 10 ,
                          TRUE                                                     ~ 5  )) %>%

  mutate(ECTS_HUM = if_else(is_HUM, ECTS, NA_real_),
         ECTS_SCI = if_else(is_SCI, ECTS, NA_real_),
         ECTS_SSC = if_else(is_SSC, ECTS, NA_real_),
         ECTS_COR = if_else(is_COR, ECTS, NA_real_),
         ECTS_SKI = if_else(is_SKI, ECTS, NA_real_),
         ECTS_PRO = if_else(is_PRO, ECTS, NA_real_)) %>%

  mutate(grade_ECTS     = Grade     * ECTS,
         grade_ECTS_HUM = grade_HUM * ECTS_HUM,
         grade_ECTS_SCI = grade_SCI * ECTS_SCI,
         grade_ECTS_SSC = grade_SSC * ECTS_SSC,
         grade_ECTS_COR = grade_COR * ECTS_COR,
         grade_ECTS_SKI = grade_SKI * ECTS_SKI,
         grade_ECTS_PRO = grade_PRO * ECTS_PRO)
```

```{r student_GPA, cache = TRUE} 
student_GPA <- d_transcript_augmented %>%

  # Courses taken in each period
  group_by(`Student ID`, time) %>%
  summarize_at(vars(matches("ECTS")), list) %>%

  # Cumulative GPAs
  group_by(`Student ID`) %>%
  arrange(time) %>%
  mutate_at(vars(matches("ECTS")), purrr::accumulate, c) %>%
  mutate_at(vars(matches("ECTS")), map_dbl, sum, na.rm = TRUE) %>%
  mutate(GPA     = grade_ECTS     / ECTS,
         GPA_HUM = grade_ECTS_HUM / ECTS_HUM,
         GPA_SCI = grade_ECTS_SCI / ECTS_SCI,
         GPA_SSC = grade_ECTS_SSC / ECTS_SSC,
         GPA_COR = grade_ECTS_COR / ECTS_COR,
         GPA_SKI = grade_ECTS_SKI / ECTS_SKI,
         GPA_PRO = grade_ECTS_PRO / ECTS_PRO) %>%
  mutate_at(vars(matches("GPA")), lag) %>%
  mutate_at(vars(matches("GPA")), ~ if_else(is.na(.), mean(d_transcript_augmented$Grade), .)) %>% # substitute missing GPA with the mean GPA across all courses (GPA_HUM is missing if student has no taken any HUM course yet)

  arrange(`Student ID`, time) 
```

# Join student TP and GPA
```{r student_profile, cache = TRUE} 
d_student_model <- d_transcript_augmented %>%

  left_join(student_GPA, by = c("Student ID", "time")) %>%

  left_join(student_TP , by = c("Student ID", "time")) %>%

  select(`Student ID`, `Course ID`, Year_numerical, Period, Grade, time, matches("GPA"), matches("Topic")) %>%
  arrange(`Student ID`, time)
```

# Save

```{r, cache = TRUE}
student_model_nest_app <- d_student_model %>%

  nest(.key = model, matches("GPA|Topic")) %>%
  mutate(model = model %>% map(as.matrix)) %>%

  group_by(`Student ID`) %>% # only keep most recent profile of each student
  top_n(1, time) %>%

  select(`Student ID`, model)
```

```{r save student_TP} 
save(d_student_model, file = "Output/student_model.RDATA")

save(student_model_nest_app, file = "APP/Recommender System/student_model_nest_app.RDATA")
```

### 2019-06-05 Conference/COPA2019/paper/conference figures COPA2019.Rmd
relocate scripts for conference configures in conference folder

--- 2019-05-22 conference figures COPA2019.Rmd
@@
 
+# TODO: set working directory to project directory
+setwd("C:/Users/JeanLuc/Desktop/Job/DARS/DARS")
+
 knitr::opts_chunk$set(echo = FALSE)
 theme_set(theme_light())
+knitr::opts_chunk$set(fig.path = "figures/")
 
@@
 
-output_folder <- "Conference/COPA2019/paper/figures"
-plot_width <- 6
+output_folder <- "figures"
+plot_width <- 4
 plot_height <- plot_width / 1.6 
@@
 conformal_results %>%
-  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
+  filter(significance < 0.2) %>%
   group_by(course, significance) %>%

### 2019-06-05 Conference/EDM2019/conference figures EDM2019.Rmd
relocate script for conference figures into folder of conference

--- 2019-04-30 conference figures.Rmd
@@
 
+# TODO: set working directory to project directory
+setwd("C:/Users/JeanLuc/Desktop/Job/DARS/DARS")
+
 knitr::opts_chunk$set(echo = FALSE)
 theme_set(theme_light())
+knitr::opts_chunk$set(fig.path = "Figures/")
 
@@
 
-output_folder <- "Conference/Figures"
+output_folder <- "Figures"
 plot_width <- 6
@@
       WAR [label = 'Warnings']
-      PRE [label = 'Preparatory Coursework']
+      PRE [label = 'Preparatory Courses']
       }
@@
 # Save by hand
-# image format: JPEG
-# Width: 626
-# Check Maintain aspect ratio
 # File name: Conference/Figures/Flowchart

### 2019-06-07 Warning Issuance - Grade Prediction with RF.Rmd
explore randomForest package

@@
 
-```{r find_df} 
-find_df <- function(course)  d_student_model %>% filter(`Course ID` == course)
-```
-
 Consider courses currently on offer and with at least 20 enrollments since 2008 
 ```{r}
-d_lasso_course <- tibble(target = course_current) %>%
+d_course <- tibble(target = course_current) %>%
 
@@
 
-# Random forest
+# Random Forest
 
 ```{r}
+## Regression:
+data(airquality)
+ozone.rf <- randomForest(Ozone ~ ., data=airquality, mtry=3, ntree = 1e3,
+                         importance=TRUE, na.action=na.omit)
+print(ozone.rf)
+## Show "importance" of variables: higher value mean more important:
+round(importance(ozone.rf), 2)
+varImpPlot(ozone.rf)
+
+# margin
+plot(randomForest::margin(iris.rf), F)
+plot(randomForest::margin(iris.rf), T)
+
+# MDSplot
+MDSplot(iris.rf, iris$Species)
+
+# Looping over variables ranked by importance:
+airquality <- na.omit(airquality)
+ozone.rf <- randomForest(Ozone ~ ., airquality, importance=TRUE)
+imp <- importance(ozone.rf)
+impvar <- rownames(imp)[order(imp[, 1], decreasing=TRUE)]
+op <- par(mfrow=c(2, 3))
+
+for (i in seq_along(impvar))
+  partialPlot(ozone.rf, 
+              airquality,
+              impvar[i], 
+              xlab=impvar[i], main=paste("Partial Dependence on", impvar[i]), ylim=c(30, 70))
+par(op)
+
+# predict
+
+ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
+iris.rf <- randomForest(Species ~ ., data=iris[ind == 1,])
+
+iris.pred <- predict(iris.rf, iris[ind == 2,])
+table(observed = iris[ind==2, "Species"], predicted = iris.pred)
+
+## Get prediction for all trees.
+predict(iris.rf, iris[ind == 2,], predict.all=TRUE)
+
+# Tune randomForest for the optimal mtry parameter
+data(fgl, package="MASS")
+fgl.res <- tuneRF(fgl[,-10], fgl[,10], ntreeTry = 1000, stepFactor=1.5)
+
+# CV for for feature selection
+myiris <- cbind(iris[1:4], matrix(runif(96 * nrow(iris)), nrow(iris), 96))
+result <- rfcv(myiris, iris$Species, cv.fold=3)
+with(result, plot(n.var, error.cv, log="x", type="o", lwd=2))
+
+## The following can take a while to run, so if you really want to try
+## it, copy and paste the code into R.
+
+## Not run: 
+result <- replicate(5, rfcv(myiris, iris$Species), simplify=FALSE)
+error.cv <- sapply(result, "[[", "error.cv")
+matplot(result[[1]]$n.var, cbind(rowMeans(error.cv), error.cv), type="l",
+        lwd=c(2, rep(1, ncol(error.cv))), col=1, lty=1, log="x",
+        xlab="Number of variables", ylab="CV Error")
+
+## End(Not run)
+
+# tree size
+hist(treesize(iris.rf))
+```
+
+TODO: combine RF of all courses to evaluate feature importance
+
+# Random forest trial
+```{r randomForest}
+## Classification:
+data(iris)
+iris.rf <- randomForest(Species ~ ., data=iris, importance=TRUE,
+                        proximity=TRUE)
+print(iris.rf)
+## Look at variable importance:
+round(importance(iris.rf), 2)
+## Do MDS on 1 - proximity:
+iris.mds <- cmdscale(1 - iris.rf$proximity, eig=TRUE)
+op <- par(pty="s")
+pairs(cbind(iris[,1:4], iris.mds$points), cex=0.6, gap=0,
+      col=c("red", "green", "blue")[as.numeric(iris$Species)],
+      main="Iris Data: Predictors and MDS of Proximity Based on RandomForest")
+par(op)
+print(iris.mds$GOF)
+
+## The `unsupervised' case:
+set.seed(17)
+iris.urf <- randomForest(iris[, -5])
+MDSplot(iris.urf, iris$Species)
+
+## stratified sampling: draw 20, 30, and 20 of the species to grow each tree.
+(iris.rf2 <- randomForest(iris[1:4], iris$Species, 
+                          sampsize=c(20, 30, 20)))
+
+## Regression:
+data(airquality)
+ozone.rf <- randomForest(Ozone ~ ., data=airquality, mtry=3,
+                         importance=TRUE, na.action=na.omit)
+print(ozone.rf)
+## Show "importance" of variables: higher value mean more important:
+round(importance(ozone.rf), 2)
+
+## "x" can be a matrix instead of a data frame:
+set.seed(17)
+x <- matrix(runif(5e2), 100)
+y <- gl(2, 50)
+(myrf <- randomForest(x, y))
+(predict(myrf, x))
+
+## "complicated" formula:
+(swiss.rf <- randomForest(sqrt(Fertility) ~ . - Catholic + I(Catholic < 50),
+                          data=swiss))
+(predict(swiss.rf, swiss))
+## Test use of 32-level factor as a predictor:
+set.seed(1)
+x <- data.frame(x1=gl(53, 10), x2=runif(530), y=rnorm(530))
+(rf1 <- randomForest(x[-3], x[[3]], ntree=10))
+
+## Grow no more than 4 nodes per tree:
+(treesize(randomForest(Species ~ ., data=iris, maxnodes=4, ntree=30)))
+
+## test proximity in regression
+iris.rrf <- randomForest(iris[-1], iris[[1]], ntree=101, proximity=TRUE, oob.prox=FALSE)
+str(iris.rrf$proximity)
+```
+
+```{r classCenter}
 data(iris)
@@
 
-```{r}
+```{r randomForest::combine}
 rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
@@
 
-rf.all <- combine(rf1, rf2, rf3)
+rf.all <- randomForest::combine(rf1, rf2, rf3)
 print(rf.all)
@@
 
-```{r}
+```{r getTree}
 ## Look at the third trees in the forest.
-getTree(randomForest(iris[,-5], iris[,5], ntree=10), 3, labelVar=TRUE)
+getTree(randomForest(iris[,-5], iris[,5], ntree=10), k = 3, labelVar=TRUE)
 ```
 
-```{r}
+```{r grow}
 iris.rf <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
@@
 
-```{r}
+```{r importance}
 set.seed(4543)
@@
 
-```{r}
+```{r imports85}
 data(imports85)
@@
 stopifnot(require(randomForest))
-price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100)
+
+price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100) # regression
 print(price.rf)
-numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100)
+
+numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100) # classification
 print(numDoors.rf)
 ```
+
+```{r margin}
+iris.rf <- randomForest(Species ~ ., iris, keep.forest=FALSE)
+plot(randomForest::margin(iris.rf), F)
+plot(randomForest::margin(iris.rf), T)
+```
+
+```{r MDSplot}
+iris.rf <- randomForest(Species ~ ., iris, proximity=TRUE,
+                        keep.forest=FALSE)
+MDSplot(iris.rf, iris$Species)
+## Using different symbols for the classes:
+MDSplot(iris.rf, iris$Species, palette=rep(1, 3), pch=as.numeric(iris$Species))
+```
+
+```{r na.roughfix}
+## artificially drop some data values.
+iris.na <- iris
+for (i in 1:4) iris.na[sample(150, sample(20)), i] <- NA
+
+iris.roughfix <- na.roughfix(iris.na)
+iris.narf <- randomForest(Species ~ ., iris.na, na.action=na.roughfix)
+print(iris.narf)
+```
+
+```{r outlier}
+iris.rf <- randomForest(iris[,-5], iris[,5], proximity=TRUE)
+plot(outlier(iris.rf), type="h",
+     col=c("red", "green", "blue")[as.numeric(iris$Species)])
+```
+
+```{r partialPlot}
+iris.rf <- randomForest(Species~., iris)
+partialPlot(iris.rf, iris, Petal.Width, "versicolor")
+
+## Looping over variables ranked by importance:
+airquality <- na.omit(airquality)
+ozone.rf <- randomForest(Ozone ~ ., airquality, importance=TRUE)
+imp <- importance(ozone.rf)
+impvar <- rownames(imp)[order(imp[, 1], decreasing=TRUE)]
+op <- par(mfrow=c(2, 3))
+
+for (i in seq_along(impvar))
+  partialPlot(ozone.rf, 
+              airquality,
+              impvar[i], 
+              xlab=impvar[i], main=paste("Partial Dependence on", impvar[i]), ylim=c(30, 70))
+par(op)
+```
+
+```{r plot.randomForest}
+data(mtcars)
+plot(randomForest(mpg ~ ., mtcars, keep.forest=FALSE, ntree=100), log="y")
+```
+
+```{r predict.randomForest}
+ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
+iris.rf <- randomForest(Species ~ ., data=iris[ind == 1,])
+
+iris.pred <- predict(iris.rf, iris[ind == 2,])
+table(observed = iris[ind==2, "Species"], predicted = iris.pred)
+
+## Get prediction for all trees.
+predict(iris.rf, iris[ind == 2,], predict.all=TRUE)
+
+## Proximities.
+predict(iris.rf, iris[ind == 2,], proximity=TRUE)
+
+## Nodes matrix.
+str(attr(predict(iris.rf, iris[ind == 2,], nodes=TRUE), "nodes"))
+```
+
+```{r rfcv}
+myiris <- cbind(iris[1:4], matrix(runif(96 * nrow(iris)), nrow(iris), 96))
+result <- rfcv(myiris, iris$Species, cv.fold=3)
+with(result, plot(n.var, error.cv, log="x", type="o", lwd=2))
+
+## The following can take a while to run, so if you really want to try
+## it, copy and paste the code into R.
+
+## Not run: 
+result <- replicate(5, rfcv(myiris, iris$Species), simplify=FALSE)
+error.cv <- sapply(result, "[[", "error.cv")
+matplot(result[[1]]$n.var, cbind(rowMeans(error.cv), error.cv), type="l",
+        lwd=c(2, rep(1, ncol(error.cv))), col=1, lty=1, log="x",
+        xlab="Number of variables", ylab="CV Error")
+
+## End(Not run)
+```
+
+```{r rfImpute}
+iris.na <- iris
+set.seed(111)
+## artificially drop some data values.
+for (i in 1:4) iris.na[sample(150, sample(20)), i] <- NA
+
+set.seed(222)
+iris.imputed <- rfImpute(Species ~ ., iris.na)
+
+set.seed(333)
+iris.rf <- randomForest(Species ~ ., iris.imputed)
+
+print(iris.rf)
+```
+
+```{r treesize}
+iris.rf <- randomForest(Species ~ ., iris)
+hist(treesize(iris.rf))
+```
+
+```{r tuneRF}
+data(fgl, package="MASS")
+fgl.res <- tuneRF(fgl[,-10], fgl[,10], ntreeTry = 1000, stepFactor=1.5)
+```
+
+```{r varImpPlot}
+mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000, keep.forest=FALSE,
+                          importance=TRUE)
+varImpPlot(mtcars.rf)
+```
+
+```{r varUsed}
+varUsed(randomForest(Species~., iris, ntree=100))
+```

### 2019-06-07 Data Preparation.Rmd
passed files to app

--- 2019-03-28 Data Preparation.Rmd
@@
----
-title: "Data Preparation"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
-
-library(tidyverse)
-library(tidytext)
-library(gsheet) # import spreadsheets from google drive
-library(tm)
-library(hunspell) # Stemmer
-library(magrittr)
-```
-
-# Import Data
-The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons).
-We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
-We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
-
-## List of AoD's and Assessments
-First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
-` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
-Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively).
-We also any imported emtpy cells.
-```{r list_AoD_assessment}
-list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
-
-  map(na.omit)
-
-# selection of most important types of assessment an AoD to keep plots clear
-list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %T>% print
-list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %T>% print
-```
-
-## Course Data
-We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
-The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
-The tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment; and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
-
-```{r d_course}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>% print
-```
-
-```{r d_assessment}
-d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key   = Assessment, value = assessment_covered, Paper : Participation) %>%
-
-  filter(assessment_covered) %>%
-
-  select(- c(assessment_covered, `Comment on Assessment`)) %T>%
-
-  print
-```
-
-```{r d_ILO}
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
-```
-
-```{r d_AoD_from_ILO}
-d_AoD_from_ILO <- d_ILO %>%
-
-  rename(ILO = Objectives) %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %T>%
-
-  print
-```
-
-## Student Data
-The tibble `d_transcript` contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it.
-
-```{r read_csv_own_parsing}
-col_parsing <- cols(
-  `Student Number`                      = "c",
-  `Program (Abbreviation)`              = "c",
-  `Appraisal Status`                    = "c",
-  `Module Booking Reason (Description)` = "c",
-  `Object name`                         = "c",
-  `Start date`                          = "c",
-  `End Date`                            = "c"
-  )
-
-read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
-```
-
-```{r d_transcript, cache = TRUE}
-d_transcript <- paste0("Input/Raw Grades/grades", 1:2, ".csv") %>%
-
-  map(read_csv_own_parsing) %>%
-
-  bind_rows
-
-rm(col_parsing, read_csv_own_parsing)
-```
-
-# Variable Engineering
-## Course Data
-The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
-
-### AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it.
-For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
-
-#### AoD from ILOs
-(For this section we use: `d_ILO`-indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD)
-
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r d_AoD_ILO}
-d_AoD_from_ILO
-```
-
-#### AoD from Assessment
-(For this section we use: `d_assessment`-indicates which type(s) of assessment each course contains with one row per course-assessment)
-
-In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
-We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
-`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-Thus, the first step is to import this matrix:
-
-```{r map_assessment_AoD}
-map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- AoD_covered) %>%
-
-  arrange(Assessment) %T>%
-
-  print
-```
-
-Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments.
-To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
-In the loop, we first extract a row of `d_assessment` and save it as `observation`.
-Then, we determine the corresponding assessment which we save as `assessment`.
-Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r d_AoD_assessment}
-d_AoD_from_assessment <- d_assessment %>%
-
-  left_join(map_assessment_AoD, by = "Assessment") %T>%
-
-  print
-
-rm(map_assessment_AoD)
-```
-
-#### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
-```{r rbind d_AoD_ILO and d_AoD_assessment}
-d_AoD <- rbind(
-  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
-  d_AoD_from_assessment %>% select(`Course ID`, AoD)
-  ) %>%
-
-  distinct %>%
-
-  arrange(`Course ID`) %T>%
-
-  print
-
-rm(d_AoD_from_assessment, d_AoD_from_ILO)
-```
-
-### Courses
-(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)
-
-Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-For this we create the following three tibbles:
-1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
-2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
-3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
-Then we use a `full_join` to add these variables to the tibble `d_course`.
-```{r d_course detail}
-count_and_paste <- function(df, var, colnam1, colnam2){
-
-  df %>%
-
-    group_by(`Course ID`) %>%
-
-    summarize(
-      !!ensym(colnam1) := n_distinct(!!enquo(var)),
-      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
-      )
-
-}
-
-join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
-```
-
-```{r join d_course_detail}
-d_course <- d_course %>%
-
-  join_by_course_ID( d_AoD        %>% count_and_paste(AoD       , n_AoD       , `AoD Covered`        ) %T>% print) %>%
-
-  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`)           ) %>%
-
-  join_by_course_ID( d_ILO        %>% count_and_paste(Objectives, n_ILO       , `ILO Covered`        )           ) %>%
-
-  select(
-    `Course ID`, `Course Title`, Cluster,
-    n_ILO,
-    n_assessment, `Assessments Covered`,
-    n_AoD, `AoD Covered`,
-    everything()
-    ) %T>%
-
-  print
-
-rm(count_and_paste, join_by_course_ID)
-```
-
-The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level).
-Yet, these course are also offered at the `2000` level (intermediate level).
-We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r create UGR2000}
-UGR_2000 <- d_course %>%
-
-  filter( `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-
-  mutate(
-    `Course ID` = case_when(
-      `Course ID` == "UGR3001" ~ "UGR2001",
-      `Course ID` == "UGR3002" ~ "UGR2002",
-      `Course ID` == "UGR3003" ~ "UGR2003",
-      `Course ID` == "UGR3005" ~ "UGR2005"
-      )
-    ) %T>%
-
-  print
-
-d_course <- d_course %>% rbind(UGR_2000)
-
-# print UGR course
-print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )
-
-rm(UGR_2000)
-```
-
-Finally, we add a series of informative variable at the course level.
-```{r d_course additional info}
-d_course <- d_course %>%
-
-  separate(
-    col     = `Course ID`,
-    into    = c("Letters", "Number"),
-    sep     = 3,
-    remove  = FALSE,
-    convert = TRUE
-    ) %>%
-
-  mutate(
-    Level   = case_when(
-      between(Number, 1000, 1999) ~ "Introductory",
-      between(Number, 2000, 2999) ~ "Intermediate",
-      between(Number, 3000, 3999) ~ "Advanced"    )
-    ) %>%
-
-  select(`Course ID`, Letters, Number, Level, everything()) %T>%
-
-  print
-```
-
-## Student Data
-
-* Is `Academic Work ID` a unique ID number?
-
-* questions...
-
-(In this section we use: `d_transcript`- contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond roughly to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it).
-
-Our dataframe contains many variables and rows that are either empty or meaningless for our analysis.
-First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor").
-Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
-
-```{r d_transcript helper}
-course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")
-
-is_UCM      <- function(course_code) course_code %>% str_detect(course_letter_UCM)
-is_elective <- function(course_code) course_code %>% str_detect("HUM|SCI|SSC")
-```
-
-```{r d_transcript row selection}
-d_transcript <- d_transcript %>%
-
-  # for simplicity, we only keep 
-  # *UCM courses*  (courses present in the UCM catalogue)
-  # taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
-
-  filter(
-    `Module (Abbrev.)` %>% is_UCM,
-    `Program (Abbreviation)` == "7501"
-    ) %>%
-
-  # The dataset has multiple rows for each student - course.
-  # Following guidelines of Richard Vos, we only consider: 
-  # `Appraisal (Description)` == "Grade supervisor"
-  # and `Appraisal Type` == "7055"
-
-  filter(
-    `Appraisal (Description)` == "Grade supervisor",
-    `Appraisal Type`          == "7055" # removes ~ 15 observations
-    )
-```
-
-```{r d_transcript column selection}
-d_transcript <- d_transcript %>%
-
-  # Remove variables with only one value (~10)
-  discard(function(x) n_distinct(x) == 1) %>%
-
-  # Select: Student ID, course ID, when a course is taken and the grade 
-  select(
-    `Student ID`   = `Student Number`,
-    `Course ID`    = `Module (Abbrev.)`,
-    Year_numerical = `Academic Year`,
-    Period         = `Academic Session`,
-    Grade          = `Grade symbol`
-    )
-```
-
-```{r clean_grade}
-clean_grade <- function(grade){
-
-  if(is.na(grade) | grade == "NG") grade <- "0"
-
-  grade %>% str_replace(",", ".") %>% as.numeric
-
-}
-```
-
-```{r clean_period}
-clean_period <- function(period){
-
-  # Course spanning over multiple period are recorder with a 1, 2 or 3
-  if(period == 1) return("1 to 6")
-  if(period == 2) return("1 to 3")
-  if(period == 3) return("4 to 6")
-
-  # Course spanning over a single period are recorded in the 100's, 200's, etc.
-  # The digit of the hundred indicates the period.
-  period %/% 100 %>% as.character
-
-}
-```
-
-```{r clean_year}
-clean_year <- function(year) str_c(year, year + 1, sep = "-")
-```
-
-```{r clean d_transcript}
-d_transcript <- d_transcript %>%
-
-  mutate(
-
-    # Clean grade, period and year
-    Grade          = Grade  %>% map_dbl(clean_grade ),
-    Period         = Period %>% map_chr(clean_period),
-    `Academic Year`= Year_numerical %>% map_chr(clean_year),
-
-    # extract first period in which course spanning over mutliple periods is given
-    period_numerical = substr(Period, 1, 1),
-
-    # Combine year and period to have be able to order the course in time using a single variable
-    time = str_c(Year_numerical, period_numerical) %>% as.numeric,
-
-    grade_ceil = ceiling(Grade)
-
-    )
-```
-
-```{r}
-d_transcript_augmented <- d_transcript %>% left_join(select(d_course, - Period), by = c("Course ID"))
-```
-
-```{r}
-d_transcript_elective <- d_transcript_augmented %>%
-  filter(`Course ID` %>% is_elective) %>%
-  select(`Student ID`, `Course ID`, time, Grade, grade_ceil)
-```
-
-### Issues
-```{r issue d_transcript}
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination.
-  add_count(
-    `Student ID`, `Course ID`, time,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination - grade.
-  add_count(
-    `Student ID`, `Course ID`, time, Grade,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
-  filter(`Student ID` == "6087587") %>%
-  arrange(`Course ID`) %>%
-  pull(`Course ID`)
-
-#TODO: list issues here
-```
-
-# Save Data
-```{r}
-save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")
-
-save(d_transcript_augmented, d_transcript_elective, file = "Output/data_pillar_1.RDATA")
-
-save(d_course, d_transcript, file = "Output/data_pillar_2.RDATA")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:5a69e7e1bed6b20a0a4d0aa7e51cb1734c29a36407828f1c5510e21e2bfd05f9
+size 16557

### 2019-06-07 Pillar 1 - Topic Profile.Rmd
passed files to app

@@
----
-title: "Pillar 1 - Student Topic Profile"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-__Considerations__:
-
-* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.
-
-* give more weight to 3000-level courses
-
-* consider following predictors:
-     * GPA (per concentration)
-
-# Set up
-
-```{r setup, include = FALSE} 
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
-
-library(magrittr)
-library(glmnet)
-library(leaps)
-library(tidyverse)
-```
-
-```{r load, cache.lazy = TRUE} 
-load("Output/app_model.RDATA")
-load("Output/data_student.RDATA")
-load("Output/course_current.RDATA")
-
-course_target <- course_current[! str_detect(course_current, "...10..")]
-course_target <- union(course_target, str_subset(course_current, "COR"))# include core courses
-```
-
-# Topic Model
-```{r gamma_spread}
-gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
-gamma_spread <- gamma %>% spread(topic, gamma)
-beta  <- app_model$Beta %>% .[[1]] %>% group_by(topic) %>% top_n(15, beta)
-remove(app_model)
-```
-
-# Students' Topic Expertise
-```{r student_TP} 
-student_TP <- d_transcript_augmented %>%
-
-  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
-
-  mutate_at(vars(matches("Topic")), .funs = funs(if_else(is.na(.), 0, .))) %>% # give a value of 0 to the topics of the courses missing from the topic model.
-  mutate_at(vars(matches("Topic")), .funs = funs(Grade/10 * .)) %>% # weigh by grade
-
-  group_by(`Student ID`, time) %>%
-  summarize_at(vars(matches("Topic")), sum) %>%
-
-  group_by(`Student ID`) %>%
-  arrange(time) %>%
-
-  mutate_at(vars(matches("Topic")), lag, default = 0) %>%
-  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile at beginning of period
-
-  ungroup %>%
-
-  arrange(`Student ID`)
-```
-
-Raphael's topic profile is coherent: topics with a high value correspond to my academic focus and topics with a low score to themes I never covered (i.e. law, literature).
-
-# Students' Academic Performance
-
-```{r grade_ECTS} 
-d_transcript_augmented <- d_transcript_augmented %>%
-
-  mutate(is_HUM = `Course ID` %>% str_detect("HUM|SAH"),
-         is_SCI = `Course ID` %>% str_detect("SCI|SAS"),
-         is_SSC = `Course ID` %>% str_detect("SSC|SAC"),
-         is_COR = `Course ID` %>% str_detect("COR"),
-         is_SKI = `Course ID` %>% str_detect("SKI|LAN"),
-         is_PRO = `Course ID` %>% str_detect("PRO|UGR|CAP")) %>%
-
-  mutate(grade_HUM = if_else(is_HUM, Grade, NA_real_),
-         grade_SCI = if_else(is_SCI, Grade, NA_real_),
-         grade_SSC = if_else(is_SSC, Grade, NA_real_),
-         grade_COR = if_else(is_COR, Grade, NA_real_),
-         grade_SKI = if_else(is_SKI, Grade, NA_real_),
-         grade_PRO = if_else(is_PRO, Grade, NA_real_)) %>%
-
-  mutate(ECTS = case_when(
-    `Course ID` %>% str_detect("HUM|SCI|SSC|COR|PRO|SA|EXT") ~ 5  ,
-    `Course ID` %>% str_detect("SKI|LAN"                   ) ~ 2.5,
-    `Course ID` %>% str_detect("CAP|UGR"                   ) ~ 10 ,
-    TRUE                                                     ~ 5  )
-    ) %>%
-
-  mutate(ECTS_HUM = if_else(is_HUM, ECTS, NA_real_),
-         ECTS_SCI = if_else(is_SCI, ECTS, NA_real_),
-         ECTS_SSC = if_else(is_SSC, ECTS, NA_real_),
-         ECTS_COR = if_else(is_COR, ECTS, NA_real_),
-         ECTS_SKI = if_else(is_SKI, ECTS, NA_real_),
-         ECTS_PRO = if_else(is_PRO, ECTS, NA_real_)) %>%
-
-  mutate(grade_ECTS     = Grade     * ECTS,
-         grade_ECTS_HUM = grade_HUM * ECTS_HUM,
-         grade_ECTS_SCI = grade_SCI * ECTS_SCI,
-         grade_ECTS_SSC = grade_SSC * ECTS_SSC,
-         grade_ECTS_COR = grade_COR * ECTS_COR,
-         grade_ECTS_SKI = grade_SKI * ECTS_SKI,
-         grade_ECTS_PRO = grade_PRO * ECTS_PRO)
-```
-
-```{r student_GPA, cache = TRUE} 
-student_GPA <- d_transcript_augmented %>%
-
-  group_by(`Student ID`, time) %>%
-  summarize_at(vars(matches("ECTS")), list) %>%
-
-  group_by(`Student ID`) %>%
-  arrange(time) %>%
-
-  mutate_at(vars(matches("ECTS")), purrr::accumulate, c) %>%
-
-  mutate_at(vars(matches("ECTS")), map_dbl, sum, na.rm = TRUE) %>%
-
-  mutate(GPA     = grade_ECTS     / ECTS,
-         GPA_HUM = grade_ECTS_HUM / ECTS_HUM,
-         GPA_SCI = grade_ECTS_SCI / ECTS_SCI,
-         GPA_SSC = grade_ECTS_SSC / ECTS_SSC,
-         GPA_COR = grade_ECTS_COR / ECTS_COR,
-         GPA_SKI = grade_ECTS_SKI / ECTS_SKI,
-         GPA_PRO = grade_ECTS_PRO / ECTS_PRO) %>%
-
-  mutate_at(vars(matches("GPA")), lag) %>%
-
-  mutate_at(vars(matches("GPA")), ~ if_else(is.na(.), mean(d_transcript_augmented$Grade), .)) %>% # substitute missing GPA with the mean GPA across all courses (GPA_HUM is missing if student has no taken any HUM course yet)
-
-  arrange(`Student ID`) 
-```
-
-# Join student TP and GPA
-```{r student_profile, cache = TRUE} 
-student_profile <- d_transcript_augmented %>%
-
-  left_join(student_GPA, by = c("Student ID", "time")) %>%
-
-  left_join(student_TP , by = c("Student ID", "time"))
-```
-
-Remove course enrolments from 2007 from the model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.
-```{r}
-student_profile <- student_profile %>% filter(Year_numerical != 2007)
-```
-
-## Save
-```{r save student_TP} 
-save(student_profile, file = "Output/student_profile.RDATA")
-```
-# Regressing grade on TP and GPA
-
-```{r find_df} 
-find_df <- function(course)  student_profile %>% filter(`Course ID` == course)
-```
-
-```{r my_cv.glmnet} 
-my_cv.glmnet <- function(df, alpha = 1, predictors){
-
-  df <- df %>% select(Grade, matches(predictors))
-
-  y <- df[names(df) == "Grade"] %>% as.matrix
-  x <- df[names(df) != "Grade"] %>% as.matrix
-
-  nfold <- min(10, floor(nrow(df) / 3)) # try nfold = 10
-
-  cv.glmnet(x, y, nfolds = nfold, type.measure = "mae", alpha = alpha)
-
-}
-```
-
-## Model fit
-```{r fit_lasso, cache = TRUE} 
-fit_lasso <- tibble(target = course_target) %>%
-
-  mutate(d = target %>% map(find_df),
-         n = d      %>% map_dbl(nrow)) %>%
-
-  filter(n > 20) %>%
-
-  mutate(cv = d %>% map(my_cv.glmnet, predictors = "GPA|Topic")) %>%
-
-  select(-d)
-```
-
-## Extract results
-```{r fit_lasso extract} 
-fit_lasso <- fit_lasso %>%
-
-  # Results from CV
-  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
-         lambda_1se   = cv %>% map_dbl(~ .[["lambda.1se"]]),
-         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]])),
-         cv_error     = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]),
-         cv_error_sd  = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvsd"]][..2])
-         ) %>%
-
-  # Best model
-  mutate(
-
-    intercept  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["a0"]][..2]),
-    coefi      = list(m_lasso, lambda_min) %>% pmap(coef), # clearer output than pmap_dbl(~ ..1[["beta"]][,..2])
-    df         = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["df"]][..2]),
-
-    dev_null   = m_lasso %>% map_dbl(~ .[["nulldev"]]),
-    dev_left   = list(m_lasso, index_best) %>% pmap_dbl(~deviance.glmnet(..1)[..2]),
-    dev_unexpl = dev_null - dev_left,
-    dev_ratio  = list(m_lasso, index_best) %>% pmap_dbl(~ ..1[["dev.ratio"]][..2])
-
-  ) %>%
-
-  select(- m_lasso) %>%
-
-  arrange(cv_error)
-```
-
-```{r} 
-save(fit_lasso, file = "Output/CV.RDATA")
-```
-
-```{r} 
-hist(fit_lasso$cv_error)
-mean(fit_lasso$cv_error); weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-```
-
-Topic chosen by model are related to the course.
-```{r}
-i <- 1; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
-beta %>% filter(topic == "Topic 27")
-beta %>% filter(topic == "Topic 62")
-
-i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
-beta %>% filter(topic == "Topic 29") 
-beta %>% filter(topic == "Topic 64")
-
-i <- 5; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
-beta %>% filter(topic == "Topic 16")
-beta %>% filter(topic == "Topic 4")
-```
-
-# Preparatory courses
-
-```{r} 
-fit_lasso_topic <- tibble(target = course_target) %>%
-
-  mutate(d = target %>% map(find_df),
-         n = d      %>% map_dbl(nrow)) %>%
-
-  filter(n > 20) %>%
-
-  mutate(cv = d %>% map(my_cv.glmnet, alpha = 0, predictors = "Topic")) %>%
-
-  select(-d)
-```
-
-```{r} 
-fit_lasso_topic <- fit_lasso_topic %>%
-
-  # Results from CV
-  mutate(m_lasso      = cv %>% map    (~ .[["glmnet.fit"]]),
-         lambda_min   = cv %>% map_dbl(~ .[["lambda.min"]]),
-         index_best   = cv %>% map_dbl(~ which.min(.[["cvm"]]))
-         ) %>%
-
-  select(- cv) %>%
-
-  # Best model
-  mutate(coefi_v = list(m_lasso, index_best) %>% pmap(~ ..1[["beta"]][,..2]),
-         coefi_v = coefi_v %>% map(~ tibble(topic = names(.), weight = .)),
-         coefi_m = list(m_lasso, lambda_min) %>% pmap(coef)) %>%
-
-  # extract coefficients
-  unnest(coefi_v) %>%
-
-  select(target, topic, weight)
-
-print(fit_lasso_topic)
-```
-
-```{r} 
-d_prep <- fit_lasso_topic %>%
-
-  left_join(gamma, by = "topic") %>%
-  rename(`Preparatory Courses` = document) %>%
-  filter(target != `Preparatory Courses`) %>%
-
-  # exclude 3000 (advanced) courses from preparation courses
-  filter(! `Preparatory Courses` %>% str_detect("^...30")) %>%
-
-  # double prep_score of intro courses
-  mutate(is_intro = `Preparatory Courses` %>% str_detect("^...10")) %>%
-  mutate(weight = weight * (1 + is_intro)) %>%
-
-  # prep_score
-  mutate(prep_score = weight * gamma) %>%
-
-  # aggregate prep_score
-  group_by(target, `Preparatory Courses`) %>%
-  summarize(prep_score = sum(prep_score)) %>%
-
-  # identify top 15 preparation courses for each course
-  group_by(target) %>%
-  top_n(15, prep_score) %>%
-  arrange(target, desc(prep_score))
-
-print(d_prep)
-```
-
-# Save
-
-```{r} 
-fit_lasso_app <- fit_lasso %>% select(target, cv)
-
-student_profile_nest_app <- student_profile %>%
-
-  nest(.key = profile, matches("GPA|Topic")) %>%
-
-  mutate(profile = profile %>% map(as.matrix)) %>%
-
-  group_by(`Student ID`) %>% # only keep most recent profile of each student
-  arrange(desc(time)) %>%
-  slice(1) %>%
-
-  select(`Student ID`, profile)
-
-save(fit_lasso_app, student_profile_nest_app, d_prep, file = "APP/Recommender System/grade_prediction.RDATA")
-```
-
-# Predict
-
-```{r my_predict} 
-my_predict <- function(model, profile){
-
-  predict.cv.glmnet(object = model, newx = profile, s = "lambda.min")
-
-}
-```
-
-```{r} 
-course_ID  <- c("COR1005", "HUM2005") # input$course
-student_ID <- "6087587" # input$student
-
-student_prof <- student_profile_nest_app %>%
-
-  filter(`Student ID` == student_ID) %>%
-
-  pull(profile) %>% .[[1]]
-
-fit_lasso_app %>%
-
-  filter(target %in% course_ID) %>%
-
-  mutate(prediction = cv %>% map_dbl(my_predict, student_prof)) %>%
-
-  mutate(flag_red    = prediction < 5.5,
-         flag_orange = prediction %>% between(5.5, 7),
-         flag_green  = prediction > 7)
-```
-
-# Extra: find best alpha
-
-Best alpha turns out to be 1 (lasso). Good, because predictor regularization also serves as predictor selection.
-
-```{r, cache = T} 
-n_alpha <- 101
-mae     <- numeric(n_alpha)
-alphas  <- seq(0, 1, length.out = n_alpha)
-
-for(i in 1 : n_alpha){
-
-  fit_lasso <- tibble(target = course_target) %>%
-
-    mutate(d = target %>% map(find_df),
-           n = d      %>% map_dbl(nrow)) %>%
-
-    filter(n > 20) %>%
-
-    mutate(cv = d %>% map(my_cv.glmnet, alpha = alphas[i], predictors = "GPA|Topic")) %>%
-
-    mutate(index_best = cv                   %>% map_dbl (~ which.min(.[["cvm"]])),
-           cv_error   = list(cv, index_best) %>% pmap_dbl(~ ..1[["cvm"]][..2]    ))
-
-  mae[i] <- weighted.mean(fit_lasso$cv_error, fit_lasso$n)
-
-}
-
-# slight decrease in mae as alpha increase. Set alpha = 1 in my_cv.glmnet().
-m <- lm(mae ~ alphas)
-plot(alphas, mae)
-abline(m, col = "red")
-m %>% summary
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:2c6d2fbf2745be1d0c00e5f68a8856e04eb293742fe9eeae9d8384a6cdfdf6d1
+size 12156

### 2019-06-07 Pillar 1 - t-test.Rmd
passed files to app

@@
----
-title: "Pillar 1 - t-test"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
-
-library(tidyverse)
-library(arulesSequences)
-library(magrittr)
-
-load("Output/data_pillar_1.RDATA")
-load("output/d_transcript_cum.RDATA")
-```
-
-# Conduct t-test
-```{r my_t_test}
-d_transcript_cum_informative <- left_join(d_transcript_cum, d_transcript_informative, by = c("sequenceID" = "Student ID", "eventID" = "time"))
-
-my_t_test <- function(predictor, response){
-
-  d_transcript_cum_informative %>%
-
-    filter(`Course ID` == response) %>%
-
-    mutate(has_taken_pred = course_past %>% map_lgl(~ predictor %in% .)) %>% # create two groups: (i) have taken the predictor (ii) have not takne predictor
-
-    t.test(Grade ~ has_taken_pred, data = .)
-
-}
-```
-
-```{r d_test}
-all_courses <- unique(d_transcript_informative$`Course ID`)
-
-d_test <- crossing(predictor = all_courses, response = all_courses) %>%
-
-  filter(predictor != response) %>%
-
-  mutate(t_test = list(predictor, response) %>% pmap(possibly(my_t_test, otherwise = "only one sample for t test")))
-```
-
-# Exploring t-test results
-
-20,000 combinations courses
-
-## Combinations of course for which no t-test was possible ()
-
-8,000 combinations for which one of the sample sizes <= 1.
-
-```{r}
-samples <- function(predictor, response){
-
-  d_transcript_cum_informative %>%
-
-    filter(`Course ID` == response) %>%
-
-    summarize(
-      n_total   = n(),
-      n_taken     = course_past %>% map_lgl(~   predictor %in% .) %>% sum,
-      n_not_taken = course_past %>% map_lgl(~ ! predictor %in% .) %>% sum
-      )
-
-}
-
-test_impossible <- d_test %>%
-
-  filter(t_test %>% map_lgl(~typeof(.) != "list")) %>%
-
-  mutate(samples = list(predictor, response) %>% pmap(samples)) %>%
-
-  unnest(samples, .drop = TRUE) %>%
-
-  select(response, predictor, everything())
-```
-
-## Results of t-test
-
-After filtering, 154 combinations left.
-
-```{r}
-test_tidy <- d_test %>%
-
-  filter(t_test %>% map_lgl(~ typeof(.) != "character")) %>%
-
-  mutate(tidied = t_test %>% map(broom::tidy)) %>% # in this case, broom::tidy and broom::glance yield the same results. broom::augment does not work.
-
-  unnest(tidied, .drop = TRUE) %>%
-
-  # disregard advanced-level predictor & introductory-level response
-  filter(! str_detect(predictor, "30")) %>% filter(! str_detect(response, "10")) %>%
-
-  # disregard negative estimates & non-significant tests
-  filter(estimate > 0) %>% filter(p.value < 0.05) %>%
-
-  group_by(response) %>% arrange(response, desc(estimate)) %>% select(response, predictor, everything())
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:6bdfa24f9d325f520ce052e86c90fe13cf40f7eb2b6af756e322e45b35eb78ef
+size 2728

### 2019-06-07 Pillar_2_-_Topic_Modeling.Rmd
passed files to app

--- 2019-04-02 Pillar_2_-_Topic_Modeling.Rmd
@@
----
-title: "Pillar 2 - Topic Modeling"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
-                      eval = FALSE)
-```
-
-```{r library, message = FALSE, eval = TRUE}
-library(tidyverse)
-library(tidytext)
-
-library(ggwordcloud) # Word Clouds
-library(topicmodels)
-library(lemon)
-library(ggthemes)
-library(rlang)
-library(ldatuning) # ideal number of topics in LDA
-
-library(modelr) #cross_validation
-```
-
-```{r function reorder_within & co., echo = FALSE}
-
-# Function for ordering within facet:
-# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
-
-reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
-  new_x <- paste(x, within, sep = sep)
-  stats::reorder(new_x, by, FUN = fun)
-}
-
-scale_x_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-
-scale_y_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-```
-
-# Setup
-We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
-`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
-For `d_description` and `d_overview`, we keep only the most recent year.
-```{r import data, eval = TRUE}
-load("output/data_pillar_2.RDATA")
-
-# Only keep course descriptions and overviews from most recent year
-d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
-```
-
-# TF-IDF
-## Functions for Generating Barplots and Word Clouds
-The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
-```{r compute_tf_idf, cache = TRUE}
-compute_tf_idf <- function(data){
-
-  data %>%
-    count(
-      `Course ID`,
-      word
-      ) %>%
-    bind_tf_idf(
-      term = word, 
-      document = `Course ID`,
-      n = n
-      )
-
-}
-
-tf_idf_description <- compute_tf_idf(d_description)
-tf_idf_overview    <- compute_tf_idf(d_overview)
-tf_idf_manual      <- compute_tf_idf(d_manual)
-
-rm(compute_tf_idf)
-```
-
-The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
-```{r plot_tf_idf}
-plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){
-
-  #
-  # Barplot
-  g <- data %>%
-    ggplot(
-      aes(
-        x = reorder_within(word, tf_idf, facet), 
-        y = tf_idf
-        )
-      ) +
-    geom_col(
-      show.legend = FALSE
-      ) +
-    labs(
-      x = NULL,
-      y = "tf-idf"
-      ) +
-    scale_x_reordered() +
-    facet_wrap(
-      facets = ~ facet, 
-      scales = "free",
-      ncol = n_col
-      ) +
-    coord_flip()
-
-  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-  #
-  # Word Cloud
-  g <- data %>%
-    group_by(
-      facet
-      ) %>%
-    mutate(
-      freq = tf_idf / sum(tf_idf)
-      ) %>% # normalization within facet
-    ggplot(
-      aes(
-        size = freq ^ 0.7, 
-        label = word, 
-        color = freq ^ 0.7
-        )
-      ) +
-    geom_text_wordcloud_area(
-      area_corr_power = 1,
-      eccentricity    = 1,
-      rm_outside      = T
-      ) +
-    scale_radius(
-      range = c(2, 10),
-      limits = c(0, NA)
-      ) +
-    scale_color_gradient(
-      low = "red", 
-      high = "blue"
-      ) +
-    facet_wrap(
-      facet = ~ facet,
-      ncol = n_col
-      ) + 
-    theme(
-      strip.text.x     = element_text(),
-      panel.background = element_rect(fill = "white"),
-      plot.title       = element_text(hjust = 0.5)
-    )
-
-  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-}
-```
-
-## Course Level
-The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
-We apply the function to `id_plot` and pipe it to produce graphs.
-```{r tf-idf course, cache = TRUE}
-prepare_tf_idf_course <- function(data){
-
-  data %>%
-
-    # Selection 25 courses randomly
-    filter(
-      `Course ID` %in% sample(
-        x = unique(.$`Course ID`),
-        size = 25, 
-        replace = FALSE
-        )
-      ) %>%
-
-    # Select top 10 words per course 
-    group_by(
-      `Course ID`
-      ) %>%
-    filter(
-      n >= 2
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = `Course ID`
-      )
-
-  }
-
-set.seed(123)
-tf_idf_description %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_description")
-
-set.seed(123)
-tf_idf_overview %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_overview")
-
-set.seed(123)
-tf_idf_manual %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_manual")
-
-rm(prepare_tf_idf_course)
-```
-
-## Cluster Level
-```{r tf-idf cluster, cache = TRUE}
-prepare_tf_idf_cluster <- function(data){
-
-  data %>%
-
-    # Include the variable Cluster
-    left_join(
-      select(d_course, `Course ID`, Cluster),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Cluster)
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Cluster, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10, 
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Cluster
-      )
-
-}
-
-tf_idf_description %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_description")
-
-tf_idf_overview %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_overview")
-
-tf_idf_manual %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_manual")
-
-rm(prepare_tf_idf_cluster)
-```
-
-## Concentration Level
-```{r tf-idf concentration, cache = TRUE}
-prepare_tf_idf_concentration <- function(data){
-
-  data %>%
-
-    # Include the variable Concentration
-    left_join(
-      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Concentration)
-      ) %>%
-    gather(
-      key = X,
-      value = Concentration,
-      Concentration, `Concentration (additional)`,
-      na.rm = TRUE
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Concentration, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Concentration
-      )
-
-}
-
-tf_idf_description %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_description")
-
-tf_idf_overview %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_overview")
-
-tf_idf_manual %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_manual")
-
-rm(prepare_tf_idf_concentration, plot_tf_idf,
-   tf_idf_description, tf_idf_overview, tf_idf_manual)
-```
-
-# LDA
-The function `my_cast_tdm` casts our dataframes into a tdm.
-```{r my_cast_tdmxxxxx}
-my_cast_tdm <- function(data, level) data %>%
-  count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
-
-d_description_cast <- my_cast_tdm(d_description)
-d_overview_cast <- my_cast_tdm(d_overview)
-d_manual_cast <- my_cast_tdm(d_manual)
-
-rm(my_cast_tdm)
-```
-
-## Ideal Number of Topics (RUN ON UM COMPUTER)
-To decide the number of topics to discover, we run (four) three different tests.
-
-First we set the control for the test.
-```{r controls, eval = TRUE}
-my_control <- list(
-
-  nstart = 20,
-  seed   = 1 : 20,
-  best   = TRUE,
-
-  burnin = 1000,
-  iter   = 15000,
-  thin   = 100
-
-)
-```
-
-```{r fast control}
-my_control_fast <- list(
-
-  nstart = 1,
-  seed   = 1,
-  best   = TRUE,
-
-  burnin = 5,
-  iter   = 10,
-  thin   = 2
-
-)
-```
-
-###With Package built in Function
-The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
-```{r function my_FindTopicsNumber }
-my_FindTopicsNumber <- function(data_cast, n_topics){
-
-  FindTopicsNumber(
-
-  dtm = data_cast,
-  topics = n_topics,
-  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
-  method = "Gibbs",
-  control = my_control,
-  mc.cores = 4L
-
-  )
-
-}
-```
-We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
-```{r description topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_description,
-     file = "Output/LDA_ntopics.RDATA")
-
-print(time.taken)
-```
-
-We run the test for overview, documeting its duration. 
-```{r overview topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_overview , result_description,
-     file = "Output/LDA_ntopics.RDATA")
-
-print(time.taken)
-```
-
-We run the test for manuals, documenting its duration.
-```{r manual topics, cache = TRUE}
-start.time <- Sys.time()
-
-result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-save(result_manual, result_overview , result_description,
-     file = "Output/LDA_ntopics.RDATA")
-
-print(time.taken)
-```
-
-from 20, to 40, by 5 topics takes
-22min for overview
-11min for description
-5.5hrs for manuals
-
-We examine the result of the experiment by plotting them on a graph.
-```{r LDA number topics plot}
-
-load("Output/LDA_ntopics.RDATA")
-
-result_description %>%
-  FindTopicsNumber_plot
-
-result_overview %>%
-  FindTopicsNumber_plot
-
-result_manual %>%
-  FindTopicsNumber_plot
-
-```
-From the results we see that the ideal number of topics is somewhere between 35 and 40.
-
-## Fitting Model
-The function `my_cast_tdm` casts our dataframes into a tdm.
-```{r my_cast_tdm, eval = TRUE}
-my_cast_tdm <- function(data) data %>%
-  count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
-
-d_cast <- d_text %>% map(my_cast_tdm)
-
-rm(my_cast_tdm)
-```
-
-The function `my_LDA` fits an LDA model on the DTM using the previous controls.
-```{r my_LDA, eval= TRUE}
-
-#my_LDA
-my_LDA <- function(n_topics, corpus, control = my_control){
-
-  LDA_model <- LDA(
-    x       = corpus,
-    k       = n_topics,
-    method  = "Gibbs",
-    control = control
-    )
-}
-
-```
-
-Next we train our model with different number of topics.
-```{r LDA fit, cache = TRUE, eval = TRUE}
-topic_model <- tibble(
-
-  n_topic = seq(from = 5, to = 250, by = 5)
-
-  ) %>%
-
-  mutate(
-    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
-    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
-  )
-```
-
-##Model Evaluation
-###Perplexity
-Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
-```{r perplexity function, eval = TRUE}
-
-#perplexity Function
-my_perplexity <- function(model, d_cast){
-  perplexity(model, d_cast, estimate_theta = FALSE)
-}
-
-#Get perplexity
-test_perplexity <- topic_model %>%
-  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
-         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
-```
-
-###log_likelihood
-```{r log likelihood, eval = TRUE}
-# #my_loglikelihood function
-# my_loglike <- function(model){
-#   return(model@loglikelihood)
-# }
-# 
-# #get loglikelihood
-# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
-#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))
-
-#Log likelihood:
-test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
-                               logLik_manual   = map(.x = TM_manual,   .f = logLik))
-
-```
-
-###Plots
-```{r perplexity plots, eval = TRUE}
-#perplexity
-plot(topic_test$n_topic, topic_test$perplex_overview)
-plot(topic_test$n_topic, topic_test$perplex_manual)
-
-#log likelihood
-plot(test3$n_topic, test3$logLik_overview)
-plot(test3$n_topic, test3$logLik_manual)
-```
-
-##Get Beta/Gamma functions
-```{r getting gamma and beta, eval = TRUE}
-get_beta <- function(results){
-
-  tidy(results, matrix = "beta")           %>%
-    mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(beta) )
-
-}
-
-get_gamma <- function(results){
-
-  tidy(results, matrix = "gamma")          %>%
-    mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(gamma) )
-}
-
-```
-
-##Apply beta and gamma
-```{r applying get_gamma and get_beta, eval = TRUE}
-topic_model_gb <- topic_model %>%
-  transmute(
-    n_topic    = n_topic,
-    g_overview = TM_overview %>% map( .f = get_gamma),
-    g_manual   = TM_manual   %>% map( .f = get_gamma),
-    b_overview = TM_overview %>% map( .f = get_beta),
-    b_manual   = TM_manual   %>% map( .f = get_beta)
-      )
-```
-##Saving filed for different sessions
-```{r saving, eval = TRUE}
-save(topic_model_gb, 
-     file = "Output/topic_model_gb.RDATA")
-```
-#Distributions
-#NOTE: We need to select how many topics to use
-##Distributions of best models
-```{r Distributions, eval = FALSE}
-#select number of topics
-n_topics_overview <- 36
-n_topics_manual   <- 40
-
-#Crop models
-TM_overview <- topic_model_gb %>%
-  filter(n_topic== n_topics_overview)
-
-TM_manual   <- topic_model_gb %>%
-  filter(n_topic== n_topics_manual)
-
-#Distributions
-distribution <- list()
-
-distribution$beta$overview  <- TM_overview %>% pull(b_overview)
-distribution$beta$manual    <- TM_manual   %>% pull(b_manual)
-
-distribution$gamma$overview <- TM_overview %>% pull(g_overview)
-distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)
-
-```
-##Inspect topics
-THE TOPICS ARE SUPPER STRANGE!
-```{r inspect topics, eval = FALSE}
-
-inspect_topics <- function(d_beta){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(10, beta)
-
-}
-
-topics <-  lapply(
-  distribution$beta,
-  inspect_topics
-)
-```
-#App
-##Selectig keywords
-```{r key words}
-get_top_words <- function(d_beta, n = 5){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(n, beta) %>%
-    pull(term)%>%
-    unique
-}
-
-kw <- lapply(
-  distribution$beta,
-  get_top_words
-)
-```
-####TEMPORTARY: stopwords for keywords
-This section is for presentations
-```{r stopwords for kw}
-#kw$overview
-not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
-                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")
-
-remove_words <- function(x){
-  setdiff(x, not_include)
-}
-
-kw1 <- lapply(
-  kw,
-  remove_words
-)
-
-```
-##Convenience vectors for APP
-```{r for convenience}
-# set seed
-set.seed(1)
-
-#
-## All courses
-course_all <- d_course %>%
-  inner_join(
-    d_transcript,
-    by = "Course ID"
-  ) %>%
-  distinct(
-    `Course ID`
-  ) %>%
-  # remove semester abroad, skills and projects
-  filter(
-    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
-  ) %>%
-  pull
-
-#
-##courses following_semester
-course_following_semester <- sample(
-  x       = course_all,
-  size    = 60,
-  replace = FALSE
-  ) %>% sort
-```
-## Saving files for APP
-```{r app files}
-save(distribution, kw, course_all, course_following_semester,
-     file = "App/Recommender System/data_topic_models.RDATA")
-```
-
-# Visualization
-### Functions 
-This part is adapted 
-```{r LDA prepare, eval = F}
-prepare_data_LDA_beta <- function(d_beta){
-
-  data.frame(d_beta) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-      group_by(topic) %>%
-        top_n(10, beta) %>%
-      ungroup %>%
-      arrange(topic, desc(beta))
-
-} #repetition??? of inspect topics?
-
-prepare_data_LDA_gamma <- function(d_gamma, level = Course){
-
-  data_gamma <- data.frame(d_gamma) %>%
-    mutate(topic = paste("Topic", topic)) %>%
-    rename(`Course ID` = document)
-
-  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
-                                      rename(facet = `Course ID`)
-
-  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
-                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
-                                       filter(!is.na(Cluster)) %>%
-                                       rename(facet = Cluster)
-
-  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
-                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
-                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
-                                             rename(facet = Concentration)
-
-  data_gamma <- data_gamma %>%
-    group_by(facet, topic) %>%
-      summarise(gamma = sum(gamma)) %>%
-    filter(gamma > 0.05) %>%
-    ungroup %>%
-    arrange(facet, desc(gamma))
-
-  return(data_gamma)
-
-}
-
-# Bet Distribution
-test <- list()
-
-a <-  names(distribution)[1]
-test[[a]] <- lapply(distribution[[a]],
-                      prepare_data_LDA_beta)
-
-# Gamma Distribution
-b <- names(distribution)[2]
-test[[b]] <- lapply(distribution[[b]],
-                    prepare_data_LDA_gamma)
-
-rm(a,b #,test
-   )
-```
-This part is not adapted
-```{r LDA visualize, eval = F}
-visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-  ggplot(aes(x = reorder_within(term,
-                                by = beta,
-                                within = topic),
-             y = beta,
-             fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, scales = "free") +
-    scale_x_reordered() +
-    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
-    coord_flip() +
-    theme_light() +
-    theme(plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "beta.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(facet, 
-                              by = gamma, 
-                              within = topic), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ topic, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma1.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-
-visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){
-
-  data_prepared %>%
-    ggplot(aes(reorder_within(topic, 
-                              by = gamma,
-                              within = facet), 
-               y = gamma, 
-               fill = topic)) +
-    geom_col(show.legend = F) +
-    facet_wrap(~ facet, 
-               scales = "free") +
-    scale_x_reordered() +
-    coord_flip() +
-  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
-    theme_light() +
-    theme(axis.text.x = element_text(angle = 90, hjust = 0),
-          plot.title = element_text(hjust = 0.5))
-
-  ggsave(paste(id_plot, "gamma2.jpeg"),
-         width = 16, height = 10, path = "Plots/Topic Model")
-
-}
-```
-
-```{r LDA visualize all distrib, eval = F}
-visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){
-
-  # Beta distribution
-  data %>% 
-    prepare_data_LDA_beta %>%
-    visualize_LDA_beta(id_plot = id_plot)
-
-  # Gamma 1 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma1(id_plot = id_plot)
-
-  # Gamma 2 distribution
-  data %>% 
-    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
-    visualize_LDA_gamma2(id_plot = id_plot)
-
-}
-```
-
-```{r LDA visualize all level, eval = F}
-visualize_LDA_all_level <- function(data, id_plot = "test"){
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Course,
-                              id_plot = paste(id_plot, "_course"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Cluster,
-                              id_plot = paste(id_plot, "_cluster"))
-
-  data %>% 
-    visualize_LDA_all_distrib(level = Concentration,
-                              id_plot = paste(id_plot, "_concentration"))
-
-}
-```
-
-### Plots
-```{r LDA plot, cache = TRUE, eval = F}
-load("LDA.RDATA")
-
-LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")
-
-LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")
-
-LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
-```
-
-```{r label, eval = FALSE, eval = F}
-tidy(LDA_manual_10, "beta") %>%
-  filter(beta > 1e-3) %>%
-  bind_tf_idf(term = term, document = topic, n = beta) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf) %>%
-  arrange(topic, desc(tf_idf))
-
-  count(term, topic) %>%
-  arrange(desc(n)) %>%
-
-  filter(beta > 1e-3) %>%
-  group_by(term) %>%
-    mutate(n_topic = n(),
-           beta = beta / n_topic) %>%
-  group_by(topic) %>%
-    top_n(10, beta)
-
-  count(topic, term, wt = beta) %>%
-  (term = term, document = topic, n = n) %>%
-  group_by(topic) %>%
-  top_n(10, tf_idf)
-
-  group_by(term) %>%
-  summarise(beta = sum(beta)) %>%
-  arrange(desc(beta))
-
-labels <- list(
-  description_10 = "X"
-)
-```
-
-```{r label bis, eval = FALSE}
-visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
-              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
-                              "Sociology", "Law", "Research", "International Politics",
-                              "Philosophy", "Humanities"))
-
-visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
-              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
-                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
-                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
-                              "Math", "Management and ?"))
-visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
-              topic_names = c(
-                "Information", "Psycho", "Bio", "Chem", "Sociology",
-                "History", "skills", "Europe", "Philosophy", "IR",
-                "Conference", "Law", "Media", "Philosophy", "Economics",
-                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
-                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:6b7cfd788e0212b258d14cc2418c44b6ff60c64a84e3c3754cc24fc2d8e01ab1
+size 24779

### 2019-06-07 conference figures.Rmd
passed files to app

@@
----
-title: "Figures for conference paper"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-library(tidyverse)
-library(kableExtra)
-library(DiagrammeR)
-
-knitr::opts_chunk$set(echo = FALSE)
-theme_set(theme_light())
-
-load("Output/app_model.RDATA")
-load("Output/data_pillar_1.Rdata")
-load("Output/d_text.RDATA")
-load("Output/df_logLike_catalogue.RDATA")
-load("Output/CV.RDATA")
-
-output_folder <- "Conference/Figures"
-plot_width <- 6
-plot_height <- plot_width / 1.6 
-```
-
-```{r TM}
-gamma <- app_model$Gamma[[1]]
-beta  <- app_model$Beta[[1]]
-```
-
-```{r student_data}
-set.seed(2019)
-
-student_data <- d_transcript_augmented %>%
-
-  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%
-
-  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization
-
-  sample_n(10) %>%
-
-  arrange(`Academic Year`) %>%
-
-  print
-```
-
-```{r}
-course_data <- d_text$catalogues %>%
-
-  slice(50005:50014) %>%
-
-  select(`Course ID`, `Course Title`, Department = department, word) %>%
-
-  print
-```
-
-# Student data
-
-```{r fig_student_data}
-student_data %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/student_data.pdf"))
-```
-
-# Course data
-
-```{r fig_course_data}
-course_data %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/course_data.pdf"))
-```
-
-# Flow chart
-
-```{r}
-grViz("digraph flowchart{
-
-      fontname = Helvetica
-      size = 15
-
-      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]
-
-      edge [fontname = Helvetica, decorate = TRUE]
-
-      subgraph cluster_data {
-      label = 'Data';
-      style = filled;
-		  color = lightgrey;
-		  node [shape = cylinder];
-      CD [label = 'Course Data']
-      SD [label = 'Student Data']
-      }
-
-      subgraph cluster_input_user {
-      label = 'User Input';
-      style = filled;
-		  color = coral;
-
-      ID [label = 'Student ID']
-      KW [label = 'Selected Key Words']
-      CS [label = 'Selected Courses']
-      }
-
-      subgraph cluster_model_fitting{
-      label = 'Model Fitting';
-      style = filled;
-		  color = LavenderBlush;
-
-      TE [label = 'Topic Expertise']
-      AP [label = 'Academic Performance']
-
-      PM [label = 'Predictive Models']
-      x1 [shape = circle, width = .01, height = .01, label = '']
-      TM [label = 'Topic Model']
-
-      }
-
-      subgraph cluster_inter_last{
-      label = 'Intermediate Results';
-      style = filled;
-		  color = Tan;
-
-      GP [label = 'Grade Prediction']
-      AI [label = 'Student´s Academic Interests']
-      }
-
-      # Ouput
-      subgraph cluster_ouput {
-      label = 'System Output';
-      style = filled;
-		  color = lightCyan;
-
-      SUG [label = 'Course Suggestions']
-      WAR [label = 'Warnings']
-      PRE [label = 'Preparatory Coursework']
-      }
-
-      TR [label = 'Student´s Transcript']
-
-      # Invisible node
-      x2 [shape = circle, width = .01, height = .01, label = '']
-      x3 [shape = circle, width = .01, height = .01, label = '']
-
-      # edges
-
-      SD -> AP [weight = 2];
-      {SD, TM} -> TE;
-      {TM, KW} -> AI;
-      ID -> TR;
-      {PM, CS, TR} -> GP;
-      GP -> WAR;
-		  WAR -> PRE;
-
-      CD -> TM [label = '  LDA'];
-
-      {AP, TE} -> x1 [arrowhead = none]
-      x1 -> PM [label = '  Lasso'];
-
-      {TM, AI} -> x2 [arrowhead = none]
-      x2 -> SUG [label = '  KL distance'];
-
-      {TM, PM} -> x3 [arrowhead = none]
-      x3 -> PRE [label = '  KL distance'];
-
-      }
-      ")
-
-# Save by hand
-# image format: JPEG
-# Width: 626
-# Check Maintain aspect ratio
-# File name: Conference/Figures/Flowchart
-```
-
-# Model Selection (topic model)
-
-```{r}
-max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]
-
-df_logLike_catalogue %>%
-  ggplot(aes(x = n_topic, y = LogLikelihood)) +
-  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
-  geom_line(linetype = "dashed") +
-  geom_point() +
-
-  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +
-
-  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-```
-
-# Beta
-
-```{r plot_beta}
-plot_beta <- function(topic = 1, resize_factor = 1){
-
-  top <-  str_c("Topic ", topic)
-
-  beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
-
-    coord_flip() +
-
-    theme(axis.text.y = element_text(size = 11)) +
-
-    labs(title = str_c("Topic ", topic),
-         x = "Terms",
-         y = "Beta"
-         )
-
-  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
-         width = plot_width / resize_factor, height = plot_height / resize_factor)
-
-}
-```
-
-```{r fig_beta}
-plot_beta(1)
-```
-
-# Gamma
-
-```{r plot_gamma}
-plot_gamma <- function(course = "COR1002"){
-
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-
-    coord_flip() +
-
-    labs(title = course,
-         x = "Topics",
-         y = "Gamma"
-         )
-
-  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-
-}
-```
-
-```{r fig_gamma}
-plot_gamma("COR1004")
-
-resize_factor <- 1.6
-
-plot_beta(4, resize_factor = resize_factor)
-plot_beta(19, resize_factor = resize_factor)
-```
-
-# Topic Expertise
-```{r}
-courses <- paste("Course", 1 : 3)
-
-transcript <- tibble(Course    = courses,
-                     Grade     = c(6  , 9  , 2.5))
-
-gamma <- tibble(Course    = courses,
-                `Topic 1` = c(0  , 0.2, 0  ),
-                `Topic 2` = c(0.7, 0.2, 0.4),
-                `Topic 3` = c(0.2, 0.2, 0.2),
-                `Topic 4` = c(0.1, 0.2, 0.1),
-                `Topic 5` = c(0  , 0.2, 0.2))
-
-df1 <- gamma %>% 
-  gather(key = Topic, value = gamma, -Course) %>% 
-  arrange(Course) %>%
-
-  left_join(transcript, by = "Course") %>%
-  mutate(contribution = Grade/10 * gamma)
-
-topic_expertise <- df1 %>%
-  select(-gamma, - Grade) %>% 
-  spread(key = Topic, value = contribution)
-
-# Table
-
-transcript %>% 
-  mutate(Grade = str_c(Grade, "/10")) %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))
-
-gamma %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))
-
-topic_expertise %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))
-
-# Plot
-df1 %>% 
-  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
-  geom_col() +
-  labs(x = "Topics", y = "Topic Expertise")
-
-ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-# CV
-```{r}
-fit_lasso %>%
-  ggplot(aes(y = cv_error, group = 1)) +
-  geom_boxplot() +
-  theme(axis.ticks.y = element_line(color = "white"),
-        axis.text.y  = element_text(color = "white"),
-        panel.border = element_rect(color = "white"),
-        panel.grid   = element_line(color = "white")
-        ) +
-
-  labs(y = "Cross-Validation Mean Absolute Error") +
-  coord_flip()
-
-ggsave(filename = str_c("CV.jpeg"), path = output_folder,
-         width = plot_width/1.5, height = plot_height/3.5)
-
-fit_lasso %>%
-  summarize(Mean = mean(cv_error),
-            `Weighted mean` = weighted.mean(cv_error, n),
-            Median = median(cv_error),
-            `Standard Deviation` = sd(cv_error),
-            Minimum = min(cv_error),
-            Maximum = max(cv_error)) %>%
-  gather(key = x, value = y) %>% 
-  kable("latex", booktabs = TRUE, col.names = NULL) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/CV.pdf"))
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:8011c4bd9ae22ca4c0ce324c2c05f3b85a93bb3fb5e51a4633b9f50318bea107
+size 8329

### 2019-06-07 App/Recommender System/server.R

@@ -1,615 +1,3 @@
-library(tidyverse)
-library(tidytext)
-library(stringr)
-library(hunspell) #for stemming
-library(glmnet)   #for grade prediction
-library(seewave)# KL distance
-
-
-#
-#General set up ---------------------------------------------------------------------------------
-load("data_pillar_1.RDATA")
-load("app_model.RDATA") #contains app_model and full dataframe of topic models
-load("rules_clean.RDATA")
-load("grade_prediction.RDATA")
-load("student_TP.RDATA")
-load("d_text.RDATA")
-
-course_all <- app_model$`All Courses`[[1]]
-course_advanced <- course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
-kw_used <- app_model$kw[[1]] #is the same as in ui
-
-titles <-  d_text$catalogues %>%
-  select(`Course ID`, `Course Title`, department) %>% 
-  distinct %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
-                                           T ~ `Course Title`),
-                      `Course_id` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
-                                              T ~ "XXX0000")) %>% 
-  transmute(`Course ID` = `Course ID`, course_and_title = paste(`Course_id`, `c_title`, sep = " - "))
-
-# titles <-  d_text$catalogues %>%
-#   select(`Course ID`, `Course Title`, department) %>% 
-#   distinct %>% transmute(`Course ID`= `Course ID`,
-#                          c_title= case_when(is.na(`Course Title`) ~ `Course ID`,
-#                                             T ~ `Course Title`))
-
-#
-#server ---------------------------------------------------------------------------------
-function(input, output, session) {
-  
-  # ---------------------------------------------------------------------------------
-  ## -- RED FLAGS --
-  # ---------------------------------------------------------------------------------
-  
-  ##Set up
-  
-  #Raw Data for RS:
-  raw_rules <- rules_clean %>%
-    select(-rules_rules)   %>%
-    filter(type_rule == "SR")
-  
-  #Helper function: return tibble of type_rules
-  get_type_rules <-  function(type) {
-    tmp <- raw_rules %>%
-      filter(ID == type) %>%
-      pull(rules_RS)
-    
-    return(tmp[[1]])
-  }
-  
-  #Helper: resettabe input
-  output$resetable_input <- renderUI({
-    times <- input$reset_input
[…]

### 2019-06-07 App/Recommender System/ui.R

@@ -1,182 +1,3 @@
-library(tidyverse)
-library(tidytext)
-library(shiny)
-library(shinythemes)
-
-#
-#General set up---------------------------------------------------------------------------------
-
-load("data_pillar_1.RDATA")
-load("app_model.RDATA") #contains distribution, kw, course_all, course_following_semester.
-load("rules_clean.RDATA")
-
-kw_used <- app_model$kw[[1]]
-
-#
-# ui ---------------------------------------------------------------------------------
-navbarPage(
-  theme = shinytheme("united"),
-  
-  # App title
-  title = "Recommender System",
-  
-  # ---------------------------------------------------------------------------------
-  # -- RED FLAGS --
-  # ---------------------------------------------------------------------------------
-  
-  tabPanel(
-    
-    # Panel Title
-    title = "Red Flag",
-    
-    # Sidebar layout
-    sidebarLayout(
-      
-      # Sidebar panel for inputs
-      sidebarPanel(
-        
-        # Input: student id number
-        textInput(
-          inputId = "student",
-          label   = "Student ID",
-          value   = "6113335"
-          ),
-        
-        uiOutput('resetable_input'),
-        tags$head(tags$style("#resetable_input{color: black; font-size: 14px;}")),
-        tags$hr(),
-        actionButton("reset_input", "Reset inputs")
-        
-        ),
-      
-      # Main panel for displaying outputs
-      mainPanel(
-        
-        # Output: dataset
-        tableOutput(
-          outputId = "red_flags"
-          ),
-        tags$head(tags$style("#red_flags{color: black; font-size: 20px;}"))
-        
-        )
-      
-      )
-    
-    ),
-  
-  # ---------------------------------------------------------------------------------
-  # -- TRAFFIC LIGHTS --
-  # ---------------------------------------------------------------------------------
-  
-  tabPanel(
-    
-    # Panel Title
-    title = "Traffic Lights",
-    
-    # Sidebar layout
-    sidebarLayout(
-      
-      # Sidebar panel for inputs
-      sidebarPanel(
-        
-        # Input: student id number
-        textInput(
-          inputId = "student_traffic",
-          label   = "Student ID",
-          value   = "6113335"
-        ),
-        
-        uiOutput('resetable_input_traffic'),
-        tags$head(tags$style("#resetable_input_traffic{color: black; font-size: 19px;}")),
-        tags$hr(),
-        actionButton("reset_input_traffic", "Reset inputs")
-        
-      ),
-      
[…]

### 2019-06-07 App/Rules/server.R

@@ -1,45 +1,3 @@
-
-
-#
-# Setup
-library(shiny)
-library(dplyr)
-#load("rules.RDATA")
-load("rules_clean.RDATA")
-
-
-#
-# Server
-function(input, output) {
-  
-  output$rules <- renderDataTable(
-    
-    expr = {
-      
-      # Selected type of rules
-      my_rules <- as_tibble(rules_clean) %>%
-        select(-rules_RS) %>%
-        filter(type_rule == input$rules) %>%
-       #get(input$rules) %>%
-         #filter for selected type of rules
-         filter(ID == input$item) %>%
-        pull(rules_rules) 
-      
-      my_rules[[1]] %>%
-         # filter rows based on the ranges of the three buttons
-         filter(
-           between(count     , input$count[1]     , input$count[2]     ),
-           between(confidence, input$confidence[1], input$confidence[2]),
-           between(lift      , input$lift[1]      , input$lift[2]      )
-         )
-      
-    },
-    
-    options = list(
-      pageLength = 10,
-      lengthMenu = c(10, 25, 50, 100)
-      )
-    
-    )
-  
-}
+version https://git-lfs.github.com/spec/v1
+oid sha256:c83b766f982c3bea9269d93d4ba29c47ca59f7ed23b89cbf4eff27ddebfb3274
+size 948

### 2019-06-07 App/Rules/ui.R

@@ -1,98 +1,3 @@
-
-fluidPage(
-  
-  # App title
-  titlePanel("Rules"),
-  
-  # Sidebar layout
-  sidebarLayout(
-    
-    # Sidebar panel for inputs
-    sidebarPanel(
-      
-      # Input: button for the type of rules
-      radioButtons(
-        inputId = "rules",
-        label   = "Type of rules",
-        choices = c(
-          "Association rules" = "AR",
-          "Sequence rules"    = "SR"
-        ),
-        selected = "SR"
-      ),
-      
-      # Input: button for the type of rules
-      radioButtons(
-        inputId = "item",
-        label   = "Type of item in rules",
-        choices = c(
-          "taken"  = "taken",
-          "PF"     = "PF",
-          "HL"     = "HL",
-          "TPF"    = "TPF",
-          "THL"    = "THL",
-          "G"      = "G"
-        ),
-        selected = "taken"
-      ),
-      
-      # Horizontal line
-      tags$hr(),
-      
-      # Input: Slider for the support
-      sliderInput(
-        inputId = "count",
-        label   = "Count",
-        min     = 1,
-        max     = 3000,
-        step    = 1,
-        value   = c(1, 3000)
-        ),
-      
-      # Input: Slider for the Cconfidence
-      sliderInput(
-        inputId = "confidence",
-        label   = "Confidence",
-        min     = 0,
-        max     = 1,
-        step    = 0.01,
-        value   = c(0.4, 1)
-      ),
-      
-      # Input: Slider for the Confidence
-      sliderInput(
-        inputId = "lift",
-        label   = "Lift",
-        min     = 0,
-        max     = 100,
-        step    = 0.01,
-        value   = c(1, 100)
-      ),
-      
-      # Horizontal line
-      tags$hr(),
-      
-      # Text
-      helpText("For PF and HL rules, we compute the confidence and lift as follows:"),
-      helpText(" "),
-      helpText(" "),
-      helpText("Confidence(A_fail -> B_fail) = P( (A_fail -> B_fail) | (A_fail -> B) )."), 
-      helpText("In other words, given a student has failed course A and is taking course B, what is the probability that (s)he will fail course B"),
-      helpText(" "),
-      helpText(" "),
-      helpText("Lift(A_fail - B_fail) = Confidence(A_fail -> B_fail) / Probability(B_fail | B)."),
[…]

### 2019-06-07 App/Recommender System/server.R
divides app in two sections for stm and lda

@@ -1,3 +1,3 @@
 version https://git-lfs.github.com/spec/v1
-oid sha256:9ad7154d8d969ff418b416c783aff2d127c1b3cf718d00c82a32233a6ff11372
-size 15684
+oid sha256:21c3ce1efbfe3dd6087676021cfe779252f95c4bb5641778e4dc5f2a009e0916
+size 30992

### 2019-06-07 App/Recommender System/ui.R
User unterface divide into two sections

@@ -1,3 +1,3 @@
 version https://git-lfs.github.com/spec/v1
-oid sha256:341cb6a7d0897a2932184696aa1996fc234fc207db7552caa5e3f1ebf44d3d01
-size 4568
+oid sha256:c8b3efb23c7205966ce4de01dffadbc4e364582c4e1a5d0b4f366df51da43956
+size 7523

### 2019-06-07 Data Preparation - Course Data.Rmd
Raphaels files from pull

--- 2019-04-15 Data Preparation - Course Catalogues.Rmd
@@
----
-title: "Data Preparation - Course Catalogues"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
-
-library(tidyverse)
-library(tidytext)
-library(gsheet) # import spreadsheets from google drive
-library(tm)
-library(hunspell) # Stemmer
-library(magrittr)
-```
-
-# Helper functions
-
-```{r helpers}
-extract_id_pdf    <- function(string) string %>% str_sub(start = 1, end = - 5)
-extract_id_course <- function(string) string %>% str_sub(start = 1, end =   7)
-
-collapse_or       <- function(string) string %>% str_c(collapse = "|")
-collapse_space    <- function(string) string %>% str_c(collapse = " ")
-
-symbol_to_line    <- c("\r\n", "\n") %>% collapse_or
-split             <- function(string) string %>% str_split(pattern = symbol_to_line) %>% .[[1]]
-
-remove_header_UCV <- function(string) string %>% str_sub(28, -1)
-
-overview_section_start <- function(string) string %>% str_detect(pattern = "^ *Core Courses|^ *Mathematics and")
-overview_section_end   <- function(string) string %>% str_detect(pattern = "Appendix|^ *Courses at\n *Maastricht Science Programme|^*Courses Available at University")
-
-headers_UCM_UCV_MSP <- c("^ *Core Courses",
-                     "^Humanities \\(HUM\\)",
-                     "^ *Life Sciences Courses",
-                     "^Sciences \\(SCI\\)",
-                     "^ *Social Sciences",
-                     "^ *Skills Trainings",
-                     "^ *Projects",
-                     "^Undergraduate Research",
-                     "Appendix",
-                     "^ *Mathematics and") %>% collapse_or
-is_header     <- function(string) string %>% str_detect(pattern = headers_UCM_UCV_MSP)
-
-course_code_UCM_UCV_MSP <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
-                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA", # UCV
-                         "BIO", "CHE", "MAT", "PHY", "NEU", "INT", "PRA" #MSP
-                         ) %>% collapse_or
-overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM
-```
-
-# Importing course data
-
-```{r read_in_pdfs}
-read_in_pdfs <- function(file){
-
-  Corpus(
-    x             = DirSource(file),
-    readerControl = list(reader = readPDF(control = list(text = "-layout")))
-    ) %>%
-
-    # turn corpus into a tibble to facilitate manipulation
-    as.list %>% tibble(raw = .) %>%
-
-    transmute(
-      ID   = raw %>% map(function(x) x$meta$id) %>% map_chr(extract_id_pdf),
-      text = raw %>% map(content) 
-      )
-
-}
-```
-
-## Application
-```{r d_text}
-d_text <- list()
-```
-
-```{r d_text$catalogues}
-d_text$catalogues <- tribble(
-  ~ ID              ,  ~ page_top                  , ~ before_overview                       ,
-  "European_studies", "^.Bachelor European Studies", "Faculty of Arts and Social Sciences"   ,
-  "Psychology"      , "^.Bachelor Psychology"      , "Faculty of Psychology and Neuroscience",
-  "UCV"             , NA_character_                , NA_character_                           ,
-  "UCM"             , NA_character_                , NA_character_                           ,
-  "MSP"             , NA_character_                , NA_character_
-  ) %>%
-
-  full_join(read_in_pdfs("./Input/Catalogues/UM"), by = "ID") %>%
-
-  mutate(year = "2018-2019") %>%
-  rename(catalogue = text)
-```
-
-```{r d_text$manuals}
-d_text$manuals <- read_in_pdfs("./Input/Manuals 2017-18") %>% rename(`Course ID` = ID) %>% mutate(text = text %>% map_chr(str_c, collapse = " "))
-```
-
-# Extracting course overviews
-
-In order to conduct a topic analysis of course content, we extract the *overview* and *description* of each course from the course catalogues, as well as the  *full text*  from the Course Manuals.
-
-(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)
-
-We start by extracting the overviews which are 1 or 2 page long and contain important information of a course.
-To accomplish this, for each catalogue (loop), we first use `grep` to determine which pages should be excluded from the analysis (`pages_to_exclude`).
-These pages are typically headers.
-Excluding them before the analysis allows use to keep the code relatively simple.
-We also make use the fact that the overviews always start with the code of the course, i.e.
-it starts with one of the elements of `course_code`; and we use `grep` to identify the first page of each overview.
-We use grep a 3rd time to identify the page containing the header *Core Coureses (COR)* and which marks the beginning of the overviews in the catalogue, and we loop from this page to the last page of the catalogue.
-
-In the loop, we first determine the content of the current and following page.
-If the current page is the first page of an overview, then we identify the overview (one or two pages) and save it to the tibble `d_description`.
-To identify the overview of a course, we check if the following page is either the first page of an overview or a page to exclude.
-If it is either of these, then the overview correspond to the content of the current page; but if the following page is neiter of these, then the overview correspond to the content of the current page and that of the following page.
-
-## ES, PSY
-```{r overview_ES_PSY}
-overview_ES_PSY <- function(catalogue, ID, page_top, before_overview){
-
-  catalogue %>%
-
-    # create tibble to facilitate manipulation
-    collapse_space %>% split %>% tibble(line = .) %>%
-
-    # remove page numbers and page top to faciliate the identification of the course description starts
-    mutate(page_top    = str_detect(line, page_top),
-           page_number = page_top %>% lead(default = FALSE)) %>%
-
-    filter(!page_top, !page_number) %>%
-
-    # identify course descriptions
-    mutate(overview_start = str_detect(line, before_overview) %>% lag(default = FALSE)) %>%
-    mutate(overview_id    = cumsum(overview_start)) %>%
-
-    filter(overview_id != 0) %>%
-
-    # extract course description
-    group_by(overview_id) %>% 
-    summarize(text        = line %>% str_c(collapse = " "),
-              `Course ID` = line %>% str_c %>% .[[1]]) %>%
-    mutate(department  = ID) %>%
-    select(-overview_id)
-
-}
-```
-
-## UCM, UCV, MSP
-
-```{r paste_if_2_page_overview}
-paste_if_2_page_overview <- function(page, page_following){
-
-  if(! page %>% overview_start) NA_character_ # if the page is not the start of an overview, return an NA
-
-  else{
-    if(page_following %>% overview_start | is.na(page_following))  page # include possibility of NA for last page of overview section
-    else                                                           str_c(page, page_following)
-  }
-
-}
-```
-
-```{r overview_UCM}
-overview_UCM_UCV_MSP <- function(catalogue, ID){
-
-  if(ID == "UCV") catalogue <- catalogue %>% remove_header_UCV
-
-  # create tibble to facilitate manipulation
-  catalogue %>% tibble(page = .) %>%
-
-  # identify start and end of overview section of catalogue
-  mutate(overview_section_start = page %>% overview_section_start,
-         overview_section_end   = page %>% overview_section_end  ) %>%
-
-  # filter the overview section
-  mutate(after_overview_section_start = cumany( overview_section_start),
-         before_overview_section_end  = cumall(!overview_section_end  )) %>%
-  filter(after_overview_section_start & before_overview_section_end    ) %>%
-
-  # exclude headers to only keep the course overviews themselves
-  filter(! page %>% is_header) %>%
-
-  # paste current page and following page (`lead(page)`) if overview is two page long
-  transmute(
-    text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
-    `Course ID` = text %>% extract_id_course) %>%
-    mutate(department  = ID) %>%
-    filter(!is.na(text))
-
-}
-```
-
-## Application
-```{r overview}
-overview <- function(ID, catalogue, page_top, before_overview){
-
-  if(ID %in% c("European_studies", "Psychology")){
-    catalogue %>% overview_ES_PSY(ID = ID, page_top = page_top, before_overview = before_overview)
-
-  }else if(ID %in% c("UCM", "UCV", "MSP")){
-    catalogue %>% overview_UCM_UCV_MSP(ID = ID)
-
-  } else "to do"
-
-}
-```
-
-```{r}
-d_text$catalogues <- d_text$catalogues %>% mutate(overviews = list(ID, catalogue, page_top, before_overview) %>% pmap(overview))
-```
-
-```{r}
-d_text$catalogues <- d_text$catalogues$overviews %>% bind_rows
-```
-
-# Clean data
-
-## Tidy data
-To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
-
-```{r}
-tidy_text <- function(df) df %>% unnest_tokens(output = word, input = text)
-```
-
-```{r tidy d_text}
-d_text <- d_text %>% map(tidy_text) %T>% print
-
-rm(tidy_text)
-```
-
-## Stem data
-We then use the function `hunspell_stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`.
-
-We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`).
-We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`.
-However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals.
-Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
-
-```{r stem}
-stem <- function(term) {
-
-  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
-  n_stems <- length(stems)            
-  if (n_stems == 0) term              # if no stems, return original term
-  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
-
-}
-```
-
-```{r dictionary, cache = TRUE}
-dictionary <- union(d_text$catalogues$word, d_text$manuals$word) %>%
-
-  tibble(word = .) %>%
-
-  mutate(word_stem = word %>% map_chr(stem))
-
-# terms for which the stem differs from the original word
-filter(dictionary, word != word_stem)
-```
-
-```{r destem}
-# TODO: "destem" terms by hand: cuss => discuss
-filter(dictionary, word_stem == "cuss")
-```
-
-Finally, we create a function `stem_with_dictionary` that performs a left join on the dataframe it takes as input with `dictionary`, thus adding the word stems to the original dataframe.
-
-Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
-
-```{r stem_with_dictionary}
-stem_with_dictionary <- function(data){
-
-  data %>% left_join(dictionary, by = "word") %>%
-
-    rename(word_original = word,
-           word          = word_stem)
-
-}
-```
-
-```{r stem d_text}
-d_text <- d_text %>% map(stem_with_dictionary)
-
-rm(stem, stem_with_dictionary)
-```
-
-# Remove stopwords
-
-Finally, we want to filter out some uninformative words from our textual data.
-For this, we first store all the unwanted words in a vector `sw_owm`.
-We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`.
-Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
-```{r sw_own}
-sw_own <- 1 : 1e3 %>% as.character %>% tibble( word = .)
-```
-
-```{r remove_sw}
-remove_sw <- function(data){
-
-  data %>%
-
-    anti_join(stop_words, by = "word") %>%
-    anti_join(sw_own    , by = "word") %>%
-
-    # remove words of 1 or 2 letters
-    filter(nchar(word) > 2) %>%
-
-    # Remove words occuring once or twice in corpus (usually names, website links or typos)
-    add_count(word) %>%
-    filter(n > 2) %>%
-    select(-n) %>%
-
-    # remove NA
-    filter(!is.na(word))
-
-}
-```
-
-```{r sw d_text}
-d_text <- d_text %>% map(remove_sw) %T>% print
-
-rm(sw_own, remove_sw)
-```
-
-# Current course
-```{r}
-course_current <- d_text$catalogues %>% filter(department == "UCM") %>% distinct(`Course ID`) %>% pull
-```
-
-# Save data
-
-```{r}
-save(course_current, file = "Output/course_current.RDATA")
-save(d_text        , file = "Output/d_text.RDATA")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:3c135a6e599db989adc786cae3f0b15798f02d897be1bb2c1ac7f8b3f3ce2be0
+size 13008

### 2019-06-07 Data Preparation - Misc.Rmd
Raphaels files from pull

--- 2019-05-16 Data Preparation - Misc.Rmd
@@
----
-title: "Data Preparation"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
-
-library(tidyverse)
-library(tidytext)
-library(gsheet) # import spreadsheets from google drive
-library(tm)
-library(hunspell) # Stemmer
-library(magrittr)
-```
-
-# Import Data
-The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons).
-We use the function `gsheet2tbl` to import them to `R Studio` as tibbles.
-We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
-
-## List of AoD's and Assessments
-First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`.
-` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
-Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively).
-We also any imported emtpy cells.
-```{r list_AoD_assessment}
-list_AoD_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
-
-  map(na.omit)
-
-# selection of most important types of assessment an AoD to keep plots clear
-list_AoD_assessment$`Assessment for Plot` <- list_AoD_assessment$Assessment[list_AoD_assessment$`Assessment for Plot` == 1] %T>% print
-list_AoD_assessment$`Aim for Plot`        <- list_AoD_assessment$Aim       [list_AoD_assessment$`Aim for Plot`        == 1] %T>% print
-```
-
-## Course Data
-We import three spreadsheets from the drive and transform them into the so-called *tidy format*.
-The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.
-The tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment; and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.
-
-```{r d_course}
-d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>% print
-```
-
-```{r d_assessment}
-d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key   = Assessment, value = assessment_covered, Paper : Participation) %>%
-
-  filter(assessment_covered) %>%
-
-  select(- c(assessment_covered, `Comment on Assessment`)) %T>%
-
-  print
-```
-
-```{r d_ILO}
-d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')
-```
-
-```{r d_AoD_from_ILO}
-d_AoD_from_ILO <- d_ILO %>%
-
-  rename(ILO = Objectives) %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- c(AoD_covered, Comments, Comments_for_Jeroen)) %T>%
-
-  print
-```
-
-# Variable Engineering
-## Course Data
-The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
-
-### AoD
-In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it.
-For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.
-
-#### AoD from ILOs
-(For this section we use: `d_ILO`-indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD)
-
-In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
-```{r d_AoD_ILO}
-d_AoD_from_ILO
-```
-
-#### AoD from Assessment
-(For this section we use: `d_assessment`-indicates which type(s) of assessment each course contains with one row per course-assessment)
-
-In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers.
-We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`.
-`map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.
-Thus, the first step is to import this matrix:
-
-```{r map_assessment_AoD}
-map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
-
-  mutate_if(is.numeric, as.logical) %>%
-
-  # Transform data into tidy format to facilitate manipulation
-  gather(key = AoD, value = AoD_covered, `Matrix Complete` : `Intercultural Skills`) %>%
-
-  filter(AoD_covered) %>%
-
-  select(- AoD_covered) %>%
-
-  arrange(Assessment) %T>%
-
-  print
-```
-
-Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments.
-To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
-In the loop, we first extract a row of `d_assessment` and save it as `observation`.
-Then, we determine the corresponding assessment which we save as `assessment`.
-Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
-```{r d_AoD_assessment}
-d_AoD_from_assessment <- d_assessment %>%
-
-  left_join(map_assessment_AoD, by = "Assessment") %>%
-
-  filter(!is.na(AoD)) %T>%
-
-  print
-
-rm(map_assessment_AoD)
-```
-
-#### Combining AoD from ILOs and from assessments
-Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
-```{r rbind d_AoD_ILO and d_AoD_assessment}
-d_AoD <- rbind(
-  d_AoD_from_ILO        %>% select(`Course ID`, AoD),
-  d_AoD_from_assessment %>% select(`Course ID`, AoD)
-  ) %>%
-
-  distinct %>%
-
-  arrange(`Course ID`) %T>%
-
-  print
-
-rm(d_AoD_from_assessment, d_AoD_from_ILO)
-```
-
-### Courses
-(In this section we use: `d_course`- contains information at the course-level such as in which cluster and concentration(s) they belong, and in which period(s) they are offered.)
-
-Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level.
-For this we create the following three tibbles:
-1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
-2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
-3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
-Then we use a `full_join` to add these variables to the tibble `d_course`.
-```{r d_course detail}
-count_and_paste <- function(df, var, colnam1, colnam2){
-
-  df %>%
-
-    group_by(`Course ID`) %>%
-
-    summarize(
-      !!ensym(colnam1) := n_distinct(!!enquo(var)),
-      !!ensym(colnam2) := str_c(!!enquo(var), collapse = ", ")
-      )
-
-}
-
-join_by_course_ID <- function(df1, df2) left_join(df1, df2, by = "Course ID")
-```
-
-```{r join d_course_detail}
-d_course <- d_course %>%
-
-  join_by_course_ID( d_AoD        %>% count_and_paste(AoD       , n_AoD       , `AoD Covered`        ) %T>% print) %>%
-
-  join_by_course_ID( d_assessment %>% count_and_paste(Assessment, n_assessment, `Assessments Covered`)           ) %>%
-
-  join_by_course_ID( d_ILO        %>% count_and_paste(Objectives, n_ILO       , `ILO Covered`        )           ) %>%
-
-  select(
-    `Course ID`, `Course Title`, Cluster,
-    n_ILO,
-    n_assessment, `Assessments Covered`,
-    n_AoD, `AoD Covered`,
-    everything()
-    ) %T>%
-
-  print
-
-rm(count_and_paste, join_by_course_ID)
-```
-
-The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level).
-Yet, these course are also offered at the `2000` level (intermediate level).
-We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
-```{r create UGR2000}
-UGR_2000 <- d_course %>%
-
-  filter( `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
-
-  mutate(
-    `Course ID` = case_when(
-      `Course ID` == "UGR3001" ~ "UGR2001",
-      `Course ID` == "UGR3002" ~ "UGR2002",
-      `Course ID` == "UGR3003" ~ "UGR2003",
-      `Course ID` == "UGR3005" ~ "UGR2005"
-      )
-    ) %T>%
-
-  print
-
-d_course <- d_course %>% rbind(UGR_2000)
-
-# print UGR course
-print(d_course %>% filter(str_detect(`Course ID`, "UGR") ) )
-
-rm(UGR_2000)
-```
-
-Finally, we add a series of informative variable at the course level.
-```{r d_course additional info}
-d_course <- d_course %>%
-
-  separate(
-    col     = `Course ID`,
-    into    = c("Letters", "Number"),
-    sep     = 3,
-    remove  = FALSE,
-    convert = TRUE
-    ) %>%
-
-  mutate(
-    Level   = case_when(
-      between(Number, 1000, 1999) ~ "Introductory",
-      between(Number, 2000, 2999) ~ "Intermediate",
-      between(Number, 3000, 3999) ~ "Advanced"    )
-    ) %>%
-
-  select(`Course ID`, Letters, Number, Level, everything()) %T>%
-
-  print
-```
-
-## Ttarget courses
-```{r}
-d_course <- d_course %>%
-  mutate(target = Number > 2000 & Type == "Elective" & (! str_detect(`Course ID`, "SA")))
-```
-
-# Save Data
-```{r}
-save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
-     file = "Output/data_general.RDATA")
-save(d_course, file = "Output/data_pillar_2.RDATA")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:92b8c2a4e364dca37026f4ebd352d442fd51e0e2d408bbcc7ee0f9bc502becb6
+size 11162

### 2019-06-07 Data Preparation - Student Data.Rmd
Raphaels files from pull

--- 2019-05-16 Data Preparation - Student Data.Rmd
@@
----
-title: "Data Preparation"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
-
-library(tidyverse)
-```
-
-# Import Data
-The tibble `d_transcript` contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it.
-
-```{r read_csv_own_parsing}
-col_parsing <- cols(
-  `Student Number`                      = "c",
-  `Program (Abbreviation)`              = "c",
-  `Appraisal Status`                    = "c",
-  `Module Booking Reason (Description)` = "c",
-  `Object name`                         = "c",
-  `Start date`                          = "c",
-  `End Date`                            = "c"
-  )
-
-read_csv_own_parsing <- function(file) file %>% read_csv(col_types = col_parsing)
-```
-
-```{r d_transcript, cache = TRUE}
-d_transcript <- paste0("Input/Raw Grades/grades", 1 : 2, ".csv") %>%
-
-  map(read_csv_own_parsing) %>%
-
-  bind_rows
-
-rm(col_parsing, read_csv_own_parsing)
-```
-
-# Variable Engineering
-
-* Is `Academic Work ID` a unique ID number?
-
-(In this section we use: `d_transcript`- contains the transcript information of students as was provided.
-It has 40 columns, and rows correspond roughly to a type of grade (e.g.
-final grade, attendance) per student per course per time they took it).
-
-Our dataframe contains many variables and rows that are either empty or meaningless for our analysis.
-First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor").
-Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
-
-The data set `d_transcript` contains both the failed grades and the grade of the resit, and does not distinguish between them (same student, same course, same yera, same period, but different grade).
-
-```{r d_transcript helper}
-course_letter_UCM <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>% paste(collapse = "|")
-
-is_UCM      <- function(course_code) course_code %>% str_detect(course_letter_UCM)
-is_elective <- function(course_code) course_code %>% str_detect("HUM|SCI|SSC")
-```
-
-```{r d_transcript row selection}
-d_transcript <- d_transcript %>%
-
-  # for simplicity, we only keep 
-  # courses taken in the framework of the *BA Liberal Arts and Sciences (UCM)* (Program (Abbreviation) = 7501)
-
-  filter(`Program (Abbreviation)` == "7501") %>%
-
-  # The dataset has multiple rows for each student - course.
-  # Following guidelines of Richard Vos, we only consider: 
-  # `Appraisal (Description)` == "Grade supervisor"
-  # and `Appraisal Type` == "7055"
-
-  filter(
-    `Appraisal (Description)` == "Grade supervisor",
-    `Appraisal Type`          == "7055" # removes ~ 15 observations
-    )
-```
-
-```{r d_transcript column selection}
-d_transcript <- d_transcript %>%
-  # keep variables: Student ID, course ID, when a course is taken and the grade 
-  select(
-    `Student ID`   = `Student Number`,
-    `Course ID`    = `Module (Abbrev.)`,
-    Year_numerical = `Academic Year`,
-    Period         = `Academic Session`,
-    Grade          = `Grade symbol`
-    )
-```
-
-```{r clean_grade}
-clean_grade <- function(grade){
-
-  if(grade == "NG" | is.na(grade)) return(NA) # conservative approach
-
-  grade %>% str_replace(",", ".") %>% as.numeric
-
-}
-```
-
-```{r clean_period}
-clean_period <- function(period){
-
-  # Course spanning over multiple period are recorder with a 1, 2 or 3
-  if(period == 1) return("1 to 6")
-  if(period == 2) return("1 to 3")
-  if(period == 3) return("4 to 6")
-
-  # Course spanning over a single period are recorded in the 100's, 200's, etc.
-  # The digit of the hundred indicates the period.
-  period %/% 100 %>% as.character
-
-}
-```
-
-```{r clean_year}
-clean_year <- function(year) str_c(year, year + 1, sep = "-")
-```
-
-```{r clean d_transcript}
-d_transcript <- d_transcript %>%
-
-  mutate(
-
-    # Clean grade, period and year
-    Grade          = Grade          %>% map_dbl(clean_grade ),
-    Period         = Period         %>% map_chr(clean_period),
-    `Academic Year`= Year_numerical %>% clean_year,
-
-    # extract first period for courses spanning mutliple periods
-    period_numerical = substr(Period, 1, 1),
-
-    # Combine year & period to chronologically order courses using a single variable
-    time = str_c(Year_numerical, period_numerical) %>% as.numeric,
-
-    grade_ceil = ceiling(Grade)
-
-    )
-```
-
-```{r}
-d_transcript <- d_transcript %>% filter(!is.na(Grade))
-```
-
-## Augment d_transcript with d_course
-```{r}
-load("Output/data_general.RDATA")
-d_transcript_augmented <- d_transcript %>%
-  left_join(select(d_course, - Period), by = c("Course ID"))
-```
-
-### Issues
-```{r issue d_transcript, eval = FALSE}
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination.
-  add_count(
-    `Student ID`, `Course ID`, time,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # multiple rows with unique student ID - course ID - time combination - grade.
-  add_count(
-    `Student ID`, `Course ID`, time, Grade,
-    sort = TRUE
-    ) %>%
-  print
-
-d_transcript %>%
-
-  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
-  filter(`Student ID` == "6087587") %>%
-  arrange(`Course ID`) %>%
-  pull(`Course ID`)
-
-  # ~ 10 incomplete rows for a student's profile
-  d_transcript %>% filter(`Student ID` == "0481343") %>% View
-
-#TODO: list issues here
-```
-"Output/data_general.RDATA"
-# Save Data
-```{r}
-save(d_transcript, d_transcript_augmented, file = "Output/data_student.RDATA")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:ff573eaf8fd6b06fcbdcb914cd193a3ab8dcca6bbc1c35dcabed64dbf5674ce3
+size 5823

### 2019-06-07 Conference/COPA2019/paper/draft.tex
final version
conferences files

@@
- %\documentclass[wcp,gray]{jmlr} % test grayscale version
- %\documentclass[wcp]{jmlr}% former name JMLR W\&CP
-\documentclass[pmlr]{jmlr}% new name PMLR (Proceedings of Machine Learning)
-
- % The following packages will be automatically loaded:
- % amsmath, amssymb, natbib, graphicx, url, algorithm2e
-
- %\usepackage{rotating}% for sideways figures and tables
-\usepackage{longtable}% for long tables
-
- % The booktabs package is used by this sample document
- % (it provides \toprule, \midrule and \bottomrule).
- % Remove the next line if you don't require it.
-\usepackage{booktabs}
- % The siunitx package is used by this sample document
- % to align numbers in a column by their decimal point.
- % Remove the next line if you don't require it.
-\usepackage[load-configurations=version-1]{siunitx} % newer version
- %\usepackage{siunitx}
-
-% Package to make table with multi rows and columns
-\usepackage{multirow}
-
- % to do
-\usepackage{xcolor}
-\newcommand\todo[1]{\textcolor{red}{#1}}
-
- % change the arguments, as appropriate, in the following:
-\jmlrvolume{1}
-\jmlryear{2019}
-\jmlrworkshop{}
-
-% start article
-% \titlebreak
-% \footnote{}
-% \textsf
-
-\title[Conformal Prediction for Students' Grades]{Conformal Prediction for Students' Grades in a Course Recommender System}	%\titletag{\thanks{XXX}} % leave empty?
-
- % Use \Name{Author Name} to specify the name.
- % If the surname contains spaces, enclose the surname
- % in braces, e.g. \Name{John {Smith Jones}} similarly
- % if the name has a "von" part, e.g \Name{Jane {de Winter}}.
- % If the first letter in the forenames is a diacritic
- % enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
-
- % Authors with different addresses:
-  \author{\Name{Rapha\"{e}l Morsomme} \Email{raphael.morsomme@maastrichtuniversity.nl}\\ % Morsomme\nametag{\thanks{with a note}} % leave this slot empty?
-   \addr Zwingelput 4, 6211 KH Maastricht, the Netherlands	
-   \AND
-   \Name{Evgueni Smirnov} \Email{smirnov@maastrichtuniversity.nl}\\
-   \addr Bouillonstraat 10, 6211 LH Maastricht, the Netherlands}
-
- % Three or more authors with the same address:
- % \author{\Name{Author Name1} \Email{an1@sample.com}\\
- %  \Name{Author Name2} \Email{an2@sample.com}\\
- %  \Name{Author Name3} \Email{an3@sample.com}\\
- %  \addr Address}
-
- % Authors with different addresses:
- % \author{\Name{Author Name1} \Email{abc@sample.com}\\
- % \addr Address 1
- % \AND
- % \Name{Author Name2} \Email{xyz@sample.com}\\
- % \addr Address 2
- %}
-
-% leave editor's section empty?
-%\editor{Editor's name}
-% \editors{List of editors' names}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-Course selection can be challenging for student of Liberal Arts programs.
-In particular, due to the highly personalized curricula of liberal arts students, it is often difficult to assess whether or not a particular course is too advanced given their academic background.
-To assist students of the liberal arts program of the University College Maastricht, \citet{Morsomme.2019} developed a course recommender system that suggests courses whose content matches the student's academic interests, and issues warnings for courses that it deems too advanced.
-
-To issue warnings, the system produces point predictions for the grades that a student will receive in the courses that she/he is considering for the following term.
-Point predictions are estimated with regression models specific to each course which take into account the academic performance of the student along with the knowledge that she/he has acquired in previous courses.
-A warning is issued if the predicted grade is a fail.
-
-In this paper, we complement the system's point predictions for grades with prediction intervals constructed using the conformal prediction framework \citep{Vovk.2005}.
-We use the Inductive Confidence Machine (ICM) \citep{Papadopoulos.2002} with standardized nonconformity scores to construct prediction intervals that are tailored to each student.
-We find that the prediction intervals constructed with the ICM are valid and that their widths are related to the accuracy of the underlying regression model.
-\end{abstract}
-
-\begin{keywords} Conformal Prediction, Recommender System, Course Grade Prediction, Lasso, Education \end{keywords}
-
-% \todo{Rapha\"{e}l: make all figures black and white}
-
-% \todo{Rapha\"{e}l: make sure that all figures have the same font size as the main text}
-
-% \todo{Rapha\"{e}l: use notation Z_k = (x_k, y_k) to simplify description of conformal prediction}
-
-\section{Introduction}
-\label{sec:intro}
-
-Liberal Arts programs are often characterized by their open curriculum which allows student to tailor their own study program to their academic objectives \citep{Surpatean.2012, Morsomme.2019}.
-These highly personalized curricula make it difficult for students, academic advisors and course coordinators to assess whether the courses that a student considers taking the following term are too advanced given her/his current academic background or whether she/he has acquired the necessary skills, perhaps through an unusual combination of courses.
-To alleviate this problem, \citet{Morsomme.2019} developed the Liberal Arts Recommender System (LARS) which suggests to students courses whose content matches their academic interests.
-In addition, LARS helps student identify courses that are too advanced for them.
-To accomplish that, the system issues \textit{point predictions} for future grade based on the past academic performance of the student and the skills she/he has acquired in previous courses.
-A warning is issued when the predicted grade is a fail.
-
-In this paper, we present an application of conformal prediction \citep{Vovk.2005} to complement the current point estimates for future grades of LARS with prediction intervals.
-For students, the advantage of prediction intervals over point predictions is clear: their information position is improved, thereby enabling them to make better-informed course selection.
-To avoid the computational costs of transductive conformal prediction, we opt for the lighter Inductive Confidence Machine (ICM) \citep{Papadopoulos.2002}.
-Furthermore, in order to provide prediction intervals that are tailored to each student, we use a normalized nonconformity measure \citep{Papadopoulos.2011}.
-
-\sectionref{sec:related} presents previous research on grade prediction.
-\sectionref{sec:data} introduces the data and \sectionref{sec:crs} briefly describes the existing LARS.
-\sectionref{sec:prediction} presents the conformal prediction framework in which we construct the prediction intervals.
-\sectionref{sec:experiment} presents the setting and results of the experiment
-and \sectionref{sec:conclusion} concludes.
-
-\section{Related Work}
-\label{sec:related}
-
-The task of predicting students' course grades prediction has recently received a lot of attention \citep{Polyzou.2016, Houbraken.2017}.
-The approaches to this problem are regression approaches, classification approaches, and collaborative-filtering approaches.
-The first two approaches employ general information (secondary education, age, sex etc.), past performance, temporal elements, and contextual information of the students \citep{Bydzovska.2016}.
-They train a regression/classification model on historical data which is latter used for predicting students' course grades.
-The collaborative-filtering approaches require only past course grades for future prediction in contrast with the previous two approaches \citep{Sweeney.2015, Houbraken.2017}.
-They are divided into nearest-neighbor approaches \citep{Bydzovska.2015} and matrix-factorization approaches \citep{Polyzou.2016}.
-The nearest-neighbor approaches first identify neighbors of a student in terms of study performance and then predict the course grades for this student by aggregating the course grades of the neighbors.
-The matrix factorization approaches first decompose the student-course data into student and course matrices and then predict student course grades using the product of these matrices.
-
-Although the progress in  student course grade prediction is significant, no research was performed on the problem of estimating the confidence in this type of prediction.
-As it is stated above we propose to employ conformal prediction for this problem.
-Our choice is justified by the fact that other approaches for reliable prediction such as version spaces \citep{Smirnov.2004}, meta approaches \citep{Smirnov.2006, Smirnov.2006b}, ROC-isometric approaches \citep{Vanderlooy.2006} are
-inapplicable for regression tasks.
-
-\section{Data for LARS}
-\label{sec:data}
-
-\citet{Morsomme.2019} employed two sets of data to develop LARS: student data and course data.
-
-The student data consisted of anonymized course enrollment information.
-It included the transcripts of the 2,526 students of the liberal arts program between 2008 and 2019 with a total of 79,245 course enrollments.
-Course enrollments with a missing grade, which indicates that the student either dropped the course or fail the attendance requirement, were removed.
-\tableref{tab:student-data} presents an example of the student data.
-Each row contains an anonymized student ID, a course ID, a year and semester, and the obtained grade.
-
-The course data consisted of a corpus of the 490 course descriptions present in the 2018-2019 course catalogues of five departments of Maastricht University: European Studies, University College Maastricht, University College Venlo, Psychology and Science Program.
-These catalogues contain a one-page description of each course on offer.
-\tableref{tab:course-data} presents a sample of this textual data for the course \textit{HUM3034 World History} in the tidy format with one row per document-term \citep{Wickham.2014}.
-The data was processed following common procedures \citep{Meyer.2008}: individual terms were tokenized, stemmed with the Hunspell dictionary and common stop words were removed, as well as numbers between 1 and 1,000 and terms occurring less than 3 times in the corpus.
-
-\begin{table}[hbtp]
-	\floatconts
-	{tab:student-data}
-	{\caption{Example of student data}}	
-	{\begin{tabular}{ccccc}
-		\toprule
-		\bfseries Student ID &\bfseries Course ID &\bfseries Academic Year &\bfseries Period &\bfseries Grade\\
-		\midrule
-		44940 & CAP3000 & 2009-2010 & 4 & 8.8\\
-		37490 & SSC2037 & 2009-2010 & 4 & 8.4\\
-		71216 & HUM1003 & 2010-2011 & 4 & 6.8\\
-		44212 & SSC2049 & 2010-2011 & 2 & 8.4\\
-		85930 & SSC2043 & 2011-2012 & 1 & 4.3\\
-		\addlinespace
-		14492 & COR1004 & 2012-2013 & 2 & 8.5\\
-		34750 & HUM2049 & 2013-2014 & 5 & 6.0\\
-		32316 & SSC1001 & 2013-2014 & 1 & 8.5\\
-		22092 & SCI1009 & 2014-2015 & 1 & 6.4\\
-		19512 & COR1004 & 2016-2017 & 5 & 7.0\\
-		\bottomrule
-	\end{tabular}}	
-\end{table}
-
-\begin{table}[hbtp]
-	\floatconts
-	{tab:course-data}
-	{\caption{Example of course data for the course HUM3034 World History}}	
-	{\begin{tabular}{cccc}
-			\toprule
-			\bfseries Course ID &\bfseries Course Title &\bfseries Department &\bfseries Term\\
-			\midrule
-			HUM3034 & World History & UCM & understand\\
-			HUM3034 & World History & UCM & major\\
-			HUM3034 & World History & UCM & issue\\
-			HUM3034 & World History & UCM & episode\\
-			HUM3034 & World History & UCM & shape\\
-			\addlinespace
-			HUM3034 & World History & UCM & history\\
-			HUM3034 & World History & UCM & mankind\\
-			HUM3034 & World History & UCM & focus\\
-			HUM3034 & World History & UCM & theme\\
-			HUM3034 & World History & UCM & topic\\
-			\bottomrule
-	\end{tabular}}	
-\end{table}
-
-\section{LARS}
-\label{sec:crs}
-\subsection{Overview}
-\label{sec:overview}
-
-LARS is composed of two pillars: course suggestions and warning issuance (see \figureref{fig:flowchart}).
-
-In pillar 1, a topic model of the courses is fitted to the course data using the Latent Dirichlet Allocation model \citep{Blei.2003}.
-A topic model represents a topic as a mixture of words and a document as a mixture of topics.
-The key words selected by the student are then mapped to the vocabulary of the topic model to represent her/his academic interests.
-Finally, the system matches the student's academic interests to the content of the courses as represented by the topic model to identify courses of interest to the student.
-
-In pillar 2 for warning issuance, a model of each student is first created which contains information about the academic performance of the student (derived from the student data) and the expertise in specific topics (derived from the topic model) that she/he has acquired in previous courses.
-A regression model for point prediction of the grades that takes the student model as input is then fitted for each course.
-LARS uses these models to predict the grade that the student will obtain in the courses that she/he is considering for the following term and issues a warning when the predicted grade is a fail.
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:flowchart}
-	{\caption{Original LARS (black) and our contribution (red)}}
-	{\includegraphics[width=0.5\linewidth]{figures/flowchart}}
-\end{figure}
-
-\subsection{Pillar 1: Course Suggestion}
-
-\subsubsection{Topic Model of the Courses}
-\label{sec:tm}
-
-\citet{Morsomme.2019} fitted a topic model to the course data using the Latent Dirichlet Allocation generative model \citep{Blei.2003} and the Gibbs sampling algorithm \citep{Phan.2008}.
-The LDA conceptualizes topics as a probability distribution over the vocabulary of the corpus, and document as a set of words, each drawn from a probability distribution over topics specific to that document.
-The term \textit{Dirichlet} comes from the fact that the word distribution $\beta_{t}$ of topic $t$ is generated from a Dirichlet distribution $\beta_{t} \sim Dirichlet(\delta)$ and the topic distribution $\theta_{d}$ for document $d$ is generated from a Dirichlet distribution $\theta_{d} \sim Dirichlet(\alpha)$ where $\delta$ and $\alpha$ act as hyper-parameters determining how concentrated the distributions of words in topics and the distributions of topics in documents are.
-
-The authors of LARS followed \citet{Phan.2008} who use a Gibbs sampler to learn the distributions $\beta$ and $\theta$ of each topic and document, and \citet{Griffiths.2004} who select the number of topics yielding the best model with respect to the log-likelihood.
-The selected topic model contains 65 topics (see \figureref{fig:ll}) and consists of a term distribution for each topic indicating the importance of each term of the corpus in the topic and a topic distribution for each course indicating the importance of each topic in the course.
-\figureref{fig:gamma} shows the main topics of the core course \textit{COR1004 Political Philosophy} and \figureref{fig:beta} presents the terms that characterize topic 4 and topic 19, the main two topics of the course.
-We can see that the topics are easy to interpret and that the content of the course, that is, its topic distribution, corresponds to what we would expect from a course on political philosophy.
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:ll}
-	{\caption{Maximum likelihood model selection: the model with 65 topics is selected.}}
-	{\includegraphics[width=0.5\linewidth]{figures/model-selection}}
-\end{figure}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:gamma}
-	{\caption{Topic distribution in the course COR1004 Political Philosophy.}}
-	{\includegraphics[width=0.5\linewidth]{figures/gamma-COR1004}}
-\end{figure}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:beta}
-	{\caption{Word distribution in the main two topics of COR1004 Political Philosophy. Topic 4 corresponds to international politics and Topic 19 to philosophy.}}
-	{\includegraphics[width=0.75\linewidth]{figures/beta}}
-\end{figure}
-
-\subsubsection{Model of a Student's Academic Interests}
-
-\citet{Morsomme.2019} employed the topic model to estimate the academic interests of a student from the key words that she/he enters into the system.
-The student's academic interest $AI_t$ in topic $t$ simply corresponds to the sum of the selected key words' importance in topic $t$ as determined by the topic model, that is,
-$$ AI_t = \sum_{i \in I^*} \beta_{t,i}, \;\;\;  \mbox{for} \;\;\;  t=1, \cdots, n,$$
-where $I^*$ is the set of key words selected by the student, $\beta_{t,i}$ corresponds to the importance of term $i$ in topic $t$ and $n$ is the number of topics present in the model (in this case $n=65$).
-The vector $AI = (AI_1, \cdots, AI_{n})^T$ therefore represents the academic interests of the student.
-
-\subsubsection{Course Matching and Suggestion}
-
-LARS uses the Kullback-Leibler (KL) divergence \citep{Kullback.1951} to identify the courses whose content best matche the academic interests of the student.
-Letting $P$ and $Q$ be two discrete probability distribution defined on the same probability space, the KL divergence between $P$ and $Q$ is defined as
-
-$$ D_{\mathrm{KL}} \left( P || Q \right) =  - \sum_{x \in X} P(x) \log\left(\dfrac{Q(x)}{P(x)}\right)$$
-
-\noindent and measures how different the probability distribution $P$ is from the reference probability distribution $Q$.
-LARS suggests to the students the $n$ courses whose topic distribution $\theta$ has the smallest KL divergence to her/his normalized academic interests $AI^* = \dfrac{AI}{\lvert AI \rvert}$.
-
-\subsection{Pillar 2: Warning Issuance}
-\subsubsection{Student Model}
-\label{sec:sm}
-The student model consists of two elements: academic performance and topic-specific expertise.
-Academic performance corresponds to the student's general GPA (grade point average) as well as her/his GPA in humanities, natural sciences, social sciences, skills and projects.
-These are derived from the students' transcripts in a straightforward way.
-Topic-specific expertise corresponds to the amount of knowledge that the student has acquired  in previous courses in each of the topics present in the topic model.
-\citet{Morsomme.2019}  posited that, when students take a course, they acquire knowledge about its content and that the amount of knowledge that they acquire is proportional to the obtained grade; that is, they assume that students who obtain 10/10 in a course acquire all the knowledge related to its content while those who obtain 5/10 only acquire half of it.
-The content of a course is determined by its topic distribution in the topic model and the grades are retrieved from the student's transcript.
-Furthermore, they assume that the knowledge acquired in different courses simply accumulates.
-Hence, if a student has taken $n$ courses and $g_{i}$ corresponds to her/his grade in course $i$, for $i = 1, \cdots, n$, then her/his expertise $exp_t$ in topic $t$ corresponds to
-
-\begin{equation}
-\label{eq:expertise}
-exp_t = \sum_{i= 1}^{n} g_i \theta_{i,t}
-\end{equation}
-
-\noindent where $\theta_{i,t}$ corresponds to the importance of topic $t$ in course $i$ as determined by the topic model.
-\tableref{tab:toy} and \figureref{fig:toy-expertise} present a toy example of the contribution of three individual courses toward a student's expertise in five topics.
-\tableref{tab:toy-gamma} and \tableref{tab:toy-grade} respectively show the topic distribution in each course as estimated by some topic model and the grades obtained by the student which are retrieved from her/his transcript.
-\tableref{tab:toy-contribution} uses \equationref{eq:expertise} to estimate the contribution of each course toward the student's topic expertise.
-\figureref{fig:toy-expertise} offers a graphical illustration of \tableref{tab:toy-contribution}.
-
-\begin{table}[htbp]
-	\floatconts
-	{tab:toy}
-	{\caption{Toy example of the contribution of individual courses toward a student's topic expertise.}}
-	{%
-		\subtable[Topic distribution $\theta$]{%
-			\label{tab:toy-gamma}%
-			\begin{tabular}{cccccc}
-				\toprule
-				\bfseries Course & \bfseries Topic 1 & \bfseries Topic 2 & \bfseries Topic 3 & \bfseries Topic 4 & \bfseries Topic 5\\
-				\midrule
-				Course 1 & 0.0 & 0.7 & 0.2 & 0.1 & 0.0\\
-				Course 2 & 0.2 & 0.2 & 0.2 & 0.2 & 0.2\\
-				Course 3 & 0.0 & 0.4 & 0.2 & 0.1 & 0.2\\
-				\bottomrule
-			\end{tabular}
-		}\qquad
-		\subtable[Transcript]{%
-			\label{tab:toy-grade}%
-			\begin{tabular}{cc}
-				\toprule
-				\bfseries Course & \bfseries Grade\\
-				\midrule
-				Course 1 & 6/10\\
-				Course 2 & 9/10\\
-				Course 3 & 2/10\\
-				\bottomrule
-			\end{tabular}
-		}\qquad
-			\subtable[Course contribution toward a student's topic expertise]{%
-			\label{tab:toy-contribution}%
-			\begin{tabular}{cccccc}
-				\toprule
-				\bfseries Course & \bfseries Topic 1 & \bfseries Topic 2 & \bfseries Topic 3 & \bfseries Topic 4 & \bfseries Topic 5\\
-				\midrule
-				Course 1 & 0.00 & 0.42 & 0.12 & 0.06 & 0.00\\
-				Course 2 & 0.18 & 0.18 & 0.18 & 0.18 & 0.18\\
-				Course 3 & 0.00 & 0.08 & 0.04 & 0.02 & 0.04\\
-				\midrule
-				\bfseries Total & 0.18 & 0.68 & 0.34 & 0.26 & 0.22\\
-				\bottomrule
-			\end{tabular}
-		}
-	}
-\end{table}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:toy-expertise}
-	{\caption{Toy example of the contribution of individual courses toward a student's topic expertise.}}
-	{\includegraphics[width=0.5\linewidth]{figures/toy-expertise}}
-\end{figure}
-
-\subsubsection{Point Prediction for Grade and Warning Issuance}
-
-To issue warnings, LARS produces point estimates for future grades.
-To accomplish this, it uses regression models.
-LARS separately fits a sparse linear regression model for grade prediction to each of the 132 courses currently offered at the University College Maastricht with at least 20 student enrollments since 2008.
-The input to the models consists of the 71 variables stored in the student model: 6 GPAs (1 general and 5 discipline-specific) and the level of expertise in the 65 topics of the topic model.
-The regression models output a point estimate for the grade.
-Note that each model is trained only on the data of the students enrolled in the associated course.
-Since the number of predictors is relatively large, the models are regularized with the Lasso penalty \citep{Tibshirani.1996} and the value of the Lasso tuning parameter $\lambda$ is chosen via cross-validation (CV).
-\figureref{fig:cv-mae} shows the distribution of the CV mean absolute error (mae) for the 132 prediction models.
-The model for the course \textit{PRO2004 Academic Debate} has the smallest prediction error (0.38 grade point) and the model for \textit{SCI3006 Mathematical Modelling} the largest (1.80 grade point).
-The mean CV mae weighted by the number of students enrolled in the course is 0.78, the median is 0.78 and the standard deviation is 0.28.
-
-% use cross-validation to find the value of the Lasso tuning parameter $lambda$ that minimizes the CV mean absolute error (mae), a more robust loss function than the squared absolute error \citep{Hastie.2009}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:cv-mae}
-	{\caption{Distribution of cross-validation error}}
-	{\includegraphics[width=0.5\linewidth]{figures/cv-mae}}
-\end{figure}
-
-In practice, the student selects the courses that she/he is considering for the following term and the system uses the regression models of these courses to provide point predictions for the future grades.
-A warning is issued when a predicted grade is a fail.
-
-We desire the following three requirements for pillar 2 Warning Issuance of LARS: accuracy, sparsity and transparency of the regression models for grade prediction.
-First, the grade predictions must be accurate so that students base their course selection on sound information.
-Second, we want the regression models to be sparse so that we can identify which topics are important to master in order to perform well in a given course.
-Such information would be extremely useful to course coordinators and curriculum managers alike.
-Third, in order to be transparent, grade predictions must be accompanied by an indication of their own accuracy.
-The first two requirements are fulfilled by the Lasso model \citep{Tibshirani.1996}, but the third requirement is not satisfied by LARS's current \textit{point predictions} for future grades.
-To fulfill the requirement for transparency, we propose to complement the existing point predictions of the system with \textit{prediction intervals}.
-In the following section, we use the conformal prediction framework to build prediction intervals for future grades that are tailored to each student.
-
-\section{Regression with Prediction Interval}
-\label{sec:prediction}
-
-Let $X$ be a space given by $n$ input variables $X_j$ ($j \in \{1, 2, \ldots, n\}$) and $Y$ be an output real-value variable.
-Any $i$-th instance in the labeled space  $(X \times Y)$ is given as a tuple $(x_i, y_i)$ where $x_i$ belongs to $X$, $x_{ij}$ is the value for the input variable $X_j$ for the instance $x_i$, and $y_i$ is the value for the output variable $Y$.
-We assume the existence of an unknown  probability distribution $P$ over $X \times Y$.
-A data set $D$ is a multi-set of $m$ instances $(x_i, y_{i}) \in (X \times Y)$ drawn from the probability distribution $P$ under the randomness assumption.
-Given an unlabeled test  instance $x_{m+1} \in X$,  the regression  task  is to find an estimate $\hat{y}_{m+1} \in \mathbb{R}$ of the value of the variable $Y$ for the instance $x_{m+1}$ according to the probability distribution $P$.
-A  prediction interval $\Gamma^\epsilon$ for the test instance $x_{m+1}$ is defined as the set $\{ y \in \mathbb{R}| p(y) > \epsilon\}$ that contains the true value of the output variable $Y$ for $x_{m+1}$ with probability of at least $1- \epsilon$, where $\epsilon$ is a given significance level.
-
-\subsection{Underlying Algorithm: Lasso Regression}
-\label{sec:lasso}
-
-Lasso is a parametric method for regression that allows regularization and variable selection \citep{Tibshirani.1996}.
-The method estimates the coefficients of the final regression model by minimizing:
-
-\[ \sum_{i = 1}^{m} ( y_i - \beta_0 - \sum_{j = 1}^{n} \beta_j x_{ij})^2 + \lambda \sum_{j = 1}^{n}\lvert\beta_j\rvert, \]
-
-\noindent i.e., by minimizing the  residual sum of the squares $\sum_{i = 1}^{m} ( y_i - \beta_0 - \sum_{j = 1}^{n} \beta_j x_{ij})^2$ and the Lasso penalty $\lambda \sum_{j = 1}^{n}\lvert\beta_j\rvert$.
-
-The Lasso method shrinks the coefficient estimates $\hat{\beta}_j$ toward 0.
-This reduces the variance of the model and thereby helps preserve its prediction accuracy.
-Furthermore, in contrast to the ridge regression penalty, the absolute-value constraint of Lasso encourages some of the coefficient estimates to be exactly zero and hence the regression model to be sparse.
-This facilitates the interpretation of the obtained models.
-
-\subsection{Conformal Prediction and the Inductive Conformal Machine}
-\label{sec:cp}
-
-The conformal prediction framework was proposed by \citet{Vovk.2005}.
-It allows the construction of  prediction intervals for regression tasks in the presence of finite data sets generated under the exchangeability assumption (which is weaker than the randomness assumption).
-In general, conformal predictors are conservatively valid; that is, the probability that any prediction interval $\Gamma^\epsilon$ does not contain the true value is not greater than $1 - \epsilon$.
-
-The conformal prediction framework assumes a nonconformity function $A$.
-The function outputs a nonconformity score $\alpha_k \in \mathbb{R}^+ \cup \{+\infty\}$ for any instance $(x_{k},y_{k})$ that indicates how unusual that instance is for the data set $D \cup \{(x_{m+1},y_{m+1})\}$.
-For the regression setting, a popular choice for the nonconformity score $\alpha_k$ of an instance $(x_{k},y_{k})$ is the residual $|y_k - \hat{y}_k|$, where $\hat{y}_k$ is the estimation for the variable $Y$ for the instance $x_k$ provided by some underlying regression model based on the data set $D \cup \{(x_{m+1}, y_{m+1})\}$ \citep{Papadopoulos.2002, Papadopoulos.2015}.
-In this paper we employ a normalized nonconformity score for the instance  $(x_{k},y_{k})$ corresponding to
-
-\begin{equation}
-\label{eq:norm}
-\alpha_k = \frac{\lvert y_k - \hat{y}_k\rvert}{\exp(\mu_k)}
-\end{equation}
-
-\noindent where $\mu_k$ is the prediction of the value $\ln \lvert y_k - \hat{y}_k \rvert$ from a second regression model \citep{Papadopoulos.2011}.
-The intuition behind equation (\equationref{eq:norm}) is that by taking into account the expected accuracy of the underlying regression model, we do not inflate the nonconformity score of instances that are intrinsically difficult to predict.
-
-Once the nonconformity scores have been computed for all the instances in the data set  $D \cup \{(x_{m+1},y_{m+1})\}$, the $p$-value $p_{m+1}$ for the output value  $y_{m+1}$ for the instance $x_{m+1}$ corresponds to the proportion of instances in $D \cup \{(x_{m+1},y_{m+1})\}$ whose nonconformity score is greater than or equal to that of the instance $(x_{m+1},y_{m+1})$; i.e.
-
-\begin{equation}
-\label{eq:p}
-p_{m+1} = \frac{\#\{i= 1,...,m|\alpha_i \geq \alpha_{m+1}\} }{m+1}.
-\end{equation}
-
-Depending on the validation procedure for estimating the nonconformity scores, there exist two approaches to generate valid conformal predictors.
-First, the \textit{transductive conformal predictors} (TCP) proposed by \citet{Saunders.1999} uses \textit{leave-one-out} cross-validation and is computationally expensive.
-To reduce the computational burden, the \textit{inductive conformal machine} (ICM) was proposed by \citet{Papadopoulos.2002}.
-It employs the hold-out method: the data $D$ is partitioned into a proper training set $D_t$ of size $p$ and a proper calibration set $D_c$ of size $q$ ($D = D_t \cup D_c$ and $m = p + q$).
-The proper training set $D_t$ is used to learn the nonconformity function $A$.
-The function is learned by training two regression models: the \textit{target} model and the \textit{error} model.
-The target model estimates the values $y_k$ which we need to estimate the residuals $\lvert y_k - \hat{y}_k\rvert$.
-The error model estimates the accuracy $\mu_k = \ln \lvert y_k - \hat{y_k} \rvert$ of the target model (see \equationref{eq:norm}).
-The use of the natural logarithm and exponent prevents the estimated residuals -- and hence the nonconformity scores -- to be negative.
-The regression models are then applied to the instances of the calibration set $D_c$ to compute their nonconformity scores $\alpha$.
-
-Once the nonconformity scores have been computed for the instances of the calibration set $D_c$, the $p$-value $p_{m+1}$ for the output value $y_{m+1}$ for the instance $x_{m+1}$ corresponds to the proportion of instances in $D_c$ whose nonconformity score is greater than or equal to that of the instance $(x_{m+1},y_{m+1})$; i.e.
-
-\begin{equation}
-\label{eq:e3}
-p_{m+1} = \frac{\#\{i= p+1,...,m|\alpha_i \geq \alpha_{m+1}\} }{m - p +1}. 
-\end{equation}
-
-The nonconformity scores of the calibration instances can be used for constructing a prediction interval for the test instance $x_{m+1}$.
-To accomplish this, the nonconformity scores are sorted in increasing order of magnitude: $ \alpha_{(1)}, \alpha_{(2)}, \ldots, \alpha_{(q)}$.
-The prediction interval for the test instance $x_{m+1}$ is constructed as:
-
-\begin{equation}
-\label{eq:e4}
-(\hat{y}_{m+1} - \alpha_{(s)} , \hat{y}_{m+1} + \alpha_{(s)})
-\end{equation}
-
-\noindent where  $\hat{y}_{m+1} $  is the value of the variable $Y$ for the instance $x_{m+1}$ estimated by the target regression model trained on the proper training set $D_t$, $s = \lfloor \epsilon (|q|+1) \rfloor$, and $\epsilon$ is a given significance level \citep{Papadopoulos.2011}.
-We note that the construction of prediction intervals is model-independent: prediction intervals can be constructed for any type of regression model.
-
-\section{Experiments}
-\label{sec:experiment}
-
-\subsection{Settings}
-
-We separately build a regression model for grade prediction for each of the 132 courses currently offered at the University College Maastricht with more than 20 student enrollments since 2008.
-To build these models, we use an ICM with normalized nonconformity scores.
-For each model, the data consists of the  models of the students enrolled in the associated course.
-A student model data consists of the 6 GPAs (1 general and 5 discipline-specific) of a student along with her/his level of expertise in the 65 topics of the topic model at the beginning of the course (see \sectionref{sec:sm}).
-
-We choose the target model to be a lasso-penalized linear regression model because it fulfills the requirements for accuracy and sparsity.
-We also choose the error model to be a lasso regression.
-We first fit the target model on the proper training set (66\% of the data) to estimate grades.
-We then fit the error model on the proper training set too to estimate the accuracy of the target model.
-Note that both models learn the lasso tuning parameter $\lambda$ with an internal 10-fold cross-validation on the proper training set.
-Finally, using \equationref{eq:e3,eq:e4}, we construct prediction intervals for each test instance  at several significance levels and evaluate their validity and tightness.
-We report the final results for an external 10-fold cross-validation.
-
-\subsection{Results}
-
-We present the results for a selection of six courses which cover a wide range of sample size and of cross-validation mean absolute error (CV mae) for the target model (see \tableref{tab:conformal-course}).
-\textit{SSC3044 Culture, Politics and Society in Contemporary Asia} and \textit{SSC3038 Contemporary Sociological Theory} have a small CV mae ($\le0.4$ point grade), while \textit{SCI2010 Introduction to Game Theory} and \textit{SCI2018 Calculus} have a large CV mae ($\ge1.4$).
-Since they are mandatory, the courses \textit{COR1004 Political Philosophy} and \textit{COR1002 Philosophy of Science} have a large sample size ($n\ge1900$), while \textit{SSC3044 Culture, Politics and Society in Contemporary Asia} and \textit{SCI2018 Calculus} have a much fewer observations ($n\le200$).
-
-\begin{table}[hbtp]
-	\floatconts
-	{tab:conformal-course}
-	{\caption{Selected courses for conformal prediction}}	
-	{\begin{tabular}{ccccc}
-			\toprule
-			\bfseries Course &\bfseries Sample Size &\bfseries CV mae \\
-			\midrule
-			SSC3044 & 136  & 0.38\\
-			SSC3038 & 272  & 0.40\\
-			COR1004 & 1998 & 0.67\\
-			COR1002 & 2067 & 1.00\\
-			SCI2010 & 417  & 1.41\\
-			SCI2018 & 198  & 1.62\\
-			\bottomrule
-	\end{tabular}}	
-\end{table}
-
-\tableref{tab:conformal-summary} and \figureref{fig:conformal-error} present the error rate of the prediction intervals constructed with the ICM at different significance levels for each course, that is, the proportion of intervals that do not contain the true grade of the student.
-We see that the prediction intervals are conservatively valid; that is, given a significance level, the probability that a prediction interval does not contain the true value is not greater than the significance level.
-
-\figureref{fig:conformal-width} shows the distribution of prediction interval width across different significance levels for each course.
-The dots correspond to the median of the distributions and the bars to the 10th and 90th percentiles.
-The width $1$ is highlighted for reference.
-We observe that the width varies across courses.
-The ICM produces relatively narrow intervals for the course COR1004, SSC3038 and SSC3044 which tend to be less than 1 unit wide for most levels of significance.
-But for SCI2010 and SCI2018, the interval become wide very quickly: they are wider than 1 unit at significance levels as large as $0.5$.
-In fact, the prediction interval width seems to be associated with the CV mae: courses with a small CV mae, such as SSC3044, SSC3038 and COR1004, have relatively tight intervals while those with a large CV mae, such as SCI2010 and SCI2018, have wide intervals.
-
-\begin{table}[hbtp]
-	\floatconts
-	{tab:conformal-summary}
-	{\caption{Prediction interval tightness and empirical validity of the ICM.}}	
-	{\begin{tabular}{cccccccccc}
-			\toprule
-			\multirow{2}{*}{\bfseries Course} & \multicolumn{3}{c}{\bfseries Median Width} & \multicolumn{3}{c}{\bfseries Error Rate}\\
-			& \bfseries 0.05 & \bfseries 0.1 & \bfseries 0.2 & \bfseries 0.05 & \bfseries 0.1 & \bfseries 0.2\\
-			\midrule
-			COR1002 & 2.39 & 1.93 & 1.46 & 0.05 & 0.10 & 0.20\\
-			COR1004 & 1.63 & 1.29 & 1.01 & 0.05 & 0.10 & 0.19\\
-			SCI2010 & 3.69 & 2.86 & 2.18 & 0.05 & 0.12 & 0.22\\
-			SCI2018 & 4.68 & 4.02 & 3.05 & 0.04 & 0.08 & 0.17\\
-			SSC3038 & \bfseries 0.91 & \bfseries 0.72 & \bfseries 0.50 & 0.07 & 0.14 & 0.23\\
-			SSC3044 & 1.02 & 0.84 & 0.63 & 0.04 & 0.07 & 0.12\\
-			\bottomrule
-	\end{tabular}}	
-\end{table}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:conformal-error}
-	{\caption{Empirical validity of the ICM}}
-	{\includegraphics[width=0.8\linewidth]{figures/conformal-error}}
-\end{figure}
-
-\begin{figure}[htbp]
-	\floatconts
-	{fig:conformal-width}
-	{\caption{Tightness of prediction interval constructed with the ICM. The dots correspond to the median width and the bars to the 10th and 90th percentiles.}}
-	{\includegraphics[width=0.8\linewidth]{figures/conformal-width}}
-\end{figure}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this paper, we complemented LARS's point predictions for course grades with prediction intervals constructed using the conformal prediction framework.
-We used the ICM with a standardized nonconformity score to construct prediction intervals that are tailored to each student.
-The results from a selection of 6 courses covering a wide range of sample size and CV mae of the underlying model indicate that the prediction intervals are conservatively valid and that their width seems to be associated with the accuracy of the underlying model.
-The courses SSC3038 and SSC3044, for example, have the tighter intervals with a median width close to 1 unit at the significance level $0.05$.
-This result shows that ICM can construct prediciton intervals that are useful for LARS and its pillar 2 for warning issuance.
-
-Yet, courses whose underlying model lacks accuracy end up with prediction intervals that are too wide to be useful.
-To make the intervals tighter, we will consider two approaches in our future research.
-First, we will try to improve the performance of the underlying regression model by considering methods that tend to be more accurate than Lasso regression, such as random forests or gradient boosting.
-Second, we will improve the informational efficiency of the ICM with cross-conformal prediction \citep{Vovk.2015} or its faster version \citep{Beganovic.2018}.
-
-\acks{Our thanks to the University College Maastricht, Maastricht University, the Institute of Data Science, the Department of Data Science and Knowledge Engineering, and in particular to Peter Vermeer for initiating the project and enabling collaboration with the University College Maastricht.}
-
-\bibliography{bibliography}
-
-\end{document}
+version https://git-lfs.github.com/spec/v1
+oid sha256:2433448a17d2e226d09ca4e30b2aff49952f1cde0390349985ba7fb08dceb964
+size 38682

### 2019-06-27 Conference/COPA2019/paper/conference figures COPA2019.Rmd
no message

@@
 
-```{r student_data}
+# Student data
+
+```{r fig_student_data}
 set.seed(2019)
@@
 
-  arrange(`Academic Year`) %>%
+  arrange(`Academic Year`)
 
-  print
-```
-
-```{r course_data}
-course_data <- d_text$catalogues %>%
-
-  slice(50005:50014) %>%
-
-  select(`Course ID`, `Course Title`, Department = department, word) %>%
-
-  print
-```
-
-# Student data
-
-```{r fig_student_data}
 student_data %>% latex_table("data-student")
@@
 ```{r fig_course_data}
+course_data <- d_text$catalogues %>%
+
+  slice(50005:50014) %>%
+
+  select(`Course ID`, `Course Title`, Department = department, word)
+
 course_data %>% latex_table("course-student")
@@
 
+```{r}
+plot_width <- 8
+plot_height <- plot_width / 1.6 
+```
+
 ## course table
@@
 
+## Error
+
+```{r}
+d_error <- conformal_results %>%
+  group_by(course, significance, underl_algo) %>%
+  summarise(error = mean(!hit))
+```
+
+```{r}
+d_error %>%
+  ggplot(aes(x = significance, y = error, col = underl_algo)) +
+  geom_abline(slope = 1, linetype = "longdash") +
+  geom_line(aes(group = underl_algo)) +
+  geom_point() +
+  facet_wrap( ~ course) +
+  labs(y = "Error Rate", x = "Significance Level") +
+  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8)) +
+  scale_color_discrete(name = "Underlying Algorithm", labels = c("Boosting", "Lasso","Random Forest"))
+
+ggsave(filename = "conformal-error.jpeg", path = output_folder,
+       width = plot_width, height = plot_height)
+```
+
 ## width
@@
 d_width <- conformal_results %>%
-  group_by(course, significance) %>%
-  summarise(q_50 = quantile(width, 0.5), # median
-            q_10 = quantile(width, 0.1),
-            q_90 = quantile(width, 0.9))
+  group_by(course, significance, underl_algo) %>%
+  summarise(q_50 = quantile(width_corrected, 0.5), # median
+            q_10 = quantile(width_corrected, 0.1),
+            q_90 = quantile(width_corrected, 0.9))
 ```
@@
 ```{r}
+dodge_width <- 0.04
+
 d_width %>%
-  ggplot() +
-  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5) +
+  ggplot(aes(col = underl_algo)) +
+  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5, position = position_dodge(width = dodge_width)) +
   geom_hline(yintercept = 1, linetype = "dashed") +
-  geom_line(aes(significance, q_50, group = 1)) +
-  geom_point(aes(significance, q_50)) +
+  geom_line(aes(significance, q_50, col = underl_algo), position = position_dodge(width = dodge_width), linetype = 2) +
+  geom_point(aes(significance, q_50), position = position_dodge(width = dodge_width)) +
   facet_wrap( ~ course) +
-  labs(y = "Width",
-       x = "Significance Level") +
-  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
+  labs(y = "Width", x = "Significance Level") +
+  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8)) +
+  scale_color_discrete(name = "Underlying Algorithm", labels = c("Boosting", "Lasso","Random Forest"))
 
@@
 
-## Error
-
 ```{r}
-d_error <- conformal_results %>%
-  group_by(course, significance) %>%
-  summarise(error = mean(!hit))
-```
-
-```{r}
-d_error %>%
-  ggplot(aes(x = significance, y = error)) +
-  geom_abline(slope = 1, linetype = "longdash") +
-  geom_line(aes(group = 1)) +
-  geom_point() +
-  facet_wrap( ~ course) +
-  labs(y = "Error Rate",
-       x = "Significance Level") +
-  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
-
-ggsave(filename = "conformal-error.jpeg", path = output_folder,
-       width = plot_width, height = plot_height)
+conformal_results %>%
+  ggplot() +
+  geom_boxplot(aes(significance, width_corrected, group = significance, col = underl_algo)) +
+  facet_wrap(~course)
 ```
@@
 conformal_results %>%
-  filter(significance < 0.2) %>%
-  group_by(course, significance) %>%
-  summarize(width_med  = median(width),
+  filter(significance <= 0.2) %>%
+  group_by(course, significance, underl_algo) %>%
+  summarize(width_med  = median(width_corrected),
             error_rate = mean(!hit)) %>%
-
   gather(key = "measure", value = "output", width_med, error_rate) %>%
   mutate(output = round(output, 2)) %>%
-  unite(id, measure, significance, sep = "-") %>%
-  spread(key = id, value = output) %>%
+#  unite(col = "ID", underl_algo, measure, sep = " ") %>%
+  unite(col = ID, measure, significance, underl_algo, sep = "-") %>%
+  spread(key = ID, value = output) %>%
 

### 2019-06-27 Data Preparation - Student Data.Rmd
no message

--- 2019-06-05 Data Preparation - Student Data.Rmd
@@
 ```{r}
-d_transcript <- d_transcript %>% filter(!is.na(Grade))
+d_transcript <- d_transcript %>%
+  filter(!is.na(Grade))
 ```
@@
   left_join(select(d_course, - Period), by = c("Course ID"))
+```
+
+## Censored data for Research Project
+
+```{r}
+student_ID <- d_transcript_augmented %>% distinct(`Student ID`)
+randomID <- sample(1 : nrow(student_ID))
+student_ID_random <- student_ID %>% mutate(Student_ID_random = randomID)
+
+d_transcript_censored <- d_transcript_augmented %>%
+  left_join(student_ID_random, by = "Student ID") %>%
+  select(Student_ID_random, Course_ID = `Course ID`, time, Concentration, Cluster,
+         Academic_year = `Academic Year`, Period = period_numerical) %>%
+  sample_frac(1, replace = FALSE)
+
+d_transcript_censored
+
+write_csv(d_transcript_censored, path = "Output/d_transcript_censored.csv")
 ```

### 2019-06-27 Warning Issuance - Conformal Prediction.Rmd
no message

@@
 ```{r setup, include = FALSE}
+time0 <- Sys.time()
+
 set.seed(1)
@@
 library(glmnet)
+library(randomForest)
+library(xgboost)
 
@@
 
-  student_profile %>%
+  student_model %>%
     filter(`Course ID` == course) %>%
@@
 ```{r,lasso helper}
-fit_target_model <- function(df){
+fit_target_model <- function(df, underlying_algorithm = underlying_algo){
 
-  X <- df %>% select(matches("GPA|Topic"))
+  X <- df %>% select(matches("GPA|Topic")) %>% as.matrix
   Y <- df %>% pull(Y)
 
-  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default. Use mean absolute error
+  if(underlying_algorithm == "lasso"){
+    cv.glmnet(x = X, y = Y,
+              type.measure = "mae") # lasso by default. Use mean absolute error
+
+  }else if(underlying_algorithm == "randomforest"){
+    randomForest(x = X, y = Y,
+                 ntree = 1000,
+                 mtry = floor(ncol(X)/3),
+                 nodesize = 5)
+
+  }else if(underlying_algorithm == "boost"){
+    xgboost(data = X, label = Y,
+            max_depth = 2, eta = .3, nrounds = 1000,
+            objective = "reg:linear", verbose = 0)
+
+  }else{stop("Unknown algorithm")}
 
@@
 
-predict_grade <- function(df, model){
+predict_grade <- function(df, model, underlying_algorithm = underlying_algo){
 
-  X <- df %>% select(matches("GPA|Topic"))
+  X <- df %>% select(matches("GPA|Topic")) %>% as.matrix
 
-  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min") # use lambda that minimizes mae
+  if(underlying_algorithm == "lasso"){
+    Y_hat <- predict.cv.glmnet(model, newx = X, s = "lambda.min") # use lambda that minimizes mae
+
+  }else if(underlying_algorithm == "randomforest"){
+    Y_hat <- predict(model, X)
+
+  }else if(underlying_algorithm == "boost"){
+    Y_hat <- predict(model, X)
+
+  }else{stop("Unknown algorithm")}
 
@@
 
-fit_error_model <- function(df){
+fit_error_model <- function(df, underlying_algorithm = underlying_algo){
 
-  X  <- df %>% select(matches("GPA|Topic"))
+  X  <- df %>% select(matches("GPA|Topic")) %>% as.matrix
   mu <- df %>% pull(mu)
 
-  cv.glmnet(x = as.matrix(X), y = mu, type.measure = "mae")
+  if(underlying_algorithm == "lasso"){
+    cv.glmnet(x = X, y = mu, type.measure = "mae")
+
+  }else if(underlying_algorithm == "randomforest"){
+    randomForest(x = X, y = mu,
+                 ntree = 1000,
+                 mtry = floor(ncol(X)/3),
+                 nodesize = 5)
+
+  }else if(underlying_algorithm == "boost"){
+    xgboost(data = X, label = mu,
+            max_depth = 2, eta = .3, nrounds = 1000,
+            objective = "reg:linear", verbose = 0)
+
+  }else{stop("Unknown algorithm")}
 
@@
 
-predict_error <- function(df, model){
+predict_error <- function(df, model, underlying_algorithm = underlying_algo){
 
-  X <- df %>% select(matches("GPA|Topic"))
+  X <- df %>% select(matches("GPA|Topic")) %>% as.matrix
 
-  mu_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")
+  if(underlying_algorithm == "lasso"){
+    mu_hat <- predict.cv.glmnet(model, newx = X, s = "lambda.min")
+
+  }else if(underlying_algorithm == "randomforest"){
+    mu_hat <- predict(model, X)
+
+  }else if(underlying_algorithm == "boost"){
+    mu_hat <- predict(model, X)
+
+  }else{stop("Unknown algorithm")}
 
@@
 ```{r}
-
 compute_ncs              <- function(df) df %>% mutate(alpha = abs(Y - Y_hat))
@@
 compute_standardized_ncs <- function(df) df %>% mutate(sigma = exp(mu_hat),
-                                                       alpha = abs(Y - Y_hat) / sigma )
+                                                       sigma_corrected = sigma + gamma,
+                                                       alpha = abs(Y - Y_hat) / sigma_corrected )
 
@@
 
-  max(df$alpha) + 0.00001
+  max(df$alpha) + 1e-5
 
@@
     sigma = exp(mu_hat),
-    width       = ncs * sigma,
+    sigma_corrected = sigma + gamma,
+    width           = ncs * sigma_corrected,
     border_low      = Y_hat - width,
@@
 
+correct_interval <- function(df){
+
+  df %>% mutate( # constraint prediction interval to [0, 10] 
+    border_low_corrected  = pmax(0 , border_low),
+    border_high_corrected = pmin(10, border_high),
+    width_corrected       = border_high_corrected - border_low_corrected)
+
+}
+
 compute_hit <- function(df){
-  df %>% mutate(hit = (border_low <= Y) & (Y <= border_high))
+  df %>% mutate(hit = (border_low_corrected <= Y) & (Y <= border_high_corrected))
 }
@@
 
-significance <- c(0.01, 0.05, seq(0.1, 0.9, 0.1))
+set.seed(1)
+significance <- c(0.05, seq(0.1, 0.9, 0.1))
 results <- list()
 n_list <- 1
+underlying_algos <- c("boost", "lasso", "randomforest")
+gamma <- 2
 
-# course <- "SSC3044"; iteration <- 1; signi <- 0.1
+# course <- "SSC3044"; iteration <- 1; signi <- 0.1; underlying_algo =
 
@@
   Z <- add_fold(Z)
+
+  for(underlying_algo in underlying_algos){
 
@@
 
-    # fit target and error model to proper training set
+      # fit target and error model on proper training set
       model_target      <- fit_target_model(Z_proper_training)
@@
 
-    # non-conformity scores on calibration
+      # non-conformity scores on calibration set
       Z_calibration <- Z_calibration %>% 
@@
 
-    # error on test set
+      # predict grade and error on test set
       Z_test <- Z_test %>% 
@@
           compute_interval(ncs = ncs) %>%
+          correct_interval %>%
           compute_hit
@@
                  iteration    = iteration,
-               course       = course) %>%
+                 course       = course,
+                 underl_algo  = underlying_algo) %>%
           select(course, iteration, significance, width, hit,
-               Y, Y_hat, error, mu, mu_hat, sigma)
+                 Y, Y_hat, error, mu, mu_hat, sigma,
+                 border_low, border_low_corrected, border_high, border_high_corrected, width_corrected,
+                 underl_algo)
 
@@
 
-  } # end CV fold
+    } # end loop CV fold
 
-}
+  } # end loop underlying_algorithms
+
+} # end loop courses
 ```
@@
     mutate(iteration    = as.factor(iteration),
-           course       = as.factor(course))
+           course       = as.factor(course),
+           underl_algo  = as.factor(underl_algo))
 
@@
 ```{r, fig.height=4, eval = F}
-Z_test %>% select(Y, Y_hat, mu_hat, width, border_low, border_high, hit)
-plot(Z_test$error, Z_test$mu_hat)
+conformal_results %>%
+  ggplot() +
+  geom_density(aes(Y)) +
+  facet_wrap(~ course)
+
+conformal_results %>%
+  ggplot() +
+  geom_density(aes(Y_hat, col = underl_algo)) +
+  facet_wrap( ~ course)
+
+conformal_results %>%
+  ggplot() +
+  geom_point(aes(Y, Y_hat), size = 0.1) +
+  facet_grid(course ~ underl_algo)
+```
+
+```{r}
+conformal_results %>%
+  ggplot() +
+  geom_point(aes(mu, mu_hat)) +
+  facet_wrap(~ course)
 ```
@@
 ```{r, eval = F}
-cor(Z_test$error, Z_test$error_hat)
+conformal_results %>%
+  group_by(course, underl_algo) %>%
+  summarize(var_Y = var(Y),
+            cor_Y = cor(Y, Y_hat),
+            error = cor(mu, mu_hat))
 ```
 
-```{r, echo = FALSE, eval = F}
-ggplot(data = Z_callibration) + geom_histogram(aes(Y), bins = 15)
-
-ggplot(data = Z_callibration) + geom_histogram(aes(Y_hat), bins = 15)
-
-ggplot(data = Z_callibration) + geom_histogram(aes(alpha), bins = 15)
+# Timing
+```{r}
+Sys.time() - time0
 ```
-
-```{r, echo = FALSE, eval = F}
-ggplot(data = Z_callibration) + geom_point(aes(Y, Y_hat))
-
-ggplot(data = Z_callibration) + geom_point(aes(Y, alpha))
-
-ggplot(data = Z_callibration) + geom_point(aes(Y_hat, alpha))
-```

### 2019-06-27 Warning Issuance - Grade Prediction with RF.Rmd
no message

--- 2019-06-05 Warning Issuance - Grade Prediction with RF.Rmd
@@
 
-# Random forest
+# Extract sample of one course
 
 ```{r}
-data(iris)
+{z <- find_df("HUM2025") %>%
+  select(Grade, matches("GPA|Topic"))
 
-iris.rf <- randomForest(iris[,-5], iris[,5], prox=TRUE)
+n_sample <- nrow(z)
+n_train  <- floor(0.67 * n_sample)
+n_test   <- n_sample - n_train
 
-iris.p <- classCenter(iris[,-5], iris[,5], iris.rf$prox)
+allocation <- sample(rep(c("train", "test"), times = c(n_train, n_test)))
+z <- z %>% mutate(allocation = allocation)
+z_train <- z %>% filter(allocation == "train") %>% select(-allocation)
+z_test  <- z %>% filter(allocation == "test" ) %>% select(-allocation)} # prepare sample
+```
 
-plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
-bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
-main="Iris Data with Prototypes")
+# Grade prediction
+```{r}
+assess_prediction <- function(test_set = z_test, predictions){
 
-points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
+  test_set <- test_set %>% mutate(y_hat = predictions,
+                                  res = Grade - y_hat)
+
+ # hist(test_set$y_hat)
+#  plot(test_set$y_hat, test_set$res)
+#  plot(test_set$Grade, test_set$res)
+  plot(test_set$Grade, test_set$y_hat)
+
+  mae <- test_set$res %>% abs %>% mean
+  print(str_c("MAE: ", mae %>% round(2)))
+
+}
 ```
@@
 ```{r}
-rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
+# data
+x <- z_train %>% select(matches("Topic|GPA")) %>% as.matrix
+y <- z_train %>% pull(Grade)
+x_test <- z_test %>% select(matches("Topic|GPA"))
 
-rf2 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
+# Boost
+m_boost <- xgboost(data = x, label = y,
+                   max_depth = 2, eta = .3, subsample = 1, nrounds = 1000, colsample_bytree = .5,
+                   objective = "reg:linear")
+y_boost <- predict(m_boost, as.matrix(x_test))
+assess_prediction(predictions = y_boost)
 
-rf3 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
+# RF
+m_RF <- randomForest(as.matrix(x), y,
+                     ntree = 1000, mtry = floor(ncol(z_train)/3))
 
-rf.all <- combine(rf1, rf2, rf3)
-print(rf.all)
+y_rf <- predict(m_RF, as.matrix(x_test))
+assess_prediction(predictions = y_rf)
+
+m_lasso <- cv.glmnet(as.matrix(x), y,
+                     nfolds = 10, type.measure = "mae")
+y_lasso <- predict(m_lasso, newx = as.matrix(x_test), s="lambda.min")
+assess_prediction(predictions = y_lasso)
 ```
-
-```{r}
-## Look at the third trees in the forest.
-getTree(randomForest(iris[,-5], iris[,5], ntree=10), 3, labelVar=TRUE)
-```
-
-```{r}
-iris.rf <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
-iris.rf <- grow(iris.rf, 50)
-print(iris.rf)
-```
-
-```{r}
-set.seed(4543)
-data(mtcars)
-mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000,
-keep.forest=FALSE, importance=TRUE)
-
-importance(mtcars.rf)
-importance(mtcars.rf, type=1)
-```
-
-```{r}
-data(imports85)
-imp85 <- imports85[,-2] # Too many NAs in normalizedLosses.
-imp85 <- imp85[complete.cases(imp85), ]
-## Drop empty levels for factors.
-imp85[] <- lapply(imp85, function(x) if (is.factor(x)) x[, drop=TRUE] else x)
-stopifnot(require(randomForest))
-price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100)
-print(price.rf)
-numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100)
-print(numDoors.rf)
-```

### 2019-06-27 Warning Issuance - Grade Prediction with xgboost.Rmd
no message

---
title: "Pillar 1 - Student Topic Profile"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
editor_options: 
  chunk_output_type: console
---

__Considerations__:

* extract course descriptions from courses not offer in 2018-2019 e.g. SCI2012.

* give more weight to 3000-level courses

* restrict prep courses to UCM courses

# Set up

```{r setup, include = FALSE}

knitr::opts_chunk$set(cache.path = "Cache/Warning Issuance/")
knitr::opts_chunk$set(cache.fig  = "Cache/Figures/")
load("Output/useful functions.RDATA")

library(xgboost)
library(tidyverse)

load("Output/student_model.RDATA")
load("Output/course_current.RDATA")
load("Output/app_model.RDATA")
```

# Data

Remove course enrollments from 2007 from the student model because we have no information on the previous course enrolment of these students, hence no data on their previous academic performance and skills acquired in previous courses.

```{r}
d_student_model <- d_student_model %>% filter(Year_numerical != 2007)
```

Consider courses currently on offer and with at least 20 enrollments since 2008 
```{r}
d_course <- tibble(target = course_current) %>%

  mutate(student_model = target        %>% map(find_df),
         n             = student_model %>% map_dbl(nrow)) %>%

  filter(n > 20)
```

Beta of topic model to inspect results
```{r}
beta  <- app_model$Beta[[1]] %>% group_by(topic) %>% top_n(10, beta)
gamma <- app_model$Gamma[[1]] %>%  mutate(topic = topic %>% str_replace(" ", "_"))
remove(app_model)
```

# Extract sample of one course

```{r}
{z <- find_df("HUM2025") %>%
  select(Grade, matches("GPA|Topic"))

n_sample <- nrow(z)
n_train  <- floor(0.67 * n_sample)
n_test   <- n_sample - n_train

allocation <- sample(rep(c("train", "test"), times = c(n_train, n_test)))
z <- z %>% mutate(allocation = allocation)
z_train <- z %>% filter(allocation == "train") %>% select(-allocation)
z_test  <- z %>% filter(allocation == "test" ) %>% select(-allocation)} # prepare sample
```

# Grade prediction
```{r}
assess_prediction <- function(test_set = z_test, predictions){

  test_set <- test_set %>% mutate(y_hat = predictions,
                                  res = Grade - y_hat)

 # hist(test_set$y_hat)
#  plot(test_set$y_hat, test_set$res)
#  plot(test_set$Grade, test_set$res)
  plot(test_set$Grade, test_set$y_hat)

  s_res <- var(test_set$res)
  s_y <- var(test_set$Grade)
  r_squared <- (s_y - s_res) / s_y
  print(str_c("R-squared: ", r_squared %>% round(2)))

  mae <- test_set$res %>% abs %>% mean
  print(str_c("MAE: ", mae %>% round(2)))

}
```

```{r}
{{m <- randomForest(Grade ~ ., data = z_train,
                  ntree = 200, do.trace = FALSE, importance = TRUE,
                  mtry = floor(ncol(z_train)/2),
                  maxnodes = 25)
y_rf <- predict(m, z_test)
assess_prediction(predictions = y_rf)}

{m <- cv.glmnet(z_train %>% select(-Grade) %>% as.matrix, z_train %>% pull(Grade),
               nfolds = 10, type.measure = "mae")
y_lasso <- predict(m,newx= z_test %>% select(-Grade) %>% as.matrix, s="lambda.min")
assess_prediction(predictions = y_lasso)}}

rf
rf$rsq # pseudo r-squared
varImpPlot(rf)
imp <- rf$importance %>% as_tibble(rownames = "var")

# TODO: partial plots
{imp_var <- imp %>% arrange(desc(`%IncMSE`)) %>% pull(var)
op <- par(mfrow=c(2, 3)) # Looping over variables ranked by importance:
for (i in seq_along(imp_var))
  partialPlot(rf, 
              z_train,
              imp_var[i], 
              xlab=imp_var[i],
              main=paste("Partial Dependence on", imp_var[i]), ylim=c(30, 70))
par(op)}

```

# Random Forest

TODO: combine RF of all courses to evaluate feature importance

# Random forest trial
```{r randomForest}
## Classification:
data(iris)
iris.rf <- randomForest(Species ~ ., data=iris, importance=TRUE,
                        proximity=TRUE)
print(iris.rf)
## Look at variable importance:
round(importance(iris.rf), 2)
## Do MDS on 1 - proximity:
iris.mds <- cmdscale(1 - iris.rf$proximity, eig=TRUE)
op <- par(pty="s")
pairs(cbind(iris[,1:4], iris.mds$points), cex=0.6, gap=0,
      col=c("red", "green", "blue")[as.numeric(iris$Species)],
      main="Iris Data: Predictors and MDS of Proximity Based on RandomForest")
par(op)
print(iris.mds$GOF)

## The `unsupervised' case:
set.seed(17)
iris.urf <- randomForest(iris[, -5])
MDSplot(iris.urf, iris$Species)

## stratified sampling: draw 20, 30, and 20 of the species to grow each tree.
(iris.rf2 <- randomForest(iris[1:4], iris$Species, 
                          sampsize=c(20, 30, 20)))

## Regression:
data(airquality)
ozone.rf <- randomForest(Ozone ~ ., data=airquality, mtry=3,
                         importance=TRUE, na.action=na.omit)
print(ozone.rf)
## Show "importance" of variables: higher value mean more important:
round(importance(ozone.rf), 2)

## "x" can be a matrix instead of a data frame:
set.seed(17)
x <- matrix(runif(5e2), 100)
y <- gl(2, 50)
(myrf <- randomForest(x, y))
(predict(myrf, x))

## "complicated" formula:
(swiss.rf <- randomForest(sqrt(Fertility) ~ . - Catholic + I(Catholic < 50),
                          data=swiss))
(predict(swiss.rf, swiss))
## Test use of 32-level factor as a predictor:
set.seed(1)
x <- data.frame(x1=gl(53, 10), x2=runif(530), y=rnorm(530))
(rf1 <- randomForest(x[-3], x[[3]], ntree=10))

## Grow no more than 4 nodes per tree:
(treesize(randomForest(Species ~ ., data=iris, maxnodes=4, ntree=30)))

## test proximity in regression
iris.rrf <- randomForest(iris[-1], iris[[1]], ntree=101, proximity=TRUE, oob.prox=FALSE)
str(iris.rrf$proximity)
```

```{r classCenter}
data(iris)

iris.rf <- randomForest(iris[,-5], iris[,5], prox=TRUE)

iris.p <- classCenter(iris[,-5], iris[,5], iris.rf$prox)

plot(iris[,3], iris[,4], pch=21, xlab=names(iris)[3], ylab=names(iris)[4],
     bg=c("red", "blue", "green")[as.numeric(factor(iris$Species))],
     main="Iris Data with Prototypes")

points(iris.p[,3], iris.p[,4], pch=21, cex=2, bg=c("red", "blue", "green"))
```

```{r randomForest::combine}
rf1 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf2 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf3 <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)

rf.all <- randomForest::combine(rf1, rf2, rf3)
print(rf.all)
```

```{r getTree}
## Look at the third trees in the forest.
getTree(randomForest(iris[,-5], iris[,5], ntree=10), k = 3, labelVar=TRUE)
```

```{r grow}
iris.rf <- randomForest(Species ~ ., iris, ntree=50, norm.votes=FALSE)
iris.rf <- grow(iris.rf, 50)
print(iris.rf)
```

```{r importance}
set.seed(4543)
data(mtcars)
mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000,
                          keep.forest=FALSE, importance=TRUE)

importance(mtcars.rf)
importance(mtcars.rf, type=1)
```

```{r imports85}
data(imports85)
imp85 <- imports85[,-2] # Too many NAs in normalizedLosses.
imp85 <- imp85[complete.cases(imp85), ]
## Drop empty levels for factors.
imp85[] <- lapply(imp85, function(x) if (is.factor(x)) x[, drop=TRUE] else x)
stopifnot(require(randomForest))

price.rf <- randomForest(price ~ ., imp85, do.trace=10, ntree=100) # regression
print(price.rf)

numDoors.rf <- randomForest(numOfDoors ~ ., imp85, do.trace=10, ntree=100) # classification
print(numDoors.rf)
```

```{r margin}
iris.rf <- randomForest(Species ~ ., iris, keep.forest=FALSE)
plot(randomForest::margin(iris.rf), F)
plot(randomForest::margin(iris.rf), T)
```

```{r MDSplot}
iris.rf <- randomForest(Species ~ ., iris, proximity=TRUE,
                        keep.forest=FALSE)
MDSplot(iris.rf, iris$Species)
## Using different symbols for the classes:
MDSplot(iris.rf, iris$Species, palette=rep(1, 3), pch=as.numeric(iris$Species))
```

```{r na.roughfix}
## artificially drop some data values.
iris.na <- iris
for (i in 1:4) iris.na[sample(150, sample(20)), i] <- NA

iris.roughfix <- na.roughfix(iris.na)
iris.narf <- randomForest(Species ~ ., iris.na, na.action=na.roughfix)
print(iris.narf)
```

```{r outlier}
iris.rf <- randomForest(iris[,-5], iris[,5], proximity=TRUE)
plot(outlier(iris.rf), type="h",
     col=c("red", "green", "blue")[as.numeric(iris$Species)])
```

```{r partialPlot}
iris.rf <- randomForest(Species~., iris)
partialPlot(iris.rf, iris, Petal.Width, "versicolor")

## Looping over variables ranked by importance:
airquality <- na.omit(airquality)
ozone.rf <- randomForest(Ozone ~ ., airquality, importance=TRUE)
imp <- importance(ozone.rf)
impvar <- rownames(imp)[order(imp[, 1], decreasing=TRUE)]
op <- par(mfrow=c(2, 3))

for (i in seq_along(impvar))
  partialPlot(ozone.rf, 
              airquality,
              impvar[i], 
              xlab=impvar[i], main=paste("Partial Dependence on", impvar[i]), ylim=c(30, 70))
par(op)
```

```{r plot.randomForest}
data(mtcars)
plot(randomForest(mpg ~ ., mtcars, keep.forest=FALSE, ntree=100), log="y")
```

```{r predict.randomForest}
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind == 1,])

iris.pred <- predict(iris.rf, iris[ind == 2,])
table(observed = iris[ind==2, "Species"], predicted = iris.pred)

## Get prediction for all trees.
predict(iris.rf, iris[ind == 2,], predict.all=TRUE)

## Proximities.
predict(iris.rf, iris[ind == 2,], proximity=TRUE)

## Nodes matrix.
str(attr(predict(iris.rf, iris[ind == 2,], nodes=TRUE), "nodes"))
```

```{r rfcv}
myiris <- cbind(iris[1:4], matrix(runif(96 * nrow(iris)), nrow(iris), 96))
result <- rfcv(myiris, iris$Species, cv.fold=3)
with(result, plot(n.var, error.cv, log="x", type="o", lwd=2))

## The following can take a while to run, so if you really want to try
## it, copy and paste the code into R.

## Not run: 
result <- replicate(5, rfcv(myiris, iris$Species), simplify=FALSE)
error.cv <- sapply(result, "[[", "error.cv")
matplot(result[[1]]$n.var, cbind(rowMeans(error.cv), error.cv), type="l",
        lwd=c(2, rep(1, ncol(error.cv))), col=1, lty=1, log="x",
        xlab="Number of variables", ylab="CV Error")

## End(Not run)
```

```{r rfImpute}
iris.na <- iris
set.seed(111)
## artificially drop some data values.
for (i in 1:4) iris.na[sample(150, sample(20)), i] <- NA

set.seed(222)
iris.imputed <- rfImpute(Species ~ ., iris.na)

set.seed(333)
iris.rf <- randomForest(Species ~ ., iris.imputed)

print(iris.rf)
```

```{r treesize}
iris.rf <- randomForest(Species ~ ., iris)
hist(treesize(iris.rf))
```

```{r tuneRF}
data(fgl, package="MASS")
fgl.res <- tuneRF(fgl[,-10], fgl[,10], ntreeTry = 1000, stepFactor=1.5)
```

```{r varImpPlot}
mtcars.rf <- randomForest(mpg ~ ., data=mtcars, ntree=1000, keep.forest=FALSE,
                          importance=TRUE)
varImpPlot(mtcars.rf)
```

```{r varUsed}
varUsed(randomForest(Species~., iris, ntree=100))
```

### 2019-06-27 Conference/COPA2019/paper/conference figures COPA2019.Rmd
no message

--- 2019-05-22 conference figures COPA2019.Rmd
@@
----
-title: "Figures for conference paper"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-library(tidyverse)
-library(kableExtra)
-library(DiagrammeR)
-
-knitr::opts_chunk$set(echo = FALSE)
-theme_set(theme_light())
-
-load("Output/app_model.RDATA")
-load("Output/data_pillar_1.Rdata")
-load("Output/d_text.RDATA")
-load("Output/df_logLike_catalogue.RDATA")
-load("Output/CV.RDATA")
-load("Output/conformal.RDATA")
-
-output_folder <- "Conference/COPA2019/paper/figures"
-plot_width <- 6
-plot_height <- plot_width / 1.6 
-```
-
-```{r latex_table}
-latex_table <- function(df, filename = "test"){
-
-  df %>%
-    kable("latex", booktabs = TRUE, align = "c") %>%
-    write(file = str_c(output_folder, "/", filename, ".txt"))
-}
-```
-
-```{r TM}
-gamma <- app_model$Gamma[[1]]
-beta  <- app_model$Beta[[1]]
-```
-
-```{r student_data}
-set.seed(2019)
-
-student_data <- d_transcript_augmented %>%
-
-  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%
-
-  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization
-
-  sample_n(10) %>%
-
-  arrange(`Academic Year`) %>%
-
-  print
-```
-
-```{r course_data}
-course_data <- d_text$catalogues %>%
-
-  slice(50005:50014) %>%
-
-  select(`Course ID`, `Course Title`, Department = department, word) %>%
-
-  print
-```
-
-# Student data
-
-```{r fig_student_data}
-student_data %>% latex_table("data-student")
-```
-
-# Course data
-
-```{r fig_course_data}
-course_data %>% latex_table("course-student")
-```
-
-# Flow chart
-
-## EDM2019 style
-```{r}
-grViz("digraph flowchart{
-
-      fontname = Helvetica
-      size = 15
-
-      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]
-
-      edge [fontname = Helvetica, decorate = TRUE]
-
-      subgraph cluster_input {
-		  color = white;
-
-      subgraph cluster_data {
-      label = 'Data';
-      style = filled;
-		  color = lightgrey;
-		  node [shape = cylinder];
-      CD [label = 'Course Data']
-      SD [label = 'Student Data']
-      }
-
-      subgraph cluster_input_user {
-      label = 'User Input';
-      style = filled;
-		  color = coral;
-
-      ID [label = 'Student ID']
-      KW [label = 'Selected Key Words']
-      CS [label = 'Selected Courses']
-      }
-
-      } #close input subgraph
-
-      subgraph cluster_model_fitting{
-      label = 'Model Fitting';
-      style = filled;
-		  color = LavenderBlush;
-
-      SM [label = 'Student Model']
-
-      PM [label = 'Predictive Models']
-      x1 [shape = circle, width = .01, height = .01, label = '']
-      TM [label = 'Topic Model']
-
-      }
-
-      subgraph cluster_inter_last{
-      label = 'Intermediate Results';
-      style = filled;
-		  color = Tan;
-
-      GP [label = 'Grade Prediction']
-      AI [label = 'Student´s Academic Interests']
-      }
-
-      # Ouput
-      subgraph cluster_ouput {
-      label = 'System Output';
-      style = filled;
-		  color = lightCyan;
-
-      SUG [label = 'Course Suggestions']
-      PR [label = 'Prediction Region']
-      }
-
-      TR [label = 'Student´s Transcript']
-
-      # Invisible node
-      x2 [shape = circle, width = .01, height = .01, label = '']
-      x3 [shape = circle, width = .01, height = .01, label = '']
-
-      # edges
-
-      {SD, TM} -> SM;
-      {TM, KW} -> AI;
-      ID -> TR;
-      {PM, CS, TR} -> GP;
-      GP -> PR [label = '  Conformal Prediction'];
-
-      CD -> TM [label = '  LDA'];
-
-      SM -> PM [label = '  Lasso'];
-
-      {TM, AI} -> x2 [arrowhead = none]
-      x2 -> SUG [label = '  KL distance'];
-
-      }
-      ")
-
-# Save by hand
-# File name: Conference/COPA2019/paper/figures/flowchart
-```
-
-## 2 pillar style
-```{r}
-grViz("digraph flowchart{
-
-      fontname = Helvetica
-      size = 15
-      newrank = true;
-
-      node [fontname = Helvetica, shape = rectangle, style = filled, fillcolor = white]
-      edge [fontname = Helvetica, decorate = TRUE]
-
-      subgraph cluster_input_kw {
-      label = 'User Input';
-      penwidth = 2;
-
-      KW [label = 'Selected Key Words']
-      }
-
-      subgraph cluster_data {
-      label = 'Data';
-      penwidth = 2;
-
-		  node [shape = cylinder];
-      SD [label = 'Student Data', group = 2]
-      CD [label = 'Course Data' , group = 1]
-      }
-
-      subgraph cluster_input_course {
-      label = 'User Input';
-      penwidth = 2;
-
-      CS [label = 'Selected Courses']
-      }
-
-      subgraph cluster_pillar_1{
-      label = 'Pillar 1: Course Suggestion';
-      penwidth = 2;
-
-      TM  [label = 'Topic Model \nof the Courses', group = 1]
-      AI  [label = 'Model of \nStudent´s Academic Interests']
-      x1  [shape = circle, width = .01, height = .01, label = '']
-      SUG [label = 'Course Suggestions', ]
-
-      } # close pillar 1
-
-      subgraph cluster_pillar_2{
-      label = 'Pillar 2: Warning Issuance';
-      penwidth = 2;
-
-      SM  [label = 'Student Model'    , group = 2]
-      PM  [label = 'Predictive Models', group = 2]
-      GP  [label = 'Point Prediction \nfor Grade' , group = 2]
-      WAR [label = 'Warning'          , group = 2]
-      PR  [label = 'Prediction Region', color = red, fontcolor = red]
-
-      } # close pillar 2
-
-		  { rank=same; KW; CD; SD; CS}
-		  { rank=same; TM; SM}
-      { rank=same; PR; WAR; SUG}
-
-      # edges
-      CD -> TM [label = '  LDA'];
-      {TM, KW} -> AI;
-      {TM, AI} -> x1 [arrowhead = none]
-      x1 -> SUG [label = '  KL distance'];
-
-      SD -> SM;
-      TM -> SM;
-      SM -> PM [label = '  Lasso'];
-      {PM, CS} -> GP;
-      GP -> WAR;
-      GP -> PR [label = ' Conformal Prediction', color = red, fontcolor = red];
-
-      }
-      ")
-
-# Save by hand
-# File name: Conference/COPA2019/paper/figures/flowchart
-```
-
-# Model Selection (topic model)
-
-```{r}
-max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]
-
-df_logLike_catalogue %>%
-  ggplot(aes(x = n_topic, y = LogLikelihood)) +
-  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
-  geom_line(linetype = "dashed") +
-  geom_point() +
-
-  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +
-
-  ggsave(filename = str_c("model-selection.jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-```
-
-# Beta
-
-```{r reorder_within}
-reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
-  new_x <- paste(x, within, sep = sep)
-  stats::reorder(new_x, by, FUN = fun)
-}
-
-scale_x_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-
-scale_y_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-```
-
-```{r plot_beta}
-plot_beta <- function(topic = 1, resize_factor = 1){
-
-  top <- str_c("Topic ", topic)
-
-  beta %>%
-    filter(topic %in% top) %>% 
-    group_by(topic) %>%
-    top_n(9, beta) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder_within(term, beta, topic), y = beta)) +
-
-    coord_flip() +
-
-    theme(axis.text.y = element_text(size = 11)) +
-
-    labs(title = NULL, x = "Terms", y = "Beta") +
-
-    facet_wrap( ~ topic, scales = "free_y") +
-    scale_x_reordered()
-
-  ggsave(filename = "beta.jpeg", path = output_folder,
-         width = 1.5 * plot_width / resize_factor, height = plot_height / resize_factor)
-
-}
-```
-
-# Gamma
-
-```{r plot_gamma}
-plot_gamma <- function(course = "COR1002"){
-
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-
-    coord_flip() +
-
-    labs(title = NULL,
-         x = "Topics",
-         y = "Gamma"
-         )
-
-  ggsave(filename = str_c("gamma-", course, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-
-}
-```
-
-```{r fig_gamma}
-plot_gamma("COR1004")
-
-resize_factor <- 1.8
-
-plot_beta(c(4,19), resize_factor = resize_factor)
-```
-
-# Topic Expertise
-```{r}
-courses <- paste("Course", 1 : 3)
-
-transcript <- tibble(Course    = courses,
-                     Grade     = c(6  , 9  , 2))
-
-gamma <- tibble(Course    = courses,
-                `Topic 1` = c(0  , 0.2, 0  ),
-                `Topic 2` = c(0.7, 0.2, 0.4),
-                `Topic 3` = c(0.2, 0.2, 0.2),
-                `Topic 4` = c(0.1, 0.2, 0.1),
-                `Topic 5` = c(0  , 0.2, 0.2))
-
-df1 <- gamma %>% 
-  gather(key = Topic, value = gamma, -Course) %>% 
-  arrange(Course) %>%
-
-  left_join(transcript, by = "Course") %>%
-  mutate(contribution = Grade/10 * gamma)
-
-topic_expertise <- df1 %>%
-  select(-gamma, - Grade)%>% 
-  spread(key = Topic, value = contribution) %>%
-  add_row(Course = "Total", `Topic 1` = 0.18, `Topic 2` = 0.68, `Topic 3` = 0.34, `Topic 4` = 0.26, `Topic 5` = 0.22)
-
-# Table
-
-transcript %>% 
-  mutate(Grade = str_c(Grade, "/10")) %>%
-  latex_table("toy-transcript")
-
-gamma %>% latex_table("toy-gamma")
-
-topic_expertise %>% latex_table("toy-contribution")
-
-# Plot
-df1 %>% 
-  mutate(Topic = factor(Topic, levels = str_c("Topic ", 5:1))) %>%
-  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
-  geom_col() +
-  coord_flip() +
-  labs(x = "Topics", y = "Topic Expertise")
-
-ggsave(filename = str_c("toy-expertise.jpeg"), path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-# CV
-```{r}
-fit_lasso %>%
-  ggplot(aes(y = cv_error, group = 1)) +
-  geom_boxplot() +
-  theme(axis.ticks.y = element_line(color = "white"),
-        axis.text.y  = element_text(color = "white"),
-        panel.border = element_rect(color = "white"),
-        panel.grid   = element_line(color = "white")
-        ) +
-
-  labs(y = "Cross-Validation Mean Absolute Error") +
-  coord_flip()
-
-ggsave(filename = str_c("cv-mae.jpeg"), path = output_folder,
-         width = plot_width/1.5, height = plot_height/3.5)
-
-fit_lasso %>%
-  summarize(Mean = mean(cv_error),
-            `Weighted mean` = weighted.mean(cv_error, n),
-            Median = median(cv_error),
-            `Standard Deviation` = sd(cv_error),
-            Minimum = min(cv_error),
-            Maximum = max(cv_error)) %>%
-  gather(key = x, value = y) %>% 
-  kable("latex", booktabs = TRUE, col.names = NULL) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/cv-mae-table.pdf"))
-```
-
-# Conformal
-
-## course table
-
-```{r}
-course_table %>%
-  select(- df) %>%
-  mutate(cv_error = cv_error %>% round(2)) %>%
-  latex_table("conformal-course")
-```
-
-## width
-
-```{r}
-d_width <- conformal_results %>%
-  group_by(course, significance) %>%
-  summarise(q_50 = quantile(width, 0.5), # median
-            q_10 = quantile(width, 0.1),
-            q_90 = quantile(width, 0.9))
-```
-
-```{r}
-d_width %>%
-  ggplot() +
-  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5) +
-  geom_hline(yintercept = 1, linetype = "dashed") +
-  geom_line(aes(significance, q_50, group = 1)) +
-  geom_point(aes(significance, q_50)) +
-  facet_wrap( ~ course) +
-  labs(y = "Width",
-       x = "Significance Level") +
-  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
-
-ggsave(filename = "conformal-width.jpeg", path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-## Error
-
-```{r}
-d_error <- conformal_results %>%
-  group_by(course, significance) %>%
-  summarise(error = mean(!hit))
-```
-
-```{r}
-d_error %>%
-  ggplot(aes(x = significance, y = error)) +
-  geom_abline(slope = 1, linetype = "longdash") +
-  geom_line(aes(group = 1)) +
-  geom_point() +
-  facet_wrap( ~ course) +
-  labs(y = "Error Rate",
-       x = "Significance Level") +
-  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))
-
-ggsave(filename = "conformal-error.jpeg", path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-## Table
-```{r}
-conformal_results %>%
-  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
-  group_by(course, significance) %>%
-  summarize(width_med  = median(width),
-            error_rate = mean(!hit)) %>%
-
-  gather(key = "measure", value = "output", width_med, error_rate) %>%
-  mutate(output = round(output, 2)) %>%
-  unite(id, measure, significance, sep = "-") %>%
-  spread(key = id, value = output) %>%
-
-  select(course, matches("med"), matches("error")) %>%
-  latex_table("conformal-table")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:9c3233bc067a993bccdab77bc21d030f1b3dfe90f2382d90d157a85083c0ac99
+size 13510

### 2019-06-27 Conference/EDM2019/conference figures EDM2019.Rmd
no message

--- 2019-04-30 conference figures.Rmd
@@
----
-title: "Figures for conference paper"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-library(tidyverse)
-library(kableExtra)
-library(DiagrammeR)
-
-knitr::opts_chunk$set(echo = FALSE)
-theme_set(theme_light())
-
-load("Output/app_model.RDATA")
-load("Output/data_pillar_1.Rdata")
-load("Output/d_text.RDATA")
-load("Output/df_logLike_catalogue.RDATA")
-load("Output/CV.RDATA")
-
-output_folder <- "Conference/Figures"
-plot_width <- 6
-plot_height <- plot_width / 1.6 
-```
-
-```{r TM}
-gamma <- app_model$Gamma[[1]]
-beta  <- app_model$Beta[[1]]
-```
-
-```{r student_data}
-set.seed(2019)
-
-student_data <- d_transcript_augmented %>%
-
-  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%
-
-  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization
-
-  sample_n(10) %>%
-
-  arrange(`Academic Year`) %>%
-
-  print
-```
-
-```{r}
-course_data <- d_text$catalogues %>%
-
-  slice(50005:50014) %>%
-
-  select(`Course ID`, `Course Title`, Department = department, word) %>%
-
-  print
-```
-
-# Student data
-
-```{r fig_student_data}
-student_data %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/student_data.pdf"))
-```
-
-# Course data
-
-```{r fig_course_data}
-course_data %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/course_data.pdf"))
-```
-
-# Flow chart
-
-```{r}
-grViz("digraph flowchart{
-
-      fontname = Helvetica
-      size = 15
-
-      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]
-
-      edge [fontname = Helvetica, decorate = TRUE]
-
-      subgraph cluster_data {
-      label = 'Data';
-      style = filled;
-		  color = lightgrey;
-		  node [shape = cylinder];
-      CD [label = 'Course Data']
-      SD [label = 'Student Data']
-      }
-
-      subgraph cluster_input_user {
-      label = 'User Input';
-      style = filled;
-		  color = coral;
-
-      ID [label = 'Student ID']
-      KW [label = 'Selected Key Words']
-      CS [label = 'Selected Courses']
-      }
-
-      subgraph cluster_model_fitting{
-      label = 'Model Fitting';
-      style = filled;
-		  color = LavenderBlush;
-
-      TE [label = 'Topic Expertise']
-      AP [label = 'Academic Performance']
-
-      PM [label = 'Predictive Models']
-      x1 [shape = circle, width = .01, height = .01, label = '']
-      TM [label = 'Topic Model']
-
-      }
-
-      subgraph cluster_inter_last{
-      label = 'Intermediate Results';
-      style = filled;
-		  color = Tan;
-
-      GP [label = 'Grade Prediction']
-      AI [label = 'Student´s Academic Interests']
-      }
-
-      # Ouput
-      subgraph cluster_ouput {
-      label = 'System Output';
-      style = filled;
-		  color = lightCyan;
-
-      SUG [label = 'Course Suggestions']
-      WAR [label = 'Warnings']
-      PRE [label = 'Preparatory Coursework']
-      }
-
-      TR [label = 'Student´s Transcript']
-
-      # Invisible node
-      x2 [shape = circle, width = .01, height = .01, label = '']
-      x3 [shape = circle, width = .01, height = .01, label = '']
-
-      # edges
-
-      SD -> AP [weight = 2];
-      {SD, TM} -> TE;
-      {TM, KW} -> AI;
-      ID -> TR;
-      {PM, CS, TR} -> GP;
-      GP -> WAR;
-		  WAR -> PRE;
-
-      CD -> TM [label = '  LDA'];
-
-      {AP, TE} -> x1 [arrowhead = none]
-      x1 -> PM [label = '  Lasso'];
-
-      {TM, AI} -> x2 [arrowhead = none]
-      x2 -> SUG [label = '  KL distance'];
-
-      {TM, PM} -> x3 [arrowhead = none]
-      x3 -> PRE [label = '  KL distance'];
-
-      }
-      ")
-
-# Save by hand
-# image format: JPEG
-# Width: 626
-# Check Maintain aspect ratio
-# File name: Conference/Figures/Flowchart
-```
-
-# Model Selection (topic model)
-
-```{r}
-max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]
-
-df_logLike_catalogue %>%
-  ggplot(aes(x = n_topic, y = LogLikelihood)) +
-  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
-  geom_line(linetype = "dashed") +
-  geom_point() +
-
-  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +
-
-  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-```
-
-# Beta
-
-```{r plot_beta}
-plot_beta <- function(topic = 1, resize_factor = 1){
-
-  top <-  str_c("Topic ", topic)
-
-  beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
-
-    coord_flip() +
-
-    theme(axis.text.y = element_text(size = 11)) +
-
-    labs(title = str_c("Topic ", topic),
-         x = "Terms",
-         y = "Beta"
-         )
-
-  ggsave(filename = str_c("Beta - topic ", topic, ".jpeg"), path = output_folder,
-         width = plot_width / resize_factor, height = plot_height / resize_factor)
-
-}
-```
-
-```{r fig_beta}
-plot_beta(1)
-```
-
-# Gamma
-
-```{r plot_gamma}
-plot_gamma <- function(course = "COR1002"){
-
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-
-    coord_flip() +
-
-    labs(title = course,
-         x = "Topics",
-         y = "Gamma"
-         )
-
-  ggsave(filename = str_c("gamma - course ", course, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-
-}
-```
-
-```{r fig_gamma}
-plot_gamma("COR1004")
-
-resize_factor <- 1.6
-
-plot_beta(4, resize_factor = resize_factor)
-plot_beta(19, resize_factor = resize_factor)
-```
-
-# Topic Expertise
-```{r}
-courses <- paste("Course", 1 : 3)
-
-transcript <- tibble(Course    = courses,
-                     Grade     = c(6  , 9  , 2.5))
-
-gamma <- tibble(Course    = courses,
-                `Topic 1` = c(0  , 0.2, 0  ),
-                `Topic 2` = c(0.7, 0.2, 0.4),
-                `Topic 3` = c(0.2, 0.2, 0.2),
-                `Topic 4` = c(0.1, 0.2, 0.1),
-                `Topic 5` = c(0  , 0.2, 0.2))
-
-df1 <- gamma %>% 
-  gather(key = Topic, value = gamma, -Course) %>% 
-  arrange(Course) %>%
-
-  left_join(transcript, by = "Course") %>%
-  mutate(contribution = Grade/10 * gamma)
-
-topic_expertise <- df1 %>%
-  select(-gamma, - Grade) %>% 
-  spread(key = Topic, value = contribution)
-
-# Table
-
-transcript %>% 
-  mutate(Grade = str_c(Grade, "/10")) %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_transcript.pdf"))
-
-gamma %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_gamma.pdf"))
-
-topic_expertise %>% 
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/toy_topic_expertise.pdf"))
-
-# Plot
-df1 %>% 
-  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
-  geom_col() +
-  labs(x = "Topics", y = "Topic Expertise")
-
-ggsave(filename = str_c("toy Topic Expertise.jpeg"), path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-# CV
-```{r}
-fit_lasso %>%
-  ggplot(aes(y = cv_error, group = 1)) +
-  geom_boxplot() +
-  theme(axis.ticks.y = element_line(color = "white"),
-        axis.text.y  = element_text(color = "white"),
-        panel.border = element_rect(color = "white"),
-        panel.grid   = element_line(color = "white")
-        ) +
-
-  labs(y = "Cross-Validation Mean Absolute Error") +
-  coord_flip()
-
-ggsave(filename = str_c("CV.jpeg"), path = output_folder,
-         width = plot_width/1.5, height = plot_height/3.5)
-
-fit_lasso %>%
-  summarize(Mean = mean(cv_error),
-            `Weighted mean` = weighted.mean(cv_error, n),
-            Median = median(cv_error),
-            `Standard Deviation` = sd(cv_error),
-            Minimum = min(cv_error),
-            Maximum = max(cv_error)) %>%
-  gather(key = x, value = y) %>% 
-  kable("latex", booktabs = TRUE, col.names = NULL) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/CV.pdf"))
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:acf1a764242de21f44aed1b7332583505cf243fabd0e5d22e18520d426f1bf59
+size 8680

### 2019-06-27 Pillar 1 - Conformal Prediction.Rmd
no message

@@
----
-title: "Pillar 1 - Conformal Prediction"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  pdf_document:
-    number_sections: true
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-set.seed(1)
-
-knitr::opts_chunk$set(fig.width = 3, fig.height = 2,
-                      echo = FALSE, warning = FALSE)
-
-library(tidyverse)
-library(glmnet)
-
-load("Output/CV.RDATA")
-load("Output/data_student.RDATA")
-load("Output/student_profile.RDATA")
-```
-
-```{r setup_graph}
-theme_set(theme_light())
-
-output_folder <- "Conference/COPA2019/paper/figures"
-plot_width  <- 6
-plot_height <- plot_width / 1.6 
-```
-
-# Course selection
-I select courses with large and small n, and large and small CV error. I do not select courses whose lasso model contains less than 3 non-zero coefficients (df).
-
-* COR1002: large n
-* COR1004: large n and smaller CV error (mean absolute error) than COR1002
-
-* SCI3003: small n and large CV error
-* SCI2040: small n and small CV erro
-
-* SSC3044: small CV error
-* SSC3038: small CV error and n twice as large as SSC3044
-
-* SCI2018: large CV error
-* SCI2010: large CV error and n twice as large as SCI2018
-
-```{r course_selection}
-course_selection <- c(
-#  "SCI3003", "SCI2040", # remove because n too small
-  "COR1002", "COR1004",  "SSC3044", "SSC3038", "SCI2018", "SCI2010")
-
-course_table <- fit_lasso %>% 
-  filter(target %in% course_selection) %>% 
-  select(target, n, cv_error, df)
-```
-
-# Conformal Prediction setp by step
-
-## Cross-validation
-
-```{r CV helper}
-create_Z <- function(course){
-
-  student_profile %>%
-    filter(`Course ID` == course) %>%
-    select(Y = Grade, matches("GPA|Topic"))
-
-}
-
-add_fold <- function(df, n_fold = 10){
-
-  n         <- nrow(df)
-  fold_size <- ceiling(n / n_fold)
-  folds     <- rep(1 : 10, fold_size) %>% sample %>% .[1 : n]
-
-  df %>% mutate(fold = folds)
-
-}
-```
-
-## Training, callibration and test sets
-
-```{r split helper}
-create_test <- function(df, fold_current) df %>% filter(fold == fold_current)
-
-create_training <- function(df, fold_current) df %>% filter(fold != fold_current)
-
-add_allocation <- function(df){
-
-  n_training <- nrow(df)
-  n_proper_training <- floor(0.67 * n_training)        # 2/3
-  n_calibration     <- n_training - n_proper_training  # 1/3
-
-  allocation <- rep(x     = c("proper training", "calibration"), 
-                    times = c(n_proper_training, n_calibration)) %>%
-  sample
-
-  df %>% mutate(allocation = allocation)
-
-}
-
-create_proper_training <- function(df) df %>% filter(allocation == "proper training")
-
-create_calibration     <- function(df) df %>% filter(allocation == "calibration")
-```
-
-## Fit lasso on training set
-```{r,lasso helper}
-fit_target_model <- function(df){
-
-  X <- df %>% select(matches("GPA|Topic"))
-  Y <- df %>% pull(Y)
-
-  cv.glmnet(x = as.matrix(X), y = Y, type.measure = "mae") # lasso by default. Use mean absolute error
-
-}
-
-predict_grade <- function(df, model){
-
-  X <- df %>% select(matches("GPA|Topic"))
-
-  Y_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min") # use lambda that minimizes mae
-
-  df %>% mutate(Y_hat = as.vector(Y_hat),
-                error = abs(Y_hat - Y),
-                mu    = log(error)) # take ln of absolute error
-
-}
-
-fit_error_model <- function(df){
-
-  X  <- df %>% select(matches("GPA|Topic"))
-  mu <- df %>% pull(mu)
-
-  cv.glmnet(x = as.matrix(X), y = mu, type.measure = "mae")
-
-}
-
-predict_error <- function(df, model){
-
-  X <- df %>% select(matches("GPA|Topic"))
-
-  mu_hat <- predict.cv.glmnet(model, newx = as.matrix(X), s = "lambda.min")
-
-  df %>% mutate(mu_hat = as.vector(mu_hat))
-
-}
-```
-
-## Compute standardized non-conformity scores on callibration test
-```{r}
-
-compute_ncs              <- function(df) df %>% mutate(alpha = abs(Y - Y_hat))
-
-compute_standardized_ncs <- function(df) df %>% mutate(sigma = exp(mu_hat),
-                                                       alpha = abs(Y - Y_hat) / sigma )
-
-compute_significance     <- function(df) df %>% mutate(significance = rank(-alpha) / nrow(.) ) # !!! double check!!!
-```
-
-## Evaluate error rate on test set
-
-```{r}
-compute_width <- function(df, significance_given){
-
-  df <- df %>% filter(significance <= significance_given)
-
-  min(df$alpha)
-
-}
-
-compute_interval <- function(df, ncs){
-
-  df %>% mutate(
-    sigma       = exp(mu_hat),
-    width       = ncs * sigma,
-    border_low  = Y_hat - width,
-    border_high = Y_hat + width
-    )
-}
-
-compute_hit <- function(df){
-  df %>% mutate(hit = (border_low <= Y) & (Y <= border_high))
-}
-```
-
-# Loop through all courses
-
-```{r, echo = FALSE}
-
-# Set up
-
-significance <- c(0.05, seq(0.1, 0.9, 0.1))
-results <- list()
-n_list <- 1
-
-for(course in course_selection){
-
-  # data
-  Z <- create_Z(course)
-  Z <- add_fold(Z)
-
-  for(iteration in 1 : 10){
-
-    # proper training, calibration and test sets
-    Z_test            <- create_test(Z, fold_current = iteration)
-    Z_training        <- create_training(Z, fold_current = iteration) %>% add_allocation
-    Z_proper_training <- create_proper_training(Z_training)
-    Z_calibration     <- create_calibration(Z_training)
-
-    # fit target and error model to proper training set
-    model_target      <- fit_target_model(Z_proper_training)
-    Z_proper_training <- predict_grade(Z_proper_training, model_target)
-    model_error       <- fit_error_model(Z_proper_training)
-
-    # non-conformity scores on calibration
-    Z_calibration <- Z_calibration %>% 
-      predict_grade(model_target) %>%
-      predict_error(model_error) %>%
-      compute_standardized_ncs %>%
-      compute_significance
-
-    # error on test set
-    Z_test <- Z_test %>% 
-      predict_grade(model_target) %>%
-      predict_error(model_error)
-
-    for(signi in significance){ # loop through significance levels
-
-      ncs <- compute_width(Z_calibration, signi)
-
-      Z_test_augmented <- Z_test %>% 
-        compute_interval(ncs = ncs) %>%
-        compute_hit
-
-      # save results
-      results[[n_list]] <- Z_test_augmented %>%
-        mutate(significance = signi,
-               iteration    = iteration,
-               course       = course) %>%
-        select(course, iteration, significance, width, hit,
-               Y, Y_hat, error, mu, mu_hat, sigma)
-
-      n_list <- n_list + 1
-
-    } # end loop significance
-
-  } # end CV fold
-
-}
-```
-
-```{r}
-conformal_results <- bind_rows(results) %>%
-    mutate(iteration    = as.factor(iteration),
-           course       = as.factor(course))
-
-save(conformal_results, course_table, file = "Output/conformal.RDATA")
-```
-
-Illustration of the effect of error_hat on interval's width (for significance of 99%):
-```{r, fig.height=4}
-Z_test %>% select(Y, Y_hat, error, error_hat, width, border_low, border_high, hit)
-plot(Z_test$error, Z_test$error_hat)
-```
-
-Correlation between the actual errors and the predicted errors (error_hat):
-```{r}
-cor(Z_test$error, Z_test$error_hat)
-```
-
-```{r, echo = FALSE, eval = F}
-ggplot(data = Z_callibration) + geom_histogram(aes(Y), bins = 15)
-
-ggplot(data = Z_callibration) + geom_histogram(aes(Y_hat), bins = 15)
-
-ggplot(data = Z_callibration) + geom_histogram(aes(alpha), bins = 15)
-```
-
-```{r, echo = FALSE, eval = F}
-ggplot(data = Z_callibration) + geom_point(aes(Y, Y_hat))
-
-ggplot(data = Z_callibration) + geom_point(aes(Y, alpha))
-
-ggplot(data = Z_callibration) + geom_point(aes(Y_hat, alpha))
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:1695b735cec1287d29ba5b74efc8cd72caa362611bd81c9a7b5d5a1855ab484d
+size 7419

### 2019-06-27 Pillar 2 - Topic Modeling.Rmd
no message

@@
----
-title: "Pillar 2 - Topic Modeling"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
-                      eval = FALSE)
-```
-
-#Setup
-##Libraries
-```{r library, message = FALSE, eval = TRUE}
-library(tidyverse)
-library(tidytext)
-
-library(ggwordcloud) # Word Clouds
-library(topicmodels)
-library(lemon)
-library(ggthemes)
-library(rlang) #quote
-library(ldatuning) # ideal number of topics in LDA
-
-```
-
-##Loading data
-We load a list `d_text` with two tibbles of textual data for catalogues and manuals.
-That is, for $catalogues and $manuals we have a tibble with the following columns: `Course ID`, `year`, `word_original`, `word`.
-
-We also load the environment `Output/data_pillar_2.RDATA` containing the data sets`d_course` and `d_transcript` that we will need to prepare some imputs for our App.
-```{r import data, eval = TRUE}
-#load
-load("./Output/d_text.RDATA")
-load("./Output/data_pillar_2.RDATA") #used for app
-```
-##Helpers
-###Preparation of course_title vector
-```{r course titles, eval = TRUE}
-#Clean titles
-course_titles <-  d_text$catalogues %>%
-  select(`Course ID`, `Course Title`, department) %>% 
-  distinct
-
-empty_titles <- course_titles %>% filter(`Course Title` == "")
-```
-####Uniform course labels
-We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title.
-```{r attatch titles}
-uniform_course_labels <- course_titles %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
-                                              T ~ `Course Title`),
-                         `Course ID` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
-                                                 T ~ "unknown"),
-                         `Course Title` = c_title
-                         ) %>% select(-c_title)
-```
-###Functions for internal faceting
-```{r function reorder_within & co., echo = FALSE, eval = TRUE}
-
-# Function for ordering within facet:
-# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R
-
-reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
-  new_x <- paste(x, within, sep = sep)
-  stats::reorder(new_x, by, FUN = fun)
-}
-
-scale_x_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-
-scale_y_reordered <- function(..., sep = "___") {
-  reg <- paste0(sep, ".+$")
-  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
-}
-```
-
-# TF-IDF
-We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.
-
-## Functions for Generating Barplots and Word Clouds
-The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
-```{r compute_tf_idf, cache = TRUE}
-#
-##Function
-compute_tf_idf <- function(data){
-
-  data %>%
-    count(
-      `Course ID`,
-      word
-      ) %>%
-    bind_tf_idf(
-      term = word, 
-      document = `Course ID`,
-      n = n
-      )
-}
-
-#
-##Application
-tf_idf <- map(d_text, .f = compute_tf_idf)
-
-#
-##Clean workspace
-rm(compute_tf_idf)
-```
-
-The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
-```{r plot_tf_idf}
-plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){
-
-  #
-  # Barplot
-  g <- data %>%
-    ggplot(
-      aes(
-        x = reorder_within(word, tf_idf, facet), 
-        y = tf_idf
-        )
-      ) +
-    geom_col(
-      show.legend = FALSE
-      ) +
-    labs(
-      x = NULL,
-      y = "tf-idf"
-      ) +
-    scale_x_reordered() +
-    facet_wrap(
-      facets = ~ facet, 
-      scales = "free",
-      ncol = n_col
-      ) +
-    coord_flip()
-
-  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-  #
-  # Word Cloud
-  g <- data %>%
-    group_by(
-      facet
-      ) %>%
-    mutate(
-      freq = tf_idf / sum(tf_idf)
-      ) %>% # normalization within facet
-    ggplot(
-      aes(
-        size = freq ^ 0.7, 
-        label = word, 
-        color = freq ^ 0.7
-        )
-      ) +
-    geom_text_wordcloud_area(
-      area_corr_power = 1,
-      eccentricity    = 1,
-      rm_outside      = T
-      ) +
-    scale_radius(
-      range = c(2, 10),
-      limits = c(0, NA)
-      ) +
-    scale_color_gradient(
-      low = "red", 
-      high = "blue"
-      ) +
-    facet_wrap(
-      facet = ~ facet,
-      ncol = n_col
-      ) + 
-    theme(
-      strip.text.x     = element_text(),
-      panel.background = element_rect(fill = "white"),
-      plot.title       = element_text(hjust = 0.5)
-    )
-
-  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)
-
-}
-```
-
-## Course Level
-The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
-We apply the function to `id_plot` and pipe it to produce graphs.
-```{r tf-idf course, cache = TRUE}
-prepare_tf_idf_course <- function(data){
-
-  data %>%
-
-    # Selection 25 courses randomly
-    filter(
-      `Course ID` %in% sample(
-        x = unique(.$`Course ID`),
-        size = 25, 
-        replace = FALSE
-        )
-      ) %>%
-
-    # Select top 10 words per course 
-    group_by(
-      `Course ID`
-      ) %>%
-    filter(
-      n >= 2
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = `Course ID`
-      )
-
-  }
-
-set.seed(123)
-tf_idf$overview %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_overview")
-
-set.seed(123)
-tf_idf$manual %>%
-  prepare_tf_idf_course %>%
-  plot_tf_idf(id_plot = "Course_manual")
-
-rm(prepare_tf_idf_course)
-```
-
-## Cluster Level
-```{r tf-idf cluster, cache = TRUE}
-prepare_tf_idf_cluster <- function(data){
-
-  data %>%
-
-    # Include the variable Cluster
-    left_join(
-      select(d_course, `Course ID`, Cluster),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Cluster)
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Cluster, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10, 
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Cluster
-      )
-
-}
-
-tf_idf$overview %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_overview")
-
-tf_idf$manual %>%
-  prepare_tf_idf_cluster %>%
-  plot_tf_idf(id_plot = "Cluster_manual")
-
-rm(prepare_tf_idf_cluster)
-```
-
-## Concentration Level
-```{r tf-idf concentration, cache = TRUE}
-prepare_tf_idf_concentration <- function(data){
-
-  data %>%
-
-    # Include the variable Concentration
-    left_join(
-      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
-      by = "Course ID"
-      ) %>%
-    filter(
-      !is.na(Concentration)
-      ) %>%
-    gather(
-      key = X,
-      value = Concentration,
-      Concentration, `Concentration (additional)`,
-      na.rm = TRUE
-      ) %>%
-
-    # Select top 10 words per cluster
-    group_by(
-      Concentration, 
-      word
-      ) %>%
-    summarise(
-      tf_idf = sum(tf_idf),
-      n = sum(n)
-      ) %>%
-    filter(
-      n >= 10
-      ) %>%
-    top_n(
-      n = 10,
-      wt = tf_idf
-      ) %>%
-    ungroup %>%
-
-    # Prepare data for function `plot_tf_idf()`
-    rename(
-      facet = Concentration
-      )
-
-}
-
-tf_idf$overview %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_overview")
-
-tf_idf$manual %>%
-  prepare_tf_idf_concentration %>%
-  plot_tf_idf(id_plot = "Concentration_manual")
-
-rm(prepare_tf_idf_concentration, plot_tf_idf)
-```
-
-# LDA
-##Setup
-###Cast DTM
-The function `my_cast_dtm` casts our dataframes (catalogues and manuals) into a DTM.
-```{r my_cast_dtm, eval = TRUE}
-#Function
-my_cast_dtm <- function(data) data %>%
-  count(`Course ID`, word) %>%
-  cast_dtm(`Course ID`, word, n)
-
-#Application
-d_cast <- d_text %>% map(my_cast_dtm)
-
-#Clean workspace
-rm(my_cast_dtm)
-```
-###Controls
-The control parameters we will use to train our LDA model are:
-```{r controls, eval = TRUE}
-my_control <- list(
-
-  nstart = 20,
-  seed   = 1 : 20, #must have length nstart
-  best   = TRUE,
-
-  burnin = 1000,
-  iter   = 6000,
-  thin   = 100
-
-)
-```
-
-We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
-```{r fast control, eval = TRUE}
-my_control_fast <- list(
-
-  nstart = 1,
-  seed   = 1,
-  best   = TRUE,
-
-  burnin = 5,
-  iter   = 10,
-  thin   = 2
-
-)
-```
-
-## Fitting Model
-The function `my_LDA` fits an LDA model on the DTM using the previous controls.
-```{r my_LDA, eval= TRUE}
-my_LDA <- function(n_topics, corpus, control = my_control){
-
-  LDA_model <- LDA(
-    x       = corpus,
-    k       = n_topics,
-    method  = "Gibbs",
-    control = control
-    )
-}
-
-```
-
-###Extracting functions
-The following functions are used as input in a map to compute and evaluate topic models. 
-```{r extracting functions, eval = TRUE}
-#extract dtm
-extract_dtm <- function(origin) d_cast[[origin]]
-
-#extract Distributions (Gamma/Beta)
-get_distributions <- function(model, distrib_str){ #input gamma or beta
-  tidy(model, matrix = distrib_str)        %>%
-    mutate(topic = paste("Topic", topic) ) %>%
-      arrange(topic, desc(!!sym(distrib_str)))
-}
-
-#perplexity Function
-my_perplexity <- function(model, dtm){
-  perplexity(model, dtm, estimate_theta = FALSE)
-}
-
-```
-
-The following functions allow us to inspect the results from our models(inspect distributions and get kw):
-```{r inspection functions, eval = TRUE}
-
-get_top_terms_topic <- function(d_beta){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(10, beta) %>%
-    select(topic, term) %>%
-    group_by(topic) %>%
-    summarise(top_words = list(term))
-
-}
-
-get_top_topics_course <- function(d_gamma){
-  data.frame(d_gamma) %>%
-    group_by(document) %>%
-    top_n(5, gamma) %>%
-    select(document, topic) %>%
-    summarise(top_topic = list(topic))
-}
-
-get_kw <- function(d_beta){
-  data.frame(d_beta) %>%
-    group_by(topic) %>%
-    top_n(3, beta) %>%
-    ungroup()%>%
-    pull(term)%>%
-    unique()
-}
-
-```
-
-###Training Models
-The function `train_topic_model` takes the type of text input ("catalogues", "manuals", c("catalogues", "manuals")) and number of topics to be trained.
-It fits an LDA model on the data and saves the output as a tibble where
-each row corresponds to a number of topics per text input (e.g.
-catalogues_50).
-It saves the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words that will be used for the app.
-
-```{r function train_model, eval = TRUE}
-train_topic_model <- function(which_text, topic_numbers){
-  topic_model <- tibble( 
-    n_topic = rep(topic_numbers, each = length(d_text)) 
-    ) %>%
-
-    mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)), 
-           `Topic ID` = paste(Origin, n_topic, sep = "_"),
-
-           #Document Term Matrix
-           DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%
-
-  filter(Origin %in% which_texts) %>% ######################## was previously == instead of %in%
-
-  mutate(
-         #Fit Model
-         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control
-
-         #Gamma distribution
-         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
-
-         #Beta distribution
-         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
-
-         #Perplexity
-         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
-
-         #Loglikelihood
-         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
-
-         #
-         ##Inspect
-
-         #top words per topic
-         top_terms_topic = map(Beta, .f = get_top_terms_topic),
-
-         #top topics per course
-         top_topic_course = map(Gamma, .f = get_top_topics_course),
-
-         #Select keywords
-         kw = map(Beta, .f = get_kw)
-         )
-}
-
-```
-
-We apply the function separately and take the time it takes to fit the model.
-
-Note: The manuals take a long time to run, we keep the trainings of catalogues and manuals separate so that changes in one do not require retraining the other. 
-####Catalogues
-```{r LDA fit catalogues, cache = TRUE, eval = TRUE}
-#
-## Catalogues
-
-#Input vectors
-which_texts <- "catalogues"
-topic_numbers <-seq(from = 5, to = 200, by = 5)
-
-#Intitial time
-initial_time <- Sys.time()
-
-#Application to catalogues
-catalogues_topic_model <- train_topic_model(which_texts, topic_numbers)
-
-#Final Time
-final_time <- Sys.time()
-took_how_long <- final_time - initial_time
-print(paste(which_texts, took_how_long, sep =" "))
-
-#Save
-save(catalogues_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
-```
-
-####Manuals
-```{r LDA fit manuals, cache = TRUE, evel = TRUE }
-#
-## Manuals
-
-#Input vectors
-which_texts <- "manuals"
-
-#Intitial time
-initial_time <- Sys.time()
-
-#Application to catalogues
-manuals_topic_model <- train_topic_model(which_texts, topic_numbers)  #number of topics stayed the same cause we want to merge them.
-
-#Final Time
-final_time <- Sys.time()
-took_how_long <- final_time - initial_time
-print(paste(which_texts, took_how_long, sep =" "))
-
-#Save
-save(manuals_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
-```
-
-```{r clean workspace functions, eval = TRUE}
-# Clean workspace
-# rm(extract_dtm, get_distributions, my_perplexity,
-#    get_top_terms_topic, get_top_topics_course, get_kw)
-```
-
-If we trained separately and wish to merge into a single tibble: 
-```{r merge if trained separately, eval = TRUE}
-tb_topic_model <- tibble()
-
-if(exists("manuals_topic_model") && exists("catalogues_topic_model")){
-  tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
-} else  if(exists("catalogues_topic_model")){
-  tb_topic_model <- catalogues_topic_model 
-  } else if (exists("manuals_topic_model")){
-    tb_topic_model <- catalogues_topic_model
-}
-
-save(tb_topic_model, file = "./Output/full_topic_model_tibble.RDATA")
-```
-
-##Model Evaluation CHANGE TO CONFERENCE CODE
-###Plots
-To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
-```{r perplexity plots, eval = TRUE}
-#Function
-plot_evaluation <- function(origin, data = tb_topic_model){
-
-  #data
-  data %>%
-
-    #Wrangling
-    select(n_topic, Origin, Perplexity, LogLikelihood) %>%
-    gather(key = "Eval Type", value = "Eval Value", c(Perplexity, LogLikelihood)) %>%
-    filter(Origin == origin) %>%
-
-    #Graphics
-    ggplot(mapping = aes(x = n_topic, y = `Eval Value`)) +
-    geom_point() +
-    geom_line() +
-    facet_grid(rows = vars(`Eval Type`), scales = "free") +
-    theme_minimal()
-
-}
-
-#Plot
-plot_evaluation("catalogues")
-plot_evaluation("manuals")
-```
-
-###Value
-```{r best number of topics extraction}
-n_topics_best_manuals    <- manuals_topic_model    %>% top_n(1, LogLikelihood) %>% pull(n_topic)
-n_topics_best_catalogues <- catalogues_topic_model %>% top_n(1, LogLikelihood) %>% pull(n_topic)
-```
-
-##Best model
-We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
-###catalogues best model
-```{r best catalogues tm, eval = T}
-catalogues_tm <- tb_topic_model %>% filter(Origin == "catalogues")
-
-catalogue_dtm <- catalogues_tm$DTM[[1]]
-
-catalogue_lda <- catalogues_tm %>% filter(n_topic == n_topics_best_catalogues) %>% pull(Model) %>%.[[1]]
-
-#Train best model 
-catalogues_best_lda <- LDA(x = catalogue_dtm, 
-                model = catalogue_lda, 
-                control =  list(
-                  nstart = 50,
-                  seed   = 1 : 50, #must have length nstart
-                  best   = TRUE,
-                  burnin = 100,
-                  iter   = 10000,
-                  thin   = 2000) 
-                )
-
-save(catalogues_best_lda, file = "./Output/catalogues_best_model.RDATA") 
-```
-###manuals best model
-NOTE: BEST MANUALS NUMBER OF TOPICS TO BE DETERMINED 
-```{r best manuals tp, eval = F}
-manuals_tm    <- tb_topic_model %>% filter(Origin == "manuals")
-
-manual_dtm <- manuals_tm$DTM[[1]]
-
-manual_lda <- manuals_tm %>% filter(n_topic == n_topics_best_manuals) %>% pull(Model) %>%.[[1]]
-
-#Train best model
-manuals_best_lda <- LDA(x = manual_dtm, 
-                model = manual_lda, 
-                control =  list(
-                  nstart = 50,
-                  seed   = 1 : 50, #must have length nstart
-                  best   = TRUE,
-                  burnin = 100,
-                  iter   = 10000,
-                  thin   = 2000) 
-                )
-
-save(manuals_best_lda, file = "./Output/manuals_best_model.RDATA") 
-```
-
-##Best model pass to app
-```{r load best models, eval = F}
-load("./Output/full_topic_model_tibble.RDATA") #contains both manuals and catalogues
-
-#Alternatively:
-#load("./Output/catalogues_topic_model_tibble.RDATA")
-
-#Best models:
-load("./Output/catalogues_best_model.RDATA")
-load("./Output/manuals_best_model.RDATA")
-```
-
-```{r best models clean for app, eval = TRUE}
-#helper function
-get_best_lda <- function(Origin){
-  if(Origin == "catalogues"){
-
-    return (catalogues_best_lda[[1]])
-
-  } else if(Origin == "manuals"){
-
-      return(manuals_best_lda[[1]])
-    }
-}
-
-best_model <- tibble( 
-  n_topic = c(n_best_catalogues, n_best_manuals)
-  ) %>%
-
-  mutate(Origin     = c("catalogues", "manuals"),
-         `Topic ID` = paste(Origin, n_topic, sep = "_"),
-
-         #Document Term Matrix
-         DTM        = pmap(.l = list(Origin), .f = extract_dtm),
-
-         #Fit Model
-         Model  = pmap(.l = list(Origin), .f = get_best_lda),
-
-         #Gamma distribution
-         Gamma = pmap(.l = list(Model), .f = get_distributions, distrib_str = "gamma"),
-
-         #Beta distribution
-         Beta = pmap(.l = list(Model),  .f = get_distributions, distrib_str = "beta"),
-
-         #Perplexity
-         Perplexity = pmap_dbl(.l = list(Model, DTM), .f = my_perplexity),
-
-         #Loglikelihood
-         LogLikelihood = pmap_dbl(.l = list(Model), .f = logLik), #this removes the degrees of freedom data
-
-         #
-         ##Inspect
-
-         #top words per topic
-         top_terms_topic = map(Beta, .f = get_top_terms_topic),
-
-         #top topics per course
-         top_topic_course = map(Gamma, .f = get_top_topics_course),
-
-         #Select keywords
-         kw = map(Beta, .f = get_kw)
-         )
-
-```
-
-###Save best model
-```{r save best model, eval = TRUE}
-save(best_model, file = "./Output/best_model.RDATA")
-```
-
-#App
-For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
-##Distributions and Key words
-The function `clean_kw` removes stopwords from our key words.
-```{r function clean key words, eval = TRUE}
-clean_kw <- function(kw_list){
-
-  #stopwords
-  kw_stopwords <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
-                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", "identify", "manner", "mechanism", "concept", "hour",
-                 "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text",
-                 "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study", "task")
-
-  #remove stopwords
-  kw <- setdiff(kw_list, kw_stopwords)
-  #return
-  return(kw[!is.na(kw)])
-
-}
-
-```
-On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
-```{r crop and clean TM for App, eval = TRUE }
-app_topic_model <- best_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
-  mutate(kw = map(kw, .f = clean_kw))
-```
-
-##Convenience Vectors
-For the app we also need to have a list of all courses and an example of a prospective semester
-```{r for convenience, eval = TRUE}
-# set seed
-set.seed(1)
-
-#
-## All courses
-course_all <- d_course %>%
-  inner_join(
-    d_transcript,
-    by = "Course ID"
-  ) %>%
-  distinct(
-    `Course ID`
-  ) %>%
-  # remove semester abroad, skills and projects
-  filter(
-    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
-  ) %>%
-  pull
-
-#
-##courses following_semester
-course_following_semester <- sample(x = course_all,
-                                    size    = 60,
-                                    replace = FALSE) %>% sort()
-
-```
-
-```{r adding convenience vectors, eval = TRUE}
-app_model <- app_topic_model %>%
-  mutate(`All Courses`     = list(course_all),
-         `Sample semester` = list(course_following_semester),
-         `Course Titles`   = list(course_titles) )
-
-#rm(course_all, course_following_semester)
-```
-## Saving files for APP
-```{r app files, eval = TRUE}
-save(app_model, file = "App/Recommender System/app_model.RDATA")
-save(app_model, file = "./Output/app_model.RDATA")
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:9234c8e0c390f24316d810502978cea0881750026150e2ff042bc8048f64367a
+size 21655

### 2019-06-27 App/Recommender System/server.R

@@ -1,615 +1,3 @@
-library(tidyverse)
-library(tidytext)
-library(stringr)
-library(hunspell) #for stemming
-library(glmnet)   #for grade prediction
-library(seewave)# KL distance
-
-
-#
-#General set up ---------------------------------------------------------------------------------
-load("data_pillar_1.RDATA")
-load("app_model.RDATA") #contains app_model and full dataframe of topic models
-load("rules_clean.RDATA")
-load("grade_prediction.RDATA")
-load("student_TP.RDATA")
-load("d_text.RDATA")
-
-course_all <- app_model$`All Courses`[[1]]
-course_advanced <- course_all[!str_detect(course_all,"HUM10|SCI10|SSC10")]
-kw_used <- app_model$kw[[1]] #is the same as in ui
-
-titles <-  d_text$catalogues %>%
-  select(`Course ID`, `Course Title`, department) %>% 
-  distinct %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
-                                           T ~ `Course Title`),
-                      `Course_id` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
-                                              T ~ "XXX0000")) %>% 
-  transmute(`Course ID` = `Course ID`, course_and_title = paste(`Course_id`, `c_title`, sep = " - "))
-
-# titles <-  d_text$catalogues %>%
-#   select(`Course ID`, `Course Title`, department) %>% 
-#   distinct %>% transmute(`Course ID`= `Course ID`,
-#                          c_title= case_when(is.na(`Course Title`) ~ `Course ID`,
-#                                             T ~ `Course Title`))
-
-#
-#server ---------------------------------------------------------------------------------
-function(input, output, session) {
-  
-  # ---------------------------------------------------------------------------------
-  ## -- RED FLAGS --
-  # ---------------------------------------------------------------------------------
-  
-  ##Set up
-  
-  #Raw Data for RS:
-  raw_rules <- rules_clean %>%
-    select(-rules_rules)   %>%
-    filter(type_rule == "SR")
-  
-  #Helper function: return tibble of type_rules
-  get_type_rules <-  function(type) {
-    tmp <- raw_rules %>%
-      filter(ID == type) %>%
-      pull(rules_RS)
-    
-    return(tmp[[1]])
-  }
-  
-  #Helper: resettabe input
-  output$resetable_input <- renderUI({
-    times <- input$reset_input
[…]

### 2019-06-27 App/Recommender System/ui.R

@@ -1,182 +1,3 @@
-library(tidyverse)
-library(tidytext)
-library(shiny)
-library(shinythemes)
-
-#
-#General set up---------------------------------------------------------------------------------
-
-load("data_pillar_1.RDATA")
-load("app_model.RDATA") #contains distribution, kw, course_all, course_following_semester.
-load("rules_clean.RDATA")
-
-kw_used <- app_model$kw[[1]]
-
-#
-# ui ---------------------------------------------------------------------------------
-navbarPage(
-  theme = shinytheme("united"),
-  
-  # App title
-  title = "Recommender System",
-  
-  # ---------------------------------------------------------------------------------
-  # -- RED FLAGS --
-  # ---------------------------------------------------------------------------------
-  
-  tabPanel(
-    
-    # Panel Title
-    title = "Red Flag",
-    
-    # Sidebar layout
-    sidebarLayout(
-      
-      # Sidebar panel for inputs
-      sidebarPanel(
-        
-        # Input: student id number
-        textInput(
-          inputId = "student",
-          label   = "Student ID",
-          value   = "6113335"
-          ),
-        
-        uiOutput('resetable_input'),
-        tags$head(tags$style("#resetable_input{color: black; font-size: 14px;}")),
-        tags$hr(),
-        actionButton("reset_input", "Reset inputs")
-        
-        ),
-      
-      # Main panel for displaying outputs
-      mainPanel(
-        
-        # Output: dataset
-        tableOutput(
-          outputId = "red_flags"
-          ),
-        tags$head(tags$style("#red_flags{color: black; font-size: 20px;}"))
-        
-        )
-      
-      )
-    
-    ),
-  
-  # ---------------------------------------------------------------------------------
-  # -- TRAFFIC LIGHTS --
-  # ---------------------------------------------------------------------------------
-  
-  tabPanel(
-    
-    # Panel Title
-    title = "Traffic Lights",
-    
-    # Sidebar layout
-    sidebarLayout(
-      
-      # Sidebar panel for inputs
-      sidebarPanel(
-        
-        # Input: student id number
-        textInput(
-          inputId = "student_traffic",
-          label   = "Student ID",
-          value   = "6113335"
-        ),
-        
-        uiOutput('resetable_input_traffic'),
-        tags$head(tags$style("#resetable_input_traffic{color: black; font-size: 19px;}")),
-        tags$hr(),
-        actionButton("reset_input_traffic", "Reset inputs")
-        
-      ),
-      
[…]

### 2019-06-27 Output/Plots/Plots.R

@@ -1,74 +1,3 @@
-load("Output/data_pillar_1.RDATA")
-library(tidyverse)
-
-# Set up
-height <- 4; width <- height * 1.6
-theme_set(theme_light())
-
-# Student transcript
-student_ID <- "6087587"
-
-transcript <- d_transcript_augmented %>%
-  
-  mutate(Cluster = factor(Cluster)) %>%
-  
-  filter(`Student ID` == student_ID)
-
-
-# Aod & Assessment
-
-my_barplot_AoD <- function(transcript, var){
-  
-  transcript %>%
-    
-    filter(! is.na(!!ensym(var))) %>%
-    
-    pull(!!ensym(var)) %>% 
-    
-    str_c(collapse = ", ") %>%
-    
-    str_split(", ") %>% .[[1]] %>%
-    
-    tibble(AoD = .) %>%
-    
-    ggplot(aes(reorder(AoD, AoD, function(x) length(x)))) +
-    geom_bar() +
-    coord_flip() +
-    labs(title = var, x = NULL)
-  
-}
-
-my_barplot_AoD(transcript, "AoD Covered")
-ggsave("AoD.jpeg", path = "Output/Plots", width = width, height = height)
-
-my_barplot_AoD(transcript, "Assessments Covered")
-ggsave("Assessment.jpeg", path = "Output/Plots", width = width, height = height)
-
-
-## Profile: cluster & concentration
-
-my_barplot_concentration <- function(transcript, var){
-  
-  transcript  %>%
-    
-    filter(! is.na(!!ensym(var)), ! is.na(Level)) %>%
-    
-    ggplot(aes(!!ensym(var), fill = Level)) +
-    
-    geom_bar(col = "black") +
-    
-    facet_grid(Year_numerical ~ .) + 
-    
-    scale_x_discrete(drop = FALSE) + 
-    scale_fill_discrete(drop = FALSE) +
-    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
-    labs(title = "Student's Courses", x = NULL)
-
-}
-
-my_barplot_concentration(transcript, "Concentration")
-ggsave("concentration.jpeg", path = "Output/Plots", width = width, height = height)
-
-my_barplot_concentration(transcript, "Cluster")
-ggsave("Cluster.jpeg", path = "Output/Plots", width = width, height = height)
-
+version https://git-lfs.github.com/spec/v1
[…]

### 2019-06-27 Output/SearchK.R

@@ -1,0 +1,3 @@
+version https://git-lfs.github.com/spec/v1
+oid sha256:8530eedfb0efa02e876686aea8edafe32f936e65036e2198fbadaed723c7dbbb
+size 3546

### 2019-06-27 test-app.R

@@ -1,193 +1,3 @@
-library(tidyverse)
-library(tidytext)
-library(stringr)
-library(hunspell) #for stemming
-library(glmnet)   #for grade prediction
-
-
-#
-#General set up ---------------------------------------------------------------------------------
-load("./App/Recommender System/data_pillar_1.RDATA")
-load("./App/Recommender System/data_topic_models.RDATA") #contains app_model and full dataframe of topic models
-load("./App/Recommender System/rules_clean.RDATA")
-load("./App/Recommender System/grade_prediction.RDATA") 
-load("./App/Recommender System/student_TP.RDATA")
-###Set up
-use_past <- T
-
-# Helper function: Return student
-student_courses <- function(d_student) {
-  student_hist <- d_transcript %>%
-    
-    filter(
-      `Student ID` == d_student
-    ) %>%
-    
-    select(
-      course = `Course ID`
-    ) 
-}
-
-student_topics <- function(d_student){
-  
-   student_TP %>% filter(`Student ID` == d_student) %>% top_n(1, time) %>%
-    select(-time, -`Student ID`) %>%
-    gather(key = topic, value = weight) %>%
-    mutate(topic = str_replace(topic, "_", " "),
-    weight = weight/sum(weight))
-    
-}
-
-#Reactive student function 
-student_past <- student_courses("6113335")
-
-student_tp <- student_topics("6113335")
-
-#recommendations
-  beta_distribution  <- app_model$Beta[[1]] 
-  gamma_distribution <- app_model$Gamma[[1]] 
-  course_titles      <- app_model$`Course Titles`[[1]]
-  
-  # Key words
-  key_words_additional <- c("student", "economic")
-  
-  
-  stem_hunspell <- function(term) {
-    
-    stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
-    n_stems <- length(stems)            # number of stems
-    
-    if (n_stems == 0) term              # if no stems, return original term
-    else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
-    
-  }
-  
-  
-  key_words_additional <- sapply(key_words_additional, stem_hunspell)
-
-  kw_used <- app_model$kw[[1]] #is the same as in ui
-  
-  with_guess <- student_tp %>% 
-    top_n(10, weight) %>%
[…]

### 2019-06-27 Pillar 1 - Sequential Pattern Mining.Rmd

--- 2019-03-21 Pillar 1 - Sequential Pattern Mining.Rmd
@@
----
-title: "Pillar 1 - Sequential Pattern Mining"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(cache.path = "Cache/Pillar 1/")
-
-library(tidyverse)
-library(arulesSequences)
-library(magrittr)
-```
-
-TODO: simplify support into one df: var1 = course id, var2 = type, var3 = rate
-
-AR with not taken on lhs is not useful.
-
-# Set up
-We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
-```{r loading data}
-load("Output/data_pillar_1.RDATA")
-```
-
-```{r helper function}
-paste_ <- function(...) paste(..., sep = "_")
-```
-
-```{r constants}
-course_all  <- unique(d_transcript_informative$`Course ID` )
-student_all <- unique(d_transcript_informative$`Student ID`)
-n_students  <- length(student_all)
-
-pass_grade <- 5.5
-high_grade <- 6.5
-```
-
-# Descriptive statistics
-We compute summary statistics (minimum, maximum, mean, median, standard deviation, failure rate, number of failure and count) at different levels (student, course, cluster, concentration, year and course level).
-We save the results in the environment `Transcript Statistics`.
-
-```{r provide_statistics}
-# helper function
-provide_statistics <- function(var, df = d_transcript_augmented, high_gr = high_grade, pass_gr = pass_grade){
-
-  df %>%
-
-    filter(!is.na(!!enquo(var))) %>%
-
-    group_by(!!enquo(var)) %>%
-
-    summarise(
-      Count           = n(),
-      Min             = min   (Grade),
-      Max             = max   (Grade),
-      Mean            = mean  (Grade),
-      Median          = median(Grade),
-      IQR             = IQR   (Grade),
-      SD              = sd    (Grade),
-      `Low Rate`      = mean  (Grade < high_grade),
-      `Fail Rate`     = mean  (Grade < pass_grade)
-      ) %>%
-
-    mutate_if(is.numeric, round, digits = 2)
-
-}
-```
-
-```{r statistics}
-statistics <- list()
-
-# Student level
-statistics$student <- provide_statistics(`Student ID`)
-
-# Course level
-statistics$course  <- provide_statistics(`Course ID`)
-
-# Cluster level
-statistics$cluster <- provide_statistics(Cluster)
-
-# Type level
-statistics$type    <- provide_statistics(Type)
-
-# Concentration level
-statistics$concentration <- d_transcript_augmented %>%
-  gather(
-    key = X, 
-    value = Concentration, 
-    Concentration, `Concentration (additional)`,
-    na.rm = TRUE
-    ) %>%
-  provide_statistics(Concentration, df = .)
-
-# Year level
-statistics$year <- provide_statistics(`Academic Year`)
-
-# Level level
-statistics$level <- provide_statistics(Level) # TODO: filter for student who completed their studies
-```
-
-```{r save statistics, include = FALSE}
-save(statistics, file = "Output/Transcript Statistics.RDATA")
-rm(statistics, provide_statistics)
-```
-
-# Support
-```{r d_support TNT}
-d_support <- list()
-
-# Probability of taking / failing / obtaining of low grade a course
-d_support$TPH <- d_transcript_informative %>%
-
-  group_by(`Course ID`) %>%
-
-  summarise(
-    rate.take = n_distinct(`Student ID`) / n_students,
-    rate.fail = mean(Grade < pass_grade),
-    rate.low  = mean(Grade < high_grade)
-    )
-```
-
-```{r d_support G}
-d_support$G <- d_transcript_informative %>%
-
-  group_by(`Course ID`) %>%
-
-  summarise(
-    `0`    = mean(Grade <= 0),
-    `1`    = mean(Grade <= 1),
-    `2`    = mean(Grade <= 2),
-    `3`    = mean(Grade <= 3),
-    `4`    = mean(Grade <= 4),
-    `5`    = mean(Grade <= 5),
-    `6`    = mean(Grade <= 6),
-    `7`    = mean(Grade <= 7),
-    `8`    = mean(Grade <= 8),
-    `9`    = mean(Grade <= 9),
-    `10`   = mean(Grade <= 10)
-  ) %>%
-
-  gather(grade_ceil, rate.grade, `0` : `10`, convert = TRUE)
-```
-
-# transactions and sequences
-For a first exploration of arules, we conceptualise our framework like this:
-transaction = student
-item = course
-
-First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.
-
-```{r d_transactions}
-d_transactions <- list()
-```
-
-## taken_PF_HL
-```{r taken_PF_HL}
-d_transactions$taken_PF_HL <- d_transcript_informative %>%
-
-  # sequenceID and event ID
-  rename(
-    sequenceID = `Student ID`,
-    eventID = time
-    ) %>%
-
-  # itemID
-  mutate(
-    item    = `Course ID`,
-    item_PF = if_else(Grade >= pass_grade, paste_(item, "pass"), paste_(item, "fail")),
-    item_HL = if_else(Grade >= high_grade, paste_(item, "high"), paste_(item, "low" ))
-    )
-```
-
-## T_PF_HL (not taken pass/fail high/low)
-```{r T_PF_HL}
-d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%
-
-  # Expand along students (sequenceID) and courses (itemID) to make missing combinations of student - course explicit
-  complete(sequenceID, item) %>%
-
-  # create a new type of item: "not taken"
-  mutate(
-    item_TPF = if_else(is.na(item_PF), paste_(item, "not"), item_PF),
-    item_THL = if_else(is.na(item_HL), paste_(item, "not"), item_HL)
-    )
-```
-
-## Grade
-```{r transactions grade}
-d_transactions$G <- d_transactions$taken_PF_HL %>%
-
-  mutate(row_of_origin = TRUE) %>%     # non-missing row_of_origin are TRUE
-
-  complete(
-    nesting(sequenceID, eventID, item, Grade), grade_ceil,
-    fill = list(row_of_origin = FALSE) # missing row_of_origin are FALSE
-    ) %>%
-
-  group_by(sequenceID, eventID, item, Grade) %>%
-
-  distinct(sequenceID, eventID, item, grade_ceil, Grade, row_of_origin) %>% # reminder that we should get rid of duplicates oin d_transcript
-
-  arrange(grade_ceil) %>%
-
-  filter(cumany(row_of_origin)) %>% # only keep grades larger than ceil_grade
-
-  mutate(item_g = paste_(item, grade_ceil)) %>%
-
-  ungroup()
-```
-
-## making transactions and sequence
-```{r make_transaction}
-make_transaction <- function(data, item){
-
-  data %>%
-
-    group_by(sequenceID) %>%
-    summarise(list_item = list(unique(!!item))) %>%
-    ungroup %$%
-
-    as(list_item, "transactions")
-
-}
-```
-
-```{r make_sequence}
-make_sequence <- function(ID, data, item){
-
-  if(ID %in% c("TPF", "THL")) return("Compute sequences including courses not taken yet by hand")
-
-  data_temp <- data %>%
-
-    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.
-
-    arrange(sequenceID, eventID) %>%
-    group_by(sequenceID, eventID) %>%
-    summarise(list_item = list(unique(!!enquo(item)))) %>%
-    ungroup
-
-  # extract transactions
-  sequences <- data_temp %>% pull(list_item) %>% as("transactions")
-
-  # add attributes fro sequence ID and event ID
-  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame
-
-  return(sequences)
-
-}
-```
-
-```{r data_general}
-data_general <- tribble(
-  ~ ID   ,  ~ data                   , ~ item         , ~ data_support, ~ var_support    , ~ suffix_lhs , ~ suffix_rhs ,
-  "taken", d_transactions$taken_PF_HL, sym("item"    ), d_support$TPH , sym("rate.take" ), NA_character_, NA_character_,
-  "PF"   , d_transactions$taken_PF_HL, sym("item_PF" ), d_support$TPH , sym("rate.fail" ), "fail"       , "fail"       ,
-  "HL"   , d_transactions$taken_PF_HL, sym("item_HL" ), d_support$TPH , sym("rate.low"  ), "low"        , "low"        ,
-  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"), d_support$TPH , sym("rate.fail" ), "not"        , "fail"       ,
-  "THL"  , d_transactions$T_PF_HL    , sym("item_THL"), d_support$TPH , sym("rate.low"  ), "not"        , "low"        ,   
-  "G"    , d_transactions$G          , sym("item_g"  ), d_support$G   , sym("rate.grade"), "_7"         , "_7"
-  )
-```
-
-```{r transactions sequences}
-data_general <- data_general %>%
-
-  mutate(
-    transactions = list(    data, item) %>% pmap(make_transaction),
-    sequences    = list(ID, data, item) %>% pmap(make_sequence)
-    ) %>%
-
-  select(-data) # for memory requirement
-
-arules::inspect(head(data_general$transactions[[3]], 10))
-arules::inspect(head(data_general$sequences   [[3]], 10))
-```
-
-# Transcript with preceding courses
-```{r d_transcript_cum, cache = TRUE}
-d_transcript_cum <- d_transactions$taken_PF_HL %>%
-
-  # item_take
-  mutate(item_take = paste_(item, "take")) %>%
-
-  # current courses
-  group_by(sequenceID, eventID) %>%
-
-  summarize_at(vars(matches("item")), ~ unique(.) %>% list) %>%
-
-  mutate(course_current = list(item, item_take, item_PF, item_HL) %>% pmap(~ c(...) %>% unique)) %>%
-
-  # courses so far, past courses and course not taken yet
-  group_by(sequenceID) %>%
-
-  arrange(eventID) %>%
-
-  mutate(
-    course_so_far  = course_current %>% accumulate(union),
-    course_past    = course_so_far  %>% lag(default = NA_character_),
-    course_not_yet = course_past    %>% map(~ setdiff(course_all, .) %>% paste_("not"))
-    ) %>%
-
-  ungroup %>%
-
-  # lhs: past courses and courses not taken yet, rhs: current courses
-  mutate(
-    lhs = list(course_past, course_not_yet) %>% pmap(union),
-    rhs = course_current
-    ) %>%
-
-  select(lhs, rhs) # for memory requirement
-```
-
-```{r, include = FALSE}
-rm(
-  high_grade, pass_grade, course_all, student_all,
-  make_transaction, make_sequence
-  )
-```
-
-# Mining Rules
-
-## Helper functions
-
-```{r}
-count_min   <- 1
-support_min <- count_min / n_students
-
-confidence_min <- 1e-3
-```
-
-```{r separate_lhs}
-separate_lhs <- function(df) df %>% separate(col = lhs , into = c("lhs_course", "lhs_outcome"), remove  = FALSE, convert = TRUE)
-```
-
-```{r separate_rhs}
-separate_rhs <- function(df) df %>% separate(col = rhs , into = c("rhs_course", "rhs_outcome"), remove  = FALSE, convert = TRUE)
-```
-
-```{r choose_lhs}
-choose_lhs <- function(rules, suffix) rules %>% filter(str_detect(lhs, suffix))
-```
-
-```{r choose_rhs}
-choose_rhs <- function(rules, suffix) rules %>% filter(str_detect(rhs, suffix))
-```
-
-### Aprior, CSPADE and rule induction
-
-The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
-```{r my_apriori}
-my_apriori <- function(data, supp_min = support_min, conf_min = confidence_min){
-
-  data %>%
-
-    apriori(
-
-      # include all AR possible
-      parameter = list(
-        supp   = supp_min, # min support
-        smax   = 1, # max support
-        conf   = conf_min, # min confidence
-        minlen = 2, # min length of rule
-        maxlen = 2  # max length of rule
-        ),
-
-      # no printing during execution
-      control = list(verbose = FALSE)
-
-      )
-
-}
-```
-
-The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
-```{r my_cspade function}
-my_cspade <- function(data, supp_min = support_min){
-
-  data %>%
-
-    cspade(
-
-      parameter = list(
-
-        # only include subsequences of the type {one item} => {one item}
-        maxlen  = 2,   # max length of sequence
-        maxsize = 1,   # max number item for element
-
-        # include all such subsequences
-        support = supp_min,   # min suppor
-        mingap  = 1,   # min time difference between consecutive element
-        maxgap  = 1e4  # max time difference between consecutive element
-
-        ),
-
-      control = list(verbose = FALSE)
-
-      )
-
-}
-```
-
-The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
-```{r my_ruleInduction}
-my_ruleInduction <- function(rules, conf_min = confidence_min){
-
-  rules %>% ruleInduction(confidence = conf_min, control = list(verbose = FALSE))
-
-}
-```
-
-### Separate rules
-The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
-```{r separate_rule}
-separate_rule <- function(rules){
-
-  rules %>%
-
-    as("data.frame") %>%
-
-    # separate rule
-    rename_at(vars(matches("rule")), ~ substr(., 1, 4)) %>%
-
-    mutate(rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")) %>%
-
-    separate(col = rule, into = c("lhs", "rhs"), sep = " = ") %>%
-
-    # separate lhs and rhs
-    separate_lhs %>%
-    separate_rhs
-
-}
-```
-
-### Compute metrics
-
-```{r}
-compute_count <- function(rules) rules %>% mutate(count = support * n_students)
-```
-
-```{r compute_rhs.support}
-compute_rhs.support <- function(rules, ID, data_support, var_support){
-
-  if(ID == "G") by_var <- c("rhs_course" = "Course ID", "rhs_outcome" = "grade_ceil")
-  else          by_var <- c("rhs_course" = "Course ID"                              )
-
-  rules %>%
-
-    left_join(data_support, by = by_var) %>%
-
-    mutate(rhs.support = !!enquo(var_support)) %>%
-
-    select(- matches("rate"))
-
-}
-```
-
-```{r compute_lhs.rhsTake}
-compute_lhs.rhsTake <- function(rules, ID){
-
-  if(ID == "G") rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = max(support)) %>% ungroup
-  else          rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = sum(support)) %>% ungroup
-
-  rules %>% mutate(lhs.rhsTake.count = lhs.rhsTake.support * n_students)
-
-}
-```
-
-```{r compute_confidence}
-compute_confidence <- function(rules, ID){
-
-  if(ID != "taken") rules <- rules %>% mutate(confidence = support / lhs.rhsTake.support)
-
-  rules
-
-}
-```
-
-```{r compute_lift}
-compute_lift <- function(rules) rules %>% mutate(lift = confidence / rhs.support)
-```
-
-```{r compute_metrics}
-compute_metrics <- function(rules, ID, data_support, var_support){
-
-  rules %>% # rules with support
-
-    compute_count %>%
-
-    compute_rhs.support(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
-
-    compute_lhs.rhsTake(ID = ID) %>%
-
-    compute_confidence(ID = ID) %>%
-
-    compute_lift %>%
-
-    arrange(desc(support))
-
-}
-```
-
-### informative_rules
-```{r informative_rules}
-informative_rules <- function(rules, ID, suffix_lhs, suffix_rhs){
-
-  if(ID != "taken") rules <- rules %>% choose_lhs(suffix_lhs) %>% choose_rhs(suffix_rhs)
-
-  rules %>% filter(lhs_course != rhs_course)
-
-}
-```
-
-## make_AR, make_SR (wrapers)
-We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
-```{r make_AR_regular}
-make_AR <- function(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs){
-
-  transactions %>%
-
-    my_apriori %>%
-
-    separate_rule %>%
-
-    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
-
-    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)
-
-}
-```
-
-We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
-```{r make_SR_regular}
-make_SR_regular <- function(sequences){
-
-  sequences %>%
-
-    my_cspade %>%
-
-    my_ruleInduction %>%
-
-    separate_rule
-
-}
-```
-
-```{r make_SR_TPF_THL}
-make_SR_TPF_THL <- function(ID){
-
-  if(ID == "TPF") suffix_rhs_take <- "pass|fail"
-  else            suffix_rhs_take <- "low|high"
-
-  d_transcript_cum %>%
-
-    # unnest rhs first for memory requirement
-
-    # rhs
-    unnest(rhs, .drop = FALSE) %>% 
-    choose_rhs(suffix_rhs_take) %>% # keep both pass & fail, or high & low, to compute support support.lhs_rhsTake
-
-    # lhs
-    unnest(lhs, .drop = FALSE) %>% 
-    choose_lhs("not") %>%
-    separate_lhs %>%
-
-    # rule support
-    count(lhs, rhs) %>%
-    rename(count = n) %>%
-    mutate(support = count / n_students) %>%
-
-    separate_lhs %>%
-    separate_rhs
-
-}
-```
-
-```{r make_SR}
-make_SR <- function(ID, sequences, data_support, var_support, suffix_lhs, suffix_rhs){
-
-  if(ID %in% c("TPF", "THL")) sequences <- make_SR_TPF_THL(ID = ID)
-  else                        sequences <- make_SR_regular(sequences)
-
-   sequences %>%
-
-    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%
-
-    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)
-
-}
-```
-
-## Mine Rules
-We apply `make_AR` to get different sets of rules:
-
-```{r make rules}
-data_general <- data_general %>%
-
-  mutate(
-    AR = list(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_AR),
-    SR = list(ID, sequences   , data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_SR)
-    )
-```
-
-```{r gather data_general}
-rules_clean <- data_general %>%
-
-  gather(key = type_rule, value = rules, AR, SR) %>%
-
-  select(ID, type_rule, rules)
-```
-
-# Editing Rules
-
-The function edit_rules makes AR easier to read.
-It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
-
-## App - Recommender System
-
-```{r edit_RS}
-edit_RS <- function(rules){
-
-  rules %>%
-
-    filter(
-       count      >= 20,
-       lift       >  1,
-       confidence >= 0.4
-       )
-
-}
-```
-
-```{r rules_RS}
-rules_clean <- rules_clean %>% mutate(rules_RS = rules %>% map(edit_RS))
-```
-
-## App - Rules
-
-```{r edit_rules}
-edit_rules <- function(rules){
-
-  rules %>%
-
-    select(
-      lhs, rhs,
-      matches("rhsTake.count"), count,
-      matches("rhsTake.support"),
-      confidence,
-      support, 
-      lift
-      ) %>%
-
-     mutate_if(
-       is.numeric,
-       round,
-       digits = 3
-       ) %>%
-
-    arrange(desc(count))
-
-}
-```
-
-```{r rules_rules}
-rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
-```
-
-```{r save rules_clean}
-save(rules_clean, file = "App/rules_clean.RDATA")
-```
-
-```{r save data_general}
-save(data_general, file = "Output/rules.RDATA")
-```
-
-```{r print SR}
-print(rules_clean$rules_RS[[10]])
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:cbd64e59d4e605c0dce7d80ed10a84c5e2bf1f58ea162c0b77fc0b3105069eb8
+size 17698

### 2019-06-27 conference figures COPA2019.Rmd

--- 2019-05-15 conference figures COPA2019.Rmd
@@
----
-title: "Figures for conference paper"
-author: "DARS"
-date: "`r Sys.Date()`"
-output: 
-  github_document:
-    toc: TRUE
-editor_options: 
-  chunk_output_type: console
----
-
-# Set up
-
-```{r setup, include = FALSE}
-library(tidyverse)
-library(kableExtra)
-library(DiagrammeR)
-
-knitr::opts_chunk$set(echo = FALSE)
-theme_set(theme_light())
-
-load("Output/app_model.RDATA")
-load("Output/data_pillar_1.Rdata")
-load("Output/d_text.RDATA")
-load("Output/df_logLike_catalogue.RDATA")
-load("Output/CV.RDATA")
-
-output_folder <- "Conference/COPA2019/paper/figures"
-plot_width <- 6
-plot_height <- plot_width / 1.6 
-```
-
-```{r TM}
-gamma <- app_model$Gamma[[1]]
-beta  <- app_model$Beta[[1]]
-```
-
-```{r student_data}
-set.seed(2019)
-
-student_data <- d_transcript_augmented %>%
-
-  select(`Student ID`, `Course ID`, `Academic Year`, Period = period_numerical, Grade) %>%
-
-  mutate(`Student ID` = ((as.numeric(`Student ID`) + 2019) * as.numeric(`Student ID`)) %% 1e5  %>% as.character) %>% # anonymization
-
-  sample_n(10) %>%
-
-  arrange(`Academic Year`) %>%
-
-  print
-```
-
-```{r}
-course_data <- d_text$catalogues %>%
-
-  slice(50005:50014) %>%
-
-  select(`Course ID`, `Course Title`, Department = department, word) %>%
-
-  print
-```
-
-# Student data
-
-```{r}
-latex_table <- function(df, filename = "test"){
-
-  df %>%
-    kable("latex", booktabs = TRUE, align = "c") %>%
-    write(file = str_c(output_folder, "/", filename, ".txt"))
-}
-```
-
-```{r fig_student_data}
-student_data %>% latex_table("data-student")
-```
-
-# Course data
-
-```{r fig_course_data}
-course_data %>% latex_table("course-student")
-```
-
-# Flow chart
-
-```{r}
-grViz("digraph flowchart{
-
-      fontname = Helvetica
-      size = 15
-
-      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]
-
-      edge [fontname = Helvetica, decorate = TRUE]
-
-      subgraph cluster_input {
-		  color = white;
-
-      subgraph cluster_data {
-      label = 'Data';
-      style = filled;
-		  color = lightgrey;
-		  node [shape = cylinder];
-      CD [label = 'Course Data']
-      SD [label = 'Student Data']
-      }
-
-      subgraph cluster_input_user {
-      label = 'User Input';
-      style = filled;
-		  color = coral;
-
-      ID [label = 'Student ID']
-      KW [label = 'Selected Key Words']
-      CS [label = 'Selected Courses']
-      }
-
-      } #close input subgraph
-
-      subgraph cluster_model_fitting{
-      label = 'Model Fitting';
-      style = filled;
-		  color = LavenderBlush;
-
-      SM [label = 'Student Model']
-
-      PM [label = 'Predictive Models']
-      x1 [shape = circle, width = .01, height = .01, label = '']
-      TM [label = 'Topic Model']
-
-      }
-
-      subgraph cluster_inter_last{
-      label = 'Intermediate Results';
-      style = filled;
-		  color = Tan;
-
-      GP [label = 'Grade Prediction']
-      AI [label = 'Student´s Academic Interests']
-      }
-
-      # Ouput
-      subgraph cluster_ouput {
-      label = 'System Output';
-      style = filled;
-		  color = lightCyan;
-
-      SUG [label = 'Course Suggestions']
-      PR [label = 'Prediction Region']
-      }
-
-      TR [label = 'Student´s Transcript']
-
-      # Invisible node
-      x2 [shape = circle, width = .01, height = .01, label = '']
-      x3 [shape = circle, width = .01, height = .01, label = '']
-
-      # edges
-
-      {SD, TM} -> SM;
-      {TM, KW} -> AI;
-      ID -> TR;
-      {PM, CS, TR} -> GP;
-      GP -> PR [label = '  Conformal Prediction'];
-
-      CD -> TM [label = '  LDA'];
-
-      SM -> PM [label = '  Lasso'];
-
-      {TM, AI} -> x2 [arrowhead = none]
-      x2 -> SUG [label = '  KL distance'];
-
-      }
-      ")
-
-# Save by hand
-# File name: Conference/COPA2019/paper/figures/flowchart
-```
-
-# Model Selection (topic model)
-
-```{r}
-max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]
-
-df_logLike_catalogue %>%
-  ggplot(aes(x = n_topic, y = LogLikelihood)) +
-  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
-  geom_line(linetype = "dashed") +
-  geom_point() +
-
-  labs(title = NULL, subtitle = NULL, x = "Number of Topics", y = "Log-Likelihood") +
-
-  ggsave(filename = str_c("Model Selection.jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-```
-
-# Beta
-
-```{r plot_beta}
-plot_beta <- function(topic = 1, resize_factor = 1){
-
-  top <-  str_c("Topic ", topic)
-
-  beta %>%
-    filter(topic == top) %>% 
-    top_n(10, beta) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(term, beta), y = beta)) +
-
-    coord_flip() +
-
-    theme(axis.text.y = element_text(size = 11)) +
-
-    labs(title = NULL,
-         x = "Terms",
-         y = "Beta"
-         )
-
-  ggsave(filename = str_c("Beta-", topic, ".jpeg"), path = output_folder,
-         width = plot_width / resize_factor, height = plot_height / resize_factor)
-
-}
-```
-
-# Gamma
-
-```{r plot_gamma}
-plot_gamma <- function(course = "COR1002"){
-
-  gamma %>%
-    filter(document == course) %>% 
-    top_n(10, gamma) %>%
-
-    ggplot() +
-    geom_col(aes(x = reorder(topic, gamma), y = gamma)) +
-
-    coord_flip() +
-
-    labs(title = NULL,
-         x = "Topics",
-         y = "Gamma"
-         )
-
-  ggsave(filename = str_c("gamma-", course, ".jpeg"), path = output_folder,
-         width = plot_width, height = plot_height)
-
-}
-```
-
-```{r fig_gamma}
-plot_gamma("COR1004")
-
-resize_factor <- 2
-
-plot_beta(4, resize_factor = resize_factor)
-plot_beta(19, resize_factor = resize_factor)
-```
-
-# Topic Expertise
-```{r}
-courses <- paste("Course", 1 : 3)
-
-transcript <- tibble(Course    = courses,
-                     Grade     = c(6  , 9  , 2.5))
-
-gamma <- tibble(Course    = courses,
-                `Topic 1` = c(0  , 0.2, 0  ),
-                `Topic 2` = c(0.7, 0.2, 0.4),
-                `Topic 3` = c(0.2, 0.2, 0.2),
-                `Topic 4` = c(0.1, 0.2, 0.1),
-                `Topic 5` = c(0  , 0.2, 0.2))
-
-df1 <- gamma %>% 
-  gather(key = Topic, value = gamma, -Course) %>% 
-  arrange(Course) %>%
-
-  left_join(transcript, by = "Course") %>%
-  mutate(contribution = Grade/10 * gamma)
-
-topic_expertise <- df1 %>%
-  select(-gamma, - Grade) %>% 
-  spread(key = Topic, value = contribution)
-
-# Table
-
-transcript %>% 
-  mutate(Grade = str_c(Grade, "/10")) %>%
-  latex_table("toy-transcript")
-
-gamma %>% latex_table("toy-gamma")
-
-topic_expertise %>% latex_table("toy-contribution")
-
-# Plot
-df1 %>% 
-  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
-  geom_col() +
-  coord_flip() +
-  labs(x = "Topics", y = "Topic Expertise")
-
-ggsave(filename = str_c("toy-expertise.jpeg"), path = output_folder,
-       width = plot_width, height = plot_height)
-```
-
-# CV
-```{r}
-fit_lasso %>%
-  ggplot(aes(y = cv_error, group = 1)) +
-  geom_boxplot() +
-  theme(axis.ticks.y = element_line(color = "white"),
-        axis.text.y  = element_text(color = "white"),
-        panel.border = element_rect(color = "white"),
-        panel.grid   = element_line(color = "white")
-        ) +
-
-  labs(y = "Cross-Validation Mean Absolute Error") +
-  coord_flip()
-
-ggsave(filename = str_c("CV.jpeg"), path = output_folder,
-         width = plot_width/1.5, height = plot_height/3.5)
-
-fit_lasso %>%
-  summarize(Mean = mean(cv_error),
-            `Weighted mean` = weighted.mean(cv_error, n),
-            Median = median(cv_error),
-            `Standard Deviation` = sd(cv_error),
-            Minimum = min(cv_error),
-            Maximum = max(cv_error)) %>%
-  gather(key = x, value = y) %>% 
-  kable("latex", booktabs = TRUE, col.names = NULL) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  as_image(file = str_c(output_folder, "/CV.pdf"))
-```
+version https://git-lfs.github.com/spec/v1
+oid sha256:8bddcd04ed0b8ed296f740584119b09de3d7d0958142947deb4804c3dc97ec3c
+size 12384
